### 2020-06-04 paper.tex
Clean endo of lines, trailing spaces, etc.

\documentclass[12pt,letterpaper,onecolumn,twoside]{article}
\usepackage[spanish]{babel}
\usepackage[left=2cm,right=2cm,top=1.5cm,bottom=1.5cm]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}\lhead{}\chead{}\rhead{}
\renewcommand{\headrulewidth}{0pt}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage{subfigure} % subgráfico
\usepackage{lscape}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage[noblocks]{authblk}
\usepackage{float}
\usepackage{cite}% para contraer referencias
\usepackage[usenames]{color}
\providecommand{\abs}[1]{\lvert#1\rvert}
\providecommand{\norm}[1]{\lVert#1\rVert}
 \title{\textbf{Optimization of Porous Silicon (PSi) with gradient refractive index (GRIN): A comparison with computational schemes with experimental results } }

\author[1]{C. A. Ospina de la Cruz}
\author[2]{W. L. Mochan }
\author[3]{V. Agarwal }

\affil[1]{{\scriptsize Posgrado en Ingenier\'ia y Ciencias Aplicadas del Centro de Investigación en Ingenier\'ia y Ciencias Aplicadas (CIICAp-IICBA), Universidad Autónoma del Estado de Morelos (UAEM), Cuernavaca CP 62209, México}}
\affil[2]{{\scriptsize Instituto de Ciencias F\'isica ,Universidad Nacional Autonoma de Mexico, Av. Universidad S/N, Col. Chamilpa, 62210 Cuernavaca, Morelos, Mexico  } }
\affil[3]{{\scriptsize Centro de Investigaci\'on en Ingenier\'ia y Ciencias Aplicadas,Universidad del Estado de Morelos, Av. Universidad 1001 Col. Chamilpa, Cuernavaca, Morelos 62209, Mexico  } }
\affil[*]{{\scriptsize Corresponding author: xxxxxx@xxxx.xxx}}
\date{}

\begin{document}
\renewcommand{\contentsname}{Contents}
\renewcommand{\abstractname}{Abstract}
\renewcommand{\tablename}{Table}
\vspace{50pt}

\maketitle
\begin{abstract}
The current density in a of Porous Silicon (PSi) with gradient  refractive index (GRIN) produced  by an electrochemical  attack on silicon (Si)  to  produce  porous  silicon (PSi), the calculated  porosity  of the GRIN structure depends  on the  position  and  distance  from  counter  electrode.   The proposed relationship shows, the  counter  electrode tip that acts  analogously  as a point charge  and  current density  for a geometry in an electrolytic  box by solving the electrostatic equations  with suitable  contour conditions.  Resulting  in an electrostatic model for photonic  crystals  with gradient refractive index (EMPCGRIN). The characterization of the  silicon structures was performed  by scanning electron microscopy   and  UV-Vis-NIR reflectance spectroscopy.  The obtained  results  open  the  possibility  of creating  silicon-based photonic  structures within  the  Visible-IR- range, within  the  sample at  different measuring distances,  where generally porous silicon does not strongly  absorb or disperse light.  Similarly, in the UV-Visible range  there is a strong absorption with more of light scattering. Having a greater  area of attack generating  different pores sizes and their porosity, and making an easy calculation  in the manufacture of porous silicon. \\

Keywords: Porous Silicon (PSi); Monolayer(Ml); Porosity(P); Reflectance Spectra.
\end{abstract}

\vspace{-0.8cm}
\singlespacing
\tableofcontents

%\newpage
\spacing{1}

 \section{Introduction}

 The structural behavior of nanostructured materials  has  become a  great  topic  of global  interest,  where numerous  research has been done so far \cite{I1}. We found a great way to go for future technological  explorations,  countless  challenges and  that  open a range of possibilities to develop further  study  on these issues\cite{I2}. Porous silicon (PSi) is a versatile nanostructured material and an excellent candidate as a technological platform for different sensing applications \cite{I3, I4}, due to its easy manufacturing,  large surface area, high surface reactivity,  and moreover, its optical transduction capacity.  Photonic crystals are multilayer dielectric structures that have periodicity in the dielectric function along one direction \cite{I5}. It has numerous studies for high reflectivity and the ability to adjust  the photonic  prohibited  band (PBG)\cite{I6} , which leads to possible applications  such as filters\cite{I7}, optical switches\cite{I8}, omnidirectional mirrors\cite{I9}, waveguides for PC \cite{I10} etc. In the conventional manufacturing of PSi the desired result  is to obtain  homogeneous samples (same structural characteristics) from the  periphery  to the center  of the electrochemically  attacked area.  However, with an asymmetric anodizing configuration,  samples with a lateral gradient in terms of pore size and thickness of the porous layer are obtained \cite{I101}. In this configuration,  the face of the platinum  electrode (cathode)  is relatively maintained  perpendicular  to the surface of the Si substrate (anode) at one end of the cell, so that the distribution of the current within the electrolyte  solution varies depending on the distance  of the electrode due to the resistance of the electrolyte,  resulting  in a decrease in current density as the distance from the electrode increases \cite{I102, I103}. The result is a porous surface with different pore sizes ranging from a few nanometers  to pores on the order of a few micrometers  \cite{I104}. The dimensions of the pores obtained on the same chip can be controlled by adjusting the anodizing current and electrolyte concentration \cite{I11}. Currently, these types of samples have found their application relevant as optical band filters \cite{I12}, devices with a multidirectional photonic band (photonic bar codes) \cite{I13} and mainly as biosensors. In this way, the effect of different topographies (porosities in the same sample) on the culture / adhesion of certain cells \cite{I14} is studied, considerably reducing the number of samples and cost of the study. In addition, they are also very useful when a biomolecule size-exclusion technique is required allowing the identification and separation of these biological compounds \cite{I15}. Recent studies  have shown that  the  combination  of thermal  oxidation  and infiltration of TiO2   by ALD offers the  opportunity to manufacture  a high index of refraction  of contrast, visibly transparent GRIN optical elements from PSi absorbent structures \cite{I16}. A Despite previous research on the formation of porous silicon with GRIN, type p in manufacturing and characterization, there was no control of current densities, much less a model that  explained said lateral  gradient. In this work, we reported a gradient refractive index (GRIN) structure by varying the current density on the fabrication of porous silicon photonic structure. This current density values, depth, and porosity of the photonic structure were calculated from an electrostatic model for photonic crystals with a gradient refractive index (EMPCGRIN). Moreover, the theoretical and experimental studies were exhibited similar results.\\
 The paper is organized as follows. In Section 2  we report the effect of how the current density can be calculated from an electrostatic model for photonic crystals with gradient refractive index (EMPCGRIN), demonstrating that there is a direct relation of the gradient generated by the electrode when it attacks the Silicon sample, we can see the depth of the structure and its porosity, in each of the measuring points. In Subsection 2.2 we present a formalism based on the methods used for the analysis of photonic crystal structures is the transfer matrix method. We use it to investigate the reflectance of light in a one-dimensional photonic crystal. In Section 3 we provide experimental  details about the manufacture of PS dielectric multilayers and Section 4 we shows the comparison of numerical and experimental results followed. Finally,  the conclusions given in Section. 5

 \section{Theory}
 \subsection{Electrostatic Model for Photonic Crystals with Gradient Refraction Index (EMPCGRIN)}
The calculate  current density in a GRIN structure produced by an electrochemical attack on Si to produce Porous Si with a position-dependent porosity due to the distance to the counter electrode. A simplifies  calculation  with geometry,
assumimg  in the form of a whole prism on the sides a, b, c with a, b horizontal and c vertical. Here c considered as the height of the liquid, and the walls are insulating, but the bottom is completely covered with the sample, which act as good conductor. The electrode is a thin insulated cable with tip, which  a point  current source.
\begin{figure}[H]
	\centering
	\includegraphics[scale=.4]{../Images/celdan}
	\caption{\emph{Diagram of the Electrolytic cell where we can see the shape of a prism on the sides a, b, c with a, b horizontal and c vertical. I'll take as the height of the liquid. The walls are insulating, but the bottom is completely covered by the sample, I suppose it is a good conductor. The tip of the electrode is a thin insulated wire located at $ \vec{r}_0 $.}}
\end{figure}
The current in the electrolyte is $ \vec {J} = \sigma \vec{E} $ with $ \sigma $ is the conductivity. This for the stationary case $ \bigtriangledown \cdot \vec{j} = 0 $. The electric field is derived from the electric potential, $\vec {E} = - \bigtriangledown \varphi $.
And we can say that $ \bigtriangledown^{2} \varphi = 0 $, since the sample is a relatively good conductor, when connected to earth $ \varphi(x, y, 0) = 0 $. Integrating $ \vec{J} $ over a small sphere superimposing the electrode gives $ \int ds \cdot \vec{J} = I $.
The current density that carries the current to the tip. So
  \begin{equation}
\int ds \cdot \vec{E} = \dfrac{I}{\sigma}
\end{equation}
The problem to be solved is thus, to obtain the potential produced by a point charge,
  \begin{equation}
 q_{_{0}} = \dfrac{I}{4 \pi \sigma}
 \end{equation}
In the positions$\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ is the tip of the electrode that is in the presence of a ground conductor plane grounded $ z = 0 $ and enclosed on the insulating walls at $ (0, y, z) $, $ (a, y, z) $, $ (x, 0, z) $ , $ (x, b, z) $. The surface of the liquid is also not conductive to $ (x, y, c) $, the normal current is $\vec{j} \cdot \hat{n}=0$ and the normal of the field is $ \vec{E} \cdot \hat{n}=0  $. i.e
\begin{equation}
E_{_{x}}(0, y ,z)= E_{_{x}}(a, y ,z)=E_{{_y}}(x, 0 ,z)=E_{{_y}}(x, b ,z)=E_{{_z}}(x, y ,c)=0
\end{equation}
This has a mixture of Dirichlet-Neumann type boundary conditions. By using the simplified prism geometry  can solve the problem using the theory of image loads. Each load has an image of the same sign and magnitude for each lateral insulating surface and the opposite sign change in the lower part of the conductive plane, as follows.
 \begin{figure}[H]
 \centering
 \includegraphics[scale=.6]{../Images/Cellgrin}
 \caption{\emph{a) Diagram of a rectangular electrolytic cell, with a real charge in the corner of the cell with its charges ($ q $) images of the same sign in $ Z_0 $ and another charge image ($ -q $) with change of sign located below the conductor in position $ -Z_0 $. b) The upper face seen from above, a real load and its image loads in $ Z_0 $. c) All this formed a systems of a real load and its image loads produced by the cell walls and its other images seen from above, forming a periodic space. }}
 \label{fig:T1}
\end{figure}

From Fig. \ref{fig:T1} we assume that if i put a real charge ($ q $) in at $\vec{r}_0= (x_0, y_0, z_0)$, in the corner of the electrolytic box it induces images at $\vec{r}_1= (-x_0, y_0, z_0)$ due to a reflection in $ (0, y, z) $, images in  $\vec{r}_2= (-x_0, -y_0, z_0)$ due to a reflection in $ (x, 0, z) $ y the image of the image in $\vec{r}_3= (x_0, -y_0, z_0)$  for  $\vec{r}_j$, $(j=0,1,2,3)$. Then, these four charges are reflected on the other two surfaces and the eight new images are reflected on the original surface, etc., producing a periodic 2D rectangular network with unit cells of signs $ L_x = 2a $, $ L_y = 2b $ and with a base of 4 equal charges. This entire network is reflected from the bottom with an opposite sign load (below the driver). Periodic copies separated by the vacuum in the $ xy $ plane whose area is being increased to achieve convergence. \\
\textbf {Problem considerations}: The problem is the potential, the field and the current produced by a periodic 2D network of a real load and all its images. The potential due to a periodic network is automatically found in the plane making a sum of 2D Fourier.

\begin{eqnarray}
 \rho(\vec{r}) =q \displaystyle\sum_{R}  \ \delta (\vec{r}-\vec{R}-\vec{r}_0) =\dfrac{q}{A}  \displaystyle\sum_{G}  e^{i G \cdot (\vec{r}-\vec{r}_{0})} \delta (z-z_0)
\end{eqnarray}
Where $ {R} $ is the 2D Bravais network and $ {G} $ its reciprocal network. It is written $ \phi (\vec{r}) = \displaystyle \sum _ {\vec{G}}  \phi_{_{G}}(z) e^{i \vec {G} \cdot \vec {r}} $. So the Poisson equation $ \bigtriangledown^2 \phi = -4 \pi \displaystyle \sum_{\vec{R}} \delta (\vec{r} - \vec{R} - \vec{r}_0) $.
Becomes
 \begin{eqnarray}
 \dfrac{\partial^2 \phi_{_{G}}(z)}{\partial z^2}+ G^2\phi_{_{G}}(z)= -\dfrac{4 \pi}{A}  q   e^{i \vec{G} \cdot \vec{r}_{_0}} \delta (z-z_0)
 \end{eqnarray}
Solving the homogeneous equation above and below $ z = z_0 $, using symmetry and conditions at $ \pm \infty $ we obtain $ \phi_{_{G}} = \phi_{_{G}}^{0} e^{ G \abs{z-z_0}} \ \ \ \ \ (G \neq 0) $. And adjusting the singularity
 \begin{eqnarray}
 \phi_{_{G}}(z)= \dfrac{2 \pi q}{AG}  e^{- G \abs{z-z_0}} e^{-i \vec{G} \cdot \vec{r}_{_0}} \ \ \ \ \ (G\neq 0)
 \end{eqnarray}
For the case $ G = 0 $ is similar $ \phi_{_{G = 0}} (z) = \dfrac{-2 \pi q}{A} \abs{z-z_0} + K, $ $ \ \ $ (K is a constant). Here $ A = L_x L_y $ is the unit cell area
 \begin{eqnarray}
 \phi(\vec{r}) = K-\dfrac{2 \pi q}{A}  \abs{z-z_0} +\dfrac{2 \pi q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} e^{- G \abs{z-z_0}}   e^{i \vec{G} \cdot \vec{r}-\vec{r}_0}
 \end{eqnarray}
Adding all the images loads,
  \begin{eqnarray}\label{Eq:EC11}
 \phi(\vec{r}) = -\dfrac{8\pi q}{A} \bigg((\abs{z-z_0}-\abs{z+z_0} ) +\dfrac{8\pi q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \bigg( e^{- G \abs{z-z_0}} -e^{- G \abs{z+z_0}}  \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}
 \end{eqnarray}
At a height $ 0 <z <z_0 $ I simplify
   \begin{eqnarray}
 \phi(\vec{r}) = -\dfrac{16\pi q}{A} \bigg( z +\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \sinh(G z)  \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}} \bigg)
 \end{eqnarray}
If the surface of the liquid is at a finite height c, then we can use images, like:
\begin{figure}[H]
	\centering
	\includegraphics[scale=.6]{../Images/celd1}
	\caption{\emph{Diagram shows that there is a positive (real) plane $ z_0 $, a negative image at $ -z_0 $ below the conductor ($ z = 0 $) and its images are a positive plate at $ 2c-z_0 $ and a negative plate at $ 2c + z_0 $, the image is repeated vertically with the period $ L_z = 4c $}}
		\label{fig:Celda1}
\end{figure}
In Fig. \ref{fig:Celda1} it is observed that there is a positive (real) plane $ z_0 $, a negative image at $ -z_0 $ below the conductor ($ z = 0 $) and its images are a positive plate at $ 2c-z_0 $ and a negative plate at $ 2c + z_0 $. Also, the image is repeated vertically with the period $ L_z = 4c $. Therefore, the equation \ref{Eq:EC11} would be rewritten, like this
 \begin{eqnarray}\label{Eq:EC1}
 \nonumber\phi(\vec{r}) = K+\dfrac{8\pi q}{A} \displaystyle\sum_{n} -\bigg(\abs{z-z_0-nL_z}-\abs{z+z_0-nL_z}-\abs{z+2c+z_0-nL_z}+\abs{z-2c-z_0-nL_z}\bigg) +\\ \nonumber \dfrac{1}{G}\displaystyle\sum_{\vec{G}}\bigg( \displaystyle\sum_{n} \bigg( e^{-\abs{z-z_0-nL_z}} +e^{-\abs{z+z_0-nL_z}}-e^{-\abs{z+2c+z_0-nL_z}}-e^{-\abs{z-2c-z_0-nL_z}}  \bigg)\bigg)\cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}\\
\end{eqnarray}
The constant K is chosen thus $ \phi (z = 0) $, substituting in Eq. (\ref {Eq:EC1}) and after factoring $ e^{- nGL_Z} $ we are explicitly left with the geometric sum over $n$
 {\small
 \begin{eqnarray}
 \nonumber\phi(\vec{r}) = K+\dfrac{16\pi q}{A} \bigg(z+z_0  + \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \bigg(e^{-Gz_0} \sinh(Gz)+e^{-Gz_0(2c_z)} \sinh(Gz_0) -e^{-2Gc} \sinh(Gz) \sinh(Gz_0) \\ \nonumber \dfrac{1+\cosh(2Gc)}{\sinh(2Gc)} - e^{-2Gc}\cosh(2Gc) \sinh(Gz_0)   \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}   \bigg)\\
 \end{eqnarray}
}
Evaluating for $ z = 0 $
 \begin{eqnarray}\label{Eq:EC2}
\nonumber\phi(x, y, 0) = K+\dfrac{16\pi q}{A} \bigg(z_0  + \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \bigg(e^{-2Gc} \sinh(Gz_0)-e^{-2Gc} \sinh(Gz_0)   \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}\bigg) =\\ \nonumber = K+\dfrac{16\pi q}{A} \\
\end{eqnarray}
Independent of $ x $ and $ y $ to configure
 \begin{eqnarray}
 K=\dfrac{16\pi q}{A}
\end{eqnarray}
I can further simplify Eq. (\ref {Eq:EC2}) to get,
 \begin{eqnarray}
\nonumber\phi(\vec{r}) = \dfrac{16\pi q}{A}\bigg( z  + \displaystyle\sum_{\vec{G}}\dfrac{\sinh(Gz_0)}{G} \bigg(e^{-Gz_0} -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\
\end{eqnarray}
I am sure it is correct. Then it goes to zero at $ z = 0 $. The term with c disappears if $ c \longrightarrow \infty $. The sum converges when $ G \longrightarrow \infty $ if $ z <z_0 <c $ and diverges to $ z \longrightarrow z_0 $. So it seems ready for calculation.
The normal component of the field is
\begin{eqnarray}
\nonumber E_\perp = -\dfrac{16\pi q}{A}\bigg( 1  + \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \cosh(Gz)\bigg(e^{-Gz_0} -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\
\end{eqnarray}
And the current density is for any $ z $, for our calculation we choose that $ z = 0 $
\begin{eqnarray}\label{Eq:J}
\nonumber J_\perp = -\dfrac{I}{ab}\bigg( 1  + \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \cosh(Gz_0) \bigg(e^{-Gz_0} -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\
\end{eqnarray}
Integrating on the surface of the sample is obtained $I_{nm} =\int^{a}_0 dx \int^{b}_0 dy \ \ e^{i\vec{G}\vec{r}}$
\begin{eqnarray}
\nonumber I_{nm}=\dfrac{1}{G_x G_y} (e^{-iG_xa}-1) (e^{-G_y b}-1) \\ I_{nm}=\dfrac{ab}{nm \pi^2} ((-1)^n-1-1)(-(1)^m-1-1)
\end{eqnarray}
Using the factor of the reciprocal vector in this way $ \vec {G} = \bigg (\dfrac{\pi}{a} n, \dfrac{\pi}{b} m \bigg) $,
however, as all the coefficients of $ e^{- i \vec{G} \vec{r}} $ in \ref{Eq:J} they are even in $ \vec{G} $ and the integral is odd in n and m, only the constant term taxpayer to the integrated current
\begin{eqnarray}
\nonumber I^{nm} =\int \vec{J} dx  dy =-\int \vec{J}_\perp dx  dy=\dfrac{I}{ab}\int dx \int dy=I
\end{eqnarray}
\subsection{Transfer Matrix Method (TMM)}
One of the methods used for the analysis of photonic crystal structures is the transfer matrix method. We use it to investigate the reflectance of light in a one-dimensional photonic crystal. The electric and magnetic fields within the layers are shown as $E_m$ and $H_m$. Then we can specify the electric and magnetic fields in the air, $ E_0 $ and $ H_0 $, by solving the following matrix equation:
\begin{equation}
\left[
\begin{matrix}
E_{_{0}}\\
H_{_{0}}
\end{matrix}
\right]= \textbf{M}_{_{1}}, \textbf{M}_{_{2}},...,\textbf{M}_{_{N}} \left[
\begin{matrix}
E_{_{m}}\\
H_{_{m}}
\end{matrix}
\right]
\end{equation}
Where N is the total number of layers including the cavity layer and $ M_j $ is the matrix characteristic of the layer $ j $ specified by:
\begin{equation}
\textbf{M}_j = \left[
\begin{matrix}
\cos \delta_j & -\frac{i}{\eta_j} \sin \delta_j \\
-i\eta_j \sin\delta_j & \cos\delta_j
\end{matrix}
\right]
\end{equation}
and
\begin{equation}
\delta_j= \frac{2\pi}{\lambda} \tilde{n}_j d_j \cos \theta_j
\end{equation}
where $ \lambda $ is the wavelength, $ \tilde{n}_{_{j}} = n_{j} - ik_{_{j}}$ is the complex refractive index (CRI) of the layer, $ d_j $ is the thickness of the layer, and $ \theta_j $ is the angle of refraction of light in the $ j $ layer. The parameter $ \eta_ {j} $ for layer j is defined as:
\begin{equation}\label{Eq:Mt1}
\eta_j=\sqrt{\frac{\epsilon_0}{\mu_0}}\tilde{n}_j cos\theta_j \hspace{1cm} (TE \ \ mode)
\end{equation}
y
\begin{equation}\label{Eq:Mt2}
\eta_j=\sqrt{\frac{\epsilon_0}{\mu_0}} \frac{\tilde{n}_j}{cos\theta_j} \hspace{1cm} (TM \ \ mode)
\end{equation}
where $ \epsilon_0 $ and $ \mu_0 $ are permittivity and free space permeability, respectively. The transfer matrix of all the photonic crystal is given by:
\begin{equation}
\textbf{M}=\textbf{M}_1,\textbf{M}_2,...,\textbf{M}_N= \left[
\begin{matrix}
m_{11} & m_{12} \\
m_{21} & m_{22}
\end{matrix}
\right]
\end{equation}
We can write the reflection and transmission coefficients in a one-dimensional photonic crystal nanocavity as:
\begin{equation}
r=\frac{\eta_0(m_{11}m_{12}\eta_m) -(m_{21}+m_{22}\eta_m)}{\eta_0(m_{11}m_{12}\eta_m) -(m_{21}+m_{22}\eta_m)}
\end{equation}
end
\begin{equation}
t=\frac{2\eta_0}{\eta_0(m_{11}m_{12}\eta_m)+(m_{21}m_{22}\eta_m)}
\end{equation}
where $ \eta_0 $ and $ \eta_m $ are parameters for air and outlet layers, respectively (as defined in equations \ref{Eq:Mt1} or \ref{Eq:Mt2}). Furthermore, the reflectivity R and transmittance T of the entire photonic crystal nanocavity is given by:
\begin{equation}
R=|r|^{2}
\end{equation}
y
\begin{equation}
T=\frac{\eta_m}{\eta_0}|t|^{2}
\end{equation}
\section{Experimental Details}
\begin{figure}[H]
	\centering
	\includegraphics[scale=0.6]{../Images/DE1}
	\caption{\emph{Schematic of the experimental set-up for fabrication of porous silicon with GRIN. a) Represents an outline of the surface section, divided by three regions A, B and C, corresponding to High, Medium and Low Porosity respectively. b) It is the diagram of the electrochemical cell with its parts: silicon wafer, Teflon cell, platinum point electrode, Electrochemical Aqueous solution and the connection of the circuit with the cathode and anode. c) It is a schematic drawing of the Cross section of the electrochemically attacked porous silicon seen in three different regions as mentioned above. }}.
	\label{fig:DE1}
\end{figure}
In the Fig. \ref{fig:DE1} a shows schematic representation of the experimental setup where porous silicon can be manufactured with GRIN, taking into account the considerations of the electrode as tip, the rectangular cell and the sample (silicon wafer) with the largest rectangular attack area.
In Fig. \ref{fig:DE1} a) we draw an outline of the surface section, divided by three regions A, B and C, dependes in therir porosity i.e., High, Medium and Low Porosity. All this corresponding to  expected to be obtained in the experiments. Fig. \ref{fig:DE1} b) the scheme shows the electrochemical cell with its parts: silicon wafer, teflon cell, platinum point electrode, electrochemical Aqueous Solution and the connection of the circuit with the cathode and anode. Finally, Fig. \ref{fig:DE1} c) it is a schematic drawing of the Cross section of the electrochemically attacked porous silicon seen from three different regions as mentioned above. In section 3.1 we give the details used to carry out our experiments.

\subsection{Fabrication of Porous Silicon Monolayers GRIN}
Some of the simulated photonic structures were made by electrochemical anodization on an oriented (100) p-type crystalline Si wafer (resistivity 0.002 - 0.005 $ \Omega \cdot cm $), under galvanostatic conditions. The electrochemical anodization process was performed at room temperature, with an electrolytic mixture of aqueous hydrofluoric acid (HF) (concentration: 48 $ \% $ wt), glycerol (purity: 99.8 $ \% $ wt) and ethanol (purity: 99.9 $ \%$ wt ) in 3: 7: 1 volume ratio, respectively. After the anodizing process, the samples are rinsed with ethanol (purity: 99.9 $ \% $  wt). The layout of the cell used is as seen in Fig. \ref{fig:DE1} b), with an area of $ 1,206 \ \ cm^2 $ (this is the area attacked in the process), has a rectangular shape ($ 0.62 \ \ cm \times 2.03 \ \ cm $)  so that the current densities  that attacks has a lateral gradient with a greater surface area. They were manufactured with a fixed current of $ 5 \ \ mA $ to generate different current densities ranging from $ 6  $ to $ 2.5 \ \ mA / cm^2 $. Similarly, we use the current from $ 40 \ \ mA $ to generate $ 50 $ to $ 20 \ \ mA / cm ^ 2 $. The cathode is made of a platinum wire that was arranged in the form of a tip with an approximate diameter of ($ 0.5 \ \ mm $).
\subsection{Reflectance Measurement}
In the experiemental parte the reflectivity measurements were carried out with a Perkin Elmer Lambda 950 UV-Vis-NIR spectrophotometer. To calculate the complex refractive index $ \tilde{n}_{_{PSi}} = n_{_ {PSi}} - ik_{_{PSi}} $ of a porous layer with homogeneous porosity and thickness with smooth interfaces to throughout the entire structure, the more suitable is the adjustment procedure of the experimental reflectance or transmittance spectrum, this is for the theoretical part. In the case of the reflectance spectrum. The corresponding theoretical calculations were carried using procedure for single  smooth layer (monolayer).
 \begin{eqnarray}\label{Eq:ECMR}
R=\dfrac{r _ {_ {01}}r _ {_ {12}} e^{-2i\delta}}{1+r _ {_ {01}}r _ {_ {12}} e^{-2i\delta}}
\end{eqnarray}
where $ r_{_ {01}} $ y $ r_{_ {12}} $ are the Fresnel reflectance coefficients at the interfaces $aire/PSi$ y $PSi/c-Si$ which are defined in terms of their complex refractive index ($\tilde{n}_{_ {1}} $, $\tilde{n}_{_ {2}} $ y $ \tilde{n}_{_ {3}} $), for them $r_{_{ij}}=(\tilde{n}_{_{i}}\cos\theta_i-\tilde{n}_{_{j}}\cos\theta_j)/(\tilde{n}_{_{i}}\cos\theta_i+\tilde{n}_{_{j}}\cos\theta_j)$, ($j=i=0,1,2$), whilst $\delta=2\pi d/\lambda\sqrt{\tilde{n}^2_{_{2}}-\tilde{n}^2_{_{1}}\sin \theta_1}$.
 To adjust the reflectance spectrum, the layer thickness is an input parameter in the Eq.\ref{Eq:ECMR}. The advantage of this method is the possibility of taking into account the interface roughness effect by including the Davies-Bennett factor in the coefficient of each Fresnel \cite{I17, I18, I19}, which represents the roughness of a Gaussian distribution.
\subsection{Morphological studies}
The morphologies of the etched porous layers (cross-sectional) was observed using SEM Hitachi SU1510 scanning electron microscopes (Hitachi High Technologies Canada, Inc., Toronto, Canada), the thickness  and porosity  of each fabricated  film was measured.
 \subsection{Refraction Indices Monolayer of Porous Silicon GRIN }
Through the electrochemical anodization of c-Si wafers, Psi monolayers were obtained. For the refractive index of each monolayer Psi calcalated by ussing  Bruggeman effective medium theory, as we consider that we have a homogeneous medium associated with effective dielectric function \cite{I20}. This effective dielectric function is related to the dielectric functions of the two media, consisting of two materials (air and silicon), where it is assumed that all the pores or islands of the bulk material experience an average electric field; the equation is expressed as follows:
 \begin{eqnarray}\label{Eq:Brugg}
 p\dfrac{\varepsilon_{_{air}}-\varepsilon_{_{PSi}}}{\varepsilon_{_{air}}+\varepsilon_{_{PSi}}}+(1-p)\dfrac{\varepsilon_{_{Si}}-\varepsilon_{_{PSi}}}{\varepsilon_{_{Si}}+ \varepsilon_{_{PSi}}}
 \end{eqnarray}
 where $ p $ is the volume fraction of air within the PSi layer (porosity); $\varepsilon_{_{air}}$ is the dielectric function of air; $\varepsilon_{_{Si}}$ is the dielectric function of c-Si, and $\varepsilon_{_{PSi}}$ represents the dielectric function of PSi. The dielectric function is a complex number and is related to the complex refractive index ($\tilde{n} = n - ik$), which is made up of real and imaginary parts, as follows $\varepsilon=\tilde{n}^2$. Its real part ($ n $) represents the ordinary refractive index when no light absorption occurs. The imaginary part ($ k $) is known as the extinction coefficient. The extinction coefficient determines the absorption rate in the medium \cite{I21}. Porosity can be estimated using the Bruggeman approximation, from Eq. \ref{Eq:Brugg} provided that the dielectric functions of each component (air and c-Si) are known.

 \subsection{Fabrication  of Microcavities of Porous Silicon GRIN }
 A conventional way to fabricate the porous silicon microcavity (MC) is a defect with a mode located between two DBRs (Distributed Bragg Reflector). Alternate layers of high refractive index (H) and low (L) refractive index are obtained, satisfying the Bragg condition $n_{_{i}}d_{_{i}}=\frac{\lambda_{_{c}}}{4}$  where $ i = H, L $. The defect must meet the condition  $n_{_{L}}d_{_{L}}=\frac{\lambda_{_{c}}}{2}$, and the MC has the following sequence: $$ (HL)_6 HH (LH )_6 $$
 Initial data for conventional design we use $\lambda_{_{c}}= 0.67 \mu m$, $n_{_{H}} =2,6$, $P_{_{H}} =0.46$, $d_{_{H}}=0.066 \mu m  $, $t_{_{H}}=35 s  $ and for $n_{_{L}}= 1,4$,  $P_{_{L}} =0.75$, $d_{_{L}}=0.117 \mu m  $, $t_{_{L}}=11 s  $. All of this data is for the $ 0 $ point of the sample that is located at one end of the sample just below the tip counter-electrode.\\
 Our proposal for the fabrication of porous silicon GRIN microcavities uses the same conditions for fabrications of porous silicon GRIN monolayers as in section 3.1, and taking the conventional data mentioned above. The porous silicon microcavities (PSiMC) with gradient refractive index (GRIN), were manufactured with different current densities ranging from $ 6 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a current of $ 5 \ \ mA $, with high refractive index $n_{_{H}} \sim 2,761 $ to $ 2,808 $ and porosities from $ 0.44 $ to $ 0.39 $. Also for $ 50  $ to $ 20 \ \ mA / cm ^ 2 $, current of $ 38 \ \ mA $, for low refractive index $n_{_{L}}\sim 1,448 $ to $ 2,267 $ and with the corresponding  porosities of $ 0.75 $ to $ 0.64 $. Using our calibration ratio to design GRIN structures,  the corresponding current density for each measurement point.

\section{Discussion and Results}
\subsection{Simulation of the EMPCGRIN model}
 To test the developed  idea in the theoretical section, we find a relation of the tip of the counter electrode that acts similarly as a point charge and the current density for a geometry in an electrolytic box and solve the electrostatic equations with suitable boundary conditions. Resulting in an electrostatic model for photonic crystals with a refractive index with gradient (EMPCGRIN).
\begin{figure}[H]
	\centering
	\includegraphics[scale=0.7]{../Images/G123}
	\caption{\emph{ Simulation to calculate the current density in a structure with gradient refractive index (GRIN) produced by electrochemical attack on crystalline silicon to produce porous silicon (PSi), with a current density profile $ J (mA / cm ^ 2 ) $ normalized with the electric current $ I (mA) $, we have $ J / I \sim 0.5 \ \ a \ \ 1.2 (cm^{-2}) $, for a cell of $ a = 2.03 \ \ cm $ y $ b = 0.62 \ \ cm $, with an electrode height $ Z_0 = 0.96 \ \ cm $} Eq. (\ref{Eq:J})}.
		\label{fig:DR1}
\end{figure}
We consider Fig. \ref{fig:DR1} which come from solving Eq. (\ref{Eq:J}), calculating the current density as a function of the rectangular cell area of $1,206 \ \ cm^2 $,  the programming with the PERL PDL package and corresponding graph in gnuplot. We optimize the appropriate values so that our current density adequately attacks crystalline silicon, giving the gradient effect. We use as length $a = 2.03 \ \ cm $ and width $b = 0.62 \ \ cm $ the height of the solution is $ c = 1 \ \ cm $ and we could locate the tip of the electrode at $ R_0 = (X_0 = 0.2 , \ \ Y_0 = 0.4 \ \, Z_0 = 0.96) \ \ cm $ and evaluated at the surface on the silicon interface, in the plane $ Z = 0 $. In this same Figure \ref{fig:DR1}, we obtain a current density profile $ J (mA / cm^2) $ normalized with the electric current $ I (mA) $, we have $ J / I \sim 1.2 \ \ a \ \ 0.5 (cm ^{-2}) $, as we see in Fig. \ref{fig:DR1} a) an effect that happens on the surface of the sample, a change of contrate due to the different densities of attacked currents. We see the decay behavior that the profile has as Fig. \ref{fig:DR1} b) which is a cut on the axis of $ a $. When we vary the currents we can observe the behavior of changes in the normalized current density, with the data obtained through the simulation we could have a better optimization in the design of porous silicon proposing a new and novel experimental arrangement, in the same way we can give ourselves an idea by means of the graph of how the attack would be and the formal side of the pores in the silicon.

\subsection{Monolayers GRIN Porous Silicon }
\begin{figure}[H]
	\centering
	\includegraphics[scale=.3]{../Images/celdan2}
	\caption{\emph{ Mechanical 3D modeling, design of the electrochemical cell where we can see the shape of a prism giving the required and necessary data for the experiments. The design of the cell used is $ 1,206 \ \ cm ^ 2 $ (this is the area attacked in the process), the area attacked is rectangular ($ 0.62 \ \ cm \times 2.03 \ \ cm $) and a height ( $ 1.2 \ \ cm $) a) Complete cell b) Cell without top cover and c) Top view}}
	\label{fig:por1}
\end{figure}
We can see in Fig. \ref{fig:por1}, 3D modeling the mechanical design for the electrochemical cell  better optimization in manufacturing silicon pores where we can see the shape of a prism giving the required data. The design of the cell used is $ 1,206 \ \ cm ^ 2 $ (this is the area attacked in the process), the area attacked is rectangular ($ 0.62 \ \ cm \times 2.03 \ \ cm $) and a height ( $ 1.2 \ \ cm $), all this in order to optimize our experiments adjusted to all the needs that this required.
\begin{figure}[H]
	\centering
	\includegraphics[scale=.5]{../Images/SPgrin51}
	\caption{\emph{a) Silicon sample attacked with an electrolytic mixture of aqueous hydrofluoric acid (HF) (concentration: 48 $ \% $  wt), glycerol (purity: 99.8 $ \% $  wt) and ethanol (purity: 99.9 $ \% $  wt ) in 3: 7: 1 volume ratio, respectively. Obtaining a monolayer of porous Silicon with GRIN G1 with an initial current of G1 (5 mA), with an attack time of 600s. Three different locations are considered, denoted as follows, A (0.3cm) and B (0.8cm) and C (1.7cm). b) Reflectance measurements to know the optical properties at each of the points and the adjustments that were produced by means of the equation \ref{Eq:ECMR}. c) We have the indices of refraction of the complex porous silicon GRIN, where we calculate the real and imaginary part by means of the equation \ref{Eq:Brugg}. for different porosities at each point, A (P = 0.44), B (P = 0.42) and C (P = 0.40) } }
	\label{fig:DR3}
\end{figure}
 The Fig. \ref{fig:DR3} a) three locations at different points are considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $, from the sample of PSi GRIN $ G1 (I = 5 mA) $. Also the Fig. \ref{fig:DR3}. b), we have the reflectance measurements to know the optical properties and the adjustments that were produced by means of the equation \ref{Eq:ECMR}. In the Fig. \ref{fig:DR3} c) are indices of refraction of the porous silicon complex GRIN, where we calculate the real and imaginary part by means of Eq. \ref{Eq:Brugg} for different porosities at each point, $ A (P = 0.44) $, $ B (P = 0.42) $ and $ C (P = 0.40) $. Location $ A $ is closest to the electrode, while location $ C $ is furthest to the other end of the sample. Since the current density is applied from one end, the field lines attack the sample laterally to the silicon wafer, in the present configuration, an assembly was made based on the simulated data shown in Fig. \ref{fig:DR1} the experimental part was taken a platinum electrode covering its surface, leaving only a very small area, as if it were a tip. The electrochemical reaction takes place when we apply currents from an anode end (electrode tip) to the silicon substrate (resistivity $ 0.002 - 0.005  \Omega \cdot cm $), through an electrolyte forming a current circuit. The reflectance spectra of the newly recorded G1 samples measured at points $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $ are presented in Fig. \ref{fig:DR3} b), a numerical reflectivity adjustment was performed using the transfer matrix method for the case of a porous monolayer in Si. It should be noted that the adjustment made was considered a spectral range of the wavelength of the experimental reflectivity spectra for which the silicon can be considered the complex index and thus find the refractive index of the complex porous silicon with the purpose of determining the porosity and the experimental physical thickness (nm) by means of the SEM. The formation of PSi GRIN in the thickness occurs due to the variation in the concentration of the voids available at the Si electrolyte interface, therefore, an increase in the applied lateral current density increases the dimension of the pores and their depth. Thus, the extent of the porous film showing a gradient that can be controlled from the lateral current density.
\begin{figure}[H]
	\centering
	\includegraphics[scale=.5]{../Images/semD11}
	\caption{\emph{Characterization of a monolayer of PSi GRIN G1 with an initial current of $ 5 \ \ mA $, seeing the morphology and depth of the cross section of several SEM micrographs, at different points, $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $. We can see the sample size for each measurement point, the depth $ d (A) = 1320 \ \ nm $, $ d (B) = 997 \ \ nm $ and $ d (C) = 605 \ \ nm $ } }
	\label{fig:DR4}
\end{figure}
In the Fig. \ref{fig:DR4} shows the cross section views   at points $ A (0.3 \ \ cm) $, $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $, we can measure the thickness for each point of the sample $ G1 (I = 5 \ \ mA) $, $ d (A) = 1320 \ \ nm $, $ d (B) = 997 \ \ nm $ and $ d (C) = 605 \ \ nm $. Likewise, we could check it for a second sample $ G2 (I = 40 \ \ mA) $, with porosities for each point, $ A (P = 0.76) $, $ B (P = 0.73) $ and $ C (P = 0.68) $ and the depths $ d (A) = 1950 \ \ nm $, $ d (B) = 1690 \ \ nm $ and $ d (C) = 1430 \ \ nm $, designed in the same way as the shows G1, only varying the current taking into account the current density ratio for each point. Apart from that, a structural gradient was formed, along the direction \emph{ a}  of the axis of the $ x $, where the tip of the electrode is near the point $ A $ and away from the point $ C $ of the substrate, using the proposed experimental setup. In addition, it was possible to control the current density based on the position of the sample and the depth, seen in the SEM micrographs.
 \begin{figure}[H]
 	\centering
 	\includegraphics[scale=.7]{../Images/grinJDR}
 	\caption{\emph{a) It is the relation of the current density $ J (mA / cm ^ 2) $ normalized with the electric current $ I (mA) $, we have $ J / I \ sim 1.2 \ \ a \ \ 0.5 ( cm^{-2}) $, when we apply it to two samples $ G1 (I = 5 \ \ mA) $ and $ G2 (I = 40 \ \ mA) $ depending on the axis $ a $ $ (0.1 ... 2.0 \ \ cm) $, measured at points $ A (0.3 \ \ cm) $ , $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $. b) The attack speed $ v = d (J_i) / t (nm / sec) $, the depths (thickness $ d (J_i) $, $ i = $ $ A (0.3 \ \ cm) $, $ B ( 0.8 \ \ cm) $ y $ C (1.7 \ \ cm)) $ taken in SEM micrographs $ d (J_i) (nm) $ and attack times $ G1 (t = 600 \ \ s) $ y $ G2 (t = 200 \ \ s) $, depending on the axis $ a $ $ (0.1 ... 2.0 \ \ cm) $ } }
 	\label{fig:JDR}
 \end{figure}
In Fig. \ref{fig:JDR} a) It is the relation of the current density $ J (mA / cm ^ 2) $ normalized with the electric current $ I (mA) $, we have $ J / I \ sim 1.2 \ \ a \ \ 0.5 (1 / cm ^ 2) $, when we apply it to two samples $ G1 (I = 5 \ \ mA) $ and $ G2 (I = 40 \ \ mA) $ depending on the axis $ a $ $ (0.1 ... 2.0 \ \ cm) $, measured at points $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $.
The Fig. \ref{fig:JDR} b) we can calculate the attack speed $ v = d (J_i) / t (nm / s) $, where the depths (thickness $ d (J_i) $, $ i = $ $ A (0.3 \ \ cm) $, $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm)) $ taken in SEM micrographs $ d (J_i) (nm) $ and attack times $ G1 (t = 600 \ \ s) $ and $ G2 (t = 200 \ \ s) $, depending on the axis $ a $ $ (0.1 ... 2.0 \ \ cm) $.
\begin{figure}[H]
	\centering
	\includegraphics[scale=.6]{../Images/grinJD31}
	\caption{\emph{The relationship of samples $ G1 (I = 5 mA) $ and $ G2 (I = 40 mA) $ were obtained to find: a) Attack speed with current density for each point and b) Porosity as a function of density current. With this we have the calibration curves for the manufacture of any GRIN porous silicon structure   } }
		\label{fig:Indr1}
\end{figure}
Fig. \ref{fig:Indr1} a) explicitly explain the relationships that emerge when designing samples $ G1 (I = 5 mA) $ and $ G2 (I = 40 mA) $. For the first case $ G1 $ the depths ($ 1320 \ \ nm $ to $ 605 \ \ nm $) and the current densities ($ 6 \ \ mA / cm ^ 2 $ to $ 2.5 \ \ mA / cm ^ 2 $), finding the attack speed $ 2.2 \ \ nm / s $ up to $ 1.1 \ \ nm / s $ relation with depth and the time ($ 600 \ \ s $) of exposure of the sample, with the current density . We also find the depth ($ 1950 \ \ nm $ at $ 1430 \ \ nm $) and the current density ($ 50 \ \ mA / cm ^ 2 $ at $ 20 \ \ mA / cm ^ 2 $) as a function of the measurement points of the sample $ G2 (I = 40 mA) $. We were able to obtain the attack speed from $ 9.8 \ \ nm / s $ up to $ 7.1 \ \ m / s $ by relating to depth and time ($ 200 \ \ s $), with current density. Once the thickness of the monolayer and the attack time applied to them are known, calculate the attack speed according to the formula $ v = d / t $, for each of the current densities at the points $ A ( 0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $. Then we fit a function to the attack speed points with the different current densities allowed by the anodizing condition. For a desired thickness $ d (J_i) $, calculate the attack time $ t $ (so, $ t = v / d (J_i) $) and we can design any structure knowing the current density and the attack time. Fig. \ref{fig:Indr1} b) we find a relation of the porosity for each position with its determined current density. Therefore, if it is desired to manufacture a PSi monolayer of a certain porosity with a certain end, it is enough to resort to the graphs of Fig. \ref{fig:Indr1} to determine the corresponding current density, attack speed and consequently the time, obtaining for that monolayer. The importance of the calibration curves is that it allows us to have a relationship of the porosities that can be reached (and by having control over the possible refractive indices) as a function of the current density and to be controlled to control the thickness of the layers that are manufactured, by controlling the attack time for each of the chosen currents.

\subsection{GRIN Porous Silicon Microcavities}
 \begin{figure}[H]
	\centering
	\includegraphics[scale=0.4]{../Images/MicrGrin}
	\caption{\emph{Diagram of a microcavity of porous silicon GRIN. Alternate layers are obtained of high (H) refractive index $n_{_{Hi}}$ and low (L) refractive index $n_{_{Li}}$, where $N_{_{H}}$ is the number of layers for  $n_{_{Hi}}$ and $N_{_{L}}$ is the number of layers for $n_{_{Li}}$. Then,  $d_{_{Hi}}$ is the monolayer thickness of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$ is the monolayer thickness of $n_{_{Hi}}$ at that measurement point. Therefore,  $d_{_{i}}$ is the total thickness calculated for each of the measurements, defining a i = $ A, B, C$. Having the following relationship $d_{_{i}} = (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$. }}
	\label{fig:MCGRIN0}
\end{figure}
The Fig. \ref{fig:MCGRIN0} the scheme of  a initially proposed lateral gradient for monolayers should be shown in section 4.2, where we designed an electolytic cell suitable for our experiments and giving us the expected results of the simulation in section 4.1. Now our purpose is to manufacture more complex photonic structures such as the Porous silicon microcavities GRIN, taking into account that we start from having a tip electrode almost on the surface and by making a variation of currents we can achieve the effect of alternating the layers. Alternate layers are obtained of high (H) refractive index $n_{_{Hi}}$ and low (L) refractive index $n_{_{Li}}$, where $N_{_{H}}$ is the number of layers for  $n_{_{Hi}}$ and $N_{_{L}}$ is the number of layers for $n_{_{Li}}$. Then,  $d_{_{Hi}}$ is the monolayer thickness of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$ is the monolayer thickness of $n_{_{Hi}}$ at that measurement point. Therefore,  $d_{_{i}}$ is the total thickness calculated for each of the measurements, defining a i = $ A, B, C$. Having the following relationship $d_{_{i}} = (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$.
Initial data for conventional design we use  $\lambda_{_{c}}= 0.67 \ \ \mu m$, $n_{_{H}} =2.6$, $P_{_{H}} =0.46$, $d_{_{H}}=0.066 \ \ \mu m  $, $t_{_{H}}=35 s  $ y para  $n_{_{L}}= 1.4$,  $P_{_{L}} =0.75$, $d_{_{L}}=0.117 \ \ \mu m  $, $t_{_{L}}=11 s  $. All these data are for the point $ 0 $ which is located at one end of the sample just below the tip counter-electrode.
\begin{figure}[H]
 	\centering
 	\includegraphics[scale=.5]{../Images/MCGRIN2}
 	\caption{\emph{a) Three locations at different points are considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the PSiMCGRIN sample $ GMC $. b) We have the reflectance measurements to know the optical properties with the proposed simulation. We were able to show that in a Porous Silicon GRIN structure, for a microcavity the data is very consistent with the simulation and the experiment, we found the refractive indices and the porosities as a function of the current density at each measurement point, see Table \ref{tabla:1}. }}
 	\label{fig:MCGRIN3}
 \end{figure}

\begin{table}[H]
	\centering
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline
		\textbf{Points} & $\lambda_c (\mu m)$ & \textbf{n} & \textbf{k} & \textbf{Porosity} & \textbf{J}$(mA/cm^2)$ & \textbf{t(s)}\\
		\hline
		A(H) & 0.65 & 2.661 & 0.0264 & 0.45 & 5.5 & 35 \\
		\hline
		B(H) & 0.58 & 2.762 & 0.0135 & 0.41 & 4.0 & 35 \\
		\hline
		C(H) & 0.54 & 2.808 & 0.0178 & 0.39 & 3.0 & 35 \\
		\hline
		A(L) & 0.65 & 1.442 & 0.0015 & 0.74 & 44 & 11 \\
		\hline
		B(L) & 0.58 & 2.295 & 0.0091 & 0.68 & 32 & 11 \\
		\hline
		C(L) & 0.54 & 2.302 & 0.001 & 0.64 & 24 & 11 \\
		\hline
	\end{tabular}
	\caption{ \emph{We have different points denoted as follows, $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the sample of a Porous Silicon Microcavity GRIN  (PSiMCGRIN) $ GMC $. Alternate layers of high refractive index (H) and low refractive index (L) are obtained at each of the measurement points (A, B and C). The refractive indexes of the PSiMCGRIN were considered from the experimental and theoretical values that were obtained for the porosity ($ P = 0.3J^{0.24}$). And we could obtain the attack time with the relation of $ V = 0.53J ^ {0.79} $ where $ t = d / V $.}}
	\label{tabla:1}
\end{table}
In Fig. \ref{fig:MCGRIN3} a) Three locations at different points are considered, denoted as follows, $ A (0.3 \ \ cm) $ , $ B (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the PSiMCGRIN sample $ GMC $. Likewise, Fig. \ref{fig:DR3} b), we have the reflectance measurements to know the optical properties with the proposed simulation. We can see how from an experimental setup we have some important results as a result of a whole calibration curve suitable for making GRIN porous silicon. The refractive index of the Porous Silicon Microcavities GRIN were considered the experimental and theoretical values obtained for the porosity and the thicknesses shown in Table 1. The porous silicon microcavities (MCSP) with refractive index with gradient (GRIN), were manufactured with different current densities ranging from $ 6 \ \ mA / cm ^ 2 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a current of $ 5 \ \ mA $, for a $t_{_{H}}=35 s $, with a high refractive index $n_{_{H}} \sim$ $ 2,661$ to $ 2,808$ and porosities of $P_{_{H}} \sim$ $ 0.45 $ to $ 0.39 $. Also for $ 44 \ \ mA /cm^2 $ to $ 24 \ \ mA / cm^2 $, current of $ 38 \ \ mA $, using $t_{_{H}}=11 s$  for low refractive index $n_{_{L}}\sim$ $ 1,448 $ to $ 2,267 $ and with porosities of  $P_{_{H}} \sim$ $0.75 $ to $ 0.64 $. The porosity was calculated with the calibration curve exposed in the ($ P = 0.3J^{0.24} $). And the attack time could be obtained with the relation of $ V = 0.53J^{0.79} $ where $ t = d / V $ and the refractive index using the Bruggeman formula. For theoretical values, we use complex refractive indices as free parameters to fit the experimental refractive spectra (Section 4.2).
 \begin{figure}[H]
	\centering
	\includegraphics[scale=.5]{../Images/MCGRINSEM}
	\caption{\emph{SEM image of the cross section profile of the microcavities with GRIN. The measured thicknesses of the complete multi-film structures showed good agreement with the simulations taken from $ V = 0.53J ^ {0.79} $ where $d_j=Vt_j$ ($j=H,L$), which are the thicknesses of each of the monolayer of the porous silicon microcavity GRIN at the measurement points and the total thickness we find it as $d_{_{i}} = (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$ defining $ i = $ A, B, C. Which resulted in (measured / simulation) $ 2.25 / 2.31 \ \ \mu m $ (for structure at Point A), $ 2.17 / 2.08 \ \ \mu m $ (for structure at point B) and $ 1.87 / 1.65 \ \ \mu m $ (for structure at point C)}}
	\label{fig:MCGRIN4}
\end{figure}

For the Fig. \ref{fig:MCGRIN4} shows the SEM cross-sectional images of the PSi samples used in this work. Relatively small interface roughness and a clear contrast between the high and low porosity of the microcavity measured at different points (A, B and C), showing the change in thickness in each of these. The measured thicknesses of the complete multi-film structures showed good agreement with the simulations taken from $ V = 0.53J^{0.79} $ where $d_j=Vt_j$ ($j=H,L$), which are the thicknesses of each of the monolayer of the porous silicon microcavity GRIN at the measurement points and the total thickness we find it as $d_{_{i}} = (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$ defining $ i = $ A, B, C. Which resulted in (measured / simulation) $ 2.25 / 2.31 \ \ \mu m $ (for structure at Point A), $ 2.17 / 2.08 \ \ \mu m $ (for structure at point B) and $ 1.87 / 1.65 \ \ \mu m $ (for structure at point C).
Being able to say that for each measurement point corresponds different calculated current densities, which correspond to different thicknesses at the end of manufacturing, clearly seeing the lateral gradient product of our experiment.

\newpage
\section{conclusion}
The necessary expressions for the potential components were derived, finding a relationship of the tip of the counter electrode that acts similarly as a point charge and the current density for a geometry in a rectangular electrolytic box and we solve the electrostatic equations with suitable boundary conditions. Resulting in an electrostatic model for  Photonics crystals with a refractive index with gradient (EMPCGRIN).
It is the first time that the formalism mentioned here has been applied to find the current density to design porous silicon. The shape of the electrode, the area of the cell produces a visible decrease in the size and density of the pores. Additionally, optimizing the structural properties for a single structure we could have a gradient with different depths, reflactances at differents measurement points. In this way, we were able to simulate the direct relationship of the attack speed with the current density at the points  the samples of interest. At the same time, we developed a characterization between porosity, refractive indices of porous silicon, with the different current densities. And in the end we were able to design and characterize Porous Silicon microcavities with refractive indices with gradients, which for each measurement point correspond to different calculated current densities, which correspond to different thicknesses, clearly seeing the lateral gradient product of our experiment.
\section{Acknowledgments}
% \backmatter
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{bibliografía.bib} %Aquí ponen el nombre del archivo .bib
\bibliographystyle{unsrt}
 \small{
\begin{thebibliography}{X}
	%forma de biblio es MLA
\bibitem{I1} P. Yeh,\textquotedblleft \emph{Optical Waves in Layered Media} \textquotedblright, 2nd edn. (Wiley-Interscience Publication,
USA, 2005).
\bibitem{I2}Canham, L. 1997.\textquotedblleft \emph{Properties of Porous Silicon} \textquotedblright. Edited by Canham L. DERA, Malvern, UK.
\bibitem{I3}{Beale, M.I.J, J.D Benjamin, M.J Uren, N.G Chew, and A.G Cullis. 1985. \emph{ \textquotedblleft An Experimental and Theoretical Study of the Formation and Microstructure of Porous Silicon.\textquotedblright} J. Crystal Growth 73: 622?36. doi:10.1021/jp0706984. }
\bibitem{I4}Canham, L. T. 1990. \emph{\textquotedblleft Silicon Quantum Wire Array Fabrication by Electrochemical and Chemical Dissolution of Wafers.\textquotedblright} Applied Physics Letters 57 (10): 1046. doi:10.1063/1.103561.

\bibitem{I5} J. D. Joannopoulos et al.,\textquotedblleft \emph{Photonic Crystals: Molding the Flow of Light}\textquotedblright, 2nd edn.
(Princeton University Press, UK, 2008).
\bibitem{I6} E. Yablonovitch, \textquotedblleft \emph{Photonic band-gap structures,}\textquotedblright J. Opt. Soc. Am. B 10, 283-295 (1993)
\bibitem{I7} Ilyas, S., and M. Gal.  \textquotedblleft \emph{ Optical devices from porous silicon having continuously varying refractive index.}\textquotedblright Journal of Materials Science: Materials in Electronics 18.1 (2007): 61-64.
\bibitem{I8} Tran, P. \textquotedblleft \emph{Optical switching with a nonlinear photonic crystal: a numerical study.}\textquotedblright Optics letters 21.15 (1996): 1138-1140.
 \bibitem{I9} Ariza-Flores, A. David, L. M. Gaggero-Sager, and V. Agarwal. \textquotedblleft \emph{White metal-like omnidirectional mirror from porous silicon dielectric multilayers.}\textquotedblright Applied Physics Letters 101.3 (2012): 031119.
\bibitem{I10} Johnson, Steven G., et al.  \textquotedblleft \emph{Linear waveguides in photonic-crystal slabs.}\textquotedblright Physical Review B 62.12 (2000): 8212.

%asimetrica
\bibitem{I101}Collins, Boyce E., et al. \textquotedblleft \emph{ Determining protein size using an electrochemically machined pore gradient in silicon.}\textquotedblright Advanced Functional Materials 12.3 (2002): 187-191.

\bibitem{I102} Khung, Y. L., G. Barritt, and N. H. Voelcker. \textquotedblleft \emph{Using continuous porous silicon gradients to study the influence of surface topography on the behaviour of neuroblastoma cells.}\textquotedblright Experimental cell research 314.4 (2008): 789-800.

\bibitem{I103} Clements, Lauren R., et al. \textquotedblleft \emph{Mesenchymal stem cell attachment to peptide density gradients on porous silicon generated by electrografting.}\textquotedblright physica status solidi (a) 208.6 (2011): 1440-1445.

\bibitem{I104} Wang, Peng-Yuan, et al. \textquotedblleft \emph{Screening the attachment and spreading of bone marrow-derived and adipose-derived mesenchymal stem cells on porous silicon gradients.}\textquotedblright Rsc Advances 2.33 (2012): 12857-12865.

 \bibitem{I11} Canham, L. \textquotedblleft \emph{Properties of Porous Silicon.}\textquotedblright Edited by Canham L. DERA, Malvern, UK. (1997).
 \bibitem{I12} Li, Yang Yang, Peter Kim, and Michael J Sailor.\textquotedblleft \emph{Painting a Rainbow on Silicon A Simple Method to Generate a Porous Silicon Band Filter Gradient}\textquotedblright Physica Status Solidi (a) 1618 (8): 161618. doi:10.1002/pssa.200461200.(2005)
 \bibitem{I13} Khung, Y L, and N H Voelcker. 2009.\textquotedblleft\emph{ Multidirectional Lateral Gradient Films with Position-Dependent Photonic Signatures Made from Porous Silicon.}\textquotedblright Optical Materials 32 (1): 23442. doi:10.1016/j.optmat.2009.07.015.
 \bibitem{I14}  Khung, Y L, G Barritt, and N H Voelcker.  \textquotedblleft \emph{Using Continuous Porous Silicon Gradients to Study the Influence of Surface Topography on the Behaviour of Neuroblastoma Cells.}\textquotedblright Experimental Cell Research 314 (4): 78900. doi:10.1016/j.yexcr.2007.10.015.(2008.)
\bibitem{I15} Collins, B.E., K.-P.S. Dancil, G. Abbi, and M.J. Sailor. 2002.\textquotedblleft \emph{Determining Protein Size Using an Electrochemically Machined Pore Gradient in Silicon.}\textquotedblright Advanced Functional Materials 12 (3): 187. doi:10.1002/1616-3028(200203)12:3,187::AID-ADFM187,3.0.CO;2-E.( 2002.)

\bibitem{I16} Ocier, C. R., Krueger, N. A., Zhou, W. and  Braun, P. V. (2017).\textquotedblleft \emph{Tunable visibly transparent optics derived from porous silicon.}\textquotedblright ACS Photonics, 4(4), 909-914.
%ecuacion
\bibitem{I17} Dariani RS, Ebrahimnasab S (2014). \textquotedblleft \emph{Root Mean Square Roughness of Nano Porous Silicon by Scattering Spectra.}\textquotedblright The
European Physical Journal Plus 129: 129.
\bibitem{I18} Lerondel G, Romestain R (1997).\textquotedblleft \emph{Roughness of the Porous Silicon Dissolution Interface.}\textquotedblright Journal of Applied Physics 81:  61716178.
\bibitem{I19} Lérondel G, Romestain R, Barret S (1997).\textquotedblleft \emph{Quantitative Analysis of the Light Scattering Effect on Porous Silicon
Optical Measurements.}\textquotedblright Thin Solid Films 297: 114?117.

\bibitem{I20} Thei, W. \textquotedblleft \emph{Optical Properties of porous silicon.}\textquotedblright Surf. Sci. Rep. 1997, 29, 91?93.
\bibitem{I21} Van Groesen, E.; Sopaheluwakan, A.; Andonowati, A. \textquotedblleft  \emph{Direct characterization of states and modes in defect grating structures.}\textquotedblright J. Nonlinear Opt. Phys. Mater. 2004, 13, 155173.
% \textquotedblleft \textquotedblright

\bibitem{In} Mazzoleni, C., and L. Pavesi. \textquotedblleft  \emph{Application to optical components of dielectric porous silicon multilayers.}\textquotedblright Applied Physics Letters 67.20 (1995): 2983-2985

\end{thebibliography}
%capitulos1111111111111111111111

\end{document}

### 2020-06-04 paper.tex
Modify abstract

@@
 \begin{abstract}
-The current density in a of Porous Silicon (PSi) with gradient  refractive index (GRIN) produced  by an electrochemical  attack on silicon (Si)  to  produce  porous  silicon (PSi), the calculated  porosity  of the GRIN structure depends  on the  position  and  distance  from  counter  electrode.
-The proposed relationship shows, the  counter  electrode tip that acts  analogously  as a point charge  and  current density  for a geometry in an electrolytic  box by solving the electrostatic equations  with suitable  contour conditions.
-Resulting  in an electrostatic model for photonic  crystals  with gradient refractive index (EMPCGRIN).
-The characterization of the  silicon structures was performed  by scanning electron microscopy   and  UV-Vis-NIR reflectance spectroscopy.
-The obtained  results  open  the  possibility  of creating  silicon-based photonic  structures within  the  Visible-IR- range, within  the  sample at  different measuring distances,  where generally porous silicon does not strongly  absorb or disperse light.
-Similarly, in the UV-Visible range  there is a strong absorption with more of light scattering.
-Having a greater  area of attack generating  different pores sizes and their porosity, and making an easy calculation  in the manufacture of porous silicon.
-\\
+We propose a simple setup which allows the calculation of the current
+density as a function of position within an electrochemical cell used
+to produce porous Silicon structures with a controlled gradient in their
+index of refraction. We produced samples under several conditions and
+characterized them with scanning electron microscopy, and
+ultraviolet-visible-near infrared reflectance spectroscopy. Our
+results allow us to obtain from experiments on a single or just a few
+samples a full characterization of the dependence of porosity,
+dielectric function and speed of attack on the current density and on
+position, so that novel nonhomogeneous devices may be designed and
+built.
 
-Keywords: Porous Silicon (PSi); Monolayer(Ml); Porosity(P); Reflectance Spectra.
+Keywords: Porous Silicon; GRIN; Reflectance Spectra.
 \end{abstract}

### 2020-06-04 paper.tex
Cut long lines. Correct figures. Correct missing brackets. Compiles.

@@
 
- The structural behavior of nanostructured materials  has  become a  great  topic  of global  interest,  where numerous  research has been done so far \cite{I1}.
-We found a great way to go for future technological  explorations,  countless  challenges and  that  open a range of possibilities to develop further  study  on these issues\cite{I2}.
-Porous silicon (PSi) is a versatile nanostructured material and an excellent candidate as a technological platform for different sensing applications \cite{I3, I4}, due to its easy manufacturing,  large surface area, high surface reactivity,  and moreover, its optical transduction capacity.
-Photonic crystals are multilayer dielectric structures that have periodicity in the dielectric function along one direction \cite{I5}.
-It has numerous studies for high reflectivity and the ability to adjust  the photonic  prohibited  band (PBG)\cite{I6} , which leads to possible applications  such as filters\cite{I7}, optical switches\cite{I8}, omnidirectional mirrors\cite{I9}, waveguides for PC \cite{I10} etc.
-In the conventional manufacturing of PSi the desired result  is to obtain  homogeneous samples (same structural characteristics) from the  periphery  to the center  of the electrochemically  attacked area.
-However, with an asymmetric anodizing configuration,  samples with a lateral gradient in terms of pore size and thickness of the porous layer are obtained \cite{I101}.
-In this configuration,  the face of the platinum  electrode (cathode)  is relatively maintained  perpendicular  to the surface of the Si substrate (anode) at one end of the cell, so that the distribution of the current within the electrolyte  solution varies depending on the distance  of the electrode due to the resistance of the electrolyte,  resulting  in a decrease in current density as the distance from the electrode increases \cite{I102, I103}.
-The result is a porous surface with different pore sizes ranging from a few nanometers  to pores on the order of a few micrometers  \cite{I104}.
-The dimensions of the pores obtained on the same chip can be controlled by adjusting the anodizing current and electrolyte concentration \cite{I11}.
-Currently, these types of samples have found their application relevant as optical band filters \cite{I12}, devices with a multidirectional photonic band (photonic bar codes) \cite{I13} and mainly as biosensors.
-In this way, the effect of different topographies (porosities in the same sample) on the culture / adhesion of certain cells \cite{I14} is studied, considerably reducing the number of samples and cost of the study.
-In addition, they are also very useful when a biomolecule size-exclusion technique is required allowing the identification and separation of these biological compounds \cite{I15}.
-Recent studies  have shown that  the  combination  of thermal  oxidation  and infiltration of TiO2   by ALD offers the  opportunity to manufacture  a high index of refraction  of contrast, visibly transparent GRIN optical elements from PSi absorbent structures \cite{I16}.
-A Despite previous research on the formation of porous silicon with GRIN, type p in manufacturing and characterization, there was no control of current densities, much less a model that  explained said lateral  gradient.
-In this work, we reported a gradient refractive index (GRIN) structure by varying the current density on the fabrication of porous silicon photonic structure.
-This current density values, depth, and porosity of the photonic structure were calculated from an electrostatic model for photonic crystals with a gradient refractive index (EMPCGRIN).
-Moreover, the theoretical and experimental studies were exhibited similar results.\\
- The paper is organized as follows.
-In Section 2  we report the effect of how the current density can be calculated from an electrostatic model for photonic crystals with gradient refractive index (EMPCGRIN), demonstrating that there is a direct relation of the gradient generated by the electrode when it attacks the Silicon sample, we can see the depth of the structure and its porosity, in each of the measuring points.
-In Subsection 2.2 we present a formalism based on the methods used for the analysis of photonic crystal structures is the transfer matrix method.
-We use it to investigate the reflectance of light in a one-dimensional photonic crystal.
-In Section 3 we provide experimental  details about the manufacture of PS dielectric multilayers and Section 4 we shows the comparison of numerical and experimental results followed.
-Finally,  the conclusions given in Section.
-5
+The structural behavior of nanostructured materials  has  become a
+great  topic  of global  interest,  where numerous  research has been
+done so far \cite{I1}. We found a great way to go for future
+technological  explorations,  countless  challenges and  that  open a
+range of possibilities to develop further  study  on these
+issues\cite{I2}. Porous silicon (PSi) is a versatile nanostructured
+material and an excellent candidate as a technological platform for
+different sensing applications \cite{I3, I4}, due to its easy
+manufacturing,  large surface area, high surface reactivity,  and
+moreover, its optical transduction capacity.  Photonic crystals are
+multilayer dielectric structures that have periodicity in the
+dielectric function along one direction \cite{I5}. It has numerous
+studies for high reflectivity and the ability to adjust  the photonic
+prohibited  band (PBG)\cite{I6} , which leads to possible applications
+such as filters\cite{I7}, optical switches\cite{I8}, omnidirectional
+mirrors\cite{I9}, waveguides for PC \cite{I10} etc. In the
+conventional manufacturing of PSi the desired result  is to obtain
+homogeneous samples (same structural characteristics) from the
+periphery  to the center  of the electrochemically  attacked area.
+However, with an asymmetric anodizing configuration,  samples with a
+lateral gradient in terms of pore size and thickness of the porous
+layer are obtained \cite{I101}. In this configuration,  the face of
+the platinum  electrode (cathode)  is relatively maintained
+perpendicular  to the surface of the Si substrate (anode) at one end
+of the cell, so that the distribution of the current within the
+electrolyte  solution varies depending on the distance  of the
+electrode due to the resistance of the electrolyte,  resulting  in a
+decrease in current density as the distance from the electrode
+increases \cite{I102, I103}. The result is a porous surface with
+different pore sizes ranging from a few nanometers  to pores on the
+order of a few micrometers  \cite{I104}. The dimensions of the pores
+obtained on the same chip can be controlled by adjusting the anodizing
+current and electrolyte concentration \cite{I11}. Currently, these
+types of samples have found their application relevant as optical band
+filters \cite{I12}, devices with a multidirectional photonic band
+(photonic bar codes) \cite{I13} and mainly as biosensors. In this way,
+the effect of different topographies (porosities in the same sample)
+on the culture / adhesion of certain cells \cite{I14} is studied,
+considerably reducing the number of samples and cost of the study. In
+addition, they are also very useful when a biomolecule size-exclusion
+technique is required allowing the identification and separation of
+these biological compounds \cite{I15}. Recent studies  have shown that
+the  combination  of thermal  oxidation  and infiltration of TiO2   by
+ALD offers the  opportunity to manufacture  a high index of refraction
+of contrast, visibly transparent GRIN optical elements from PSi
+absorbent structures \cite{I16}. A Despite previous research on the
+formation of porous silicon with GRIN, type p in manufacturing and
+characterization, there was no control of current densities, much less
+a model that  explained said lateral  gradient. In this work, we
+reported a gradient refractive index (GRIN) structure by varying the
+current density on the fabrication of porous silicon photonic
+structure. This current density values, depth, and porosity of the
+photonic structure were calculated from an electrostatic model for
+photonic crystals with a gradient refractive index
+(EMPCGRIN). Moreover, the theoretical and experimental studies were
+exhibited similar results.
+
+The paper is organized as follows. In Section 2  we report the effect
+of how the current density can be calculated from an electrostatic
+model for photonic crystals with gradient refractive index (EMPCGRIN),
+demonstrating that there is a direct relation of the gradient
+generated by the electrode when it attacks the Silicon sample, we can
+see the depth of the structure and its porosity, in each of the
+measuring points. In Subsection 2.2 we present a formalism based on
+the methods used for the analysis of photonic crystal structures is
+the transfer matrix method. We use it to investigate the reflectance
+of light in a one-dimensional photonic crystal. In Section 3 we
+provide experimental  details about the manufacture of PS dielectric
+multilayers and Section 4 we shows the comparison of numerical and
+experimental results followed. Finally,  the conclusions given in
+Section. 5
 
 \section{Theory}
- \subsection{Electrostatic Model for Photonic Crystals with Gradient Refraction Index (EMPCGRIN)}
-The calculate  current density in a GRIN structure produced by an electrochemical attack on Si to produce Porous Si with a position-dependent porosity due to the distance to the counter electrode.
-A simplifies  calculation  with geometry,
-assumimg  in the form of a whole prism on the sides a, b, c with a, b horizontal and c vertical.
-Here c considered as the height of the liquid, and the walls are insulating, but the bottom is completely covered with the sample, which act as good conductor.
-The electrode is a thin insulated cable with tip, which  a point  current source.
+\subsection{Electrostatic Model for Photonic Crystals with Gradient
+  Refraction Index (EMPCGRIN)}
+
+The calculate  current density in a GRIN structure produced by an
+electrochemical attack on Si to produce Porous Si with a
+position-dependent porosity due to the distance to the counter
+electrode. A simplifies  calculation  with geometry,
+assumimg  in the form of a whole prism on the sides a, b, c with a, b
+horizontal and c vertical. Here c considered as the height of the
+liquid, and the walls are insulating, but the bottom is completely
+covered with the sample, which act as good conductor. The electrode is
+a thin insulated cable with tip, which  a point  current source.
 \begin{figure}[H]
   \centering
-	\includegraphics[scale=.4]{../Images/celdan}
+  \includegraphics[scale=.4]{Images/celdan}
   \caption{\emph{Diagram of the Electrolytic cell where we can see the shape of a prism on the sides a, b, c with a, b horizontal and c vertical.
@@
 \end{figure}
-The current in the electrolyte is $ \vec {J} = \sigma \vec{E} $ with $ \sigma $ is the conductivity.
-This for the stationary case $ \bigtriangledown \cdot \vec{j} = 0 $.
-The electric field is derived from the electric potential, $\vec {E} = - \bigtriangledown \varphi $.
-And we can say that $ \bigtriangledown^{2} \varphi = 0 $, since the sample is a relatively good conductor, when connected to earth $ \varphi(x, y, 0) = 0 $.
-Integrating $ \vec{J} $ over a small sphere superimposing the electrode gives $ \int ds \cdot \vec{J} = I $.
+The current in the electrolyte is $ \vec {J} = \sigma \vec{E} $ with $
+\sigma $ is the conductivity. This for the stationary case $
+\bigtriangledown \cdot \vec{j} = 0 $. The electric field is derived
+from the electric potential, $\vec {E} = - \bigtriangledown \varphi
+$.
+And we can say that $ \bigtriangledown^{2} \varphi = 0 $, since the
+sample is a relatively good conductor, when connected to earth $
+\varphi(x, y, 0) = 0 $. Integrating $ \vec{J} $ over a small sphere
+superimposing the electrode gives $ \int ds \cdot \vec{J} = I $.
 The current density that carries the current to the tip. So
@@
 \end{equation}
-In the positions$\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ is the tip of the electrode that is in the presence of a ground conductor plane grounded $ z = 0 $ and enclosed on the insulating walls at $ (0, y, z) $, $ (a, y, z) $, $ (x, 0, z) $ , $ (x, b, z) $.
-The surface of the liquid is also not conductive to $ (x, y, c) $, the normal current is $\vec{j} \cdot \hat{n}=0$ and the normal of the field is $ \vec{E} \cdot \hat{n}=0  $.
-i.e
+In the positions$\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ is the
+tip of the electrode that is in the presence of a ground conductor
+plane grounded $ z = 0 $ and enclosed on the insulating walls at $ (0,
+y, z) $, $ (a, y, z) $, $ (x, 0, z) $ , $ (x, b, z) $. The surface of
+the liquid is also not conductive to $ (x, y, c) $, the normal current
+is $\vec{j} \cdot \hat{n}=0$ and the normal of the field is $ \vec{E}
+\cdot \hat{n}=0  $. i.e
 \begin{equation}
@@
 \end{equation}
-This has a mixture of Dirichlet-Neumann type boundary conditions.
-By using the simplified prism geometry  can solve the problem using the theory of image loads.
-Each load has an image of the same sign and magnitude for each lateral insulating surface and the opposite sign change in the lower part of the conductive plane, as follows.
+This has a mixture of Dirichlet-Neumann type boundary conditions. By
+using the simplified prism geometry  can solve the problem using the
+theory of image loads. Each load has an image of the same sign and
+magnitude for each lateral insulating surface and the opposite sign
+change in the lower part of the conductive plane, as follows.
  \begin{figure}[H]
  \centering
- \includegraphics[scale=.6]{../Images/Cellgrin}
- \caption{\emph{a) Diagram of a rectangular electrolytic cell, with a real charge in the corner of the cell with its charges ($ q $) images of the same sign in $ Z_0 $ and another charge image ($ -q $) with change of sign located below the conductor in position $ -Z_0 $.
-b) The upper face seen from above, a real load and its image loads in $ Z_0 $.
-c) All this formed a systems of a real load and its image loads produced by the cell walls and its other images seen from above, forming a periodic space.
-}}
+ \includegraphics[scale=.6]{Images/Cellgrin}
+ \caption{\emph{a) Diagram of a rectangular electrolytic cell, with a
+     real charge in the corner of the cell with its charges ($ q $)
+     images of the same sign in $ Z_0 $ and another charge image ($ -q
+     $) with change of sign located below the conductor in position $
+     -Z_0 $. b) The upper face seen from above, a real load and its
+     image loads in $ Z_0 $. c) All this formed a systems of a real
+     load and its image loads produced by the cell walls and its other
+     images seen from above, forming a periodic space. }}
  \label{fig:T1}
@@
 
-From Fig.
-\ref{fig:T1} we assume that if i put a real charge ($ q $) in at $\vec{r}_0= (x_0, y_0, z_0)$, in the corner of the electrolytic box it induces images at $\vec{r}_1= (-x_0, y_0, z_0)$ due to a reflection in $ (0, y, z) $, images in  $\vec{r}_2= (-x_0, -y_0, z_0)$ due to a reflection in $ (x, 0, z) $ y the image of the image in $\vec{r}_3= (x_0, -y_0, z_0)$  for  $\vec{r}_j$, $(j=0,1,2,3)$.
-Then, these four charges are reflected on the other two surfaces and the eight new images are reflected on the original surface, etc., producing a periodic 2D rectangular network with unit cells of signs $ L_x = 2a $, $ L_y = 2b $ and with a base of 4 equal charges.
-This entire network is reflected from the bottom with an opposite sign load (below the driver).
-Periodic copies separated by the vacuum in the $ xy $ plane whose area is being increased to achieve convergence.
-\\
-\textbf {Problem considerations}: The problem is the potential, the field and the current produced by a periodic 2D network of a real load and all its images.
-The potential due to a periodic network is automatically found in the plane making a sum of 2D Fourier.
+From Fig. \ref{fig:T1} we assume that if i put a real charge ($ q $)
+in at $\vec{r}_0= (x_0, y_0, z_0)$, in the corner of the electrolytic
+box it induces images at $\vec{r}_1= (-x_0, y_0, z_0)$ due to a
+reflection in $ (0, y, z) $, images in  $\vec{r}_2= (-x_0, -y_0, z_0)$
+due to a reflection in $ (x, 0, z) $ y the image of the image in
+$\vec{r}_3= (x_0, -y_0, z_0)$  for  $\vec{r}_j$, $(j=0,1,2,3)$. Then,
+these four charges are reflected on the other two surfaces and the
+eight new images are reflected on the original surface, etc.,
+producing a periodic 2D rectangular network with unit cells of signs $
+L_x = 2a $, $ L_y = 2b $ and with a base of 4 equal charges. This
+entire network is reflected from the bottom with an opposite sign load
+(below the driver). Periodic copies separated by the vacuum in the $
+xy $ plane whose area is being increased to achieve convergence.
 
+\textbf {Problem considerations}: The problem is the potential, the
+field and the current produced by a periodic 2D network of a real load
+and all its images. The potential due to a periodic network is
+automatically found in the plane making a sum of 2D Fourier.
 \begin{eqnarray}
- \rho(\vec{r}) =q \displaystyle\sum_{R}  \ \delta (\vec{r}-\vec{R}-\vec{r}_0) =\dfrac{q}{A}  \displaystyle\sum_{G}  e^{i G \cdot (\vec{r}-\vec{r}_{0})} \delta (z-z_0)
+ \rho(\vec{r}) =q \displaystyle\sum_{R}  \ \delta
+  (\vec{r}-\vec{R}-\vec{r}_0) =\dfrac{q}{A}  \displaystyle\sum_{G}
+  e^{i G \cdot (\vec{r}-\vec{r}_{0})} \delta (z-z_0)
 \end{eqnarray}
-Where $ {R} $ is the 2D Bravais network and $ {G} $ its reciprocal network.
-It is written $ \phi (\vec{r}) = \displaystyle \sum _ {\vec{G}}  \phi_{_{G}}(z) e^{i \vec {G} \cdot \vec {r}} $.
-So the Poisson equation $ \bigtriangledown^2 \phi = -4 \pi \displaystyle \sum_{\vec{R}} \delta (\vec{r} - \vec{R} - \vec{r}_0) $.
+Where $ {R} $ is the 2D Bravais network and $ {G} $ its reciprocal
+network. It is written $ \phi (\vec{r}) = \displaystyle \sum _
+{\vec{G}}  \phi_{_{G}}(z) e^{i \vec {G} \cdot \vec {r}} $. So the
+Poisson equation $ \bigtriangledown^2 \phi = -4 \pi \displaystyle
+\sum_{\vec{R}} \delta (\vec{r} - \vec{R} - \vec{r}_0) $.
 Becomes
  \begin{eqnarray}
- \dfrac{\partial^2 \phi_{_{G}}(z)}{\partial z^2}+ G^2\phi_{_{G}}(z)= -\dfrac{4 \pi}{A}  q   e^{i \vec{G} \cdot \vec{r}_{_0}} \delta (z-z_0)
+ \dfrac{\partial^2 \phi_{_{G}}(z)}{\partial z^2}+ G^2\phi_{_{G}}(z)=
+   -\dfrac{4 \pi}{A}  q   e^{i \vec{G} \cdot \vec{r}_{_0}} \delta
+   (z-z_0)
  \end{eqnarray}
-Solving the homogeneous equation above and below $ z = z_0 $, using symmetry and conditions at $ \pm \infty $ we obtain $ \phi_{_{G}} = \phi_{_{G}}^{0} e^{ G \abs{z-z_0}} \ \ \ \ \ (G \neq 0) $.
-And adjusting the singularity
+Solving the homogeneous equation above and below $ z = z_0 $, using
+symmetry and conditions at $ \pm \infty $ we obtain $ \phi_{_{G}} =
+\phi_{_{G}}^{0} e^{ G \abs{z-z_0}} \ \ \ \ \ (G \neq 0) $. And
+adjusting the singularity
  \begin{eqnarray}
- \phi_{_{G}}(z)= \dfrac{2 \pi q}{AG}  e^{- G \abs{z-z_0}} e^{-i \vec{G} \cdot \vec{r}_{_0}} \ \ \ \ \ (G\neq 0)
+ \phi_{_{G}}(z)= \dfrac{2 \pi q}{AG}  e^{- G \abs{z-z_0}} e^{-i
+   \vec{G} \cdot \vec{r}_{_0}} \ \ \ \ \ (G\neq 0)
  \end{eqnarray}
-For the case $ G = 0 $ is similar $ \phi_{_{G = 0}} (z) = \dfrac{-2 \pi q}{A} \abs{z-z_0} + K, $ $ \ \ $ (K is a constant). Here $ A = L_x L_y $ is the unit cell area
+For the case $ G = 0 $ is similar $ \phi_{_{G = 0}} (z) = \dfrac{-2
+  \pi q}{A} \abs{z-z_0} + K, $ $ \ \ $ (K is a constant). Here $ A =
+L_x L_y $ is the unit cell area
  \begin{eqnarray}
- \phi(\vec{r}) = K-\dfrac{2 \pi q}{A}  \abs{z-z_0} +\dfrac{2 \pi q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} e^{- G \abs{z-z_0}}   e^{i \vec{G} \cdot \vec{r}-\vec{r}_0}
+ \phi(\vec{r}) = K-\dfrac{2 \pi q}{A}  \abs{z-z_0} +\dfrac{2 \pi
+   q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} e^{- G \abs{z-z_0}}
+   e^{i \vec{G} \cdot \vec{r}-\vec{r}_0}
  \end{eqnarray}
@@
   \begin{eqnarray}\label{Eq:EC11}
- \phi(\vec{r}) = -\dfrac{8\pi q}{A} \bigg((\abs{z-z_0}-\abs{z+z_0} ) +\dfrac{8\pi q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \bigg( e^{- G \abs{z-z_0}} -e^{- G \abs{z+z_0}}  \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}
+ \phi(\vec{r}) = -\dfrac{8\pi q}{A} \bigg((\abs{z-z_0}-\abs{z+z_0} )
+    +\dfrac{8\pi q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \bigg(
+    e^{- G \abs{z-z_0}} -e^{- G \abs{z+z_0}}  \bigg) \cos(G_x x_0)
+    \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}
  \end{eqnarray}
@@
    \begin{eqnarray}
- \phi(\vec{r}) = -\dfrac{16\pi q}{A} \bigg( z +\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \sinh(G z)  \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}} \bigg)
+ \phi(\vec{r}) = -\dfrac{16\pi q}{A} \bigg( z
+     +\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \sinh(G z)  \cos(G_x
+     x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}} \bigg)
  \end{eqnarray}
@@
   \centering
-	\includegraphics[scale=.6]{../Images/celd1}
-	\caption{\emph{Diagram shows that there is a positive (real) plane $ z_0 $, a negative image at $ -z_0 $ below the conductor ($ z = 0 $) and its images are a positive plate at $ 2c-z_0 $ and a negative plate at $ 2c + z_0 $, the image is repeated vertically with the period $ L_z = 4c $}}
+  \includegraphics[scale=.6]{Images/celd1}
+  \caption{\emph{Diagram shows that there is a positive (real) plane $
+      z_0 $, a negative image at $ -z_0 $ below the conductor ($ z = 0
+      $) and its images are a positive plate at $ 2c-z_0 $ and a
+      negative plate at $ 2c + z_0 $, the image is repeated vertically
+      with the period $ L_z = 4c $}}
   \label{fig:Celda1}
 \end{figure}
-In Fig.
-\ref{fig:Celda1} it is observed that there is a positive (real) plane $ z_0 $, a negative image at $ -z_0 $ below the conductor ($ z = 0 $) and its images are a positive plate at $ 2c-z_0 $ and a negative plate at $ 2c + z_0 $.
-Also, the image is repeated vertically with the period $ L_z = 4c $.
-Therefore, the equation \ref{Eq:EC11} would be rewritten, like this
+In Fig. \ref{fig:Celda1} it is observed that there is a positive
+(real) plane $ z_0 $, a negative image at $ -z_0 $ below the conductor
+($ z = 0 $) and its images are a positive plate at $ 2c-z_0 $ and a
+negative plate at $ 2c + z_0 $. Also, the image is repeated vertically
+with the period $ L_z = 4c $. Therefore, the equation \ref{Eq:EC11}
+would be rewritten, like this
  \begin{eqnarray}\label{Eq:EC1}
- \nonumber\phi(\vec{r}) = K+\dfrac{8\pi q}{A} \displaystyle\sum_{n} -\bigg(\abs{z-z_0-nL_z}-\abs{z+z_0-nL_z}-\abs{z+2c+z_0-nL_z}+\abs{z-2c-z_0-nL_z}\bigg) +\\ \nonumber \dfrac{1}{G}\displaystyle\sum_{\vec{G}}\bigg( \displaystyle\sum_{n} \bigg( e^{-\abs{z-z_0-nL_z}} +e^{-\abs{z+z_0-nL_z}}-e^{-\abs{z+2c+z_0-nL_z}}-e^{-\abs{z-2c-z_0-nL_z}}  \bigg)\bigg)\cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}\\
+ \nonumber\phi(\vec{r}) = K+\dfrac{8\pi q}{A} \displaystyle\sum_{n}
+   -\bigg(\abs{z-z_0-nL_z}-\abs{z+z_0-nL_z}-\abs{z+2c+z_0-nL_z}+\abs{z-2c-z_0-nL_z}\bigg)
+   +\\ \nonumber \dfrac{1}{G}\displaystyle\sum_{\vec{G}}\bigg(
+   \displaystyle\sum_{n} \bigg( e^{-\abs{z-z_0-nL_z}}
+   +e^{-\abs{z+z_0-nL_z}}-e^{-\abs{z+2c+z_0-nL_z}}-e^{-\abs{z-2c-z_0-nL_z}}
+   \bigg)\bigg)\cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot
+   \vec{r}}\\
 \end{eqnarray}
-The constant K is chosen thus $ \phi (z = 0) $, substituting in Eq. (\ref {Eq:EC1}) and after factoring $ e^{- nGL_Z} $ we are explicitly left with the geometric sum over $n$
+The constant K is chosen thus $ \phi (z = 0) $, substituting in
+Eq. (\ref {Eq:EC1}) and after factoring $ e^{- nGL_Z} $ we are
+explicitly left with the geometric sum over $n$
 {\small
   \begin{eqnarray}
- \nonumber\phi(\vec{r}) = K+\dfrac{16\pi q}{A} \bigg(z+z_0  + \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \bigg(e^{-Gz_0} \sinh(Gz)+e^{-Gz_0(2c_z)} \sinh(Gz_0) -e^{-2Gc} \sinh(Gz) \sinh(Gz_0) \\ \nonumber \dfrac{1+\cosh(2Gc)}{\sinh(2Gc)} - e^{-2Gc}\cosh(2Gc) \sinh(Gz_0)   \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}   \bigg)\\
+    \nonumber\phi(\vec{r}) = K+\dfrac{16\pi q}{A} \bigg(z+z_0  +
+    \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \bigg(e^{-Gz_0}
+    \sinh(Gz)+e^{-Gz_0(2c_z)} \sinh(Gz_0) -e^{-2Gc} \sinh(Gz)
+    \sinh(Gz_0) \\ \nonumber \dfrac{1+\cosh(2Gc)}{\sinh(2Gc)} -
+    e^{-2Gc}\cosh(2Gc) \sinh(Gz_0)   \bigg) \cos(G_x x_0) \cos(G_y
+    y_0) e^{i \vec{G} \cdot \vec{r}}   \bigg)\\
  \end{eqnarray}
@@
  \begin{eqnarray}\label{Eq:EC2}
-\nonumber\phi(x, y, 0) = K+\dfrac{16\pi q}{A} \bigg(z_0  + \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \bigg(e^{-2Gc} \sinh(Gz_0)-e^{-2Gc} \sinh(Gz_0)   \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}\bigg) =\\ \nonumber = K+\dfrac{16\pi q}{A} \\
+\nonumber\phi(x, y, 0) = K+\dfrac{16\pi q}{A} \bigg(z_0  +
+   \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \bigg(e^{-2Gc}
+   \sinh(Gz_0)-e^{-2Gc} \sinh(Gz_0)   \bigg) \cos(G_x x_0) \cos(G_y
+   y_0) e^{i \vec{G} \cdot \vec{r}}\bigg) =\\ \nonumber =
+   K+\dfrac{16\pi q}{A} \\
 \end{eqnarray}
@@
  \begin{eqnarray}
-\nonumber\phi(\vec{r}) = \dfrac{16\pi q}{A}\bigg( z  + \displaystyle\sum_{\vec{G}}\dfrac{\sinh(Gz_0)}{G} \bigg(e^{-Gz_0} -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\
+\nonumber\phi(\vec{r}) = \dfrac{16\pi q}{A}\bigg( z  +
+   \displaystyle\sum_{\vec{G}}\dfrac{\sinh(Gz_0)}{G} \bigg(e^{-Gz_0}
+   -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg)
+   \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\
 \end{eqnarray}
-I am sure it is correct.
-Then it goes to zero at $ z = 0 $.
-The term with c disappears if $ c \longrightarrow \infty $.
-The sum converges when $ G \longrightarrow \infty $ if $ z <z_0 <c $ and diverges to $ z \longrightarrow z_0 $.
-So it seems ready for calculation.
+I am sure it is correct. Then it goes to zero at $ z = 0 $. The term
+with c disappears if $ c \longrightarrow \infty $. The sum converges
+when $ G \longrightarrow \infty $ if $ z <z_0 <c $ and diverges to $ z
+\longrightarrow z_0 $. So it seems ready for calculation.
 The normal component of the field is
 \begin{eqnarray}
-\nonumber E_\perp = -\dfrac{16\pi q}{A}\bigg( 1  + \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \cosh(Gz)\bigg(e^{-Gz_0} -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\
+\nonumber E_\perp = -\dfrac{16\pi q}{A}\bigg( 1  +
+  \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \cosh(Gz)\bigg(e^{-Gz_0}
+  -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x
+  x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\
 \end{eqnarray}
-And the current density is for any $ z $, for our calculation we choose that $ z = 0 $
+And the current density is for any $ z $, for our calculation we
+choose that $ z = 0 $
 \begin{eqnarray}\label{Eq:J}
-\nonumber J_\perp = -\dfrac{I}{ab}\bigg( 1  + \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \cosh(Gz_0) \bigg(e^{-Gz_0} -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\
+\nonumber J_\perp = -\dfrac{I}{ab}\bigg( 1  +
+  \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \cosh(Gz_0) \bigg(e^{-Gz_0}
+  -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x
+  x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\
 \end{eqnarray}
-Integrating on the surface of the sample is obtained $I_{nm} =\int^{a}_0 dx \int^{b}_0 dy \ \ e^{i\vec{G}\vec{r}}$
+Integrating on the surface of the sample is obtained $I_{nm}
+=\int^{a}_0 dx \int^{b}_0 dy \ \ e^{i\vec{G}\vec{r}}$
 \begin{eqnarray}
-\nonumber I_{nm}=\dfrac{1}{G_x G_y} (e^{-iG_xa}-1) (e^{-G_y b}-1) \\ I_{nm}=\dfrac{ab}{nm \pi^2} ((-1)^n-1-1)(-(1)^m-1-1)
+\nonumber I_{nm}=\dfrac{1}{G_x G_y} (e^{-iG_xa}-1) (e^{-G_y b}-1) \\
+  I_{nm}=\dfrac{ab}{nm \pi^2} ((-1)^n-1-1)(-(1)^m-1-1)
 \end{eqnarray}
-Using the factor of the reciprocal vector in this way $ \vec {G} = \bigg (\dfrac{\pi}{a} n, \dfrac{\pi}{b} m \bigg) $,
-however, as all the coefficients of $ e^{- i \vec{G} \vec{r}} $ in \ref{Eq:J} they are even in $ \vec{G} $ and the integral is odd in n and m, only the constant term taxpayer to the integrated current
+Using the factor of the reciprocal vector in this way $ \vec {G} =
+\bigg (\dfrac{\pi}{a} n, \dfrac{\pi}{b} m \bigg) $,
+however, as all the coefficients of $ e^{- i \vec{G} \vec{r}} $ in
+\ref{Eq:J} they are even in $ \vec{G} $ and the integral is odd in n
+and m, only the constant term taxpayer to the integrated current
 \begin{eqnarray}
@@
 \subsection{Transfer Matrix Method (TMM)}
-One of the methods used for the analysis of photonic crystal structures is the transfer matrix method.
-We use it to investigate the reflectance of light in a one-dimensional photonic crystal.
-The electric and magnetic fields within the layers are shown as $E_m$ and $H_m$.
-Then we can specify the electric and magnetic fields in the air, $ E_0 $ and $ H_0 $, by solving the following matrix equation:
+One of the methods used for the analysis of photonic crystal
+structures is the transfer matrix method. We use it to investigate the
+reflectance of light in a one-dimensional photonic crystal. The
+electric and magnetic fields within the layers are shown as $E_m$ and
+$H_m$. Then we can specify the electric and magnetic fields in the
+air, $ E_0 $ and $ H_0 $, by solving the following matrix equation:
 \begin{equation}
@@
 \end{equation}
-Where N is the total number of layers including the cavity layer and $ M_j $ is the matrix characteristic of the layer $ j $ specified by:
+Where N is the total number of layers including the cavity layer and $
+M_j $ is the matrix characteristic of the layer $ j $ specified by:
 \begin{equation}
@@
 \end{equation}
-where $ \lambda $ is the wavelength, $ \tilde{n}_{_{j}} = n_{j} - ik_{_{j}}$ is the complex refractive index (CRI) of the layer, $ d_j $ is the thickness of the layer, and $ \theta_j $ is the angle of refraction of light in the $ j $ layer.
-The parameter $ \eta_ {j} $ for layer j is defined as:
+where $ \lambda $ is the wavelength, $ \tilde{n}_{_{j}} = n_{j} -
+ik_{_{j}}$ is the complex refractive index (CRI) of the layer, $ d_j $
+is the thickness of the layer, and $ \theta_j $ is the angle of
+refraction of light in the $ j $ layer. The parameter $ \eta_ {j} $
+for layer j is defined as:
 \begin{equation}\label{Eq:Mt1}
@@
 \end{equation}
-where $ \epsilon_0 $ and $ \mu_0 $ are permittivity and free space permeability, respectively. The transfer matrix of all the photonic crystal is given by:
+where $ \epsilon_0 $ and $ \mu_0 $ are permittivity and free space
+permeability, respectively. The transfer matrix of all the photonic
+crystal is given by:
 \begin{equation}
@@
 \end{equation}
-We can write the reflection and transmission coefficients in a one-dimensional photonic crystal nanocavity as:
+We can write the reflection and transmission coefficients in a
+one-dimensional photonic crystal nanocavity as:
 \begin{equation}
-r=\frac{\eta_0(m_{11}m_{12}\eta_m) -(m_{21}+m_{22}\eta_m)}{\eta_0(m_{11}m_{12}\eta_m) -(m_{21}+m_{22}\eta_m)}
+r=\frac{\eta_0(m_{11}m_{12}\eta_m)
+  -(m_{21}+m_{22}\eta_m)}{\eta_0(m_{11}m_{12}\eta_m)
+  -(m_{21}+m_{22}\eta_m)}
 \end{equation}
@@
 \end{equation}
-where $ \eta_0 $ and $ \eta_m $ are parameters for air and outlet layers, respectively (as defined in equations \ref{Eq:Mt1} or \ref{Eq:Mt2}).
-Furthermore, the reflectivity R and transmittance T of the entire photonic crystal nanocavity is given by:
+where $ \eta_0 $ and $ \eta_m $ are parameters for air and outlet
+layers, respectively (as defined in equations \ref{Eq:Mt1} or
+\ref{Eq:Mt2}). Furthermore, the reflectivity R and transmittance T of
+the entire photonic crystal nanocavity is given by:
 \begin{equation}
@@
   \centering
-	\includegraphics[scale=0.6]{../Images/DE1}
-	\caption{\emph{Schematic of the experimental set-up for fabrication of porous silicon with GRIN.
-a) Represents an outline of the surface section, divided by three regions A, B and C, corresponding to High, Medium and Low Porosity respectively.
-b) It is the diagram of the electrochemical cell with its parts: silicon wafer, Teflon cell, platinum point electrode, Electrochemical Aqueous solution and the connection of the circuit with the cathode and anode.
-c) It is a schematic drawing of the Cross section of the electrochemically attacked porous silicon seen in three different regions as mentioned above.
-}}.
+  \includegraphics[scale=0.6]{Images/DE1}
+\caption{\emph{Schematic of the experimental set-up for
+      fabrication of porous silicon with GRIN. (a) Represents an
+      outline of the surface section, divided by three regions
+      A, B and C, corresponding to High, Medium and Low Porosity
+      respectively. (b) It is the diagram of the electrochemical
+      cell with its parts: silicon wafer, Teflon cell, platinum
+      point electrode, Electrochemical Aqueous solution and the
+      connection of the circuit with the cathode and anode. (c)
+      It is a schematic drawing of the Cross section of the
+      electrochemically attacked porous silicon seen in three
+      different regions as mentioned above. }}
     \label{fig:DE1}
   \end{figure}
-In the Fig.
-\ref{fig:DE1} a shows schematic representation of the experimental setup where porous silicon can be manufactured with GRIN, taking into account the considerations of the electrode as tip, the rectangular cell and the sample (silicon wafer) with the largest rectangular attack area.
-In Fig.
-\ref{fig:DE1} a) we draw an outline of the surface section, divided by three regions A, B and C, dependes in therir porosity i.e., High, Medium and Low Porosity.
-All this corresponding to  expected to be obtained in the experiments.
-Fig.
-\ref{fig:DE1} b) the scheme shows the electrochemical cell with its parts: silicon wafer, teflon cell, platinum point electrode, electrochemical Aqueous Solution and the connection of the circuit with the cathode and anode.
-Finally, Fig.
-\ref{fig:DE1} c) it is a schematic drawing of the Cross section of the electrochemically attacked porous silicon seen from three different regions as mentioned above.
-In section 3.1 we give the details used to carry out our experiments.
+\end{document}
+In the Fig. \ref{fig:DE1} a shows schematic representation of the
+experimental setup where porous silicon can be manufactured with GRIN,
+taking into account the considerations of the electrode as tip, the
+rectangular cell and the sample (silicon wafer) with the largest
+rectangular attack area.
+In Fig. \ref{fig:DE1} a) we draw an outline of the surface section,
+divided by three regions A, B and C, dependes in therir porosity i.e.,
+High, Medium and Low Porosity. All this corresponding to  expected to
+be obtained in the experiments. Fig. \ref{fig:DE1} b) the scheme shows
+the electrochemical cell with its parts: silicon wafer, teflon cell,
+platinum point electrode, electrochemical Aqueous Solution and the
+connection of the circuit with the cathode and anode. Finally,
+Fig. \ref{fig:DE1} c) it is a schematic drawing of the Cross section
+of the electrochemically attacked porous silicon seen from three
+different regions as mentioned above. In section 3.1 we give the
+details used to carry out our experiments.
 
 \subsection{Fabrication of Porous Silicon Monolayers GRIN}
-Some of the simulated photonic structures were made by electrochemical anodization on an oriented (100) p-type crystalline Si wafer (resistivity 0.002 - 0.005 $ \Omega \cdot cm $), under galvanostatic conditions.
-The electrochemical anodization process was performed at room temperature, with an electrolytic mixture of aqueous hydrofluoric acid (HF) (concentration: 48 $ \% $ wt), glycerol (purity: 99.8 $ \% $ wt) and ethanol (purity: 99.9 $ \%$ wt ) in 3: 7: 1 volume ratio, respectively.
-After the anodizing process, the samples are rinsed with ethanol (purity: 99.9 $ \% $  wt).
-The layout of the cell used is as seen in Fig.
-\ref{fig:DE1} b), with an area of $ 1,206 \ \ cm^2 $ (this is the area attacked in the process), has a rectangular shape ($ 0.62 \ \ cm \times 2.03 \ \ cm $)  so that the current densities  that attacks has a lateral gradient with a greater surface area.
-They were manufactured with a fixed current of $ 5 \ \ mA $ to generate different current densities ranging from $ 6  $ to $ 2.5 \ \ mA / cm^2 $.
-Similarly, we use the current from $ 40 \ \ mA $ to generate $ 50 $ to $ 20 \ \ mA / cm ^ 2 $.
-The cathode is made of a platinum wire that was arranged in the form of a tip with an approximate diameter of ($ 0.5 \ \ mm $).
+Some of the simulated photonic structures were made by electrochemical
+anodization on an oriented (100) p-type crystalline Si wafer
+(resistivity 0.002 - 0.005 $ \Omega \cdot cm $), under galvanostatic
+conditions. The electrochemical anodization process was performed at
+room temperature, with an electrolytic mixture of aqueous hydrofluoric
+acid (HF) (concentration: 48 $ \% $ wt), glycerol (purity: 99.8 $ \% $
+wt) and ethanol (purity: 99.9 $ \%$ wt ) in 3: 7: 1 volume ratio,
+respectively. After the anodizing process, the samples are rinsed with
+ethanol (purity: 99.9 $ \% $  wt). The layout of the cell used is as
+seen in Fig. \ref{fig:DE1} b), with an area of $ 1,206 \ \ cm^2 $
+(this is the area attacked in the process), has a rectangular shape ($
+0.62 \ \ cm \times 2.03 \ \ cm $)  so that the current densities  that
+attacks has a lateral gradient with a greater surface area. They were
+manufactured with a fixed current of $ 5 \ \ mA $ to generate
+different current densities ranging from $ 6  $ to $ 2.5 \ \ mA / cm^2
+$. Similarly, we use the current from $ 40 \ \ mA $ to generate $ 50 $
+to $ 20 \ \ mA / cm ^ 2 $. The cathode is made of a platinum wire that
+was arranged in the form of a tip with an approximate diameter of ($
+0.5 \ \ mm $).
 \subsection{Reflectance Measurement}
-In the experiemental parte the reflectivity measurements were carried out with a Perkin Elmer Lambda 950 UV-Vis-NIR spectrophotometer.
-To calculate the complex refractive index $ \tilde{n}_{_{PSi}} = n_{_ {PSi}} - ik_{_{PSi}} $ of a porous layer with homogeneous porosity and thickness with smooth interfaces to throughout the entire structure, the more suitable is the adjustment procedure of the experimental reflectance or transmittance spectrum, this is for the theoretical part.
-In the case of the reflectance spectrum.
-The corresponding theoretical calculations were carried using procedure for single  smooth layer (monolayer).
+In the experiemental parte the reflectivity measurements were carried
+out with a Perkin Elmer Lambda 950 UV-Vis-NIR spectrophotometer. To
+calculate the complex refractive index $ \tilde{n}_{_{PSi}} = n_{_
+  {PSi}} - ik_{_{PSi}} $ of a porous layer with homogeneous porosity
+and thickness with smooth interfaces to throughout the entire
+structure, the more suitable is the adjustment procedure of the
+experimental reflectance or transmittance spectrum, this is for the
+theoretical part. In the case of the reflectance spectrum. The
+corresponding theoretical calculations were carried using procedure
+for single  smooth layer (monolayer).
  \begin{eqnarray}\label{Eq:ECMR}
@@
 \end{eqnarray}
-where $ r_{_ {01}} $ y $ r_{_ {12}} $ are the Fresnel reflectance coefficients at the interfaces $aire/PSi$ y $PSi/c-Si$ which are defined in terms of their complex refractive index ($\tilde{n}_{_ {1}} $, $\tilde{n}_{_ {2}} $ y $ \tilde{n}_{_ {3}} $), for them $r_{_{ij}}=(\tilde{n}_{_{i}}\cos\theta_i-\tilde{n}_{_{j}}\cos\theta_j)/(\tilde{n}_{_{i}}\cos\theta_i+\tilde{n}_{_{j}}\cos\theta_j)$, ($j=i=0,1,2$), whilst $\delta=2\pi d/\lambda\sqrt{\tilde{n}^2_{_{2}}-\tilde{n}^2_{_{1}}\sin \theta_1}$.
- To adjust the reflectance spectrum, the layer thickness is an input parameter in the Eq.\ref{Eq:ECMR}.
-The advantage of this method is the possibility of taking into account the interface roughness effect by including the Davies-Bennett factor in the coefficient of each Fresnel \cite{I17, I18, I19}, which represents the roughness of a Gaussian distribution.
+where $ r_{_ {01}} $ y $ r_{_ {12}} $ are the Fresnel reflectance
+coefficients at the interfaces $aire/PSi$ y $PSi/c-Si$ which are
+defined in terms of their complex refractive index ($\tilde{n}_{_ {1}}
+$, $\tilde{n}_{_ {2}} $ y $ \tilde{n}_{_ {3}} $), for them
+$r_{_{ij}}=(\tilde{n}_{_{i}}\cos\theta_i-\tilde{n}_{_{j}}\cos\theta_j)/(\tilde{n}_{_{i}}\cos\theta_i+\tilde{n}_{_{j}}\cos\theta_j)$,
+($j=i=0,1,2$), whilst $\delta=2\pi
+d/\lambda\sqrt{\tilde{n}^2_{_{2}}-\tilde{n}^2_{_{1}}\sin \theta_1}$.
+ To adjust the reflectance spectrum, the layer thickness is an input
+ parameter in the Eq.\ref{Eq:ECMR}. The advantage of this method is
+ the possibility of taking into account the interface roughness effect
+ by including the Davies-Bennett factor in the coefficient of each
+ Fresnel \cite{I17, I18, I19}, which represents the roughness of a
+ Gaussian distribution.
 \subsection{Morphological studies}
-The morphologies of the etched porous layers (cross-sectional) was observed using SEM Hitachi SU1510 scanning electron microscopes (Hitachi High Technologies Canada, Inc., Toronto, Canada), the thickness  and porosity  of each fabricated  film was measured.
+The morphologies of the etched porous layers (cross-sectional) was
+observed using SEM Hitachi SU1510 scanning electron microscopes
+(Hitachi High Technologies Canada, Inc., Toronto, Canada), the
+thickness  and porosity  of each fabricated  film was measured.
  \subsection{Refraction Indices Monolayer of Porous Silicon GRIN }
-Through the electrochemical anodization of c-Si wafers, Psi monolayers were obtained.
-For the refractive index of each monolayer Psi calcalated by ussing  Bruggeman effective medium theory, as we consider that we have a homogeneous medium associated with effective dielectric function \cite{I20}.
-This effective dielectric function is related to the dielectric functions of the two media, consisting of two materials (air and silicon), where it is assumed that all the pores or islands of the bulk material experience an average electric field; the equation is expressed as follows:
+Through the electrochemical anodization of c-Si wafers, Psi monolayers
+were obtained. For the refractive index of each monolayer Psi
+calcalated by ussing  Bruggeman effective medium theory, as we
+consider that we have a homogeneous medium associated with effective
+dielectric function \cite{I20}. This effective dielectric function is
+related to the dielectric functions of the two media, consisting of
+two materials (air and silicon), where it is assumed that all the
+pores or islands of the bulk material experience an average electric
+field; the equation is expressed as follows:
  \begin{eqnarray}\label{Eq:Brugg}
- p\dfrac{\varepsilon_{_{air}}-\varepsilon_{_{PSi}}}{\varepsilon_{_{air}}+\varepsilon_{_{PSi}}}+(1-p)\dfrac{\varepsilon_{_{Si}}-\varepsilon_{_{PSi}}}{\varepsilon_{_{Si}}+ \varepsilon_{_{PSi}}}
+ p\dfrac{\varepsilon_{_{air}}-\varepsilon_{_{PSi}}}{\varepsilon_{_{air}}+\varepsilon_{_{PSi}}}+(1-p)\dfrac{\varepsilon_{_{Si}}-\varepsilon_{_{PSi}}}{\varepsilon_{_{Si}}+
+   \varepsilon_{_{PSi}}}
  \end{eqnarray}
- where $ p $ is the volume fraction of air within the PSi layer (porosity); $\varepsilon_{_{air}}$ is the dielectric function of air; $\varepsilon_{_{Si}}$ is the dielectric function of c-Si, and $\varepsilon_{_{PSi}}$ represents the dielectric function of PSi.
-The dielectric function is a complex number and is related to the complex refractive index ($\tilde{n} = n - ik$), which is made up of real and imaginary parts, as follows $\varepsilon=\tilde{n}^2$.
-Its real part ($ n $) represents the ordinary refractive index when no light absorption occurs.
-The imaginary part ($ k $) is known as the extinction coefficient.
-The extinction coefficient determines the absorption rate in the medium \cite{I21}.
-Porosity can be estimated using the Bruggeman approximation, from Eq.
-\ref{Eq:Brugg} provided that the dielectric functions of each component (air and c-Si) are known.
+ where $ p $ is the volume fraction of air within the PSi layer
+ (porosity); $\varepsilon_{_{air}}$ is the dielectric function of air;
+ $\varepsilon_{_{Si}}$ is the dielectric function of c-Si, and
+ $\varepsilon_{_{PSi}}$ represents the dielectric function of PSi. The
+ dielectric function is a complex number and is related to the complex
+ refractive index ($\tilde{n} = n - ik$), which is made up of real and
+ imaginary parts, as follows $\varepsilon=\tilde{n}^2$. Its real part
+ ($ n $) represents the ordinary refractive index when no light
+ absorption occurs. The imaginary part ($ k $) is known as the
+ extinction coefficient. The extinction coefficient determines the
+ absorption rate in the medium \cite{I21}. Porosity can be estimated
+ using the Bruggeman approximation, from Eq. \ref{Eq:Brugg} provided
+ that the dielectric functions of each component (air and c-Si) are
+ known.
 
  \subsection{Fabrication  of Microcavities of Porous Silicon GRIN }
- A conventional way to fabricate the porous silicon microcavity (MC) is a defect with a mode located between two DBRs (Distributed Bragg Reflector).
-Alternate layers of high refractive index (H) and low (L) refractive index are obtained, satisfying the Bragg condition $n_{_{i}}d_{_{i}}=\frac{\lambda_{_{c}}}{4}$  where $ i = H, L $.
-The defect must meet the condition  $n_{_{L}}d_{_{L}}=\frac{\lambda_{_{c}}}{2}$, and the MC has the following sequence: $$ (HL)_6 HH (LH )_6 $$
- Initial data for conventional design we use $\lambda_{_{c}}= 0.67 \mu m$, $n_{_{H}} =2,6$, $P_{_{H}} =0.46$, $d_{_{H}}=0.066 \mu m  $, $t_{_{H}}=35 s  $ and for $n_{_{L}}= 1,4$,  $P_{_{L}} =0.75$, $d_{_{L}}=0.117 \mu m  $, $t_{_{L}}=11 s  $.
-All of this data is for the $ 0 $ point of the sample that is located at one end of the sample just below the tip counter-electrode.\\
- Our proposal for the fabrication of porous silicon GRIN microcavities uses the same conditions for fabrications of porous silicon GRIN monolayers as in section 3.1, and taking the conventional data mentioned above.
-The porous silicon microcavities (PSiMC) with gradient refractive index (GRIN), were manufactured with different current densities ranging from $ 6 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a current of $ 5 \ \ mA $, with high refractive index $n_{_{H}} \sim 2,761 $ to $ 2,808 $ and porosities from $ 0.44 $ to $ 0.39 $.
-Also for $ 50  $ to $ 20 \ \ mA / cm ^ 2 $, current of $ 38 \ \ mA $, for low refractive index $n_{_{L}}\sim 1,448 $ to $ 2,267 $ and with the corresponding  porosities of $ 0.75 $ to $ 0.64 $.
-Using our calibration ratio to design GRIN structures,  the corresponding current density for each measurement point.
+ A conventional way to fabricate the porous silicon microcavity (MC)
+ is a defect with a mode located between two DBRs (Distributed Bragg
+ Reflector). Alternate layers of high refractive index (H) and low (L)
+ refractive index are obtained, satisfying the Bragg condition
+ $n_{_{i}}d_{_{i}}=\frac{\lambda_{_{c}}}{4}$  where $ i = H, L $. The
+ defect must meet the condition
+ $n_{_{L}}d_{_{L}}=\frac{\lambda_{_{c}}}{2}$, and the MC has the
+ following sequence: $$ (HL)_6 HH (LH )_6 $$
+ Initial data for conventional design we use $\lambda_{_{c}}= 0.67 \mu
+ m$, $n_{_{H}} =2,6$, $P_{_{H}} =0.46$, $d_{_{H}}=0.066 \mu m  $,
+ $t_{_{H}}=35 s  $ and for $n_{_{L}}= 1,4$,  $P_{_{L}} =0.75$,
+ $d_{_{L}}=0.117 \mu m  $, $t_{_{L}}=11 s  $. All of this data is for
+ the $ 0 $ point of the sample that is located at one end of the
+ sample just below the tip counter-electrode.\\
+ Our proposal for the fabrication of porous silicon GRIN microcavities
+ uses the same conditions for fabrications of porous silicon GRIN
+ monolayers as in section 3.1, and taking the conventional data
+ mentioned above. The porous silicon microcavities (PSiMC) with
+ gradient refractive index (GRIN), were manufactured with different
+ current densities ranging from $ 6 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a
+ current of $ 5 \ \ mA $, with high refractive index $n_{_{H}} \sim
+ 2,761 $ to $ 2,808 $ and porosities from $ 0.44 $ to $ 0.39 $. Also
+ for $ 50  $ to $ 20 \ \ mA / cm ^ 2 $, current of $ 38 \ \ mA $, for
+ low refractive index $n_{_{L}}\sim 1,448 $ to $ 2,267 $ and with the
+ corresponding  porosities of $ 0.75 $ to $ 0.64 $. Using our
+ calibration ratio to design GRIN structures,  the corresponding
+ current density for each measurement point.
 
@@
 \subsection{Simulation of the EMPCGRIN model}
- To test the developed  idea in the theoretical section, we find a relation of the tip of the counter electrode that acts similarly as a point charge and the current density for a geometry in an electrolytic box and solve the electrostatic equations with suitable boundary conditions.
-Resulting in an electrostatic model for photonic crystals with a refractive index with gradient (EMPCGRIN).
+ To test the developed  idea in the theoretical section, we find a
+ relation of the tip of the counter electrode that acts similarly as a
+ point charge and the current density for a geometry in an
+ electrolytic box and solve the electrostatic equations with suitable
+ boundary conditions. Resulting in an electrostatic model for photonic
+ crystals with a refractive index with gradient (EMPCGRIN).
 \begin{figure}[H]
   \centering
-	\includegraphics[scale=0.7]{../Images/G123}
-	\caption{\emph{ Simulation to calculate the current density in a structure with gradient refractive index (GRIN) produced by electrochemical attack on crystalline silicon to produce porous silicon (PSi), with a current density profile $ J (mA / cm ^ 2 ) $ normalized with the electric current $ I (mA) $, we have $ J / I \sim 0.5 \ \ a \ \ 1.2 (cm^{-2}) $, for a cell of $ a = 2.03 \ \ cm $ y $ b = 0.62 \ \ cm $, with an electrode height $ Z_0 = 0.96 \ \ cm $} Eq.
-(\ref{Eq:J})}.
+  \includegraphics[scale=0.7]{Images/G123}
+  \caption{\emph{ Simulation to calculate the current density in
+      a structure with gradient refractive index (GRIN) produced
+      by electrochemical attack on crystalline silicon to
+      produce porous silicon (PSi), with a current density
+      profile $ J (mA / cm ^ 2 ) $ normalized with the electric
+      current $ I (mA) $, we have $ J / I \sim 0.5 \ \ a \ \ 1.2
+      (cm^{-2}) $, for a cell of $ a = 2.03 \ \ cm $ y $ b =
+      0.62 \ \ cm $, with an electrode height $ Z_0 = 0.96 \ \
+      cm $} Eq. (\ref{Eq:J})}.
   \label{fig:DR1}
 \end{figure}
-We consider Fig.
-\ref{fig:DR1} which come from solving Eq.
-(\ref{Eq:J}), calculating the current density as a function of the rectangular cell area of $1,206 \ \ cm^2 $,  the programming with the PERL PDL package and corresponding graph in gnuplot.
-We optimize the appropriate values so that our current density adequately attacks crystalline silicon, giving the gradient effect.
-We use as length $a = 2.03 \ \ cm $ and width $b = 0.62 \ \ cm $ the height of the solution is $ c = 1 \ \ cm $ and we could locate the tip of the electrode at $ R_0 = (X_0 = 0.2 , \ \ Y_0 = 0.4 \ \, Z_0 = 0.96) \ \ cm $ and evaluated at the surface on the silicon interface, in the plane $ Z = 0 $.
-In this same Figure \ref{fig:DR1}, we obtain a current density profile $ J (mA / cm^2) $ normalized with the electric current $ I (mA) $, we have $ J / I \sim 1.2 \ \ a \ \ 0.5 (cm ^{-2}) $, as we see in Fig.
-\ref{fig:DR1} a) an effect that happens on the surface of the sample, a change of contrate due to the different densities of attacked currents.
-We see the decay behavior that the profile has as Fig.
-\ref{fig:DR1} b) which is a cut on the axis of $ a $.
-When we vary the currents we can observe the behavior of changes in the normalized current density, with the data obtained through the simulation we could have a better optimization in the design of porous silicon proposing a new and novel experimental arrangement, in the same way we can give ourselves an idea by means of the graph of how the attack would be and the formal side of the pores in the silicon.
+We consider Fig. \ref{fig:DR1} which come from solving
+Eq. (\ref{Eq:J}), calculating the current density as a function of the
+rectangular cell area of $1,206 \ \ cm^2 $,  the programming with the
+PERL PDL package and corresponding graph in gnuplot. We optimize the
+appropriate values so that our current density adequately attacks
+crystalline silicon, giving the gradient effect. We use as length $a =
+2.03 \ \ cm $ and width $b = 0.62 \ \ cm $ the height of the solution
+is $ c = 1 \ \ cm $ and we could locate the tip of the electrode at $
+R_0 = (X_0 = 0.2 , \ \ Y_0 = 0.4 \ \, Z_0 = 0.96) \ \ cm $ and
+evaluated at the surface on the silicon interface, in the plane $ Z =
+0 $. In this same Figure \ref{fig:DR1}, we obtain a current density
+profile $ J (mA / cm^2) $ normalized with the electric current $ I
+(mA) $, we have $ J / I \sim 1.2 \ \ a \ \ 0.5 (cm ^{-2}) $, as we see
+in Fig. \ref{fig:DR1} a) an effect that happens on the surface of the
+sample, a change of contrate due to the different densities of
+attacked currents. We see the decay behavior that the profile has as
+Fig. \ref{fig:DR1} b) which is a cut on the axis of $ a $. When we
+vary the currents we can observe the behavior of changes in the
+normalized current density, with the data obtained through the
+simulation we could have a better optimization in the design of porous
+silicon proposing a new and novel experimental arrangement, in the
+same way we can give ourselves an idea by means of the graph of how
+the attack would be and the formal side of the pores in the silicon.
 
@@
 	\includegraphics[scale=.3]{../Images/celdan2}
-	\caption{\emph{ Mechanical 3D modeling, design of the electrochemical cell where we can see the shape of a prism giving the required and necessary data for the experiments.
-The design of the cell used is $ 1,206 \ \ cm ^ 2 $ (this is the area attacked in the process), the area attacked is rectangular ($ 0.62 \ \ cm \times 2.03 \ \ cm $) and a height ( $ 1.2 \ \ cm $) a) Complete cell b) Cell without top cover and c) Top view}}
+	\caption{\emph{ Mechanical 3D modeling, design of the
+            electrochemical cell where we can see the shape of a prism
+            giving the required and necessary data for the
+            experiments. The design of the cell used is $ 1,206 \ \ cm
+            ^ 2 $ (this is the area attacked in the process), the area
+            attacked is rectangular ($ 0.62 \ \ cm \times 2.03 \ \ cm
+            $) and a height ( $ 1.2 \ \ cm $) a) Complete cell b) Cell
+            without top cover and c) Top view}}
 	\label{fig:por1}
 \end{figure}
-We can see in Fig.
-\ref{fig:por1}, 3D modeling the mechanical design for the electrochemical cell  better optimization in manufacturing silicon pores where we can see the shape of a prism giving the required data.
-The design of the cell used is $ 1,206 \ \ cm ^ 2 $ (this is the area attacked in the process), the area attacked is rectangular ($ 0.62 \ \ cm \times 2.03 \ \ cm $) and a height ( $ 1.2 \ \ cm $), all this in order to optimize our experiments adjusted to all the needs that this required.
+We can see in Fig. \ref{fig:por1}, 3D modeling the mechanical design
+for the electrochemical cell  better optimization in manufacturing
+silicon pores where we can see the shape of a prism giving the
+required data. The design of the cell used is $ 1,206 \ \ cm ^ 2 $
+(this is the area attacked in the process), the area attacked is
+rectangular ($ 0.62 \ \ cm \times 2.03 \ \ cm $) and a height ( $ 1.2
+\ \ cm $), all this in order to optimize our experiments adjusted to
+all the needs that this required.
 \begin{figure}[H]
   \centering
-	\includegraphics[scale=.5]{../Images/SPgrin51}
-	\caption{\emph{a) Silicon sample attacked with an electrolytic mixture of aqueous hydrofluoric acid (HF) (concentration: 48 $ \% $  wt), glycerol (purity: 99.8 $ \% $  wt) and ethanol (purity: 99.9 $ \% $  wt ) in 3: 7: 1 volume ratio, respectively.
-Obtaining a monolayer of porous Silicon with GRIN G1 with an initial current of G1 (5 mA), with an attack time of 600s.
-Three different locations are considered, denoted as follows, A (0.3cm) and B (0.8cm) and C (1.7cm).
-b) Reflectance measurements to know the optical properties at each of the points and the adjustments that were produced by means of the equation \ref{Eq:ECMR}.
-c) We have the indices of refraction of the complex porous silicon GRIN, where we calculate the real and imaginary part by means of the equation \ref{Eq:Brugg}.
-for different porosities at each point, A (P = 0.44), B (P = 0.42) and C (P = 0.40) } }
+  \includegraphics[scale=.5]{Images/SPgrin51}
+  \caption{\emph{a) Silicon sample attacked with an electrolytic
+      mixture of aqueous hydrofluoric acid (HF) (concentration:
+      48 $ \% $  wt), glycerol (purity: 99.8 $ \% $  wt) and
+      ethanol (purity: 99.9 $ \% $  wt ) in 3: 7: 1 volume
+      ratio, respectively. Obtaining a monolayer of porous
+      Silicon with GRIN G1 with an initial current of G1 (5 mA),
+      with an attack time of 600s. Three different locations are
+      considered, denoted as follows, A (0.3cm) and B (0.8cm)
+      and C (1.7cm). b) Reflectance measurements to know the
+      optical properties at each of the points and the
+      adjustments that were produced by means of the equation
+      \ref{Eq:ECMR}. c) We have the indices of refraction of the
+      complex porous silicon GRIN, where we calculate the real
+      and imaginary part by means of the equation
+      \ref{Eq:Brugg}. for different porosities at each point, A
+      (P = 0.44), B (P = 0.42) and C (P = 0.40) } }
   \label{fig:DR3}
 \end{figure}
- The Fig.
-\ref{fig:DR3} a) three locations at different points are considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $, from the sample of PSi GRIN $ G1 (I = 5 mA) $.
-Also the Fig.
-\ref{fig:DR3}.
-b), we have the reflectance measurements to know the optical properties and the adjustments that were produced by means of the equation \ref{Eq:ECMR}.
-In the Fig.
-\ref{fig:DR3} c) are indices of refraction of the porous silicon complex GRIN, where we calculate the real and imaginary part by means of Eq.
-\ref{Eq:Brugg} for different porosities at each point, $ A (P = 0.44) $, $ B (P = 0.42) $ and $ C (P = 0.40) $.
-Location $ A $ is closest to the electrode, while location $ C $ is furthest to the other end of the sample.
-Since the current density is applied from one end, the field lines attack the sample laterally to the silicon wafer, in the present configuration, an assembly was made based on the simulated data shown in Fig.
-\ref{fig:DR1} the experimental part was taken a platinum electrode covering its surface, leaving only a very small area, as if it were a tip.
-The electrochemical reaction takes place when we apply currents from an anode end (electrode tip) to the silicon substrate (resistivity $ 0.002 - 0.005  \Omega \cdot cm $), through an electrolyte forming a current circuit.
-The reflectance spectra of the newly recorded G1 samples measured at points $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $ are presented in Fig.
-\ref{fig:DR3} b), a numerical reflectivity adjustment was performed using the transfer matrix method for the case of a porous monolayer in Si.
-It should be noted that the adjustment made was considered a spectral range of the wavelength of the experimental reflectivity spectra for which the silicon can be considered the complex index and thus find the refractive index of the complex porous silicon with the purpose of determining the porosity and the experimental physical thickness (nm) by means of the SEM.
-The formation of PSi GRIN in the thickness occurs due to the variation in the concentration of the voids available at the Si electrolyte interface, therefore, an increase in the applied lateral current density increases the dimension of the pores and their depth.
-Thus, the extent of the porous film showing a gradient that can be controlled from the lateral current density.
+ The Fig. \ref{fig:DR3} a) three locations at different points are
+ considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B (0.8 \ \
+ cm) $ and $ C (1.7 \ \ cm) $, from the sample of PSi GRIN $ G1 (I = 5
+ mA) $. Also the Fig. \ref{fig:DR3}. b), we have the reflectance
+ measurements to know the optical properties and the adjustments that
+ were produced by means of the equation \ref{Eq:ECMR}. In the
+ Fig. \ref{fig:DR3} c) are indices of refraction of the porous silicon
+ complex GRIN, where we calculate the real and imaginary part by means
+ of Eq. \ref{Eq:Brugg} for different porosities at each point, $ A (P
+ = 0.44) $, $ B (P = 0.42) $ and $ C (P = 0.40) $. Location $ A $ is
+ closest to the electrode, while location $ C $ is furthest to the
+ other end of the sample. Since the current density is applied from
+ one end, the field lines attack the sample laterally to the silicon
+ wafer, in the present configuration, an assembly was made based on
+ the simulated data shown in Fig. \ref{fig:DR1} the experimental part
+ was taken a platinum electrode covering its surface, leaving only a
+ very small area, as if it were a tip. The electrochemical reaction
+ takes place when we apply currents from an anode end (electrode tip)
+ to the silicon substrate (resistivity $ 0.002 - 0.005  \Omega \cdot
+ cm $), through an electrolyte forming a current circuit. The
+ reflectance spectra of the newly recorded G1 samples measured at
+ points $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm)
+ $ are presented in Fig. \ref{fig:DR3} b), a numerical reflectivity
+ adjustment was performed using the transfer matrix method for the
+ case of a porous monolayer in Si. It should be noted that the
+ adjustment made was considered a spectral range of the wavelength of
+ the experimental reflectivity spectra for which the silicon can be
+ considered the complex index and thus find the refractive index of
+ the complex porous silicon with the purpose of determining the
+ porosity and the experimental physical thickness (nm) by means of the
+ SEM. The formation of PSi GRIN in the thickness occurs due to the
+ variation in the concentration of the voids available at the Si
+ electrolyte interface, therefore, an increase in the applied lateral
+ current density increases the dimension of the pores and their
+ depth. Thus, the extent of the porous film showing a gradient that
+ can be controlled from the lateral current density.
 \begin{figure}[H]
   \centering
-	\includegraphics[scale=.5]{../Images/semD11}
-	\caption{\emph{Characterization of a monolayer of PSi GRIN G1 with an initial current of $ 5 \ \ mA $, seeing the morphology and depth of the cross section of several SEM micrographs, at different points, $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $.
-We can see the sample size for each measurement point, the depth $ d (A) = 1320 \ \ nm $, $ d (B) = 997 \ \ nm $ and $ d (C) = 605 \ \ nm $ } }
+  \includegraphics[scale=.5]{Images/semD11}
+  \caption{\emph{Characterization of a monolayer of PSi GRIN G1
+      with an initial current of $ 5 \ \ mA $, seeing the
+      morphology and depth of the cross section of several SEM
+      micrographs, at different points, $ A (0.3 \ \ cm) $ and $
+      B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $. We can see the
+      sample size for each measurement point, the depth $ d (A)
+      = 1320 \ \ nm $, $ d (B) = 997 \ \ nm $ and $ d (C) = 605
+      \ \ nm $ } }
   \label{fig:DR4}
 \end{figure}
-In the Fig.
-\ref{fig:DR4} shows the cross section views   at points $ A (0.3 \ \ cm) $, $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $, we can measure the thickness for each point of the sample $ G1 (I = 5 \ \ mA) $, $ d (A) = 1320 \ \ nm $, $ d (B) = 997 \ \ nm $ and $ d (C) = 605 \ \ nm $.
-Likewise, we could check it for a second sample $ G2 (I = 40 \ \ mA) $, with porosities for each point, $ A (P = 0.76) $, $ B (P = 0.73) $ and $ C (P = 0.68) $ and the depths $ d (A) = 1950 \ \ nm $, $ d (B) = 1690 \ \ nm $ and $ d (C) = 1430 \ \ nm $, designed in the same way as the shows G1, only varying the current taking into account the current density ratio for each point.
-Apart from that, a structural gradient was formed, along the direction \emph{ a}  of the axis of the $ x $, where the tip of the electrode is near the point $ A $ and away from the point $ C $ of the substrate, using the proposed experimental setup.
-In addition, it was possible to control the current density based on the position of the sample and the depth, seen in the SEM micrographs.
+In the Fig. \ref{fig:DR4} shows the cross section views   at points $
+A (0.3 \ \ cm) $, $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $, we can
+measure the thickness for each point of the sample $ G1 (I = 5 \ \ mA)
+$, $ d (A) = 1320 \ \ nm $, $ d (B) = 997 \ \ nm $ and $ d (C) = 605 \
+\ nm $. Likewise, we could check it for a second sample $ G2 (I = 40 \
+\ mA) $, with porosities for each point, $ A (P = 0.76) $, $ B (P =
+0.73) $ and $ C (P = 0.68) $ and the depths $ d (A) = 1950 \ \ nm $, $
+d (B) = 1690 \ \ nm $ and $ d (C) = 1430 \ \ nm $, designed in the
+same way as the shows G1, only varying the current taking into account
+the current density ratio for each point. Apart from that, a
+structural gradient was formed, along the direction \emph{ a}  of the
+axis of the $ x $, where the tip of the electrode is near the point $
+A $ and away from the point $ C $ of the substrate, using the proposed
+experimental setup. In addition, it was possible to control the
+current density based on the position of the sample and the depth,
+seen in the SEM micrographs.
  \begin{figure}[H]
    \centering
- 	\includegraphics[scale=.7]{../Images/grinJDR}
- 	\caption{\emph{a) It is the relation of the current density $ J (mA / cm ^ 2) $ normalized with the electric current $ I (mA) $, we have $ J / I \ sim 1.2 \ \ a \ \ 0.5 ( cm^{-2}) $, when we apply it to two samples $ G1 (I = 5 \ \ mA) $ and $ G2 (I = 40 \ \ mA) $ depending on the axis $ a $ $ (0.1 ...
-2.0 \ \ cm) $, measured at points $ A (0.3 \ \ cm) $ , $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $.
-b) The attack speed $ v = d (J_i) / t (nm / sec) $, the depths (thickness $ d (J_i) $, $ i = $ $ A (0.3 \ \ cm) $, $ B ( 0.8 \ \ cm) $ y $ C (1.7 \ \ cm)) $ taken in SEM micrographs $ d (J_i) (nm) $ and attack times $ G1 (t = 600 \ \ s) $ y $ G2 (t = 200 \ \ s) $, depending on the axis $ a $ $ (0.1 ...
-2.0 \ \ cm) $ } }
+   \includegraphics[scale=.7]{Images/grinJDR}
+   \caption{\emph{a) It is the relation of the current density $
+       J (mA / cm ^ 2) $ normalized with the electric current $ I
+       (mA) $, we have $ J / I \ sim 1.2 \ \ a \ \ 0.5 ( cm^{-2})
+       $, when we apply it to two samples $ G1 (I = 5 \ \ mA) $
+       and $ G2 (I = 40 \ \ mA) $ depending on the axis $ a $ $
+       (0.1 ... 2.0 \ \ cm) $, measured at points $ A (0.3 \ \
+       cm) $ , $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $. b) The
+       attack speed $ v = d (J_i) / t (nm / sec) $, the depths
+       (thickness $ d (J_i) $, $ i = $ $ A (0.3 \ \ cm) $, $ B (
+       0.8 \ \ cm) $ y $ C (1.7 \ \ cm)) $ taken in SEM
+       micrographs $ d (J_i) (nm) $ and attack times $ G1 (t =
+       600 \ \ s) $ y $ G2 (t = 200 \ \ s) $, depending on the
+       axis $ a $ $ (0.1 ... 2.0 \ \ cm) $ } }
    \label{fig:JDR}
  \end{figure}
-In Fig.
-\ref{fig:JDR} a) It is the relation of the current density $ J (mA / cm ^ 2) $ normalized with the electric current $ I (mA) $, we have $ J / I \ sim 1.2 \ \ a \ \ 0.5 (1 / cm ^ 2) $, when we apply it to two samples $ G1 (I = 5 \ \ mA) $ and $ G2 (I = 40 \ \ mA) $ depending on the axis $ a $ $ (0.1 ...
-2.0 \ \ cm) $, measured at points $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $.
-The Fig.
-\ref{fig:JDR} b) we can calculate the attack speed $ v = d (J_i) / t (nm / s) $, where the depths (thickness $ d (J_i) $, $ i = $ $ A (0.3 \ \ cm) $, $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm)) $ taken in SEM micrographs $ d (J_i) (nm) $ and attack times $ G1 (t = 600 \ \ s) $ and $ G2 (t = 200 \ \ s) $, depending on the axis $ a $ $ (0.1 ...
-2.0 \ \ cm) $.
+In Fig. \ref{fig:JDR} a) It is the relation of the current density $ J
+(mA / cm ^ 2) $ normalized with the electric current $ I (mA) $, we
+have $ J / I \ sim 1.2 \ \ a \ \ 0.5 (1 / cm ^ 2) $, when we apply it
+to two samples $ G1 (I = 5 \ \ mA) $ and $ G2 (I = 40 \ \ mA) $
+depending on the axis $ a $ $ (0.1 ... 2.0 \ \ cm) $, measured at
+points $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm)
+$.
+The Fig. \ref{fig:JDR} b) we can calculate the attack speed $ v = d
+(J_i) / t (nm / s) $, where the depths (thickness $ d (J_i) $, $ i = $
+$ A (0.3 \ \ cm) $, $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm)) $ taken
+in SEM micrographs $ d (J_i) (nm) $ and attack times $ G1 (t = 600 \ \
+s) $ and $ G2 (t = 200 \ \ s) $, depending on the axis $ a $ $ (0.1
+... 2.0 \ \ cm) $.
 \begin{figure}[H]
   \centering
-	\includegraphics[scale=.6]{../Images/grinJD31}
-	\caption{\emph{The relationship of samples $ G1 (I = 5 mA) $ and $ G2 (I = 40 mA) $ were obtained to find: a) Attack speed with current density for each point and b) Porosity as a function of density current.
-With this we have the calibration curves for the manufacture of any GRIN porous silicon structure   } }
+  \includegraphics[scale=.6]{Images/grinJD31}
+  \caption{\emph{The relationship of samples $ G1 (I = 5 mA) $ and $
+      G2 (I = 40 mA) $ were obtained to find: a) Attack speed with
+      current density for each point and b) Porosity as a function of
+      density current. With this we have the calibration curves for
+      the manufacture of any GRIN porous silicon structure   } }
   \label{fig:Indr1}
 \end{figure}
-Fig.
-\ref{fig:Indr1} a) explicitly explain the relationships that emerge when designing samples $ G1 (I = 5 mA) $ and $ G2 (I = 40 mA) $.
-For the first case $ G1 $ the depths ($ 1320 \ \ nm $ to $ 605 \ \ nm $) and the current densities ($ 6 \ \ mA / cm ^ 2 $ to $ 2.5 \ \ mA / cm ^ 2 $), finding the attack speed $ 2.2 \ \ nm / s $ up to $ 1.1 \ \ nm / s $ relation with depth and the time ($ 600 \ \ s $) of exposure of the sample, with the current density .
-We also find the depth ($ 1950 \ \ nm $ at $ 1430 \ \ nm $) and the current density ($ 50 \ \ mA / cm ^ 2 $ at $ 20 \ \ mA / cm ^ 2 $) as a function of the measurement points of the sample $ G2 (I = 40 mA) $.
-We were able to obtain the attack speed from $ 9.8 \ \ nm / s $ up to $ 7.1 \ \ m / s $ by relating to depth and time ($ 200 \ \ s $), with current density.
-Once the thickness of the monolayer and the attack time applied to them are known, calculate the attack speed according to the formula $ v = d / t $, for each of the current densities at the points $ A ( 0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $.
-Then we fit a function to the attack speed points with the different current densities allowed by the anodizing condition.
-For a desired thickness $ d (J_i) $, calculate the attack time $ t $ (so, $ t = v / d (J_i) $) and we can design any structure knowing the current density and the attack time.
-Fig.
-\ref{fig:Indr1} b) we find a relation of the porosity for each position with its determined current density.
-Therefore, if it is desired to manufacture a PSi monolayer of a certain porosity with a certain end, it is enough to resort to the graphs of Fig.
-\ref{fig:Indr1} to determine the corresponding current density, attack speed and consequently the time, obtaining for that monolayer.
-The importance of the calibration curves is that it allows us to have a relationship of the porosities that can be reached (and by having control over the possible refractive indices) as a function of the current density and to be controlled to control the thickness of the layers that are manufactured, by controlling the attack time for each of the chosen currents.
+Fig. \ref{fig:Indr1} a) explicitly explain the relationships that
+emerge when designing samples $ G1 (I = 5 mA) $ and $ G2 (I = 40 mA)
+$. For the first case $ G1 $ the depths ($ 1320 \ \ nm $ to $ 605 \ \
+nm $) and the current densities ($ 6 \ \ mA / cm ^ 2 $ to $ 2.5 \ \ mA
+/ cm ^ 2 $), finding the attack speed $ 2.2 \ \ nm / s $ up to $ 1.1 \
+\ nm / s $ relation with depth and the time ($ 600 \ \ s $) of
+exposure of the sample, with the current density . We also find the
+depth ($ 1950 \ \ nm $ at $ 1430 \ \ nm $) and the current density ($
+50 \ \ mA / cm ^ 2 $ at $ 20 \ \ mA / cm ^ 2 $) as a function of the
+measurement points of the sample $ G2 (I = 40 mA) $. We were able to
+obtain the attack speed from $ 9.8 \ \ nm / s $ up to $ 7.1 \ \ m / s
+$ by relating to depth and time ($ 200 \ \ s $), with current
+density. Once the thickness of the monolayer and the attack time
+applied to them are known, calculate the attack speed according to the
+formula $ v = d / t $, for each of the current densities at the points
+$ A ( 0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm)
+$. Then we fit a function to the attack speed points with the
+different current densities allowed by the anodizing condition. For a
+desired thickness $ d (J_i) $, calculate the attack time $ t $ (so, $
+t = v / d (J_i) $) and we can design any structure knowing the current
+density and the attack time. Fig. \ref{fig:Indr1} b) we find a
+relation of the porosity for each position with its determined current
+density. Therefore, if it is desired to manufacture a PSi monolayer of
+a certain porosity with a certain end, it is enough to resort to the
+graphs of Fig. \ref{fig:Indr1} to determine the corresponding current
+density, attack speed and consequently the time, obtaining for that
+monolayer. The importance of the calibration curves is that it allows
+us to have a relationship of the porosities that can be reached (and
+by having control over the possible refractive indices) as a function
+of the current density and to be controlled to control the thickness
+of the layers that are manufactured, by controlling the attack time
+for each of the chosen currents.
 
@@
 	\centering
-	\includegraphics[scale=0.4]{../Images/MicrGrin}
-	\caption{\emph{Diagram of a microcavity of porous silicon GRIN.
-Alternate layers are obtained of high (H) refractive index $n_{_{Hi}}$ and low (L) refractive index $n_{_{Li}}$, where $N_{_{H}}$ is the number of layers for  $n_{_{Hi}}$ and $N_{_{L}}$ is the number of layers for $n_{_{Li}}$.
-Then,  $d_{_{Hi}}$ is the monolayer thickness of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$ is the monolayer thickness of $n_{_{Hi}}$ at that measurement point.
-Therefore,  $d_{_{i}}$ is the total thickness calculated for each of the measurements, defining a i = $ A, B, C$.
-Having the following relationship $d_{_{i}} = (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$.
-}}
+	\includegraphics[scale=0.4]{Images/MicrGrin}
+	\caption{\emph{Diagram of a microcavity of porous silicon
+            GRIN. Alternate layers are obtained of high (H) refractive
+            index $n_{_{Hi}}$ and low (L) refractive index
+            $n_{_{Li}}$, where $N_{_{H}}$ is the number of layers for
+            $n_{_{Hi}}$ and $N_{_{L}}$ is the number of layers for
+            $n_{_{Li}}$. Then,  $d_{_{Hi}}$ is the monolayer thickness
+            of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$
+            is the monolayer thickness of $n_{_{Hi}}$ at that
+            measurement point. Therefore,  $d_{_{i}}$ is the total
+            thickness calculated for each of the measurements,
+            defining a i = $ A, B, C$. Having the following
+            relationship $d_{_{i}} =
+            (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) +
+            (2d_{_{Hi}})$. }}
 	\label{fig:MCGRIN0}
 \end{figure}
-The Fig.
-\ref{fig:MCGRIN0} the scheme of  a initially proposed lateral gradient for monolayers should be shown in section 4.2, where we designed an electolytic cell suitable for our experiments and giving us the expected results of the simulation in section 4.1.
-Now our purpose is to manufacture more complex photonic structures such as the Porous silicon microcavities GRIN, taking into account that we start from having a tip electrode almost on the surface and by making a variation of currents we can achieve the effect of alternating the layers.
-Alternate layers are obtained of high (H) refractive index $n_{_{Hi}}$ and low (L) refractive index $n_{_{Li}}$, where $N_{_{H}}$ is the number of layers for  $n_{_{Hi}}$ and $N_{_{L}}$ is the number of layers for $n_{_{Li}}$.
-Then,  $d_{_{Hi}}$ is the monolayer thickness of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$ is the monolayer thickness of $n_{_{Hi}}$ at that measurement point.
-Therefore,  $d_{_{i}}$ is the total thickness calculated for each of the measurements, defining a i = $ A, B, C$.
-Having the following relationship $d_{_{i}} = (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$.
-Initial data for conventional design we use  $\lambda_{_{c}}= 0.67 \ \ \mu m$, $n_{_{H}} =2.6$, $P_{_{H}} =0.46$, $d_{_{H}}=0.066 \ \ \mu m  $, $t_{_{H}}=35 s  $ y para  $n_{_{L}}= 1.4$,  $P_{_{L}} =0.75$, $d_{_{L}}=0.117 \ \ \mu m  $, $t_{_{L}}=11 s  $.
-All these data are for the point $ 0 $ which is located at one end of the sample just below the tip counter-electrode.
+The Fig. \ref{fig:MCGRIN0} the scheme of  a initially proposed lateral
+gradient for monolayers should be shown in section 4.2, where we
+designed an electolytic cell suitable for our experiments and giving
+us the expected results of the simulation in section 4.1. Now our
+purpose is to manufacture more complex photonic structures such as the
+Porous silicon microcavities GRIN, taking into account that we start
+from having a tip electrode almost on the surface and by making a
+variation of currents we can achieve the effect of alternating the
+layers. Alternate layers are obtained of high (H) refractive index
+$n_{_{Hi}}$ and low (L) refractive index $n_{_{Li}}$, where $N_{_{H}}$
+is the number of layers for  $n_{_{Hi}}$ and $N_{_{L}}$ is the number
+of layers for $n_{_{Li}}$. Then,  $d_{_{Hi}}$ is the monolayer
+thickness of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$ is
+the monolayer thickness of $n_{_{Hi}}$ at that measurement
+point. Therefore,  $d_{_{i}}$ is the total thickness calculated for
+each of the measurements, defining a i = $ A, B, C$. Having the
+following relationship $d_{_{i}} =
+(N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$.
+Initial data for conventional design we use  $\lambda_{_{c}}= 0.67 \ \
+\mu m$, $n_{_{H}} =2.6$, $P_{_{H}} =0.46$, $d_{_{H}}=0.066 \ \ \mu m
+$, $t_{_{H}}=35 s  $ y para  $n_{_{L}}= 1.4$,  $P_{_{L}} =0.75$,
+$d_{_{L}}=0.117 \ \ \mu m  $, $t_{_{L}}=11 s  $. All these data are
+for the point $ 0 $ which is located at one end of the sample just
+below the tip counter-electrode.
 \begin{figure}[H]
   \centering
- 	\includegraphics[scale=.5]{../Images/MCGRIN2}
- 	\caption{\emph{a) Three locations at different points are considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the PSiMCGRIN sample $ GMC $.
-b) We have the reflectance measurements to know the optical properties with the proposed simulation.
-We were able to show that in a Porous Silicon GRIN structure, for a microcavity the data is very consistent with the simulation and the experiment, we found the refractive indices and the porosities as a function of the current density at each measurement point, see Table \ref{tabla:1}.
-}}
+  \includegraphics[scale=.5]{Images/MCGRIN2}
+  \caption{\emph{a) Three locations at different points are
+      considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B
+      (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the PSiMCGRIN
+      sample $ GMC $. b) We have the reflectance measurements to
+      know the optical properties with the proposed
+      simulation. We were able to show that in a Porous Silicon
+      GRIN structure, for a microcavity the data is very
+      consistent with the simulation and the experiment, we
+      found the refractive indices and the porosities as a
+      function of the current density at each measurement point,
+      see Table \ref{tabla:1}. }}
   \label{fig:MCGRIN3}
@@
   \end{tabular}
-	\caption{ \emph{We have different points denoted as follows, $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the sample of a Porous Silicon Microcavity GRIN  (PSiMCGRIN) $ GMC $.
-Alternate layers of high refractive index (H) and low refractive index (L) are obtained at each of the measurement points (A, B and C).
-The refractive indexes of the PSiMCGRIN were considered from the experimental and theoretical values that were obtained for the porosity ($ P = 0.3J^{0.24}$).
-And we could obtain the attack time with the relation of $ V = 0.53J ^ {0.79} $ where $ t = d / V $.}}
+  \caption{ \emph{We have different points denoted as follows, $ A
+      (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $,
+      from the sample of a Porous Silicon Microcavity GRIN
+      (PSiMCGRIN) $ GMC $. Alternate layers of high refractive index
+      (H) and low refractive index (L) are obtained at each of the
+      measurement points (A, B and C). The refractive indexes of the
+      PSiMCGRIN were considered from the experimental and theoretical
+      values that were obtained for the porosity ($ P =
+      0.3J^{0.24}$). And we could obtain the attack time with the
+      relation of $ V = 0.53J ^ {0.79} $ where $ t = d / V $.}}
 	\label{tabla:1}
 \end{table}
-In Fig.
-\ref{fig:MCGRIN3} a) Three locations at different points are considered, denoted as follows, $ A (0.3 \ \ cm) $ , $ B (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the PSiMCGRIN sample $ GMC $.
-Likewise, Fig.
-\ref{fig:DR3} b), we have the reflectance measurements to know the optical properties with the proposed simulation.
-We can see how from an experimental setup we have some important results as a result of a whole calibration curve suitable for making GRIN porous silicon.
-The refractive index of the Porous Silicon Microcavities GRIN were considered the experimental and theoretical values obtained for the porosity and the thicknesses shown in Table 1.
-The porous silicon microcavities (MCSP) with refractive index with gradient (GRIN), were manufactured with different current densities ranging from $ 6 \ \ mA / cm ^ 2 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a current of $ 5 \ \ mA $, for a $t_{_{H}}=35 s $, with a high refractive index $n_{_{H}} \sim$ $ 2,661$ to $ 2,808$ and porosities of $P_{_{H}} \sim$ $ 0.45 $ to $ 0.39 $.
-Also for $ 44 \ \ mA /cm^2 $ to $ 24 \ \ mA / cm^2 $, current of $ 38 \ \ mA $, using $t_{_{H}}=11 s$  for low refractive index $n_{_{L}}\sim$ $ 1,448 $ to $ 2,267 $ and with porosities of  $P_{_{H}} \sim$ $0.75 $ to $ 0.64 $.
-The porosity was calculated with the calibration curve exposed in the ($ P = 0.3J^{0.24} $).
-And the attack time could be obtained with the relation of $ V = 0.53J^{0.79} $ where $ t = d / V $ and the refractive index using the Bruggeman formula.
-For theoretical values, we use complex refractive indices as free parameters to fit the experimental refractive spectra (Section 4.2).
+In Fig. \ref{fig:MCGRIN3} a) Three locations at different points are
+considered, denoted as follows, $ A (0.3 \ \ cm) $ , $ B (0.8 \ \ cm)
+$ and $ C (1.2 \ \ cm) $, from the PSiMCGRIN sample $ GMC $. Likewise,
+Fig. \ref{fig:DR3} b), we have the reflectance measurements to know
+the optical properties with the proposed simulation. We can see how
+from an experimental setup we have some important results as a result
+of a whole calibration curve suitable for making GRIN porous
+silicon. The refractive index of the Porous Silicon Microcavities GRIN
+were considered the experimental and theoretical values obtained for
+the porosity and the thicknesses shown in Table 1. The porous silicon
+microcavities (MCSP) with refractive index with gradient (GRIN), were
+manufactured with different current densities ranging from $ 6 \ \ mA
+/ cm ^ 2 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a current of $ 5 \ \ mA $,
+for a $t_{_{H}}=35 s $, with a high refractive index $n_{_{H}} \sim$ $
+2,661$ to $ 2,808$ and porosities of $P_{_{H}} \sim$ $ 0.45 $ to $
+0.39 $. Also for $ 44 \ \ mA /cm^2 $ to $ 24 \ \ mA / cm^2 $, current
+of $ 38 \ \ mA $, using $t_{_{H}}=11 s$  for low refractive index
+$n_{_{L}}\sim$ $ 1,448 $ to $ 2,267 $ and with porosities of
+$P_{_{H}} \sim$ $0.75 $ to $ 0.64 $. The porosity was calculated with
+the calibration curve exposed in the ($ P = 0.3J^{0.24} $). And the
+attack time could be obtained with the relation of $ V = 0.53J^{0.79}
+$ where $ t = d / V $ and the refractive index using the Bruggeman
+formula. For theoretical values, we use complex refractive indices as
+free parameters to fit the experimental refractive spectra (Section
+4.2).
  \begin{figure}[H]
    \centering
-	\includegraphics[scale=.5]{../Images/MCGRINSEM}
-	\caption{\emph{SEM image of the cross section profile of the microcavities with GRIN.
-The measured thicknesses of the complete multi-film structures showed good agreement with the simulations taken from $ V = 0.53J ^ {0.79} $ where $d_j=Vt_j$ ($j=H,L$), which are the thicknesses of each of the monolayer of the porous silicon microcavity GRIN at the measurement points and the total thickness we find it as $d_{_{i}} = (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$ defining $ i = $ A, B, C.
-Which resulted in (measured / simulation) $ 2.25 / 2.31 \ \ \mu m $ (for structure at Point A), $ 2.17 / 2.08 \ \ \mu m $ (for structure at point B) and $ 1.87 / 1.65 \ \ \mu m $ (for structure at point C)}}
+   \includegraphics[scale=.5]{Images/MCGRINSEM}
+   \caption{\emph{SEM image of the cross section profile of the
+       microcavities with GRIN. The measured thicknesses of the
+       complete multi-film structures showed good agreement with the
+       simulations taken from $ V = 0.53J ^ {0.79} $ where $d_j=Vt_j$
+       ($j=H,L$), which are the thicknesses of each of the monolayer
+       of the porous silicon microcavity GRIN at the measurement
+       points and the total thickness we find it as $d_{_{i}} =
+       (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$
+       defining $ i = $ A, B, C. Which resulted in (measured /
+       simulation) $ 2.25 / 2.31 \ \ \mu m $ (for structure at Point
+       A), $ 2.17 / 2.08 \ \ \mu m $ (for structure at point B) and $
+       1.87 / 1.65 \ \ \mu m $ (for structure at point C)}}
 	\label{fig:MCGRIN4}
@@
 
-For the Fig.
-\ref{fig:MCGRIN4} shows the SEM cross-sectional images of the PSi samples used in this work.
-Relatively small interface roughness and a clear contrast between the high and low porosity of the microcavity measured at different points (A, B and C), showing the change in thickness in each of these.
-The measured thicknesses of the complete multi-film structures showed good agreement with the simulations taken from $ V = 0.53J^{0.79} $ where $d_j=Vt_j$ ($j=H,L$), which are the thicknesses of each of the monolayer of the porous silicon microcavity GRIN at the measurement points and the total thickness we find it as $d_{_{i}} = (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$ defining $ i = $ A, B, C.
-Which resulted in (measured / simulation) $ 2.25 / 2.31 \ \ \mu m $ (for structure at Point A), $ 2.17 / 2.08 \ \ \mu m $ (for structure at point B) and $ 1.87 / 1.65 \ \ \mu m $ (for structure at point C).
-Being able to say that for each measurement point corresponds different calculated current densities, which correspond to different thicknesses at the end of manufacturing, clearly seeing the lateral gradient product of our experiment.
+For the Fig. \ref{fig:MCGRIN4} shows the SEM cross-sectional images of
+the PSi samples used in this work. Relatively small interface
+roughness and a clear contrast between the high and low porosity of
+the microcavity measured at different points (A, B and C), showing the
+change in thickness in each of these. The measured thicknesses of the
+complete multi-film structures showed good agreement with the
+simulations taken from $ V = 0.53J^{0.79} $ where $d_j=Vt_j$
+($j=H,L$), which are the thicknesses of each of the monolayer of the
+porous silicon microcavity GRIN at the measurement points and the
+total thickness we find it as $d_{_{i}} =
+(N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$ defining $ i
+= $ A, B, C. Which resulted in (measured / simulation) $ 2.25 / 2.31 \
+\ \mu m $ (for structure at Point A), $ 2.17 / 2.08 \ \ \mu m $ (for
+structure at point B) and $ 1.87 / 1.65 \ \ \mu m $ (for structure at
+point C).
+Being able to say that for each measurement point corresponds
+different calculated current densities, which correspond to different
+thicknesses at the end of manufacturing, clearly seeing the lateral
+gradient product of our experiment.
 
-\newpage
 \section{conclusion}
-The necessary expressions for the potential components were derived, finding a relationship of the tip of the counter electrode that acts similarly as a point charge and the current density for a geometry in a rectangular electrolytic box and we solve the electrostatic equations with suitable boundary conditions.
-Resulting in an electrostatic model for  Photonics crystals with a refractive index with gradient (EMPCGRIN).
-It is the first time that the formalism mentioned here has been applied to find the current density to design porous silicon.
-The shape of the electrode, the area of the cell produces a visible decrease in the size and density of the pores.
-Additionally, optimizing the structural properties for a single structure we could have a gradient with different depths, reflactances at differents measurement points.
-In this way, we were able to simulate the direct relationship of the attack speed with the current density at the points  the samples of interest.
-At the same time, we developed a characterization between porosity, refractive indices of porous silicon, with the different current densities.
-And in the end we were able to design and characterize Porous Silicon microcavities with refractive indices with gradients, which for each measurement point correspond to different calculated current densities, which correspond to different thicknesses, clearly seeing the lateral gradient product of our experiment.
+The necessary expressions for the potential components were derived,
+finding a relationship of the tip of the counter electrode that acts
+similarly as a point charge and the current density for a geometry in
+a rectangular electrolytic box and we solve the electrostatic
+equations with suitable boundary conditions. Resulting in an
+electrostatic model for  Photonics crystals with a refractive index
+with gradient (EMPCGRIN).
+It is the first time that the formalism mentioned here has been
+applied to find the current density to design porous silicon. The
+shape of the electrode, the area of the cell produces a visible
+decrease in the size and density of the pores. Additionally,
+optimizing the structural properties for a single structure we could
+have a gradient with different depths, reflactances at differents
+measurement points. In this way, we were able to simulate the direct
+relationship of the attack speed with the current density at the
+points  the samples of interest. At the same time, we developed a
+characterization between porosity, refractive indices of porous
+silicon, with the different current densities. And in the end we were
+able to design and characterize Porous Silicon microcavities with
+refractive indices with gradients, which for each measurement point
+correspond to different calculated current densities, which correspond
+to different thicknesses, clearly seeing the lateral gradient product
+of our experiment.
 \section{Acknowledgments}
@@
 \bibliographystyle{unsrt}
- \small{
 \begin{thebibliography}{X}
-	%forma de biblio es MLA
-\bibitem{I1} P. Yeh,\textquotedblleft \emph{Optical Waves in Layered Media} \textquotedblright, 2nd edn. (Wiley-Interscience Publication,
+  % forma de biblio es MLA
+\bibitem{I1} P. Yeh,\textquotedblleft \emph{Optical Waves in Layered
+    Media} \textquotedblright, 2nd edn. (Wiley-Interscience
+  Publication,
   USA, 2005).
-\bibitem{I2}Canham, L. 1997.\textquotedblleft \emph{Properties of Porous Silicon} \textquotedblright. Edited by Canham L. DERA, Malvern, UK.
-\bibitem{I3}{Beale, M.I.J, J.D Benjamin, M.J Uren, N.G Chew, and A.G Cullis.
-1985.
-\emph{ \textquotedblleft An Experimental and Theoretical Study of the Formation and Microstructure of Porous Silicon.\textquotedblright} J.
-Crystal Growth 73: 622?36.
-doi:10.1021/jp0706984.
-}
-\bibitem{I4}Canham, L.
-T.
-1990.
-\emph{\textquotedblleft Silicon Quantum Wire Array Fabrication by Electrochemical and Chemical Dissolution of Wafers.\textquotedblright} Applied Physics Letters 57 (10): 1046.
-doi:10.1063/1.103561.
+\bibitem{I2}Canham, L. 1997.\textquotedblleft \emph{Properties of
+    Porous Silicon} \textquotedblright. Edited by Canham L. DERA,
+  Malvern, UK.
+\bibitem{I3}{Beale, M.I.J, J.D Benjamin, M.J Uren, N.G Chew, and A.G
+    Cullis. 1985. \emph{ \textquotedblleft An Experimental and
+      Theoretical Study of the Formation and Microstructure of
+      Porous Silicon.\textquotedblright} J. Crystal Growth 73:
+    622?36. doi:10.1021/jp0706984. }
+\bibitem{I4}Canham, L. T. 1990. \emph{\textquotedblleft Silicon
+    Quantum Wire Array Fabrication by Electrochemical and Chemical
+    Dissolution of Wafers.\textquotedblright} Applied Physics
+  Letters 57 (10): 1046. doi:10.1063/1.103561.
+\bibitem{I5} J. D. Joannopoulos et al.,\textquotedblleft
+  \emph{Photonic Crystals: Molding the Flow of
+    Light}\textquotedblright, 2nd edn.
+  (Princeton University Press, UK, 2008).
+\bibitem{I6} E. Yablonovitch, \textquotedblleft \emph{Photonic
+    band-gap structures,}\textquotedblright J. Opt. Soc. Am. B 10,
+  283-295 (1993)
+\bibitem{I7} Ilyas, S., and M. Gal.  \textquotedblleft \emph{
+    Optical devices from porous silicon having continuously varying
+    refractive index.}\textquotedblright Journal of Materials
+  Science: Materials in Electronics 18.1 (2007): 61-64.
+\bibitem{I8} Tran, P. \textquotedblleft \emph{Optical switching with
+    a nonlinear photonic crystal: a numerical
+    study.}\textquotedblright Optics letters 21.15 (1996):
+  1138-1140.
+\bibitem{I9} Ariza-Flores, A. David, L. M. Gaggero-Sager, and
+  V. Agarwal. \textquotedblleft \emph{White metal-like
+    omnidirectional mirror from porous silicon dielectric
+    multilayers.}\textquotedblright Applied Physics Letters 101.3
+  (2012): 031119.
+\bibitem{I10} Johnson, Steven G., et al.  \textquotedblleft
+  \emph{Linear waveguides in photonic-crystal
+    slabs.}\textquotedblright Physical Review B 62.12 (2000): 8212.
 
-\bibitem{I5} J. D. Joannopoulos et al.,\textquotedblleft \emph{Photonic Crystals: Molding the Flow of Light}\textquotedblright, 2nd edn.
-(Princeton University Press, UK, 2008).
-\bibitem{I6} E. Yablonovitch, \textquotedblleft \emph{Photonic band-gap structures,}\textquotedblright J. Opt. Soc. Am. B 10, 283-295 (1993)
-\bibitem{I7} Ilyas, S., and M.
-Gal.
-\textquotedblleft \emph{ Optical devices from porous silicon having continuously varying refractive index.}\textquotedblright Journal of Materials Science: Materials in Electronics 18.1 (2007): 61-64.
-\bibitem{I8} Tran, P. \textquotedblleft \emph{Optical switching with a nonlinear photonic crystal: a numerical study.}\textquotedblright Optics letters 21.15 (1996): 1138-1140.
- \bibitem{I9} Ariza-Flores, A.
-David, L.
-M.
-Gaggero-Sager, and V.
-Agarwal.
-\textquotedblleft \emph{White metal-like omnidirectional mirror from porous silicon dielectric multilayers.}\textquotedblright Applied Physics Letters 101.3 (2012): 031119.
-\bibitem{I10} Johnson, Steven G., et al.  \textquotedblleft \emph{Linear waveguides in photonic-crystal slabs.}\textquotedblright Physical Review B 62.12 (2000): 8212.
+  % asimetrica
+\bibitem{I101}Collins, Boyce E., et al. \textquotedblleft \emph{
+    Determining protein size using an electrochemically machined
+    pore gradient in silicon.}\textquotedblright Advanced Functional
+  Materials 12.3 (2002): 187-191.
 
-%asimetrica
-\bibitem{I101}Collins, Boyce E., et al.
-\textquotedblleft \emph{ Determining protein size using an electrochemically machined pore gradient in silicon.}\textquotedblright Advanced Functional Materials 12.3 (2002): 187-191.
+\bibitem{I102} Khung, Y. L., G. Barritt, and
+  N. H. Voelcker. \textquotedblleft \emph{Using continuous porous
+    silicon gradients to study the influence of surface topography
+    on the behaviour of neuroblastoma cells.}\textquotedblright
+  Experimental cell research 314.4 (2008): 789-800.
 
-\bibitem{I102} Khung, Y.
-L., G.
-Barritt, and N.
-H.
-Voelcker.
-\textquotedblleft \emph{Using continuous porous silicon gradients to study the influence of surface topography on the behaviour of neuroblastoma cells.}\textquotedblright Experimental cell research 314.4 (2008): 789-800.
+\bibitem{I103} Clements, Lauren R., et al. \textquotedblleft
+  \emph{Mesenchymal stem cell attachment to peptide density
+    gradients on porous silicon generated by
+    electrografting.}\textquotedblright physica status solidi (a)
+  208.6 (2011): 1440-1445.
 
-\bibitem{I103} Clements, Lauren R., et al.
-\textquotedblleft \emph{Mesenchymal stem cell attachment to peptide density gradients on porous silicon generated by electrografting.}\textquotedblright physica status solidi (a) 208.6 (2011): 1440-1445.
+\bibitem{I104} Wang, Peng-Yuan, et al. \textquotedblleft
+  \emph{Screening the attachment and spreading of bone
+    marrow-derived and adipose-derived mesenchymal stem cells on
+    porous silicon gradients.}\textquotedblright Rsc Advances 2.33
+  (2012): 12857-12865.
+\bibitem{I11} Canham, L. \textquotedblleft \emph{Properties of
+    Porous Silicon.}\textquotedblright Edited by Canham L. DERA,
+  Malvern, UK. (1997).
+\bibitem{I12} Li, Yang Yang, Peter Kim, and Michael J
+  Sailor.\textquotedblleft \emph{Painting a Rainbow on Silicon A
+    Simple Method to Generate a Porous Silicon Band Filter
+    Gradient}\textquotedblright Physica Status Solidi (a) 1618 (8):
+  161618. doi:10.1002/pssa.200461200.(2005)
+\bibitem{I13} Khung, Y L, and N H
+  Voelcker. 2009.\textquotedblleft\emph{ Multidirectional Lateral
+    Gradient Films with Position-Dependent Photonic Signatures Made
+    from Porous Silicon.}\textquotedblright Optical Materials 32
+  (1): 23442. doi:10.1016/j.optmat.2009.07.015.
+\bibitem{I14}  Khung, Y L, G Barritt, and N H Voelcker.
+  \textquotedblleft \emph{Using Continuous Porous Silicon Gradients
+    to Study the Influence of Surface Topography on the Behaviour of
+    Neuroblastoma Cells.}\textquotedblright Experimental Cell
+  Research 314 (4): 78900. doi:10.1016/j.yexcr.2007.10.015.(2008.)
+\bibitem{I15} Collins, B.E., K.-P.S. Dancil, G. Abbi, and
+  M.J. Sailor. 2002.\textquotedblleft \emph{Determining Protein Size
+    Using an Electrochemically Machined Pore Gradient in
+    Silicon.}\textquotedblright Advanced Functional Materials 12 (3):
+  187. doi:10.1002/1616-3028(200203)12:3,187::AID-ADFM187,3.0.CO;2-E.(
+  2002.)
 
-\bibitem{I104} Wang, Peng-Yuan, et al.
-\textquotedblleft \emph{Screening the attachment and spreading of bone marrow-derived and adipose-derived mesenchymal stem cells on porous silicon gradients.}\textquotedblright Rsc Advances 2.33 (2012): 12857-12865.
-
- \bibitem{I11} Canham, L. \textquotedblleft \emph{Properties of Porous Silicon.}\textquotedblright Edited by Canham L. DERA, Malvern, UK. (1997).
- \bibitem{I12} Li, Yang Yang, Peter Kim, and Michael J Sailor.\textquotedblleft \emph{Painting a Rainbow on Silicon A Simple Method to Generate a Porous Silicon Band Filter Gradient}\textquotedblright Physica Status Solidi (a) 1618 (8): 161618.
-doi:10.1002/pssa.200461200.(2005)
- \bibitem{I13} Khung, Y L, and N H Voelcker.
-2009.\textquotedblleft\emph{ Multidirectional Lateral Gradient Films with Position-Dependent Photonic Signatures Made from Porous Silicon.}\textquotedblright Optical Materials 32 (1): 23442.
-doi:10.1016/j.optmat.2009.07.015.
- \bibitem{I14}  Khung, Y L, G Barritt, and N H Voelcker.
-\textquotedblleft \emph{Using Continuous Porous Silicon Gradients to Study the Influence of Surface Topography on the Behaviour of Neuroblastoma Cells.}\textquotedblright Experimental Cell Research 314 (4): 78900.
-doi:10.1016/j.yexcr.2007.10.015.(2008.)
-\bibitem{I15} Collins, B.E., K.-P.S.
-Dancil, G.
-Abbi, and M.J.
-Sailor.
-2002.\textquotedblleft \emph{Determining Protein Size Using an Electrochemically Machined Pore Gradient in Silicon.}\textquotedblright Advanced Functional Materials 12 (3): 187.
-doi:10.1002/1616-3028(200203)12:3,187::AID-ADFM187,3.0.CO;2-E.( 2002.)
-
-\bibitem{I16} Ocier, C.
-R., Krueger, N.
-A., Zhou, W.
-and  Braun, P.
-V.
-(2017).\textquotedblleft \emph{Tunable visibly transparent optics derived from porous silicon.}\textquotedblright ACS Photonics, 4(4), 909-914.
-%ecuacion
-\bibitem{I17} Dariani RS, Ebrahimnasab S (2014). \textquotedblleft \emph{Root Mean Square Roughness of Nano Porous Silicon by Scattering Spectra.}\textquotedblright The
+\bibitem{I16} Ocier, C. R., Krueger, N. A., Zhou, W. and  Braun,
+  P. V. (2017).\textquotedblleft \emph{Tunable visibly transparent
+    optics derived from porous silicon.}\textquotedblright ACS
+  Photonics, 4(4), 909-914.
+\bibitem{I17} Dariani RS, Ebrahimnasab S (2014). \textquotedblleft
+  \emph{Root Mean Square Roughness of Nano Porous Silicon by
+    Scattering Spectra.}\textquotedblright The
   European Physical Journal Plus 129: 129.
-\bibitem{I18} Lerondel G, Romestain R (1997).\textquotedblleft \emph{Roughness of the Porous Silicon Dissolution Interface.}\textquotedblright Journal of Applied Physics 81:  61716178.
-\bibitem{I19} Lérondel G, Romestain R, Barret S (1997).\textquotedblleft \emph{Quantitative Analysis of the Light Scattering Effect on Porous Silicon
-Optical Measurements.}\textquotedblright Thin Solid Films 297: 114?117.
+\bibitem{I18} Lerondel G, Romestain R (1997).\textquotedblleft
+  \emph{Roughness of the Porous Silicon Dissolution
+    Interface.}\textquotedblright Journal of Applied Physics 81:
+  61716178.
+\bibitem{I19} Lérondel G, Romestain R, Barret S
+  (1997).\textquotedblleft \emph{Quantitative Analysis of the Light
+    Scattering Effect on Porous Silicon
+    Optical Measurements.}\textquotedblright Thin Solid Films 297:
+  114?117.
 
 \bibitem{I20} Thei, W. \textquotedblleft \emph{Optical Properties of porous silicon.}\textquotedblright Surf. Sci. Rep. 1997, 29, 91?93.
-\bibitem{I21} Van Groesen, E.; Sopaheluwakan, A.; Andonowati, A.
-\textquotedblleft  \emph{Direct characterization of states and modes in defect grating structures.}\textquotedblright J.
-Nonlinear Opt.
-Phys.
-Mater.
-2004, 13, 155173.
-% \textquotedblleft \textquotedblright
+\bibitem{I21} Van Groesen, E.; Sopaheluwakan, A.; Andonowati,
+  A. \textquotedblleft  \emph{Direct characterization of states and
+    modes in defect grating structures.}\textquotedblright
+  J. Nonlinear Opt. Phys. Mater. 2004, 13, 155173.
 
-\bibitem{In} Mazzoleni, C., and L.
-Pavesi.
-\textquotedblleft  \emph{Application to optical components of dielectric porous silicon multilayers.}\textquotedblright Applied Physics Letters 67.20 (1995): 2983-2985
+\bibitem{In} Mazzoleni, C., and L. Pavesi. \textquotedblleft
+  \emph{Application to optical components of dielectric porous silicon
+    multilayers.}\textquotedblright Applied Physics Letters 67.20
+  (1995): 2983-2985
 
 \end{thebibliography}
-%capitulos1111111111111111111111
 

### 2020-06-04 paper.tex
Added some comments.

@@
-\documentclass[12pt,letterpaper,onecolumn,twoside]{article}
-\usepackage[spanish]{babel}
-\usepackage[left=2cm,right=2cm,top=1.5cm,bottom=1.5cm]{geometry}
-\usepackage{fancyhdr}
-\pagestyle{fancy}
-\fancyhead{}\lhead{}\chead{}\rhead{}
-\renewcommand{\headrulewidth}{0pt}
-\usepackage[latin1]{inputenc}
+\documentclass{article}
 \usepackage{amsmath}
 \usepackage{graphicx} % gráficos
-\usepackage{subfigure} % subgráfico
-\usepackage{lscape}
-\usepackage{setspace}
-\usepackage{enumitem}
 \usepackage[noblocks]{authblk}
-\usepackage{float}
-\usepackage{cite}% para contraer referencias
-\usepackage[usenames]{color}
-\providecommand{\abs}[1]{\lvert#1\rvert}
-\providecommand{\norm}[1]{\lVert#1\rVert}
+%\usepackage{float}
+%\usepackage{cite}% para contraer referencias
+%\usepackage[usenames]{color}
+\newcommand{\abs}[1]{\lvert#1\rvert}
+\usepackage{xcolor}
+\newcommand{\notaL}[1]{{\color{blue}L:#1}}
 \title{\textbf{Optimization of Porous Silicon (PSi) with gradient refractive index (GRIN): A comparison with computational schemes with experimental results } }
@@
 \author[1]{C. A. Ospina de la Cruz}
-\author[2]{W. L. Mochan }
+\author[2]{W. L. Mochán }
 \author[3]{V. Agarwal }
 
-\affil[1]{{\scriptsize Posgrado en Ingenier\'ia y Ciencias Aplicadas del Centro de Investigación en Ingenier\'ia y Ciencias Aplicadas (CIICAp-IICBA), Universidad Autónoma del Estado de Morelos (UAEM), Cuernavaca CP 62209, México}}
-\affil[2]{{\scriptsize Instituto de Ciencias F\'isica ,Universidad Nacional Autonoma de Mexico, Av. Universidad S/N, Col. Chamilpa, 62210 Cuernavaca, Morelos, Mexico  } }
-\affil[3]{{\scriptsize Centro de Investigaci\'on en Ingenier\'ia y Ciencias Aplicadas,Universidad del Estado de Morelos, Av. Universidad 1001 Col. Chamilpa, Cuernavaca, Morelos 62209, Mexico  } }
-\affil[*]{{\scriptsize Corresponding author: xxxxxx@xxxx.xxx}}
-\date{}
-
+\affil[1]{Posgrado en Ingenier\'ia y Ciencias Aplicadas del Centro de
+  Investigación en Ingenier\'ia y Ciencias Aplicadas (CIICAp-IICBA),
+  Universidad Autónoma del Estado de Morelos (UAEM), Cuernavaca CP
+  62209, México}
+\affil[2]{Instituto de Ciencias F\'isica ,Universidad Nacional
+  Autonoma de Mexico, Av. Universidad S/N, Col. Chamilpa, 62210
+  Cuernavaca, Morelos, Mexico}
+\affil[3]{Centro de Investigaci\'on en Ingenier\'ia y Ciencias
+  Aplicadas,Universidad del Estado de Morelos, Av. Universidad 1001
+  Col. Chamilpa, Cuernavaca, Morelos 62209, Mexico  }
 \begin{document}
-\renewcommand{\contentsname}{Contents}
-\renewcommand{\abstractname}{Abstract}
-\renewcommand{\tablename}{Table}
-\vspace{50pt}
 
 \maketitle
+\notaL{Quité los intentos de tipografiar. Que de eso se encargue la
+  revista.}
+\notaL{Cambié la codificación a utf8; ya no uses latin1, es obsoleto.}
+\notaL{Quité las líneas kilométricas. No te ocupes de su longitud y no
+  juntes mis líneas.}
+\notaL{Quité paquetes no escenciales}
+\notaL{Cuida de no poner espacios al final de las líneas.}
+
 \begin{abstract}
@@
 \end{abstract}
-
-\vspace{-0.8cm}
-\singlespacing
-\tableofcontents
-
-%\newpage
-\spacing{1}
-
+\notaL{Cambié el abstract, pero habrá que revisarlo después.}
  \section{Introduction}
@@
 The structural behavior of nanostructured materials  has  become a
-great  topic  of global  interest,  where numerous  research has been
+topic  of global  interest,  where numerous  research has been
 done so far \cite{I1}. We found a great way to go for future
@@
 a thin insulated cable with tip, which  a point  current source.
-\begin{figure}[H]
+\begin{figure}
   \centering
@@
 change in the lower part of the conductive plane, as follows.
- \begin{figure}[H]
+ \begin{figure}
  \centering
@@
 If the surface of the liquid is at a finite height c, then we can use images, like:
-\begin{figure}[H]
+\begin{figure}
   \centering
@@
 \section{Experimental Details}
-\begin{figure}[H]
+\begin{figure}
   \centering
@@
  crystals with a refractive index with gradient (EMPCGRIN).
-\begin{figure}[H]
+\begin{figure}
   \centering
@@
 \subsection{Monolayers GRIN Porous Silicon }
-\begin{figure}[H]
+\begin{figure}
 	\centering
@@
 all the needs that this required.
-\begin{figure}[H]
+\begin{figure}
   \centering
@@
  can be controlled from the lateral current density.
-\begin{figure}[H]
+\begin{figure}
   \centering
@@
 seen in the SEM micrographs.
- \begin{figure}[H]
+ \begin{figure}
    \centering
@@
 ... 2.0 \ \ cm) $.
-\begin{figure}[H]
+\begin{figure}
   \centering
@@
 \subsection{GRIN Porous Silicon Microcavities}
- \begin{figure}[H]
+ \begin{figure}
 	\centering
@@
 below the tip counter-electrode.
-\begin{figure}[H]
+\begin{figure}
   \centering
@@
 4.2).
- \begin{figure}[H]
+ \begin{figure}
    \centering

### 2020-06-06 paper.tex
Fix a few latex mistakes

@@
   \end{figure}
-\end{document}
+
 In the Fig. \ref{fig:DE1} a shows schematic representation of the
@@
 	\centering
-	\includegraphics[scale=.3]{../Images/celdan2}
+	\includegraphics[scale=.3]{Images/celdan2}
 	\caption{\emph{ Mechanical 3D modeling, design of the
@@
 
-\begin{table}[H]
+\begin{table}
   \centering

### 2020-06-08 paper.tex
Modify theory. Incorporate new figures.

@@
 %\usepackage[usenames]{color}
+\usepackage{bm}
 \newcommand{\abs}[1]{\lvert#1\rvert}
 \usepackage{xcolor}
-\newcommand{\notaL}[1]{{\color{blue}L:#1}}
-\title{\textbf{Optimization of Porous Silicon (PSi) with gradient refractive index (GRIN): A comparison with computational schemes with experimental results } }
-
+\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
+\title{\textbf{Optimization of Porous Silicon Gradient Refractive
+    Index Structures.} }
+% A comparison with computational schemes with experimental results
 \author[1]{C. A. Ospina de la Cruz}
@@
 
-The structural behavior of nanostructured materials  has  become a
-topic  of global  interest,  where numerous  research has been
-done so far \cite{I1}. We found a great way to go for future
+\notaL{No entiendo nada de la introducción}
+The structural properties of nanostructured materials  has  received a
+considerable attention,  and a large research effort has been devoted
+to them \cite{I1}. We found a great way to go for future
 technological  explorations,  countless  challenges and  that  open a
 range of possibilities to develop further  study  on these
-issues\cite{I2}. Porous silicon (PSi) is a versatile nanostructured
+issues\cite{I2}. Porous silicon (PS) is a versatile nanostructured
 material and an excellent candidate as a technological platform for
@@
 mirrors\cite{I9}, waveguides for PC \cite{I10} etc. In the
-conventional manufacturing of PSi the desired result  is to obtain
+conventional manufacturing of PS the desired result  is to obtain
 homogeneous samples (same structural characteristics) from the
@@
 ALD offers the  opportunity to manufacture  a high index of refraction
-of contrast, visibly transparent GRIN optical elements from PSi
+of contrast, visibly transparent GRIN optical elements from PS
 absorbent structures \cite{I16}. A Despite previous research on the
@@
 \section{Theory}
-\subsection{Electrostatic Model for Photonic Crystals with Gradient
-  Refraction Index (EMPCGRIN)}
-
-The calculate  current density in a GRIN structure produced by an
-electrochemical attack on Si to produce Porous Si with a
-position-dependent porosity due to the distance to the counter
-electrode. A simplifies  calculation  with geometry,
-assumimg  in the form of a whole prism on the sides a, b, c with a, b
-horizontal and c vertical. Here c considered as the height of the
-liquid, and the walls are insulating, but the bottom is completely
-covered with the sample, which act as good conductor. The electrode is
-a thin insulated cable with tip, which  a point  current source.
+\subsection{Calculation of the current density}
+\notaL{check where acronyms are first defined}
+A gradient in the optical properties of porous Silicon (PS) systems may be
+obtained by electrochemically attacking a Si surface with a position dependent current
+density ${\bm j(\bm r)}$, as the porosity and refractive index depend on
+the current density, as well as the speed of attack and the width of the
+porous layer. Nevertheless, it is not a simple to task to measure the
+{\em local} value of $\bm j(\bm r)$ along the surface. This hampers the
+design and optimization of well characterized reproducible GRIN PS
+structures. Thus, a system for which the current density field may be
+easily computed would be useful.
+Though $\bm j(\bm r)$ may be in principle be numerically calculated for a
+given arbitrary experimental setup,  here we propose a particularly
+simple setup that allows an expression for the current in terms
+of a series that is rapidly convergent and each of whose terms is a
+simple analytic function. With this setup it is easy to characterize
+the dependence of different properties of interest on the current, and
+this allows the design and optimization of diverse GRIN PS devices.
+
+We assume that our electrolytic cell has the shape of a
+prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
+filled with the electrolyte up to a height $c$. We assume that the
+walls of the cell are insulating while the bottom is completely
+covered with the sample, which is a good conductor which is
+electrically grounded. Within the electrolyte we position an electrode
+which we assume is a thin conductor, insulated from the electrolyte
+but for a small area near its tip, which we thus approximate as a
+point current source.
 \begin{figure}
@@
   \includegraphics[scale=.4]{Images/celdan}
-  \caption{\emph{Diagram of the Electrolytic cell where we can see the shape of a prism on the sides a, b, c with a, b horizontal and c vertical.
-I'll take as the height of the liquid.
-The walls are insulating, but the bottom is completely covered by the sample, I suppose it is a good conductor.
-The tip of the electrode is a thin insulated wire located at $ \vec{r}_0 $.}}
-\end{figure}
-The current in the electrolyte is $ \vec {J} = \sigma \vec{E} $ with $
-\sigma $ is the conductivity. This for the stationary case $
-\bigtriangledown \cdot \vec{j} = 0 $. The electric field is derived
-from the electric potential, $\vec {E} = - \bigtriangledown \varphi
-$.
-And we can say that $ \bigtriangledown^{2} \varphi = 0 $, since the
-sample is a relatively good conductor, when connected to earth $
-\varphi(x, y, 0) = 0 $. Integrating $ \vec{J} $ over a small sphere
-superimposing the electrode gives $ \int ds \cdot \vec{J} = I $.
-The current density that carries the current to the tip. So
-\begin{equation}
-  \int ds \cdot \vec{E} = \dfrac{I}{\sigma}
-\end{equation}
-The problem to be solved is thus, to obtain the potential produced by a point charge,
-\begin{equation}
-  q_{_{0}} = \dfrac{I}{4 \pi \sigma}
-\end{equation}
-In the positions$\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ is the
-tip of the electrode that is in the presence of a ground conductor
-plane grounded $ z = 0 $ and enclosed on the insulating walls at $ (0,
-y, z) $, $ (a, y, z) $, $ (x, 0, z) $ , $ (x, b, z) $. The surface of
-the liquid is also not conductive to $ (x, y, c) $, the normal current
-is $\vec{j} \cdot \hat{n}=0$ and the normal of the field is $ \vec{E}
-\cdot \hat{n}=0  $. i.e
-\begin{equation}
-E_{_{x}}(0, y ,z)= E_{_{x}}(a, y ,z)=E_{{_y}}(x, 0 ,z)=E_{{_y}}(x, b ,z)=E_{{_z}}(x, y ,c)=0
-\end{equation}
+  \caption{Prism shaped electrolytic cell with a rectangular base of
+    sides $a$, $b$ filled with electrolyte up to a height $c$. The
+    walls of the cell are insulating and the bottom is completely
+    covered by the sample, which is assumed to be a good
+    conductor. The tip of the electrode is a thin insulated wire with
+    just the tip uncovered and located at $ \vec{r}_0 $ within the
+    liquid.\notaL{Quité el tipo de letra del pie de figura. Que la pongan en la
+      revista.}\notaL{En la punta pusiste dos esferas. Quítalas y sólo
+    pon un puntito dorado del ancho del cable. Muestra que la base
+    está aterrizada}\notaL{Indica el voltaje y la
+    corriente}\notaL{¿Está bien la polaridad de la batería?}}
+  \label{f:celda}
+\end{figure}
+Within the electrolyte the current density is
+\begin{equation}
+  \label{eq:j}
+  \bm j=\sigma\bm E,
+\end{equation}
+with
+$\sigma$ the conductivity, $\bm E=-\nabla\varphi$ the electric field,
+and $\varphi$ the electric potential. For a
+stationary situation\notaL{Latex usa nabla como el nombre de
+  $\nabla$}
+$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
+\begin{equation}
+  \label{eq:laplace}
+\nabla^{2} \varphi=0.
+\end{equation}
+Consider now an arbitrary closed surface
+$\mathcal S$
+within the electrolyte that surrounds completely the tip of the
+electrode. Integrating $ \bm j$ over this surface we obtain
+\begin{equation}
+  \label{eq:I}
+\int_{\mathcal S'} d\bm a \cdot \bm j = I,
+\end{equation}
+where the prime on $\mathcal S'$ means we remove from the surface a
+very small hole through which the wire that feeds the current gets
+through. Assuming the wire is narrower than any other relevant
+distance in the system, we may interpret Eq. \eqref{eq:I} as an
+integral over a closed surface of the current \eqref{eq:j} within the
+electrolyte, ignoring the actual current within the wire. Thus
+\begin{equation}
+  \label{eq:gauss}
+  \int_{\mathcal S} d\bm a \cdot \bm E = \frac{I}{\sigma}
+\end{equation}
+Using Gauss's law, we interpret this equation as a source for the
+potential in the form of a point charge
+\begin{equation}
+  q_{_{0}} = \frac{I}{4 \pi \sigma}
+\end{equation}
+at the position $\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ of the
+tip of the electrode. Note that $q_0$ would be the total charge,
+and it shouldn't be further screened through the permittivity of the
+electrolyte.
+
+The effective conductivity of the relatively thin sample in contact
+with the grounded counterelectrode is large enough that we may assume its
+surface $z=0$ is an equipotential.
+On the other hand, no current can go across the insulating walls of
+the cell, situated at $x=0$, $x=a$,, $y=0$ and $y=b$, nor through the
+free surface of the liquid at $z=c$. Thus, the problem to solve is Poisson
+equation with a point charge source
+\begin{equation}
+  \label{eq:poisson}
+  \nabla^2\varphi=-4\pi q_0\delta(\bm r-\bm r_0),
+\end{equation}
+with mixed boundary conditions
+\begin{equation}
+  \label{eq:ground}
+  \varphi(x,y,0)=0,
+\end{equation}
+and
+\begin{equation}
+E_{_{x}}(0, y ,z)= E_{_{x}}(a, y ,z)=E_{{_y}}(x, 0 ,z)=E_{{_y}}(x, b
+,z)=E_{{_z}}(x, y ,c)=0.
+\end{equation}
+This problem may be solved readily using image charge theory
+\notaL{ref}. The potential within the electrolytic cell coincides the
+the field within an infinite vacuum containing the point charge
+$q_0$ at the tip of the electrode at $\bm r_0$, and an array of its fictitious image
+charges. The images include a reflection on the conducting bottom of the
+cell, of the opposite charge $-q_0$ and situated at $(x_0, y_0,-z_0)$,
+to guarantee that the bottom stays at potential zero.
+There are further images on the four walls of the cell, of the same charge $q_0$
+and situated at $(-x_0,Y_0,z_0)$, $(x_0,-y_0, z_0)$, $(2a-x_0, y_0,
+z_0)$ and $(x_0, 2b-y_0,z_0)$ to guarantee that no current goes across
+them. Similarly, there is an image of the same charge $q_0$ at
+$(x_0,y_0,2c-z_0)$ to guarantee that no current goes across the
+surface of the electrolyte. Furthermore, each image charge has to be
+further reflected by each of the aforementioned surfaces, yielding new
+images.
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{paper-1}
+  \caption{Top view of the electrolytic cell (light blue) showing the charge at the
+    tip of the electrode (red dot) and its images on the walls of the
+    rectangular cell, the images of its images and so on (blue dots). The walls are at $x=0,a$,
+    $y=0,b$. The relation of some charges and their images is
+    indicated by dashed arrows, with a bar to indicate the
+    corresponding reflecting wall. The system may be interpreted as a
+    periodic lattice with a rectangular unit cell of size $2a\times 2b$,
+    one of which is indicated  by wide dashed lines, and with a basis of four equal
+    charges at $(\pm x_0, \pm y_0, z_0)$.}
+  \label{fig:topview}
+\end{figure}
+In Fig. \ref{fig:topview} we illustrate the real charge and all of
+its images within the plane $z=z_0$. They form a periodic rectangular
+lattice with a unit cell of size $2a\times 2b$ and with a basis of
+four equal charges situated at the positions $\bm r_0$, $\bm
+r_1=(-x_0, y_0, z_0)$, $\bm r_2=(x_0, -y_0, z_0)$ and $\bm r_3=(-x_0,
+-y_0, z_0)$. In Fig. \ref{fig:sideview} we show a lateral view of the
+image charges.
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{paper-2}
+  \caption{Side view of the electrolytic cell (light blue)
+    showing the charge at the tip of the electrode (red dot), its
+    images within the plane $z=z_0$ (blue dots), and its images at the
+    surface of the sample and the top of the electrolyte (green
+    dots). We use solid dots to denote particles with the same charge
+    as that corresponding to the tip $q_0$, and open dots for those of
+    opposite charge. The system may be interpreted as a periodic
+    lattice with a rectangular unit cell of size $2a\times 4c$, one of
+    which is indicated by wide dashed lines, and with a basis of four
+    charges $q_0$ and another four charges $-q_0$.}
+  \label{fig:sideview}
+\end{figure}
+
 This has a mixture of Dirichlet-Neumann type boundary conditions. By
@@
 {\vec{G}}  \phi_{_{G}}(z) e^{i \vec {G} \cdot \vec {r}} $. So the
-Poisson equation $ \bigtriangledown^2 \phi = -4 \pi \displaystyle
+Poisson equation $ \nabla^2 \phi = -4 \pi \displaystyle
 \sum_{\vec{R}} \delta (\vec{r} - \vec{R} - \vec{r}_0) $.
@@
 out with a Perkin Elmer Lambda 950 UV-Vis-NIR spectrophotometer. To
-calculate the complex refractive index $ \tilde{n}_{_{PSi}} = n_{_
-  {PSi}} - ik_{_{PSi}} $ of a porous layer with homogeneous porosity
+calculate the complex refractive index $ \tilde{n}_{_{PS}} = n_{_
+  {PS}} - ik_{_{PS}} $ of a porous layer with homogeneous porosity
 and thickness with smooth interfaces to throughout the entire
@@
 where $ r_{_ {01}} $ y $ r_{_ {12}} $ are the Fresnel reflectance
-coefficients at the interfaces $aire/PSi$ y $PSi/c-Si$ which are
+coefficients at the interfaces $aire/PS$ y $PS/c-Si$ which are
 defined in terms of their complex refractive index ($\tilde{n}_{_ {1}}
@@
  \begin{eqnarray}\label{Eq:Brugg}
- p\dfrac{\varepsilon_{_{air}}-\varepsilon_{_{PSi}}}{\varepsilon_{_{air}}+\varepsilon_{_{PSi}}}+(1-p)\dfrac{\varepsilon_{_{Si}}-\varepsilon_{_{PSi}}}{\varepsilon_{_{Si}}+
-   \varepsilon_{_{PSi}}}
- \end{eqnarray}
- where $ p $ is the volume fraction of air within the PSi layer
+ p\dfrac{\varepsilon_{_{air}}-\varepsilon_{_{PS}}}{\varepsilon_{_{air}}+\varepsilon_{_{PS}}}+(1-p)\dfrac{\varepsilon_{_{Si}}-\varepsilon_{_{PS}}}{\varepsilon_{_{Si}}+
+   \varepsilon_{_{PS}}}
+ \end{eqnarray}
+ where $ p $ is the volume fraction of air within the PS layer
  (porosity); $\varepsilon_{_{air}}$ is the dielectric function of air;
  $\varepsilon_{_{Si}}$ is the dielectric function of c-Si, and
- $\varepsilon_{_{PSi}}$ represents the dielectric function of PSi. The
+ $\varepsilon_{_{PS}}$ represents the dielectric function of PS. The
  dielectric function is a complex number and is related to the complex
@@
  monolayers as in section 3.1, and taking the conventional data
- mentioned above. The porous silicon microcavities (PSiMC) with
+ mentioned above. The porous silicon microcavities (PSMC) with
  gradient refractive index (GRIN), were manufactured with different
@@
       by electrochemical attack on crystalline silicon to
-      produce porous silicon (PSi), with a current density
+      produce porous silicon (PS), with a current density
       profile $ J (mA / cm ^ 2 ) $ normalized with the electric
@@
  considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B (0.8 \ \
- cm) $ and $ C (1.7 \ \ cm) $, from the sample of PSi GRIN $ G1 (I = 5
+ cm) $ and $ C (1.7 \ \ cm) $, from the sample of PS GRIN $ G1 (I = 5
  mA) $. Also the Fig. \ref{fig:DR3}. b), we have the reflectance
@@
  porosity and the experimental physical thickness (nm) by means of the
- SEM. The formation of PSi GRIN in the thickness occurs due to the
+ SEM. The formation of PS GRIN in the thickness occurs due to the
  variation in the concentration of the voids available at the Si
@@
   \includegraphics[scale=.5]{Images/semD11}
-  \caption{\emph{Characterization of a monolayer of PSi GRIN G1
+  \caption{\emph{Characterization of a monolayer of PS GRIN G1
       with an initial current of $ 5 \ \ mA $, seeing the
@@
 relation of the porosity for each position with its determined current
-density. Therefore, if it is desired to manufacture a PSi monolayer of
+density. Therefore, if it is desired to manufacture a PS monolayer of
 a certain porosity with a certain end, it is enough to resort to the
@@
       considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B
-      (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the PSiMCGRIN
+      (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the PSMCGRIN
       sample $ GMC $. b) We have the reflectance measurements to
@@
       from the sample of a Porous Silicon Microcavity GRIN
-      (PSiMCGRIN) $ GMC $. Alternate layers of high refractive index
+      (PSMCGRIN) $ GMC $. Alternate layers of high refractive index
       (H) and low refractive index (L) are obtained at each of the
       measurement points (A, B and C). The refractive indexes of the
-      PSiMCGRIN were considered from the experimental and theoretical
+      PSMCGRIN were considered from the experimental and theoretical
       values that were obtained for the porosity ($ P =
@@
 considered, denoted as follows, $ A (0.3 \ \ cm) $ , $ B (0.8 \ \ cm)
-$ and $ C (1.2 \ \ cm) $, from the PSiMCGRIN sample $ GMC $. Likewise,
+$ and $ C (1.2 \ \ cm) $, from the PSMCGRIN sample $ GMC $. Likewise,
 Fig. \ref{fig:DR3} b), we have the reflectance measurements to know
@@
 For the Fig. \ref{fig:MCGRIN4} shows the SEM cross-sectional images of
-the PSi samples used in this work. Relatively small interface
+the PS samples used in this work. Relatively small interface
 roughness and a clear contrast between the high and low porosity of

### 2020-06-08 paper.tex
Reached the orthorhombic lattice

@@
 the cell, situated at $x=0$, $x=a$,, $y=0$ and $y=b$, nor through the
-free surface of the liquid at $z=c$. Thus, the problem to solve is Poisson
+free surface of the liquid at $z=c$. Thus, the problem to solve is Poisson's
 equation with a point charge source
@@
 \end{figure}
-
-This has a mixture of Dirichlet-Neumann type boundary conditions. By
-using the simplified prism geometry  can solve the problem using the
-theory of image loads. Each load has an image of the same sign and
-magnitude for each lateral insulating surface and the opposite sign
-change in the lower part of the conductive plane, as follows.
- \begin{figure}
- \centering
- \includegraphics[scale=.6]{Images/Cellgrin}
- \caption{\emph{a) Diagram of a rectangular electrolytic cell, with a
-     real charge in the corner of the cell with its charges ($ q $)
-     images of the same sign in $ Z_0 $ and another charge image ($ -q
-     $) with change of sign located below the conductor in position $
-     -Z_0 $. b) The upper face seen from above, a real load and its
-     image loads in $ Z_0 $. c) All this formed a systems of a real
-     load and its image loads produced by the cell walls and its other
-     images seen from above, forming a periodic space. }}
- \label{fig:T1}
-\end{figure}
-
-From Fig. \ref{fig:T1} we assume that if i put a real charge ($ q $)
-in at $\vec{r}_0= (x_0, y_0, z_0)$, in the corner of the electrolytic
-box it induces images at $\vec{r}_1= (-x_0, y_0, z_0)$ due to a
-reflection in $ (0, y, z) $, images in  $\vec{r}_2= (-x_0, -y_0, z_0)$
-due to a reflection in $ (x, 0, z) $ y the image of the image in
-$\vec{r}_3= (x_0, -y_0, z_0)$  for  $\vec{r}_j$, $(j=0,1,2,3)$. Then,
-these four charges are reflected on the other two surfaces and the
-eight new images are reflected on the original surface, etc.,
-producing a periodic 2D rectangular network with unit cells of signs $
-L_x = 2a $, $ L_y = 2b $ and with a base of 4 equal charges. This
-entire network is reflected from the bottom with an opposite sign load
-(below the driver). Periodic copies separated by the vacuum in the $
-xy $ plane whose area is being increased to achieve convergence.
+Each plane of charges upon reflection on the surface of the sample yields an
+plane of image charges of the opposite sign, while reflections
+on the surface of the liquid yields a plane of charges of the same
+sign. The side view may be interpreted as a periodic rectangular
+lattice with a unit cell of size $2a\times 4c$ containing a basis of eight point
+charges, four positive and four negative. A projection onto the $yz$
+plane would similarly yield a rectangular lattice with a  $2b\times4c$
+unit cell. Putting everything together, the problem is that of solving
+Poisson's equation within an orthothombic lattice of size
+$2a\times2b\times4c$ with a basis of 16 point charges arranged in
+positive and negative planes.
 

### 2020-06-09 CAOspinaCDGRIN02.tex
Hice los cambios y modificaciones de la celda, los estilo de letra de los pie de imagenas

--- 2020-06-06 paper.tex
@@
-\documentclass{article}
+\documentclass[12pt,letterpaper,onecolumn,twoside]{article}
+\usepackage[spanish]{babel} 
+\usepackage[left=2cm,right=2cm,top=1.5cm,bottom=1.5cm]{geometry}
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+\fancyhead{}\lhead{}\chead{}\rhead{}
+\renewcommand{\headrulewidth}{0pt}
+\usepackage[latin1]{inputenc}
 \usepackage{amsmath}
 \usepackage{graphicx} % gráficos
+\usepackage{subfigure} % subgráfico
+\usepackage{lscape}
+\usepackage{setspace}
+\usepackage{enumitem}
 \usepackage[noblocks]{authblk}
-%\usepackage{float}
-%\usepackage{cite}% para contraer referencias
-%\usepackage[usenames]{color}
-\newcommand{\abs}[1]{\lvert#1\rvert}
-\usepackage{xcolor}
-\newcommand{\notaL}[1]{{\color{blue}L:#1}}
+\usepackage{float}
+\usepackage{cite}% para contraer referencias
+\usepackage[usenames]{color}
+\providecommand{\abs}[1]{\lvert#1\rvert}
+\providecommand{\norm}[1]{\lVert#1\rVert}
  \title{\textbf{Optimization of Porous Silicon (PSi) with gradient refractive index (GRIN): A comparison with computational schemes with experimental results } }
@@
 \author[1]{C. A. Ospina de la Cruz}
-\author[2]{W. L. Mochán }
+\author[2]{W. L. Mochan }
 \author[3]{V. Agarwal }
 
-\affil[1]{Posgrado en Ingenier\'ia y Ciencias Aplicadas del Centro de
-  Investigación en Ingenier\'ia y Ciencias Aplicadas (CIICAp-IICBA),
-  Universidad Autónoma del Estado de Morelos (UAEM), Cuernavaca CP
-  62209, México}
-\affil[2]{Instituto de Ciencias F\'isica ,Universidad Nacional
-  Autonoma de Mexico, Av. Universidad S/N, Col. Chamilpa, 62210
-  Cuernavaca, Morelos, Mexico}
-\affil[3]{Centro de Investigaci\'on en Ingenier\'ia y Ciencias
-  Aplicadas,Universidad del Estado de Morelos, Av. Universidad 1001
-  Col. Chamilpa, Cuernavaca, Morelos 62209, Mexico  }
+\affil[1]{{\scriptsize Posgrado en Ingenier\'ia y Ciencias Aplicadas del Centro de Investigación en Ingenier\'ia y Ciencias Aplicadas (CIICAp-IICBA), Universidad Autónoma del Estado de Morelos (UAEM), Cuernavaca CP 62209, México}}
+\affil[2]{{\scriptsize Instituto de Ciencias F\'isica ,Universidad Nacional Autonoma de Mexico, Av. Universidad S/N, Col. Chamilpa, 62210 Cuernavaca, Morelos, Mexico  } }
+\affil[3]{{\scriptsize Centro de Investigaci\'on en Ingenier\'ia y Ciencias Aplicadas,Universidad del Estado de Morelos, Av. Universidad 1001 Col. Chamilpa, Cuernavaca, Morelos 62209, Mexico  } }
+\affil[*]{{\scriptsize Corresponding author: xxxxxx@xxxx.xxx}}
+\date{}
+
 \begin{document}
+\renewcommand{\contentsname}{Contents}
+\renewcommand{\abstractname}{Abstract}
+\renewcommand{\tablename}{Table}
+\vspace{50pt}
 
 \maketitle
-\notaL{Quité los intentos de tipografiar. Que de eso se encargue la
-  revista.}
-\notaL{Cambié la codificación a utf8; ya no uses latin1, es obsoleto.}
-\notaL{Quité las líneas kilométricas. No te ocupes de su longitud y no
-  juntes mis líneas.}
-\notaL{Quité paquetes no escenciales}
-\notaL{Cuida de no poner espacios al final de las líneas.}
+\begin{abstract}
+The current density in a of Porous Silicon (PSi) with gradient  refractive index (GRIN) produced  by an electrochemical  attack on silicon (Si)  to  produce  porous  silicon (PSi), the calculated  porosity  of the GRIN structure depends  on the  position  and  distance  from  counter  electrode.
+The proposed relationship shows, the  counter  electrode tip that acts  analogously  as a point charge  and  current density  for a geometry in an electrolytic  box by solving the electrostatic equations  with suitable  contour conditions.
+Resulting  in an electrostatic model for photonic  crystals  with gradient refractive index (EMPCGRIN).
+The characterization of the  silicon structures was performed  by scanning electron microscopy   and  UV-Vis-NIR reflectance spectroscopy.
+The obtained  results  open  the  possibility  of creating  silicon-based photonic  structures within  the  Visible-IR- range, within  the  sample at  different measuring distances,  where generally porous silicon does not strongly  absorb or disperse light.
+Similarly, in the UV-Visible range  there is a strong absorption with more of light scattering.
+Having a greater  area of attack generating  different pores sizes and their porosity, and making an easy calculation  in the manufacture of porous silicon.
+\\
 
-\begin{abstract}
-We propose a simple setup which allows the calculation of the current
-density as a function of position within an electrochemical cell used
-to produce porous Silicon structures with a controlled gradient in their
-index of refraction. We produced samples under several conditions and
-characterized them with scanning electron microscopy, and
-ultraviolet-visible-near infrared reflectance spectroscopy. Our
-results allow us to obtain from experiments on a single or just a few
-samples a full characterization of the dependence of porosity,
-dielectric function and speed of attack on the current density and on
-position, so that novel nonhomogeneous devices may be designed and
-built.
+Keywords: Porous Silicon (PSi); Monolayer(Ml); Porosity(P); Reflectance Spectra.
+\end{abstract}
 
-Keywords: Porous Silicon; GRIN; Reflectance Spectra.
-\end{abstract}
-\notaL{Cambié el abstract, pero habrá que revisarlo después.}
+\vspace{-0.8cm}
+\singlespacing 
+\tableofcontents
+
+%\newpage
+\spacing{1}
+
  \section{Introduction}
 
-The structural behavior of nanostructured materials  has  become a
-topic  of global  interest,  where numerous  research has been
-done so far \cite{I1}. We found a great way to go for future
-technological  explorations,  countless  challenges and  that  open a
-range of possibilities to develop further  study  on these
-issues\cite{I2}. Porous silicon (PSi) is a versatile nanostructured
-material and an excellent candidate as a technological platform for
-different sensing applications \cite{I3, I4}, due to its easy
-manufacturing,  large surface area, high surface reactivity,  and
-moreover, its optical transduction capacity.  Photonic crystals are
-multilayer dielectric structures that have periodicity in the
-dielectric function along one direction \cite{I5}. It has numerous
-studies for high reflectivity and the ability to adjust  the photonic
-prohibited  band (PBG)\cite{I6} , which leads to possible applications
-such as filters\cite{I7}, optical switches\cite{I8}, omnidirectional
-mirrors\cite{I9}, waveguides for PC \cite{I10} etc. In the
-conventional manufacturing of PSi the desired result  is to obtain
-homogeneous samples (same structural characteristics) from the
-periphery  to the center  of the electrochemically  attacked area.
-However, with an asymmetric anodizing configuration,  samples with a
-lateral gradient in terms of pore size and thickness of the porous
-layer are obtained \cite{I101}. In this configuration,  the face of
-the platinum  electrode (cathode)  is relatively maintained
-perpendicular  to the surface of the Si substrate (anode) at one end
-of the cell, so that the distribution of the current within the
-electrolyte  solution varies depending on the distance  of the
-electrode due to the resistance of the electrolyte,  resulting  in a
-decrease in current density as the distance from the electrode
-increases \cite{I102, I103}. The result is a porous surface with
-different pore sizes ranging from a few nanometers  to pores on the
-order of a few micrometers  \cite{I104}. The dimensions of the pores
-obtained on the same chip can be controlled by adjusting the anodizing
-current and electrolyte concentration \cite{I11}. Currently, these
-types of samples have found their application relevant as optical band
-filters \cite{I12}, devices with a multidirectional photonic band
-(photonic bar codes) \cite{I13} and mainly as biosensors. In this way,
-the effect of different topographies (porosities in the same sample)
-on the culture / adhesion of certain cells \cite{I14} is studied,
-considerably reducing the number of samples and cost of the study. In
-addition, they are also very useful when a biomolecule size-exclusion
-technique is required allowing the identification and separation of
-these biological compounds \cite{I15}. Recent studies  have shown that
-the  combination  of thermal  oxidation  and infiltration of TiO2   by
-ALD offers the  opportunity to manufacture  a high index of refraction
-of contrast, visibly transparent GRIN optical elements from PSi
-absorbent structures \cite{I16}. A Despite previous research on the
-formation of porous silicon with GRIN, type p in manufacturing and
-characterization, there was no control of current densities, much less
-a model that  explained said lateral  gradient. In this work, we
-reported a gradient refractive index (GRIN) structure by varying the
-current density on the fabrication of porous silicon photonic
-structure. This current density values, depth, and porosity of the
-photonic structure were calculated from an electrostatic model for
-photonic crystals with a gradient refractive index
-(EMPCGRIN). Moreover, the theoretical and experimental studies were
-exhibited similar results.
-
-The paper is organized as follows. In Section 2  we report the effect
-of how the current density can be calculated from an electrostatic
-model for photonic crystals with gradient refractive index (EMPCGRIN),
-demonstrating that there is a direct relation of the gradient
-generated by the electrode when it attacks the Silicon sample, we can
-see the depth of the structure and its porosity, in each of the
-measuring points. In Subsection 2.2 we present a formalism based on
-the methods used for the analysis of photonic crystal structures is
-the transfer matrix method. We use it to investigate the reflectance
-of light in a one-dimensional photonic crystal. In Section 3 we
-provide experimental  details about the manufacture of PS dielectric
-multilayers and Section 4 we shows the comparison of numerical and
-experimental results followed. Finally,  the conclusions given in
-Section. 5
+ The structural behavior of nanostructured materials  has  become a  great  topic  of global  interest,  where numerous  research has been done so far \cite{I1}.
+We found a great way to go for future technological  explorations,  countless  challenges and  that  open a range of possibilities to develop further  study  on these issues\cite{I2}.
+Porous silicon (PSi) is a versatile nanostructured material and an excellent candidate as a technological platform for different sensing applications \cite{I3, I4}, due to its easy manufacturing,  large surface area, high surface reactivity,  and moreover, its optical transduction capacity.
+Photonic crystals are multilayer dielectric structures that have periodicity in the dielectric function along one direction \cite{I5}.
+It has numerous studies for high reflectivity and the ability to adjust  the photonic  prohibited  band (PBG)\cite{I6} , which leads to possible applications  such as filters\cite{I7}, optical switches\cite{I8}, omnidirectional mirrors\cite{I9}, waveguides for PC \cite{I10} etc.
+In the conventional manufacturing of PSi the desired result  is to obtain  homogeneous samples (same structural characteristics) from the  periphery  to the center  of the electrochemically  attacked area.
+However, with an asymmetric anodizing configuration,  samples with a lateral gradient in terms of pore size and thickness of the porous layer are obtained \cite{I101}.
+In this configuration,  the face of the platinum  electrode (cathode)  is relatively maintained  perpendicular  to the surface of the Si substrate (anode) at one end of the cell, so that the distribution of the current within the electrolyte  solution varies depending on the distance  of the electrode due to the resistance of the electrolyte,  resulting  in a decrease in current density as the distance from the electrode increases \cite{I102, I103}.
+The result is a porous surface with different pore sizes ranging from a few nanometers  to pores on the order of a few micrometers  \cite{I104}.
+The dimensions of the pores obtained on the same chip can be controlled by adjusting the anodizing current and electrolyte concentration \cite{I11}.
+Currently, these types of samples have found their application relevant as optical band filters \cite{I12}, devices with a multidirectional photonic band (photonic bar codes) \cite{I13} and mainly as biosensors.
+In this way, the effect of different topographies (porosities in the same sample) on the culture / adhesion of certain cells \cite{I14} is studied, considerably reducing the number of samples and cost of the study.
+In addition, they are also very useful when a biomolecule size-exclusion technique is required allowing the identification and separation of these biological compounds \cite{I15}.
+Recent studies  have shown that  the  combination  of thermal  oxidation  and infiltration of TiO2   by ALD offers the  opportunity to manufacture  a high index of refraction  of contrast, visibly transparent GRIN optical elements from PSi absorbent structures \cite{I16}.
+A Despite previous research on the formation of porous silicon with GRIN, type p in manufacturing and characterization, there was no control of current densities, much less a model that  explained said lateral  gradient.
+In this work, we reported a gradient refractive index (GRIN) structure by varying the current density on the fabrication of porous silicon photonic structure.
+This current density values, depth, and porosity of the photonic structure were calculated from an electrostatic model for photonic crystals with a gradient refractive index (EMPCGRIN).
+Moreover, the theoretical and experimental studies were exhibited similar results.\\
+ The paper is organized as follows.
+In Section 2  we report the effect of how the current density can be calculated from an electrostatic model for photonic crystals with gradient refractive index (EMPCGRIN), demonstrating that there is a direct relation of the gradient generated by the electrode when it attacks the Silicon sample, we can see the depth of the structure and its porosity, in each of the measuring points.
+In Subsection 2.2 we present a formalism based on the methods used for the analysis of photonic crystal structures is the transfer matrix method.
+We use it to investigate the reflectance of light in a one-dimensional photonic crystal.
+In Section 3 we provide experimental  details about the manufacture of PS dielectric multilayers and Section 4 we shows the comparison of numerical and experimental results followed.
+Finally,  the conclusions given in Section.
+5
 
  \section{Theory}
-\subsection{Electrostatic Model for Photonic Crystals with Gradient
-  Refraction Index (EMPCGRIN)}
-
-The calculate  current density in a GRIN structure produced by an
-electrochemical attack on Si to produce Porous Si with a
-position-dependent porosity due to the distance to the counter
-electrode. A simplifies  calculation  with geometry,
-assumimg  in the form of a whole prism on the sides a, b, c with a, b
-horizontal and c vertical. Here c considered as the height of the
-liquid, and the walls are insulating, but the bottom is completely
-covered with the sample, which act as good conductor. The electrode is
-a thin insulated cable with tip, which  a point  current source.
-\begin{figure}
+ \subsection{Electrostatic Model for Photonic Crystals with Gradient Refraction Index (EMPCGRIN)}
+The calculate  current density in a GRIN structure produced by an electrochemical attack on Si to produce Porous Si with a position-dependent porosity due to the distance to the counter electrode.
+A simplifies  calculation  with geometry,
+assumimg  in the form of a whole prism on the sides a, b, c with a, b horizontal and c vertical.
+Here c considered as the height of the liquid, and the walls are insulating, but the bottom is completely covered with the sample, which act as good conductor.
+The electrode is a thin insulated cable with tip, which  a point  current source.
+\begin{figure}[H]
 	\centering
-  \includegraphics[scale=.4]{Images/celdan}
+	\includegraphics[scale=.4]{../Images/celdan} 
 	\caption{\emph{Diagram of the Electrolytic cell where we can see the shape of a prism on the sides a, b, c with a, b horizontal and c vertical.
@@
 \end{figure}
-The current in the electrolyte is $ \vec {J} = \sigma \vec{E} $ with $
-\sigma $ is the conductivity. This for the stationary case $
-\bigtriangledown \cdot \vec{j} = 0 $. The electric field is derived
-from the electric potential, $\vec {E} = - \bigtriangledown \varphi
-$.
-And we can say that $ \bigtriangledown^{2} \varphi = 0 $, since the
-sample is a relatively good conductor, when connected to earth $
-\varphi(x, y, 0) = 0 $. Integrating $ \vec{J} $ over a small sphere
-superimposing the electrode gives $ \int ds \cdot \vec{J} = I $.
+The current in the electrolyte is $ \vec {J} = \sigma \vec{E} $ with $ \sigma $ is the conductivity.
+This for the stationary case $ \bigtriangledown \cdot \vec{j} = 0 $.
+The electric field is derived from the electric potential, $\vec {E} = - \bigtriangledown \varphi $.
+And we can say that $ \bigtriangledown^{2} \varphi = 0 $, since the sample is a relatively good conductor, when connected to earth $ \varphi(x, y, 0) = 0 $.
+Integrating $ \vec{J} $ over a small sphere superimposing the electrode gives $ \int ds \cdot \vec{J} = I $.
 The current density that carries the current to the tip. So
@@
  \end{equation}
-In the positions$\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ is the
-tip of the electrode that is in the presence of a ground conductor
-plane grounded $ z = 0 $ and enclosed on the insulating walls at $ (0,
-y, z) $, $ (a, y, z) $, $ (x, 0, z) $ , $ (x, b, z) $. The surface of
-the liquid is also not conductive to $ (x, y, c) $, the normal current
-is $\vec{j} \cdot \hat{n}=0$ and the normal of the field is $ \vec{E}
-\cdot \hat{n}=0  $. i.e
+In the positions$\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ is the tip of the electrode that is in the presence of a ground conductor plane grounded $ z = 0 $ and enclosed on the insulating walls at $ (0, y, z) $, $ (a, y, z) $, $ (x, 0, z) $ , $ (x, b, z) $.
+The surface of the liquid is also not conductive to $ (x, y, c) $, the normal current is $\vec{j} \cdot \hat{n}=0$ and the normal of the field is $ \vec{E} \cdot \hat{n}=0  $.
+i.e
 \begin{equation}
@@
 \end{equation}
-This has a mixture of Dirichlet-Neumann type boundary conditions. By
-using the simplified prism geometry  can solve the problem using the
-theory of image loads. Each load has an image of the same sign and
-magnitude for each lateral insulating surface and the opposite sign
-change in the lower part of the conductive plane, as follows.
- \begin{figure}
+This has a mixture of Dirichlet-Neumann type boundary conditions.
+By using the simplified prism geometry  can solve the problem using the theory of image loads.
+Each load has an image of the same sign and magnitude for each lateral insulating surface and the opposite sign change in the lower part of the conductive plane, as follows.
+ \begin{figure}[H]
  \centering
- \includegraphics[scale=.6]{Images/Cellgrin}
- \caption{\emph{a) Diagram of a rectangular electrolytic cell, with a
-     real charge in the corner of the cell with its charges ($ q $)
-     images of the same sign in $ Z_0 $ and another charge image ($ -q
-     $) with change of sign located below the conductor in position $
-     -Z_0 $. b) The upper face seen from above, a real load and its
-     image loads in $ Z_0 $. c) All this formed a systems of a real
-     load and its image loads produced by the cell walls and its other
-     images seen from above, forming a periodic space. }}
+ \includegraphics[scale=.6]{../Images/Cellgrin}
+ \caption{\emph{a) Diagram of a rectangular electrolytic cell, with a real charge in the corner of the cell with its charges ($ q $) images of the same sign in $ Z_0 $ and another charge image ($ -q $) with change of sign located below the conductor in position $ -Z_0 $.
+b) The upper face seen from above, a real load and its image loads in $ Z_0 $.
+c) All this formed a systems of a real load and its image loads produced by the cell walls and its other images seen from above, forming a periodic space.
+}}
  \label{fig:T1}
@@
 
-From Fig. \ref{fig:T1} we assume that if i put a real charge ($ q $)
-in at $\vec{r}_0= (x_0, y_0, z_0)$, in the corner of the electrolytic
-box it induces images at $\vec{r}_1= (-x_0, y_0, z_0)$ due to a
-reflection in $ (0, y, z) $, images in  $\vec{r}_2= (-x_0, -y_0, z_0)$
-due to a reflection in $ (x, 0, z) $ y the image of the image in
-$\vec{r}_3= (x_0, -y_0, z_0)$  for  $\vec{r}_j$, $(j=0,1,2,3)$. Then,
-these four charges are reflected on the other two surfaces and the
-eight new images are reflected on the original surface, etc.,
-producing a periodic 2D rectangular network with unit cells of signs $
-L_x = 2a $, $ L_y = 2b $ and with a base of 4 equal charges. This
-entire network is reflected from the bottom with an opposite sign load
-(below the driver). Periodic copies separated by the vacuum in the $
-xy $ plane whose area is being increased to achieve convergence.
+From Fig.
+\ref{fig:T1} we assume that if i put a real charge ($ q $) in at $\vec{r}_0= (x_0, y_0, z_0)$, in the corner of the electrolytic box it induces images at $\vec{r}_1= (-x_0, y_0, z_0)$ due to a reflection in $ (0, y, z) $, images in  $\vec{r}_2= (-x_0, -y_0, z_0)$ due to a reflection in $ (x, 0, z) $ y the image of the image in $\vec{r}_3= (x_0, -y_0, z_0)$  for  $\vec{r}_j$, $(j=0,1,2,3)$.
+Then, these four charges are reflected on the other two surfaces and the eight new images are reflected on the original surface, etc., producing a periodic 2D rectangular network with unit cells of signs $ L_x = 2a $, $ L_y = 2b $ and with a base of 4 equal charges.
+This entire network is reflected from the bottom with an opposite sign load (below the driver).
+Periodic copies separated by the vacuum in the $ xy $ plane whose area is being increased to achieve convergence.
+\\
+\textbf {Problem considerations}: The problem is the potential, the field and the current produced by a periodic 2D network of a real load and all its images.
+The potential due to a periodic network is automatically found in the plane making a sum of 2D Fourier.
 
-\textbf {Problem considerations}: The problem is the potential, the
-field and the current produced by a periodic 2D network of a real load
-and all its images. The potential due to a periodic network is
-automatically found in the plane making a sum of 2D Fourier.
 \begin{eqnarray}
- \rho(\vec{r}) =q \displaystyle\sum_{R}  \ \delta
-  (\vec{r}-\vec{R}-\vec{r}_0) =\dfrac{q}{A}  \displaystyle\sum_{G}
-  e^{i G \cdot (\vec{r}-\vec{r}_{0})} \delta (z-z_0)
+ \rho(\vec{r}) =q \displaystyle\sum_{R}  \ \delta (\vec{r}-\vec{R}-\vec{r}_0) =\dfrac{q}{A}  \displaystyle\sum_{G}  e^{i G \cdot (\vec{r}-\vec{r}_{0})} \delta (z-z_0)
 \end{eqnarray}
-Where $ {R} $ is the 2D Bravais network and $ {G} $ its reciprocal
-network. It is written $ \phi (\vec{r}) = \displaystyle \sum _
-{\vec{G}}  \phi_{_{G}}(z) e^{i \vec {G} \cdot \vec {r}} $. So the
-Poisson equation $ \bigtriangledown^2 \phi = -4 \pi \displaystyle
-\sum_{\vec{R}} \delta (\vec{r} - \vec{R} - \vec{r}_0) $.
+Where $ {R} $ is the 2D Bravais network and $ {G} $ its reciprocal network.
+It is written $ \phi (\vec{r}) = \displaystyle \sum _ {\vec{G}}  \phi_{_{G}}(z) e^{i \vec {G} \cdot \vec {r}} $.
+So the Poisson equation $ \bigtriangledown^2 \phi = -4 \pi \displaystyle \sum_{\vec{R}} \delta (\vec{r} - \vec{R} - \vec{r}_0) $.
 Becomes
  \begin{eqnarray}
- \dfrac{\partial^2 \phi_{_{G}}(z)}{\partial z^2}+ G^2\phi_{_{G}}(z)=
-   -\dfrac{4 \pi}{A}  q   e^{i \vec{G} \cdot \vec{r}_{_0}} \delta
-   (z-z_0)
+ \dfrac{\partial^2 \phi_{_{G}}(z)}{\partial z^2}+ G^2\phi_{_{G}}(z)= -\dfrac{4 \pi}{A}  q   e^{i \vec{G} \cdot \vec{r}_{_0}} \delta (z-z_0)
  \end{eqnarray}
-Solving the homogeneous equation above and below $ z = z_0 $, using
-symmetry and conditions at $ \pm \infty $ we obtain $ \phi_{_{G}} =
-\phi_{_{G}}^{0} e^{ G \abs{z-z_0}} \ \ \ \ \ (G \neq 0) $. And
-adjusting the singularity
+Solving the homogeneous equation above and below $ z = z_0 $, using symmetry and conditions at $ \pm \infty $ we obtain $ \phi_{_{G}} = \phi_{_{G}}^{0} e^{ G \abs{z-z_0}} \ \ \ \ \ (G \neq 0) $.
+And adjusting the singularity
  \begin{eqnarray}
- \phi_{_{G}}(z)= \dfrac{2 \pi q}{AG}  e^{- G \abs{z-z_0}} e^{-i
-   \vec{G} \cdot \vec{r}_{_0}} \ \ \ \ \ (G\neq 0)
+ \phi_{_{G}}(z)= \dfrac{2 \pi q}{AG}  e^{- G \abs{z-z_0}} e^{-i \vec{G} \cdot \vec{r}_{_0}} \ \ \ \ \ (G\neq 0)
  \end{eqnarray}
-For the case $ G = 0 $ is similar $ \phi_{_{G = 0}} (z) = \dfrac{-2
-  \pi q}{A} \abs{z-z_0} + K, $ $ \ \ $ (K is a constant). Here $ A =
-L_x L_y $ is the unit cell area
+For the case $ G = 0 $ is similar $ \phi_{_{G = 0}} (z) = \dfrac{-2 \pi q}{A} \abs{z-z_0} + K, $ $ \ \ $ (K is a constant). Here $ A = L_x L_y $ is the unit cell area 	
  \begin{eqnarray}
- \phi(\vec{r}) = K-\dfrac{2 \pi q}{A}  \abs{z-z_0} +\dfrac{2 \pi
-   q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} e^{- G \abs{z-z_0}}
-   e^{i \vec{G} \cdot \vec{r}-\vec{r}_0}
+ \phi(\vec{r}) = K-\dfrac{2 \pi q}{A}  \abs{z-z_0} +\dfrac{2 \pi q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} e^{- G \abs{z-z_0}}   e^{i \vec{G} \cdot \vec{r}-\vec{r}_0}
  \end{eqnarray}
@@
   \begin{eqnarray}\label{Eq:EC11}
- \phi(\vec{r}) = -\dfrac{8\pi q}{A} \bigg((\abs{z-z_0}-\abs{z+z_0} )
-    +\dfrac{8\pi q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \bigg(
-    e^{- G \abs{z-z_0}} -e^{- G \abs{z+z_0}}  \bigg) \cos(G_x x_0)
-    \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}
+ \phi(\vec{r}) = -\dfrac{8\pi q}{A} \bigg((\abs{z-z_0}-\abs{z+z_0} ) +\dfrac{8\pi q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \bigg( e^{- G \abs{z-z_0}} -e^{- G \abs{z+z_0}}  \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}
  \end{eqnarray}
@@
    \begin{eqnarray}
- \phi(\vec{r}) = -\dfrac{16\pi q}{A} \bigg( z
-     +\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \sinh(G z)  \cos(G_x
-     x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}} \bigg)
+ \phi(\vec{r}) = -\dfrac{16\pi q}{A} \bigg( z +\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \sinh(G z)  \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}} \bigg)
  \end{eqnarray}
 If the surface of the liquid is at a finite height c, then we can use images, like:
-\begin{figure}
+\begin{figure}[H]
 	\centering
-  \includegraphics[scale=.6]{Images/celd1}
-  \caption{\emph{Diagram shows that there is a positive (real) plane $
-      z_0 $, a negative image at $ -z_0 $ below the conductor ($ z = 0
-      $) and its images are a positive plate at $ 2c-z_0 $ and a
-      negative plate at $ 2c + z_0 $, the image is repeated vertically
-      with the period $ L_z = 4c $}}
+	\includegraphics[scale=.6]{../Images/celd1}
+	\caption{\emph{Diagram shows that there is a positive (real) plane $ z_0 $, a negative image at $ -z_0 $ below the conductor ($ z = 0 $) and its images are a positive plate at $ 2c-z_0 $ and a negative plate at $ 2c + z_0 $, the image is repeated vertically with the period $ L_z = 4c $}}
 		\label{fig:Celda1}
 \end{figure}
-In Fig. \ref{fig:Celda1} it is observed that there is a positive
-(real) plane $ z_0 $, a negative image at $ -z_0 $ below the conductor
-($ z = 0 $) and its images are a positive plate at $ 2c-z_0 $ and a
-negative plate at $ 2c + z_0 $. Also, the image is repeated vertically
-with the period $ L_z = 4c $. Therefore, the equation \ref{Eq:EC11}
-would be rewritten, like this
+In Fig.
+\ref{fig:Celda1} it is observed that there is a positive (real) plane $ z_0 $, a negative image at $ -z_0 $ below the conductor ($ z = 0 $) and its images are a positive plate at $ 2c-z_0 $ and a negative plate at $ 2c + z_0 $.
+Also, the image is repeated vertically with the period $ L_z = 4c $.
+Therefore, the equation \ref{Eq:EC11} would be rewritten, like this
  \begin{eqnarray}\label{Eq:EC1}
- \nonumber\phi(\vec{r}) = K+\dfrac{8\pi q}{A} \displaystyle\sum_{n}
-   -\bigg(\abs{z-z_0-nL_z}-\abs{z+z_0-nL_z}-\abs{z+2c+z_0-nL_z}+\abs{z-2c-z_0-nL_z}\bigg)
-   +\\ \nonumber \dfrac{1}{G}\displaystyle\sum_{\vec{G}}\bigg(
-   \displaystyle\sum_{n} \bigg( e^{-\abs{z-z_0-nL_z}}
-   +e^{-\abs{z+z_0-nL_z}}-e^{-\abs{z+2c+z_0-nL_z}}-e^{-\abs{z-2c-z_0-nL_z}}
-   \bigg)\bigg)\cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot
-   \vec{r}}\\
+ \nonumber\phi(\vec{r}) = K+\dfrac{8\pi q}{A} \displaystyle\sum_{n} -\bigg(\abs{z-z_0-nL_z}-\abs{z+z_0-nL_z}-\abs{z+2c+z_0-nL_z}+\abs{z-2c-z_0-nL_z}\bigg) +\\ \nonumber \dfrac{1}{G}\displaystyle\sum_{\vec{G}}\bigg( \displaystyle\sum_{n} \bigg( e^{-\abs{z-z_0-nL_z}} +e^{-\abs{z+z_0-nL_z}}-e^{-\abs{z+2c+z_0-nL_z}}-e^{-\abs{z-2c-z_0-nL_z}}  \bigg)\bigg)\cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}\\
 \end{eqnarray}
-The constant K is chosen thus $ \phi (z = 0) $, substituting in
-Eq. (\ref {Eq:EC1}) and after factoring $ e^{- nGL_Z} $ we are
-explicitly left with the geometric sum over $n$
+The constant K is chosen thus $ \phi (z = 0) $, substituting in Eq. (\ref {Eq:EC1}) and after factoring $ e^{- nGL_Z} $ we are explicitly left with the geometric sum over $n$
  {\small
  \begin{eqnarray}
-    \nonumber\phi(\vec{r}) = K+\dfrac{16\pi q}{A} \bigg(z+z_0  +
-    \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \bigg(e^{-Gz_0}
-    \sinh(Gz)+e^{-Gz_0(2c_z)} \sinh(Gz_0) -e^{-2Gc} \sinh(Gz)
-    \sinh(Gz_0) \\ \nonumber \dfrac{1+\cosh(2Gc)}{\sinh(2Gc)} -
-    e^{-2Gc}\cosh(2Gc) \sinh(Gz_0)   \bigg) \cos(G_x x_0) \cos(G_y
-    y_0) e^{i \vec{G} \cdot \vec{r}}   \bigg)\\
+ \nonumber\phi(\vec{r}) = K+\dfrac{16\pi q}{A} \bigg(z+z_0  + \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \bigg(e^{-Gz_0} \sinh(Gz)+e^{-Gz_0(2c_z)} \sinh(Gz_0) -e^{-2Gc} \sinh(Gz) \sinh(Gz_0) \\ \nonumber \dfrac{1+\cosh(2Gc)}{\sinh(2Gc)} - e^{-2Gc}\cosh(2Gc) \sinh(Gz_0)   \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}   \bigg)\\
  \end{eqnarray}
@@
  \begin{eqnarray}\label{Eq:EC2}
-\nonumber\phi(x, y, 0) = K+\dfrac{16\pi q}{A} \bigg(z_0  +
-   \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \bigg(e^{-2Gc}
-   \sinh(Gz_0)-e^{-2Gc} \sinh(Gz_0)   \bigg) \cos(G_x x_0) \cos(G_y
-   y_0) e^{i \vec{G} \cdot \vec{r}}\bigg) =\\ \nonumber =
-   K+\dfrac{16\pi q}{A} \\
+\nonumber\phi(x, y, 0) = K+\dfrac{16\pi q}{A} \bigg(z_0  + \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \bigg(e^{-2Gc} \sinh(Gz_0)-e^{-2Gc} \sinh(Gz_0)   \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}\bigg) =\\ \nonumber = K+\dfrac{16\pi q}{A} \\
 \end{eqnarray}
@@
  \begin{eqnarray}
-\nonumber\phi(\vec{r}) = \dfrac{16\pi q}{A}\bigg( z  +
-   \displaystyle\sum_{\vec{G}}\dfrac{\sinh(Gz_0)}{G} \bigg(e^{-Gz_0}
-   -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg)
-   \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\
+\nonumber\phi(\vec{r}) = \dfrac{16\pi q}{A}\bigg( z  + \displaystyle\sum_{\vec{G}}\dfrac{\sinh(Gz_0)}{G} \bigg(e^{-Gz_0} -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\
 \end{eqnarray}
-I am sure it is correct. Then it goes to zero at $ z = 0 $. The term
-with c disappears if $ c \longrightarrow \infty $. The sum converges
-when $ G \longrightarrow \infty $ if $ z <z_0 <c $ and diverges to $ z
-\longrightarrow z_0 $. So it seems ready for calculation.
+I am sure it is correct.
+Then it goes to zero at $ z = 0 $.
+The term with c disappears if $ c \longrightarrow \infty $.
+The sum converges when $ G \longrightarrow \infty $ if $ z <z_0 <c $ and diverges to $ z \longrightarrow z_0 $.
+So it seems ready for calculation.
 The normal component of the field is
 \begin{eqnarray}
-\nonumber E_\perp = -\dfrac{16\pi q}{A}\bigg( 1  +
-  \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \cosh(Gz)\bigg(e^{-Gz_0}
-  -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x
-  x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\
+\nonumber E_\perp = -\dfrac{16\pi q}{A}\bigg( 1  + \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \cosh(Gz)\bigg(e^{-Gz_0} -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\
 \end{eqnarray}
-And the current density is for any $ z $, for our calculation we
-choose that $ z = 0 $
+And the current density is for any $ z $, for our calculation we choose that $ z = 0 $
 \begin{eqnarray}\label{Eq:J}
-\nonumber J_\perp = -\dfrac{I}{ab}\bigg( 1  +
-  \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \cosh(Gz_0) \bigg(e^{-Gz_0}
-  -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x
-  x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\
+\nonumber J_\perp = -\dfrac{I}{ab}\bigg( 1  + \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \cosh(Gz_0) \bigg(e^{-Gz_0} -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\
 \end{eqnarray}
-Integrating on the surface of the sample is obtained $I_{nm}
-=\int^{a}_0 dx \int^{b}_0 dy \ \ e^{i\vec{G}\vec{r}}$
+Integrating on the surface of the sample is obtained $I_{nm} =\int^{a}_0 dx \int^{b}_0 dy \ \ e^{i\vec{G}\vec{r}}$
 \begin{eqnarray}
-\nonumber I_{nm}=\dfrac{1}{G_x G_y} (e^{-iG_xa}-1) (e^{-G_y b}-1) \\
-  I_{nm}=\dfrac{ab}{nm \pi^2} ((-1)^n-1-1)(-(1)^m-1-1)
+\nonumber I_{nm}=\dfrac{1}{G_x G_y} (e^{-iG_xa}-1) (e^{-G_y b}-1) \\ I_{nm}=\dfrac{ab}{nm \pi^2} ((-1)^n-1-1)(-(1)^m-1-1) 
 \end{eqnarray}
-Using the factor of the reciprocal vector in this way $ \vec {G} =
-\bigg (\dfrac{\pi}{a} n, \dfrac{\pi}{b} m \bigg) $,
-however, as all the coefficients of $ e^{- i \vec{G} \vec{r}} $ in
-\ref{Eq:J} they are even in $ \vec{G} $ and the integral is odd in n
-and m, only the constant term taxpayer to the integrated current
+Using the factor of the reciprocal vector in this way $ \vec {G} = \bigg (\dfrac{\pi}{a} n, \dfrac{\pi}{b} m \bigg) $,
+however, as all the coefficients of $ e^{- i \vec{G} \vec{r}} $ in \ref{Eq:J} they are even in $ \vec{G} $ and the integral is odd in n and m, only the constant term taxpayer to the integrated current
 \begin{eqnarray}
@@
 \subsection{Transfer Matrix Method (TMM)}
-One of the methods used for the analysis of photonic crystal
-structures is the transfer matrix method. We use it to investigate the
-reflectance of light in a one-dimensional photonic crystal. The
-electric and magnetic fields within the layers are shown as $E_m$ and
-$H_m$. Then we can specify the electric and magnetic fields in the
-air, $ E_0 $ and $ H_0 $, by solving the following matrix equation:
+One of the methods used for the analysis of photonic crystal structures is the transfer matrix method.
+We use it to investigate the reflectance of light in a one-dimensional photonic crystal.
+The electric and magnetic fields within the layers are shown as $E_m$ and $H_m$.
+Then we can specify the electric and magnetic fields in the air, $ E_0 $ and $ H_0 $, by solving the following matrix equation:
 \begin{equation}
@@
 \end{equation}
-Where N is the total number of layers including the cavity layer and $
-M_j $ is the matrix characteristic of the layer $ j $ specified by:
+Where N is the total number of layers including the cavity layer and $ M_j $ is the matrix characteristic of the layer $ j $ specified by:
 \begin{equation}
@@
 \end{equation}
-where $ \lambda $ is the wavelength, $ \tilde{n}_{_{j}} = n_{j} -
-ik_{_{j}}$ is the complex refractive index (CRI) of the layer, $ d_j $
-is the thickness of the layer, and $ \theta_j $ is the angle of
-refraction of light in the $ j $ layer. The parameter $ \eta_ {j} $
-for layer j is defined as:
+where $ \lambda $ is the wavelength, $ \tilde{n}_{_{j}} = n_{j} - ik_{_{j}}$ is the complex refractive index (CRI) of the layer, $ d_j $ is the thickness of the layer, and $ \theta_j $ is the angle of refraction of light in the $ j $ layer.
+The parameter $ \eta_ {j} $ for layer j is defined as:
 \begin{equation}\label{Eq:Mt1}
@@
 \end{equation}
-where $ \epsilon_0 $ and $ \mu_0 $ are permittivity and free space
-permeability, respectively. The transfer matrix of all the photonic
-crystal is given by:
+where $ \epsilon_0 $ and $ \mu_0 $ are permittivity and free space permeability, respectively. The transfer matrix of all the photonic crystal is given by:
 \begin{equation}
@@
 \end{equation}
-We can write the reflection and transmission coefficients in a
-one-dimensional photonic crystal nanocavity as:
+We can write the reflection and transmission coefficients in a one-dimensional photonic crystal nanocavity as:
 \begin{equation}
-r=\frac{\eta_0(m_{11}m_{12}\eta_m)
-  -(m_{21}+m_{22}\eta_m)}{\eta_0(m_{11}m_{12}\eta_m)
-  -(m_{21}+m_{22}\eta_m)}
+r=\frac{\eta_0(m_{11}m_{12}\eta_m) -(m_{21}+m_{22}\eta_m)}{\eta_0(m_{11}m_{12}\eta_m) -(m_{21}+m_{22}\eta_m)}
 \end{equation}
@@
 \end{equation}
-where $ \eta_0 $ and $ \eta_m $ are parameters for air and outlet
-layers, respectively (as defined in equations \ref{Eq:Mt1} or
-\ref{Eq:Mt2}). Furthermore, the reflectivity R and transmittance T of
-the entire photonic crystal nanocavity is given by:
+where $ \eta_0 $ and $ \eta_m $ are parameters for air and outlet layers, respectively (as defined in equations \ref{Eq:Mt1} or \ref{Eq:Mt2}).
+Furthermore, the reflectivity R and transmittance T of the entire photonic crystal nanocavity is given by:
 \begin{equation}
@@
 \section{Experimental Details}
-\begin{figure}
+\begin{figure}[H]
 	\centering
-  \includegraphics[scale=0.6]{Images/DE1}
-\caption{\emph{Schematic of the experimental set-up for
-      fabrication of porous silicon with GRIN. (a) Represents an
-      outline of the surface section, divided by three regions
-      A, B and C, corresponding to High, Medium and Low Porosity
-      respectively. (b) It is the diagram of the electrochemical
-      cell with its parts: silicon wafer, Teflon cell, platinum
-      point electrode, Electrochemical Aqueous solution and the
-      connection of the circuit with the cathode and anode. (c)
-      It is a schematic drawing of the Cross section of the
-      electrochemically attacked porous silicon seen in three
-      different regions as mentioned above. }}
+	\includegraphics[scale=0.6]{../Images/DE1}
+	\caption{\emph{Schematic of the experimental set-up for fabrication of porous silicon with GRIN.
+a) Represents an outline of the surface section, divided by three regions A, B and C, corresponding to High, Medium and Low Porosity respectively.
+b) It is the diagram of the electrochemical cell with its parts: silicon wafer, Teflon cell, platinum point electrode, Electrochemical Aqueous solution and the connection of the circuit with the cathode and anode.
+c) It is a schematic drawing of the Cross section of the electrochemically attacked porous silicon seen in three different regions as mentioned above.
+}}.
 	\label{fig:DE1}
 \end{figure}
-
-In the Fig. \ref{fig:DE1} a shows schematic representation of the
-experimental setup where porous silicon can be manufactured with GRIN,
-taking into account the considerations of the electrode as tip, the
-rectangular cell and the sample (silicon wafer) with the largest
-rectangular attack area.
-In Fig. \ref{fig:DE1} a) we draw an outline of the surface section,
-divided by three regions A, B and C, dependes in therir porosity i.e.,
-High, Medium and Low Porosity. All this corresponding to  expected to
-be obtained in the experiments. Fig. \ref{fig:DE1} b) the scheme shows
-the electrochemical cell with its parts: silicon wafer, teflon cell,
-platinum point electrode, electrochemical Aqueous Solution and the
-connection of the circuit with the cathode and anode. Finally,
-Fig. \ref{fig:DE1} c) it is a schematic drawing of the Cross section
-of the electrochemically attacked porous silicon seen from three
-different regions as mentioned above. In section 3.1 we give the
-details used to carry out our experiments.
+In the Fig.
+\ref{fig:DE1} a shows schematic representation of the experimental setup where porous silicon can be manufactured with GRIN, taking into account the considerations of the electrode as tip, the rectangular cell and the sample (silicon wafer) with the largest rectangular attack area.
+In Fig.
+\ref{fig:DE1} a) we draw an outline of the surface section, divided by three regions A, B and C, dependes in therir porosity i.e., High, Medium and Low Porosity.
+All this corresponding to  expected to be obtained in the experiments.
+Fig.
+\ref{fig:DE1} b) the scheme shows the electrochemical cell with its parts: silicon wafer, teflon cell, platinum point electrode, electrochemical Aqueous Solution and the connection of the circuit with the cathode and anode.
+Finally, Fig.
+\ref{fig:DE1} c) it is a schematic drawing of the Cross section of the electrochemically attacked porous silicon seen from three different regions as mentioned above.
+In section 3.1 we give the details used to carry out our experiments.
 
 \subsection{Fabrication of Porous Silicon Monolayers GRIN}
-Some of the simulated photonic structures were made by electrochemical
-anodization on an oriented (100) p-type crystalline Si wafer
-(resistivity 0.002 - 0.005 $ \Omega \cdot cm $), under galvanostatic
-conditions. The electrochemical anodization process was performed at
-room temperature, with an electrolytic mixture of aqueous hydrofluoric
-acid (HF) (concentration: 48 $ \% $ wt), glycerol (purity: 99.8 $ \% $
-wt) and ethanol (purity: 99.9 $ \%$ wt ) in 3: 7: 1 volume ratio,
-respectively. After the anodizing process, the samples are rinsed with
-ethanol (purity: 99.9 $ \% $  wt). The layout of the cell used is as
-seen in Fig. \ref{fig:DE1} b), with an area of $ 1,206 \ \ cm^2 $
-(this is the area attacked in the process), has a rectangular shape ($
-0.62 \ \ cm \times 2.03 \ \ cm $)  so that the current densities  that
-attacks has a lateral gradient with a greater surface area. They were
-manufactured with a fixed current of $ 5 \ \ mA $ to generate
-different current densities ranging from $ 6  $ to $ 2.5 \ \ mA / cm^2
-$. Similarly, we use the current from $ 40 \ \ mA $ to generate $ 50 $
-to $ 20 \ \ mA / cm ^ 2 $. The cathode is made of a platinum wire that
-was arranged in the form of a tip with an approximate diameter of ($
-0.5 \ \ mm $).
+Some of the simulated photonic structures were made by electrochemical anodization on an oriented (100) p-type crystalline Si wafer (resistivity 0.002 - 0.005 $ \Omega \cdot cm $), under galvanostatic conditions.
+The electrochemical anodization process was performed at room temperature, with an electrolytic mixture of aqueous hydrofluoric acid (HF) (concentration: 48 $ \% $ wt), glycerol (purity: 99.8 $ \% $ wt) and ethanol (purity: 99.9 $ \%$ wt ) in 3: 7: 1 volume ratio, respectively.
+After the anodizing process, the samples are rinsed with ethanol (purity: 99.9 $ \% $  wt).
+The layout of the cell used is as seen in Fig.
+\ref{fig:DE1} b), with an area of $ 1,206 \ \ cm^2 $ (this is the area attacked in the process), has a rectangular shape ($ 0.62 \ \ cm \times 2.03 \ \ cm $)  so that the current densities  that attacks has a lateral gradient with a greater surface area.
+They were manufactured with a fixed current of $ 5 \ \ mA $ to generate different current densities ranging from $ 6  $ to $ 2.5 \ \ mA / cm^2 $.
+Similarly, we use the current from $ 40 \ \ mA $ to generate $ 50 $ to $ 20 \ \ mA / cm ^ 2 $.
+The cathode is made of a platinum wire that was arranged in the form of a tip with an approximate diameter of ($ 0.5 \ \ mm $).
 \subsection{Reflectance Measurement}
-In the experiemental parte the reflectivity measurements were carried
-out with a Perkin Elmer Lambda 950 UV-Vis-NIR spectrophotometer. To
-calculate the complex refractive index $ \tilde{n}_{_{PSi}} = n_{_
-  {PSi}} - ik_{_{PSi}} $ of a porous layer with homogeneous porosity
-and thickness with smooth interfaces to throughout the entire
-structure, the more suitable is the adjustment procedure of the
-experimental reflectance or transmittance spectrum, this is for the
-theoretical part. In the case of the reflectance spectrum. The
-corresponding theoretical calculations were carried using procedure
-for single  smooth layer (monolayer).
+In the experiemental parte the reflectivity measurements were carried out with a Perkin Elmer Lambda 950 UV-Vis-NIR spectrophotometer.
+To calculate the complex refractive index $ \tilde{n}_{_{PSi}} = n_{_ {PSi}} - ik_{_{PSi}} $ of a porous layer with homogeneous porosity and thickness with smooth interfaces to throughout the entire structure, the more suitable is the adjustment procedure of the experimental reflectance or transmittance spectrum, this is for the theoretical part.
+In the case of the reflectance spectrum.
+The corresponding theoretical calculations were carried using procedure for single  smooth layer (monolayer).
  \begin{eqnarray}\label{Eq:ECMR}
@@
 \end{eqnarray}
-where $ r_{_ {01}} $ y $ r_{_ {12}} $ are the Fresnel reflectance
-coefficients at the interfaces $aire/PSi$ y $PSi/c-Si$ which are
-defined in terms of their complex refractive index ($\tilde{n}_{_ {1}}
-$, $\tilde{n}_{_ {2}} $ y $ \tilde{n}_{_ {3}} $), for them
-$r_{_{ij}}=(\tilde{n}_{_{i}}\cos\theta_i-\tilde{n}_{_{j}}\cos\theta_j)/(\tilde{n}_{_{i}}\cos\theta_i+\tilde{n}_{_{j}}\cos\theta_j)$,
-($j=i=0,1,2$), whilst $\delta=2\pi
-d/\lambda\sqrt{\tilde{n}^2_{_{2}}-\tilde{n}^2_{_{1}}\sin \theta_1}$.
- To adjust the reflectance spectrum, the layer thickness is an input
- parameter in the Eq.\ref{Eq:ECMR}. The advantage of this method is
- the possibility of taking into account the interface roughness effect
- by including the Davies-Bennett factor in the coefficient of each
- Fresnel \cite{I17, I18, I19}, which represents the roughness of a
- Gaussian distribution.
+where $ r_{_ {01}} $ y $ r_{_ {12}} $ are the Fresnel reflectance coefficients at the interfaces $aire/PSi$ y $PSi/c-Si$ which are defined in terms of their complex refractive index ($\tilde{n}_{_ {1}} $, $\tilde{n}_{_ {2}} $ y $ \tilde{n}_{_ {3}} $), for them $r_{_{ij}}=(\tilde{n}_{_{i}}\cos\theta_i-\tilde{n}_{_{j}}\cos\theta_j)/(\tilde{n}_{_{i}}\cos\theta_i+\tilde{n}_{_{j}}\cos\theta_j)$, ($j=i=0,1,2$), whilst $\delta=2\pi d/\lambda\sqrt{\tilde{n}^2_{_{2}}-\tilde{n}^2_{_{1}}\sin \theta_1}$.
+ To adjust the reflectance spectrum, the layer thickness is an input parameter in the Eq.\ref{Eq:ECMR}.
+The advantage of this method is the possibility of taking into account the interface roughness effect by including the Davies-Bennett factor in the coefficient of each Fresnel \cite{I17, I18, I19}, which represents the roughness of a Gaussian distribution.
 \subsection{Morphological studies}
-The morphologies of the etched porous layers (cross-sectional) was
-observed using SEM Hitachi SU1510 scanning electron microscopes
-(Hitachi High Technologies Canada, Inc., Toronto, Canada), the
-thickness  and porosity  of each fabricated  film was measured.
+The morphologies of the etched porous layers (cross-sectional) was observed using SEM Hitachi SU1510 scanning electron microscopes (Hitachi High Technologies Canada, Inc., Toronto, Canada), the thickness  and porosity  of each fabricated  film was measured.
  \subsection{Refraction Indices Monolayer of Porous Silicon GRIN } 
-Through the electrochemical anodization of c-Si wafers, Psi monolayers
-were obtained. For the refractive index of each monolayer Psi
-calcalated by ussing  Bruggeman effective medium theory, as we
-consider that we have a homogeneous medium associated with effective
-dielectric function \cite{I20}. This effective dielectric function is
-related to the dielectric functions of the two media, consisting of
-two materials (air and silicon), where it is assumed that all the
-pores or islands of the bulk material experience an average electric
-field; the equation is expressed as follows:
+Through the electrochemical anodization of c-Si wafers, Psi monolayers were obtained.
+For the refractive index of each monolayer Psi calcalated by ussing  Bruggeman effective medium theory, as we consider that we have a homogeneous medium associated with effective dielectric function \cite{I20}.
+This effective dielectric function is related to the dielectric functions of the two media, consisting of two materials (air and silicon), where it is assumed that all the pores or islands of the bulk material experience an average electric field; the equation is expressed as follows:
  \begin{eqnarray}\label{Eq:Brugg}
- p\dfrac{\varepsilon_{_{air}}-\varepsilon_{_{PSi}}}{\varepsilon_{_{air}}+\varepsilon_{_{PSi}}}+(1-p)\dfrac{\varepsilon_{_{Si}}-\varepsilon_{_{PSi}}}{\varepsilon_{_{Si}}+
-   \varepsilon_{_{PSi}}}
+ p\dfrac{\varepsilon_{_{air}}-\varepsilon_{_{PSi}}}{\varepsilon_{_{air}}+\varepsilon_{_{PSi}}}+(1-p)\dfrac{\varepsilon_{_{Si}}-\varepsilon_{_{PSi}}}{\varepsilon_{_{Si}}+ \varepsilon_{_{PSi}}}
  \end{eqnarray}
- where $ p $ is the volume fraction of air within the PSi layer
- (porosity); $\varepsilon_{_{air}}$ is the dielectric function of air;
- $\varepsilon_{_{Si}}$ is the dielectric function of c-Si, and
- $\varepsilon_{_{PSi}}$ represents the dielectric function of PSi. The
- dielectric function is a complex number and is related to the complex
- refractive index ($\tilde{n} = n - ik$), which is made up of real and
- imaginary parts, as follows $\varepsilon=\tilde{n}^2$. Its real part
- ($ n $) represents the ordinary refractive index when no light
- absorption occurs. The imaginary part ($ k $) is known as the
- extinction coefficient. The extinction coefficient determines the
- absorption rate in the medium \cite{I21}. Porosity can be estimated
- using the Bruggeman approximation, from Eq. \ref{Eq:Brugg} provided
- that the dielectric functions of each component (air and c-Si) are
- known.
+ where $ p $ is the volume fraction of air within the PSi layer (porosity); $\varepsilon_{_{air}}$ is the dielectric function of air; $\varepsilon_{_{Si}}$ is the dielectric function of c-Si, and $\varepsilon_{_{PSi}}$ represents the dielectric function of PSi.
+The dielectric function is a complex number and is related to the complex refractive index ($\tilde{n} = n - ik$), which is made up of real and imaginary parts, as follows $\varepsilon=\tilde{n}^2$.
+Its real part ($ n $) represents the ordinary refractive index when no light absorption occurs.
+The imaginary part ($ k $) is known as the extinction coefficient.
+The extinction coefficient determines the absorption rate in the medium \cite{I21}.
+Porosity can be estimated using the Bruggeman approximation, from Eq.
+\ref{Eq:Brugg} provided that the dielectric functions of each component (air and c-Si) are known.
 
  \subsection{Fabrication  of Microcavities of Porous Silicon GRIN }
- A conventional way to fabricate the porous silicon microcavity (MC)
- is a defect with a mode located between two DBRs (Distributed Bragg
- Reflector). Alternate layers of high refractive index (H) and low (L)
- refractive index are obtained, satisfying the Bragg condition
- $n_{_{i}}d_{_{i}}=\frac{\lambda_{_{c}}}{4}$  where $ i = H, L $. The
- defect must meet the condition
- $n_{_{L}}d_{_{L}}=\frac{\lambda_{_{c}}}{2}$, and the MC has the
- following sequence: $$ (HL)_6 HH (LH )_6 $$
- Initial data for conventional design we use $\lambda_{_{c}}= 0.67 \mu
- m$, $n_{_{H}} =2,6$, $P_{_{H}} =0.46$, $d_{_{H}}=0.066 \mu m  $,
- $t_{_{H}}=35 s  $ and for $n_{_{L}}= 1,4$,  $P_{_{L}} =0.75$,
- $d_{_{L}}=0.117 \mu m  $, $t_{_{L}}=11 s  $. All of this data is for
- the $ 0 $ point of the sample that is located at one end of the
- sample just below the tip counter-electrode.\\
- Our proposal for the fabrication of porous silicon GRIN microcavities
- uses the same conditions for fabrications of porous silicon GRIN
- monolayers as in section 3.1, and taking the conventional data
- mentioned above. The porous silicon microcavities (PSiMC) with
- gradient refractive index (GRIN), were manufactured with different
- current densities ranging from $ 6 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a
- current of $ 5 \ \ mA $, with high refractive index $n_{_{H}} \sim
- 2,761 $ to $ 2,808 $ and porosities from $ 0.44 $ to $ 0.39 $. Also
- for $ 50  $ to $ 20 \ \ mA / cm ^ 2 $, current of $ 38 \ \ mA $, for
- low refractive index $n_{_{L}}\sim 1,448 $ to $ 2,267 $ and with the
- corresponding  porosities of $ 0.75 $ to $ 0.64 $. Using our
- calibration ratio to design GRIN structures,  the corresponding
- current density for each measurement point.
+ A conventional way to fabricate the porous silicon microcavity (MC) is a defect with a mode located between two DBRs (Distributed Bragg Reflector).
+Alternate layers of high refractive index (H) and low (L) refractive index are obtained, satisfying the Bragg condition $n_{_{i}}d_{_{i}}=\frac{\lambda_{_{c}}}{4}$  where $ i = H, L $.
+The defect must meet the condition  $n_{_{L}}d_{_{L}}=\frac{\lambda_{_{c}}}{2}$, and the MC has the following sequence: $$ (HL)_6 HH (LH )_6 $$
+ Initial data for conventional design we use $\lambda_{_{c}}= 0.67 \mu m$, $n_{_{H}} =2,6$, $P_{_{H}} =0.46$, $d_{_{H}}=0.066 \mu m  $, $t_{_{H}}=35 s  $ and for $n_{_{L}}= 1,4$,  $P_{_{L}} =0.75$, $d_{_{L}}=0.117 \mu m  $, $t_{_{L}}=11 s  $.
+All of this data is for the $ 0 $ point of the sample that is located at one end of the sample just below the tip counter-electrode.\\
+ Our proposal for the fabrication of porous silicon GRIN microcavities uses the same conditions for fabrications of porous silicon GRIN monolayers as in section 3.1, and taking the conventional data mentioned above.
+The porous silicon microcavities (PSiMC) with gradient refractive index (GRIN), were manufactured with different current densities ranging from $ 6 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a current of $ 5 \ \ mA $, with high refractive index $n_{_{H}} \sim 2,761 $ to $ 2,808 $ and porosities from $ 0.44 $ to $ 0.39 $.
+Also for $ 50  $ to $ 20 \ \ mA / cm ^ 2 $, current of $ 38 \ \ mA $, for low refractive index $n_{_{L}}\sim 1,448 $ to $ 2,267 $ and with the corresponding  porosities of $ 0.75 $ to $ 0.64 $.
+Using our calibration ratio to design GRIN structures,  the corresponding current density for each measurement point.
 
@@
 \subsection{Simulation of the EMPCGRIN model}
- To test the developed  idea in the theoretical section, we find a
- relation of the tip of the counter electrode that acts similarly as a
- point charge and the current density for a geometry in an
- electrolytic box and solve the electrostatic equations with suitable
- boundary conditions. Resulting in an electrostatic model for photonic
- crystals with a refractive index with gradient (EMPCGRIN).
-\begin{figure}
+ To test the developed  idea in the theoretical section, we find a relation of the tip of the counter electrode that acts similarly as a point charge and the current density for a geometry in an electrolytic box and solve the electrostatic equations with suitable boundary conditions.
+Resulting in an electrostatic model for photonic crystals with a refractive index with gradient (EMPCGRIN).
+\begin{figure}[H]
 	\centering
-  \includegraphics[scale=0.7]{Images/G123}
-  \caption{\emph{ Simulation to calculate the current density in
-      a structure with gradient refractive index (GRIN) produced
-      by electrochemical attack on crystalline silicon to
-      produce porous silicon (PSi), with a current density
-      profile $ J (mA / cm ^ 2 ) $ normalized with the electric
-      current $ I (mA) $, we have $ J / I \sim 0.5 \ \ a \ \ 1.2
-      (cm^{-2}) $, for a cell of $ a = 2.03 \ \ cm $ y $ b =
-      0.62 \ \ cm $, with an electrode height $ Z_0 = 0.96 \ \
-      cm $} Eq. (\ref{Eq:J})}.
+	\includegraphics[scale=0.7]{../Images/G123}
+	\caption{\emph{ Simulation to calculate the current density in a structure with gradient refractive index (GRIN) produced by electrochemical attack on crystalline silicon to produce porous silicon (PSi), with a current density profile $ J (mA / cm ^ 2 ) $ normalized with the electric current $ I (mA) $, we have $ J / I \sim 0.5 \ \ a \ \ 1.2 (cm^{-2}) $, for a cell of $ a = 2.03 \ \ cm $ y $ b = 0.62 \ \ cm $, with an electrode height $ Z_0 = 0.96 \ \ cm $} Eq.
+(\ref{Eq:J})}.
 		\label{fig:DR1}
 \end{figure} 
-We consider Fig. \ref{fig:DR1} which come from solving
-Eq. (\ref{Eq:J}), calculating the current density as a function of the
-rectangular cell area of $1,206 \ \ cm^2 $,  the programming with the
-PERL PDL package and corresponding graph in gnuplot. We optimize the
-appropriate values so that our current density adequately attacks
-crystalline silicon, giving the gradient effect. We use as length $a =
-2.03 \ \ cm $ and width $b = 0.62 \ \ cm $ the height of the solution
-is $ c = 1 \ \ cm $ and we could locate the tip of the electrode at $
-R_0 = (X_0 = 0.2 , \ \ Y_0 = 0.4 \ \, Z_0 = 0.96) \ \ cm $ and
-evaluated at the surface on the silicon interface, in the plane $ Z =
-0 $. In this same Figure \ref{fig:DR1}, we obtain a current density
-profile $ J (mA / cm^2) $ normalized with the electric current $ I
-(mA) $, we have $ J / I \sim 1.2 \ \ a \ \ 0.5 (cm ^{-2}) $, as we see
-in Fig. \ref{fig:DR1} a) an effect that happens on the surface of the
-sample, a change of contrate due to the different densities of
-attacked currents. We see the decay behavior that the profile has as
-Fig. \ref{fig:DR1} b) which is a cut on the axis of $ a $. When we
-vary the currents we can observe the behavior of changes in the
-normalized current density, with the data obtained through the
-simulation we could have a better optimization in the design of porous
-silicon proposing a new and novel experimental arrangement, in the
-same way we can give ourselves an idea by means of the graph of how
-the attack would be and the formal side of the pores in the silicon.
+We consider Fig.
+\ref{fig:DR1} which come from solving Eq.
+(\ref{Eq:J}), calculating the current density as a function of the rectangular cell area of $1,206 \ \ cm^2 $,  the programming with the PERL PDL package and corresponding graph in gnuplot.
+We optimize the appropriate values so that our current density adequately attacks crystalline silicon, giving the gradient effect.
+We use as length $a = 2.03 \ \ cm $ and width $b = 0.62 \ \ cm $ the height of the solution is $ c = 1 \ \ cm $ and we could locate the tip of the electrode at $ R_0 = (X_0 = 0.2 , \ \ Y_0 = 0.4 \ \, Z_0 = 0.96) \ \ cm $ and evaluated at the surface on the silicon interface, in the plane $ Z = 0 $.
+In this same Figure \ref{fig:DR1}, we obtain a current density profile $ J (mA / cm^2) $ normalized with the electric current $ I (mA) $, we have $ J / I \sim 1.2 \ \ a \ \ 0.5 (cm ^{-2}) $, as we see in Fig.
+\ref{fig:DR1} a) an effect that happens on the surface of the sample, a change of contrate due to the different densities of attacked currents.
+We see the decay behavior that the profile has as Fig.
+\ref{fig:DR1} b) which is a cut on the axis of $ a $.
+When we vary the currents we can observe the behavior of changes in the normalized current density, with the data obtained through the simulation we could have a better optimization in the design of porous silicon proposing a new and novel experimental arrangement, in the same way we can give ourselves an idea by means of the graph of how the attack would be and the formal side of the pores in the silicon.
 
 \subsection{Monolayers GRIN Porous Silicon }
-\begin{figure}
+\begin{figure}[H]
 	\centering
-	\includegraphics[scale=.3]{Images/celdan2}
-	\caption{\emph{ Mechanical 3D modeling, design of the
-            electrochemical cell where we can see the shape of a prism
-            giving the required and necessary data for the
-            experiments. The design of the cell used is $ 1,206 \ \ cm
-            ^ 2 $ (this is the area attacked in the process), the area
-            attacked is rectangular ($ 0.62 \ \ cm \times 2.03 \ \ cm
-            $) and a height ( $ 1.2 \ \ cm $) a) Complete cell b) Cell
-            without top cover and c) Top view}}
+	\includegraphics[scale=.3]{../Images/celdan2} 
+	\caption{\emph{ Mechanical 3D modeling, design of the electrochemical cell where we can see the shape of a prism giving the required and necessary data for the experiments.
+The design of the cell used is $ 1,206 \ \ cm ^ 2 $ (this is the area attacked in the process), the area attacked is rectangular ($ 0.62 \ \ cm \times 2.03 \ \ cm $) and a height ( $ 1.2 \ \ cm $) a) Complete cell b) Cell without top cover and c) Top view}}
 	\label{fig:por1}
 \end{figure}
-We can see in Fig. \ref{fig:por1}, 3D modeling the mechanical design
-for the electrochemical cell  better optimization in manufacturing
-silicon pores where we can see the shape of a prism giving the
-required data. The design of the cell used is $ 1,206 \ \ cm ^ 2 $
-(this is the area attacked in the process), the area attacked is
-rectangular ($ 0.62 \ \ cm \times 2.03 \ \ cm $) and a height ( $ 1.2
-\ \ cm $), all this in order to optimize our experiments adjusted to
-all the needs that this required.
-\begin{figure}
+We can see in Fig.
+\ref{fig:por1}, 3D modeling the mechanical design for the electrochemical cell  better optimization in manufacturing silicon pores where we can see the shape of a prism giving the required data.
+The design of the cell used is $ 1,206 \ \ cm ^ 2 $ (this is the area attacked in the process), the area attacked is rectangular ($ 0.62 \ \ cm \times 2.03 \ \ cm $) and a height ( $ 1.2 \ \ cm $), all this in order to optimize our experiments adjusted to all the needs that this required.
+\begin{figure}[H]
 	\centering
-  \includegraphics[scale=.5]{Images/SPgrin51}
-  \caption{\emph{a) Silicon sample attacked with an electrolytic
-      mixture of aqueous hydrofluoric acid (HF) (concentration:
-      48 $ \% $  wt), glycerol (purity: 99.8 $ \% $  wt) and
-      ethanol (purity: 99.9 $ \% $  wt ) in 3: 7: 1 volume
-      ratio, respectively. Obtaining a monolayer of porous
-      Silicon with GRIN G1 with an initial current of G1 (5 mA),
-      with an attack time of 600s. Three different locations are
-      considered, denoted as follows, A (0.3cm) and B (0.8cm)
-      and C (1.7cm). b) Reflectance measurements to know the
-      optical properties at each of the points and the
-      adjustments that were produced by means of the equation
-      \ref{Eq:ECMR}. c) We have the indices of refraction of the
-      complex porous silicon GRIN, where we calculate the real
-      and imaginary part by means of the equation
-      \ref{Eq:Brugg}. for different porosities at each point, A
-      (P = 0.44), B (P = 0.42) and C (P = 0.40) } }
+	\includegraphics[scale=.5]{../Images/SPgrin51}
+	\caption{\emph{a) Silicon sample attacked with an electrolytic mixture of aqueous hydrofluoric acid (HF) (concentration: 48 $ \% $  wt), glycerol (purity: 99.8 $ \% $  wt) and ethanol (purity: 99.9 $ \% $  wt ) in 3: 7: 1 volume ratio, respectively.
+Obtaining a monolayer of porous Silicon with GRIN G1 with an initial current of G1 (5 mA), with an attack time of 600s.
+Three different locations are considered, denoted as follows, A (0.3cm) and B (0.8cm) and C (1.7cm).
+b) Reflectance measurements to know the optical properties at each of the points and the adjustments that were produced by means of the equation \ref{Eq:ECMR}.
+c) We have the indices of refraction of the complex porous silicon GRIN, where we calculate the real and imaginary part by means of the equation \ref{Eq:Brugg}.
+for different porosities at each point, A (P = 0.44), B (P = 0.42) and C (P = 0.40) } }
 	\label{fig:DR3}
 \end{figure} 
- The Fig. \ref{fig:DR3} a) three locations at different points are
- considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B (0.8 \ \
- cm) $ and $ C (1.7 \ \ cm) $, from the sample of PSi GRIN $ G1 (I = 5
- mA) $. Also the Fig. \ref{fig:DR3}. b), we have the reflectance
- measurements to know the optical properties and the adjustments that
- were produced by means of the equation \ref{Eq:ECMR}. In the
- Fig. \ref{fig:DR3} c) are indices of refraction of the porous silicon
- complex GRIN, where we calculate the real and imaginary part by means
- of Eq. \ref{Eq:Brugg} for different porosities at each point, $ A (P
- = 0.44) $, $ B (P = 0.42) $ and $ C (P = 0.40) $. Location $ A $ is
- closest to the electrode, while location $ C $ is furthest to the
- other end of the sample. Since the current density is applied from
- one end, the field lines attack the sample laterally to the silicon
- wafer, in the present configuration, an assembly was made based on
- the simulated data shown in Fig. \ref{fig:DR1} the experimental part
- was taken a platinum electrode covering its surface, leaving only a
- very small area, as if it were a tip. The electrochemical reaction
- takes place when we apply currents from an anode end (electrode tip)
- to the silicon substrate (resistivity $ 0.002 - 0.005  \Omega \cdot
- cm $), through an electrolyte forming a current circuit. The
- reflectance spectra of the newly recorded G1 samples measured at
- points $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm)
- $ are presented in Fig. \ref{fig:DR3} b), a numerical reflectivity
- adjustment was performed using the transfer matrix method for the
- case of a porous monolayer in Si. It should be noted that the
- adjustment made was considered a spectral range of the wavelength of
- the experimental reflectivity spectra for which the silicon can be
- considered the complex index and thus find the refractive index of
- the complex porous silicon with the purpose of determining the
- porosity and the experimental physical thickness (nm) by means of the
- SEM. The formation of PSi GRIN in the thickness occurs due to the
- variation in the concentration of the voids available at the Si
- electrolyte interface, therefore, an increase in the applied lateral
- current density increases the dimension of the pores and their
- depth. Thus, the extent of the porous film showing a gradient that
- can be controlled from the lateral current density.
-\begin{figure}
+ The Fig.
+\ref{fig:DR3} a) three locations at different points are considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $, from the sample of PSi GRIN $ G1 (I = 5 mA) $.
+Also the Fig.
+\ref{fig:DR3}.
+b), we have the reflectance measurements to know the optical properties and the adjustments that were produced by means of the equation \ref{Eq:ECMR}.
+In the Fig.
+\ref{fig:DR3} c) are indices of refraction of the porous silicon complex GRIN, where we calculate the real and imaginary part by means of Eq.
+\ref{Eq:Brugg} for different porosities at each point, $ A (P = 0.44) $, $ B (P = 0.42) $ and $ C (P = 0.40) $.
+Location $ A $ is closest to the electrode, while location $ C $ is furthest to the other end of the sample.
+Since the current density is applied from one end, the field lines attack the sample laterally to the silicon wafer, in the present configuration, an assembly was made based on the simulated data shown in Fig.
+\ref{fig:DR1} the experimental part was taken a platinum electrode covering its surface, leaving only a very small area, as if it were a tip.
+The electrochemical reaction takes place when we apply currents from an anode end (electrode tip) to the silicon substrate (resistivity $ 0.002 - 0.005  \Omega \cdot cm $), through an electrolyte forming a current circuit.
+The reflectance spectra of the newly recorded G1 samples measured at points $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $ are presented in Fig.
+\ref{fig:DR3} b), a numerical reflectivity adjustment was performed using the transfer matrix method for the case of a porous monolayer in Si.
+It should be noted that the adjustment made was considered a spectral range of the wavelength of the experimental reflectivity spectra for which the silicon can be considered the complex index and thus find the refractive index of the complex porous silicon with the purpose of determining the porosity and the experimental physical thickness (nm) by means of the SEM.
+The formation of PSi GRIN in the thickness occurs due to the variation in the concentration of the voids available at the Si electrolyte interface, therefore, an increase in the applied lateral current density increases the dimension of the pores and their depth.
+Thus, the extent of the porous film showing a gradient that can be controlled from the lateral current density.
+\begin{figure}[H]
 	\centering
-  \includegraphics[scale=.5]{Images/semD11}
-  \caption{\emph{Characterization of a monolayer of PSi GRIN G1
-      with an initial current of $ 5 \ \ mA $, seeing the
-      morphology and depth of the cross section of several SEM
-      micrographs, at different points, $ A (0.3 \ \ cm) $ and $
-      B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $. We can see the
-      sample size for each measurement point, the depth $ d (A)
-      = 1320 \ \ nm $, $ d (B) = 997 \ \ nm $ and $ d (C) = 605
-      \ \ nm $ } }
+	\includegraphics[scale=.5]{../Images/semD11}
+	\caption{\emph{Characterization of a monolayer of PSi GRIN G1 with an initial current of $ 5 \ \ mA $, seeing the morphology and depth of the cross section of several SEM micrographs, at different points, $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $.
+We can see the sample size for each measurement point, the depth $ d (A) = 1320 \ \ nm $, $ d (B) = 997 \ \ nm $ and $ d (C) = 605 \ \ nm $ } }
 	\label{fig:DR4}
 \end{figure} 
-In the Fig. \ref{fig:DR4} shows the cross section views   at points $
-A (0.3 \ \ cm) $, $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $, we can
-measure the thickness for each point of the sample $ G1 (I = 5 \ \ mA)
-$, $ d (A) = 1320 \ \ nm $, $ d (B) = 997 \ \ nm $ and $ d (C) = 605 \
-\ nm $. Likewise, we could check it for a second sample $ G2 (I = 40 \
-\ mA) $, with porosities for each point, $ A (P = 0.76) $, $ B (P =
-0.73) $ and $ C (P = 0.68) $ and the depths $ d (A) = 1950 \ \ nm $, $
-d (B) = 1690 \ \ nm $ and $ d (C) = 1430 \ \ nm $, designed in the
-same way as the shows G1, only varying the current taking into account
-the current density ratio for each point. Apart from that, a
-structural gradient was formed, along the direction \emph{ a}  of the
-axis of the $ x $, where the tip of the electrode is near the point $
-A $ and away from the point $ C $ of the substrate, using the proposed
-experimental setup. In addition, it was possible to control the
-current density based on the position of the sample and the depth,
-seen in the SEM micrographs.
- \begin{figure}
+In the Fig.
+\ref{fig:DR4} shows the cross section views   at points $ A (0.3 \ \ cm) $, $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $, we can measure the thickness for each point of the sample $ G1 (I = 5 \ \ mA) $, $ d (A) = 1320 \ \ nm $, $ d (B) = 997 \ \ nm $ and $ d (C) = 605 \ \ nm $.
+Likewise, we could check it for a second sample $ G2 (I = 40 \ \ mA) $, with porosities for each point, $ A (P = 0.76) $, $ B (P = 0.73) $ and $ C (P = 0.68) $ and the depths $ d (A) = 1950 \ \ nm $, $ d (B) = 1690 \ \ nm $ and $ d (C) = 1430 \ \ nm $, designed in the same way as the shows G1, only varying the current taking into account the current density ratio for each point.
+Apart from that, a structural gradient was formed, along the direction \emph{ a}  of the axis of the $ x $, where the tip of the electrode is near the point $ A $ and away from the point $ C $ of the substrate, using the proposed experimental setup.
+In addition, it was possible to control the current density based on the position of the sample and the depth, seen in the SEM micrographs.
+ \begin{figure}[H]
  	\centering
-   \includegraphics[scale=.7]{Images/grinJDR}
-   \caption{\emph{a) It is the relation of the current density $
-       J (mA / cm ^ 2) $ normalized with the electric current $ I
-       (mA) $, we have $ J / I \ sim 1.2 \ \ a \ \ 0.5 ( cm^{-2})
-       $, when we apply it to two samples $ G1 (I = 5 \ \ mA) $
-       and $ G2 (I = 40 \ \ mA) $ depending on the axis $ a $ $
-       (0.1 ... 2.0 \ \ cm) $, measured at points $ A (0.3 \ \
-       cm) $ , $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $. b) The
-       attack speed $ v = d (J_i) / t (nm / sec) $, the depths
-       (thickness $ d (J_i) $, $ i = $ $ A (0.3 \ \ cm) $, $ B (
-       0.8 \ \ cm) $ y $ C (1.7 \ \ cm)) $ taken in SEM
-       micrographs $ d (J_i) (nm) $ and attack times $ G1 (t =
-       600 \ \ s) $ y $ G2 (t = 200 \ \ s) $, depending on the
-       axis $ a $ $ (0.1 ... 2.0 \ \ cm) $ } }
+ 	\includegraphics[scale=.7]{../Images/grinJDR}
+ 	\caption{\emph{a) It is the relation of the current density $ J (mA / cm ^ 2) $ normalized with the electric current $ I (mA) $, we have $ J / I \ sim 1.2 \ \ a \ \ 0.5 ( cm^{-2}) $, when we apply it to two samples $ G1 (I = 5 \ \ mA) $ and $ G2 (I = 40 \ \ mA) $ depending on the axis $ a $ $ (0.1 ...
+2.0 \ \ cm) $, measured at points $ A (0.3 \ \ cm) $ , $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $.
+b) The attack speed $ v = d (J_i) / t (nm / sec) $, the depths (thickness $ d (J_i) $, $ i = $ $ A (0.3 \ \ cm) $, $ B ( 0.8 \ \ cm) $ y $ C (1.7 \ \ cm)) $ taken in SEM micrographs $ d (J_i) (nm) $ and attack times $ G1 (t = 600 \ \ s) $ y $ G2 (t = 200 \ \ s) $, depending on the axis $ a $ $ (0.1 ...
+2.0 \ \ cm) $ } }
  	\label{fig:JDR}
  \end{figure}
-In Fig. \ref{fig:JDR} a) It is the relation of the current density $ J
-(mA / cm ^ 2) $ normalized with the electric current $ I (mA) $, we
-have $ J / I \ sim 1.2 \ \ a \ \ 0.5 (1 / cm ^ 2) $, when we apply it
-to two samples $ G1 (I = 5 \ \ mA) $ and $ G2 (I = 40 \ \ mA) $
-depending on the axis $ a $ $ (0.1 ... 2.0 \ \ cm) $, measured at
-points $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm)
-$.
-The Fig. \ref{fig:JDR} b) we can calculate the attack speed $ v = d
-(J_i) / t (nm / s) $, where the depths (thickness $ d (J_i) $, $ i = $
-$ A (0.3 \ \ cm) $, $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm)) $ taken
-in SEM micrographs $ d (J_i) (nm) $ and attack times $ G1 (t = 600 \ \
-s) $ and $ G2 (t = 200 \ \ s) $, depending on the axis $ a $ $ (0.1
-... 2.0 \ \ cm) $.
-\begin{figure}
+In Fig.
+\ref{fig:JDR} a) It is the relation of the current density $ J (mA / cm ^ 2) $ normalized with the electric current $ I (mA) $, we have $ J / I \ sim 1.2 \ \ a \ \ 0.5 (1 / cm ^ 2) $, when we apply it to two samples $ G1 (I = 5 \ \ mA) $ and $ G2 (I = 40 \ \ mA) $ depending on the axis $ a $ $ (0.1 ...
+2.0 \ \ cm) $, measured at points $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $.
+The Fig.
+\ref{fig:JDR} b) we can calculate the attack speed $ v = d (J_i) / t (nm / s) $, where the depths (thickness $ d (J_i) $, $ i = $ $ A (0.3 \ \ cm) $, $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm)) $ taken in SEM micrographs $ d (J_i) (nm) $ and attack times $ G1 (t = 600 \ \ s) $ and $ G2 (t = 200 \ \ s) $, depending on the axis $ a $ $ (0.1 ...
+2.0 \ \ cm) $.
+\begin{figure}[H]
 	\centering
-  \includegraphics[scale=.6]{Images/grinJD31}
-  \caption{\emph{The relationship of samples $ G1 (I = 5 mA) $ and $
-      G2 (I = 40 mA) $ were obtained to find: a) Attack speed with
-      current density for each point and b) Porosity as a function of
-      density current. With this we have the calibration curves for
-      the manufacture of any GRIN porous silicon structure   } }
+	\includegraphics[scale=.6]{../Images/grinJD31}
+	\caption{\emph{The relationship of samples $ G1 (I = 5 mA) $ and $ G2 (I = 40 mA) $ were obtained to find: a) Attack speed with current density for each point and b) Porosity as a function of density current.
+With this we have the calibration curves for the manufacture of any GRIN porous silicon structure   } }
 		\label{fig:Indr1}
 \end{figure}
-Fig. \ref{fig:Indr1} a) explicitly explain the relationships that
-emerge when designing samples $ G1 (I = 5 mA) $ and $ G2 (I = 40 mA)
-$. For the first case $ G1 $ the depths ($ 1320 \ \ nm $ to $ 605 \ \
-nm $) and the current densities ($ 6 \ \ mA / cm ^ 2 $ to $ 2.5 \ \ mA
-/ cm ^ 2 $), finding the attack speed $ 2.2 \ \ nm / s $ up to $ 1.1 \
-\ nm / s $ relation with depth and the time ($ 600 \ \ s $) of
-exposure of the sample, with the current density . We also find the
-depth ($ 1950 \ \ nm $ at $ 1430 \ \ nm $) and the current density ($
-50 \ \ mA / cm ^ 2 $ at $ 20 \ \ mA / cm ^ 2 $) as a function of the
-measurement points of the sample $ G2 (I = 40 mA) $. We were able to
-obtain the attack speed from $ 9.8 \ \ nm / s $ up to $ 7.1 \ \ m / s
-$ by relating to depth and time ($ 200 \ \ s $), with current
-density. Once the thickness of the monolayer and the attack time
-applied to them are known, calculate the attack speed according to the
-formula $ v = d / t $, for each of the current densities at the points
-$ A ( 0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm)
-$. Then we fit a function to the attack speed points with the
-different current densities allowed by the anodizing condition. For a
-desired thickness $ d (J_i) $, calculate the attack time $ t $ (so, $
-t = v / d (J_i) $) and we can design any structure knowing the current
-density and the attack time. Fig. \ref{fig:Indr1} b) we find a
-relation of the porosity for each position with its determined current
-density. Therefore, if it is desired to manufacture a PSi monolayer of
-a certain porosity with a certain end, it is enough to resort to the
-graphs of Fig. \ref{fig:Indr1} to determine the corresponding current
-density, attack speed and consequently the time, obtaining for that
-monolayer. The importance of the calibration curves is that it allows
-us to have a relationship of the porosities that can be reached (and
-by having control over the possible refractive indices) as a function
-of the current density and to be controlled to control the thickness
-of the layers that are manufactured, by controlling the attack time
-for each of the chosen currents.
+Fig.
+\ref{fig:Indr1} a) explicitly explain the relationships that emerge when designing samples $ G1 (I = 5 mA) $ and $ G2 (I = 40 mA) $.
+For the first case $ G1 $ the depths ($ 1320 \ \ nm $ to $ 605 \ \ nm $) and the current densities ($ 6 \ \ mA / cm ^ 2 $ to $ 2.5 \ \ mA / cm ^ 2 $), finding the attack speed $ 2.2 \ \ nm / s $ up to $ 1.1 \ \ nm / s $ relation with depth and the time ($ 600 \ \ s $) of exposure of the sample, with the current density .
+We also find the depth ($ 1950 \ \ nm $ at $ 1430 \ \ nm $) and the current density ($ 50 \ \ mA / cm ^ 2 $ at $ 20 \ \ mA / cm ^ 2 $) as a function of the measurement points of the sample $ G2 (I = 40 mA) $.
+We were able to obtain the attack speed from $ 9.8 \ \ nm / s $ up to $ 7.1 \ \ m / s $ by relating to depth and time ($ 200 \ \ s $), with current density.
+Once the thickness of the monolayer and the attack time applied to them are known, calculate the attack speed according to the formula $ v = d / t $, for each of the current densities at the points $ A ( 0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $.
+Then we fit a function to the attack speed points with the different current densities allowed by the anodizing condition.
+For a desired thickness $ d (J_i) $, calculate the attack time $ t $ (so, $ t = v / d (J_i) $) and we can design any structure knowing the current density and the attack time.
+Fig.
+\ref{fig:Indr1} b) we find a relation of the porosity for each position with its determined current density.
+Therefore, if it is desired to manufacture a PSi monolayer of a certain porosity with a certain end, it is enough to resort to the graphs of Fig.
+\ref{fig:Indr1} to determine the corresponding current density, attack speed and consequently the time, obtaining for that monolayer.
+The importance of the calibration curves is that it allows us to have a relationship of the porosities that can be reached (and by having control over the possible refractive indices) as a function of the current density and to be controlled to control the thickness of the layers that are manufactured, by controlling the attack time for each of the chosen currents.
 
 \subsection{GRIN Porous Silicon Microcavities}
- \begin{figure}
+ \begin{figure}[H]
 	\centering
-	\includegraphics[scale=0.4]{Images/MicrGrin}
-	\caption{\emph{Diagram of a microcavity of porous silicon
-            GRIN. Alternate layers are obtained of high (H) refractive
-            index $n_{_{Hi}}$ and low (L) refractive index
-            $n_{_{Li}}$, where $N_{_{H}}$ is the number of layers for
-            $n_{_{Hi}}$ and $N_{_{L}}$ is the number of layers for
-            $n_{_{Li}}$. Then,  $d_{_{Hi}}$ is the monolayer thickness
-            of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$
-            is the monolayer thickness of $n_{_{Hi}}$ at that
-            measurement point. Therefore,  $d_{_{i}}$ is the total
-            thickness calculated for each of the measurements,
-            defining a i = $ A, B, C$. Having the following
-            relationship $d_{_{i}} =
-            (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) +
-            (2d_{_{Hi}})$. }}
+	\includegraphics[scale=0.4]{../Images/MicrGrin}
+	\caption{\emph{Diagram of a microcavity of porous silicon GRIN.
+Alternate layers are obtained of high (H) refractive index $n_{_{Hi}}$ and low (L) refractive index $n_{_{Li}}$, where $N_{_{H}}$ is the number of layers for  $n_{_{Hi}}$ and $N_{_{L}}$ is the number of layers for $n_{_{Li}}$.
+Then,  $d_{_{Hi}}$ is the monolayer thickness of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$ is the monolayer thickness of $n_{_{Hi}}$ at that measurement point.
+Therefore,  $d_{_{i}}$ is the total thickness calculated for each of the measurements, defining a i = $ A, B, C$.
+Having the following relationship $d_{_{i}} = (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$.
+}}
 	\label{fig:MCGRIN0}
 \end{figure}
-The Fig. \ref{fig:MCGRIN0} the scheme of  a initially proposed lateral
-gradient for monolayers should be shown in section 4.2, where we
-designed an electolytic cell suitable for our experiments and giving
-us the expected results of the simulation in section 4.1. Now our
-purpose is to manufacture more complex photonic structures such as the
-Porous silicon microcavities GRIN, taking into account that we start
-from having a tip electrode almost on the surface and by making a
-variation of currents we can achieve the effect of alternating the
-layers. Alternate layers are obtained of high (H) refractive index
-$n_{_{Hi}}$ and low (L) refractive index $n_{_{Li}}$, where $N_{_{H}}$
-is the number of layers for  $n_{_{Hi}}$ and $N_{_{L}}$ is the number
-of layers for $n_{_{Li}}$. Then,  $d_{_{Hi}}$ is the monolayer
-thickness of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$ is
-the monolayer thickness of $n_{_{Hi}}$ at that measurement
-point. Therefore,  $d_{_{i}}$ is the total thickness calculated for
-each of the measurements, defining a i = $ A, B, C$. Having the
-following relationship $d_{_{i}} =
-(N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$.
-Initial data for conventional design we use  $\lambda_{_{c}}= 0.67 \ \
-\mu m$, $n_{_{H}} =2.6$, $P_{_{H}} =0.46$, $d_{_{H}}=0.066 \ \ \mu m
-$, $t_{_{H}}=35 s  $ y para  $n_{_{L}}= 1.4$,  $P_{_{L}} =0.75$,
-$d_{_{L}}=0.117 \ \ \mu m  $, $t_{_{L}}=11 s  $. All these data are
-for the point $ 0 $ which is located at one end of the sample just
-below the tip counter-electrode.
-\begin{figure}
+The Fig.
+\ref{fig:MCGRIN0} the scheme of  a initially proposed lateral gradient for monolayers should be shown in section 4.2, where we designed an electolytic cell suitable for our experiments and giving us the expected results of the simulation in section 4.1.
+Now our purpose is to manufacture more complex photonic structures such as the Porous silicon microcavities GRIN, taking into account that we start from having a tip electrode almost on the surface and by making a variation of currents we can achieve the effect of alternating the layers.
+Alternate layers are obtained of high (H) refractive index $n_{_{Hi}}$ and low (L) refractive index $n_{_{Li}}$, where $N_{_{H}}$ is the number of layers for  $n_{_{Hi}}$ and $N_{_{L}}$ is the number of layers for $n_{_{Li}}$.
+Then,  $d_{_{Hi}}$ is the monolayer thickness of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$ is the monolayer thickness of $n_{_{Hi}}$ at that measurement point.
+Therefore,  $d_{_{i}}$ is the total thickness calculated for each of the measurements, defining a i = $ A, B, C$.
+Having the following relationship $d_{_{i}} = (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$.
+Initial data for conventional design we use  $\lambda_{_{c}}= 0.67 \ \ \mu m$, $n_{_{H}} =2.6$, $P_{_{H}} =0.46$, $d_{_{H}}=0.066 \ \ \mu m  $, $t_{_{H}}=35 s  $ y para  $n_{_{L}}= 1.4$,  $P_{_{L}} =0.75$, $d_{_{L}}=0.117 \ \ \mu m  $, $t_{_{L}}=11 s  $.
+All these data are for the point $ 0 $ which is located at one end of the sample just below the tip counter-electrode.
+\begin{figure}[H]
  	\centering
-  \includegraphics[scale=.5]{Images/MCGRIN2}
-  \caption{\emph{a) Three locations at different points are
-      considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B
-      (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the PSiMCGRIN
-      sample $ GMC $. b) We have the reflectance measurements to
-      know the optical properties with the proposed
-      simulation. We were able to show that in a Porous Silicon
-      GRIN structure, for a microcavity the data is very
-      consistent with the simulation and the experiment, we
-      found the refractive indices and the porosities as a
-      function of the current density at each measurement point,
-      see Table \ref{tabla:1}. }}
+ 	\includegraphics[scale=.5]{../Images/MCGRIN2}
+ 	\caption{\emph{a) Three locations at different points are considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the PSiMCGRIN sample $ GMC $.
+b) We have the reflectance measurements to know the optical properties with the proposed simulation.
+We were able to show that in a Porous Silicon GRIN structure, for a microcavity the data is very consistent with the simulation and the experiment, we found the refractive indices and the porosities as a function of the current density at each measurement point, see Table \ref{tabla:1}.
+}}
  	\label{fig:MCGRIN3}
@@
 
-\begin{table}
+\begin{table}[H]
 	\centering
@@
 	\end{tabular} 
-  \caption{ \emph{We have different points denoted as follows, $ A
-      (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $,
-      from the sample of a Porous Silicon Microcavity GRIN
-      (PSiMCGRIN) $ GMC $. Alternate layers of high refractive index
-      (H) and low refractive index (L) are obtained at each of the
-      measurement points (A, B and C). The refractive indexes of the
-      PSiMCGRIN were considered from the experimental and theoretical
-      values that were obtained for the porosity ($ P =
-      0.3J^{0.24}$). And we could obtain the attack time with the
-      relation of $ V = 0.53J ^ {0.79} $ where $ t = d / V $.}}
+	\caption{ \emph{We have different points denoted as follows, $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the sample of a Porous Silicon Microcavity GRIN  (PSiMCGRIN) $ GMC $.
+Alternate layers of high refractive index (H) and low refractive index (L) are obtained at each of the measurement points (A, B and C).
+The refractive indexes of the PSiMCGRIN were considered from the experimental and theoretical values that were obtained for the porosity ($ P = 0.3J^{0.24}$).
+And we could obtain the attack time with the relation of $ V = 0.53J ^ {0.79} $ where $ t = d / V $.}}
 	\label{tabla:1}
 \end{table}
-In Fig. \ref{fig:MCGRIN3} a) Three locations at different points are
-considered, denoted as follows, $ A (0.3 \ \ cm) $ , $ B (0.8 \ \ cm)
-$ and $ C (1.2 \ \ cm) $, from the PSiMCGRIN sample $ GMC $. Likewise,
-Fig. \ref{fig:DR3} b), we have the reflectance measurements to know
-the optical properties with the proposed simulation. We can see how
-from an experimental setup we have some important results as a result
-of a whole calibration curve suitable for making GRIN porous
-silicon. The refractive index of the Porous Silicon Microcavities GRIN
-were considered the experimental and theoretical values obtained for
-the porosity and the thicknesses shown in Table 1. The porous silicon
-microcavities (MCSP) with refractive index with gradient (GRIN), were
-manufactured with different current densities ranging from $ 6 \ \ mA
-/ cm ^ 2 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a current of $ 5 \ \ mA $,
-for a $t_{_{H}}=35 s $, with a high refractive index $n_{_{H}} \sim$ $
-2,661$ to $ 2,808$ and porosities of $P_{_{H}} \sim$ $ 0.45 $ to $
-0.39 $. Also for $ 44 \ \ mA /cm^2 $ to $ 24 \ \ mA / cm^2 $, current
-of $ 38 \ \ mA $, using $t_{_{H}}=11 s$  for low refractive index
-$n_{_{L}}\sim$ $ 1,448 $ to $ 2,267 $ and with porosities of
-$P_{_{H}} \sim$ $0.75 $ to $ 0.64 $. The porosity was calculated with
-the calibration curve exposed in the ($ P = 0.3J^{0.24} $). And the
-attack time could be obtained with the relation of $ V = 0.53J^{0.79}
-$ where $ t = d / V $ and the refractive index using the Bruggeman
-formula. For theoretical values, we use complex refractive indices as
-free parameters to fit the experimental refractive spectra (Section
-4.2).
- \begin{figure}
+In Fig.
+\ref{fig:MCGRIN3} a) Three locations at different points are considered, denoted as follows, $ A (0.3 \ \ cm) $ , $ B (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the PSiMCGRIN sample $ GMC $.
+Likewise, Fig.
+\ref{fig:DR3} b), we have the reflectance measurements to know the optical properties with the proposed simulation.
+We can see how from an experimental setup we have some important results as a result of a whole calibration curve suitable for making GRIN porous silicon.
+The refractive index of the Porous Silicon Microcavities GRIN were considered the experimental and theoretical values obtained for the porosity and the thicknesses shown in Table 1.
+The porous silicon microcavities (MCSP) with refractive index with gradient (GRIN), were manufactured with different current densities ranging from $ 6 \ \ mA / cm ^ 2 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a current of $ 5 \ \ mA $, for a $t_{_{H}}=35 s $, with a high refractive index $n_{_{H}} \sim$ $ 2,661$ to $ 2,808$ and porosities of $P_{_{H}} \sim$ $ 0.45 $ to $ 0.39 $.
+Also for $ 44 \ \ mA /cm^2 $ to $ 24 \ \ mA / cm^2 $, current of $ 38 \ \ mA $, using $t_{_{H}}=11 s$  for low refractive index $n_{_{L}}\sim$ $ 1,448 $ to $ 2,267 $ and with porosities of  $P_{_{H}} \sim$ $0.75 $ to $ 0.64 $.
+The porosity was calculated with the calibration curve exposed in the ($ P = 0.3J^{0.24} $).
+And the attack time could be obtained with the relation of $ V = 0.53J^{0.79} $ where $ t = d / V $ and the refractive index using the Bruggeman formula.
+For theoretical values, we use complex refractive indices as free parameters to fit the experimental refractive spectra (Section 4.2).
+ \begin{figure}[H]
 	\centering
-   \includegraphics[scale=.5]{Images/MCGRINSEM}
-   \caption{\emph{SEM image of the cross section profile of the
-       microcavities with GRIN. The measured thicknesses of the
-       complete multi-film structures showed good agreement with the
-       simulations taken from $ V = 0.53J ^ {0.79} $ where $d_j=Vt_j$
-       ($j=H,L$), which are the thicknesses of each of the monolayer
-       of the porous silicon microcavity GRIN at the measurement
-       points and the total thickness we find it as $d_{_{i}} =
-       (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$
-       defining $ i = $ A, B, C. Which resulted in (measured /
-       simulation) $ 2.25 / 2.31 \ \ \mu m $ (for structure at Point
-       A), $ 2.17 / 2.08 \ \ \mu m $ (for structure at point B) and $
-       1.87 / 1.65 \ \ \mu m $ (for structure at point C)}}
+	\includegraphics[scale=.5]{../Images/MCGRINSEM}
+	\caption{\emph{SEM image of the cross section profile of the microcavities with GRIN.
+The measured thicknesses of the complete multi-film structures showed good agreement with the simulations taken from $ V = 0.53J ^ {0.79} $ where $d_j=Vt_j$ ($j=H,L$), which are the thicknesses of each of the monolayer of the porous silicon microcavity GRIN at the measurement points and the total thickness we find it as $d_{_{i}} = (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$ defining $ i = $ A, B, C.
+Which resulted in (measured / simulation) $ 2.25 / 2.31 \ \ \mu m $ (for structure at Point A), $ 2.17 / 2.08 \ \ \mu m $ (for structure at point B) and $ 1.87 / 1.65 \ \ \mu m $ (for structure at point C)}}
 	\label{fig:MCGRIN4}
@@
 
-For the Fig. \ref{fig:MCGRIN4} shows the SEM cross-sectional images of
-the PSi samples used in this work. Relatively small interface
-roughness and a clear contrast between the high and low porosity of
-the microcavity measured at different points (A, B and C), showing the
-change in thickness in each of these. The measured thicknesses of the
-complete multi-film structures showed good agreement with the
-simulations taken from $ V = 0.53J^{0.79} $ where $d_j=Vt_j$
-($j=H,L$), which are the thicknesses of each of the monolayer of the
-porous silicon microcavity GRIN at the measurement points and the
-total thickness we find it as $d_{_{i}} =
-(N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$ defining $ i
-= $ A, B, C. Which resulted in (measured / simulation) $ 2.25 / 2.31 \
-\ \mu m $ (for structure at Point A), $ 2.17 / 2.08 \ \ \mu m $ (for
-structure at point B) and $ 1.87 / 1.65 \ \ \mu m $ (for structure at
-point C).
-Being able to say that for each measurement point corresponds
-different calculated current densities, which correspond to different
-thicknesses at the end of manufacturing, clearly seeing the lateral
-gradient product of our experiment.
+For the Fig.
+\ref{fig:MCGRIN4} shows the SEM cross-sectional images of the PSi samples used in this work.
+Relatively small interface roughness and a clear contrast between the high and low porosity of the microcavity measured at different points (A, B and C), showing the change in thickness in each of these.
+The measured thicknesses of the complete multi-film structures showed good agreement with the simulations taken from $ V = 0.53J^{0.79} $ where $d_j=Vt_j$ ($j=H,L$), which are the thicknesses of each of the monolayer of the porous silicon microcavity GRIN at the measurement points and the total thickness we find it as $d_{_{i}} = (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$ defining $ i = $ A, B, C.
+Which resulted in (measured / simulation) $ 2.25 / 2.31 \ \ \mu m $ (for structure at Point A), $ 2.17 / 2.08 \ \ \mu m $ (for structure at point B) and $ 1.87 / 1.65 \ \ \mu m $ (for structure at point C).
+Being able to say that for each measurement point corresponds different calculated current densities, which correspond to different thicknesses at the end of manufacturing, clearly seeing the lateral gradient product of our experiment.
 
+\newpage
 \section{conclusion}
-The necessary expressions for the potential components were derived,
-finding a relationship of the tip of the counter electrode that acts
-similarly as a point charge and the current density for a geometry in
-a rectangular electrolytic box and we solve the electrostatic
-equations with suitable boundary conditions. Resulting in an
-electrostatic model for  Photonics crystals with a refractive index
-with gradient (EMPCGRIN).
-It is the first time that the formalism mentioned here has been
-applied to find the current density to design porous silicon. The
-shape of the electrode, the area of the cell produces a visible
-decrease in the size and density of the pores. Additionally,
-optimizing the structural properties for a single structure we could
-have a gradient with different depths, reflactances at differents
-measurement points. In this way, we were able to simulate the direct
-relationship of the attack speed with the current density at the
-points  the samples of interest. At the same time, we developed a
-characterization between porosity, refractive indices of porous
-silicon, with the different current densities. And in the end we were
-able to design and characterize Porous Silicon microcavities with
-refractive indices with gradients, which for each measurement point
-correspond to different calculated current densities, which correspond
-to different thicknesses, clearly seeing the lateral gradient product
-of our experiment.
+The necessary expressions for the potential components were derived, finding a relationship of the tip of the counter electrode that acts similarly as a point charge and the current density for a geometry in a rectangular electrolytic box and we solve the electrostatic equations with suitable boundary conditions.
+Resulting in an electrostatic model for  Photonics crystals with a refractive index with gradient (EMPCGRIN).
+It is the first time that the formalism mentioned here has been applied to find the current density to design porous silicon.
+The shape of the electrode, the area of the cell produces a visible decrease in the size and density of the pores.
+Additionally, optimizing the structural properties for a single structure we could have a gradient with different depths, reflactances at differents measurement points.
+In this way, we were able to simulate the direct relationship of the attack speed with the current density at the points  the samples of interest.
+At the same time, we developed a characterization between porosity, refractive indices of porous silicon, with the different current densities.
+And in the end we were able to design and characterize Porous Silicon microcavities with refractive indices with gradients, which for each measurement point correspond to different calculated current densities, which correspond to different thicknesses, clearly seeing the lateral gradient product of our experiment.
 \section{Acknowledgments}
@@
 \bibliographystyle{unsrt}
+ \small{
 \begin{thebibliography}{X}
-  % forma de biblio es MLA
-\bibitem{I1} P. Yeh,\textquotedblleft \emph{Optical Waves in Layered
-    Media} \textquotedblright, 2nd edn. (Wiley-Interscience
-  Publication,
+	%forma de biblio es MLA
+\bibitem{I1} P. Yeh,\textquotedblleft \emph{Optical Waves in Layered Media} \textquotedblright, 2nd edn. (Wiley-Interscience Publication,
 USA, 2005).
-\bibitem{I2}Canham, L. 1997.\textquotedblleft \emph{Properties of
-    Porous Silicon} \textquotedblright. Edited by Canham L. DERA,
-  Malvern, UK.
-\bibitem{I3}{Beale, M.I.J, J.D Benjamin, M.J Uren, N.G Chew, and A.G
-    Cullis. 1985. \emph{ \textquotedblleft An Experimental and
-      Theoretical Study of the Formation and Microstructure of
-      Porous Silicon.\textquotedblright} J. Crystal Growth 73:
-    622?36. doi:10.1021/jp0706984. }
-\bibitem{I4}Canham, L. T. 1990. \emph{\textquotedblleft Silicon
-    Quantum Wire Array Fabrication by Electrochemical and Chemical
-    Dissolution of Wafers.\textquotedblright} Applied Physics
-  Letters 57 (10): 1046. doi:10.1063/1.103561.
-\bibitem{I5} J. D. Joannopoulos et al.,\textquotedblleft
-  \emph{Photonic Crystals: Molding the Flow of
-    Light}\textquotedblright, 2nd edn.
+\bibitem{I2}Canham, L. 1997.\textquotedblleft \emph{Properties of Porous Silicon} \textquotedblright. Edited by Canham L. DERA, Malvern, UK.
+\bibitem{I3}{Beale, M.I.J, J.D Benjamin, M.J Uren, N.G Chew, and A.G Cullis.
+1985.
+\emph{ \textquotedblleft An Experimental and Theoretical Study of the Formation and Microstructure of Porous Silicon.\textquotedblright} J.
+Crystal Growth 73: 622?36.
+doi:10.1021/jp0706984.
+}
+\bibitem{I4}Canham, L.
+T.
+1990.
+\emph{\textquotedblleft Silicon Quantum Wire Array Fabrication by Electrochemical and Chemical Dissolution of Wafers.\textquotedblright} Applied Physics Letters 57 (10): 1046.
+doi:10.1063/1.103561.
+
+\bibitem{I5} J. D. Joannopoulos et al.,\textquotedblleft \emph{Photonic Crystals: Molding the Flow of Light}\textquotedblright, 2nd edn.
 (Princeton University Press, UK, 2008).
-\bibitem{I6} E. Yablonovitch, \textquotedblleft \emph{Photonic
-    band-gap structures,}\textquotedblright J. Opt. Soc. Am. B 10,
-  283-295 (1993)
-\bibitem{I7} Ilyas, S., and M. Gal.  \textquotedblleft \emph{
-    Optical devices from porous silicon having continuously varying
-    refractive index.}\textquotedblright Journal of Materials
-  Science: Materials in Electronics 18.1 (2007): 61-64.
-\bibitem{I8} Tran, P. \textquotedblleft \emph{Optical switching with
-    a nonlinear photonic crystal: a numerical
-    study.}\textquotedblright Optics letters 21.15 (1996):
-  1138-1140.
-\bibitem{I9} Ariza-Flores, A. David, L. M. Gaggero-Sager, and
-  V. Agarwal. \textquotedblleft \emph{White metal-like
-    omnidirectional mirror from porous silicon dielectric
-    multilayers.}\textquotedblright Applied Physics Letters 101.3
-  (2012): 031119.
-\bibitem{I10} Johnson, Steven G., et al.  \textquotedblleft
-  \emph{Linear waveguides in photonic-crystal
-    slabs.}\textquotedblright Physical Review B 62.12 (2000): 8212.
+\bibitem{I6} E. Yablonovitch, \textquotedblleft \emph{Photonic band-gap structures,}\textquotedblright J. Opt. Soc. Am. B 10, 283-295 (1993)
+\bibitem{I7} Ilyas, S., and M.
+Gal.
+\textquotedblleft \emph{ Optical devices from porous silicon having continuously varying refractive index.}\textquotedblright Journal of Materials Science: Materials in Electronics 18.1 (2007): 61-64.
+\bibitem{I8} Tran, P. \textquotedblleft \emph{Optical switching with a nonlinear photonic crystal: a numerical study.}\textquotedblright Optics letters 21.15 (1996): 1138-1140.
+ \bibitem{I9} Ariza-Flores, A.
+David, L.
+M.
+Gaggero-Sager, and V.
+Agarwal.
+\textquotedblleft \emph{White metal-like omnidirectional mirror from porous silicon dielectric multilayers.}\textquotedblright Applied Physics Letters 101.3 (2012): 031119.
+\bibitem{I10} Johnson, Steven G., et al.  \textquotedblleft \emph{Linear waveguides in photonic-crystal slabs.}\textquotedblright Physical Review B 62.12 (2000): 8212.
 
-  % asimetrica
-\bibitem{I101}Collins, Boyce E., et al. \textquotedblleft \emph{
-    Determining protein size using an electrochemically machined
-    pore gradient in silicon.}\textquotedblright Advanced Functional
-  Materials 12.3 (2002): 187-191.
+%asimetrica 
+\bibitem{I101}Collins, Boyce E., et al.
+\textquotedblleft \emph{ Determining protein size using an electrochemically machined pore gradient in silicon.}\textquotedblright Advanced Functional Materials 12.3 (2002): 187-191.
 
-\bibitem{I102} Khung, Y. L., G. Barritt, and
-  N. H. Voelcker. \textquotedblleft \emph{Using continuous porous
-    silicon gradients to study the influence of surface topography
-    on the behaviour of neuroblastoma cells.}\textquotedblright
-  Experimental cell research 314.4 (2008): 789-800.
+\bibitem{I102} Khung, Y.
+L., G.
+Barritt, and N.
+H.
+Voelcker.
+\textquotedblleft \emph{Using continuous porous silicon gradients to study the influence of surface topography on the behaviour of neuroblastoma cells.}\textquotedblright Experimental cell research 314.4 (2008): 789-800.
 
-\bibitem{I103} Clements, Lauren R., et al. \textquotedblleft
-  \emph{Mesenchymal stem cell attachment to peptide density
-    gradients on porous silicon generated by
-    electrografting.}\textquotedblright physica status solidi (a)
-  208.6 (2011): 1440-1445.
+\bibitem{I103} Clements, Lauren R., et al.
+\textquotedblleft \emph{Mesenchymal stem cell attachment to peptide density gradients on porous silicon generated by electrografting.}\textquotedblright physica status solidi (a) 208.6 (2011): 1440-1445.
 
-\bibitem{I104} Wang, Peng-Yuan, et al. \textquotedblleft
-  \emph{Screening the attachment and spreading of bone
-    marrow-derived and adipose-derived mesenchymal stem cells on
-    porous silicon gradients.}\textquotedblright Rsc Advances 2.33
-  (2012): 12857-12865.
-\bibitem{I11} Canham, L. \textquotedblleft \emph{Properties of
-    Porous Silicon.}\textquotedblright Edited by Canham L. DERA,
-  Malvern, UK. (1997).
-\bibitem{I12} Li, Yang Yang, Peter Kim, and Michael J
-  Sailor.\textquotedblleft \emph{Painting a Rainbow on Silicon A
-    Simple Method to Generate a Porous Silicon Band Filter
-    Gradient}\textquotedblright Physica Status Solidi (a) 1618 (8):
-  161618. doi:10.1002/pssa.200461200.(2005)
-\bibitem{I13} Khung, Y L, and N H
-  Voelcker. 2009.\textquotedblleft\emph{ Multidirectional Lateral
-    Gradient Films with Position-Dependent Photonic Signatures Made
-    from Porous Silicon.}\textquotedblright Optical Materials 32
-  (1): 23442. doi:10.1016/j.optmat.2009.07.015.
+\bibitem{I104} Wang, Peng-Yuan, et al.
+\textquotedblleft \emph{Screening the attachment and spreading of bone marrow-derived and adipose-derived mesenchymal stem cells on porous silicon gradients.}\textquotedblright Rsc Advances 2.33 (2012): 12857-12865.
+
+ \bibitem{I11} Canham, L. \textquotedblleft \emph{Properties of Porous Silicon.}\textquotedblright Edited by Canham L. DERA, Malvern, UK. (1997).
+ \bibitem{I12} Li, Yang Yang, Peter Kim, and Michael J Sailor.\textquotedblleft \emph{Painting a Rainbow on Silicon A Simple Method to Generate a Porous Silicon Band Filter Gradient}\textquotedblright Physica Status Solidi (a) 1618 (8): 161618.
+doi:10.1002/pssa.200461200.(2005)
+ \bibitem{I13} Khung, Y L, and N H Voelcker.
+2009.\textquotedblleft\emph{ Multidirectional Lateral Gradient Films with Position-Dependent Photonic Signatures Made from Porous Silicon.}\textquotedblright Optical Materials 32 (1): 23442.
+doi:10.1016/j.optmat.2009.07.015.
  \bibitem{I14}  Khung, Y L, G Barritt, and N H Voelcker.
-  \textquotedblleft \emph{Using Continuous Porous Silicon Gradients
-    to Study the Influence of Surface Topography on the Behaviour of
-    Neuroblastoma Cells.}\textquotedblright Experimental Cell
-  Research 314 (4): 78900. doi:10.1016/j.yexcr.2007.10.015.(2008.)
-\bibitem{I15} Collins, B.E., K.-P.S. Dancil, G. Abbi, and
-  M.J. Sailor. 2002.\textquotedblleft \emph{Determining Protein Size
-    Using an Electrochemically Machined Pore Gradient in
-    Silicon.}\textquotedblright Advanced Functional Materials 12 (3):
-  187. doi:10.1002/1616-3028(200203)12:3,187::AID-ADFM187,3.0.CO;2-E.(
-  2002.)
+\textquotedblleft \emph{Using Continuous Porous Silicon Gradients to Study the Influence of Surface Topography on the Behaviour of Neuroblastoma Cells.}\textquotedblright Experimental Cell Research 314 (4): 78900.
+doi:10.1016/j.yexcr.2007.10.015.(2008.)
+\bibitem{I15} Collins, B.E., K.-P.S.
+Dancil, G.
+Abbi, and M.J.
+Sailor.
+2002.\textquotedblleft \emph{Determining Protein Size Using an Electrochemically Machined Pore Gradient in Silicon.}\textquotedblright Advanced Functional Materials 12 (3): 187.
+doi:10.1002/1616-3028(200203)12:3,187::AID-ADFM187,3.0.CO;2-E.( 2002.)
 
-\bibitem{I16} Ocier, C. R., Krueger, N. A., Zhou, W. and  Braun,
-  P. V. (2017).\textquotedblleft \emph{Tunable visibly transparent
-    optics derived from porous silicon.}\textquotedblright ACS
-  Photonics, 4(4), 909-914.
-\bibitem{I17} Dariani RS, Ebrahimnasab S (2014). \textquotedblleft
-  \emph{Root Mean Square Roughness of Nano Porous Silicon by
-    Scattering Spectra.}\textquotedblright The
+\bibitem{I16} Ocier, C.
+R., Krueger, N.
+A., Zhou, W.
+and  Braun, P.
+V.
+(2017).\textquotedblleft \emph{Tunable visibly transparent optics derived from porous silicon.}\textquotedblright ACS Photonics, 4(4), 909-914.
+%ecuacion
+\bibitem{I17} Dariani RS, Ebrahimnasab S (2014). \textquotedblleft \emph{Root Mean Square Roughness of Nano Porous Silicon by Scattering Spectra.}\textquotedblright The
 European Physical Journal Plus 129: 129.
-\bibitem{I18} Lerondel G, Romestain R (1997).\textquotedblleft
-  \emph{Roughness of the Porous Silicon Dissolution
-    Interface.}\textquotedblright Journal of Applied Physics 81:
-  61716178.
-\bibitem{I19} Lérondel G, Romestain R, Barret S
-  (1997).\textquotedblleft \emph{Quantitative Analysis of the Light
-    Scattering Effect on Porous Silicon
-    Optical Measurements.}\textquotedblright Thin Solid Films 297:
-  114?117.
+\bibitem{I18} Lerondel G, Romestain R (1997).\textquotedblleft \emph{Roughness of the Porous Silicon Dissolution Interface.}\textquotedblright Journal of Applied Physics 81:  61716178.
+\bibitem{I19} Lérondel G, Romestain R, Barret S (1997).\textquotedblleft \emph{Quantitative Analysis of the Light Scattering Effect on Porous Silicon 
+Optical Measurements.}\textquotedblright Thin Solid Films 297: 114?117.
 
 \bibitem{I20} Thei, W. \textquotedblleft \emph{Optical Properties of porous silicon.}\textquotedblright Surf. Sci. Rep. 1997, 29, 91?93. 
-\bibitem{I21} Van Groesen, E.; Sopaheluwakan, A.; Andonowati,
-  A. \textquotedblleft  \emph{Direct characterization of states and
-    modes in defect grating structures.}\textquotedblright
-  J. Nonlinear Opt. Phys. Mater. 2004, 13, 155173.
+\bibitem{I21} Van Groesen, E.; Sopaheluwakan, A.; Andonowati, A.
+\textquotedblleft  \emph{Direct characterization of states and modes in defect grating structures.}\textquotedblright J.
+Nonlinear Opt.
+Phys.
+Mater.
+2004, 13, 155173.
+% \textquotedblleft \textquotedblright
 
-\bibitem{In} Mazzoleni, C., and L. Pavesi. \textquotedblleft
-  \emph{Application to optical components of dielectric porous silicon
-    multilayers.}\textquotedblright Applied Physics Letters 67.20
-  (1995): 2983-2985
+\bibitem{In} Mazzoleni, C., and L.
+Pavesi.
+\textquotedblleft  \emph{Application to optical components of dielectric porous silicon multilayers.}\textquotedblright Applied Physics Letters 67.20 (1995): 2983-2985
 
 \end{thebibliography}
+%capitulos1111111111111111111111
 

### 2020-06-09 paper.tex
Hice los cambios y modificaciones de la celda, los estilo de letra de los pie de imagenas

@@
   \centering
-  \includegraphics[scale=.4]{Images/celdan}
+  \includegraphics[width=\textwidth]{Images/celdan1}
   \caption{Prism shaped electrolytic cell with a rectangular base of
@@
 \end{equation}
-This problem may be solved readily using image charge theory
+This problem may be solved readily using image charge theory \cite{T1,T2}
 \notaL{ref}. The potential within the electrolytic cell coincides the
@@
   \centering
-  \includegraphics[scale=.6]{Images/celd1}
-  \caption{\emph{Diagram shows that there is a positive (real) plane $
+  \includegraphics[width=\textwidth]{Images/celd1}
+  \caption{Diagram shows that there is a positive (real) plane $
       z_0 $, a negative image at $ -z_0 $ below the conductor ($ z = 0
@@
       negative plate at $ 2c + z_0 $, the image is repeated vertically
-      with the period $ L_z = 4c $}}
+      with the period $ L_z = 4c $}
   \label{fig:Celda1}
@@
   \centering
-  \includegraphics[scale=0.6]{Images/DE1}
-\caption{\emph{Schematic of the experimental set-up for
+  \includegraphics[width=\textwidth]{Images/DE1}
+\caption{Schematic of the experimental set-up for
       fabrication of porous silicon with GRIN. (a) Represents an
@@
       electrochemically attacked porous silicon seen in three
-      different regions as mentioned above. }}
+      different regions as mentioned above. }
     \label{fig:DE1}
@@
 \section{Discussion and Results}
-\subsection{Simulation of the EMPCGRIN model}
+\subsection{Simulation of  the current density}
  To test the developed  idea in the theoretical section, we find a
@@
   \centering
-  \includegraphics[scale=0.7]{Images/G123}
-  \caption{\emph{ Simulation to calculate the current density in
+  \includegraphics[width=\textwidth]{Images/G123}
+  \caption{Simulation to calculate the current density in
       a structure with gradient refractive index (GRIN) produced
@@
       0.62 \ \ cm $, with an electrode height $ Z_0 = 0.96 \ \
-      cm $} Eq. (\ref{Eq:J})}.
+      cm $ Eq. (\ref{Eq:J})}.
   \label{fig:DR1}
@@
 	\centering
-	\includegraphics[scale=.3]{Images/celdan2}
-	\caption{\emph{ Mechanical 3D modeling, design of the
+	\includegraphics[width=\textwidth]{Images/celdan2}
+	\caption{Mechanical 3D modeling, design of the
             electrochemical cell where we can see the shape of a prism
@@
             $) and a height ( $ 1.2 \ \ cm $) a) Complete cell b) Cell
-            without top cover and c) Top view}}
+            without top cover and c) Top view}
 	\label{fig:por1}
@@
   \centering
-  \includegraphics[scale=.5]{Images/SPgrin51}
-  \caption{\emph{a) Silicon sample attacked with an electrolytic
+  \includegraphics[width=\textwidth]{Images/SPgrin51}
+  \caption{a) Silicon sample attacked with an electrolytic
       mixture of aqueous hydrofluoric acid (HF) (concentration:
@@
       \ref{Eq:Brugg}. for different porosities at each point, A
-      (P = 0.44), B (P = 0.42) and C (P = 0.40) } }
+      (P = 0.44), B (P = 0.42) and C (P = 0.40) }
   \label{fig:DR3}
@@
   \centering
-  \includegraphics[scale=.5]{Images/semD11}
-  \caption{\emph{Characterization of a monolayer of PS GRIN G1
+  \includegraphics[width=\textwidth]{Images/semD11}
+  \caption{Characterization of a monolayer of PS GRIN G1
       with an initial current of $ 5 \ \ mA $, seeing the
@@
       = 1320 \ \ nm $, $ d (B) = 997 \ \ nm $ and $ d (C) = 605
-      \ \ nm $ } }
+      \ \ nm $ }
   \label{fig:DR4}
@@
    \centering
-   \includegraphics[scale=.7]{Images/grinJDR}
-   \caption{\emph{a) It is the relation of the current density $
+   \includegraphics[width=\textwidth]{Images/grinJDR}
+   \caption{a) It is the relation of the current density $
        J (mA / cm ^ 2) $ normalized with the electric current $ I
@@
        600 \ \ s) $ y $ G2 (t = 200 \ \ s) $, depending on the
-       axis $ a $ $ (0.1 ... 2.0 \ \ cm) $ } }
+       axis $ a $ $ (0.1 ... 2.0 \ \ cm) $ }
    \label{fig:JDR}
@@
   \centering
-  \includegraphics[scale=.6]{Images/grinJD31}
-  \caption{\emph{The relationship of samples $ G1 (I = 5 mA) $ and $
+  \includegraphics[width=\textwidth]{Images/grinJD31}
+  \caption{The relationship of samples $ G1 (I = 5 mA) $ and $
       G2 (I = 40 mA) $ were obtained to find: a) Attack speed with
@@
       density current. With this we have the calibration curves for
-      the manufacture of any GRIN porous silicon structure   } }
+      the manufacture of any GRIN porous silicon structure   }
   \label{fig:Indr1}
@@
 	\centering
-	\includegraphics[scale=0.4]{Images/MicrGrin}
-	\caption{\emph{Diagram of a microcavity of porous silicon
+	\includegraphics[width=\textwidth]{Images/MicrGrin}
+	\caption{Diagram of a microcavity of porous silicon
             GRIN. Alternate layers are obtained of high (H) refractive
@@
             (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) +
-            (2d_{_{Hi}})$. }}
+            (2d_{_{Hi}})$. }
 	\label{fig:MCGRIN0}
@@
   \centering
-  \includegraphics[scale=.5]{Images/MCGRIN2}
-  \caption{\emph{a) Three locations at different points are
+  \includegraphics[width=\textwidth]{Images/MCGRIN2}
+  \caption{a) Three locations at different points are
       considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B
@@
       function of the current density at each measurement point,
-      see Table \ref{tabla:1}. }}
+      see Table \ref{tabla:1}. }
   \label{fig:MCGRIN3}
@@
    \centering
-   \includegraphics[scale=.5]{Images/MCGRINSEM}
-   \caption{\emph{SEM image of the cross section profile of the
+   \includegraphics[width=\textwidth]{Images/MCGRINSEM}
+   \caption{SEM image of the cross section profile of the
        microcavities with GRIN. The measured thicknesses of the
@@
        A), $ 2.17 / 2.08 \ \ \mu m $ (for structure at point B) and $
-       1.87 / 1.65 \ \ \mu m $ (for structure at point C)}}
+       1.87 / 1.65 \ \ \mu m $ (for structure at point C)}
 	\label{fig:MCGRIN4}
@@
   Photonics, 4(4), 909-914.
+
+  \bibitem{T1}Jackson, John David. \textquotedblleft 
+  \emph{Classical electrodynamics.}\textquotedblright (1999): 841-842.
+
+\bibitem{T2}Griffiths, David J. \textquotedblleft 
+\emph{Introduction to electrodynamics.}\textquotedblright 
+ New Jersey: Prentice Hall, 1962.
+
 \bibitem{I17} Dariani RS, Ebrahimnasab S (2014). \textquotedblleft
@@
 
-\bibitem{I20} Thei, W. \textquotedblleft \emph{Optical Properties of porous silicon.}\textquotedblright Surf. Sci. Rep. 1997, 29, 91?93.
+\bibitem{I20} Thei, W. \textquotedblleft \emph{Optical Properties of porous silicon.}
+\textquotedblright Surf. Sci. Rep. 1997, 29, 91?93.
 \bibitem{I21} Van Groesen, E.; Sopaheluwakan, A.; Andonowati,

### 2020-06-09 paper.tex
Revise theory up to full potential

--- 2020-06-08 paper.tex
@@
     which is indicated by wide dashed lines, and with a basis of four
-    charges $q_0$ and another four charges $-q_0$.}
+    charges $q_0$ and another four charges $-q_0$. Within this cell,
+    we indicate its $G=0$ contribution to the electric field (solid
+    arrows, see text).}
   \label{fig:sideview}
@@
 Poisson's equation within an orthothombic lattice of size
-$2a\times2b\times4c$ with a basis of 16 point charges arranged in
-positive and negative planes.
-
-\textbf {Problem considerations}: The problem is the potential, the
-field and the current produced by a periodic 2D network of a real load
-and all its images. The potential due to a periodic network is
-automatically found in the plane making a sum of 2D Fourier.
+$2a\times2b\times4c$ with a basis of 16 point charges of charge $\pm
+q_0$ arranged in positive and negative planes.
+
+The electrostatic potential produced by an infinite array of
+charges expressed as a sum in real space of Coulomb terms has ill
+convergence properties. The potential can be obtained
+using the Ewald summation technique \notaL{ref}, which yields two rapidly converging
+series, one in real space and another one in reciprocal space.
+Nevertheless, as we need the potential and the field to obtain the
+current density on the surface of the sample on which there are no
+real nor image charges, we may perform a somewhat simpler planewise
+summation, where we first obtain the potential and field produced by a
+simple periodic lattice of charges using a fast convergent sum over the 2D
+reciprocal vectors, and then sum over the charges that form the basis
+of the 2D {\em crystal} plane and finally sum over all the planes \notaL{ref}.
+
+We consider first a system made of identical unit charges
+ocuppying the positions $\bm R$ of a 2D Bravais lattice $\{\bm R\}$,
+which we will take as a rectangular lattice with lattice parameters
+$2a$ and $2b$, and lying, for the time being, at the $z=0$ plane.
+The potential it produces obeys
+\begin{equation}
+  \label{eq:poissonRed}
+  \nabla^2\varphi(\bm r)=-4\pi\sum_{\bm R}\delta(\bm r_\|-\bm
+  R)\delta(z)=-\frac{4\pi}{A}\sum_{\bm G}e^{i\bm G\cdot\bm r_\|}\delta(z),
+\end{equation}
+where $\bm r_\|$ is the projection of the observation position $\bm
+r=(x,y,z)$ onto the $xy$ plane,
+$\delta(\ldots)$ is Dirac's delta function, $\{\bm G\}$ is the
+reciprocal lattice defined through $e^{i\bm G\cdot\bm R}=1$ for all
+$\bm R$ and $\bm G$, $A=4ab$ is the area of the unit cell
+and we used the Fourier representation of the 2D
+periodically repeated delta function. We introduce a 2D Fourier representation for
+the potential \notaL{Checar consistencia entre phi y varphi en todos lados}
+\begin{equation}
+  \label{eq:phifourier}
+  \phi(\bm r)=\sum_{\bm G}\phi_{\bm G}(z)e^{i\bm G\cdot\bm r_\|}
+\end{equation}
+where $\phi_{\bm G}(z)$ is the Fourier coefficient of the potential at
+the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
+ordinary differential equation \notaL{El signo estaba mal. Chécalo.}
  \begin{eqnarray}
- \rho(\vec{r}) =q \displaystyle\sum_{R}  \ \delta
-  (\vec{r}-\vec{R}-\vec{r}_0) =\dfrac{q}{A}  \displaystyle\sum_{G}
-  e^{i G \cdot (\vec{r}-\vec{r}_{0})} \delta (z-z_0)
-\end{eqnarray}
-Where $ {R} $ is the 2D Bravais network and $ {G} $ its reciprocal
-network. It is written $ \phi (\vec{r}) = \displaystyle \sum _
-{\vec{G}}  \phi_{_{G}}(z) e^{i \vec {G} \cdot \vec {r}} $. So the
-Poisson equation $ \nabla^2 \phi = -4 \pi \displaystyle
-\sum_{\vec{R}} \delta (\vec{r} - \vec{R} - \vec{r}_0) $.
-Becomes
+ \frac{d^2}{dz^2}\phi_{\bm G}(z)-G^2\phi_{_{G}}(z)=
+   -\frac{4 \pi}{A} \delta(z),
+ \end{eqnarray}
+an homogeneous equation for $z\ne0$ which may be trivially
+solved. After applying boundary conditions at $z=0$ and regularity
+conditions at infinity, we obtain
+\begin{equation}
+  \label{eq:phiG}
+  \phi_{\bm G}(z)=
+  \begin{cases}
+    -\dfrac{2\pi}{A}\abs{z}&\text{if }G=0,\\
+    \dfrac{2 \pi}{AG}  e^{- G \abs{z}}&\text{if }G\neq 0.
+  \end{cases}
+\end{equation}
+The case $G=0$ corresponds to the potential produced by a uniformly charged plane,
+while the case $G\ne 0$ is the symmetric solution that decays far from
+the source plane. Substituting into Eq. \eqref{eq:phifourier} yields
 \begin{eqnarray}
- \dfrac{\partial^2 \phi_{_{G}}(z)}{\partial z^2}+ G^2\phi_{_{G}}(z)=
-   -\dfrac{4 \pi}{A}  q   e^{i \vec{G} \cdot \vec{r}_{_0}} \delta
-   (z-z_0)
- \end{eqnarray}
-Solving the homogeneous equation above and below $ z = z_0 $, using
-symmetry and conditions at $ \pm \infty $ we obtain $ \phi_{_{G}} =
-\phi_{_{G}}^{0} e^{ G \abs{z-z_0}} \ \ \ \ \ (G \neq 0) $. And
-adjusting the singularity
- \begin{eqnarray}
- \phi_{_{G}}(z)= \dfrac{2 \pi q}{AG}  e^{- G \abs{z-z_0}} e^{-i
-   \vec{G} \cdot \vec{r}_{_0}} \ \ \ \ \ (G\neq 0)
- \end{eqnarray}
-For the case $ G = 0 $ is similar $ \phi_{_{G = 0}} (z) = \dfrac{-2
-  \pi q}{A} \abs{z-z_0} + K, $ $ \ \ $ (K is a constant). Here $ A =
-L_x L_y $ is the unit cell area
- \begin{eqnarray}
- \phi(\vec{r}) = K-\dfrac{2 \pi q}{A}  \abs{z-z_0} +\dfrac{2 \pi
-   q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} e^{- G \abs{z-z_0}}
-   e^{i \vec{G} \cdot \vec{r}-\vec{r}_0}
- \end{eqnarray}
-Adding all the images loads,
+  \label{eq:phiG1}
+ \phi(\bm r) = -\frac{2 \pi}{A}  \abs{z} +{\sum_{\bm G}}' \frac{2 \pi
+   }{AG} e^{- G \abs{z}} e^{i \bm G\cdot\bm r_\|},
+ \end{eqnarray}
+where the prime indicates that the term $G=0$ should be ommited from
+the sum.
+
+We consider now the basis of our 2D lattice, with equal charges at the
+four positions $(\pm x_0, \pm y_0)$. Each of the corresponding four
+sublattices produces a potential as that in Eq. \eqref{eq:phiG1} but
+shifted by the corresponding basis vector, yielding
+\begin{equation}
+  \label{eq:phiG4}
+  \phi(\bm r) = -\frac{8\pi}{A} \abs{z}
+    +{\sum_{\bm G}}' \frac{8\pi}{AG} e^{- G \abs{z}}\cos(G_x x_0)
+    \cos(G_y y_0) e^{i \bm G\cdot\bm r_\|}.
+\end{equation}
+Finally, we shift the origin of Eq. \eqref{eq:phiG4} vertically to each of the planes shown in
+Fig. \ref{fig:sideview} and multiply by the corresponding charge $q_0$
+or $-q_0$ to obtain the contribution to the total potential. The charge $q_0$ corresponds to
+the planes with heights of the form $z_0+4nc$ and $-z_0+(4n+2)c$, with
+$n=\ldots-2,-1,0,1,2\ldots$ an arbitrary integer, while the charge
+$-q_0$ corresponds to the planes with height $z_0+(4n+2)c$ and
+$-z_0+(4n+4)c$.
+
+We concentrate our attention only on the region $a\le z<z_0$. From
+Fig. \ref{fig:sideview} we see that the $G=0$
+field has contributions only from the charges at $z_0$ and their
+images ant $-z_0$, this contribution is like that of a parallel plate
+capacitor $E_{0z}=-4\pi q_0/ab=-16\pi q_0/A$, which corresponds to the
+potential $\phi_0=16\pi q_0 z/A$. Other contiguous planes of with opposite charges
+contribute to the field elsewhere. The contributions to the potential
+from the $G\ne0$ are simple geometric sums that may be summed
+analytically over $n$ and yield the total potential
+\begin{equation}
+  \label{eq:phitot}
+  \begin{split}
+    \phi(\bm r)=&\frac{16\pi q_0}{A}\biggl(z+{\sum_{\bm G}}'\frac{2\sinh
+      Gc}{G \sinh 2Gc}\cosh G(c-z_0)\cos G_x x_0 \cos G_y y_0\\
+    &\times \sinh Gz\, e^{i\bm G\cdot\bm r_\|}\biggr).
+  \end{split}
+\end{equation}
+
+\notaL{Aquí voy. Checa la ecuación previa}
+
+In our case of
+interest we take $0\le z < z_0$ and thus write
+
   \begin{eqnarray}\label{Eq:EC11}

### 2020-06-09 paper.tex

--- 2020-06-09 paper.tex
@@
 \usepackage{bm}
+\usepackage{ulem} %opcional para la correcciones
 \newcommand{\abs}[1]{\lvert#1\rvert}
@@
     just the tip uncovered and located at $ \vec{r}_0 $ within the
-    liquid.\notaL{Quité el tipo de letra del pie de figura. Que la pongan en la
-      revista.}\notaL{En la punta pusiste dos esferas. Quítalas y sólo
+    liquid.\notaL{\sout{Quité el tipo de letra del pie de figura. Que la pongan en la
+      revista.}}\notaL{\sout{En la punta pusiste dos esferas. Quítalas y sólo
     pon un puntito dorado del ancho del cable. Muestra que la base
-    está aterrizada}\notaL{Indica el voltaje y la
-    corriente}\notaL{¿Está bien la polaridad de la batería?}}
+    está aterrizada}}\notaL{\sout{Indica el voltaje y la
+    corriente}}\notaL{\sout{¿Está bien la polaridad de la batería?}}}
   \label{f:celda}
@@
 This problem may be solved readily using image charge theory \cite{T1,T2}
-\notaL{ref}. The potential within the electrolytic cell coincides the
+\notaL{\sout{ref}}. The potential within the electrolytic cell coincides the
 the field within an infinite vacuum containing the point charge
@@
 Poisson's equation within an orthothombic lattice of size
-$2a\times2b\times4c$ with a basis of 16 point charges arranged in
-positive and negative planes.
-
-\textbf {Problem considerations}: The problem is the potential, the
-field and the current produced by a periodic 2D network of a real load
-and all its images. The potential due to a periodic network is
-automatically found in the plane making a sum of 2D Fourier.
+$2a\times2b\times4c$ with a basis of 16 point charges of charge $\pm
+q_0$ arranged in positive and negative planes.
+
+The electrostatic potential produced by an infinite array of
+charges expressed as a sum in real space of Coulomb terms has ill
+convergence properties. The potential can be obtained
+using the Ewald summation technique \cite{T3,T4,T5}\notaL{\sout{ref}}, which yields
+ two rapidly convergingseries, one in real space and another one in reciprocal space.
+Nevertheless, as we need the potential and the field to obtain the
+current density on the surface of the sample on which there are no
+real nor image charges, we may perform a somewhat simpler planewise
+summation, where we first obtain the potential and field produced by a
+simple periodic lattice of charges using a fast convergent sum over the 2D
+reciprocal vectors, and then sum over the charges that form the basis
+of the 2D {\em crystal} plane and finally sum over all the
+ planes \cite{T6,T7} \notaL{\sout{ref}}.
+
+We consider first a system made of identical unit charges
+ocuppying the positions $\bm R$ of a 2D Bravais lattice $\{\bm R\}$,
+which we will take as a rectangular lattice with lattice parameters
+$2a$ and $2b$, and lying, for the time being, at the $z=0$ plane.
+The potential it produces obeys
+\begin{equation}
+  \label{eq:poissonRed}
+  \nabla^2\varphi(\bm r)=-4\pi\sum_{\bm R}\delta(\bm r_\|-\bm
+  R)\delta(z)=-\frac{4\pi}{A}\sum_{\bm G}e^{i\bm G\cdot\bm r_\|}\delta(z),
+\end{equation}
+where $\bm r_\|$ is the projection of the observation position $\bm
+r=(x,y,z)$ onto the $xy$ plane,
+$\delta(\ldots)$ is Dirac's delta function, $\{\bm G\}$ is the
+reciprocal lattice defined through $e^{i\bm G\cdot\bm R}=1$ for all
+$\bm R$ and $\bm G$, $A=4ab$ is the area of the unit cell
+and we used the Fourier representation of the 2D
+periodically repeated delta function. We introduce a 2D Fourier representation for
+the potential \notaL{Checar consistencia entre phi y varphi en todos lados}
+\begin{equation}
+  \label{eq:phifourier}
+  \phi(\bm r)=\sum_{\bm G}\phi_{_{\bm G}}(z)e^{i\bm G\cdot\bm r_\|} 
+\end{equation}
+where $\phi_{_{\bm G}}(z)$ is the Fourier coefficient of the potential at
+the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
+ordinary differential equation \notaL{El signo estaba mal. Chécalo.}
  \begin{eqnarray}
- \rho(\vec{r}) =q \displaystyle\sum_{R}  \ \delta
-  (\vec{r}-\vec{R}-\vec{r}_0) =\dfrac{q}{A}  \displaystyle\sum_{G}
-  e^{i G \cdot (\vec{r}-\vec{r}_{0})} \delta (z-z_0)
-\end{eqnarray}
-Where $ {R} $ is the 2D Bravais network and $ {G} $ its reciprocal
-network. It is written $ \phi (\vec{r}) = \displaystyle \sum _
-{\vec{G}}  \phi_{_{G}}(z) e^{i \vec {G} \cdot \vec {r}} $. So the
-Poisson equation $ \nabla^2 \phi = -4 \pi \displaystyle
-\sum_{\vec{R}} \delta (\vec{r} - \vec{R} - \vec{r}_0) $.
-Becomes
+ \frac{d^2}{dz^2}\phi_{_{\bm G}}(z)-G^2\phi_{_{\bm G}}(z)=
+   -\frac{4 \pi}{A} \delta(z),
+ \end{eqnarray}
+an homogeneous equation for $z\ne0$ which may be trivially
+solved. After applying boundary conditions at $z=0$ and regularity
+conditions at infinity, we obtain
+\begin{equation}
+  \label{eq:phiG}
+  \phi_{\bm G}(z)=
+  \begin{cases}
+    -\dfrac{2\pi}{A}\abs{z}&\text{if }G=0,\\
+    \dfrac{2 \pi}{AG}  e^{- G \abs{z}}&\text{if }G\neq 0.
+  \end{cases}
+\end{equation}
+The case $G=0$ corresponds to the potential produced by a uniformly charged plane,
+while the case $G\ne 0$ is the symmetric solution that decays far from
+the source plane. Substituting into Eq. \eqref{eq:phifourier} yields
 \begin{eqnarray}
- \dfrac{\partial^2 \phi_{_{G}}(z)}{\partial z^2}+ G^2\phi_{_{G}}(z)=
-   -\dfrac{4 \pi}{A}  q   e^{i \vec{G} \cdot \vec{r}_{_0}} \delta
-   (z-z_0)
- \end{eqnarray}
-Solving the homogeneous equation above and below $ z = z_0 $, using
-symmetry and conditions at $ \pm \infty $ we obtain $ \phi_{_{G}} =
-\phi_{_{G}}^{0} e^{ G \abs{z-z_0}} \ \ \ \ \ (G \neq 0) $. And
-adjusting the singularity
- \begin{eqnarray}
- \phi_{_{G}}(z)= \dfrac{2 \pi q}{AG}  e^{- G \abs{z-z_0}} e^{-i
-   \vec{G} \cdot \vec{r}_{_0}} \ \ \ \ \ (G\neq 0)
- \end{eqnarray}
-For the case $ G = 0 $ is similar $ \phi_{_{G = 0}} (z) = \dfrac{-2
-  \pi q}{A} \abs{z-z_0} + K, $ $ \ \ $ (K is a constant). Here $ A =
-L_x L_y $ is the unit cell area
- \begin{eqnarray}
- \phi(\vec{r}) = K-\dfrac{2 \pi q}{A}  \abs{z-z_0} +\dfrac{2 \pi
-   q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} e^{- G \abs{z-z_0}}
-   e^{i \vec{G} \cdot \vec{r}-\vec{r}_0}
- \end{eqnarray}
-Adding all the images loads,
+  \label{eq:phiG1}
+ \phi(\bm r) = -\frac{2 \pi}{A}  \abs{z} +{\sum_{\bm G}}' \frac{2 \pi
+   }{AG} e^{- G \abs{z}} e^{i \bm G\cdot\bm r_\|},
+ \end{eqnarray}
+where the prime indicates that the term $G=0$ should be ommited from
+the sum.
+
+We consider now the basis of our 2D lattice, with equal charges at the
+four positions $(\pm x_0, \pm y_0)$. Each of the corresponding four
+sublattices produces a potential as that in Eq. \eqref{eq:phiG1} but
+shifted by the corresponding basis vector, yielding
+\begin{equation}
+  \label{eq:phiG4}
+  \phi(\bm r) = -\frac{8\pi}{A} \abs{z}
+    +{\sum_{\bm G}}' \frac{8\pi}{AG} e^{- G \abs{z}}\cos(G_x x_0)
+    \cos(G_y y_0) e^{i \bm G\cdot\bm r_\|}.
+\end{equation}
+Finally, we shift the origin of Eq. \eqref{eq:phiG4} vertically to each of the planes shown in
+Fig. \ref{fig:sideview} and multiply by the corresponding charge $q_0$
+or $-q_0$ to obtain the contribution to the total potential. The charge $q_0$ corresponds to
+the planes with heights of the form $z_0+4nc$ and $-z_0+(4n+2)c$, with
+$n=\ldots-2,-1,0,1,2\ldots$ an arbitrary integer, while the charge
+$-q_0$ corresponds to the planes with height $z_0+(4n+2)c$ and
+$-z_0+(4n+4)c$.
+
+We concentrate our attention only on the region $a\le z<z_0$. From
+Fig. \ref{fig:sideview} we see that the $G=0$
+field has contributions only from the charges at $z_0$ and their
+images ant $-z_0$, this contribution is like that of a parallel plate
+capacitor $E_{0z}=-4\pi q_0/ab=-16\pi q_0/A$, which corresponds to the
+potential $\phi_0=16\pi q_0 z/A$. Other contiguous planes of with opposite charges
+contribute to the field elsewhere. The contributions to the potential
+from the $G\ne0$ are simple geometric sums that may be summed
+analytically over $n$ and yield the total potential
+\begin{equation}
+  \label{eq:phitot}
+  \begin{split}
+    \phi(\bm r)=&\frac{16\pi q_0}{A}\biggl(z+{\sum_{\bm G}}'\frac{2\sinh
+      Gc}{G \sinh 2Gc}\cosh G(c-z_0)\cos G_x x_0 \cos G_y y_0\\
+    &\times \sinh Gz\, e^{i\bm G\cdot\bm r_\|}\biggr).
+  \end{split}
+\end{equation}
+
+\notaL{Aquí voy. Checa la ecuación previa}
+
+In our case of
+interest we take $0\le z < z_0$ and thus write
+
   \begin{eqnarray}\label{Eq:EC11}
@@
 
+ \bibitem{T3} Mahfoud Belhadj, Howard E. Alper, and Ronald M. Levy. \textquotedblleft 
+ \emph{ Molecular dynamics simulations of water with Ewald summation 
+ 	for the long range electrostatic interactions.}\textquotedblright Chemical
+  Physics Letters, 179(1-2):13–20, 1991.
+   \bibitem{T4}A. Bródka.\textquotedblleft 
+   \emph{ Ewald summation method with electrostatic layer correction for
+  interactions of point dipoles in slab geometry.}\textquotedblright Chemical 
+Physics Letters, 400(1):62–67, December 2004.
+ \bibitem{T5} A. Grzybowski, E. Gwóźdź, and A. Bródka.\textquotedblleft 
+ \emph{ Ewald summation of electrostatic interactions in molecular dynamics
+ 	 of a three-dimensional system with periodicity in two directions.}\textquotedblright 
+  Physical Review B, 61(10):6706–6712, March 2000.
+
+ \bibitem{T6} Kratzer, Peter, and Jörg Neugebauer. \textquotedblleft \emph{The basics of 
+ 	electronic structure theory for periodic systems.}\textquotedblright 
+  Frontiers in chemistry 7 (2019).
+ \bibitem{T7} Charles Kittel. \textquotedblleft \emph{Introduction to Solid State
+ 	 Physics.}\textquotedblright Wiley, Hoboken, NJ, 8 edition, 2005.
+
 \bibitem{I17} Dariani RS, Ebrahimnasab S (2014). \textquotedblleft

### 2020-06-10 paper.tex
Finish the theory of the attack current.

--- 2020-06-09 paper.tex
@@
 
-\notaL{Aquí voy. Checa la ecuación previa}
-
-In our case of
-interest we take $0\le z < z_0$ and thus write
-
-  \begin{eqnarray}\label{Eq:EC11}
- \phi(\vec{r}) = -\dfrac{8\pi q}{A} \bigg((\abs{z-z_0}-\abs{z+z_0} )
-    +\dfrac{8\pi q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \bigg(
-    e^{- G \abs{z-z_0}} -e^{- G \abs{z+z_0}}  \bigg) \cos(G_x x_0)
-    \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}
- \end{eqnarray}
-At a height $ 0 <z <z_0 $ I simplify
-   \begin{eqnarray}
- \phi(\vec{r}) = -\dfrac{16\pi q}{A} \bigg( z
-     +\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \sinh(G z)  \cos(G_x
-     x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}} \bigg)
- \end{eqnarray}
-If the surface of the liquid is at a finite height c, then we can use images, like:
-\begin{figure}
-  \centering
-  \includegraphics[scale=.6]{Images/celd1}
-  \caption{\emph{Diagram shows that there is a positive (real) plane $
-      z_0 $, a negative image at $ -z_0 $ below the conductor ($ z = 0
-      $) and its images are a positive plate at $ 2c-z_0 $ and a
-      negative plate at $ 2c + z_0 $, the image is repeated vertically
-      with the period $ L_z = 4c $}}
-  \label{fig:Celda1}
-\end{figure}
-In Fig. \ref{fig:Celda1} it is observed that there is a positive
-(real) plane $ z_0 $, a negative image at $ -z_0 $ below the conductor
-($ z = 0 $) and its images are a positive plate at $ 2c-z_0 $ and a
-negative plate at $ 2c + z_0 $. Also, the image is repeated vertically
-with the period $ L_z = 4c $. Therefore, the equation \ref{Eq:EC11}
-would be rewritten, like this
- \begin{eqnarray}\label{Eq:EC1}
- \nonumber\phi(\vec{r}) = K+\dfrac{8\pi q}{A} \displaystyle\sum_{n}
-   -\bigg(\abs{z-z_0-nL_z}-\abs{z+z_0-nL_z}-\abs{z+2c+z_0-nL_z}+\abs{z-2c-z_0-nL_z}\bigg)
-   +\\ \nonumber \dfrac{1}{G}\displaystyle\sum_{\vec{G}}\bigg(
-   \displaystyle\sum_{n} \bigg( e^{-\abs{z-z_0-nL_z}}
-   +e^{-\abs{z+z_0-nL_z}}-e^{-\abs{z+2c+z_0-nL_z}}-e^{-\abs{z-2c-z_0-nL_z}}
-   \bigg)\bigg)\cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot
-   \vec{r}}\\
-\end{eqnarray}
-The constant K is chosen thus $ \phi (z = 0) $, substituting in
-Eq. (\ref {Eq:EC1}) and after factoring $ e^{- nGL_Z} $ we are
-explicitly left with the geometric sum over $n$
-{\small
-  \begin{eqnarray}
-    \nonumber\phi(\vec{r}) = K+\dfrac{16\pi q}{A} \bigg(z+z_0  +
-    \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \bigg(e^{-Gz_0}
-    \sinh(Gz)+e^{-Gz_0(2c_z)} \sinh(Gz_0) -e^{-2Gc} \sinh(Gz)
-    \sinh(Gz_0) \\ \nonumber \dfrac{1+\cosh(2Gc)}{\sinh(2Gc)} -
-    e^{-2Gc}\cosh(2Gc) \sinh(Gz_0)   \bigg) \cos(G_x x_0) \cos(G_y
-    y_0) e^{i \vec{G} \cdot \vec{r}}   \bigg)\\
- \end{eqnarray}
-}
-Evaluating for $ z = 0 $
- \begin{eqnarray}\label{Eq:EC2}
-\nonumber\phi(x, y, 0) = K+\dfrac{16\pi q}{A} \bigg(z_0  +
-   \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \bigg(e^{-2Gc}
-   \sinh(Gz_0)-e^{-2Gc} \sinh(Gz_0)   \bigg) \cos(G_x x_0) \cos(G_y
-   y_0) e^{i \vec{G} \cdot \vec{r}}\bigg) =\\ \nonumber =
-   K+\dfrac{16\pi q}{A} \\
-\end{eqnarray}
-Independent of $ x $ and $ y $ to configure
- \begin{eqnarray}
- K=\dfrac{16\pi q}{A}
-\end{eqnarray}
-I can further simplify Eq. (\ref {Eq:EC2}) to get,
- \begin{eqnarray}
-\nonumber\phi(\vec{r}) = \dfrac{16\pi q}{A}\bigg( z  +
-   \displaystyle\sum_{\vec{G}}\dfrac{\sinh(Gz_0)}{G} \bigg(e^{-Gz_0}
-   -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg)
-   \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\
-\end{eqnarray}
-I am sure it is correct. Then it goes to zero at $ z = 0 $. The term
-with c disappears if $ c \longrightarrow \infty $. The sum converges
-when $ G \longrightarrow \infty $ if $ z <z_0 <c $ and diverges to $ z
-\longrightarrow z_0 $. So it seems ready for calculation.
-The normal component of the field is
-\begin{eqnarray}
-\nonumber E_\perp = -\dfrac{16\pi q}{A}\bigg( 1  +
-  \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \cosh(Gz)\bigg(e^{-Gz_0}
-  -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x
-  x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\
-\end{eqnarray}
-And the current density is for any $ z $, for our calculation we
-choose that $ z = 0 $
-\begin{eqnarray}\label{Eq:J}
-\nonumber J_\perp = -\dfrac{I}{ab}\bigg( 1  +
-  \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \cosh(Gz_0) \bigg(e^{-Gz_0}
-  -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x
-  x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\
-\end{eqnarray}
-Integrating on the surface of the sample is obtained $I_{nm}
-=\int^{a}_0 dx \int^{b}_0 dy \ \ e^{i\vec{G}\vec{r}}$
-\begin{eqnarray}
-\nonumber I_{nm}=\dfrac{1}{G_x G_y} (e^{-iG_xa}-1) (e^{-G_y b}-1) \\
-  I_{nm}=\dfrac{ab}{nm \pi^2} ((-1)^n-1-1)(-(1)^m-1-1)
-\end{eqnarray}
-Using the factor of the reciprocal vector in this way $ \vec {G} =
-\bigg (\dfrac{\pi}{a} n, \dfrac{\pi}{b} m \bigg) $,
-however, as all the coefficients of $ e^{- i \vec{G} \vec{r}} $ in
-\ref{Eq:J} they are even in $ \vec{G} $ and the integral is odd in n
-and m, only the constant term taxpayer to the integrated current
-\begin{eqnarray}
-\nonumber I^{nm} =\int \vec{J} dx  dy =-\int \vec{J}_\perp dx  dy=\dfrac{I}{ab}\int dx \int dy=I
-\end{eqnarray}
+Notice that the terms of the sum above converge exponentially to zero
+as $G$ increases for any $z$ such that $0\le z <z_0 \le c$, and thus
+the sum is convergent. The divergence in the limit $ z
+\longrightarrow z_0 $ is not worrisome, as we are interested in the
+field close to bottom $z=0$ of the cell.
+
+The current density normal to the surface may now be obtained as
+$j_\perp=-\sigma\partial\phi/\partial z$,
+\begin{equation}
+  \label{Eq:J}
+  \begin{split}
+    j_\perp(\bm r) =& -\frac{I}{ab}\biggl(1+{\sum_{\bm G}}'\frac{2\sinh
+      Gc}{\sinh 2Gc}\cosh G(c-z_0)\cos G_x x_0 \cos G_y y_0\\
+    &\times \cosh Gz\, e^{i\bm G\cdot\bm r_\|}\biggr).
+  \end{split}
+\end{equation}
+Eq. \eqref{Eq:J} is a very rapidly convergent expression that allows,
+in particular, to calculate the current $j_\perp(x,y,0)$ that attacks
+the substrate to produce the PS sample.
+Integrating over the surface of the sample we verify
+\begin{equation}
+  \label{eq:intj}
+  \int_0^adx\int_0^bdy\,j_\perp(\bm r)=-I,
+\end{equation}
+as the contributions of opposite non-null reciprocal vectors cancel
+out. As expected, all of the current that leaves the electrode find
+its way to the substrate.
+
 \subsection{Transfer Matrix Method (TMM)}

### 2020-06-10 paper.tex
Finished theory. No need to present the transfer matrix theory.

@@
 
-\subsection{Transfer Matrix Method (TMM)}
-One of the methods used for the analysis of photonic crystal
-structures is the transfer matrix method. We use it to investigate the
-reflectance of light in a one-dimensional photonic crystal. The
-electric and magnetic fields within the layers are shown as $E_m$ and
-$H_m$. Then we can specify the electric and magnetic fields in the
-air, $ E_0 $ and $ H_0 $, by solving the following matrix equation:
-\begin{equation}
-\left[
-\begin{matrix}
-E_{_{0}}\\
-H_{_{0}}
-\end{matrix}
-\right]= \textbf{M}_{_{1}}, \textbf{M}_{_{2}},...,\textbf{M}_{_{N}} \left[
-\begin{matrix}
-E_{_{m}}\\
-H_{_{m}}
-\end{matrix}
-\right]
-\end{equation}
-Where N is the total number of layers including the cavity layer and $
-M_j $ is the matrix characteristic of the layer $ j $ specified by:
-\begin{equation}
-\textbf{M}_j = \left[
-\begin{matrix}
-\cos \delta_j & -\frac{i}{\eta_j} \sin \delta_j \\
--i\eta_j \sin\delta_j & \cos\delta_j
-\end{matrix}
-\right]
-\end{equation}
-and
-\begin{equation}
-\delta_j= \frac{2\pi}{\lambda} \tilde{n}_j d_j \cos \theta_j
-\end{equation}
-where $ \lambda $ is the wavelength, $ \tilde{n}_{_{j}} = n_{j} -
-ik_{_{j}}$ is the complex refractive index (CRI) of the layer, $ d_j $
-is the thickness of the layer, and $ \theta_j $ is the angle of
-refraction of light in the $ j $ layer. The parameter $ \eta_ {j} $
-for layer j is defined as:
-\begin{equation}\label{Eq:Mt1}
-\eta_j=\sqrt{\frac{\epsilon_0}{\mu_0}}\tilde{n}_j cos\theta_j \hspace{1cm} (TE \ \ mode)
-\end{equation}
-y
-\begin{equation}\label{Eq:Mt2}
-\eta_j=\sqrt{\frac{\epsilon_0}{\mu_0}} \frac{\tilde{n}_j}{cos\theta_j} \hspace{1cm} (TM \ \ mode)
-\end{equation}
-where $ \epsilon_0 $ and $ \mu_0 $ are permittivity and free space
-permeability, respectively. The transfer matrix of all the photonic
-crystal is given by:
-\begin{equation}
-\textbf{M}=\textbf{M}_1,\textbf{M}_2,...,\textbf{M}_N= \left[
-\begin{matrix}
-m_{11} & m_{12} \\
-m_{21} & m_{22}
-\end{matrix}
-\right]
-\end{equation}
-We can write the reflection and transmission coefficients in a
-one-dimensional photonic crystal nanocavity as:
-\begin{equation}
-r=\frac{\eta_0(m_{11}m_{12}\eta_m)
-  -(m_{21}+m_{22}\eta_m)}{\eta_0(m_{11}m_{12}\eta_m)
-  -(m_{21}+m_{22}\eta_m)}
-\end{equation}
-end
-\begin{equation}
-t=\frac{2\eta_0}{\eta_0(m_{11}m_{12}\eta_m)+(m_{21}m_{22}\eta_m)}
-\end{equation}
-where $ \eta_0 $ and $ \eta_m $ are parameters for air and outlet
-layers, respectively (as defined in equations \ref{Eq:Mt1} or
-\ref{Eq:Mt2}). Furthermore, the reflectivity R and transmittance T of
-the entire photonic crystal nanocavity is given by:
-\begin{equation}
-R=|r|^{2}
-\end{equation}
-y
-\begin{equation}
-T=\frac{\eta_m}{\eta_0}|t|^{2}
-\end{equation}
+Using Eq. \eqref{Eq:J} we can correlate the local current density at
+the sample as it is prepared with its geometric and optical
+properties. For the calculation of the optical properties we use the
+well known transfer matrix method \notaL{refs}.
+
 \section{Experimental Details}

### 2020-06-10 paper.tex
Add a couple of notes
Start to revise experimental details.

@@
 its way to the substrate.
+\notaL{En este sistema, ¿cuál es el cátodo y cuál el ánodo? ¿de dónde
+  hacia dónde va la corriente? ¿$q_0$ es positiva o negativa?}
 
@@
 well known transfer matrix method \notaL{refs}.
+\notaL{No necesitamos presentar la teoría de matrices de
+  transferencia. No hay nada original ahí.}
 
@@
   \includegraphics[scale=0.6]{Images/DE1}
-\caption{\emph{Schematic of the experimental set-up for
-      fabrication of porous silicon with GRIN. (a) Represents an
-      outline of the surface section, divided by three regions
-      A, B and C, corresponding to High, Medium and Low Porosity
-      respectively. (b) It is the diagram of the electrochemical
-      cell with its parts: silicon wafer, Teflon cell, platinum
-      point electrode, Electrochemical Aqueous solution and the
-      connection of the circuit with the cathode and anode. (c)
-      It is a schematic drawing of the Cross section of the
-      electrochemically attacked porous silicon seen in three
-      different regions as mentioned above. }}
+\caption{(a) \notaL{reordenar figura} Experimental set-up for
+      fabrication of porous silicon with GRIN, consisting of a
+      rectangular electrochemical cell. We indicate the Si wafer, the
+      teflon cell, the platinum point electrode, the electrolyte and the
+      current source. (b) Top and (c) side schematic views of the resulting sample,
+      illustrating three regions $A$, $B$ and $C$ of relatively high, medium and
+      low porosity respectively illustrating the change gradient in
+      pore size and depth. }}
     \label{fig:DE1}
@@
 
-In the Fig. \ref{fig:DE1} a shows schematic representation of the
-experimental setup where porous silicon can be manufactured with GRIN,
+Fig. \ref{fig:DE1} shows a schematic representation of our
+experimental setup to manufacture porous silicon with GRIN.
+\notaL{La figura está feita. Hay un abultamiento extraño en la
+  punta. Debería verse el aislamiento y la punta descubierta y más
+  sumergida. La letra está demasiado chica. El gradiente de porosidad va
+  en la dirección opuesta. El panel (a) tiene una discontinuidad. ¿Tú
+  la hiciste o la adaptaste? Usa dos paréntesis (a), (b),
+  (c). Alínealos. Pon primero la preparación y luego los resultados
+  vistos de arriba y de lado. Está en desorden. Se ve muy descuidada. No dice nada sobre la
+  preparación que no esté en la figura 1. Dos páneles no ilustran el
+  método experimental, sino el resultado. Quizás yo la quitaría.}
 taking into account the considerations of the electrode as tip, the
@@
 rectangular attack area.
+
 In Fig. \ref{fig:DE1} a) we draw an outline of the surface section,

### 2020-06-10 paper.tex
Correct small mistake
Some corrections, describe new figures, upt to sec. 3.1

@@
   \label{eq:I}
-\int_{\mathcal S'} d\bm a \cdot \bm j = I,
+\int_{\mathcal S'} d\bm a \cdot \bm j = -I,
 \end{equation}
@@
   \label{eq:gauss}
-  \int_{\mathcal S} d\bm a \cdot \bm E = \frac{I}{\sigma}
+  \int_{\mathcal S} d\bm a \cdot \bm E = -\frac{I}{\sigma}
 \end{equation}
@@
 \begin{equation}
-  q_{_{0}} = \frac{I}{4 \pi \sigma}
+  q_{_{0}} = -\frac{I}{4 \pi \sigma}
 \end{equation}
@@
   \includegraphics[width=\textwidth]{paper-1}
-  \caption{Top view of the electrolytic cell (light blue) showing the charge at the
+  \caption{Top view of the fictitious system formed by reflections of
+    the electrolytic cell (light blue) showing the charge at the
     tip of the electrode (red dot) and its images on the walls of the
-    rectangular cell, the images of its images and so on (blue dots). The walls are at $x=0,a$,
-    $y=0,b$. The relation of some charges and their images is
+    rectangular cell, the images of its images and so on (blue
+    dots). The walls are at $x=0,a$,
+    $y=0,b$ (blue lines). The relation of some charges and their images is
     indicated by dashed arrows, with a bar to indicate the
@@
   \includegraphics[width=\textwidth]{paper-2}
-  \caption{Side view of the electrolytic cell (light blue)
+  \caption{Side view of the fictitious system formed by reflections of
+    the electrolytic cell (light blue)
     showing the charge at the tip of the electrode (red dot), its
@@
     surface of the sample and the top of the electrolyte (green
-    dots). We use solid dots to denote particles with the same charge
-    as that corresponding to the tip $q_0$, and open dots for those of
-    opposite charge. The system may be interpreted as a periodic
+    dots). We use solid dots to denote images with the same charge $q_0$
+    as that corresponding to the tip of the electrode, and open dots for those of
+    opposite charge $-q_0$. The mirror planes that don't invert the charge
+    are indicated by blue lines and the mirror plane that inverts the
+    charge is indicated by a red line. The relation of some charges and their images is
+    indicated by dashed arrows, with a bar to indicate the
+    corresponding reflecting wall. The system may be interpreted as a periodic
     lattice with a rectangular unit cell of size $2a\times 4c$, one of
@@
 \end{figure}
-Each plane of charges upon reflection on the surface of the sample yields an
+Each plane of charges upon reflection on the surface of the sample at
+the bottom of the cell yields an
 plane of image charges of the opposite sign, while reflections
@@
   \centering
-  \includegraphics[scale=0.6]{Images/DE1}
-\caption{(a) \notaL{reordenar figura} Experimental set-up for
-      fabrication of porous silicon with GRIN, consisting of a
-      rectangular electrochemical cell. We indicate the Si wafer, the
-      teflon cell, the platinum point electrode, the electrolyte and the
-      current source. (b) Top and (c) side schematic views of the resulting sample,
+  \includegraphics[width=.8\textwidth]{paper-3}\\[12pt]
+  \includegraphics[width=.8\textwidth]{paper-4}\\[12pt]
+  \includegraphics[width=.8\textwidth]{paper-5}
+  %\\[12pt]
+  %\includegraphics[scale=0.6]{Images/DE1}
+
+\caption{\notaL{reordené figura y rehice} Experimental set-up for
+      the fabrication of porous silicon with GRIN, consisting of a
+      rectangular electrochemical cell. We indicate the Si wafer (dark
+      gray), the teflon cell (light gray), the sealing o-ring (black
+      circles), the insulated feeding cable (white lines within black
+      lines), the uncovered platinum tip (white) within the
+      electrolyte (blue), the electrical contact below the sample
+      (yellow) and the current source. We indicate some geometrical
+      parameters of the arrangement $x0$, $z0$, $a$ and $c$
+      and the current source (upper panel) and a few current density
+      field lines. Top (middle panel) and
+      side (lower panel) schematic views of the resulting sample,
       illustrating three regions $A$, $B$ and $C$ of relatively high, medium and
-      low porosity respectively illustrating the change gradient in
-      pore size and depth. }}
+      low porosity respectively illustrating the gradients in pore
+      size, density and depth. \notaL{Es $\nabla p$ razonable para el
+        gradiente de la porosidad}}
     \label{fig:DE1}
@@
 
-Fig. \ref{fig:DE1} shows a schematic representation of our
+In Fig. \ref{fig:DE1} we show a schematic representation of our
 experimental setup to manufacture porous silicon with GRIN.
-\notaL{La figura está feita. Hay un abultamiento extraño en la
+\notaL{Cambié las figuras} \notaL{La figura está feita. Hay un abultamiento extraño en la
   punta. Debería verse el aislamiento y la punta descubierta y más
@@
   método experimental, sino el resultado. Quizás yo la quitaría.}
-taking into account the considerations of the electrode as tip, the
-rectangular cell and the sample (silicon wafer) with the largest
-rectangular attack area.
-
-In Fig. \ref{fig:DE1} a) we draw an outline of the surface section,
-divided by three regions A, B and C, dependes in therir porosity i.e.,
-High, Medium and Low Porosity. All this corresponding to  expected to
-be obtained in the experiments. Fig. \ref{fig:DE1} b) the scheme shows
-the electrochemical cell with its parts: silicon wafer, teflon cell,
-platinum point electrode, electrochemical Aqueous Solution and the
-connection of the circuit with the cathode and anode. Finally,
-Fig. \ref{fig:DE1} c) it is a schematic drawing of the Cross section
-of the electrochemically attacked porous silicon seen from three
-different regions as mentioned above. In section 3.1 we give the
-details used to carry out our experiments.
+As dicussed above, we fabricated an electrolytic cell with the shape of a
+rectangular prism on the bottom of which we place a Si which makes an
+electrical contact to a gold plate \notaL{Lo inventé; de qué material es
+  el contacto bajo la muestra} which together make the anode. The
+catode consists of a platinum wire insulated except for a small region
+at its tip, which we take as a point current drain.
+We also show a schematic drawing of the expected GRIN PS structures,
+with a gradient in the porosity, and in the width, density and depth
+of the resulting pores.
 

### 2020-06-11 paper.tex

@@
 \end{equation}
-This problem may be solved readily using image charge theory
-\notaL{ref}. The potential within the electrolytic cell coincides the
+This problem may be solved readily using image charge theory \cite{T1,T2}
+\notaL{\sout{ref}}. The potential within the electrolytic cell coincides the
 the field within an infinite vacuum containing the point charge
@@
 convergence properties. The potential can be obtained
-using the Ewald summation technique \notaL{ref}, which yields two rapidly converging
-series, one in real space and another one in reciprocal space.
+using the Ewald summation technique \cite{T3,T4,T5}\notaL{\sout{ref}}, which yields
+ two rapidly convergingseries, one in real space and another one in reciprocal space.
 Nevertheless, as we need the potential and the field to obtain the
@@
 reciprocal vectors, and then sum over the charges that form the basis
-of the 2D {\em crystal} plane and finally sum over all the planes \notaL{ref}.
+of the 2D {\em crystal} plane and finally sum over all the
+ planes \cite{T6,T7} \notaL{\sout{ref}}.
 
@@
   \label{eq:phifourier}
-  \phi(\bm r)=\sum_{\bm G}\phi_{\bm G}(z)e^{i\bm G\cdot\bm r_\|}
-\end{equation}
-where $\phi_{\bm G}(z)$ is the Fourier coefficient of the potential at
+  \phi(\bm r)=\sum_{\bm G}\phi_{_{\bm G}}(z)e^{i\bm G\cdot\bm r_\|} 
+\end{equation}
+where $\phi_{_{\bm G}}(z)$ is the Fourier coefficient of the potential at
 the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
@@
  \begin{eqnarray}
- \frac{d^2}{dz^2}\phi_{\bm G}(z)-G^2\phi_{_{G}}(z)=
+ \frac{d^2}{dz^2}\phi_{_{\bm G}}(z)-G^2\phi_{_{\bm G}}(z)=
    -\frac{4 \pi}{A} \delta(z),
@@
   Photonics, 4(4), 909-914.
+
+  \bibitem{T1}Jackson, John David. \textquotedblleft 
+  \emph{Classical electrodynamics.}\textquotedblright (1999): 841-842.
+
+\bibitem{T2}Griffiths, David J. \textquotedblleft 
+\emph{Introduction to electrodynamics.}\textquotedblright 
+ New Jersey: Prentice Hall, 1962.
+
+ \bibitem{T3} Mahfoud Belhadj, Howard E. Alper, and Ronald M. Levy. \textquotedblleft 
+ \emph{ Molecular dynamics simulations of water with Ewald summation 
+ 	for the long range electrostatic interactions.}\textquotedblright Chemical
+  Physics Letters, 179(1-2):13–20, 1991.
+   \bibitem{T4}A. Bródka.\textquotedblleft 
+   \emph{ Ewald summation method with electrostatic layer correction for
+  interactions of point dipoles in slab geometry.}\textquotedblright Chemical 
+Physics Letters, 400(1):62–67, December 2004.
+ \bibitem{T5} A. Grzybowski, E. Gwóźdź, and A. Bródka.\textquotedblleft 
+ \emph{ Ewald summation of electrostatic interactions in molecular dynamics
+ 	 of a three-dimensional system with periodicity in two directions.}\textquotedblright 
+  Physical Review B, 61(10):6706–6712, March 2000.
+
+ \bibitem{T6} Kratzer, Peter, and Jörg Neugebauer. \textquotedblleft \emph{The basics of 
+ 	electronic structure theory for periodic systems.}\textquotedblright 
+  Frontiers in chemistry 7 (2019).
+ \bibitem{T7} Charles Kittel. \textquotedblleft \emph{Introduction to Solid State
+ 	 Physics.}\textquotedblright Wiley, Hoboken, NJ, 8 edition, 2005.
+
 \bibitem{I17} Dariani RS, Ebrahimnasab S (2014). \textquotedblleft

### 2020-06-13 paper.tex
Review manuscript. Correct mistakes. Start on experimental details

--- 2020-06-10 paper.tex
@@
 \begin{abstract}
-We propose a simple setup which allows the calculation of the current
+We propose a simple setup which that the calculation of the current
 density as a function of position within an electrochemical cell used
@@
 the current density, as well as the speed of attack and the width of the
-porous layer. Nevertheless, it is not a simple to task to measure the
+porous layer. Nevertheless, it is not a simple task to measure the
 {\em local} value of $\bm j(\bm r)$ along the surface. This hampers the
 design and optimization of well characterized reproducible GRIN PS
-structures. Thus, a system for which the current density field may be
+structures.\notaL{Tenemos referencias para afirmar esto?} Thus, we
+believe a
+system for which the current density field may be
 easily computed would be useful.
@@
 walls of the cell are insulating while the bottom is completely
-covered with the sample, which is a good conductor which is
-electrically grounded. Within the electrolyte we position an electrode
+covered with the sample, which is a which is an
+electrically grounded good conductor. Within the electrolyte we position an electrode
 which we assume is a thin conductor, insulated from the electrolyte
@@
     conductor. The tip of the electrode is a thin insulated wire with
-    just the tip uncovered and located at $ \vec{r}_0 $ within the
+    just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
     liquid.\notaL{Quité el tipo de letra del pie de figura. Que la pongan en la
@@
     está aterrizada}\notaL{Indica el voltaje y la
-    corriente}\notaL{¿Está bien la polaridad de la batería?}}
+    corriente}\notaL{Mejor pon una fuente de corriente en lugar de una
+  fuente de voltaje}}
   \label{f:celda}
@@
 where the prime on $\mathcal S'$ means we remove from the surface a
-very small hole through which the wire that feeds the current gets
+very small hole through which the wire that feeds the current to the
+electrode gets
 through. Assuming the wire is narrower than any other relevant
@@
 This problem may be solved readily using image charge theory
-\notaL{ref}. The potential within the electrolytic cell coincides the
-the field within an infinite vacuum containing the point charge
+\notaL{ref}. The potential within the electrolytic cell coincides
+within the region $0\le x\le a$, $0\le y \le b$, $0\le z\le c$
+with that an infinite fictitious empty space but for the point charge
 $q_0$ at the tip of the electrode at $\bm r_0$, and an array of its fictitious image
@@
     one of which is indicated  by wide dashed lines, and with a basis of four equal
-    charges at $(\pm x_0, \pm y_0, z_0)$.}
+    charges $q_0$ at $(\pm x_0, \pm y_0, z_0)$.}
   \label{fig:topview}
@@
 lattice with a unit cell of size $2a\times 2b$ and with a basis of
-four equal charges situated at the positions $\bm r_0$, $\bm
+four equal charges $q_0$ situated at the positions $\bm r_0$, $\bm
 r_1=(-x_0, y_0, z_0)$, $\bm r_2=(x_0, -y_0, z_0)$ and $\bm r_3=(-x_0,
@@
 series, one in real space and another one in reciprocal space.
-Nevertheless, as we need the potential and the field to obtain the
-current density on the surface of the sample on which there are no
-real nor image charges, we may perform a somewhat simpler planewise
+Nevertheless, as we have to evaluate the potential and the field on
+the bottom of the cell to obtain the current density which attacks the
+surface of the sample, and as there are no
+real nor image charges there, we may perform a somewhat simpler planewise
 summation, where we first obtain the potential and field produced by a
 simple periodic lattice of charges using a fast convergent sum over the 2D
-reciprocal vectors, and then sum over the charges that form the basis
-of the 2D {\em crystal} plane and finally sum over all the planes \notaL{ref}.
+reciprocal vectors, we then sum over the charges that form the basis
+of the 2D {\em crystal} plane and we finally sum over all the planes \notaL{ref}.
 
@@
 The case $G=0$ corresponds to the potential produced by a uniformly charged plane,
-while the case $G\ne 0$ is the symmetric solution that decays far from
+while the case $G\ne 0$ is the potential produced by a sinusoidal
+charge density on a plane given by the
+symmetric solution that decays exponentially as we get away from
 the source plane. Substituting into Eq. \eqref{eq:phifourier} yields
@@
 We consider now the basis of our 2D lattice, with equal charges at the
-four positions $(\pm x_0, \pm y_0)$. Each of the corresponding four
+four positions $(\pm x_0, \pm y_0,0)$. Each of the corresponding four
 sublattices produces a potential as that in Eq. \eqref{eq:phiG1} but
@@
 field has contributions only from the charges at $z_0$ and their
-images ant $-z_0$, this contribution is like that of a parallel plate
+images at $-z_0$, and that this contribution is like that of a parallel plate
 capacitor $E_{0z}=-4\pi q_0/ab=-16\pi q_0/A$, which corresponds to the
@@
 contribute to the field elsewhere. The contributions to the potential
-from the $G\ne0$ are simple geometric sums that may be summed
+from the $G\ne0$ are simple geometric sums that may be added
 analytically over $n$ and yield the total potential
@@
 the sum is convergent. The divergence in the limit $ z
-\longrightarrow z_0 $ is not worrisome, as we are interested in the
-field close to bottom $z=0$ of the cell.
+\longrightarrow z_0 $ corresponds to the singularity of the potential
+at the position of a point charge, and it is not worrisome, as we are
+interested in the field close to bottom $z=0$ of the cell.
 
@@
   \begin{split}
-    j_\perp(\bm r) =& -\frac{I}{ab}\biggl(1+{\sum_{\bm G}}'\frac{2\sinh
+    j_\perp(\bm r) =& \frac{I}{ab}\biggl(1+{\sum_{\bm G}}'\frac{2\sinh
       Gc}{\sinh 2Gc}\cosh G(c-z_0)\cos G_x x_0 \cos G_y y_0\\
@@
   \label{eq:intj}
-  \int_0^adx\int_0^bdy\,j_\perp(\bm r)=-I,
+  \int_0^adx\int_0^bdy\,j_\perp(\bm r)=I,
 \end{equation}
 as the contributions of opposite non-null reciprocal vectors cancel
-out. As expected, all of the current that leaves the electrode find
-its way to the substrate.
-\notaL{En este sistema, ¿cuál es el cátodo y cuál el ánodo? ¿de dónde
-  hacia dónde va la corriente? ¿$q_0$ es positiva o negativa?}
+out. As expected, all the current that leaves sample finds
+its way to the cathode.
 
@@
       the fabrication of porous silicon with GRIN, consisting of a
-      rectangular electrochemical cell. We indicate the Si wafer (dark
+      electrochemical cell with the shape of a
+      rectangular prism. We indicate the Si wafer (dark
       gray), the teflon cell (light gray), the sealing o-ring (black
@@
       electrolyte (blue), the electrical contact below the sample
-      (yellow) and the current source. We indicate some geometrical
-      parameters of the arrangement $x0$, $z0$, $a$ and $c$
+      (yellow) and the controlled current source. We indicate some geometrical
+      parameters of the arrangement $x_0$, $z_0$, $a$ and $c$
       and the current source (upper panel) and a few current density
@@
 experimental setup to manufacture porous silicon with GRIN.
-\notaL{Cambié las figuras} \notaL{La figura está feita. Hay un abultamiento extraño en la
-  punta. Debería verse el aislamiento y la punta descubierta y más
-  sumergida. La letra está demasiado chica. El gradiente de porosidad va
-  en la dirección opuesta. El panel (a) tiene una discontinuidad. ¿Tú
-  la hiciste o la adaptaste? Usa dos paréntesis (a), (b),
-  (c). Alínealos. Pon primero la preparación y luego los resultados
-  vistos de arriba y de lado. Está en desorden. Se ve muy descuidada. No dice nada sobre la
-  preparación que no esté en la figura 1. Dos páneles no ilustran el
-  método experimental, sino el resultado. Quizás yo la quitaría.}
+\notaL{Cambié las figuras}
 As dicussed above, we fabricated an electrolytic cell with the shape of a
-rectangular prism on the bottom of which we place a Si which makes an
+rectangular prism on the bottom of which we place a Si wafer which makes
 electrical contact to a gold plate \notaL{Lo inventé; de qué material es
@@
 
-\subsection{Fabrication of Porous Silicon Monolayers GRIN}
-Some of the simulated photonic structures were made by electrochemical
-anodization on an oriented (100) p-type crystalline Si wafer
-(resistivity 0.002 - 0.005 $ \Omega \cdot cm $), under galvanostatic
-conditions. The electrochemical anodization process was performed at
-room temperature, with an electrolytic mixture of aqueous hydrofluoric
+\subsection{Fabrication of PS  GRIN Monolayers}
+We manufactured single layer PS structures through an electrochemical
+anodization on a (100) $p$-type crystalline Si wafer
+(resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
+conditions. The process was performed at
+room temperature,\notaL{Controlaste/mediste la temperatura?} with an
+electrolytic mixture of aqueous hydrofluoric
 acid (HF) (concentration: 48 $ \% $ wt), glycerol (purity: 99.8 $ \% $
-wt) and ethanol (purity: 99.9 $ \%$ wt ) in 3: 7: 1 volume ratio,
-respectively. After the anodizing process, the samples are rinsed with
-ethanol (purity: 99.9 $ \% $  wt). The layout of the cell used is as
-seen in Fig. \ref{fig:DE1} b), with an area of $ 1,206 \ \ cm^2 $
-(this is the area attacked in the process), has a rectangular shape ($
-0.62 \ \ cm \times 2.03 \ \ cm $)  so that the current densities  that
-attacks has a lateral gradient with a greater surface area. They were
-manufactured with a fixed current of $ 5 \ \ mA $ to generate
-different current densities ranging from $ 6  $ to $ 2.5 \ \ mA / cm^2
-$. Similarly, we use the current from $ 40 \ \ mA $ to generate $ 50 $
-to $ 20 \ \ mA / cm ^ 2 $. The cathode is made of a platinum wire that
-was arranged in the form of a tip with an approximate diameter of ($
-0.5 \ \ mm $).
+wt) and ethanol (purity: 99.9 $ \%$ wt ) in a 3:7:1 volume ratio,
+respectively. After the anodizing process, the samples were rinsed with
+ethanol (purity: 99.9 $ \% $  wt). The electrolytic cell had the shape
+of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
+size $0.62\text{cm}\times2.03\text{cm}$) with an uncovered sample area
+of $1.206\text{cm}^2$. \notaL{¿Cuáles fueron las coordenadas del
+  electrodo?} We manufactured samples using a current $I=5\text{mA}$
+which yielded current densities in the range
+$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$ and other smples using a larger
+current $I=40\text{mA}$ corresponding to current densities in the
+range $j_\perp=20-50\text{mA}/\text{cm}^2$. The cathode was a
+platinum wire that with an approximate diameter of $0.5\text{mm}$.
 \subsection{Reflectance Measurement}
-In the experiemental parte the reflectivity measurements were carried
-out with a Perkin Elmer Lambda 950 UV-Vis-NIR spectrophotometer. To
+We measured the reflectivity spectra using a {\em Perkin Elmer Lambda 950}
+UV-Vis-NIR spectrophotometer.
+
+To
 calculate the complex refractive index $ \tilde{n}_{_{PS}} = n_{_

### 2020-06-14 paper.tex
Revise up to Sect. 4

@@
 \begin{equation}
-  q_{_{0}} = -\frac{I}{4 \pi \sigma}
-\end{equation}
-at the position $\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ of the
+  q_0 = -\frac{I}{4 \pi \sigma}
+\end{equation}
+at the position $\bm r_0=(x_0, y_0, z_0)$ of the
 tip of the electrode. Note that $q_0$ would be the total charge,
@@
 \begin{equation}
-E_{_{x}}(0, y ,z)= E_{_{x}}(a, y ,z)=E_{{_y}}(x, 0 ,z)=E_{{_y}}(x, b
+E_x(0, y ,z)= E_x(a, y ,z)=E_{{_y}}(x, 0 ,z)=E_{{_y}}(x, b
 ,z)=E_{{_z}}(x, y ,c)=0.
@@
  \begin{eqnarray}
- \frac{d^2}{dz^2}\phi_{\bm G}(z)-G^2\phi_{_{G}}(z)=
+ \frac{d^2}{dz^2}\phi_{\bm G}(z)-G^2\phi_G(z)=
    -\frac{4 \pi}{A} \delta(z),
@@
 
-\section{Experimental Details}
+\section{Procedures}
 \begin{figure}
@@
   \includegraphics[width=.8\textwidth]{paper-5}
-  %\\[12pt]
-  %\includegraphics[scale=0.6]{Images/DE1}
+  % \\[12pt]
+  % \includegraphics[scale=0.6]{Images/DE1}
 
@@
 
+\notaL{Cambié el título, pues tienes una mezcla de experimento y
+  teoría aquí}
 In Fig. \ref{fig:DE1} we show a schematic representation of our
@@
 
-\subsection{Fabrication of PS  GRIN Monolayers}
+\subsection{Fabrication of PS  GRIN Single Layers}
 We manufactured single layer PS structures through an electrochemical
@@
 platinum wire that with an approximate diameter of $0.5\text{mm}$.
+\subsection{Morphological studies}
+\notaL{Cambié el orden}
+The morphologies of the etched porous layers were
+observed using a Hitachi SU1510 scanning electron microscope (SEM)
+with which we measured the thickness $d$ and the porosity $p$ of the
+films at different positions along the sample from its top and side
+views (Fig. \ref{fig:DE1}).
+
 \subsection{Reflectance Measurement}
 We measured the reflectivity spectra using a {\em Perkin Elmer Lambda 950}
-UV-Vis-NIR spectrophotometer.
-
-To
-calculate the complex refractive index $ \tilde{n}_{_{PS}} = n_{_
-  {PS}} - ik_{_{PS}} $ of a porous layer with homogeneous porosity
-and thickness with smooth interfaces to throughout the entire
-structure, the more suitable is the adjustment procedure of the
-experimental reflectance or transmittance spectrum, this is for the
-theoretical part. In the case of the reflectance spectrum. The
-corresponding theoretical calculations were carried using procedure
-for single  smooth layer (monolayer).
+UV-Vis-NIR spectrophotometer. For iterpretation of the data in the
+case of a single PS layer we used
+the standard formula \notaL{referencia} for three media air (0), PS
+(1) and c-Si (2),
  \begin{eqnarray}\label{Eq:ECMR}
-R=\dfrac{r _ {_ {01}}r _ {_ {12}} e^{-2i\delta}}{1+r _ {_ {01}}r _ {_ {12}} e^{-2i\delta}}
+   R=\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}{1+r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}
 \end{eqnarray}
-where $ r_{_ {01}} $ y $ r_{_ {12}} $ are the Fresnel reflectance
-coefficients at the interfaces $aire/PS$ y $PS/c-Si$ which are
-defined in terms of their complex refractive index ($\tilde{n}_{_ {1}}
-$, $\tilde{n}_{_ {2}} $ y $ \tilde{n}_{_ {3}} $), for them
-$r_{_{ij}}=(\tilde{n}_{_{i}}\cos\theta_i-\tilde{n}_{_{j}}\cos\theta_j)/(\tilde{n}_{_{i}}\cos\theta_i+\tilde{n}_{_{j}}\cos\theta_j)$,
-($j=i=0,1,2$), whilst $\delta=2\pi
-d/\lambda\sqrt{\tilde{n}^2_{_{2}}-\tilde{n}^2_{_{1}}\sin \theta_1}$.
- To adjust the reflectance spectrum, the layer thickness is an input
- parameter in the Eq.\ref{Eq:ECMR}. The advantage of this method is
+where $ r_{01} $ y $ r_{12}$ are the Fresnel reflectance
+coefficients at the air/PS and PS/c-Si interfaces \notaL{referencias}
+and $\delta=k_{PS}^\perp d$, where $k_{PS}^\perp$ is
+the component of the wavevector perpendicular to the surface within
+the porous layer of width $d$.
+\notaL{Me tienes que explicar dónde y cómo usaste lo que mencionas en
+  la siguiente frase:
+The advantage of this method is
 the possibility of taking into account the interface roughness effect
@@
 Fresnel \cite{I17, I18, I19}, which represents the roughness of a
- Gaussian distribution.
-\subsection{Morphological studies}
-The morphologies of the etched porous layers (cross-sectional) was
-observed using SEM Hitachi SU1510 scanning electron microscopes
-(Hitachi High Technologies Canada, Inc., Toronto, Canada), the
-thickness  and porosity  of each fabricated  film was measured.
- \subsection{Refraction Indices Monolayer of Porous Silicon GRIN }
-Through the electrochemical anodization of c-Si wafers, Psi monolayers
-were obtained. For the refractive index of each monolayer Psi
-calcalated by ussing  Bruggeman effective medium theory, as we
-consider that we have a homogeneous medium associated with effective
-dielectric function \cite{I20}. This effective dielectric function is
-related to the dielectric functions of the two media, consisting of
-two materials (air and silicon), where it is assumed that all the
-pores or islands of the bulk material experience an average electric
-field; the equation is expressed as follows:
+Gaussian distribution.}
+\subsection{Refraction Index of PS GRIN Single Layers}
+The local refractive index $n_{PS}$ of the PS layer was calculated from its
+porosity $p$ through
+Bruggeman's effective medium theory \cite{I20} \notaL{Elegir y checar:
+  varepsilon o epsilon para funciones dieléctricas}
 \begin{eqnarray}\label{Eq:Brugg}
- p\dfrac{\varepsilon_{_{air}}-\varepsilon_{_{PS}}}{\varepsilon_{_{air}}+\varepsilon_{_{PS}}}+(1-p)\dfrac{\varepsilon_{_{Si}}-\varepsilon_{_{PS}}}{\varepsilon_{_{Si}}+
-   \varepsilon_{_{PS}}}
+ p\frac{1-\varepsilon_{PS}} {1+\varepsilon_{PS}} + (1-p)
+  \frac{\varepsilon_{\text{Si}} - \varepsilon_{PS}}
+  {\varepsilon_{\text{Si}}+\varepsilon_{PS}}
 \end{eqnarray}
- where $ p $ is the volume fraction of air within the PS layer
- (porosity); $\varepsilon_{_{air}}$ is the dielectric function of air;
- $\varepsilon_{_{Si}}$ is the dielectric function of c-Si, and
- $\varepsilon_{_{PS}}$ represents the dielectric function of PS. The
- dielectric function is a complex number and is related to the complex
- refractive index ($\tilde{n} = n - ik$), which is made up of real and
- imaginary parts, as follows $\varepsilon=\tilde{n}^2$. Its real part
- ($ n $) represents the ordinary refractive index when no light
- absorption occurs. The imaginary part ($ k $) is known as the
- extinction coefficient. The extinction coefficient determines the
- absorption rate in the medium \cite{I21}. Porosity can be estimated
- using the Bruggeman approximation, from Eq. \ref{Eq:Brugg} provided
- that the dielectric functions of each component (air and c-Si) are
- known.
-
- \subsection{Fabrication  of Microcavities of Porous Silicon GRIN }
- A conventional way to fabricate the porous silicon microcavity (MC)
- is a defect with a mode located between two DBRs (Distributed Bragg
- Reflector). Alternate layers of high refractive index (H) and low (L)
- refractive index are obtained, satisfying the Bragg condition
- $n_{_{i}}d_{_{i}}=\frac{\lambda_{_{c}}}{4}$  where $ i = H, L $. The
- defect must meet the condition
- $n_{_{L}}d_{_{L}}=\frac{\lambda_{_{c}}}{2}$, and the MC has the
- following sequence: $$ (HL)_6 HH (LH )_6 $$
- Initial data for conventional design we use $\lambda_{_{c}}= 0.67 \mu
- m$, $n_{_{H}} =2,6$, $P_{_{H}} =0.46$, $d_{_{H}}=0.066 \mu m  $,
- $t_{_{H}}=35 s  $ and for $n_{_{L}}= 1,4$,  $P_{_{L}} =0.75$,
- $d_{_{L}}=0.117 \mu m  $, $t_{_{L}}=11 s  $. All of this data is for
- the $ 0 $ point of the sample that is located at one end of the
- sample just below the tip counter-electrode.\\
- Our proposal for the fabrication of porous silicon GRIN microcavities
- uses the same conditions for fabrications of porous silicon GRIN
- monolayers as in section 3.1, and taking the conventional data
- mentioned above. The porous silicon microcavities (PSMC) with
- gradient refractive index (GRIN), were manufactured with different
- current densities ranging from $ 6 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a
- current of $ 5 \ \ mA $, with high refractive index $n_{_{H}} \sim
- 2,761 $ to $ 2,808 $ and porosities from $ 0.44 $ to $ 0.39 $. Also
- for $ 50  $ to $ 20 \ \ mA / cm ^ 2 $, current of $ 38 \ \ mA $, for
- low refractive index $n_{_{L}}\sim 1,448 $ to $ 2,267 $ and with the
- corresponding  porosities of $ 0.75 $ to $ 0.64 $. Using our
- calibration ratio to design GRIN structures,  the corresponding
- current density for each measurement point.
+where the porosity $p$ is the volume fraction of air within the PS
+layer, $\varepsilon_{Si}$ is the dielectric function of c-Si, and
+$\varepsilon_{PS}=n_{PS}^2$ is the dielectric function of the PS.
+\notaL{Quité frases irrelevantes.}
+\subsection{Fabrication  of GRIN PS Microcavities}
+After characterizing the preparation of single PS GRIN layers, we
+fabricated PS GRIN microcavities (MC) as specific defects between two distributed Bragg
+mirrors  (DBR). Alternate quarter wavelength plates of high (H) and low (L)
+refractive indices $n_i$ of widths $d_i$, $i=H,L$ were prepared satisfying the Bragg condition
+$n_id_i=\frac{\lambda_c}{4}$ at a given design
+wavelength $\lambda_c$ and at a position $A$ (Fig. \ref{fig:DE1} which
+we chose as that directly below the point-like electrode. The defect
+was chosen as a half-wavelength low index layer of width $d_d$ such that
+$n_Ld_L=\lambda_c/2$, and the MC has the
+following sequence: $(HL)_6HH(LH )_6$. \notaL{Hay algo mal. La
+  película de $\lambda/2$ fue de alto o de bajo índice? En una parte
+  dices una cosa y en otra otra. ¿Será $(HL)_jHLLH(LH)_6$? ¿O será
+  $(LH)_6LL(HL)_6$? ¡Muy descuidado!}
+We chose $\lambda_c= 0.67 \mu\text{m}$. For the high index layers we
+chose a current $I_H=5\text{mA}$ which corresponded to a current density
+$j_{HA\perp}= 6\text{mA}/\text{cm}^2$ below the tip \notaL{checar}, and yielded
+$n_H =2.6$, corresponding to a porosity \notaL{P mayúscula
+  es porosidad, o p minúscula. Checar consistencia} $P_H =0.46$, and a
+width $d_H=0.066 \mu\text{m}$, which required an attack time of
+$t_H=35 \text{s}$. The corresponding parameters for the low density
+layers were $I_L=38\text{mA}$, $j_{LA\perp}=50\text{mA}/\text{cm}^2$, $n_L= 1.4$,  $P_L =0.75$,
+$d_L=0.117 \mu \text{m}$, and $t_L=11 \text{s}$. For the rest of the
+sample the current density, porosity, index of refraction and width
+varied, yielding a GRIN MC.
 
@@
             GRIN. Alternate layers are obtained of high (H) refractive
-            index $n_{_{Hi}}$ and low (L) refractive index
-            $n_{_{Li}}$, where $N_{_{H}}$ is the number of layers for
-            $n_{_{Hi}}$ and $N_{_{L}}$ is the number of layers for
-            $n_{_{Li}}$. Then,  $d_{_{Hi}}$ is the monolayer thickness
-            of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$
-            is the monolayer thickness of $n_{_{Hi}}$ at that
-            measurement point. Therefore,  $d_{_{i}}$ is the total
+            index $n_{Hi}$ and low (L) refractive index
+            $n_{Li}$, where $N_H$ is the number of layers for
+            $n_{Hi}$ and $N_L$ is the number of layers for
+            $n_{Li}$. Then,  $d_{Hi}$ is the monolayer thickness
+            of  $n_{Hi}$ at that measurement point and $d_{Li}$
+            is the monolayer thickness of $n_{Hi}$ at that
+            measurement point. Therefore,  $d_i$ is the total
             thickness calculated for each of the measurements,
             defining a i = $ A, B, C$. Having the following
-            relationship $d_{_{i}} =
-            (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) +
-            (2d_{_{Hi}})$. }}
+            relationship $d_i =
+            (N_{Hi}d_{Hi})+(N_{Li}d_{Li}) +
+            (2d_{Hi})$. }}
 	\label{fig:MCGRIN0}
@@
 layers. Alternate layers are obtained of high (H) refractive index
-$n_{_{Hi}}$ and low (L) refractive index $n_{_{Li}}$, where $N_{_{H}}$
-is the number of layers for  $n_{_{Hi}}$ and $N_{_{L}}$ is the number
-of layers for $n_{_{Li}}$. Then,  $d_{_{Hi}}$ is the monolayer
-thickness of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$ is
-the monolayer thickness of $n_{_{Hi}}$ at that measurement
-point. Therefore,  $d_{_{i}}$ is the total thickness calculated for
+$n_{Hi}$ and low (L) refractive index $n_{Li}$, where $N_{H}$
+is the number of layers for  $n_{Hi}$ and $N_L$ is the number
+of layers for $n_{Li}$. Then,  $d_{Hi}$ is the monolayer
+thickness of  $n_{Hi}$ at that measurement point and $d_{Li}$ is
+the monolayer thickness of $n_{Hi}$ at that measurement
+point. Therefore,  $d_i$ is the total thickness calculated for
 each of the measurements, defining a i = $ A, B, C$. Having the
-following relationship $d_{_{i}} =
-(N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$.
-Initial data for conventional design we use  $\lambda_{_{c}}= 0.67 \ \
-\mu m$, $n_{_{H}} =2.6$, $P_{_{H}} =0.46$, $d_{_{H}}=0.066 \ \ \mu m
-$, $t_{_{H}}=35 s  $ y para  $n_{_{L}}= 1.4$,  $P_{_{L}} =0.75$,
-$d_{_{L}}=0.117 \ \ \mu m  $, $t_{_{L}}=11 s  $. All these data are
+following relationship $d_i =
+(N_{Hi}d_{Hi})+(N_{Li}d_{Li}) + (2d_{Hi})$.
+Initial data for conventional design we use  $\lambda_c= 0.67 \ \
+\mu m$, $n_H =2.6$, $P_H =0.46$, $d_H=0.066 \ \ \mu m
+$, $t_H=35 s  $ y para  $n_L= 1.4$,  $P_L =0.75$,
+$d_L=0.117 \ \ \mu m  $, $t_L=11 s  $. All these data are
 for the point $ 0 $ which is located at one end of the sample just
@@
 / cm ^ 2 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a current of $ 5 \ \ mA $,
-for a $t_{_{H}}=35 s $, with a high refractive index $n_{_{H}} \sim$ $
-2,661$ to $ 2,808$ and porosities of $P_{_{H}} \sim$ $ 0.45 $ to $
+for a $t_H=35 s $, with a high refractive index $n_H \sim$ $
+2,661$ to $ 2,808$ and porosities of $P_H \sim$ $ 0.45 $ to $
 0.39 $. Also for $ 44 \ \ mA /cm^2 $ to $ 24 \ \ mA / cm^2 $, current
-of $ 38 \ \ mA $, using $t_{_{H}}=11 s$  for low refractive index
-$n_{_{L}}\sim$ $ 1,448 $ to $ 2,267 $ and with porosities of
-$P_{_{H}} \sim$ $0.75 $ to $ 0.64 $. The porosity was calculated with
+of $ 38 \ \ mA $, using $t_H=11 s$  for low refractive index
+$n_L\sim$ $ 1,448 $ to $ 2,267 $ and with porosities of
+$P_H \sim$ $0.75 $ to $ 0.64 $. The porosity was calculated with
 the calibration curve exposed in the ($ P = 0.3J^{0.24} $). And the
@@
        of the porous silicon microcavity GRIN at the measurement
-       points and the total thickness we find it as $d_{_{i}} =
-       (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$
+       points and the total thickness we find it as $d_i =
+       (N_{Hi}d_{Hi})+(N_{Li}d_{Li}) + (2d_{Hi})$
        defining $ i = $ A, B, C. Which resulted in (measured /
@@
 porous silicon microcavity GRIN at the measurement points and the
-total thickness we find it as $d_{_{i}} =
-(N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$ defining $ i
+total thickness we find it as $d_i =
+(N_{Hi}d_{Hi})+(N_{Li}d_{Li}) + (2d_{Hi})$ defining $ i
 = $ A, B, C. Which resulted in (measured / simulation) $ 2.25 / 2.31 \

### 2020-06-15 paper.tex

@@
     conductor. The tip of the electrode is a thin insulated wire with
+    just the tip uncovered and located at $ \vec{r}_0 $ within the
+    liquid.\notaL{\sout{Quité el tipo de letra del pie de figura. Que la pongan en la
+      revista.}}\notaL{\sout{En la punta pusiste dos esferas. Quítalas y sólo
+    pon un puntito dorado del ancho del cable. Muestra que la base
+    está aterrizada}}\notaL{\sout{Indica el voltaje y la
+    corriente}}\notaL{\sout{¿Está bien la polaridad de la batería?}}}
     just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
@@
 \end{equation}
+This problem may be solved readily using image charge theory \cite{T1,T2}
+\notaL{\sout{ref}}. The potential within the electrolytic cell coincides the
+the field within an infinite vacuum containing the point charge
 This problem may be solved readily using image charge theory
@@
 convergence properties. The potential can be obtained
+using the Ewald summation technique \cite{T3,T4,T5}\notaL{\sout{ref}}, which yields
+ two rapidly convergingseries, one in real space and another one in reciprocal space.
+Nevertheless, as we need the potential and the field to obtain the
+current density on the surface of the sample on which there are no
+real nor image charges, we may perform a somewhat simpler planewise
+summation, where we first obtain the potential and field produced by a
+simple periodic lattice of charges using a fast convergent sum over the 2D
+reciprocal vectors, and then sum over the charges that form the basis
+of the 2D {\em crystal} plane and finally sum over all the
+ planes \cite{T6,T7} \notaL{\sout{ref}}.
 using the Ewald summation technique \notaL{ref}, which yields two rapidly converging
@@
  \begin{eqnarray}
+ \frac{d^2}{dz^2}\phi_{_{\bm G}}(z)-G^2\phi_{_{\bm G}}(z)=
  \frac{d^2}{dz^2}\phi_{\bm G}(z)-G^2\phi_G(z)=
@@
             defining a i = $ A, B, C$. Having the following
+            relationship $d_{_{i}} =
+            (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) +
+            (2d_{_{Hi}})$. }
             relationship $d_i =

### 2020-06-15 paper.tex
Modifice el paper.tex y añadi la grafica celda1.png

@@
     está aterrizada}}\notaL{\sout{Indica el voltaje y la
-    corriente}}\notaL{\sout{¿Está bien la polaridad de la batería?}}}
+    corriente}}\notaL{\sout{¿Está bien la polaridad de la batería?}}
     just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
@@
             defining a i = $ A, B, C$. Having the following
-            relationship $d_{_{i}} =
-            (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) +
-            (2d_{_{Hi}})$. }
-            relationship $d_i =
-            (N_{Hi}d_{Hi})+(N_{Li}d_{Li}) +
-            (2d_{Hi})$. }}
+            relationship $d_i =(N_{Hi}d_{Hi})+(N_{Li}d_{Li}) +
+            (2d_{Hi})$. }
 	\label{fig:MCGRIN0}

### 2020-06-15 Programas/GrinJI.pl
Pase mi programa para J/I

@@ -1,0 +1,175 @@
+#!/usr/bin/env perl
+
+use strict;
+use warnings;
+
+use Getopt::Long;
+use List::Util;
+use POSIX qw(DBL_MAX);
+use PDL;
+use PDL::NiceSlice;
+use PDL::FFTW3;
+use PDL::Complex;
+use PDL::Graphics::Gnuplot;
+use constant {PI=>4*atan2(1,1), LM=>log(DBL_MAX)};
+use IO::Prompter;
+#use Chart::Gnuplot;
+#use GD::Graph;
+
+#Calculate current density in an electrolytic cell with a 'point'
+#electrode, to build GRIN structures.
+#Notes GX
+#Eq. Gx33
+
+#Normalize to I and to the area.
+my $a; #size of cell along x
+my $b; #size of cell along y
+my $C; #size of cell along z (water height)
+my ($X0, $Y0, $Z0); #positioin of electrode
+my $Z; #height to evaluate current.
+my $N; #2N+1=number of points along each direction
+my $I; #corriente
+# $M; #2*$M+1=size of mask in reciprocal space
+Getopt::Long::Configure('no_ignore_case');
+GetOptions(
+    'a=f'=>\$a, 
+    'b=f'=>\$b,   
+    'C=f'=>\$C,
+    'X0=f'=>\$X0,
+    'Y0=f'=>\$Y0,
+    'Z0=f'=>\$Z0,
+    'Z=f'=>\$Z,
+    'N=f'=>\$N,
+    'I=f'=>\$I,
+    #'M=f'=>\$M
+    )
+    or usage();
+usage("Undefined parameters") unless List::Util::all {defined $_}
+($a, $b, $C, $X0, $Y0, $Z0, $Z, $I, $N); #, $M);
+my $A=$a*$b; #area celda
+my $u=sqrt($A); #unidades 
+my $a1=$a/$u; # largo adimensional
+my $c=$C/$u;  # altura de liquido adimensional
+my $x0=$X0/$u;
+my $y0=$Y0/$u;
+my $z0=$Z0/$u;
+my $z=$Z/$u;
+my $b1=1/$a1; #So area=1, this is our unit of area, and from here, distance
+#Real space
[…]

### 2020-06-15 paper.tex
Revise upto fig. 7

--- 2020-06-14 paper.tex
@@
 \section{Introduction}
-
+\label{sec:introduction}
+\notaL{Debiste poner etiquetas en todas las subsecciones y secciones, y
+  ecuaciones y figuras.}
 \notaL{No entiendo nada de la introducción}
@@
 
-\section{Theory}
+\section{Theory} \label{sec:theory}
 \subsection{Calculation of the current density}
+\label{sec:calc-curr-dens}
 \notaL{check where acronyms are first defined}
@@
 \section{Procedures}
+\label{sec:procedures}
 \begin{figure}
@@
 \subsection{Fabrication of PS  GRIN Single Layers}
+\label{sec:fabrication-ps-grin}
 We manufactured single layer PS structures through an electrochemical
@@
 electrolytic mixture of aqueous hydrofluoric
-acid (HF) (concentration: 48 $ \% $ wt), glycerol (purity: 99.8 $ \% $
-wt) and ethanol (purity: 99.9 $ \%$ wt ) in a 3:7:1 volume ratio,
-respectively. After the anodizing process, the samples were rinsed with
+acid (HF) (concentration 48\% wt), glycerol (purity 99.8 \% wt) and
+ethanol (purity 99.9\% wt) in a 3:7:1 volume ratio. After the
+anodizing process, the samples were rinsed with
 ethanol (purity: 99.9 $ \% $  wt). The electrolytic cell had the shape
@@
 \subsection{Morphological studies}
+\label{sec:morph-stud}
 \notaL{Cambié el orden}
@@
 \subsection{Reflectance Measurement}
+\label{sec:refl-meas}
 We measured the reflectivity spectra using a {\em Perkin Elmer Lambda 950}
@@
 Gaussian distribution.}
+
 \subsection{Refraction Index of PS GRIN Single Layers}
+\label{sec:refraction-index-ps}
 The local refractive index $n_{PS}$ of the PS layer was calculated from its
@@
   \frac{\varepsilon_{\text{Si}} - \varepsilon_{PS}}
-  {\varepsilon_{\text{Si}}+\varepsilon_{PS}}
+  {\varepsilon_{\text{Si}}+\varepsilon_{PS}}=0
 \end{eqnarray}
+\notaL{Te faltaba la igualdad}
 where the porosity $p$ is the volume fraction of air within the PS
@@
 \subsection{Fabrication  of GRIN PS Microcavities}
+\label{sec:fabrication-grin-ps}
 After characterizing the preparation of single PS GRIN layers, we
@@
 \section{Discussion and Results}
-\subsection{Simulation of the EMPCGRIN model}
- To test the developed  idea in the theoretical section, we find a
- relation of the tip of the counter electrode that acts similarly as a
- point charge and the current density for a geometry in an
- electrolytic box and solve the electrostatic equations with suitable
- boundary conditions. Resulting in an electrostatic model for photonic
- crystals with a refractive index with gradient (EMPCGRIN).
+\label{sec:discussion-results}
+\subsection{Current Density}
+\label{sec:current-density}
 \begin{figure}
   \centering
-  \includegraphics[scale=0.7]{Images/G123}
-  \caption{\emph{ Simulation to calculate the current density in
-      a structure with gradient refractive index (GRIN) produced
-      by electrochemical attack on crystalline silicon to
-      produce porous silicon (PS), with a current density
-      profile $ J (mA / cm ^ 2 ) $ normalized with the electric
-      current $ I (mA) $, we have $ J / I \sim 0.5 \ \ a \ \ 1.2
-      (cm^{-2}) $, for a cell of $ a = 2.03 \ \ cm $ y $ b =
-      0.62 \ \ cm $, with an electrode height $ Z_0 = 0.96 \ \
-      cm $} Eq. (\ref{Eq:J})}.
+  \includegraphics[width=\textwidth]{Images/G123}
+  \caption{Normalized current density $j_\perp(z,0,0)/I$ calculated through
+    Eq. (\ref{Eq:J}) for a
+    system as in Figs. \ref{f:celda} and \ref{fig:DE1} for a cell of
+    length $a = 2.03\text{cm}$ and width $b=0.62\text{cm}$, for a
+    point-like electrode at $\bm r_0=(0.2\text{cm},
+    0.4\text{cm},0.98\text{cm})$ (top panel). Normalized current
+    along the line $y=?$ (bottom panel). \notaL{qué valor de $y$ usaste para la
+      gráfica de abajo?} \notaL{Puse $x_0$
+      y $y_0$ que faltaban. Checale. Se me hace raro que no esté
+      centrado en la celda a lo ancho. ¿No está debería estar en
+      $y_0=0.31\text{cm}?$} \notaL{Cambia los letreros, $J$ por
+      $j_\perp$. La ordenada no es a, sino $x$ y la abcisa no es b
+      sino $y$}. }
   \label{fig:DR1}
 \end{figure}
-We consider Fig. \ref{fig:DR1} which come from solving
-Eq. (\ref{Eq:J}), calculating the current density as a function of the
-rectangular cell area of $1,206 \ \ cm^2 $,  the programming with the
-PERL PDL package and corresponding graph in gnuplot. We optimize the
+\notaL{Checar consistencia notación. $x_0$, $y_0$ y $z_0$ en
+  minúsculas. Igual $j_\perp$.}
+In Fig. \ref{fig:DR1} we show the current density $j_\perp(x,y,0)$ calculated through
+Eq. \eqref{Eq:J} at the surface of the sample for the cell we built
+(see Figs. \ref{f:celda} and \ref{fig:DE1}) with length
+$a=2.03\text{cm}$ and width $b = 0.62\text{cm}$, the height of the
+solution was taken as $c=1\text{cm}$ and we set the tip of the
+electrode at $\bm
+r_0=(x_0,y_0,z_0)=(0.2\text{cm},0.4\text{cm},0.96\text{cm})$
+\notaL{Descuidado. En la figura dice 0.98, no 0.96}.
+\notaL{¿Por qué usaste estos valores?}
+\notaL{Esto no es interesante: the programming with the
+  PERL PDL package and corresponding graph in gnuplot.}
+\notaL{¿Qué significa esto?:We optimize the
 appropriate values so that our current density adequately attacks
-crystalline silicon, giving the gradient effect. We use as length $a =
-2.03 \ \ cm $ and width $b = 0.62 \ \ cm $ the height of the solution
-is $ c = 1 \ \ cm $ and we could locate the tip of the electrode at $
-R_0 = (X_0 = 0.2 , \ \ Y_0 = 0.4 \ \, Z_0 = 0.96) \ \ cm $ and
-evaluated at the surface on the silicon interface, in the plane $ Z =
-0 $. In this same Figure \ref{fig:DR1}, we obtain a current density
-profile $ J (mA / cm^2) $ normalized with the electric current $ I
-(mA) $, we have $ J / I \sim 1.2 \ \ a \ \ 0.5 (cm ^{-2}) $, as we see
-in Fig. \ref{fig:DR1} a) an effect that happens on the surface of the
-sample, a change of contrate due to the different densities of
-attacked currents. We see the decay behavior that the profile has as
-Fig. \ref{fig:DR1} b) which is a cut on the axis of $ a $. When we
-vary the currents we can observe the behavior of changes in the
-normalized current density, with the data obtained through the
-simulation we could have a better optimization in the design of porous
-silicon proposing a new and novel experimental arrangement, in the
-same way we can give ourselves an idea by means of the graph of how
-the attack would be and the formal side of the pores in the silicon.
-
-\subsection{Monolayers GRIN Porous Silicon }
+crystalline silicon, giving the gradient effect.}
+For these parameters we obtained $ j_\perp/I\sim
+0.5-1.2\text{cm}^{-2}$
+\notaL{Quité el resto del párrafo pues no entendí nada.}
+
+\subsection{PS GRIN Single Layer }
+\label{sec:ps-grin-single}
+\notaL{Quité la figura pues no añade nada}
+\notaL{Quité la descripción, pues está arriba}
 \begin{figure}
   \centering
-	\includegraphics[scale=.3]{Images/celdan2}
-	\caption{\emph{ Mechanical 3D modeling, design of the
-            electrochemical cell where we can see the shape of a prism
-            giving the required and necessary data for the
-            experiments. The design of the cell used is $ 1,206 \ \ cm
-            ^ 2 $ (this is the area attacked in the process), the area
-            attacked is rectangular ($ 0.62 \ \ cm \times 2.03 \ \ cm
-            $) and a height ( $ 1.2 \ \ cm $) a) Complete cell b) Cell
-            without top cover and c) Top view}}
-	\label{fig:por1}
-\end{figure}
-We can see in Fig. \ref{fig:por1}, 3D modeling the mechanical design
-for the electrochemical cell  better optimization in manufacturing
-silicon pores where we can see the shape of a prism giving the
-required data. The design of the cell used is $ 1,206 \ \ cm ^ 2 $
-(this is the area attacked in the process), the area attacked is
-rectangular ($ 0.62 \ \ cm \times 2.03 \ \ cm $) and a height ( $ 1.2
-\ \ cm $), all this in order to optimize our experiments adjusted to
-all the needs that this required.
-\begin{figure}
-  \centering
-  \includegraphics[scale=.5]{Images/SPgrin51}
-  \caption{\emph{a) Silicon sample attacked with an electrolytic
-      mixture of aqueous hydrofluoric acid (HF) (concentration:
-      48 $ \% $  wt), glycerol (purity: 99.8 $ \% $  wt) and
-      ethanol (purity: 99.9 $ \% $  wt ) in 3: 7: 1 volume
-      ratio, respectively. Obtaining a monolayer of porous
-      Silicon with GRIN G1 with an initial current of G1 (5 mA),
-      with an attack time of 600s. Three different locations are
-      considered, denoted as follows, A (0.3cm) and B (0.8cm)
-      and C (1.7cm). b) Reflectance measurements to know the
-      optical properties at each of the points and the
-      adjustments that were produced by means of the equation
-      \ref{Eq:ECMR}. c) We have the indices of refraction of the
-      complex porous silicon GRIN, where we calculate the real
-      and imaginary part by means of the equation
-      \ref{Eq:Brugg}. for different porosities at each point, A
-      (P = 0.44), B (P = 0.42) and C (P = 0.40) } }
+  \includegraphics[width=\textwidth]{Images/SPgrin51}
+  \caption{(a)  Sample $G_1$ prepared as described in
+     \ref{sec:fabrication-ps-grin} using a current $I=5 \text{mA}$
+    during a time $t=600\text{s}$. We indicate three regions $A$,
+    $B$, and $C$ centered at positions at positions,
+    $x_A=0.3\text{cm}$ \notaL{Atrás habías dicho que era justo abajo
+      del electrodo. ¿Es cierto o no? ¿Dónde estaba el electrodo? ¿Qué
+    altura tenía el agua? ¿Igual que en la sección previa?}, $x_B=0.8\text{cm}$ and
+    $x_C=1.7\text{cm}$. \notaL{¿Cuánto vale $y$?} (b) Reflectance
+    spectra measured at the center of regions $A$, $B$, and $C$ and fit
+    using Eq. \eqref{Eq:ECMR}.\notaL{¿Cuáles parámetros se ajustaron y
+      cuáles se midieron independientemente}\notaL{Para que no se vean
+      tan chicas las figuras, quita las R's y los números en el segundo
+      renglon, excepto en el extremo izquierdo, y pega las tres
+      figuras una tras la otra. Haz lo mismo en el tercer renglón,
+      quitando dos de los letreros Refractive index, pero antes
+      asegúrate de usar la misma escala en las tres figuras} (c)
+    Corresponding complex indices of refraction $n+ik$ obtained from
+    Eq. \eqref{Eq:Brugg} using the fitted porosities $p_A=0.44$,
+    $p_B=0.42$, and $p_C= 0.40$ at the chosen positions. \notaL{En las
+      figuras escribe A, B y C en lugar de
+      Point A, Point B y Point C. Escribe $p_A$, $p_B$ y $p_C$ en lugar
+      de la palabra Porosity. Escribe $n$ y $k$ nada más, sin la
+      palabra Real ni Imaginary. Usa Theory en lugar de
+      Simulation. Usa línea a trazos para la parte
+      imaginaria. Alínea todos los letreros. En inglés, los rótulos
+      a), b) y c) se escriben como (a), (b) y (c), aunque creo que se
+      pueden eliminar (porque además, no los alineaste bien). }
+  \notaL{A ojo no se notan las diferencias en epsilon. Mejor junta las
+  tres partes reales en una sola gráfica y las tres partes imaginarias
+en otra y ponerlas una al lado de la otra.}}
   \label{fig:DR3}
 \end{figure}
- The Fig. \ref{fig:DR3} a) three locations at different points are
- considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B (0.8 \ \
- cm) $ and $ C (1.7 \ \ cm) $, from the sample of PS GRIN $ G1 (I = 5
- mA) $. Also the Fig. \ref{fig:DR3}. b), we have the reflectance
- measurements to know the optical properties and the adjustments that
- were produced by means of the equation \ref{Eq:ECMR}. In the
- Fig. \ref{fig:DR3} c) are indices of refraction of the porous silicon
- complex GRIN, where we calculate the real and imaginary part by means
- of Eq. \ref{Eq:Brugg} for different porosities at each point, $ A (P
- = 0.44) $, $ B (P = 0.42) $ and $ C (P = 0.40) $. Location $ A $ is
- closest to the electrode, while location $ C $ is furthest to the
- other end of the sample. Since the current density is applied from
- one end, the field lines attack the sample laterally to the silicon
- wafer, in the present configuration, an assembly was made based on
- the simulated data shown in Fig. \ref{fig:DR1} the experimental part
- was taken a platinum electrode covering its surface, leaving only a
- very small area, as if it were a tip. The electrochemical reaction
- takes place when we apply currents from an anode end (electrode tip)
- to the silicon substrate (resistivity $ 0.002 - 0.005  \Omega \cdot
- cm $), through an electrolyte forming a current circuit. The
- reflectance spectra of the newly recorded G1 samples measured at
- points $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm)
- $ are presented in Fig. \ref{fig:DR3} b), a numerical reflectivity
- adjustment was performed using the transfer matrix method for the
- case of a porous monolayer in Si. It should be noted that the
- adjustment made was considered a spectral range of the wavelength of
- the experimental reflectivity spectra for which the silicon can be
- considered the complex index and thus find the refractive index of
- the complex porous silicon with the purpose of determining the
- porosity and the experimental physical thickness (nm) by means of the
- SEM. The formation of PS GRIN in the thickness occurs due to the
- variation in the concentration of the voids available at the Si
- electrolyte interface, therefore, an increase in the applied lateral
- current density increases the dimension of the pores and their
- depth. Thus, the extent of the porous film showing a gradient that
- can be controlled from the lateral current density.
+ In Fig. \ref{fig:DR3} we show a photograph of one of our single layer PS GRIN
+ structures, $G_1$, prepared as described in
+ \ref{sec:fabrication-ps-grin} applying a current $I=5\text{mA}$ for
+ $t=600\text{s}$. We employed the same geometry as described in
+ Sec. \ref{sec:current-density} \notaL{Lo inventé. ¿Es cierto?}
+The position of electrode corresponds to the upper left side of the
+photograph. The variation of the optical properties across the
+sample is evident. We chose three positions $x_A=0.3\text{cm}$,
+$x_B=0.8\text{cm}$ and $x_C=1.7\text{cm}$ \notaL{¿valor de y?} on
+which we measured the reflectance spectra, also shown in the figure.
+We fitted the measurements using Eqs. \eqref{Eq:ECMR} and
+\eqref{Eq:Brugg} using the local porosity and the depth of the layer
+as adjustable parameters. We obtained $p_A=0.44$, $p_B=0.42$, and
+$p_C= 0.40$. \notaL{Falta decir cuáles fueron las profundidades}
+Location $A$ is
+closest to the electrode, while location $ C $ is the furthest.
+\notaL{Quité una frase sin sentido.}
+We also show in Fig. \ref{fig:DR3} the wavelength dependence of
+ the complex index of refraction corresponding to the fitted porosities.
+\notaL{Quité otra frase que no entendí, pero que me generó una duda:
+  la profundidad la ajustaste ópticamente o la mediste en SEM y luego
+  hiciste el ajuste a la reflectancia?}
+
 \begin{figure}
@@
 \subsection{GRIN Porous Silicon Microcavities}
+\label{sec:grin-porous-silicon}
 \begin{figure}
@@
 \section{conclusion}
+\label{sec:conclusion}
 The necessary expressions for the potential components were derived,
@@
 \section{Acknowledgments}
+\label{sec:acknowledgments}
 % \backmatter

### 2020-06-15 paper.tex

@@
     conductor. The tip of the electrode is a thin insulated wire with
+    just the tip uncovered and located at $ \vec{r}_0 $ within the
+    liquid.\notaL{\sout{Quité el tipo de letra del pie de figura. Que la pongan en la
+      revista.}}\notaL{\sout{En la punta pusiste dos esferas. Quítalas y sólo
+    pon un puntito dorado del ancho del cable. Muestra que la base
+    está aterrizada}}\notaL{\sout{Indica el voltaje y la
+    corriente}}\notaL{\sout{¿Está bien la polaridad de la batería?}}
     just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
@@
   \label{eq:phifourier}
-  \phi(\bm r)=\sum_{\bm G}\phi_{\bm G}(z)e^{i\bm G\cdot\bm r_\|}
-\end{equation}
-where $\phi_{\bm G}(z)$ is the Fourier coefficient of the potential at
+  \phi(\bm r)=\sum_{\bm G}\phi_{_{\bm G}}(z)e^{i\bm G\cdot\bm r_\|}
+\end{equation}
+where $\phi_{_{\bm G}}(z)$ is the Fourier coefficient of the potential at
 the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
@@
     point-like electrode at $\bm r_0=(0.2\text{cm},
-    0.4\text{cm},0.98\text{cm})$ (top panel). Normalized current
+    0.4\text{cm},0.96\text{cm})$ (top panel). Normalized current
     along the line $y=?$ (bottom panel). \notaL{qué valor de $y$ usaste para la
@@
             defining a i = $ A, B, C$. Having the following
-            relationship $d_i =
-            (N_{Hi}d_{Hi})+(N_{Li}d_{Li}) +
-            (2d_{Hi})$. }}
+            relationship $d_i =(N_{Hi}d_{Hi})+(N_{Li}d_{Li}) +
+            (2d_{Hi})$. }
 	\label{fig:MCGRIN0}
@@
   Photonics, 4(4), 909-914.
+
+  \bibitem{T1}Jackson, John David. \textquotedblleft
+  \emph{Classical electrodynamics.}\textquotedblright (1999): 841-842.
+
+\bibitem{T2}Griffiths, David J. \textquotedblleft
+\emph{Introduction to electrodynamics.}\textquotedblright
+ New Jersey: Prentice Hall, 1962.
+
+ \bibitem{T3} Mahfoud Belhadj, Howard E. Alper, and Ronald M. Levy. \textquotedblleft
+ \emph{ Molecular dynamics simulations of water with Ewald summation
+ 	for the long range electrostatic interactions.}\textquotedblright Chemical
+  Physics Letters, 179(1-2):13–20, 1991.
+   \bibitem{T4}A. Bródka.\textquotedblleft
+   \emph{ Ewald summation method with electrostatic layer correction for
+  interactions of point dipoles in slab geometry.}\textquotedblright Chemical
+Physics Letters, 400(1):62–67, December 2004.
+ \bibitem{T5} A. Grzybowski, E. Gwóźdź, and A. Bródka.\textquotedblleft
+ \emph{ Ewald summation of electrostatic interactions in molecular dynamics
+ 	 of a three-dimensional system with periodicity in two directions.}\textquotedblright
+  Physical Review B, 61(10):6706–6712, March 2000.
+
+ \bibitem{T6} Kratzer, Peter, and Jörg Neugebauer. \textquotedblleft \emph{The basics of
+ 	electronic structure theory for periodic systems.}\textquotedblright
+  Frontiers in chemistry 7 (2019).
+ \bibitem{T7} Charles Kittel. \textquotedblleft \emph{Introduction to Solid State
+ 	 Physics.}\textquotedblright Wiley, Hoboken, NJ, 8 edition, 2005.
+
 \bibitem{I17} Dariani RS, Ebrahimnasab S (2014). \textquotedblleft

### 2020-06-15 Programas/GrinJI.pl
Le quité loas retornos de carro al programa

@@ -32,8 +32,8 @@ my $I; #corriente
 # $M; #2*$M+1=size of mask in reciprocal space
 Getopt::Long::Configure('no_ignore_case');
 GetOptions(
-    'a=f'=>\$a, 
-    'b=f'=>\$b,   
+    'a=f'=>\$a,
+    'b=f'=>\$b,
     'C=f'=>\$C,
     'X0=f'=>\$X0,
     'Y0=f'=>\$Y0,
@@ -47,7 +47,7 @@ GetOptions(
 usage("Undefined parameters") unless List::Util::all {defined $_}
 ($a, $b, $C, $X0, $Y0, $Z0, $Z, $I, $N); #, $M);
 my $A=$a*$b; #area celda
-my $u=sqrt($A); #unidades 
+my $u=sqrt($A); #unidades
 my $a1=$a/$u; # largo adimensional
 my $c=$C/$u;  # altura de liquido adimensional
 my $x0=$X0/$u;
@@ -84,8 +84,8 @@ my $Y=$y*$u;
 my $w=gpwin;
 #figura 3d Grin
 $w->plot3d({title=>["{/Time*2 a=$a cm, b=$b cm, C=$C cm, R0=($X0,$Y0,$Z0)cm, Z=$Z}",textcolor=>'"black"'],
-	   xrange=>[0,$a], yrange=>[0,$b], view=>['equal','xy'],xlabel=>["{/Times*2 a(cm)}", textcolor=>'"black"'] ,ylabel=>["{/Times*2 b (cm)}",textcolor=>'"black"'],xtics=>{font=>"Time,12"}, ytics=>{font=>"Time,12"}}, 
-	  with=>'pm3d', $X, $Y, $jR); 
+	   xrange=>[0,$a], yrange=>[0,$b], view=>['equal','xy'],xlabel=>["{/Times*2 a(cm)}", textcolor=>'"black"'] ,ylabel=>["{/Times*2 b (cm)}",textcolor=>'"black"'],xtics=>{font=>"Time,12"}, ytics=>{font=>"Time,12"}},
+	  with=>'pm3d', $X, $Y, $jR);
 
 #figura vista desde arriba
 my $gw=PDL::Graphics::Gnuplot->new();
@@ -119,8 +119,8 @@ my $N; #2N+1=number of points along each direction
 my $I; #corriente
[…]

### 2020-06-16 paper.tex
Modifique y respondi algunas observaciones

@@
 \newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
+\newcommand{\notaC}[1]{{\color{red}+C:#1+}}
 \title{\textbf{Optimization of Porous Silicon Gradient Refractive
@@
 with
-$\sigma$ the conductivity, $\bm E=-\nabla\varphi$ the electric field,
-and $\varphi$ the electric potential. For a
+$\sigma$ the conductivity, $\bm E=-\nabla\phi$ the electric field,
+and $\phi$ the electric potential. For a
 stationary situation\notaL{Latex usa nabla como el nombre de
@@
   \label{eq:laplace}
-\nabla^{2} \varphi=0.
+\nabla^{2} \phi=0.
 \end{equation}
@@
   \label{eq:poisson}
-  \nabla^2\varphi=-4\pi q_0\delta(\bm r-\bm r_0),
+  \nabla^2\phi=-4\pi q_0\delta(\bm r-\bm r_0),
 \end{equation}
@@
   \label{eq:ground}
-  \varphi(x,y,0)=0,
+  \phi(x,y,0)=0,
 \end{equation}
@@
 This problem may be solved readily using image charge theory \cite{T1,T2}
-\notaL{\sout{ref}}. The potential within the electrolytic cell coincides the
-the field within an infinite vacuum containing the point charge
-This problem may be solved readily using image charge theory
-\notaL{ref}. The potential within the electrolytic cell coincides
+\notaL{\sout{ref}}. The potential within the electrolytic cell coincides
 within the region $0\le x\le a$, $0\le y \le b$, $0\le z\le c$
@@
  planes \cite{T6,T7} \notaL{\sout{ref}}.
-using the Ewald summation technique \notaL{ref}, which yields two rapidly converging
-series, one in real space and another one in reciprocal space.
-Nevertheless, as we have to evaluate the potential and the field on
-the bottom of the cell to obtain the current density which attacks the
-surface of the sample, and as there are no
-real nor image charges there, we may perform a somewhat simpler planewise
-summation, where we first obtain the potential and field produced by a
-simple periodic lattice of charges using a fast convergent sum over the 2D
-reciprocal vectors, we then sum over the charges that form the basis
-of the 2D {\em crystal} plane and we finally sum over all the planes \notaL{ref}.
-
 We consider first a system made of identical unit charges
@@
   \label{eq:poissonRed}
-  \nabla^2\varphi(\bm r)=-4\pi\sum_{\bm R}\delta(\bm r_\|-\bm
+  \nabla^2\phi(\bm r)=-4\pi\sum_{\bm R}\delta(\bm r_\|-\bm
   R)\delta(z)=-\frac{4\pi}{A}\sum_{\bm G}e^{i\bm G\cdot\bm r_\|}\delta(z),
@@
 periodically repeated delta function. We introduce a 2D Fourier representation for
-the potential \notaL{Checar consistencia entre phi y varphi en todos lados}
+the potential \notaL{\sout{Checar consistencia entre phi y varphi en todos lados}}
 \begin{equation}
@@
 the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
-ordinary differential equation \notaL{El signo estaba mal. Chécalo.}
+ordinary differential equation \notaL{\sout{El signo estaba mal. Chécalo.}} \notaC{En efecto el sino 
+estaba mal yo tenia +, y es - por la ecuacion de segundo orden que sale en este caso, tenia tambien 
+derivadas parciales y son totales}
  \begin{eqnarray}
- \frac{d^2}{dz^2}\phi_{_{\bm G}}(z)-G^2\phi_{_{\bm G}}(z)=
  \frac{d^2}{dz^2}\phi_{\bm G}(z)-G^2\phi_G(z)=
@@
 well known transfer matrix method \notaL{refs}.
-\notaL{No necesitamos presentar la teoría de matrices de
-  transferencia. No hay nada original ahí.}
+\notaL{\sout{No necesitamos presentar la teoría de matrices de
+  transferencia. No hay nada original ahí.}}
 
@@
 
-\notaL{Cambié el título, pues tienes una mezcla de experimento y
-  teoría aquí}
+\notaL{\sout{Cambié el título, pues tienes una mezcla de experimento y
+  teoría aquí}}
 In Fig. \ref{fig:DE1} we show a schematic representation of our
 experimental setup to manufacture porous silicon with GRIN.
-\notaL{Cambié las figuras}
+\notaL{\sout{Cambié las figuras}}
 As dicussed above, we fabricated an electrolytic cell with the shape of a
 rectangular prism on the bottom of which we place a Si wafer which makes
-electrical contact to a gold plate \notaL{Lo inventé; de qué material es
-  el contacto bajo la muestra} which together make the anode. The
-catode consists of a platinum wire insulated except for a small region
-at its tip, which we take as a point current drain.
+electrical contact to a metal plate \notaC{\sout{gold plate} error de escritura} 
+\notaL{\sout{Lo inventé; de qué material es el contacto bajo la muestra}}
+ which together make the anode. The catode consists of a platinum wire 
+ insulated except for a small region at its tip, which we take as a 
+ point current drain.
 We also show a schematic drawing of the expected GRIN PS structures,
@@
 size $0.62\text{cm}\times2.03\text{cm}$) with an uncovered sample area
-of $1.206\text{cm}^2$. \notaL{¿Cuáles fueron las coordenadas del
-  electrodo?} We manufactured samples using a current $I=5\text{mA}$
+of $1.206\text{cm}^2$. \notaC{Estan son las coordenadas del electrodo} The coordinates the tip of the
+electrode at $\bm
+r_0=(x_0,y_0,z_0)=(0.1\text{cm},0.3\text{cm},0.9\text{cm})$
+\notaL{\sout{¿Cuáles fueron las coordenadas del
+  electrodo?}} We manufactured samples using a current $I=5\text{mA}$
 which yielded current densities in the range
@@
 case of a single PS layer we used
-the standard formula \notaL{referencia} for three media air (0), PS
+the standard formula \cite{T8,T9} \notaL{\sout{referencia}} for three media air (0), PS
 (1) and c-Si (2),
@@
 where $ r_{01} $ y $ r_{12}$ are the Fresnel reflectance
-coefficients at the air/PS and PS/c-Si interfaces \notaL{referencias}
+coefficients at the air/PS and PS/c-Si interfaces \cite{T10,T11}\notaL{\sout{referencias}}
 and $\delta=k_{PS}^\perp d$, where $k_{PS}^\perp$ is
@@
 the porous layer of width $d$.
-\notaL{Me tienes que explicar dónde y cómo usaste lo que mencionas en
+\notaL{\sout{Me tienes que explicar dónde y cómo usaste lo que mencionas en
   la siguiente frase:
@@
 by including the Davies-Bennett factor in the coefficient of each
-Fresnel \cite{I17, I18, I19}, which represents the roughness of a
-Gaussian distribution.}
+Fresnel cite{I17, I18, I19}, which represents the roughness of a
+Gaussian distribution.}} \notaC{No tenia ninguna relevancia en este 
+punto de la discusión, y si fue una equivocación dejarla hasta el 
+final}
 
@@
 Bruggeman's effective medium theory \cite{I20} \notaL{Elegir y checar:
-  varepsilon o epsilon para funciones dieléctricas}
+  $\varepsilon o \epsilon$ para funciones dieléctricas}
 \begin{eqnarray}\label{Eq:Brugg}
@@
 was chosen as a half-wavelength low index layer of width $d_d$ such that
-$n_Ld_L=\lambda_c/2$, and the MC has the
-following sequence: $(HL)_6HH(LH )_6$. \notaL{Hay algo mal. La
+$n_Hd_H=\lambda_c/2$ \notaC{$n_Ld_L=\lambda_c/2$ error y
+ descuido de escritura.} and the MC has the
+following sequence: $(HL)_6HH(LH )_6$. \notaL{\sout{Hay algo mal. La
   película de $\lambda/2$ fue de alto o de bajo índice? En una parte
   dices una cosa y en otra otra. ¿Será $(HL)_jHLLH(LH)_6$? ¿O será
-  $(LH)_6LL(HL)_6$? ¡Muy descuidado!}
+  $(LH)_6LL(HL)_6$? ¡Muy descuidado!}}
 We chose $\lambda_c= 0.67 \mu\text{m}$. For the high index layers we
@@
 $j_{HA\perp}= 6\text{mA}/\text{cm}^2$ below the tip \notaL{checar}, and yielded
-$n_H =2.6$, corresponding to a porosity \notaL{P mayúscula
-  es porosidad, o p minúscula. Checar consistencia} $P_H =0.46$, and a
+$n_H =2.6$, corresponding to a porosity \notaL{\sout{P mayúscula
+  es porosidad, o p minúscula. Checar consistencia}} $p_H =0.46$, and a
 width $d_H=0.066 \mu\text{m}$, which required an attack time of
 $t_H=35 \text{s}$. The corresponding parameters for the low density
-layers were $I_L=38\text{mA}$, $j_{LA\perp}=50\text{mA}/\text{cm}^2$, $n_L= 1.4$,  $P_L =0.75$,
+layers were $I_L=38\text{mA}$, $j_{LA\perp}=50\text{mA}/\text{cm}^2$, $n_L= 1.4$,  $p_L =0.75$,
 $d_L=0.117 \mu \text{m}$, and $t_L=11 \text{s}$. For the rest of the
@@
 electrode at $\bm
-r_0=(x_0,y_0,z_0)=(0.2\text{cm},0.4\text{cm},0.96\text{cm})$
-\notaL{Descuidado. En la figura dice 0.98, no 0.96}.
-\notaL{¿Por qué usaste estos valores?}
-\notaL{Esto no es interesante: the programming with the
-  PERL PDL package and corresponding graph in gnuplot.}
-\notaL{¿Qué significa esto?:We optimize the
+r_0=(x_0,y_0,z_0)=(0.1\text{cm},0.3\text{cm},0.9\text{cm})$ \notaC{ya lo corregi 
+$0.1\text{cm},0.3\text{cm},0.9\text{cm})$ }.
+\notaL{\sout{Descuidado. En la figura dice 0.98, no 0.96}}.
+\notaL{\sout{¿Por qué usaste estos valores?}}
+\notaL{\sout{Esto no es interesante: the programming with the
+  PERL PDL package and corresponding graph in gnuplot.}}
+\notaL{\sout{¿Qué significa esto?:We optimize the
 appropriate values so that our current density adequately attacks
-crystalline silicon, giving the gradient effect.}
+crystalline silicon, giving the gradient effect.}} \notaC{Yo quise volver a 
+reafirmar algo, pero se pierde el sentido real de la frease:"optimizamos los
+valores apropiados de fabricación para que nuestra densidad actual, atacará
+silicio cristalino, dando el efecto gradiente al silicio poroso"}
 For these parameters we obtained $ j_\perp/I\sim
 0.5-1.2\text{cm}^{-2}$
-\notaL{Quité el resto del párrafo pues no entendí nada.}
+\notaL{\sout{Quité el resto del párrafo pues no entendí nada.}}
 
@@
 as adjustable parameters. We obtained $p_A=0.44$, $p_B=0.42$, and
-$p_C= 0.40$. \notaL{Falta decir cuáles fueron las profundidades}
+$p_C= 0.40$. The depth $ d_A= 1320nm $, $ d_B= 997nm $ and $ d_C= 605nm $ 
+respectively. \notaC{Las profundidades $ d_A= 1320nm $, $ d_B= 997nm $ 
+and $ d_C= 605nm $ }
+\notaL{\sout{Falta decir cuáles fueron las profundidades}}
 Location $A$ is
@@
  the complex index of refraction corresponding to the fitted porosities.
-\notaL{Quité otra frase que no entendí, pero que me generó una duda:
+\notaL{\sout{Quité otra frase que no entendí, pero que me generó una duda:
   la profundidad la ajustaste ópticamente o la mediste en SEM y luego
-  hiciste el ajuste a la reflectancia?}
+  hiciste el ajuste a la reflectancia?}} \notaC{Esta parte, siempre se midio la
+  profundida en SEM, por eso me costo poder ajustar el espectro de reflactacia
+  en un primer inicio, hasta que coloque la ecuacion de de fresnel
+  para una monopelicula.}
 
@@
   \end{tabular}
-  \caption{ \emph{We have different points denoted as follows, $ A
+  \caption{We have different points denoted as follows, $ A
       (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $,
@@
       0.3J^{0.24}$). And we could obtain the attack time with the
-      relation of $ V = 0.53J ^ {0.79} $ where $ t = d / V $.}}
+      relation of $ V = 0.53J ^ {0.79} $ where $ t = d / V $.}
 	\label{tabla:1}
@@
 
+ \bibitem{T8}Born, Max, and Emil Wolf. \textquotedblleft \emph{Basic properties of 
+   	the electromagnetic field.}\textquotedblright Principles of optics 44 (1980).
+  \bibitem{T9} Stenzel, Olaf. \textquotedblleft \emph{ The physics of thin film 
+  	optical spectra.}\textquotedblright Springer, 2015.
+
+  \bibitem{T10}Born, Max, and Emil Wolf.\textquotedblleft \emph{ Principles of optics: 
+  	electromagnetic theory of propagation, interference
+  	 and diffraction of light.}\textquotedblright Elsevier, 2013.
+  \bibitem{T11} Sattler, Klaus D., ed. \textquotedblleft \emph{ Silicon Nanomaterials 
+  	Sourcebook: Low-Dimensional Structures, Quantum Dots, and Nanowires }\textquotedblright,
+   Volume One. CRC Press, 2017.
+
 \bibitem{I17} Dariani RS, Ebrahimnasab S (2014). \textquotedblleft

### 2020-06-17 paper.tex
Correct up to Fig. 8

--- 2020-06-15 paper.tex
@@
 \newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
+\newcommand{\notaC}[1]{{\color{green}+C:#1+}}
+\newcommand{\notaV}[1]{{\color{red}+V:#1+}}
 \title{\textbf{Optimization of Porous Silicon Gradient Refractive
@@
 \maketitle
-\notaL{Quité los intentos de tipografiar. Que de eso se encargue la
-  revista.}
-\notaL{Cambié la codificación a utf8; ya no uses latin1, es obsoleto.}
-\notaL{Quité las líneas kilométricas. No te ocupes de su longitud y no
-  juntes mis líneas.}
-\notaL{Quité paquetes no escenciales}
-\notaL{Cuida de no poner espacios al final de las líneas.}
 
@@
 \notaL{Cambié el abstract, pero habrá que revisarlo después.}
+\notaL{Si quieres ponerme algún comentario en el manuscrito usa el
+  comando notaC, similar al comando notaL que uso yo}
 \section{Introduction}
@@
 density ${\bm j(\bm r)}$, as the porosity and refractive index depend on
-the current density, as well as the speed of attack and the width of the
+the current density, as well as the speed of attack and the thickness of the
 porous layer. Nevertheless, it is not a simple task to measure the
@@
     covered by the sample, which is assumed to be a good
-    conductor. The tip of the electrode is a thin insulated wire with
-    just the tip uncovered and located at $ \vec{r}_0 $ within the
-    liquid.\notaL{\sout{Quité el tipo de letra del pie de figura. Que la pongan en la
-      revista.}}\notaL{\sout{En la punta pusiste dos esferas. Quítalas y sólo
-    pon un puntito dorado del ancho del cable. Muestra que la base
-    está aterrizada}}\notaL{\sout{Indica el voltaje y la
-    corriente}}\notaL{\sout{¿Está bien la polaridad de la batería?}}
-    just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
-    liquid.\notaL{Quité el tipo de letra del pie de figura. Que la pongan en la
-      revista.}\notaL{En la punta pusiste dos esferas. Quítalas y sólo
-    pon un puntito dorado del ancho del cable. Muestra que la base
-    está aterrizada}\notaL{Indica el voltaje y la
-    corriente}\notaL{Mejor pon una fuente de corriente en lugar de una
-  fuente de voltaje}}
+    conductor. The tip of the electrode is a thin insulated wire
+    \notaL{El punto del electrodo hazlo más chico que el ancho
+      del cable.} with just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
+    liquid.}
   \label{f:celda}
@@
 \end{equation}
-This problem may be solved readily using image charge theory \cite{T1,T2}
-\notaL{\sout{ref}}. The potential within the electrolytic cell coincides the
-the field within an infinite vacuum containing the point charge
-This problem may be solved readily using image charge theory
-\notaL{ref}. The potential within the electrolytic cell coincides
+This problem may be solved readily using image charge theory \cite{T1,T2}.
+The potential within the electrolytic cell coincides
 within the region $0\le x\le a$, $0\le y \le b$, $0\le z\le c$
@@
 convergence properties. The potential can be obtained
-using the Ewald summation technique \cite{T3,T4,T5}\notaL{\sout{ref}}, which yields
- two rapidly convergingseries, one in real space and another one in reciprocal space.
+using the Ewald summation technique \cite{T3,T4,T5}, which yields
+two rapidly converging series, one in real space and another one in reciprocal space.
 Nevertheless, as we need the potential and the field to obtain the
@@
 simple periodic lattice of charges using a fast convergent sum over the 2D
-reciprocal vectors, and then sum over the charges that form the basis
-of the 2D {\em crystal} plane and finally sum over all the
- planes \cite{T6,T7} \notaL{\sout{ref}}.
-using the Ewald summation technique \notaL{ref}, which yields two rapidly converging
-series, one in real space and another one in reciprocal space.
-Nevertheless, as we have to evaluate the potential and the field on
-the bottom of the cell to obtain the current density which attacks the
-surface of the sample, and as there are no
-real nor image charges there, we may perform a somewhat simpler planewise
-summation, where we first obtain the potential and field produced by a
-simple periodic lattice of charges using a fast convergent sum over the 2D
-reciprocal vectors, we then sum over the charges that form the basis
-of the 2D {\em crystal} plane and we finally sum over all the planes \notaL{ref}.
+reciprocal vectors, then sum over the charges that form the basis
+of the 2D {\em crystal} plane, and finally sum over all the
+ planes \cite{T6,T7}.
 
@@
   \label{eq:phifourier}
-  \phi(\bm r)=\sum_{\bm G}\phi_{_{\bm G}}(z)e^{i\bm G\cdot\bm r_\|}
-\end{equation}
-where $\phi_{_{\bm G}}(z)$ is the Fourier coefficient of the potential at
+  \phi(\bm r)=\sum_{\bm G}\phi_{\bm G}(z)e^{i\bm G\cdot\bm r_\|}
+\end{equation}
+where $\phi_{\bm G}(z)$ is the Fourier coefficient of the potential at
 the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
@@
  \begin{eqnarray}
- \frac{d^2}{dz^2}\phi_{_{\bm G}}(z)-G^2\phi_{_{\bm G}}(z)=
  \frac{d^2}{dz^2}\phi_{\bm G}(z)-G^2\phi_G(z)=
@@
 We also show a schematic drawing of the expected GRIN PS structures,
-with a gradient in the porosity, and in the width, density and depth
+with a gradient in the porosity, and in the thickness, density and depth
 of the resulting pores.
@@
 conditions. The process was performed at
-room temperature,\notaL{Controlaste/mediste la temperatura?} with an
+room temperature,\notaL{OJO. No controlaste la temperatura} with an
 electrolytic mixture of aqueous hydrofluoric
@@
 of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
-size $0.62\text{cm}\times2.03\text{cm}$) with an uncovered sample area
-of $1.206\text{cm}^2$. \notaL{¿Cuáles fueron las coordenadas del
-  electrodo?} We manufactured samples using a current $I=5\text{mA}$
+size $6.2\text{mm}\times2.03\text{cm}$) with an uncovered sample area
+of about $1.21\text{cm}^2$. The height of the liquid was set at
+$c=1\text{cm}$. The cathode was a
+platinum wire that with a diameter of $0.41\text{mm}$ insulated by a
+teflon cylinder of external diameter $2\text{mm}$. \notaL{¿Están
+  bien estos diámetros?} with an uncovered tip located at $\bm r_0=(x_0,
+y_0,z_0)=(0.1,0.31,0.9)$.
+\notaL{Cambiar figura a una adecuada}
+We manufactured samples using a current $I=5\text{mA}$
 which yielded current densities in the range
-$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$ and other smples using a larger
+$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$ and other samples using a larger
 current $I=40\text{mA}$ corresponding to current densities in the
-range $j_\perp=20-50\text{mA}/\text{cm}^2$. The cathode was a
-platinum wire that with an approximate diameter of $0.5\text{mm}$.
+range $j_\perp=20-50\text{mA}/\text{cm}^2$.
 \subsection{Morphological studies}
@@
 the component of the wavevector perpendicular to the surface within
-the porous layer of width $d$.
+the porous layer of thickness $d$.
 \notaL{Me tienes que explicar dónde y cómo usaste lo que mencionas en
@@
 \label{sec:fabrication-grin-ps}
-After characterizing the preparation of single PS GRIN layers, we
+After characterizing the fabrication process through measurements and
+calculations corresponding to single PS GRIN layers, we
 fabricated PS GRIN microcavities (MC) as specific defects between two distributed Bragg
 mirrors  (DBR). Alternate quarter wavelength plates of high (H) and low (L)
-refractive indices $n_i$ of widths $d_i$, $i=H,L$ were prepared satisfying the Bragg condition
-$n_id_i=\frac{\lambda_c}{4}$ at a given design
-wavelength $\lambda_c$ and at a position $A$ (Fig. \ref{fig:DE1} which
-we chose as that directly below the point-like electrode. The defect
-was chosen as a half-wavelength low index layer of width $d_d$ such that
-$n_Ld_L=\lambda_c/2$, and the MC has the
-following sequence: $(HL)_6HH(LH )_6$. \notaL{Hay algo mal. La
-  película de $\lambda/2$ fue de alto o de bajo índice? En una parte
-  dices una cosa y en otra otra. ¿Será $(HL)_jHLLH(LH)_6$? ¿O será
-  $(LH)_6LL(HL)_6$? ¡Muy descuidado!}
-We chose $\lambda_c= 0.67 \mu\text{m}$. For the high index layers we
+refractive indices $n_i$ of thickness $d_i$, $i=H,L$ were prepared satisfying the Bragg condition
+$n_id_i=\lambda_c/4$ at a given design
+wavelength $\lambda_c$ and at a position $A$ (Fig. \ref{fig:DE1}) which
+we chose as that directly below the point-like electrode.\notaL{Checar
+  veracidad} The defect
+was chosen as a half-wavelength high index layer of thickness $d_d=2d_H$ such that
+$n_Hd_d=\lambda_c/2$. The MC corresponds to the
+sequence $(HL)_6HH(LH )_6$ where each letter $H$ or $L$ corresponds to
+a quarter wavelength plate of high and low index of refraction correspondingly.
+We chose $\lambda_c= 0.67 \mu\text{m}$.\notaL{Algún motivo para esta
+  elección?} For preparing the high index layers we
 chose a current $I_H=5\text{mA}$ which corresponded to a current density
 $j_{HA\perp}= 6\text{mA}/\text{cm}^2$ below the tip \notaL{checar}, and yielded
-$n_H =2.6$, corresponding to a porosity \notaL{P mayúscula
-  es porosidad, o p minúscula. Checar consistencia} $P_H =0.46$, and a
-width $d_H=0.066 \mu\text{m}$, which required an attack time of
+$n_H =2.6$, corresponding to a porosity \notaL{Explicar esta
+  correspondencia entre $p$ y $n$} \notaL{P mayúscula
+  es porosidad, o p minúscula. Checar consistencia} $p_H =0.46$, and a
+thickness $d_H=0.066 \mu\text{m}$, which required an attack time of
 $t_H=35 \text{s}$. The corresponding parameters for the low density
@@
 $d_L=0.117 \mu \text{m}$, and $t_L=11 \text{s}$. For the rest of the
-sample the current density, porosity, index of refraction and width
+sample the current density, porosity, index of refraction and thickness
 varied, yielding a GRIN MC.
@@
     length $a = 2.03\text{cm}$ and width $b=0.62\text{cm}$, for a
-    point-like electrode at $\bm r_0=(0.2\text{cm},
-    0.4\text{cm},0.96\text{cm})$ (top panel). Normalized current
-    along the line $y=?$ (bottom panel). \notaL{qué valor de $y$ usaste para la
-      gráfica de abajo?} \notaL{Puse $x_0$
-      y $y_0$ que faltaban. Checale. Se me hace raro que no esté
-      centrado en la celda a lo ancho. ¿No está debería estar en
-      $y_0=0.31\text{cm}?$} \notaL{Cambia los letreros, $J$ por
+    point-like electrode at $\bm r_0=(0.1\text{cm},
+    0.31\text{cm},0.9\text{cm})$ (top panel). Normalized current
+    along the line $y=?$ (bottom panel). \notaL{Escoger el valor de
+      $y$ y poner la figura correspondiente} \notaL{Cambia los letreros, $J$ por
       $j_\perp$. La ordenada no es a, sino $x$ y la abcisa no es b
-      sino $y$}. }
+      sino $y$}.\notaL{Volverla a hacer con los datos
+      correctos. Rotular la figura con la misma notación que en el
+      texto. Preparar la figura como dos figuras independientes.}. }
   \label{fig:DR1}
@@
 electrode at $\bm
-r_0=(x_0,y_0,z_0)=(0.2\text{cm},0.4\text{cm},0.96\text{cm})$
-\notaL{Descuidado. En la figura dice 0.98, no 0.96}.
+r_0=(x_0,y_0,z_0)=(0.1\text{cm},0.31\text{cm},0.9\text{cm})$
 \notaL{¿Por qué usaste estos valores?}
-\notaL{Esto no es interesante: the programming with the
-  PERL PDL package and corresponding graph in gnuplot.}
-\notaL{¿Qué significa esto?:We optimize the
-appropriate values so that our current density adequately attacks
-crystalline silicon, giving the gradient effect.}
 For these parameters we obtained $ j_\perp/I\sim
-0.5-1.2\text{cm}^{-2}$
-\notaL{Quité el resto del párrafo pues no entendí nada.}
+0.5-1.2\text{cm}^{-2}$.
 
@@
   \caption{(a)  Sample $G_1$ prepared as described in
-     \ref{sec:fabrication-ps-grin} using a current $I=5 \text{mA}$
-    during a time $t=600\text{s}$. We indicate three regions $A$,
+     \ref{sec:fabrication-ps-grin} using a current $I_1=5 \text{mA}$
+    during a time $t_1=600\text{s}$. We indicate three regions $A$,
     $B$, and $C$ centered at positions at positions,
@@
     Corresponding complex indices of refraction $n+ik$ obtained from
-    Eq. \eqref{Eq:Brugg} using the fitted porosities $p_A=0.44$,
-    $p_B=0.42$, and $p_C= 0.40$ at the chosen positions. \notaL{En las
+    Eq. \eqref{Eq:Brugg} using the fitted porosities $p_{1A}=0.44$,
+    $p_{1B}=0.42$, and $p_{1C}= 0.40$ at the chosen positions. \notaL{En las
       figuras escribe A, B y C en lugar de
-      Point A, Point B y Point C. Escribe $p_A$, $p_B$ y $p_C$ en lugar
+      Point A, Point B y Point C. Escribe $p_{1A}$, $p_{1B}$ y $p_{1C}$ en lugar
       de la palabra Porosity. Escribe $n$ y $k$ nada más, sin la
@@
   tres partes reales en una sola gráfica y las tres partes imaginarias
-en otra y ponerlas una al lado de la otra.}}
+en otra y ponerlas una al lado de la otra.}\notaL{Las letras A, B y C
+están colocadas en el lugar preciso, a escala?}\notaL{Quizás sea mejor
+que hagas tres figuras distintas, una para cada panel, y las alineamos
+con latex}}
   \label{fig:DR3}
@@
  structures, $G_1$, prepared as described in
- \ref{sec:fabrication-ps-grin} applying a current $I=5\text{mA}$ for
- $t=600\text{s}$. We employed the same geometry as described in
+ \ref{sec:fabrication-ps-grin} applying a current $I_1=5\text{mA}$ for
+ $t_1=600\text{s}$.\notaL{Quizás podamos quitar la repetición de I y
+   t} We employed the same geometry as that described in
  Sec. \ref{sec:current-density} \notaL{Lo inventé. ¿Es cierto?}
@@
 sample is evident. We chose three positions $x_A=0.3\text{cm}$,
-$x_B=0.8\text{cm}$ and $x_C=1.7\text{cm}$ \notaL{¿valor de y?} on
+$x_B=0.8\text{cm}$ and $x_C=1.7\text{cm}$ \notaL{¿Son correctos estos
+  valores? Antes dijiste que $A$ estaba abajo del electrodo}\notaL{¿valor de y?} on
 which we measured the reflectance spectra, also shown in the figure.
@@
 \eqref{Eq:Brugg} using the local porosity and the depth of the layer
-as adjustable parameters. We obtained $p_A=0.44$, $p_B=0.42$, and
-$p_C= 0.40$. \notaL{Falta decir cuáles fueron las profundidades}
+as adjustable parameters. \notal{¿Es cierto?} We obtained $p_{1A}=0.44$, $p_{1B}=0.42$, and
+$p_{1C}= 0.40$. \notaL{Falta decir cuáles fueron las profundidades}
 Location $A$ is
-closest to the electrode, while location $ C $ is the furthest.
+closest to the electrode, while location $C$ is the furthest.
 \notaL{Quité una frase sin sentido.}
@@
   \includegraphics[width=\textwidth]{Images/semD11}
-  \caption{Characterization of a monolayer of PS GRIN G1
-      with an initial current of $ 5 \ \ mA $, seeing the
-      morphology and depth of the cross section of several SEM
-      micrographs, at different points, $ A (0.3 \ \ cm) $ and $
-      B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $. We can see the
-      sample size for each measurement point, the depth $ d (A)
-      = 1320 \ \ nm $, $ d (B) = 997 \ \ nm $ and $ d (C) = 605
-      \ \ nm $ }
+  \caption{Side-view SEM micrographs of the PS GRIN single layer
+    taken at positions $A$, $B$, and $C$ of sample $G_1$ shown in
+    Fig. \ref{fig:DR3}.
+    \notaL{Quité la info redundante}}
   \label{fig:DR4}
 \end{figure}
-In the Fig. \ref{fig:DR4} shows the cross section views   at points $
-A (0.3 \ \ cm) $, $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $, we can
-measure the thickness for each point of the sample $ G1 (I = 5 \ \ mA)
-$, $ d (A) = 1320 \ \ nm $, $ d (B) = 997 \ \ nm $ and $ d (C) = 605 \
-\ nm $. Likewise, we could check it for a second sample $ G2 (I = 40 \
-\ mA) $, with porosities for each point, $ A (P = 0.76) $, $ B (P =
-0.73) $ and $ C (P = 0.68) $ and the depths $ d (A) = 1950 \ \ nm $, $
-d (B) = 1690 \ \ nm $ and $ d (C) = 1430 \ \ nm $, designed in the
-same way as the shows G1, only varying the current taking into account
-the current density ratio for each point. Apart from that, a
-structural gradient was formed, along the direction \emph{ a}  of the
-axis of the $ x $, where the tip of the electrode is near the point $
-A $ and away from the point $ C $ of the substrate, using the proposed
-experimental setup. In addition, it was possible to control the
-current density based on the position of the sample and the depth,
-seen in the SEM micrographs.
+
+In Fig. \ref{fig:DR4} we shows side-view SEM micrographs taken at
+positions $A$, $B$, and $C$ of sample $G_1$ shown in
+Fig. \ref{fig:DR3}. From these micrographs we can
+obtain the thicknesses of the porous layer at different
+positions. Thus, we obtained that for our sample $G_1$
+$d_{1A}= 1320\text{nm}$, $ d_{1B} = 997\text{nm}$, and $d_{1c} = 605
+\text{nm}$. Similarly, for a second sample $G_2$, attacked with a
+larger current $I_2 =40 \text{mA}$, for a time $t_2=$?\notaL{El ancho no
+  tiene sentido si no especificas el tiempo} we obtained the
+porosities \notaL{las posiciones ¿fueron las mismas?}, $p_{2A}= 0.76$, $p_{2B}=
+0.73$, and $p_{2C}= 0.68$, and the corresponding depths $d_{2A}=1950\text{nm}$,
+$d_{2B}=1690\text{nm}$, and $d_{2C}= 1430\text{nm}$. \notaL{Quité otra
+  frase vacía}\notaL{Me es importante entenderte: La profundidad la
+  obtuviste de SEM. ¿También la obtuviste de R, o primero la obtuviste
+  de SEM y luego la sustituiste en la fórmula de R? Recuerdo que nos
+  presentaste alguna vez que la profundidad obtenida de la óptica
+  correspondía a la medida por SEM. ¿Fue así? Si sí, por qué no lo
+  escribes aquí?}
+
 \begin{figure}
@@
    \includegraphics[width=\textwidth]{Images/grinJDR}
-   \caption{a) It is the relation of the current density $
-       J (mA / cm ^ 2) $ normalized with the electric current $ I
-       (mA) $, we have $ J / I \ sim 1.2 \ \ a \ \ 0.5 ( cm^{-2})
-       $, when we apply it to two samples $ G1 (I = 5 \ \ mA) $
-       and $ G2 (I = 40 \ \ mA) $ depending on the axis $ a $ $
-       (0.1 ... 2.0 \ \ cm) $, measured at points $ A (0.3 \ \
-       cm) $ , $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm) $. b) The
-       attack speed $ v = d (J_i) / t (nm / sec) $, the depths
-       (thickness $ d (J_i) $, $ i = $ $ A (0.3 \ \ cm) $, $ B (
-       0.8 \ \ cm) $ y $ C (1.7 \ \ cm)) $ taken in SEM
-       micrographs $ d (J_i) (nm) $ and attack times $ G1 (t =
-       600 \ \ s) $ y $ G2 (t = 200 \ \ s) $, depending on the
-       axis $ a $ $ (0.1 ... 2.0 \ \ cm) $ }
+  \caption{(a)Current density calulated on different positions
+    $A$, $B$, and $C$ along the samples $G_1$ and $G_2$ (as shown in
+    Fig. \ref{fig:DR3}), for attack currents $I_1=5\text{mA}$ and
+    $I_2=40\text{mA}$ (left panel), obtained by properly scaling the
+    results of Fig. \ref{fig:DR1}. \notaL{Pon paréntesis de ambos
+      lados (a) y (b). El eje horizontal es $x$, no $a$. El eje
+      vertical es $j_\perp$.}
+    (b)Attack speed $v=d/t$ obtained at different positions $A$, $B$,
+    and $C$ over samples $G_1$ and $G_2$, where $d$ is the thickness
+    as measured from SEM micrographs, as in Fig. \ref{fig:DR4},
+    and $t$ is the attack time.}
   \label{fig:JDR}

### 2020-06-17 paper.tex

@@
 the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
-ordinary differential equation \notaL{El signo estaba mal. Chécalo.}
+ordinary differential equation \notaL{\sout{El signo estaba mal. Chécalo.}} \notaC{En efecto el sino 
+estaba mal yo tenia +, y es - por la ecuacion de segundo orden que sale en este caso, tenia tambien 
+derivadas parciales y son totales}
  \begin{eqnarray}
@@
 of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
-size $6.2\text{mm}\times2.03\text{cm}$) with an uncovered sample area
-of about $1.21\text{cm}^2$. The height of the liquid was set at
-$c=1\text{cm}$. The cathode was a
-platinum wire that with a diameter of $0.41\text{mm}$ insulated by a
-teflon cylinder of external diameter $2\text{mm}$. \notaL{¿Están
-  bien estos diámetros?} with an uncovered tip located at $\bm r_0=(x_0,
-y_0,z_0)=(0.1,0.31,0.9)$.
-\notaL{Cambiar figura a una adecuada}
-We manufactured samples using a current $I=5\text{mA}$
+size $0.62\text{cm}\times2.03\text{cm}$) with an uncovered sample area
+of $1.206\text{cm}^2$. \notaC{Estan son las coordenadas del electrodo} The coordinates the tip of the
+electrode at $\bm
+r_0=(x_0,y_0,z_0)=(0.1\text{cm},0.3\text{cm},0.9\text{cm})$
+\notaL{\sout{¿Cuáles fueron las coordenadas del
+  electrodo?}} We manufactured samples using a current $I=5\text{mA}$
 which yielded current densities in the range
@@
 was chosen as a half-wavelength high index layer of thickness $d_d=2d_H$ such that
-$n_Hd_d=\lambda_c/2$. The MC corresponds to the
+$n_Hd_h=\lambda_c/2$. The MC corresponds to the
 sequence $(HL)_6HH(LH )_6$ where each letter $H$ or $L$ corresponds to
@@
 $t_H=35 \text{s}$. The corresponding parameters for the low density
-layers were $I_L=38\text{mA}$, $j_{LA\perp}=50\text{mA}/\text{cm}^2$, $n_L= 1.4$,  $P_L =0.75$,
+layers were $I_L=38\text{mA}$, $j_{LA\perp}=50\text{mA}/\text{cm}^2$, $n_L= 1.4$,  $p_L =0.75$,
 $d_L=0.117 \mu \text{m}$, and $t_L=11 \text{s}$. For the rest of the

### 2020-06-17 paper.tex
Revise up to sec. 4.3

--- 2020-06-17 paper.tex
@@
  Sec. \ref{sec:current-density} \notaL{Lo inventé. ¿Es cierto?}
-The position of electrode corresponds to the upper left side of the
+The position of the electrode corresponds to the left side of the
 photograph. The variation of the optical properties across the
@@
 \eqref{Eq:Brugg} using the local porosity and the depth of the layer
-as adjustable parameters. \notal{¿Es cierto?} We obtained $p_{1A}=0.44$, $p_{1B}=0.42$, and
+as adjustable parameters. \notaL{¿Es cierto?} We obtained $p_{1A}=0.44$, $p_{1B}=0.42$, and
 $p_{1C}= 0.40$. \notaL{Falta decir cuáles fueron las profundidades}
@@
 
-In Fig. \ref{fig:DR4} we shows side-view SEM micrographs taken at
-positions $A$, $B$, and $C$ of sample $G_1$ shown in
+In Fig. \ref{fig:DR4} we show side-view SEM micrographs of sample
+$G_1$ taken at the
+positions $A$, $B$, and $C$ shown in
 Fig. \ref{fig:DR3}. From these micrographs we can
@@
   tiene sentido si no especificas el tiempo} we obtained the
-porosities \notaL{las posiciones ¿fueron las mismas?}, $p_{2A}= 0.76$, $p_{2B}=
+porosities \notaL{las posiciones ¿fueron las mismas que para $G_1$?}, $p_{2A}= 0.76$, $p_{2B}=
 0.73$, and $p_{2C}= 0.68$, and the corresponding depths $d_{2A}=1950\text{nm}$,
@@
    \includegraphics[width=\textwidth]{Images/grinJDR}
-  \caption{(a)Current density calulated on different positions
-    $A$, $B$, and $C$ along the samples $G_1$ and $G_2$ (as shown in
-    Fig. \ref{fig:DR3}), for attack currents $I_1=5\text{mA}$ and
-    $I_2=40\text{mA}$ (left panel), obtained by properly scaling the
-    results of Fig. \ref{fig:DR1}. \notaL{Pon paréntesis de ambos
+  \caption{(a)Current density calculated by scaling the results of
+    Fig. \ref{fig:DR1} by the currents $I_1=5\text{mA}$ and
+    $I_2=40\text{mA}$ used to prepare samples $G_1$ and $G_2$.
+. \notaL{Pon paréntesis de ambos
       lados (a) y (b). El eje horizontal es $x$, no $a$. El eje
       vertical es $j_\perp$.}
-    (b)Attack speed $v=d/t$ obtained at different positions $A$, $B$,
+    (b)Etching rate speed $v=d/t$ obtained at different positions $A$, $B$,
     and $C$ over samples $G_1$ and $G_2$, where $d$ is the thickness
     as measured from SEM micrographs, as in Fig. \ref{fig:DR4},
-    and $t$ is the attack time.}
+    and $t$ is the etching time.\notaL{Falta una gráfica similar de
+      porosidad vs. x para las dos muestras}\notaL{Las escalas del
+      lado derecho no tienen que ver con las del lado
+      izquierdo. Deberías poner la misma escala de ambos lados, con el
+    mismo quiebre.}\notaL{Sugiero en la gráfica de la corriente
+    graficar las dos líneas completas, además de los 6 puntos
+    correpondientes a A, B y C de las dos muestras}}
   \label{fig:JDR}
 \end{figure}
-In Fig. \ref{fig:JDR} a) It is the relation of the current density $ J
-(mA / cm ^ 2) $ normalized with the electric current $ I (mA) $, we
-have $ J / I \ sim 1.2 \ \ a \ \ 0.5 (1 / cm ^ 2) $, when we apply it
-to two samples $ G1 (I = 5 \ \ mA) $ and $ G2 (I = 40 \ \ mA) $
-depending on the axis $ a $ $ (0.1 ... 2.0 \ \ cm) $, measured at
-points $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm)
-$.
-The Fig. \ref{fig:JDR} b) we can calculate the attack speed $ v = d
-(J_i) / t (nm / s) $, where the depths (thickness $ d (J_i) $, $ i = $
-$ A (0.3 \ \ cm) $, $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm)) $ taken
-in SEM micrographs $ d (J_i) (nm) $ and attack times $ G1 (t = 600 \ \
-s) $ and $ G2 (t = 200 \ \ s) $, depending on the axis $ a $ $ (0.1
-... 2.0 \ \ cm) $.
+In Fig. \ref{fig:JDR}(a) we show the actual current current density
+$j_\perp$ obtained from Fig. \ref{fig:DR1} by scaling by the actual
+current $I_1=5\text{mA}$ and $I_2=40\text{mA}$ employed to prepare
+samples $G_1$ and $G_2$, respectively. We indicate the values
+corresponding to positions $A$, $B$, and $C$ on the samples.
+\notaL{la
+  corriente que muestras no es normalizada}
+In Fig. \ref{fig:JDR} (b) we show the etching rate $v = d/t$ on
+selected positions of both samples obtained by dividing the thickness
+$d$ measured as in Fig. \ref{fig:DR4} by the etching time.
+
 \begin{figure}
@@
   \includegraphics[width=\textwidth]{Images/grinJD31}
-  \caption{The relationship of samples $ G1 (I = 5 mA) $ and $
-      G2 (I = 40 mA) $ were obtained to find: a) Attack speed with
-      current density for each point and b) Porosity as a function of
-      density current. With this we have the calibration curves for
-      the manufacture of any GRIN porous silicon structure   }
+  \caption{(a) Etching rate $v$ and (b) porosity $p$ as a function of the
+    density current $j_\perp$, obtained from Fig. \ref{fig:JDR}. We
+    show the data points and the results of power
+    law fits, yielding $v=0.53j_\perp^{0.79}$ and
+    $p=0.3j_\perp^0.24$, with corresponding correlation coefficients
+      $r_v^2=0.993$ and $r_p^2=0.989$ (here $v$ is in nm/s, $p$ is
+      dimensionless and $j_\perp$ is in mA/cm$^2$). \notaL{cambia J por $j_\perp$, V por $v$ y P
+      por $p$. Quita el letrero fitting data, la ecuación y el valor
+      de $R^2$}\notaL{Los ajustes ¿son correctos con estas unidades?}}
   \label{fig:Indr1}
 \end{figure}
-Fig. \ref{fig:Indr1} a) explicitly explain the relationships that
-emerge when designing samples $ G1 (I = 5 mA) $ and $ G2 (I = 40 mA)
-$. For the first case $ G1 $ the depths ($ 1320 \ \ nm $ to $ 605 \ \
-nm $) and the current densities ($ 6 \ \ mA / cm ^ 2 $ to $ 2.5 \ \ mA
-/ cm ^ 2 $), finding the attack speed $ 2.2 \ \ nm / s $ up to $ 1.1 \
-\ nm / s $ relation with depth and the time ($ 600 \ \ s $) of
-exposure of the sample, with the current density . We also find the
-depth ($ 1950 \ \ nm $ at $ 1430 \ \ nm $) and the current density ($
-50 \ \ mA / cm ^ 2 $ at $ 20 \ \ mA / cm ^ 2 $) as a function of the
-measurement points of the sample $ G2 (I = 40 mA) $. We were able to
-obtain the attack speed from $ 9.8 \ \ nm / s $ up to $ 7.1 \ \ m / s
-$ by relating to depth and time ($ 200 \ \ s $), with current
-density. Once the thickness of the monolayer and the attack time
-applied to them are known, calculate the attack speed according to the
-formula $ v = d / t $, for each of the current densities at the points
-$ A ( 0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm)
-$. Then we fit a function to the attack speed points with the
-different current densities allowed by the anodizing condition. For a
-desired thickness $ d (J_i) $, calculate the attack time $ t $ (so, $
-t = v / d (J_i) $) and we can design any structure knowing the current
-density and the attack time. Fig. \ref{fig:Indr1} b) we find a
-relation of the porosity for each position with its determined current
-density. Therefore, if it is desired to manufacture a PS monolayer of
-a certain porosity with a certain end, it is enough to resort to the
-graphs of Fig. \ref{fig:Indr1} to determine the corresponding current
-density, attack speed and consequently the time, obtaining for that
-monolayer. The importance of the calibration curves is that it allows
-us to have a relationship of the porosities that can be reached (and
-by having control over the possible refractive indices) as a function
-of the current density and to be controlled to control the thickness
-of the layers that are manufactured, by controlling the attack time
-for each of the chosen currents.
+By relating among themselves the panels of Fig. \ref{fig:JDR} we
+may obtain the etching rate $v$ and the porosity $p$ as
+functions of the current density $j_\perp$. The results are shown in
+Fig. \ref{fig:Indr1}.\notaL{\ldots Apenas aquí dijiste cuál fue el
+  tiempo de ataque de la muestra dos: relating to depth and time ($
+  200 \ \ s $ ). ¿Es correcto este tiempo? Ponlo en su lugar}
+We fitted the data points with simple power laws and found
+$v=0.53j_\perp^{0.79}$ and $p=0.3j_\perp^{0.24}$, where $v$ is
+expressed in nm/s, $p$ is dimensionless and $j_\perp$ is expressed as
+mA/cm$^2$. The corresponding correlation coefficients are $r_v^2=0.993$
+and $r_p^2=0.989$. \notaL{Digresión teórica. El producto $pv$ es
+  proporcional a la cantidad de materia removida por segundo. En mi
+  opinión, esto debería ser proporcional a la corriente $pv\propto
+  j_\perp$. ¿Es correcto? A tí te sale algo parecido pero no
+  exacto. ¿Se podrá hacer un mejor ajuste tomando esto en cuenta?
+  ¿Alguien lo ha discutido en la literatura?}\notaL{En todo caso, todo
+  esto se tiene que rehacer usando la expresión teórica correcta y las
+  posiciones correctas}
+
+Fig. \ref{fig:Indr1} illustrates an advantage of using a cell
+geometry for which the current density may be obtained
+analytically. Namely, we can relate the etching rate and the
+porosity to the current density by taking measurements at
+different positions along just a few PS GRIN samples. Thus, it is much easier
+and faster to obtain calibration curves which are useful in the
+fabrication of PS photonic structures, GRIN or otherwise.
 

### 2020-06-17 paper.tex
Revise up to figs. 11 and table 1.

@@
 We fitted the data points with simple power laws and found
-$v=0.53j_\perp^{0.79}$ and $p=0.3j_\perp^{0.24}$, where $v$ is
+\begin{equation}
+  \label{eq:etch}
+  v=0.53j_\perp^{0.79}
+\end{equation}
+and
+\begin{equation}
+  \label{eq:poros}
+  p=0.3j_\perp^{0.24},
+\end{equation}
+where $v$ is
 expressed in nm/s, $p$ is dimensionless and $j_\perp$ is expressed as
@@
 
-\subsection{GRIN Porous Silicon Microcavities}
+\subsection{PS GRIN Microcavities}
 \label{sec:grin-porous-silicon}
@@
   \includegraphics[width=\textwidth]{Images/MicrGrin}
-	\caption{Diagram of a microcavity of porous silicon
-            GRIN. Alternate layers are obtained of high (H) refractive
-            index $n_{Hi}$ and low (L) refractive index
-            $n_{Li}$, where $N_H$ is the number of layers for
-            $n_{Hi}$ and $N_L$ is the number of layers for
-            $n_{Li}$. Then,  $d_{Hi}$ is the monolayer thickness
-            of  $n_{Hi}$ at that measurement point and $d_{Li}$
-            is the monolayer thickness of $n_{Hi}$ at that
-            measurement point. Therefore,  $d_i$ is the total
-            thickness calculated for each of the measurements,
-            defining a i = $ A, B, C$. Having the following
-            relationship $d_i =(N_{Hi}d_{Hi})+(N_{Li}d_{Li}) +
-            (2d_{Hi})$. }
+  \caption{\notaL{Está bonita la figura, pero tiene errores. La
+      superficie del electrolito y la superficie de la muestra
+      deben ser ambas horizontales. Cambia la fuente por fuente
+      de corriente. La punta del electrodo no debe ser una
+      bola. Quita todo lo que está abajo del sustrato. Mejor pon
+      solamente una H en alguna región amarilla y una L en
+      alguna región azul. El electrolito tiene gotas o
+      burbujas. Tal vez sea mejor ponerle un color uniforme. Quita los
+      anchos totales, pues no creo que nos sean útiles. Haz que los cables
+      horizontales sean horizontales.}
+    PS GRIN microcavity made of layers of high (H) and low (L)
+    refractive index $n_H$ and $n_L$ and widths $d_H$ and $d_L$
+    arranged in the sequence $(HL)_NHH(HL)_N$. Both the index of
+    refraction and the widths depend on position along the
+    sample and are chosen to obey a quarter wavelength
+    condition at a given position $A$ and wavelength $\lambda_c$.
+  }
   \label{fig:MCGRIN0}
 \end{figure}
-The Fig. \ref{fig:MCGRIN0} the scheme of  a initially proposed lateral
-gradient for monolayers should be shown in section 4.2, where we
-designed an electolytic cell suitable for our experiments and giving
-us the expected results of the simulation in section 4.1. Now our
-purpose is to manufacture more complex photonic structures such as the
-Porous silicon microcavities GRIN, taking into account that we start
-from having a tip electrode almost on the surface and by making a
-variation of currents we can achieve the effect of alternating the
-layers. Alternate layers are obtained of high (H) refractive index
-$n_{Hi}$ and low (L) refractive index $n_{Li}$, where $N_{H}$
-is the number of layers for  $n_{Hi}$ and $N_L$ is the number
-of layers for $n_{Li}$. Then,  $d_{Hi}$ is the monolayer
-thickness of  $n_{Hi}$ at that measurement point and $d_{Li}$ is
-the monolayer thickness of $n_{Hi}$ at that measurement
-point. Therefore,  $d_i$ is the total thickness calculated for
-each of the measurements, defining a i = $ A, B, C$. Having the
-following relationship $d_i =
-(N_{Hi}d_{Hi})+(N_{Li}d_{Li}) + (2d_{Hi})$.
-Initial data for conventional design we use  $\lambda_c= 0.67 \ \
-\mu m$, $n_H =2.6$, $P_H =0.46$, $d_H=0.066 \ \ \mu m
-$, $t_H=35 s  $ y para  $n_L= 1.4$,  $P_L =0.75$,
-$d_L=0.117 \ \ \mu m  $, $t_L=11 s  $. All these data are
-for the point $ 0 $ which is located at one end of the sample just
-below the tip counter-electrode.
+
+As a simple application of our preparation and calibration methods, we
+prepare a PS GRIN microcavity (MC), as illustrated in
+Fig. \ref{fig:MCGRIN0}.  Alternate layers of relatively high (H) and low and low
+(L) refractive indices $n_H$ and $n_L$, of corresponding thicknesses
+$d_H$ and $d_L$, are prepared by alternatingly etching a Si sample in our
+electrolytic cell with a current $I_H$ during a time $t_H$ and with a
+current $I_L$ during a time $t_L$. We chose the currents $I_H=5\text{mA}$
+and $I_L=40\text{mA}$ \notaL{¿son correctos estos valores?}, the same
+that were used above to prepare samples $G_1$ and $G_2$.
+We chose the etching times to obtain a MC at the given
+position $A$ tuned to a given wavelength
+$\lambda_c=0.67\mu\text{m}$. Thus, we chose the thicknesses so they
+correspond to quarter wavelength plates, $n_Hd_H=n_Ld_L=\lambda_c/4$,
+at this position and wavelength, yielding $n_H =2.6$,\notaL{Por qué no
+  coincide con el dato de la tabla 1?} $p_H =0.46$,
+$d_H=0.066\mu\text{m}$, $t_H=35\text{s}$, $n_L= 1.4$, $p_L =0.75$,
+$d_L=0.117\mu\text{m}$, $t_L=11\text{s}$.
 \begin{figure}
@@
   \includegraphics[width=\textwidth]{Images/MCGRIN2}
-  \caption{a) Three locations at different points are
-      considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B
-      (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the PSMCGRIN
-      sample $ GMC $. b) We have the reflectance measurements to
-      know the optical properties with the proposed
-      simulation. We were able to show that in a Porous Silicon
-      GRIN structure, for a microcavity the data is very
-      consistent with the simulation and the experiment, we
-      found the refractive indices and the porosities as a
-      function of the current density at each measurement point,
-      see Table \ref{tabla:1}. }
+  \caption{(a)Top view photograph of a PS GRIN MC showing the position
+    of the three measuring points $A$, $B$ and $C$. The cavity was
+    tuned to the wavelength $\lambda_c=0.67\mu\text{m}$ at position
+    $A$ (see text). We chose $x_A=0.3\text{cm}$, $x_B=0.8\text{cm}$,
+    and $x_C=1.2\text{cm}$. (b-d) Reflectance spectra measured and
+    calculated at positions $A-C$. For the calculation, the porosity
+    and etching rates were obtained from Fig. \ref{fig:Indr1},
+    the dielectric functions and indices of refracton from
+    Eqs. \eqref{Eq:Brugg} and the reflectance from standard transfer
+    matrix theory. \notaL{Quizás haya que usar D E F en lugar de A B
+      C, pues A B C se usó para otras posiciones sobre la muestra
+      $G_1$ y $G_2$. ¿Son correctas las posiciones aquí?}}
   \label{fig:MCGRIN3}
@@
   \centering
-  \begin{tabular}{|c|c|c|c|c|c|c|}
+  \begin{tabular}{ccccccc}
     \hline
-    \textbf{Points} & $\lambda_c (\mu m)$ & \textbf{n} & \textbf{k} & \textbf{Porosity} & \textbf{J}$(mA/cm^2)$ & \textbf{t(s)}\\
+    Pos(kind)&Current(mA/cm$^2$)&Porosity&Index&Wavelength($\mu\text{m}$)\\
     \hline
-    A(H) & 0.65 & 2.661 & 0.0264 & 0.45 & 5.5 & 35 \\
     \hline
-    B(H) & 0.58 & 2.762 & 0.0135 & 0.41 & 4.0 & 35 \\
-    \hline
-    C(H) & 0.54 & 2.808 & 0.0178 & 0.39 & 3.0 & 35 \\
-    \hline
-    A(L) & 0.65 & 1.442 & 0.0015 & 0.74 & 44 & 11 \\
-    \hline
-    B(L) & 0.58 & 2.295 & 0.0091 & 0.68 & 32 & 11 \\
-    \hline
-    C(L) & 0.54 & 2.302 & 0.001 & 0.64 & 24 & 11 \\
-    \hline
+    A(H) & 5.5 & 0.45& 2.66& 0.65   \\
+    A(L) & 44  & 0.74& 1.44& 0.65   \\
+    B(H) & 4.0 & 0.41& 2.76& 0.58   \\
+    B(L) & 32  & 0.68& 2.29& 0.58   \\
+    C(H) & 3.0 & 0.39& 2.81&0.54    \\
+    C(L) & 24  & 0.64& 2.30&0.54    \\
   \end{tabular}
-  \caption{ \emph{We have different points denoted as follows, $ A
-      (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $,
-      from the sample of a Porous Silicon Microcavity GRIN
-      (PSMCGRIN) $ GMC $. Alternate layers of high refractive index
-      (H) and low refractive index (L) are obtained at each of the
-      measurement points (A, B and C). The refractive indexes of the
-      PSMCGRIN were considered from the experimental and theoretical
-      values that were obtained for the porosity ($ P =
-      0.3J^{0.24}$). And we could obtain the attack time with the
-      relation of $ V = 0.53J ^ {0.79} $ where $ t = d / V $.}}
+  \caption{Some properties of the PS GRIN MC corresponding to the
+    positions $A$, $B$ and $C$ and the corresponding high ($H$) and
+    low ($L$) index layers. The current densities were obtained by
+    scaling the results in Fig. \ref{fig:DR1} with $I_H$ and
+    $I_L$, the depths were obtained from the etching
+    times and the current density using \eqref{eq:etch}, the porosity
+    was obtained from Eq. \eqref{eq:poros}, the indices of refraction
+    were obtained from Eq. \eqref{Eq:Brugg} using the porosity, and
+    the resonant wavelengths of the cavity were read from
+    Fig. \ref{fig:MCGRIN3}.
+    \notaL{Inventé lo de arriba. Qué es cierto y qué
+      mentira?}\notaL{Por qué resuenas en 0.65 si habías diseñado
+      0.67 en A?} \notaL{¿De dónde sacaste
+        $\lambda_c$ para los otros puntos? ¿Cómo le hiciste para que
+        $\lambda_c$ diera lo mismo en $H$ y en $L$? $n$ y $k$ dependen de la
+        frecuencia. ¿Qué frecuencia usaste para darles valores en esta
+        tabla?}\notaL{quité digitos a n. quité k pues es chiquita,
+        ¿no? quité los tiempos pues son los mismos. Quité las
+        posiciones pues están descritas antes. Añade una columna
+        con las profundidades $d_H$ y $d_L$. }}
 	\label{tabla:1}
 \end{table}
-In Fig. \ref{fig:MCGRIN3} a) Three locations at different points are
-considered, denoted as follows, $ A (0.3 \ \ cm) $ , $ B (0.8 \ \ cm)
-$ and $ C (1.2 \ \ cm) $, from the PSMCGRIN sample $ GMC $. Likewise,
+In Fig. \ref{fig:MCGRIN3} we show a photograph of a PS GRIN MC
+sample, which displays a color that shifts towards the blue when we
+move towards its right, that is, away from where the electrode was
+positioned. In the figure we indicate three points with $x$ coordinate
+$x_A=0.3\text{cm)$ , $x_B=0.8\text{cm}$, and $x_C=1.2\text{cm}$.
+  \notaL{***Aquí voy***}
+  Likewise,
 Fig. \ref{fig:DR3} b), we have the reflectance measurements to know

### 2020-06-17 paper.tex
Revise up to conclusions

@@
     refractive index $n_H$ and $n_L$ and widths $d_H$ and $d_L$
-    arranged in the sequence $(HL)_NHH(HL)_N$. Both the index of
+    arranged in the sequence $(HL)_NHH(HL)_N$. \notaL{CUánto vale $N$?
+    Antes habías dicho que 6, pero en la figura 12 parece otra cosa} Both the index of
     refraction and the widths depend on position along the
@@
         posiciones pues están descritas antes. Añade una columna
-        con las profundidades $d_H$ y $d_L$. }}
+        con las profundidades $d_H$ y $d_L$. }\notaL{De los rótulos de
+      la figura quita las palabras Point. Cambia simulation por Theory.}
 	\label{tabla:1}
@@
 move towards its right, that is, away from where the electrode was
-positioned. In the figure we indicate three points with $x$ coordinate
-$x_A=0.3\text{cm)$ , $x_B=0.8\text{cm}$, and $x_C=1.2\text{cm}$.
-  \notaL{***Aquí voy***}
-  Likewise,
-Fig. \ref{fig:DR3} b), we have the reflectance measurements to know
-the optical properties with the proposed simulation. We can see how
-from an experimental setup we have some important results as a result
-of a whole calibration curve suitable for making GRIN porous
-silicon. The refractive index of the Porous Silicon Microcavities GRIN
-were considered the experimental and theoretical values obtained for
-the porosity and the thicknesses shown in Table 1. The porous silicon
-microcavities (MCSP) with refractive index with gradient (GRIN), were
-manufactured with different current densities ranging from $ 6 \ \ mA
-/ cm ^ 2 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a current of $ 5 \ \ mA $,
-for a $t_H=35 s $, with a high refractive index $n_H \sim$ $
-2,661$ to $ 2,808$ and porosities of $P_H \sim$ $ 0.45 $ to $
-0.39 $. Also for $ 44 \ \ mA /cm^2 $ to $ 24 \ \ mA / cm^2 $, current
-of $ 38 \ \ mA $, using $t_H=11 s$  for low refractive index
-$n_L\sim$ $ 1,448 $ to $ 2,267 $ and with porosities of
-$P_H \sim$ $0.75 $ to $ 0.64 $. The porosity was calculated with
-the calibration curve exposed in the ($ P = 0.3J^{0.24} $). And the
-attack time could be obtained with the relation of $ V = 0.53J^{0.79}
-$ where $ t = d / V $ and the refractive index using the Bruggeman
-formula. For theoretical values, we use complex refractive indices as
-free parameters to fit the experimental refractive spectra (Section
-4.2).
+positioned. In the figure we indicate three points with $x$ coordinates
+$x_A=0.3\text{cm}$,  $x_B=0.8\text{cm}$, and $x_C=1.2\text{cm}$
+on we measured the reflectance spectra, also shown in the figure.
+\notaL{No dices cómo hiciste las curvas teóricas} The spectra have the
+expected shape: a high reflectance plateau corresponding to the
+photonic band gap of the Bragg mirror, with a deep narrow minimum due
+to the Fabry-Perot resonance of the cavity. We also present the
+calculated spectra. To that end, we calculated the current density
+using the theory developed in Sec. \ref{sec:calc-curr-dens}, i.e., by
+scaling Fig. \ref{fig:DR1} with the total current $I_H$ and $I_L$ used
+to fabricate each layer. From the current densities we obtained the
+corresponding etching rates and the porosities using
+Eqs.~\eqref{eq:etch} and  \eqref{eq:poros}, and from the, the
+thickness of each layer, the index of refraction
+(Eq. \eqref{Eq:Brugg}) and the reflectance,using standard transfer
+matrix theory \notaL{ref}. Notice the good agreement between theory
+and experiment. \notaL{No me lo creo. Me sospecho que más bien,
+  ajustaste el experimento no sé con qué parámetro. Explícame cómo
+  hiciste el cálculo.} The parameters used are shown in Table \ref{tabla:1}.
+\notaL{No entiendo qué quisiste decir aquí: For theoretical values, we
+  use complex refractive indices as free parameters to fit the
+  experimental refractive spectra (Section 4.2).} The band-gap, the
+resonance and the oscillations due to multiple reflections in the
+region of transparency are similar, though the experimental spectra is
+more rounded and the central resonance is wider. This might be due to
+the roughness of the interfaces, which would lead to some scattering
+whose effects are similar to those of an additional absorption
+\ref{cita el artículo en prensa de Guille y mío}.\notaL{Checar que no
+  diga mentiras arriba. El ajuste es demasiado bueno, pero no sé cómo
+  se hizo. Hay que explicar qué significan y de dónde salieron las
+  $\lambda_c$ de la tabla. }
+
  \begin{figure}
@@
    \includegraphics[width=\textwidth]{Images/MCGRINSEM}
-   \caption{SEM image of the cross section profile of the
-       microcavities with GRIN. The measured thicknesses of the
-       complete multi-film structures showed good agreement with the
-       simulations taken from $ V = 0.53J ^ {0.79} $ where $d_j=Vt_j$
-       ($j=H,L$), which are the thicknesses of each of the monolayer
-       of the porous silicon microcavity GRIN at the measurement
-       points and the total thickness we find it as $d_i =
-       (N_{Hi}d_{Hi})+(N_{Li}d_{Li}) + (2d_{Hi})$
-       defining $ i = $ A, B, C. Which resulted in (measured /
-       simulation) $ 2.25 / 2.31 \ \ \mu m $ (for structure at Point
-       A), $ 2.17 / 2.08 \ \ \mu m $ (for structure at point B) and $
-       1.87 / 1.65 \ \ \mu m $ (for structure at point C)}
+   \caption{Cross section SEM images corresponding to the positions
+     $A$, $B$, and $C$ of the PS GRIN MC shown in
+     Fig. \ref{fig:MCGRIN3}. The total thickness of the system at
+     different positions, $d_A=2.25\mu\text{m}$,
+     $d_B=2.17\mu\text{m}$, and $d_C=1.87\mu\text{m}$ are
+     indicated. \notaL{Porque se ve una capa más ancha a la izquierda?
+       ¿Por qué el número de capas arriba no es igual que abajo? ¿Por
+       qué el número de capas no es el mismo en las distintas fotos?
+       ¿Por qué no es 6 como dice el texto en la
+       Sec. \ref{sec:fabrication-grin-ps}?}
+     }
    \label{fig:MCGRIN4}
  \end{figure}
-
-For the Fig. \ref{fig:MCGRIN4} shows the SEM cross-sectional images of
-the PS samples used in this work. Relatively small interface
-roughness and a clear contrast between the high and low porosity of
-the microcavity measured at different points (A, B and C), showing the
-change in thickness in each of these. The measured thicknesses of the
-complete multi-film structures showed good agreement with the
-simulations taken from $ V = 0.53J^{0.79} $ where $d_j=Vt_j$
-($j=H,L$), which are the thicknesses of each of the monolayer of the
-porous silicon microcavity GRIN at the measurement points and the
-total thickness we find it as $d_i =
-(N_{Hi}d_{Hi})+(N_{Li}d_{Li}) + (2d_{Hi})$ defining $ i
-= $ A, B, C. Which resulted in (measured / simulation) $ 2.25 / 2.31 \
-\ \mu m $ (for structure at Point A), $ 2.17 / 2.08 \ \ \mu m $ (for
-structure at point B) and $ 1.87 / 1.65 \ \ \mu m $ (for structure at
-point C).
-Being able to say that for each measurement point corresponds
-different calculated current densities, which correspond to different
-thicknesses at the end of manufacturing, clearly seeing the lateral
-gradient product of our experiment.
-
-\section{conclusion}
+In Fig. \ref{fig:MCGRIN4} we show SEM cross-sectional images of
+the PS GRIN MC sample. We can appreciate a relatively small interface
+roughness and a clear contrast between the high and low porosity
+layers. The structure of the microcavity is also visible, with a
+central layer of twice the thickness of the corresponding layers
+within the Bragg mirrors. The gradient of the thickness is also
+evident, as $d_A>d_B>d_C$, with $d_A=2.25\mu\text{m}$,
+$d_B=2.17\mu\text{m}$, and $d_C=1.87\mu\text{m}$ the total thickness
+of the structure measured at the positions $A$, $B$, and $C$.
+The measured thickness are in good agreement with those computed from
+the current densities and the etching times $N(d_H+d_L)+2 d_H$ using
+Eq. \eqref{eq:etch}, where $N$ is the number of pairs of layers in the
+Bragg mirrors, which yield $d_A=2.31\mu\text{m}$,
+$d_B=2.08\mu\text{m}$, and $d_C=1.65\mu\text{m}$. \notaL{Por qué una
+  te dio más grande y las otras más chicas? Aquí tienes que decir
+  cuánto vale $N$ y no has dicho cuánto valieron $d_L$ y $d_H$}
+
+\section{Conclusions}
 \label{sec:conclusion}
-The necessary expressions for the potential components were derived,
-finding a relationship of the tip of the counter electrode that acts
-similarly as a point charge and the current density for a geometry in
-a rectangular electrolytic box and we solve the electrostatic
-equations with suitable boundary conditions. Resulting in an
-electrostatic model for  Photonics crystals with a refractive index
-with gradient (EMPCGRIN).
-It is the first time that the formalism mentioned here has been
-applied to find the current density to design porous silicon. The
-shape of the electrode, the area of the cell produces a visible
-decrease in the size and density of the pores. Additionally,
-optimizing the structural properties for a single structure we could
-have a gradient with different depths, reflactances at differents
-measurement points. In this way, we were able to simulate the direct
-relationship of the attack speed with the current density at the
-points  the samples of interest. At the same time, we developed a
-characterization between porosity, refractive indices of porous
-silicon, with the different current densities. And in the end we were
-able to design and characterize Porous Silicon microcavities with
-refractive indices with gradients, which for each measurement point
-correspond to different calculated current densities, which correspond
-to different thicknesses, clearly seeing the lateral gradient product
-of our experiment.
-\section{Acknowledgments}
+By choosing a simple geometry for our electrochemical cell, namely, a
+rectangular prism, and employing a point-like electrode, we were able
+to derive a simplel expression for the calculation of the electric current
+density along the surface of a Si sample. The expression was obtained
+by using image charge theory and a planewise summation of Coulomb
+potentials in reciprocal space, and it is made up of
+a rapidly converging sum of analytical terms. This allowed us to
+characterize the porosity of a PS layer and the etching
+rate for different values of the etching current density by making
+optical experiments on just a
+few samples. We illustrated the procedure with two samples each of which we
+measured at three different positions. These calibration curves are
+very useful as the etching rate for the formation of porous silicon
+and the resulting porosity is very sensitive to the growth conditions
+and to the properties of the substrate, such as its doping. Thus,
+there are no universal calibration curves. Having obtained these calibration curves
+and being able to compute the current density at different positions
+allows the prediction of the properties of GRIN structures. We
+illustrated this by desigining a PS GRIN microcavity tuned at one
+position to a given wavelength. We found a good agreement between its
+measured reflectance spectra at different points with the spectra
+calculated from the values of the expected local current
+density using the calibration curves. We also found good agreement
+between the measured and the expected geometry of the system. These
+results show that the use of a simple electrolytic cell and our
+computational procedure does allow the accurate prediction of the
+optical properties of GRIN structures, and thus we believe it will
+prove helpful for the design fabrication and characterization of novel
+devices based on PS GRIN systems.
+
+\section*{Acknowledgments}
 \label{sec:acknowledgments}
+WLM acknowledges the support of DGAPA-UNAM under grant IN111119.
 % \backmatter
@@
 %\bibliography{bibliografía.bib} %Aquí ponen el nombre del archivo .bib
+\notaL{Manda toda la bibliografía a un archivo .bib}
+\notaL{Cuando esté listo, quiero que me expliques por qué incluiste
+  cada uno de los artículos citados}
 \bibliographystyle{unsrt}

### 2020-06-18 paper.tex
Correct a few mistakes

@@
 \usepackage{bm}
-\usepackage{ulem} %opcional para la correcciones
+\usepackage[normalem]{ulem} %opcional para la correcciones
 \newcommand{\abs}[1]{\lvert#1\rvert}
@@
 density ${\bm j(\bm r)}$, as the porosity and refractive index depend on
-the current density, as well as the speed of attack and the thickness of the
+the current density, as well as the etching rate and the thickness of the
 porous layer. Nevertheless, it is not a simple task to measure the
@@
 walls of the cell are insulating while the bottom is completely
-covered with the sample, which is a which is an
+covered with the sample, which is an
 electrically grounded good conductor. Within the electrolyte we position an electrode
@@
 with
-$\sigma$ the conductivity, $\bm E=-\nabla\varphi$ the electric field,
-and $\varphi$ the electric potential. For a
-stationary situation\notaL{Latex usa nabla como el nombre de
-  $\nabla$}
+$\sigma$ the conductivity, $\bm E=-\nabla\phi$ the electric field,
+and $\phi$ the electric potential. For a
+stationary situation
 $\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
@@
 \begin{equation}
-E_x(0, y ,z)= E_x(a, y ,z)=E_{{_y}}(x, 0 ,z)=E_{{_y}}(x, b
-,z)=E_{{_z}}(x, y ,c)=0.
+E_x(0, y ,z)= E_x(a, y ,z)=E_y(x, 0 ,z)=E_y(x, b
+,z)=E_z(x, y ,c)=0.
 \end{equation}
@@
 periodically repeated delta function. We introduce a 2D Fourier representation for
-the potential \notaL{Checar consistencia entre phi y varphi en todos lados}
+the potential
 \begin{equation}
@@
 the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
-ordinary differential equation \notaL{El signo estaba mal. Chécalo.}
+ordinary differential equation
  \begin{eqnarray}
@@
 $-q_0$ corresponds to the planes with height $z_0+(4n+2)c$ and
-$-z_0+(4n+4)c$.
+$-z_0+4(n+1)c$.
 
@@
 as the contributions of opposite non-null reciprocal vectors cancel
-out. As expected, all the current that leaves sample finds
-its way to the cathode.
+out. As expected, all the charges that leave the sample find
+their way  to the cathode across the electrolyte.
 
@@
 
-  \caption{\notaL{reordené figura y rehice} Experimental set-up for
+  \caption{Experimental set-up for
     the fabrication of porous silicon with GRIN, consisting of a
@@
     low porosity respectively illustrating the gradients in pore
-    size, density and depth. \notaL{Es $\nabla p$ razonable para el
-      gradiente de la porosidad}}
+    size, density and depth.}
   \label{fig:DE1}
@@
 experimental setup to manufacture porous silicon with GRIN.
-\notaL{Cambié las figuras}
 As dicussed above, we fabricated an electrolytic cell with the shape of a
@@
   el contacto bajo la muestra} which together make the anode. The
-catode consists of a platinum wire insulated except for a small region
+cathode consists of a platinum wire insulated except for a small region
 at its tip, which we take as a point current drain.
@@
 y_0,z_0)=(0.1,0.31,0.9)$.
-\notaL{Cambiar figura a una adecuada}
 We manufactured samples using a current $I=5\text{mA}$
@@
 \label{sec:morph-stud}
-\notaL{Cambié el orden}
 The morphologies of the etched porous layers were
@@
 films at different positions along the sample from its top and side
-views (Fig. \ref{fig:DE1}).
+views (Fig. \ref{fig:DE1}). \notaL{¿Sí se midió la porosidad con SEM?}
 
@@
 the porous layer of thickness $d$.
-\notaL{Me tienes que explicar dónde y cómo usaste lo que mencionas en
-  la siguiente frase:
-The advantage of this method is
-the possibility of taking into account the interface roughness effect
-by including the Davies-Bennett factor in the coefficient of each
-Fresnel \cite{I17, I18, I19}, which represents the roughness of a
-Gaussian distribution.}
 
@@
 porosity $p$ through
-Bruggeman's effective medium theory \cite{I20} \notaL{Elegir y checar:
-  varepsilon o epsilon para funciones dieléctricas}
+Bruggeman's effective medium theory \cite{I20}
 \begin{eqnarray}\label{Eq:Brugg}
- p\frac{1-\varepsilon_{PS}} {1+\varepsilon_{PS}} + (1-p)
-  \frac{\varepsilon_{\text{Si}} - \varepsilon_{PS}}
-  {\varepsilon_{\text{Si}}+\varepsilon_{PS}}=0
+ p\frac{1-\epsilon_{PS}} {1+\epsilon_{PS}} + (1-p)
+  \frac{\epsilon_{\text{Si}} - \epsilon_{PS}}
+  {\epsilon_{\text{Si}}+\epsilon_{PS}}=0
 \end{eqnarray}
-\notaL{Te faltaba la igualdad}
 where the porosity $p$ is the volume fraction of air within the PS
-layer, $\varepsilon_{Si}$ is the dielectric function of c-Si, and
-$\varepsilon_{PS}=n_{PS}^2$ is the dielectric function of the PS.
-\notaL{Quité frases irrelevantes.}
+layer, $\epsilon_{Si}$ is the dielectric function of c-Si, and
+$\epsilon_{PS}=n_{PS}^2$ is the dielectric function of the PS.
+
 \subsection{Fabrication  of GRIN PS Microcavities}
@@
 mirrors  (DBR). Alternate quarter wavelength plates of high (H) and low (L)
-refractive indices $n_i$ of thickness $d_i$, $i=H,L$ were prepared satisfying the Bragg condition
-$n_id_i=\lambda_c/4$ at a given design
+refractive indices $n_H$ and $n_L$ and of thicknesses $d_H$ and $d_L$,
+respectively, were prepared satisfying the Bragg condition
+$n_Hd_H=n_Ld_L=\lambda_c/4$ at a given design
 wavelength $\lambda_c$ and at a position $A$ (Fig. \ref{fig:DE1}) which
@@
 $n_Hd_d=\lambda_c/2$. The MC corresponds to the
-sequence $(HL)_6HH(LH )_6$ where each letter $H$ or $L$ corresponds to
-a quarter wavelength plate of high and low index of refraction correspondingly.
+sequence $(HL)_6HH(LH )_6$ \notaL{Esto no corresponde a la
+  realidad. Cambiar.} where each letter $H$ or $L$ corresponds to
+a quarter-wave plate of high and low index of refraction correspondingly.
 We chose $\lambda_c= 0.67 \mu\text{m}$.\notaL{Algún motivo para esta
   elección?} For preparing the high index layers we
-chose a current $I_H=5\text{mA}$ which corresponded to a current density
-$j_{HA\perp}= 6\text{mA}/\text{cm}^2$ below the tip \notaL{checar}, and yielded
-$n_H =2.6$, corresponding to a porosity \notaL{Explicar esta
-  correspondencia entre $p$ y $n$} \notaL{P mayúscula
-  es porosidad, o p minúscula. Checar consistencia} $p_H =0.46$, and a
-thickness $d_H=0.066 \mu\text{m}$, which required an attack time of
-$t_H=35 \text{s}$. The corresponding parameters for the low density
-layers were $I_L=38\text{mA}$, $j_{LA\perp}=50\text{mA}/\text{cm}^2$, $n_L= 1.4$,  $P_L =0.75$,
+chose a current $I_H=5\text{mA}$ applied during  time
+$t_H=35 \text{s}$. The current density was
+$j_{HA\perp}= 6\text{mA}/\text{cm}^2$ below the tip \notaL{checar},
+and yielded (see Sec. \ref{sec:ps-grin-single} below)
+$n_H =2.6$, corresponding to a porosity $p_H =0.46$, and a
+thickness $d_H=0.066 \mu\text{m}$. The corresponding parameters for the low density
+layers were $I_L=38\text{mA}$, $j_{LA\perp}=50\text{mA}/\text{cm}^2$, $n_L= 1.4$,  $p_L =0.75$,
 $d_L=0.117 \mu \text{m}$, and $t_L=11 \text{s}$. For the rest of the
 sample the current density, porosity, index of refraction and thickness
-varied, yielding a GRIN MC.
+varied, yielding a PS GRIN MC. \notaL{Los datos de arriba ¿son
+  consistentes con los de la sección \ref{sec:grin-porous-silicon}?}
 
@@
 \end{figure}
-\notaL{Checar consistencia notación. $x_0$, $y_0$ y $z_0$ en
-  minúsculas. Igual $j_\perp$.}
 In Fig. \ref{fig:DR1} we show the current density $j_\perp(x,y,0)$ calculated through
@@
 r_0=(x_0,y_0,z_0)=(0.1\text{cm},0.31\text{cm},0.9\text{cm})$
-\notaL{¿Por qué usaste estos valores?}
+\notaL{¿Por qué usaste estos valores? Asegurarte de usar valores
+  relevantes a lo que sigue y rehacer las gráficas.}
 For these parameters we obtained $ j_\perp/I\sim
@@
 photograph. The variation of the optical properties across the
-sample is evident. We chose three positions $x_A=0.3\text{cm}$,
+sample is evident. \notaL{Tenemos algo sensato que decir sobre el
+  gradiente en la dirección vertical cerca de los bordes?}
+ We chose three positions $x_A=0.3\text{cm}$,
 $x_B=0.8\text{cm}$ and $x_C=1.7\text{cm}$ \notaL{¿Son correctos estos
   valores? Antes dijiste que $A$ estaba abajo del electrodo}\notaL{¿valor de y?} on
-which we measured the reflectance spectra, also shown in the figure.
+which we measured the reflectance spectra, also shown in the figure. Location $A$ is
+closest to the electrode, while location $C$ is the furthest.
 We fitted the measurements using Eqs. \eqref{Eq:ECMR} and
@@
 $p_{1C}= 0.40$. \notaL{Falta decir cuáles fueron las profundidades}
-Location $A$ is
-closest to the electrode, while location $C$ is the furthest.
-\notaL{Quité una frase sin sentido.}
 We also show in Fig. \ref{fig:DR3} the wavelength dependence of
@@
 \end{figure}
-In Fig. \ref{fig:JDR}(a) we show the actual current current density
+In Fig. \ref{fig:JDR}(a) we show the actual current density
 $j_\perp$ obtained from Fig. \ref{fig:DR1} by scaling by the actual
 current $I_1=5\text{mA}$ and $I_2=40\text{mA}$ employed to prepare
-samples $G_1$ and $G_2$, respectively. We indicate the values
+samples $G_1$ and $G_2$, respectively (Eq. \eqref{Eq:J}). We indicate the values
 corresponding to positions $A$, $B$, and $C$ on the samples.
-\notaL{la
-  corriente que muestras no es normalizada}
 In Fig. \ref{fig:JDR} (b) we show the etching rate $v = d/t$ on
@@
         con las profundidades $d_H$ y $d_L$. }\notaL{De los rótulos de
-      la figura quita las palabras Point. Cambia simulation por Theory.}
+      la figura quita las palabras Point. Cambia simulation por Theory.}}
 	\label{tabla:1}
@@
 $x_A=0.3\text{cm}$,  $x_B=0.8\text{cm}$, and $x_C=1.2\text{cm}$
-on we measured the reflectance spectra, also shown in the figure.
+on which we measured the reflectance spectra, also shown in the figure.
 \notaL{No dices cómo hiciste las curvas teóricas} The spectra have the
 expected shape: a high reflectance plateau corresponding to the
-photonic band gap of the Bragg mirror, with a deep narrow minimum due
+photonic band gap of the Bragg mirrors, with a deep narrow minimum due
 to the Fabry-Perot resonance of the cavity. We also present the
@@
 corresponding etching rates and the porosities using
-Eqs.~\eqref{eq:etch} and  \eqref{eq:poros}, and from the, the
+Eqs.~\eqref{eq:etch} and  \eqref{eq:poros}, and from them, the
 thickness of each layer, the index of refraction
@@
 whose effects are similar to those of an additional absorption
-\ref{cita el artículo en prensa de Guille y mío}.\notaL{Checar que no
+\notaL{cita el artículo en prensa de Guille y mío}.\notaL{Checar que no
   diga mentiras arriba. El ajuste es demasiado bueno, pero no sé cómo
@@
 rectangular prism, and employing a point-like electrode, we were able
-to derive a simplel expression for the calculation of the electric current
+to derive an expression for the calculation of the electric current
 density along the surface of a Si sample. The expression was obtained
 by using image charge theory and a planewise summation of Coulomb
-potentials in reciprocal space, and it is made up of
-a rapidly converging sum of analytical terms. This allowed us to
-characterize the porosity of a PS layer and the etching
+potentials in 2D reciprocal space, and it is made up of
+a rapidly converging sum of analytical terms. This allows the characterization
+of the porosity of a PS layer and the etching
 rate for different values of the etching current density by making
-optical experiments on just a
+optical measurements on several positions of just a
 few samples. We illustrated the procedure with two samples each of which we
@@
 optical properties of GRIN structures, and thus we believe it will
-prove helpful for the design fabrication and characterization of novel
+prove helpful for the design, fabrication, and characterization of novel
 devices based on PS GRIN systems.
@@
 \bibliographystyle{unsrt}
-\begin{thebibliography}{X}
+\begin{thebibliography}{XX}
   % forma de biblio es MLA

### 2020-06-19 paper.tex
Subi las primera correciones 18 junio

@@
 size $0.62\text{cm}\times2.03\text{cm}$) with an uncovered sample area
-of $1.206\text{cm}^2$. \notaC{Estan son las coordenadas del electrodo} The coordinates the tip of the
-electrode at $\bm
+of $1.206\text{cm}^2$. \notaC{Estan son las coordenadas del electrodo} 
+The coordinates the tip of the electrode at $\bm
 r_0=(x_0,y_0,z_0)=(0.1\text{cm},0.3\text{cm},0.9\text{cm})$
@@
 which yielded current densities in the range
-$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$ and other samples using a larger
+$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$, which required an attack time of
+$t_1=600 \text{s}$ and other samples using a larger
 current $I=40\text{mA}$ corresponding to current densities in the
-range $j_\perp=20-50\text{mA}/\text{cm}^2$.
+range $j_\perp=20-50\text{mA}/\text{cm}^2$ and $t_2=200 \text{s}$ . \notaC{
+Coloque los tiempo de ataque para $t_1$ y $t_2$}
 \subsection{Morphological studies}
@@
 \end{eqnarray}
-where $ r_{01} $ y $ r_{12}$ are the Fresnel reflectance
-coefficients at the air/PS and PS/c-Si interfaces \cite{T10,T11}\notaL{\sout{referencias}}
+%where $ r_{01} $ y $ r_{12}$ are the Fresnel reflectance
+coefficients at the air/PS and PS/c-Si interfaces \cite{T10,T11}
 and $\delta=k_{PS}^\perp d$, where $k_{PS}^\perp$ is
@@
 Fresnel cite{I17, I18, I19}, which represents the roughness of a
-Gaussian distribution.}} \notaC{No tenia ninguna relevancia en este 
-punto de la discusión, y si fue una equivocación dejarla hasta el 
-final}
+Gaussian distribution.} \notaC{No tenia ninguna relevancia en este 
+punto de la discusión, y si fue una equivocación dejarla hasta el final}
 
@@
 whose effects are similar to those of an additional absorption
-\ref{cita el artículo en prensa de Guille y mío}.\notaL{Checar que no
+ref{cita el artículo en prensa de Guille y mío}.\notaL{Checar que no
   diga mentiras arriba. El ajuste es demasiado bueno, pero no sé cómo

### 2020-06-19 paper.tex
Cambio de la figura 1 y coloque el tiempo t2

--- 2020-06-18 paper.tex
@@
 %\usepackage[usenames]{color}
-\usepackage{bm}
+%\usepackage{bm}
 \usepackage[normalem]{ulem} %opcional para la correcciones
@@
   \label{eq:laplace}
-\nabla^{2} \phi=0.
-\end{equation}
-Consider now an arbitrary closed surface
-$\mathcal S$
-within the electrolyte that surrounds completely the tip of the
-electrode. Integrating $ \bm j$ over this surface we obtain
-\begin{equation}
-  \label{eq:I}
-\int_{\mathcal S'} d\bm a \cdot \bm j = -I,
-\end{equation}
-where the prime on $\mathcal S'$ means we remove from the surface a
-very small hole through which the wire that feeds the current to the
-electrode gets
-through. Assuming the wire is narrower than any other relevant
-distance in the system, we may interpret Eq. \eqref{eq:I} as an
-integral over a closed surface of the current \eqref{eq:j} within the
-electrolyte, ignoring the actual current within the wire. Thus
 \begin{equation}
@@
 
-\notaL{Cambié el título, pues tienes una mezcla de experimento y
-  teoría aquí}
+\notaL{\sout{Cambié el título, pues tienes una mezcla de experimento y
+  teoría aquí}}
 In Fig. \ref{fig:DE1} we show a schematic representation of our
@@
 \end{eqnarray}
-where $ r_{01} $ y $ r_{12}$ are the Fresnel reflectance
-coefficients at the air/PS and PS/c-Si interfaces \notaL{referencias}
+%where $ r_{01} $ y $ r_{12}$ are the Fresnel reflectance
+coefficients at the air/PS and PS/c-Si interfaces \cite{T10,T11}
 and $\delta=k_{PS}^\perp d$, where $k_{PS}^\perp$ is

### 2020-06-19 Programas/GrinJI.pl
New version of programa

@@ -58,45 +58,55 @@ my $b1=1/$a1; #So area=1, this is our unit of area, and from here, distance
 #Real space
 my $x=zeroes(2*$N+1, 2*$N+1)->xvals*2*$a1/(2*$N+1);
 my $y=zeroes(2*$N+1, 2*$N+1)->yvals*2*$b1/(2*$N+1);
-#mask in reciprocal space
-#my $mask=zeroes(2*$N+1, 2*$N+1);
-#$mask=(($mask->xvals>=($N-$M)) & ($mask->xvals <= ($N+$M))
-#       & ($mask->yvals>=($N-$M)) & ($mask->yvals <= ($N+$M)))
-#    ->rotate(-$N)->mv(1,0)->rotate(-$N)->mv(0,1);
 #Reciprocal lattice shifted for Fourier transforms.
 my $G=((zeroes(2*$N+1, 2*$N+1)->ndcoords-$N)*PI/pdl($a1, $b1))
     ->mv(1,0)->rotate(-$N)->mv(0,1)->mv(2,0)->rotate(-$N)->mv(0,2);
 my $Gn=($G*$G)->sumover->sqrt; #norm;
 my $sinh2Gc=sinh(mymin(2*$Gn*$c, LM));
 $sinh2Gc->((0),(0)).=1; #to avoid division by 0 down
-my $jG=cosh(mymin($Gn*$z,LM))*
-    (exp(-mymin($Gn*$z0,LM))
-     -exp(-mymin(3*$Gn*$c,LM))*cosh(mymin($Gn*$c,LM))*sinh(mymin($Gn*$z0,LM))
-     /$sinh2Gc)
-    *cos($G->((0))*$x0)*cos($G->((1))*$y0); #*$mask;
-$jG->((0),(0)).=1; #Special value for G=0;
+#my $jG=cosh(mymin($Gn*$z,LM))*
+#    (exp(-mymin($Gn*$z0,LM))
+#     -exp(-mymin(3*$Gn*$c,LM))*cosh(mymin($Gn*$c,LM))*sinh(mymin($Gn*$z0,LM))
+#     /$sinh2Gc)
+#    *cos($G->((0))*$x0)*cos($G->((1))*$y0); #*$mask;
+#$jG->((0),(0)).=1; #Special value for G=0;
 #my $jR=fft2($jG->r2C->real)->complex->re;
-my $j1=fft2($jG->r2C->real)->complex->re;
-my $jR=$j1/$A;
[…]

### 2020-06-19 paper.tex

@@
 %\usepackage[usenames]{color}
-%\usepackage{bm}
+\usepackage{bm}
 \usepackage[normalem]{ulem} %opcional para la correcciones
@@
   \label{eq:laplace}
+\nabla^{2} \phi=0.
+\end{equation}
+Consider now an arbitrary closed surface
+$\mathcal S$
+within the electrolyte that surrounds completely the tip of the
+electrode. Integrating $ \bm j$ over this surface we obtain
+\begin{equation}
+  \label{eq:I}
+\int_{\mathcal S'} d\bm a \cdot \bm j = -I,
+\end{equation}
+where the prime on $\mathcal S'$ means we remove from the surface a
+very small hole through which the wire that feeds the current to the
+electrode gets
+through. Assuming the wire is narrower than any other relevant
+distance in the system, we may interpret Eq. \eqref{eq:I} as an
+integral over a closed surface of the current \eqref{eq:j} within the
+electrolyte, ignoring the actual current within the wire. Thus
 \begin{equation}
@@
 y_0,z_0)=(0.1,0.31,0.9)$.
-We manufactured samples using a current $I=5\text{mA}$
+We manufactured a sample applying a current $I=5\text{mA}$,
 which yielded current densities in the range
-$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$, which required an attack time of
-$t_1=600 \text{s}$ and other samples using a larger
-current $I=40\text{mA}$ corresponding to current densities in the
-range $j_\perp=20-50\text{mA}/\text{cm}^2$ and $t_2=200 \text{s}$ . \notaC{
+$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$,\notaL{verificar} during an attack time
+$t_1=600 \text{s}$, and another sample using a larger
+current $I=40\text{mA}$, corresponding to current densities in the
+range $j_\perp=20-50\text{mA}/\text{cm}^2$, for a time $t_2=200 \text{s}$ . \notaC{
 Coloque los tiempo de ataque para $t_1$ y $t_2$}

### 2020-06-23 paper.tex
cambios
Coloque los cambios de las figuras con la correcion de j

@@
 \usepackage[noblocks]{authblk}
-%\usepackage{float}
+%\usepackage{authblk}
+%\usepackage[•]{•}ckage{float}
 %\usepackage{cite}% para contraer referencias
@@
     Index Structures.} }
-% A comparison with computational schemes with experimental results
 \author[1]{C. A. Ospina de la Cruz}
@@
     show the data points and the results of power
-    law fits, yielding $v=0.53j_\perp^{0.79}$ and
-    $p=0.3j_\perp^0.24$, with corresponding correlation coefficients
-      $r_v^2=0.993$ and $r_p^2=0.989$ (here $v$ is in nm/s, $p$ is
+    law fits, yielding $v=0.68j_\perp^{0.69}$ and
+    $p=0.33j_\perp^0.21$, \notaC{cambie las expresiones $v=0.53j_\perp^{0.79}$ 
+    and $p=0.3j_\perp^0.24$}
+    with corresponding correlation coefficients
+      $r_v^2=0.951$ and $r_p^2=0.989$ \notaC{ tambien cambie $r_v^2=0.993$ 
+      and $r_p^2=0.0.847$ }(here $v$ is in nm/s, $p$ is
       dimensionless and $j_\perp$ is in mA/cm$^2$). \notaL{cambia J por $j_\perp$, V por $v$ y P
@@
   \label{eq:etch}
-  v=0.53j_\perp^{0.79}
+  v=0.68j_\perp^{0.69} \notaC{cambie v=0.53j_\perp^{0.79}}
 \end{equation}
@@
   \label{eq:poros}
-  p=0.3j_\perp^{0.24},
+  p=0.33j_\perp^{0.21}, \notaC{cambie p=0.3j_\perp^{0.24}}
 \end{equation}
@@
 expressed in nm/s, $p$ is dimensionless and $j_\perp$ is expressed as
-mA/cm$^2$. The corresponding correlation coefficients are $r_v^2=0.993$
-and $r_p^2=0.989$. \notaL{Digresión teórica. El producto $pv$ es
+mA/cm$^2$. The corresponding correlation coefficients are $r_v^2=0.951$
+and $r_p^2=0.847$. \notaC{cambie $r_v^2=0.993$
+and $r_p^2=0.989$.}
+\notaL{Digresión teórica. El producto $pv$ es
   proporcional a la cantidad de materia removida por segundo. En mi

### 2020-06-23 paper.tex
Add comments to some results

--- 2020-06-19 paper.tex
@@
 We chose three positions $x_A=0.3\text{cm}$,
-$x_B=0.8\text{cm}$ and $x_C=1.7\text{cm}$ \notaL{¿Son correctos estos
+$x_B=0.8\text{cm}$ and $x_C=1.7\text{cm}$ and
+$y_A=y_B=y_C=0.31\text{cm}$  \notaL{¿Son correctos estos
   valores? Antes dijiste que $A$ estaba abajo del electrodo}\notaL{¿valor de y?} on
@@
 closest to the electrode, while location $C$ is the furthest.
-We fitted the measurements using Eqs. \eqref{Eq:ECMR} and
-\eqref{Eq:Brugg} using the local porosity and the depth of the layer
-as adjustable parameters. \notaL{¿Es cierto?} We obtained $p_{1A}=0.44$, $p_{1B}=0.42$, and
-$p_{1C}= 0.40$. \notaL{Falta decir cuáles fueron las profundidades}
-We also show in Fig. \ref{fig:DR3} the wavelength dependence of
- the complex index of refraction corresponding to the fitted porosities.
-\notaL{\sout{Quité otra frase que no entendí, pero que me generó una duda:
-  la profundidad la ajustaste ópticamente o la mediste en SEM y luego
-  hiciste el ajuste a la reflectancia?}} \notaC{Esta parte, siempre se midio la
-  profundida en SEM, por eso me costo poder ajustar el espectro de reflactacia
-  en un primer inicio, hasta que coloque la ecuacion de de fresnel
-  para una monopelicula.}
-
+
+The thicknesses of the layer were measured
+using SEM. In Fig. \ref{fig:DR4} we show side-view SEM micrographs of sample
+$G_1$ taken at the
+positions $A$, $B$, and $C$ shown in
+Fig. \ref{fig:DR3}. From these micrographs we can
+obtain the thicknesses of the porous layer at different
+positions. Thus, we obtained that for our sample $G_1$
+$d_{1A}= 1320\text{nm}$, $ d_{1B} = 997\text{nm}$, and $d_{1c} = 605
+\text{nm}$.
 \begin{figure}
@@
 \end{figure}
-
-In Fig. \ref{fig:DR4} we show side-view SEM micrographs of sample
-$G_1$ taken at the
-positions $A$, $B$, and $C$ shown in
-Fig. \ref{fig:DR3}. From these micrographs we can
-obtain the thicknesses of the porous layer at different
-positions. Thus, we obtained that for our sample $G_1$
-$d_{1A}= 1320\text{nm}$, $ d_{1B} = 997\text{nm}$, and $d_{1c} = 605
-\text{nm}$. Similarly, for a second sample $G_2$, attacked with a
+We fitted then reflectance measurements using Eqs. \eqref{Eq:ECMR} and
+\eqref{Eq:Brugg} using the local porosities $p_{1A}$, $p_{1B}$ and $p_{1C}$ as
+adjustable parameters and using Eqs. \eqref{Eq:ECMR} and
+\eqref{Eq:Brugg}. We obtained $p_{1A}=0.44$, $p_{1B}=0.42$, and
+$p_{1C}= 0.40$. The fitted reflectance has a good agreement with the
+measured one, though its interference oscillations are larger towards
+the blue region probably due to the lack of surface scattering in our
+calculation. We also show in Fig. \ref{fig:DR3} the wavelength dependence of
+the complex index of refraction corresponding to the fitted porosities.
+Similarly, for a second sample $G_2$, etched with a
 larger current $I_2 =40 \text{mA}$, for a time $t_2=$?\notaL{El ancho no
   tiene sentido si no especificas el tiempo} we obtained the
-porosities \notaL{las posiciones ¿fueron las mismas que para $G_1$?}, $p_{2A}= 0.76$, $p_{2B}=
-0.73$, and $p_{2C}= 0.68$, and the corresponding depths $d_{2A}=1950\text{nm}$,
-$d_{2B}=1690\text{nm}$, and $d_{2C}= 1430\text{nm}$. \notaL{Quité otra
-  frase vacía}\notaL{Me es importante entenderte: La profundidad la
-  obtuviste de SEM. ¿También la obtuviste de R, o primero la obtuviste
-  de SEM y luego la sustituiste en la fórmula de R? Recuerdo que nos
-  presentaste alguna vez que la profundidad obtenida de la óptica
-  correspondía a la medida por SEM. ¿Fue así? Si sí, por qué no lo
-  escribes aquí?}
+depths $d_{2A}=1950\text{nm}$, $d_{2B}=1690\text{nm}$, and $d_{2C}=
+1430\text{nm}$, and the corresponding porosities \notaL{las posiciones ¿fueron las mismas que para $G_1$?}, $p_{2A}= 0.76$, $p_{2B}=
+0.73$, and $p_{2C}= 0.68$.
 
@@
 \end{figure}
-In Fig. \ref{fig:JDR}(a) we show the actual current density
+
+In Fig. \ref{fig:JDR}(a) we show the current density
 $j_\perp$ obtained from Fig. \ref{fig:DR1} by scaling by the actual
@@
 $d$ measured as in Fig. \ref{fig:DR4} by the etching time.
-
 \begin{figure}
@@
     \hline
-    Pos(kind)&Current(mA/cm$^2$)&Porosity&Index&Wavelength($\mu\text{m}$)\\
+    Pos.(kind)&Curr. dens.(mA/cm$^2$)&Porosity&Index&Wavelength($\mu\text{m}$)\\
     \hline
@@
 on which we measured the reflectance spectra, also shown in the figure.
-\notaL{No dices cómo hiciste las curvas teóricas} The spectra have the
+\notaL{Estas $x_A$ y $x_B$ son iguales a las anteriores, pero $x_C$
+  no. ¿Es correcto? Me dice que sí, pues no podría irse al
+  ultravioleta} \notaL{No dices cómo hiciste las curvas teóricas. Ya
+  me explicó. {\bf la teoría es trampa} Dado el mínimo de reflectancia
+medido, calculó una microcavidad {\em diseñada} para ese mínimo, en
+lugar de usar los anchos predichos} The
+spectra have the
 expected shape: a high reflectance plateau corresponding to the
@@
 (Eq. \eqref{Eq:Brugg}) and the reflectance,using standard transfer
-matrix theory \notaL{ref}. Notice the good agreement between theory
+matrix theory \notaL{ref}. \notaL{Esto sería innecesario para los
+  puntos A y B, aunque tal vez sí se necesita para C, oyes $x_C$
+  parece ser distinto.}
+Notice the good agreement between theory
 and experiment. \notaL{No me lo creo. Me sospecho que más bien,

### 2020-09-15 paper.tex
Adapt paper to new results

@@
 %\usepackage[usenames]{color}
+\usepackage{showkeys}
 \usepackage{bm}
+\usepackage{hyperref}
 \usepackage[normalem]{ulem} %opcional para la correcciones
@@
 \usepackage{xcolor}
+\newif{\ifexclude}
 \newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
@@
 \newcommand{\notaV}[1]{{\color{red}+V:#1+}}
+
 \title{\textbf{Optimization of Porous Silicon Gradient Refractive
@@
 ALD offers the  opportunity to manufacture  a high index of refraction
-of contrast, visibly transparent GRIN optical elements from PS
+of contrast, visibly transparent GRIN \notaL{Define acrónimos antes de
+  usarlos}. optical elements from PS
 absorbent structures \cite{I16}. A Despite previous research on the
@@
 experimental results followed. Finally,  the conclusions given in
-Section. 5
-
-\section{Theory} \label{sec:theory}
-\subsection{Calculation of the current density}
+Section. 5 \notaL{Checar que esto corresponda a lo que sigue del
+  artículo}
+
+\section{Theory: current density}
+\label{sec:theory}
 \label{sec:calc-curr-dens}
@@
 electrically grounded good conductor. Within the electrolyte we position an electrode
-which we assume is a thin conductor, insulated from the electrolyte
+which we assume is a thin conducting wire, insulated from the electrolyte
 but for a small area near its tip, which we thus approximate as a
@@
     conductor. The tip of the electrode is a thin insulated wire
-    \notaL{El punto del electrodo hazlo más chico que el ancho
-      del cable.} with just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
-    liquid.}
+    with just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
+    liquid. The current flows through the electrolyte from the sample
+    to the tip.}
   \label{f:celda}
@@
 $\sigma$ the conductivity, $\bm E=-\nabla\phi$ the electric field,
-and $\phi$ the electric potential. For a
+and $\phi$ the electric potential. In a
 stationary situation
@@
 electrode gets
-through. Assuming the wire is narrower than any other relevant
+through, and the sign is consistent with the current direction in
+Fig. \ref{f:celda}. Assuming the wire is narrower than any other relevant
 distance in the system, we may interpret Eq. \eqref{eq:I} as an
@@
 There are further images on the four walls of the cell, of the same charge $q_0$
-and situated at $(-x_0,Y_0,z_0)$, $(x_0,-y_0, z_0)$, $(2a-x_0, y_0,
+and situated at $(-x_0,y_0,z_0)$, $(x_0,-y_0, z_0)$, $(2a-x_0, y_0,
 z_0)$ and $(x_0, 2b-y_0,z_0)$ to guarantee that no current goes across
@@
 of the 2D {\em crystal} plane, and finally sum over all the
- planes \cite{T6,T7}.
+ planes \cite{T6,T7}.\notaL{¿Estas referencias son relevantes? ¿En verdad
+   se define en ellas la suma de Ewald por planos? Dime dónde p.f., en qué
+   página. Y checa que todas las referencias tengan que ver con lo que decimos}
 
@@
 while the case $G\ne 0$ is the potential produced by a sinusoidal
-charge density on a plane given by the
-symmetric solution that decays exponentially as we get away from
+charge density on a plane, given by the
+symmetric solution that decays exponentially as we get away, upwards
+or downwards, from
 the source plane. Substituting into Eq. \eqref{eq:phifourier} yields
@@
 $n=\ldots-2,-1,0,1,2\ldots$ an arbitrary integer, while the charge
-$-q_0$ corresponds to the planes with height $z_0+(4n+2)c$ and
+$-q_0$ corresponds to the planes with heights $z_0+(4n+2)c$ and
 $-z_0+4(n+1)c$.
 
-We concentrate our attention only on the region $a\le z<z_0$. From
+We concentrate our attention only on the region $0\le z<z_0$. From
 Fig. \ref{fig:sideview} we see that the $G=0$
@@
 capacitor $E_{0z}=-4\pi q_0/ab=-16\pi q_0/A$, which corresponds to the
-potential $\phi_0=16\pi q_0 z/A$. Other contiguous planes of with opposite charges
+potential $\phi_0=16\pi q_0 z/A$. Other pairs of contiguous planes of with opposite charges
 contribute to the field elsewhere. The contributions to the potential
@@
 Using Eq. \eqref{Eq:J} we can correlate the local current density at
-the sample as it is prepared with its geometric and optical
-properties. For the calculation of the optical properties we use the
-well known transfer matrix method \notaL{refs}.
-\notaL{\sout{No necesitamos presentar la teoría de matrices de
-  transferencia. No hay nada original ahí.}}
+the sample as it is prepared with its geometric, structural and optical
+properties.
+
+\notaL{Quizás ni merece ser mencionado aquí: For the calculation of the optical properties we use the
+well known transfer matrix method \notaL{refs}.}
 
@@
   \includegraphics[width=.8\textwidth]{paper-5}
-  % \\[12pt]
-  % \includegraphics[scale=0.6]{Images/DE1}
 
   \caption{Experimental set-up for
-    the fabrication of porous silicon with GRIN, consisting of a
+    the fabrication of GRIN PS structures. We show a side view of the
     electrochemical cell with the shape of a
-    rectangular prism. We indicate the Si wafer (dark
+    rectangular prism (top panel). We indicate the Si wafer (dark
     gray), the teflon cell (light gray), the sealing o-ring (black
@@
     parameters of the arrangement $x_0$, $z_0$, $a$ and $c$
-    and the current source (upper panel) and a few current density
-    field lines. Top (middle panel) and
-    side (lower panel) schematic views of the resulting sample,
-    illustrating three regions $A$, $B$ and $C$ of relatively high, medium and
-    low porosity respectively illustrating the gradients in pore
-    size, density and depth.}
+    and the current source and a few schematic current flux
+    lines. Top and side schematic views of the resulting sample
+    (middle and lower panels),
+    illustrating eght regions $1\ldots8$ of decreasing porosity,
+    illustrating the changes in pore radii,
+    length, and density and the porosity gradient.}
   \label{fig:DE1}
@@
 
-\notaL{\sout{Cambié el título, pues tienes una mezcla de experimento y
-  teoría aquí}}
 In Fig. \ref{fig:DE1} we show a schematic representation of our
-experimental setup to manufacture porous silicon with GRIN.
+experimental setup to manufacture GRIN PS structures.
 As dicussed above, we fabricated an electrolytic cell with the shape of a
@@
 electrical contact to a gold plate \notaL{Lo inventé; de qué material es
-  el contacto bajo la muestra} which together make the anode. The
+  el contacto bajo la muestra?} which together make the anode. The
 cathode consists of a platinum wire insulated except for a small region
@@
 
-\subsection{Fabrication of PS  GRIN Single Layers}
+\subsection{Fabrication of GRIN  PS Single Layers}
 \label{sec:fabrication-ps-grin}
@@
 acid (HF) (concentration 48\% wt), glycerol (purity 99.8 \% wt) and
-ethanol (purity 99.9\% wt) in a 3:7:1 volume ratio. After the
+ethanol (purity 99.9\% wt) in a 3:7:1 volume ratio. \notaL{Checa que
+  todo esto sí corresponda a tus últimas muestras} After the
 anodizing process, the samples were rinsed with
@@
 of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
-size $6.2\text{mm}\times2.03\text{cm}$) with an uncovered sample area
-of about $1.21\text{cm}^2$. The height of the liquid was set at
-$c=1\text{cm}$. The cathode was a
-platinum wire that with a diameter of $0.41\text{mm}$ insulated by a
-teflon cylinder of external diameter $2\text{mm}$. \notaL{¿Están
-  bien estos diámetros?} with an uncovered tip located at $\bm r_0=(x_0,
-y_0,z_0)=(0.1,0.31,0.9)$.
-We manufactured a sample applying a current $I=5\text{mA}$,
-which yielded current densities in the range
-$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$,\notaL{verificar} during an attack time
-$t_1=600 \text{s}$, and another sample using a larger
-current $I=40\text{mA}$, corresponding to current densities in the
-range $j_\perp=20-50\text{mA}/\text{cm}^2$, for a time $t_2=200 \text{s}$ . \notaC{
-Coloque los tiempo de ataque para $t_1$ y $t_2$}
+sides $a=2.03\,\text{cm}$ and $b=1.48\,\text{cm}$, with an uncovered sample area
+of about $3\,\text{cm}^2$. The height of the liquid was set at
+$c=1\,\text{cm}$. The cathode was a
+platinum wire that with a diameter of $0.41\,\text{mm}$ insulated by a
+teflon cylinder of external diameter $\,2\text{mm}$, with an uncovered
+tip located at $\bm r_0=(x_0,
+y_0,z_0)=(0.2\,\text{cm},0.74\,\text{cm},0.9\,\text{cm})$. \notaL{Checa todos estos datos}
+We manufactured three samples $G_1$, $G_2$ and $G_3$ by applying a
+current $I_1=5\,\text{mA}$, $I_2=10\,\text{mA}$ and
+$I_3=20\,\text{mA}$, respectively, during a time of $t=250s$.
+
+\ifexclude
+\notaL{Tal vez esto no lo hicimos:
   \subsection{Morphological studies}
@@
 films at different positions along the sample from its top and side
-views (Fig. \ref{fig:DE1}). \notaL{¿Sí se midió la porosidad con SEM?}
+views (Fig. \ref{fig:DE1}).} \notaL{¿Sí se midió la porosidad con SEM?}
+\fi %exclude
 
@@
 \label{sec:refl-meas}
-We measured the reflectivity spectra using a {\em Perkin Elmer Lambda 950}
-UV-Vis-NIR spectrophotometer. For iterpretation of the data in the
-case of a single PS layer we used
-the standard formula \cite{T8,T9} \notaL{\sout{referencia}} for three media air (0), PS
-(1) and c-Si (2),
- \begin{eqnarray}\label{Eq:ECMR}
-   R=\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}{1+r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}
-\end{eqnarray}
-%where $ r_{01} $ y $ r_{12}$ are the Fresnel reflectance
-coefficients at the air/PS and PS/c-Si interfaces \cite{T10,T11}
-and $\delta=k_{PS}^\perp d$, where $k_{PS}^\perp$ is
+We measured the reflectivity spectra at different positions over our
+samples using a {\em Perkin Elmer Lambda 950}
+UV-Vis-NIR spectrophotometer.\notaL{Finalmente, ¿fue éste el que se
+  usó? Si sí, ¿hay algo internesante que decir sobre el? Cosas como el
+tamaño de mancha, resolución espectral, etc.} For interpretation of the
+data layer we used
+the standard formula \cite{T8,T9} for the reflectance of three media:
+air (0) environment, the PS film (1) and the c-Si substrate (2),
+ \begin{equation}\label{Eq:ECMR}
+   R=\left |\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}{1+r _ {_
+   {01}}r _ {_ {12}} e^{2i\delta}}\right |^2
+\end{equation}
+where $r_{01}$ and $r_{12}$ are the Fresnel reflectance
+coefficients of the air/PS and PS/c-Si interfaces \cite{T10,T11}
+and $\delta=k_1^\perp d$, where $k_1^\perp$ is
 the component of the wavevector perpendicular to the surface within
-the porous layer of thickness $d$.
-
-\subsection{Refraction Index of PS GRIN Single Layers}
-\label{sec:refraction-index-ps}
-The local refractive index $n_{PS}$ of the PS layer was calculated from its
-porosity $p$ through
-Bruggeman's effective medium theory \cite{I20}
-\begin{eqnarray}\label{Eq:Brugg}
- p\frac{1-\epsilon_{PS}} {1+\epsilon_{PS}} + (1-p)
-  \frac{\epsilon_{\text{Si}} - \epsilon_{PS}}
-  {\epsilon_{\text{Si}}+\epsilon_{PS}}=0
-\end{eqnarray}
-where the porosity $p$ is the volume fraction of air within the PS
-layer, $\epsilon_{Si}$ is the dielectric function of c-Si, and
-$\epsilon_{PS}=n_{PS}^2$ is the dielectric function of the PS.
-
+the porous layer of thickness $d$. The reflectance depends on the
+thickness of the film and on the index of refraction $n_1=n_{\text{PS}}$ of the porous
+layer, which we relate to the porosity through Bruggeman's
+effective medium theory \cite{I20},
+\begin{equation}\label{Eq:Brugg}
+ p\frac{1-\epsilon_1} {1+\epsilon_1} + (1-p)
+  \frac{\epsilon_2 - \epsilon_1}
+  {\epsilon_2+\epsilon_1}=0,
+\end{equation}
+where $\epsilon_2=\epsilon_{\text{Si}}$ is the dielectric function of
+the c-Si substrate, and
+$\epsilon_1=n_{\text{PS}}^2$ is the dielectric function of the PS layer.
+We fitted the reflectance spectra using the porosity $p$ and the
+thickness $d$ and a scale calibration factor $s$ as fitting
+parameters, and thus, we related the porosity
+$p$ and the etching rate $v=d/t$ to the local current density $j_\perp$.
+
+\ifexclude
+\notaL{Quitar esta sección:
 \subsection{Fabrication  of GRIN PS Microcavities}
@@
   elección?} For preparing the high index layers we
-chose a current $I_H=5\text{mA}$ applied during  time
-$t_H=35 \text{s}$. The current density was
-$j_{HA\perp}= 6\text{mA}/\text{cm}^2$ below the tip \notaL{checar},
+chose a current $I_H=5\,\text{mA}$ applied during  time
+$t_H=35 \,\text{s}$. The current density was
+$j_{HA\perp}= 6\,\text{mA}/\,\text{cm}^2$ below the tip \notaL{checar},
 and yielded (see Sec. \ref{sec:ps-grin-single} below)
 $n_H =2.6$, corresponding to a porosity $p_H =0.46$, and a
-thickness $d_H=0.066 \mu\text{m}$. The corresponding parameters for the low density
-layers were $I_L=38\text{mA}$, $j_{LA\perp}=50\text{mA}/\text{cm}^2$, $n_L= 1.4$,  $p_L =0.75$,
-$d_L=0.117 \mu \text{m}$, and $t_L=11 \text{s}$. For the rest of the
+thickness $d_H=0.066 \mu\,\text{m}$. The corresponding parameters for the low density
+layers were $I_L=38\,\text{mA}$, $j_{LA\perp}=50\,\text{mA}/\,\text{cm}^2$, $n_L= 1.4$,  $p_L =0.75$,
+$d_L=0.117 \mu \,\text{m}$, and $t_L=11 \,\text{s}$. For the rest of the
 sample the current density, porosity, index of refraction and thickness
@@
   consistentes con los de la sección \ref{sec:grin-porous-silicon}?}
+}
+\fi %exclude
 
@@
   \centering
-  \includegraphics[width=\textwidth]{Images/G123}
-  \caption{Normalized current density $j_\perp(z,0,0)/I$ calculated through
+  \includegraphics[width=1.2\textwidth]{j_Ivsxy.png}
+  \includegraphics[width=\textwidth]{j_Ivsx.png}
+  \caption{Normalized current density $j_\perp(x,y,0)/I$ calculated a
+    the surface of the sample through
     Eq. (\ref{Eq:J}) for a
     system as in Figs. \ref{f:celda} and \ref{fig:DE1} for a cell of
-    length $a = 2.03\text{cm}$ and width $b=0.62\text{cm}$, for a
-    point-like electrode at $\bm r_0=(0.1\text{cm},
-    0.31\text{cm},0.9\text{cm})$ (top panel). Normalized current
-    along the line $y=?$ (bottom panel). \notaL{Escoger el valor de
-      $y$ y poner la figura correspondiente} \notaL{Cambia los letreros, $J$ por
-      $j_\perp$. La ordenada no es a, sino $x$ y la abcisa no es b
-      sino $y$}.\notaL{Volverla a hacer con los datos
-      correctos. Rotular la figura con la misma notación que en el
-      texto. Preparar la figura como dos figuras independientes.}. }
+    length $a = 2.03\,\text{cm}$ and width $b=1.48\,\text{cm}$, with
+    the surface of the electrolyte at a heigth $c=1.0\,\text{cm}$, with a
+    point-like electrode at $\bm r_0=(0.2\,\text{cm},
+    0.74\,\text{cm},0.9\,\text{cm})$ (top panel). Normalized current
+    along the center line $y=0.74\,\text{cm}$ (bottom
+    panel).}
   \label{fig:DR1}
@@
 In Fig. \ref{fig:DR1} we show the current density $j_\perp(x,y,0)$ calculated through
-Eq. \eqref{Eq:J} at the surface of the sample for the cell we built
-(see Figs. \ref{f:celda} and \ref{fig:DE1}) with length
-$a=2.03\text{cm}$ and width $b = 0.62\text{cm}$, the height of the
-solution was taken as $c=1\text{cm}$ and we set the tip of the
-electrode at $\bm
-r_0=(x_0,y_0,z_0)=(0.1\text{cm},0.31\text{cm},0.9\text{cm})$
-\notaL{¿Por qué usaste estos valores? Asegurarte de usar valores
-  relevantes a lo que sigue y rehacer las gráficas.}
-For these parameters we obtained $ j_\perp/I\sim
-0.5-1.2\text{cm}^{-2}$.
-
-\subsection{PS GRIN Single Layer }
+Eq. \eqref{Eq:J} at the surface of the sample for our cell, as shown
+in Figs. \ref{f:celda} and \ref{fig:DE1} and described in
+Sect. \ref{sec:fabrication-ps-grin}). For these parameters we obtained
+a large range of values for $ j_\perp/I\sim 0.11-.72\,\text{cm}^{-2}$
+that vary mostly along the $x$ direction. Of course, this would differ
+for cells with aspect ratios closer to 1.
+
+\subsection{PS GRIN Films }
 \label{sec:ps-grin-single}
-\notaL{Quité la figura pues no añade nada}
-\notaL{Quité la descripción, pues está arriba}
+\begin{figure}
+ \centering
+  \includegraphics[width=\textwidth]{G3I20proc}
+  \caption{ Photograph of sample $G_3$ prepared as described in
+    Sec. \ref{sec:fabrication-ps-grin} using the same parameters as
+    in Fig. \ref{fig:DR1} with a current $ I_3=20 \text{mA}$,
+    during a time $t=250\text{s}$. We indicate eight regions $x_i$
+    $(i=1, 2,...8)$ centered at positions,
+    $x_1=0.2\text{cm}$,  $x_2=0.4\text{cm}$, $x_3=0.6\text{cm}$,
+    $x_4=0.8\text{cm}$, $x_5=1\text{cm}$, $x_6=1.2\text{cm}$,
+    $x_7=1.4\text{cm}$, $x_8=1.6\text{cm}$, with $y_n=0.74\,\text{cm}$
+    on which we measured reflectance spectra. During the preparation the cathode was over
+    the leftmost point $x_1$.}
+  \label{fig:SI3}
+\end{figure}
+
+In Fig. \ref{fig:SI3} we show a photograph of one of our samples,
+prepared as described in Sec. \ref{sec:fabrication-ps-grin}, with the
+same conditions as those corresponding to Fig. \ref{fig:SI3} applying a current
+$I_3=20\,\text{mA}$ during a time $t=250\,s$. We notice a series of
+visible interference fringes that get wider as we move towards the
+right end of the sample, consistent with a inhomogeneous film that
+gets thinner towards the right, and qualitatively consistent with
+Fig. \ref{fig:DR1} that shows a current density that decays towards
+the right. Equal color lines seem to correspond to iso-current lines of
+Fig. \ref{fig:SI3}, except very close to the the walls of the cell,
+where the film rapidly becomes very narrow. The reason is that there
+is a small region below the cell walls where the electrolyte penetrates
+up to the sealing o-ring (see upper panel of
+Fig. \ref{fig:DE1}) and towards which the current leaks from the
+neighborhood of the wall. Thus, we may expect our formula \eqref{Eq:J}
+to fail close to the border, at distances of the order of the radius
+of the cross-section of the o-ring.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{R20vslambda}
+  \caption{Reflectance spectra at different positions $(x,y)$
+    on sample $G_3$ (shown in Fig. \ref{fig:SI3}), where
+    $x=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
+  experimental results and results fitted through
+  equations~\eqref{Eq:ECMR}} and \eqref{Eq:Brugg}.
+  \label{fig:R20}
+\end{figure}
+
 \begin{figure}
@@
   \caption{(a)  Sample $G_1$ prepared as described in
-     \ref{sec:fabrication-ps-grin} using a current $I_1=5 \text{mA}$
-    during a time $t_1=600\text{s}$. We indicate three regions $A$,
+     \ref{sec:fabrication-ps-grin} using a current $I_1=5 \,\text{mA}$
+    during a time $t_1=600\,\text{s}$. We indicate three regions $A$,
     $B$, and $C$ centered at positions at positions,
-    $x_A=0.3\text{cm}$ \notaL{Atrás habías dicho que era justo abajo
+    $x_A=0.3\,\text{cm}$ \notaL{Atrás habías dicho que era justo abajo
       del electrodo. ¿Es cierto o no? ¿Dónde estaba el electrodo? ¿Qué
-    altura tenía el agua? ¿Igual que en la sección previa?}, $x_B=0.8\text{cm}$ and
-    $x_C=1.7\text{cm}$. \notaL{¿Cuánto vale $y$?} (b) Reflectance
+    altura tenía el agua? ¿Igual que en la sección previa?}, $x_B=0.8\,\text{cm}$ and
+  $x_C=1.7\,\text{cm}$. \notaL{¿Cuánto vale $y$?} (b) Reflectance
     spectra measured at the center of regions $A$, $B$, and $C$ and fit
@@
  In Fig. \ref{fig:DR3} we show a photograph of one of our single layer PS GRIN
- structures, $G_1$, prepared as described in
- \ref{sec:fabrication-ps-grin} applying a current $I_1=5\text{mA}$ for
- $t_1=600\text{s}$.\notaL{Quizás podamos quitar la repetición de I y
-   t} We employed the same geometry as that described in
- Sec. \ref{sec:current-density} \notaL{Lo inventé. ¿Es cierto?}
-The position of the electrode corresponds to the left side of the
+ structures, $G_3$, prepared as described in
+ \ref{sec:fabrication-ps-grin} applying a current $I_3=20\,\text{mA}$
+ for a time $t=250\,\text{s}$. We employed the same geometry as that described in
+ Sec. \ref{sec:current-density}
+The positions $\bm R_n=(x_n,y_n)$, $n=1\ldots8$  with
+$x_n=0.2n\,\text{cm}$ and $y_n=0.74\,\text{cm}$ on which reflectance
+spectra were measured are indicated. The electrode was situated above
+the position $\bm R_1$  corresponds to the left side of the
 photograph. The variation of the optical properties across the
@@
   gradiente en la dirección vertical cerca de los bordes?}
-We chose three positions $x_A=0.3\text{cm}$,
-$x_B=0.8\text{cm}$ and $x_C=1.7\text{cm}$ and
-$y_A=y_B=y_C=0.31\text{cm}$  \notaL{¿Son correctos estos
-  valores? Antes dijiste que $A$ estaba abajo del electrodo}\notaL{¿valor de y?} on
-which we measured the reflectance spectra, also shown in the figure. Location $A$ is
-closest to the electrode, while location $C$ is the furthest.
 
@@
 positions. Thus, we obtained that for our sample $G_1$
-$d_{1A}= 1320\text{nm}$, $ d_{1B} = 997\text{nm}$, and $d_{1c} = 605
-\text{nm}$.
+$d_{1A}= 1320\,\text{nm}$, $ d_{1B} = 997\,\text{nm}$, and $d_{1c} = 605
+\,\text{nm}$.
 \begin{figure}
@@
 Similarly, for a second sample $G_2$, etched with a
-larger current $I_2 =40 \text{mA}$, for a time $t_2=$?\notaL{El ancho no
+larger current $I_2 =40 \,\text{mA}$, for a time $t_2=$?\notaL{El ancho no
   tiene sentido si no especificas el tiempo} we obtained the
-depths $d_{2A}=1950\text{nm}$, $d_{2B}=1690\text{nm}$, and $d_{2C}=
-1430\text{nm}$, and the corresponding porosities \notaL{las posiciones ¿fueron las mismas que para $G_1$?}, $p_{2A}= 0.76$, $p_{2B}=
+depths $d_{2A}=1950\,\text{nm}$, $d_{2B}=1690\,\text{nm}$, and $d_{2C}=
+1430\,\text{nm}$, and the corresponding porosities \notaL{las posiciones ¿fueron las mismas que para $G_1$?}, $p_{2A}= 0.76$, $p_{2B}=
 0.73$, and $p_{2C}= 0.68$.
@@
 $j_\perp$ obtained from Fig. \ref{fig:DR1} by scaling by the actual
-current $I_1=5\text{mA}$ and $I_2=40\text{mA}$ employed to prepare
+current $I_1=5\,\text{mA}$ and $I_2=40\,\text{mA}$ employed to prepare
 samples $G_1$ and $G_2$, respectively (Eq. \eqref{Eq:J}). We indicate the values
@@
 
+\notaL{Removí lo de grinMC}
+\ifexclude
 \subsection{PS GRIN Microcavities}
@@
 electrolytic cell with a current $I_H$ during a time $t_H$ and with a
-current $I_L$ during a time $t_L$. We chose the currents $I_H=5\text{mA}$
-and $I_L=40\text{mA}$ \notaL{¿son correctos estos valores?}, the same
+current $I_L$ during a time $t_L$. We chose the currents $I_H=5\,\text{mA}$
+and $I_L=40\,\text{mA}$ \notaL{¿son correctos estos valores?}, the same
 that were used above to prepare samples $G_1$ and $G_2$.
@@
 position $A$ tuned to a given wavelength
-$\lambda_c=0.67\mu\text{m}$. Thus, we chose the thicknesses so they
+$\lambda_c=0.67\mu\,\text{m}$. Thus, we chose the thicknesses so they
 correspond to quarter wavelength plates, $n_Hd_H=n_Ld_L=\lambda_c/4$,
@@
     of the three measuring points $A$, $B$ and $C$. The cavity was
-    tuned to the wavelength $\lambda_c=0.67\mu\text{m}$ at position
-    $A$ (see text). We chose $x_A=0.3\text{cm}$, $x_B=0.8\text{cm}$,
-    and $x_C=1.2\text{cm}$. (b-d) Reflectance spectra measured and
+    tuned to the wavelength $\lambda_c=0.67\mu\,\text{m}$ at position
+    $A$ (see text). We chose $x_A=0.3\,\text{cm}$, $x_B=0.8\,\text{cm}$,
+    and $x_C=1.2\,\text{cm}$. (b-d) Reflectance spectra measured and
     calculated at positions $A-C$. For the calculation, the porosity
@@
 positioned. In the figure we indicate three points with $x$ coordinates
-$x_A=0.3\text{cm}$,  $x_B=0.8\text{cm}$, and $x_C=1.2\text{cm}$
+$x_A=0.3\,\text{cm}$,  $x_B=0.8\,\text{cm}$, and $x_C=1.2\,\text{cm}$
 on which we measured the reflectance spectra, also shown in the figure.
@@
      Fig. \ref{fig:MCGRIN3}. The total thickness of the system at
-     different positions, $d_A=2.25\mu\text{m}$,
+     different positions, $d_A=2.25\mu\,\text{m}$,
      $d_B=2.17\mu\text{m}$, and $d_C=1.87\mu\text{m}$ are
@@
   cuánto vale $N$ y no has dicho cuánto valieron $d_L$ y $d_H$}
+\fi %exclude
 

### 2020-09-17 paper.tex
Revise up to results

@@
 easily computed would be useful.
-Though $\bm j(\bm r)$ may be in principle be numerically calculated for a
+Though $\bm j(\bm r)$ may be numerically calculated for any
 given arbitrary experimental setup,  here we propose a particularly
@@
 
-We assume that our electrolytic cell has the shape of a
-prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
+We assume that our electrolytic cell has the shape of a rectangular
+prism (see Fig. \ref{f:celda}) with a horizontal base of sides $a$ and $b$, and
 filled with the electrolyte up to a height $c$. We assume that the
@@
 covered with the sample, which is an
-electrically grounded good conductor. Within the electrolyte we position an electrode
+electrically grounded relatively good conductor. Within the electrolyte we position an electrode
 which we assume is a thin conducting wire, insulated from the electrolyte
-but for a small area near its tip, which we thus approximate as a
+but for a small tip, which we approximate as a
 point current source.
@@
 stationary situation
-$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
+$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, the potential
+obeys Laplace's equation within the electrolyte,
 \begin{equation}
@@
 The effective conductivity of the relatively thin sample in contact
-with the grounded counterelectrode is large enough that we may assume its
+with the grounded counter-electrode is large enough that we may assume its
 surface $z=0$ is an equipotential.
@@
 \begin{equation}
+  \label{eq:E0}
 E_x(0, y ,z)= E_x(a, y ,z)=E_y(x, 0 ,z)=E_y(x, b
@@
 $q_0$ at the tip of the electrode at $\bm r_0$, and an array of its fictitious image
-charges. The images include a reflection on the conducting bottom of the
+charges situated out of the cell. They include an image on the conducting bottom of the
 cell, of the opposite charge $-q_0$ and situated at $(x_0, y_0,-z_0)$,
@@
 and situated at $(-x_0,y_0,z_0)$, $(x_0,-y_0, z_0)$, $(2a-x_0, y_0,
-z_0)$ and $(x_0, 2b-y_0,z_0)$ to guarantee that no current goes across
-them. Similarly, there is an image of the same charge $q_0$ at
-$(x_0,y_0,2c-z_0)$ to guarantee that no current goes across the
+z_0)$ and $(x_0, 2b-y_0,z_0)$ so that, taken one at a time, no current goes across
+the corresponding wall. Similarly, there is an image of the same charge $q_0$ at
+$(x_0,y_0,2c-z_0)$ so that no current goes across the
 surface of the electrolyte. Furthermore, each image charge has to be
-further reflected by each of the aforementioned surfaces, yielding new
-images.
+further reflected by each of the aforementioned surfaces, yielding
+infinitely many new images so that Eqs. \eqref{eq:ground} and
+\eqref{eq:E0} hold when all charges are considered together.
 \begin{figure}
@@
   \includegraphics[width=\textwidth]{paper-1}
-  \caption{Top view of the fictitious system formed by reflections of
+  \caption{Top view of the $z=z_0$ plane of the fictitious system formed by reflections of
     the electrolytic cell (light blue) showing the charge at the
@@
 -y_0, z_0)$. In Fig. \ref{fig:sideview} we show a lateral view of the
-image charges.
+image charges within the plane $y=y_0$.
 \begin{figure}
@@
   \includegraphics[width=\textwidth]{paper-2}
-  \caption{Side view of the fictitious system formed by reflections of
+  \caption{Side view of the $y=y_0$ plane of the fictitious system formed by reflections of
     the electrolytic cell (light blue)
@@
 the bottom of the cell yields an
-plane of image charges of the opposite sign, while reflections
+plane of image charges of the opposite sign, while each reflection
 on the surface of the liquid yields a plane of charges of the same
@@
 Nevertheless, as we need the potential and the field to obtain the
-current density on the surface of the sample on which there are no
-real nor image charges, we may perform a somewhat simpler planewise
+current density on the surface of the sample on which  no
+real nor image charges lie, we may perform a somewhat simpler planewise
 summation, where we first obtain the potential and field produced by a
@@
 
-We consider first a system made of identical unit charges
+We consider first a system made of identical {\em unit} charges
 ocuppying the positions $\bm R$ of a 2D Bravais lattice $\{\bm R\}$,
@@
  \end{eqnarray}
-an homogeneous equation for $z\ne0$ which may be trivially
+for each coefficient, an homogeneous equation for $z\ne0$ which may be trivially
 solved. After applying boundary conditions at $z=0$ and regularity
@@
 
-We concentrate our attention only on the region $0\le z<z_0$. From
+We concentrate our attention only on the region $0\le z<z_0$ above the
+sample but below the electrode. From
 Fig. \ref{fig:sideview} we see that the $G=0$
@@
 contribute to the field elsewhere. The contributions to the potential
-from the $G\ne0$ are simple geometric sums that may be added
-analytically over $n$ and yield the total potential
+from the $G\ne0$ terms are simple geometric series that may be summed
+over $n$ analytically and yield the total potential
 \begin{equation}
@@
 as the contributions of opposite non-null reciprocal vectors cancel
-out. As expected, all the charges that leave the sample find
+out: as expected, all the charges that leave the sample find
 their way  to the cathode across the electrolyte.
@@
 \label{sec:fabrication-ps-grin}
-We manufactured single layer PS structures through an electrochemical
-anodization on a (100) $p$-type crystalline Si wafer
+We manufactured single layer PS structures through electrochemical
+anodization of a (100) $p$-type crystalline Si wafer
 (resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
@@
 of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
-sides $a=2.03\,\text{cm}$ and $b=1.48\,\text{cm}$, with an uncovered sample area
+sides $a=2.01\,\text{cm}$ \notaL{Cambié el número, de acuerdo a unas
+  mediciones de Cristian} and $b=1.48\,\text{cm}$, with an uncovered sample area
 of about $3\,\text{cm}^2$. The height of the liquid was set at
@@
 thickness $d$ and a scale calibration factor $s$ as fitting
-parameters, and thus, we related the porosity
-$p$ and the etching rate $v=d/t$ to the local current density $j_\perp$.
-
-\ifexclude
-\notaL{Quitar esta sección:
-\subsection{Fabrication  of GRIN PS Microcavities}
-\label{sec:fabrication-grin-ps}
-After characterizing the fabrication process through measurements and
-calculations corresponding to single PS GRIN layers, we
-fabricated PS GRIN microcavities (MC) as specific defects between two distributed Bragg
-mirrors  (DBR). Alternate quarter wavelength plates of high (H) and low (L)
-refractive indices $n_H$ and $n_L$ and of thicknesses $d_H$ and $d_L$,
-respectively, were prepared satisfying the Bragg condition
-$n_Hd_H=n_Ld_L=\lambda_c/4$ at a given design
-wavelength $\lambda_c$ and at a position $A$ (Fig. \ref{fig:DE1}) which
-we chose as that directly below the point-like electrode.\notaL{Checar
-  veracidad} The defect
-was chosen as a half-wavelength high index layer of thickness $d_d=2d_H$ such that
-$n_Hd_d=\lambda_c/2$. The MC corresponds to the
-sequence $(HL)_6HH(LH )_6$ \notaL{Esto no corresponde a la
-  realidad. Cambiar.} where each letter $H$ or $L$ corresponds to
-a quarter-wave plate of high and low index of refraction correspondingly.
-We chose $\lambda_c= 0.67 \mu\text{m}$.\notaL{Algún motivo para esta
-  elección?} For preparing the high index layers we
-chose a current $I_H=5\,\text{mA}$ applied during  time
-$t_H=35 \,\text{s}$. The current density was
-$j_{HA\perp}= 6\,\text{mA}/\,\text{cm}^2$ below the tip \notaL{checar},
-and yielded (see Sec. \ref{sec:ps-grin-single} below)
-$n_H =2.6$, corresponding to a porosity $p_H =0.46$, and a
-thickness $d_H=0.066 \mu\,\text{m}$. The corresponding parameters for the low density
-layers were $I_L=38\,\text{mA}$, $j_{LA\perp}=50\,\text{mA}/\,\text{cm}^2$, $n_L= 1.4$,  $p_L =0.75$,
-$d_L=0.117 \mu \,\text{m}$, and $t_L=11 \,\text{s}$. For the rest of the
-sample the current density, porosity, index of refraction and thickness
-varied, yielding a PS GRIN MC. \notaL{Los datos de arriba ¿son
-  consistentes con los de la sección \ref{sec:grin-porous-silicon}?}
-}
-\fi %exclude
+parameters, and thus, we obtained the porosity
+$p$ and the etching rate $v=d/t$ for different values of the local
+current density $j_\perp$ expected at several positions on different
+samples.
 

### 2020-09-17 paper.tex
Revise up to the SEM images. Remove them.

@@
     system as in Figs. \ref{f:celda} and \ref{fig:DE1} for a cell of
-    length $a = 2.03\,\text{cm}$ and width $b=1.48\,\text{cm}$, with
+    length $a = 2.01\,\text{cm}$ and width $b=1.48\,\text{cm}$, with
     the surface of the electrolyte at a heigth $c=1.0\,\text{cm}$, with a
@@
 that vary mostly along the $x$ direction. Of course, this would differ
-for cells with aspect ratios closer to 1.
+for cells with different aspect ratios.
 
@@
     $(i=1, 2,...8)$ centered at positions,
-    $x_1=0.2\text{cm}$,  $x_2=0.4\text{cm}$, $x_3=0.6\text{cm}$,
-    $x_4=0.8\text{cm}$, $x_5=1\text{cm}$, $x_6=1.2\text{cm}$,
-    $x_7=1.4\text{cm}$, $x_8=1.6\text{cm}$, with $y_n=0.74\,\text{cm}$
-    on which we measured reflectance spectra. During the preparation the cathode was over
-    the leftmost point $x_1$.}
+    $x'_1=0.2\text{cm}$,  $x'_2=0.4\text{cm}$, $x'_3=0.6\text{cm}$,
+    $x'_4=0.8\text{cm}$, $x'_5=1\text{cm}$, $x'_6=1.2\text{cm}$,
+    $x'_7=1.4\text{cm}$, $x'_8=1.6\text{cm}$, with $y_n=0.74\,\text{cm}$
+    on which we measured reflectance spectra. Here,
+    $x'_n=x_n+0.14\,\text{cm}$ is the position from the sealing o-ring.}
   \label{fig:SI3}
@@
 In Fig. \ref{fig:SI3} we show a photograph of one of our samples,
+$G_3$
 prepared as described in Sec. \ref{sec:fabrication-ps-grin}, with the
-same conditions as those corresponding to Fig. \ref{fig:SI3} applying a current
+same conditions as those corresponding to Fig.~\ref{fig:DR1} applying
+a current
 $I_3=20\,\text{mA}$ during a time $t=250\,s$. We notice a series of
@@
 Fig. \ref{fig:DE1}) and towards which the current leaks from the
-neighborhood of the wall. Thus, we may expect our formula \eqref{Eq:J}
+neighborhood of the wall. The width of this region is
+$0.14\,\text{cm}$. Thus, we may expect our formula \eqref{Eq:J}
 to fail close to the border, at distances of the order of the radius
-of the cross-section of the o-ring.
+of the cross-section of the o-ring, of the order of a milimeter. The
+figure shows eight positions
+$x'_n=0.2\,\text{cm},0.4\,\text{cm},\ldots,1.6\,\text{cm}$ on which we
+measured the near normal incidence reflection spectra of the
+sample. Here, we defined $x'_n$ as the distance to the sealing o-ring,
+which differed by $0.14\,\text{cm}$ from the corresponding distance
+$x_n$ to the wall of the cell.
 
@@
   \includegraphics[width=\textwidth]{R20vslambda}
-  \caption{Reflectance spectra at different positions $(x,y)$
+  \caption{Reflectance spectra at different positions
     on sample $G_3$ (shown in Fig. \ref{fig:SI3}), where
-    $x=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
+    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
   experimental results and results fitted through
@@
 \end{figure}
- In Fig. \ref{fig:DR3} we show a photograph of one of our single layer PS GRIN
- structures, $G_3$, prepared as described in
- \ref{sec:fabrication-ps-grin} applying a current $I_3=20\,\text{mA}$
- for a time $t=250\,\text{s}$. We employed the same geometry as that described in
- Sec. \ref{sec:current-density}
-The positions $\bm R_n=(x_n,y_n)$, $n=1\ldots8$  with
-$x_n=0.2n\,\text{cm}$ and $y_n=0.74\,\text{cm}$ on which reflectance
-spectra were measured are indicated. The electrode was situated above
-the position $\bm R_1$  corresponds to the left side of the
-photograph. The variation of the optical properties across the
-sample is evident. \notaL{Tenemos algo sensato que decir sobre el
-  gradiente en la dirección vertical cerca de los bordes?}
-
+
+\ifexclude
 The thicknesses of the layer were measured
@@
 \end{figure}
-We fitted then reflectance measurements using Eqs. \eqref{Eq:ECMR} and
-\eqref{Eq:Brugg} using the local porosities $p_{1A}$, $p_{1B}$ and $p_{1C}$ as
-adjustable parameters and using Eqs. \eqref{Eq:ECMR} and
-\eqref{Eq:Brugg}. We obtained $p_{1A}=0.44$, $p_{1B}=0.42$, and
+\fi %exclude
+We fitted the reflectance measurements using Eqs. \eqref{Eq:ECMR} and
+\eqref{Eq:Brugg} using the local porosity $p$, and the thickness of the
+film  as
+adjustable parameters. We also fitted a scaling parameter $s$ to allow
+for calibration variations among spectra. ****AQUIVOY***
+
+ We obtained $p_{1A}=0.44$, $p_{1B}=0.42$, and
 $p_{1C}= 0.40$. The fitted reflectance has a good agreement with the

### 2020-09-17 paper.tex
Removed some commented out sections

@@
 \usepackage{xcolor}
-\newif{\ifexclude}
+\newif{\ifinclude}
 \newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
@@
 
-\ifexclude
+\ifinclude
 \notaL{Tal vez esto no lo hicimos:
@@
 views (Fig. \ref{fig:DE1}).} \notaL{¿Sí se midió la porosidad con SEM?}
-\fi %exclude
+\fi %include
 
@@
 
-\subsection{PS GRIN Films }
+\subsection{Samples }
 \label{sec:ps-grin-single}
@@
 neighborhood of the wall. The width of this region is
-$0.14\,\text{cm}$. Thus, we may expect our formula \eqref{Eq:J}
-to fail close to the border, at distances of the order of the radius
+$w=0.14\,\text{cm}$. Thus, we may expect our formula \eqref{Eq:J}
+to fail within that region and close to the border, at distances of the order of the radius
 of the cross-section of the o-ring, of the order of a milimeter. The
@@
 measured the near normal incidence reflection spectra of the
-sample. Here, we defined $x'_n$ as the distance to the sealing o-ring,
-which differed by $0.14\,\text{cm}$ from the corresponding distance
-$x_n$ to the wall of the cell.
+sample. Here, we defined $x'_n=x_n+w$ as the distance to the sealing o-ring,
+where $x_n$ is the corresponding distance to the wall of the
+cell.
+
+From Eq. \eqref{Eq:J} we evaluate the
+normalized current density $j_\perp/I$ expected at the positions $n$ indicated in
+Fig. \ref{fig:SI3}.
+(Table \ref{t:xj}).
+\begin{table}
+  \centering
+  \begin{tabular}{rrr}
+    \(x'\)(cm) & \(x\)(cm)& \(j_\perp/I\) (\(\text{cm}^{-2})\)\\
+    from edge& from wall&\\
+    \hline
+    0.2 & 0.06 & 0.7219\\
+    0.4 & 0.26 & 0.6723\\
+    0.6 & 0.46 & 0.5769\\
+    0.8 & 0.66 & 0.4645\\
+    1.0 & 0.86 & 0.3599\\
+    1.2 & 1.06 & 0.2749\\
+    1.4 & 1.26 & 0.2112\\
+    1.6 & 1.46 & 0.1666\\
+  \end{tabular}
+  \caption{Normalized current density expected at different positions on
+    different samples.}
+  \label{t:xj}
+\end{table}
+
+\subsection{Reflectance}
 
@@
   experimental results and results fitted through
-  equations~\eqref{Eq:ECMR}} and \eqref{Eq:Brugg}.
+  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
   \label{fig:R20}
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{Images/SPgrin51}
-  \caption{(a)  Sample $G_1$ prepared as described in
-     \ref{sec:fabrication-ps-grin} using a current $I_1=5 \,\text{mA}$
-    during a time $t_1=600\,\text{s}$. We indicate three regions $A$,
-    $B$, and $C$ centered at positions at positions,
-    $x_A=0.3\,\text{cm}$ \notaL{Atrás habías dicho que era justo abajo
-      del electrodo. ¿Es cierto o no? ¿Dónde estaba el electrodo? ¿Qué
-    altura tenía el agua? ¿Igual que en la sección previa?}, $x_B=0.8\,\text{cm}$ and
-  $x_C=1.7\,\text{cm}$. \notaL{¿Cuánto vale $y$?} (b) Reflectance
-    spectra measured at the center of regions $A$, $B$, and $C$ and fit
-    using Eq. \eqref{Eq:ECMR}.\notaL{¿Cuáles parámetros se ajustaron y
-      cuáles se midieron independientemente}\notaL{Para que no se vean
-      tan chicas las figuras, quita las R's y los números en el segundo
-      renglon, excepto en el extremo izquierdo, y pega las tres
-      figuras una tras la otra. Haz lo mismo en el tercer renglón,
-      quitando dos de los letreros Refractive index, pero antes
-      asegúrate de usar la misma escala en las tres figuras} (c)
-    Corresponding complex indices of refraction $n+ik$ obtained from
-    Eq. \eqref{Eq:Brugg} using the fitted porosities $p_{1A}=0.44$,
-    $p_{1B}=0.42$, and $p_{1C}= 0.40$ at the chosen positions. \notaL{En las
-      figuras escribe A, B y C en lugar de
-      Point A, Point B y Point C. Escribe $p_{1A}$, $p_{1B}$ y $p_{1C}$ en lugar
-      de la palabra Porosity. Escribe $n$ y $k$ nada más, sin la
-      palabra Real ni Imaginary. Usa Theory en lugar de
-      Simulation. Usa línea a trazos para la parte
-      imaginaria. Alínea todos los letreros. En inglés, los rótulos
-      a), b) y c) se escriben como (a), (b) y (c), aunque creo que se
-      pueden eliminar (porque además, no los alineaste bien). }
-  \notaL{A ojo no se notan las diferencias en epsilon. Mejor junta las
-  tres partes reales en una sola gráfica y las tres partes imaginarias
-en otra y ponerlas una al lado de la otra.}\notaL{Las letras A, B y C
-están colocadas en el lugar preciso, a escala?}\notaL{Quizás sea mejor
-que hagas tres figuras distintas, una para cada panel, y las alineamos
-con latex}}
-  \label{fig:DR3}
-\end{figure}
-
-\ifexclude
-The thicknesses of the layer were measured
-using SEM. In Fig. \ref{fig:DR4} we show side-view SEM micrographs of sample
-$G_1$ taken at the
-positions $A$, $B$, and $C$ shown in
-Fig. \ref{fig:DR3}. From these micrographs we can
-obtain the thicknesses of the porous layer at different
-positions. Thus, we obtained that for our sample $G_1$
-$d_{1A}= 1320\,\text{nm}$, $ d_{1B} = 997\,\text{nm}$, and $d_{1c} = 605
-\,\text{nm}$.
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{Images/semD11}
-  \caption{Side-view SEM micrographs of the PS GRIN single layer
-    taken at positions $A$, $B$, and $C$ of sample $G_1$ shown in
-    Fig. \ref{fig:DR3}.
-    \notaL{Quité la info redundante}}
-  \label{fig:DR4}
-\end{figure}
-\fi %exclude
+We measured the reflectance spectra of sample $G_3$ at the positions
+indicated in Fig. \ref{fig:SI3}. The results are shown in
+Fig. \ref{fig:R20}.
 We fitted the reflectance measurements using Eqs. \eqref{Eq:ECMR} and
 \eqref{Eq:Brugg} using the local porosity $p$, and the thickness of the
-film  as
+film  $d$ as
 adjustable parameters. We also fitted a scaling parameter $s$ to allow
-for calibration variations among spectra. ****AQUIVOY***
-
+for calibration variations among spectra. From the thickness we
+obtained the etching rate $v=d/t$. Notice that the fit is reasonably
+good. The contrast of the reflectance in the experiment is smaller
+than the fit. We believe this is due to the finite width
+\notaL{beams width=?} of the illuminating beam of our
+spectrometer. Thus, as our GRIN sample is not homogeneous, the
+experimental results show an average over regions with slightly
+different porosities and thicknesses, averaging out the interference
+maxima and minima. This is most notable for the thicker regions
+towards the left side of Fig. \ref{fig:SI3} and for smaller
+wavelengths. Similar remarks apply to the fits to the reflectance
+spectra of the other samples, incorporated in our supplemental
+material (Figs. \ref{fig:R5} and \ref{figR10}).
+The results obtained from the reflectance fits are summarized in table
+\ref{t:jpdv}.
+
+\begin{table}
+\centering
+\begin{tabular}{lrrrrrr}
+  Sample & current &  density \(j\) & porosity &
+  thickness & scale \(s\)& etching rate\\
+       & $I$ (mA)      & $j$ ($\text{mA}/\text{cm}^2$) & $p$
+       & $d$ ($\mu\text{m}$) & $s$ & $v$ (nm/s)\\
+\hline
+$G_1$ & 5  & 3.609 & 0.4943 & 0.3402 & 0.8493&  1.3608 \\
+      &    & 3.361 & 0.5713 & 0.3895 & 0.9789&  1.558  \\
+      &    & 2.884 & 0.5657 & 0.3312 & 0.9569&  1.3248 \\
+      &    & 2.322 & 0.5555 & 0.2732 & 0.9536&  1.0928 \\
+      &    & 1.799 & 0.5592 & 0.2236 & 0.9951&  0.8944 \\
+      &    & 1.374 & 0.5557 & 0.1886 & 0.9729&  0.7544 \\
+      &    & 1.056 & 0.5491 & 0.1512 & 0.9606&  0.6048 \\
+      &    & 0.833 & 0.5519 & 0.1238 & 0.9897&  0.4952 \\
+$G_2$ & 10 & 7.219 & 0.5910 & 0.6347 & 0.8559&  2.5388 \\
+      &    & 6.723 & 0.6437 & 0.6934 & 0.9914&  2.7736 \\
+      &    & 5.769 & 0.6383 & 0.5907 & 0.9523&  2.3628 \\
+      &    & 4.645 & 0.6265 & 0.5327 & 0.9798&  2.1308 \\
+      &    & 3.599 & 0.5991 & 0.4587 & 0.9389&  1.8348 \\
+      &    & 2.749 & 0.5902 & 0.4044 & 0.9449&  1.6176 \\
+      &    & 2.112 & 0.5753 & 0.3378 & 0.9361&  1.3512 \\
+      &    & 1.666 & 0.5711 & 0.2958 & 0.9481&  1.1832 \\
+$G_3$ & 20 & 14.438& 0.6860 & 1.2044 & 1.1491&  4.8176 \\
+      &    & 13.44 & 0.7129 & 1.1931 & 1.0767&  4.7724 \\
+      &    &11.538 & 0.7031 & 1.0443 & 1.0588&  4.1772 \\
+      &    & 9.29  & 0.6258 & 0.7516 & 1.0063&  3.0064 \\
+      &    & 7.198 & 0.6247 & 0.5380 & 1.0104&  2.152  \\
+      &    & 5.498 & 0.5927 & 0.4387 & 0.9625&  1.7548 \\
+      &    & 4.224 & 0.5844 & 0.3633 & 0.9625&  1.4532 \\
+      &    & 3.332 & 0.5909 & 0.3392 & 1.0112&  1.3568 \\
+\end{tabular}
+\caption{\label{t:jpdv}
+  Names of data files, current, current density and fitted parameters:
+  porosity, thickness and scale factor.}
+\end{table}
+
+\ifinclude
 We obtained $p_{1A}=0.44$, $p_{1B}=0.42$, and
@@
 fabrication of PS photonic structures, GRIN or otherwise.
-
+\fi %include
 \notaL{Removí lo de grinMC}
-\ifexclude
+\ifinclude
 \subsection{PS GRIN Microcavities}
@@
   cuánto vale $N$ y no has dicho cuánto valieron $d_L$ y $d_H$}
-\fi %exclude
+\fi %include
 
@@
 
+\section{Supplementary material}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{R5vslambda}
+  \caption{Reflectance spectra at different positions
+    on sample $G_1$ (shown in Fig. \ref{fig:SI3}), where
+    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
+  experimental results and results fitted through
+  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
+  \label{fig:R5}
+\end{figure}
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{R10vslambda}
+  \caption{Reflectance spectra at different positions
+    on sample $G_2$ (shown in Fig. \ref{fig:SI3}), where
+    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
+  experimental results and results fitted through
+  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
+  \label{fig:R10}
+\end{figure}
+
 \end{document}

### 2020-09-17 paper.tex
Revise until conclusions

@@
   \begin{tabular}{rrr}
-    \(x'\)(cm) & \(x\)(cm)& \(j_\perp/I\) (\(\text{cm}^{-2})\)\\
+    \(x'_n\)(cm) & \(x\)(cm)& \(j_\perp/I\) (\(\text{cm}^{-2})\)\\
     from edge& from wall&\\
@@
   \end{tabular}
-  \caption{Normalized current density expected at different positions on
-    different samples.}
+  \caption{Normalized current density $j_\perp/I$ expected at different positions $x'_n$.}
   \label{t:xj}
@@
 \subsection{Reflectance}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{R5vslambda}
+  \caption{Reflectance spectra at different positions
+    on sample $G_1$ ($I_1=5\,\text{mA}$), where
+    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
+  experimental results and results fitted through
+  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
+  \label{fig:R5}
+\end{figure}
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{R10vslambda}
+  \caption{Reflectance spectra at different positions
+    on sample $G_2$ (shown in Fig. \ref{fig:SI3}), where
+    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
+  experimental results and results fitted through
+  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
+  \label{fig:R10}
+\end{figure}
 
@@
 
-We measured the reflectance spectra of sample $G_3$ at the positions
-indicated in Fig. \ref{fig:SI3}. The results are shown in
-Fig. \ref{fig:R20}.
+We measured the reflectance spectra  at the positions indicated in
+Fig. \ref{fig:SI3} on our three samples $G_1$, $G_2$,
+and$G_3$, prepared using the same procedure
+(Sec. \ref{sec:fabrication-ps-grin}) but applying different currents
+$I_1=5\,\text{mA}$, $I_2=10\,\text{mA}$, and $I_3=20\,\text{mA}$, . The results are shown in
+Figs. \ref{fig:R5}, \ref{fig:R10}, and \ref{fig:R20}.
 We fitted the reflectance measurements using Eqs. \eqref{Eq:ECMR} and
@@
 for calibration variations among spectra. From the thickness we
-obtained the etching rate $v=d/t$. Notice that the fit is reasonably
-good. The contrast of the reflectance in the experiment is smaller
-than the fit. We believe this is due to the finite width
+obtained the etching rate $v=d/t$ at each position. Notice that the fit is reasonably
+good. The contrast of the reflectance in the experiment is somewhat smaller
+than in our fitted curves. We believe this is due to the finite width
 \notaL{beams width=?} of the illuminating beam of our
-spectrometer. Thus, as our GRIN sample is not homogeneous, the
-experimental results show an average over regions with slightly
+spectrometer. Thus, as our GRIN sample is not macroscopically homogeneous and its
+properties have a gradient, the
+experimental results have contributions from regions with slightly
 different porosities and thicknesses, averaging out the interference
-maxima and minima. This is most notable for the thicker regions
+maxima and minima. We also expect microscopic inhomogeneities such as
+interface roughness that might also reduce the contrast.
+This is most notable for the thicker regions
 towards the left side of Fig. \ref{fig:SI3} and for smaller
-wavelengths. Similar remarks apply to the fits to the reflectance
-spectra of the other samples, incorporated in our supplemental
-material (Figs. \ref{fig:R5} and \ref{figR10}).
+wavelengths.
+
 The results obtained from the reflectance fits are summarized in table
-\ref{t:jpdv}.
+\ref{t:jpdv}. Notice that the scaling parameters are close to 1,
+showing that the calibration was adequate. \notaL{Is this meaningful?}.
 
@@
 \begin{tabular}{lrrrrrr}
-  Sample & current &  density \(j\) & porosity &
-  thickness & scale \(s\)& etching rate\\
-       & $I$ (mA)      & $j$ ($\text{mA}/\text{cm}^2$) & $p$
+  Sample/ & position & density & porosity &
+  thickness & scale & etching rate\\
+  $I$ (mA) &$x'_n$ (cm)&  $j$ ($\text{mA}/\text{cm}^2$) & $p$
        & $d$ ($\mu\text{m}$) & $s$ & $v$ (nm/s)\\
 \hline
-$G_1$ & 5  & 3.609 & 0.4943 & 0.3402 & 0.8493&  1.3608 \\
-      &    & 3.361 & 0.5713 & 0.3895 & 0.9789&  1.558  \\
-      &    & 2.884 & 0.5657 & 0.3312 & 0.9569&  1.3248 \\
-      &    & 2.322 & 0.5555 & 0.2732 & 0.9536&  1.0928 \\
-      &    & 1.799 & 0.5592 & 0.2236 & 0.9951&  0.8944 \\
-      &    & 1.374 & 0.5557 & 0.1886 & 0.9729&  0.7544 \\
-      &    & 1.056 & 0.5491 & 0.1512 & 0.9606&  0.6048 \\
-      &    & 0.833 & 0.5519 & 0.1238 & 0.9897&  0.4952 \\
-$G_2$ & 10 & 7.219 & 0.5910 & 0.6347 & 0.8559&  2.5388 \\
-      &    & 6.723 & 0.6437 & 0.6934 & 0.9914&  2.7736 \\
-      &    & 5.769 & 0.6383 & 0.5907 & 0.9523&  2.3628 \\
-      &    & 4.645 & 0.6265 & 0.5327 & 0.9798&  2.1308 \\
-      &    & 3.599 & 0.5991 & 0.4587 & 0.9389&  1.8348 \\
-      &    & 2.749 & 0.5902 & 0.4044 & 0.9449&  1.6176 \\
-      &    & 2.112 & 0.5753 & 0.3378 & 0.9361&  1.3512 \\
-      &    & 1.666 & 0.5711 & 0.2958 & 0.9481&  1.1832 \\
-$G_3$ & 20 & 14.438& 0.6860 & 1.2044 & 1.1491&  4.8176 \\
-      &    & 13.44 & 0.7129 & 1.1931 & 1.0767&  4.7724 \\
-      &    &11.538 & 0.7031 & 1.0443 & 1.0588&  4.1772 \\
-      &    & 9.29  & 0.6258 & 0.7516 & 1.0063&  3.0064 \\
-      &    & 7.198 & 0.6247 & 0.5380 & 1.0104&  2.152  \\
-      &    & 5.498 & 0.5927 & 0.4387 & 0.9625&  1.7548 \\
-      &    & 4.224 & 0.5844 & 0.3633 & 0.9625&  1.4532 \\
-      &    & 3.332 & 0.5909 & 0.3392 & 1.0112&  1.3568 \\
+$G_1$/ 5 &0.2 & 3.609 & 0.4943 & 0.3402 & 0.8493&  1.3608 \\
+         &0.4 & 3.361 & 0.5713 & 0.3895 & 0.9789&  1.558  \\
+         &0.6  & 2.884 & 0.5657 & 0.3312 & 0.9569&  1.3248 \\
+         &0.8 & 2.322 & 0.5555 & 0.2732 & 0.9536&  1.0928 \\
+         &1.0 & 1.799 & 0.5592 & 0.2236 & 0.9951&  0.8944 \\
+         &1.2 & 1.374 & 0.5557 & 0.1886 & 0.9729&  0.7544 \\
+         &1.4 & 1.056 & 0.5491 & 0.1512 & 0.9606&  0.6048 \\
+         &1.6 & 0.833 & 0.5519 & 0.1238 & 0.9897&  0.4952 \\
+$G_2$/10&0.2 & 7.219 & 0.5910 & 0.6347 & 0.8559&  2.5388 \\
+         &0.4 & 6.723 & 0.6437 & 0.6934 & 0.9914&  2.7736 \\
+         &0.6 & 5.769 & 0.6383 & 0.5907 & 0.9523&  2.3628 \\
+         &0.8 & 4.645 & 0.6265 & 0.5327 & 0.9798&  2.1308 \\
+         &1.0 & 3.599 & 0.5991 & 0.4587 & 0.9389&  1.8348 \\
+         &1.2 & 2.749 & 0.5902 & 0.4044 & 0.9449&  1.6176 \\
+         &1.4 & 2.112 & 0.5753 & 0.3378 & 0.9361&  1.3512 \\
+         &1.6 & 1.666 & 0.5711 & 0.2958 & 0.9481&  1.1832 \\
+$G_3$/20 &0.2 & 14.438& 0.6860 & 1.2044 & 1.1491&  4.8176 \\
+          &0.4 & 13.44 & 0.7129 & 1.1931 & 1.0767&  4.7724 \\
+          &0.6 &11.538 & 0.7031 & 1.0443 & 1.0588&  4.1772 \\
+          &0.8 & 9.29  & 0.6258 & 0.7516 & 1.0063&  3.0064 \\
+          &1.0 & 7.198 & 0.6247 & 0.5380 & 1.0104&  2.152  \\
+          &1.2 & 5.498 & 0.5927 & 0.4387 & 0.9625&  1.7548 \\
+          &1.4 & 4.224 & 0.5844 & 0.3633 & 0.9625&  1.4532 \\
+          &1.6 & 3.332 & 0.5909 & 0.3392 & 1.0112&  1.3568 \\
 \end{tabular}
 \caption{\label{t:jpdv}
-  Names of data files, current, current density and fitted parameters:
-  porosity, thickness and scale factor.}
+  Current density and fitted parameters for saveral positions on
+  three samples:  porosity, thickness, scale factor and etching rate.}
 \end{table}
 
-\ifinclude
-We obtained $p_{1A}=0.44$, $p_{1B}=0.42$, and
-$p_{1C}= 0.40$. The fitted reflectance has a good agreement with the
-measured one, though its interference oscillations are larger towards
-the blue region probably due to the lack of surface scattering in our
-calculation. We also show in Fig. \ref{fig:DR3} the wavelength dependence of
-the complex index of refraction corresponding to the fitted porosities.
-Similarly, for a second sample $G_2$, etched with a
-larger current $I_2 =40 \,\text{mA}$, for a time $t_2=$?\notaL{El ancho no
-  tiene sentido si no especificas el tiempo} we obtained the
-depths $d_{2A}=1950\,\text{nm}$, $d_{2B}=1690\,\text{nm}$, and $d_{2C}=
-1430\,\text{nm}$, and the corresponding porosities \notaL{las posiciones ¿fueron las mismas que para $G_1$?}, $p_{2A}= 0.76$, $p_{2B}=
-0.73$, and $p_{2C}= 0.68$.
-
-\begin{figure}
-  \centering
-   \includegraphics[width=\textwidth]{Images/grinJDR}
-  \caption{(a)Current density calculated by scaling the results of
-    Fig. \ref{fig:DR1} by the currents $I_1=5\text{mA}$ and
-    $I_2=40\text{mA}$ used to prepare samples $G_1$ and $G_2$.
-. \notaL{Pon paréntesis de ambos
-      lados (a) y (b). El eje horizontal es $x$, no $a$. El eje
-      vertical es $j_\perp$.}
-    (b)Etching rate speed $v=d/t$ obtained at different positions $A$, $B$,
-    and $C$ over samples $G_1$ and $G_2$, where $d$ is the thickness
-    as measured from SEM micrographs, as in Fig. \ref{fig:DR4},
-    and $t$ is the etching time.\notaL{Falta una gráfica similar de
-      porosidad vs. x para las dos muestras}\notaL{Las escalas del
-      lado derecho no tienen que ver con las del lado
-      izquierdo. Deberías poner la misma escala de ambos lados, con el
-    mismo quiebre.}\notaL{Sugiero en la gráfica de la corriente
-    graficar las dos líneas completas, además de los 6 puntos
-    correpondientes a A, B y C de las dos muestras}}
-  \label{fig:JDR}
-\end{figure}
-
-In Fig. \ref{fig:JDR}(a) we show the current density
-$j_\perp$ obtained from Fig. \ref{fig:DR1} by scaling by the actual
-current $I_1=5\,\text{mA}$ and $I_2=40\,\text{mA}$ employed to prepare
-samples $G_1$ and $G_2$, respectively (Eq. \eqref{Eq:J}). We indicate the values
-corresponding to positions $A$, $B$, and $C$ on the samples.
-In Fig. \ref{fig:JDR} (b) we show the etching rate $v = d/t$ on
-selected positions of both samples obtained by dividing the thickness
-$d$ measured as in Fig. \ref{fig:DR4} by the etching time.
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{Images/grinJD31}
-  \caption{(a) Etching rate $v$ and (b) porosity $p$ as a function of the
-    density current $j_\perp$, obtained from Fig. \ref{fig:JDR}. We
-    show the data points and the results of power
-    law fits, yielding $v=0.68j_\perp^{0.69}$ and
-    $p=0.33j_\perp^0.21$, \notaC{cambie las expresiones $v=0.53j_\perp^{0.79}$
-    and $p=0.3j_\perp^0.24$}
-    with corresponding correlation coefficients
-      $r_v^2=0.951$ and $r_p^2=0.989$ \notaC{ tambien cambie $r_v^2=0.993$
-      and $r_p^2=0.0.847$ }(here $v$ is in nm/s, $p$ is
-      dimensionless and $j_\perp$ is in mA/cm$^2$). \notaL{cambia J por $j_\perp$, V por $v$ y P
-      por $p$. Quita el letrero fitting data, la ecuación y el valor
-      de $R^2$}\notaL{Los ajustes ¿son correctos con estas unidades?}}
-  \label{fig:Indr1}
-\end{figure}
-By relating among themselves the panels of Fig. \ref{fig:JDR} we
-may obtain the etching rate $v$ and the porosity $p$ as
-functions of the current density $j_\perp$. The results are shown in
-Fig. \ref{fig:Indr1}.\notaL{\ldots Apenas aquí dijiste cuál fue el
-  tiempo de ataque de la muestra dos: relating to depth and time ($
-  200 \ \ s $ ). ¿Es correcto este tiempo? Ponlo en su lugar}
-We fitted the data points with simple power laws and found
-\begin{equation}
-  \label{eq:etch}
-  v=0.68j_\perp^{0.69} \notaC{cambie v=0.53j_\perp^{0.79}}
-\end{equation}
-and
-\begin{equation}
-  \label{eq:poros}
-  p=0.33j_\perp^{0.21}, \notaC{cambie p=0.3j_\perp^{0.24}}
-\end{equation}
-where $v$ is
-expressed in nm/s, $p$ is dimensionless and $j_\perp$ is expressed as
-mA/cm$^2$. The corresponding correlation coefficients are $r_v^2=0.951$
-and $r_p^2=0.847$. \notaC{cambie $r_v^2=0.993$
-and $r_p^2=0.989$.}
-\notaL{Digresión teórica. El producto $pv$ es
-  proporcional a la cantidad de materia removida por segundo. En mi
-  opinión, esto debería ser proporcional a la corriente $pv\propto
-  j_\perp$. ¿Es correcto? A tí te sale algo parecido pero no
-  exacto. ¿Se podrá hacer un mejor ajuste tomando esto en cuenta?
-  ¿Alguien lo ha discutido en la literatura?}\notaL{En todo caso, todo
-  esto se tiene que rehacer usando la expresión teórica correcta y las
-  posiciones correctas}
-
-Fig. \ref{fig:Indr1} illustrates an advantage of using a cell
-geometry for which the current density may be obtained
-analytically. Namely, we can relate the etching rate and the
-porosity to the current density by taking measurements at
-different positions along just a few PS GRIN samples. Thus, it is much easier
-and faster to obtain calibration curves which are useful in the
-fabrication of PS photonic structures, GRIN or otherwise.
-\fi %include
-\notaL{Removí lo de grinMC}
-\ifinclude
-\subsection{PS GRIN Microcavities}
-\label{sec:grin-porous-silicon}
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{Images/MicrGrin}
-  \caption{\notaL{Está bonita la figura, pero tiene errores. La
-      superficie del electrolito y la superficie de la muestra
-      deben ser ambas horizontales. Cambia la fuente por fuente
-      de corriente. La punta del electrodo no debe ser una
-      bola. Quita todo lo que está abajo del sustrato. Mejor pon
-      solamente una H en alguna región amarilla y una L en
-      alguna región azul. El electrolito tiene gotas o
-      burbujas. Tal vez sea mejor ponerle un color uniforme. Quita los
-      anchos totales, pues no creo que nos sean útiles. Haz que los cables
-      horizontales sean horizontales.}
-    PS GRIN microcavity made of layers of high (H) and low (L)
-    refractive index $n_H$ and $n_L$ and widths $d_H$ and $d_L$
-    arranged in the sequence $(HL)_NHH(HL)_N$. \notaL{CUánto vale $N$?
-    Antes habías dicho que 6, pero en la figura 12 parece otra cosa} Both the index of
-    refraction and the widths depend on position along the
-    sample and are chosen to obey a quarter wavelength
-    condition at a given position $A$ and wavelength $\lambda_c$.
-  }
-  \label{fig:MCGRIN0}
-\end{figure}
-
-As a simple application of our preparation and calibration methods, we
-prepare a PS GRIN microcavity (MC), as illustrated in
-Fig. \ref{fig:MCGRIN0}.  Alternate layers of relatively high (H) and low and low
-(L) refractive indices $n_H$ and $n_L$, of corresponding thicknesses
-$d_H$ and $d_L$, are prepared by alternatingly etching a Si sample in our
-electrolytic cell with a current $I_H$ during a time $t_H$ and with a
-current $I_L$ during a time $t_L$. We chose the currents $I_H=5\,\text{mA}$
-and $I_L=40\,\text{mA}$ \notaL{¿son correctos estos valores?}, the same
-that were used above to prepare samples $G_1$ and $G_2$.
-We chose the etching times to obtain a MC at the given
-position $A$ tuned to a given wavelength
-$\lambda_c=0.67\mu\,\text{m}$. Thus, we chose the thicknesses so they
-correspond to quarter wavelength plates, $n_Hd_H=n_Ld_L=\lambda_c/4$,
-at this position and wavelength, yielding $n_H =2.6$,\notaL{Por qué no
-  coincide con el dato de la tabla 1?} $p_H =0.46$,
-$d_H=0.066\mu\text{m}$, $t_H=35\text{s}$, $n_L= 1.4$, $p_L =0.75$,
-$d_L=0.117\mu\text{m}$, $t_L=11\text{s}$.
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{Images/MCGRIN2}
-  \caption{(a)Top view photograph of a PS GRIN MC showing the position
-    of the three measuring points $A$, $B$ and $C$. The cavity was
-    tuned to the wavelength $\lambda_c=0.67\mu\,\text{m}$ at position
-    $A$ (see text). We chose $x_A=0.3\,\text{cm}$, $x_B=0.8\,\text{cm}$,
-    and $x_C=1.2\,\text{cm}$. (b-d) Reflectance spectra measured and
-    calculated at positions $A-C$. For the calculation, the porosity
-    and etching rates were obtained from Fig. \ref{fig:Indr1},
-    the dielectric functions and indices of refracton from
-    Eqs. \eqref{Eq:Brugg} and the reflectance from standard transfer
-    matrix theory. \notaL{Quizás haya que usar D E F en lugar de A B
-      C, pues A B C se usó para otras posiciones sobre la muestra
-      $G_1$ y $G_2$. ¿Son correctas las posiciones aquí?}}
-  \label{fig:MCGRIN3}
-\end{figure}
-
-\begin{table}
-  \centering
-  \begin{tabular}{ccccccc}
-    \hline
-    Pos.(kind)&Curr. dens.(mA/cm$^2$)&Porosity&Index&Wavelength($\mu\text{m}$)\\
-    \hline
-    \hline
-    A(H) & 5.5 & 0.45& 2.66& 0.65   \\
-    A(L) & 44  & 0.74& 1.44& 0.65   \\
-    B(H) & 4.0 & 0.41& 2.76& 0.58   \\
-    B(L) & 32  & 0.68& 2.29& 0.58   \\
-    C(H) & 3.0 & 0.39& 2.81&0.54    \\
-    C(L) & 24  & 0.64& 2.30&0.54    \\
-  \end{tabular}
-  \caption{Some properties of the PS GRIN MC corresponding to the
-    positions $A$, $B$ and $C$ and the corresponding high ($H$) and
-    low ($L$) index layers. The current densities were obtained by
-    scaling the results in Fig. \ref{fig:DR1} with $I_H$ and
-    $I_L$, the depths were obtained from the etching
-    times and the current density using \eqref{eq:etch}, the porosity
-    was obtained from Eq. \eqref{eq:poros}, the indices of refraction
-    were obtained from Eq. \eqref{Eq:Brugg} using the porosity, and
-    the resonant wavelengths of the cavity were read from
-    Fig. \ref{fig:MCGRIN3}.
-    \notaL{Inventé lo de arriba. Qué es cierto y qué
-      mentira?}\notaL{Por qué resuenas en 0.65 si habías diseñado
-      0.67 en A?} \notaL{¿De dónde sacaste
-        $\lambda_c$ para los otros puntos? ¿Cómo le hiciste para que
-        $\lambda_c$ diera lo mismo en $H$ y en $L$? $n$ y $k$ dependen de la
-        frecuencia. ¿Qué frecuencia usaste para darles valores en esta
-        tabla?}\notaL{quité digitos a n. quité k pues es chiquita,
-        ¿no? quité los tiempos pues son los mismos. Quité las
-        posiciones pues están descritas antes. Añade una columna
-        con las profundidades $d_H$ y $d_L$. }\notaL{De los rótulos de
-      la figura quita las palabras Point. Cambia simulation por Theory.}}
-	\label{tabla:1}
-\end{table}
-In Fig. \ref{fig:MCGRIN3} we show a photograph of a PS GRIN MC
-sample, which displays a color that shifts towards the blue when we
-move towards its right, that is, away from where the electrode was
-positioned. In the figure we indicate three points with $x$ coordinates
-$x_A=0.3\,\text{cm}$,  $x_B=0.8\,\text{cm}$, and $x_C=1.2\,\text{cm}$
-on which we measured the reflectance spectra, also shown in the figure.
-\notaL{Estas $x_A$ y $x_B$ son iguales a las anteriores, pero $x_C$
-  no. ¿Es correcto? Me dice que sí, pues no podría irse al
-  ultravioleta} \notaL{No dices cómo hiciste las curvas teóricas. Ya
-  me explicó. {\bf la teoría es trampa} Dado el mínimo de reflectancia
-medido, calculó una microcavidad {\em diseñada} para ese mínimo, en
-lugar de usar los anchos predichos} The
-spectra have the
-expected shape: a high reflectance plateau corresponding to the
-photonic band gap of the Bragg mirrors, with a deep narrow minimum due
-to the Fabry-Perot resonance of the cavity. We also present the
-calculated spectra. To that end, we calculated the current density
-using the theory developed in Sec. \ref{sec:calc-curr-dens}, i.e., by
-scaling Fig. \ref{fig:DR1} with the total current $I_H$ and $I_L$ used
-to fabricate each layer. From the current densities we obtained the
-corresponding etching rates and the porosities using
-Eqs.~\eqref{eq:etch} and  \eqref{eq:poros}, and from them, the
-thickness of each layer, the index of refraction
-(Eq. \eqref{Eq:Brugg}) and the reflectance,using standard transfer
-matrix theory \notaL{ref}. \notaL{Esto sería innecesario para los
-  puntos A y B, aunque tal vez sí se necesita para C, oyes $x_C$
-  parece ser distinto.}
-Notice the good agreement between theory
-and experiment. \notaL{No me lo creo. Me sospecho que más bien,
-  ajustaste el experimento no sé con qué parámetro. Explícame cómo
-  hiciste el cálculo.} The parameters used are shown in Table \ref{tabla:1}.
-\notaL{No entiendo qué quisiste decir aquí: For theoretical values, we
-  use complex refractive indices as free parameters to fit the
-  experimental refractive spectra (Section 4.2).} The band-gap, the
-resonance and the oscillations due to multiple reflections in the
-region of transparency are similar, though the experimental spectra is
-more rounded and the central resonance is wider. This might be due to
-the roughness of the interfaces, which would lead to some scattering
-whose effects are similar to those of an additional absorption
-\notaL{cita el artículo en prensa de Guille y mío}.\notaL{Checar que no
-  diga mentiras arriba. El ajuste es demasiado bueno, pero no sé cómo
-  se hizo. Hay que explicar qué significan y de dónde salieron las
-  $\lambda_c$ de la tabla. }
-
-\begin{figure}
-   \centering
-   \includegraphics[width=\textwidth]{Images/MCGRINSEM}
-   \caption{Cross section SEM images corresponding to the positions
-     $A$, $B$, and $C$ of the PS GRIN MC shown in
-     Fig. \ref{fig:MCGRIN3}. The total thickness of the system at
-     different positions, $d_A=2.25\mu\,\text{m}$,
-     $d_B=2.17\mu\text{m}$, and $d_C=1.87\mu\text{m}$ are
-     indicated. \notaL{Porque se ve una capa más ancha a la izquierda?
-       ¿Por qué el número de capas arriba no es igual que abajo? ¿Por
-       qué el número de capas no es el mismo en las distintas fotos?
-       ¿Por qué no es 6 como dice el texto en la
-       Sec. \ref{sec:fabrication-grin-ps}?}
-     }
-   \label{fig:MCGRIN4}
- \end{figure}
-In Fig. \ref{fig:MCGRIN4} we show SEM cross-sectional images of
-the PS GRIN MC sample. We can appreciate a relatively small interface
-roughness and a clear contrast between the high and low porosity
-layers. The structure of the microcavity is also visible, with a
-central layer of twice the thickness of the corresponding layers
-within the Bragg mirrors. The gradient of the thickness is also
-evident, as $d_A>d_B>d_C$, with $d_A=2.25\mu\text{m}$,
-$d_B=2.17\mu\text{m}$, and $d_C=1.87\mu\text{m}$ the total thickness
-of the structure measured at the positions $A$, $B$, and $C$.
-The measured thickness are in good agreement with those computed from
-the current densities and the etching times $N(d_H+d_L)+2 d_H$ using
-Eq. \eqref{eq:etch}, where $N$ is the number of pairs of layers in the
-Bragg mirrors, which yield $d_A=2.31\mu\text{m}$,
-$d_B=2.08\mu\text{m}$, and $d_C=1.65\mu\text{m}$. \notaL{Por qué una
-  te dio más grande y las otras más chicas? Aquí tienes que decir
-  cuánto vale $N$ y no has dicho cuánto valieron $d_L$ y $d_H$}
-\fi %include
+From the data in Table \ref{t:jpdv} we can plot the fitted porosity as
+a function of the calculated density current, as shown for our three
+samples in Fig. \ref{fig:p}.
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{pvsj}
+  \caption{Porosity as a function of current density for three samples
+    $G_1$, $G_2$, $G_3$. The data points for each sample are joined by
+    thick lines. The arrows point to data that correspond to
+    position $x'_1=0.2\,\text{cm}$, joined to the other data by a thin
+    line (see text). We include linear fits to the data from
+    sample $G_3$ (thick straight line) and to that from all the
+    samples (thin straight line). }
+  \label{fig:p}
+\end{figure}
+Notice that for each sample the data points lie around straight lines,
+except for one outlier point in each corresponding to position
+$x'_1$. As discussed in Sec. \ref{sec:ps-grin-single}, those points
+were very close to a wall of the electrolytic cell, so they were
+affected by leakage currents towards the underside of the wall.
+For this reason, we exclude those points from the following
+analysis. We made a linear fit to the data from sample $G_3$ and to
+the data from the three samples. A comparison shows that a fit to the
+data of just one sample, $G_3$, turns out to be a reasonable predictor for the
+porosity of all the samples.  From that fit we obtain that for our
+preparation conditions
+\begin{equation}\label{eq:p}
+  p\approx 0.013\frac{\text{cm}^2}{\text{mA}} j_\perp+0.53.
+\end{equation}
+
+Similarly, we can plot the fitted etching rate as
+a function of the calculated density current, as shown for our three
+samples in Fig. \ref{fig:v}.
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{vvsj}
+  \caption{Etching rate as a function of current density for three samples
+    $G_1$, $G_2$, $G_3$. The data points for each sample are joined by
+    thick lines. The arrows point to data that correspond to
+    position $x'_1=0.2\,\text{cm}$, joined to the other data by a thin
+    line (see text). We include linear fits to the data from
+    sample $G_3$ (thick straight line) and to that from all the
+    samples (thin straight line). }
+  \label{fig:v}
+\end{figure}
+As for the porosity, there are outlier points corresponding to the
+immediate proximity of the wall of the cell, but the remaining points
+lie on straight lines for each sample, and they
+may all be approximated by a linear fit to the data of just one
+sample, $G_3$, from which we get
+\begin{equation}\label{eq:v}
+  v\approx 0.35\frac{\text{cm}^2}{\text{mA}}
+  \frac{\text{nm}}{\text{s}}j_\perp + 0.092\frac{\text{nm}}{{s}}.
+\end{equation}
+
+Using Eqs. \eqref{eq:p}, \eqref{eq:v}, \eqref{Eq:ECMR}, and
+\eqref{Eq:Brugg}, we can calculate the reflectance spectra for any
+desired current density $j_\perp$ and etching time. This is
+illustrated in Fig. \ref{fig:Rvsjl} for the parameters that correspond
+to our samples.
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{jlr}
+  \caption{Reflection $R$ of a PS film as a function of the current density
+    current $j_\perp$ and wavelength $\lambda$ for an etching time
+    $t=250\,\text{s}$. Theory (left panel) and experiment (right
+    panel, see text). We indicate with the numbers 1, 2, 3 the
+    data corresponding to the corresponding samples $G_1$, $G_2$ and
+    $G_3$.}
+  \label{fig:Rvsjl}
+\end{figure}
+On the right hand side of the figure we display a quilt made by
+patching together the experimental reflectance data corresponding to
+Figs. \ref{fig:R5}- \ref{fig:R20}, ordered according to the
+corresponding current density as presented in Table
+\ref{t:jpdv}. Nevertheless, for the reasons mentioned above, we
+eliminated the data corresponding to position $x'_1$ on all
+samples. Furthermore, as the results corresponding to sample $G_2$ in
+Figs. \ref{fig:p} and  \ref{fig:v} seem shifted with respect to those
+of the other samples, in order to facilitate the visualization of the
+results, we artificially shifted horizontally towards the
+right their contributions to Fig. \ref{fig:Rvsjl} by
+$1\,\text{mA}/\text{cm}^2$. Notice that the experimental results may
+be grouped along bright and dark bands and that they correspond closely to
+those expected theoretically, though the experimental bands are somewhat shifted,
+especially for low current densities, and the minima are not as low.
+
+The theoretical reflectance coudl as well be calculated using
+Eqs. \eqref{eq:p}, \eqref{eq:v}, \eqref{Eq:ECMR}, and
+\eqref{Eq:Brugg}, for more complicated structures, in which the
+current $I$ is modulated in time, allowing the design and analysis of
+non-trivial multilayered GRIN PS structures.
 
@@
 
-\section{Supplementary material}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{R5vslambda}
-  \caption{Reflectance spectra at different positions
-    on sample $G_1$ (shown in Fig. \ref{fig:SI3}), where
-    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
-  experimental results and results fitted through
-  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
-  \label{fig:R5}
-\end{figure}
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{R10vslambda}
-  \caption{Reflectance spectra at different positions
-    on sample $G_2$ (shown in Fig. \ref{fig:SI3}), where
-    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
-  experimental results and results fitted through
-  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
-  \label{fig:R10}
-\end{figure}
-
 \end{document}

### 2020-09-17 paper.tex
Finish rewriting paper

@@
 %\usepackage[usenames]{color}
-\usepackage{showkeys}
+%\usepackage{showkeys}
 \usepackage{bm}
@@
 potentials in 2D reciprocal space, and it is made up of
-a rapidly converging sum of analytical terms. This allows the characterization
+a rapidly converging sum of analytical terms, just a few of which
+should be kept. This allows the characterization
 of the porosity of a PS layer and the etching
@@
 optical measurements on several positions of just a
-few samples. We illustrated the procedure with two samples each of which we
-measured at three different positions. These calibration curves are
-very useful as the etching rate for the formation of porous silicon
-and the resulting porosity is very sensitive to the growth conditions
-and to the properties of the substrate, such as its doping. Thus,
-there are no universal calibration curves. Having obtained these calibration curves
-and being able to compute the current density at different positions
-allows the prediction of the properties of GRIN structures. We
-illustrated this by desigining a PS GRIN microcavity tuned at one
-position to a given wavelength. We found a good agreement between its
-measured reflectance spectra at different points with the spectra
-calculated from the values of the expected local current
-density using the calibration curves. We also found good agreement
-between the measured and the expected geometry of the system. These
-results show that the use of a simple electrolytic cell and our
-computational procedure does allow the accurate prediction of the
-optical properties of GRIN structures, and thus we believe it will
-prove helpful for the design, fabrication, and characterization of novel
-devices based on PS GRIN systems.
+few samples. We illustrated the procedure with three samples on each of which we
+measured reflectance spectra at eight different positions.
+Through a optimization procedure we fitted the porosity and etching
+rate corresponding to each current density.
+We showed that an analysis of the data of just one of the samples, which we chose
+as that with the largest current density range, yielded calibration
+curves that allow the approximate prediction of the properties of the other
+samples. The calibration curves can be used to design and calculate the optical
+properties of other systems prepared under similar conditions, such as
+multilayered GRIN systems from which photonic crystals, microcavities
+and sensors with position dependent properties. This is the subject of
+ongoing work. As the etching rate for the formation of porous silicon
+and the resulting porosity are very sensitive to the growth conditions
+and to the properties of the substrate, such as its doping,
+there are no universal calibration curves. Thus, it is useful to have
+a procedure that from just one sample can produce calibration curves
+that may be employed for other samples grown in the same conditions.
 
@@
 \label{sec:acknowledgments}
-WLM acknowledges the support of DGAPA-UNAM under grant IN111119.
+WLM acknowledges the support of DGAPA-UNAM under grant
+IN111119. \notaL{Cristian debe agradecer a conacyt y faltan
+  agradecimientos de Vivechna (quizás incluyendo al icf)}
 % \backmatter

### 2020-09-17 paper.tex
Delete unused files, reorganize, update manuscript

@@
   \centering
-  \includegraphics[width=\textwidth]{Images/celdan1}
+  \includegraphics[width=\textwidth]{celdan1}
   \caption{Prism shaped electrolytic cell with a rectangular base of
@@
 $I_3=20\,\text{mA}$, respectively, during a time of $t=250s$.
-
-\ifinclude
-\notaL{Tal vez esto no lo hicimos:
-  \subsection{Morphological studies}
-\label{sec:morph-stud}
-The morphologies of the etched porous layers were
-observed using a Hitachi SU1510 scanning electron microscope (SEM)
-with which we measured the thickness $d$ and the porosity $p$ of the
-films at different positions along the sample from its top and side
-views (Fig. \ref{fig:DE1}).} \notaL{¿Sí se midió la porosidad con SEM?}
-\fi %include
 

### 2020-09-17 Programas/GrinJI.pl

@@ -1,180 +1,0 @@
-#!/usr/bin/env perl
-
-use strict;
-use warnings;
-
-use Getopt::Long;
-use List::Util;
-use POSIX qw(DBL_MAX);
-use PDL;
-use PDL::NiceSlice;
-use PDL::FFTW3;
-use PDL::Complex;
-use PDL::Graphics::Gnuplot;
-use constant {PI=>4*atan2(1,1), LM=>log(DBL_MAX)};
-use IO::Prompter;
-#use Chart::Gnuplot;
-#use GD::Graph;
-
-#Calculate current density in an electrolytic cell with a 'point'
-#electrode, to build GRIN structures.
-#Notes GX
-#Eq. Gx33
-
-#Normalize to I and to the area.
-my $a; #size of cell along x
-my $b; #size of cell along y
-my $C; #size of cell along z (water height)
-my ($X0, $Y0, $Z0); #positioin of electrode
-my $Z; #height to evaluate current.
-my $N; #2N+1=number of points along each direction
-my $I; #corriente
-# $M; #2*$M+1=size of mask in reciprocal space
-Getopt::Long::Configure('no_ignore_case');
-GetOptions(
-    'a=f'=>\$a,
-    'b=f'=>\$b,
-    'C=f'=>\$C,
-    'X0=f'=>\$X0,
-    'Y0=f'=>\$Y0,
-    'Z0=f'=>\$Z0,
-    'Z=f'=>\$Z,
-    'N=f'=>\$N,
-    'I=f'=>\$I,
-    #'M=f'=>\$M
-    )
-    or usage();
-usage("Undefined parameters") unless List::Util::all {defined $_}
-($a, $b, $C, $X0, $Y0, $Z0, $Z, $I, $N); #, $M);
-my $A=$a*$b; #area celda
-my $u=sqrt($A); #unidades
-my $a1=$a/$u; # largo adimensional
-my $c=$C/$u;  # altura de liquido adimensional
-my $x0=$X0/$u;
-my $y0=$Y0/$u;
-my $z0=$Z0/$u;
-my $z=$Z/$u;
-my $b1=1/$a1; #So area=1, this is our unit of area, and from here, distance
-#Real space
[…]

### 2020-09-18 paper.tex
Small corrections and changes

@@
   \label{eq:poisson}
-  \nabla^2\phi=-4\pi q_0\delta(\bm r-\bm r_0),
+  \nabla^2\phi=-4\pi q_0\delta^{(3)}(\bm r-\bm r_0),
 \end{equation}
@@
 \end{equation}
+Here, $\delta^{(D)}$ is Dirac's delta function in $D$ dimensions.
 This problem may be solved readily using image charge theory \cite{T1,T2}.
@@
   \label{eq:poissonRed}
-  \nabla^2\phi(\bm r)=-4\pi\sum_{\bm R}\delta(\bm r_\|-\bm
-  R)\delta(z)=-\frac{4\pi}{A}\sum_{\bm G}e^{i\bm G\cdot\bm r_\|}\delta(z),
+  \nabla^2\phi(\bm r)=-4\pi\sum_{\bm R}\delta^{(2)}(\bm r_\|-\bm
+  R)\delta^{(1)}(z)=-\frac{4\pi}{A}\sum_{\bm G}e^{i\bm G\cdot\bm r_\|}\delta^{(1)}(z),
 \end{equation}
 where $\bm r_\|$ is the projection of the observation position $\bm
-r=(x,y,z)$ onto the $xy$ plane,
-$\delta(\ldots)$ is Dirac's delta function, $\{\bm G\}$ is the
+r=(x,y,z)$ onto the $xy$ plane, $\{\bm G\}$ is the
 reciprocal lattice defined through $e^{i\bm G\cdot\bm R}=1$ for all
@@
  \frac{d^2}{dz^2}\phi_{\bm G}(z)-G^2\phi_G(z)=
-   -\frac{4 \pi}{A} \delta(z),
+   -\frac{4 \pi}{A} \delta^{(1)}(z),
  \end{eqnarray}
@@
  \begin{equation}\label{Eq:ECMR}
-   R=\left |\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}{1+r _ {_
-   {01}}r _ {_ {12}} e^{2i\delta}}\right |^2
+   R=\left |\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\psi}}{1+r _ {_
+   {01}}r _ {_ {12}} e^{2i\psi}}\right |^2
 \end{equation}
@@
 coefficients of the air/PS and PS/c-Si interfaces \cite{T10,T11}
-and $\delta=k_1^\perp d$, where $k_1^\perp$ is
+and $\psi=k_1^\perp d$, where $k_1^\perp$ is
 the component of the wavevector perpendicular to the surface within
@@
     \hline
-    0.2 & 0.06 & 0.7219\\
-    0.4 & 0.26 & 0.6723\\
-    0.6 & 0.46 & 0.5769\\
-    0.8 & 0.66 & 0.4645\\
-    1.0 & 0.86 & 0.3599\\
-    1.2 & 1.06 & 0.2749\\
-    1.4 & 1.26 & 0.2112\\
-    1.6 & 1.46 & 0.1666\\
+    0.2 & 0.06 & 0.722\\
+    0.4 & 0.26 & 0.672\\
+    0.6 & 0.46 & 0.577\\
+    0.8 & 0.66 & 0.464\\
+    1.0 & 0.86 & 0.360\\
+    1.2 & 1.06 & 0.275\\
+    1.4 & 1.26 & 0.211\\
+    1.6 & 1.46 & 0.167\\
   \end{tabular}
@@
   \caption{Reflectance spectra at different positions
-    on sample $G_1$ ($I_1=5\,\text{mA}$), where
-    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
+    ($x'_n=0.2-1.6\,\text{cm}$, $y=0.74\,\text{cm}$)
+    on sample $G_1$ ($I_1=5\,\text{mA}$). We show
   experimental results and results fitted through
@@
   \caption{Reflectance spectra at different positions
-    on sample $G_2$ (shown in Fig. \ref{fig:SI3}), where
-    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
+    ($x'_n=0.2-1.6\,\text{cm}$, $y=0.74\,\text{cm}$)
+    on sample $G_2$ ($I_1=10\,\text{mA}$). We show
   experimental results and results fitted through
@@
   \caption{Reflectance spectra at different positions
-    on sample $G_3$ (shown in Fig. \ref{fig:SI3}), where
-    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
+    ($x'_n=0.2-1.6\,\text{cm}$, $y=0.74\,\text{cm}$)
+    on sample $G_3$ ($I_3=20\,\text{mA}$) (Fig. \ref{fig:SI3}),
+    We show
     experimental results and results fitted through
@@
 Fig. \ref{fig:SI3} on our three samples $G_1$, $G_2$,
-and$G_3$, prepared using the same procedure
+and $G_3$, prepared using the same procedure
 (Sec. \ref{sec:fabrication-ps-grin}) but applying different currents
@@
 for calibration variations among spectra. From the thickness we
-obtained the etching rate $v=d/t$ at each position. Notice that the fit is reasonably
+obtained the etching rate $v=d/t$ at each position. Notice that the fits are reasonably
 good. The contrast of the reflectance in the experiment is somewhat smaller
@@
 different porosities and thicknesses, averaging out the interference
-maxima and minima. We also expect microscopic inhomogeneities such as
-interface roughness that might also reduce the contrast.
-This is most notable for the thicker regions
+maxima and minima. We expect microscopic inhomogeneities such as
+interface roughness might also reduce the contrast through scattering
+and its corresponding apparent dissipation \notaL{citar a Guille}.
+The loss of contrast is most notable for the thicker regions
 towards the left side of Fig. \ref{fig:SI3} and for smaller
@@
   Sample/ & position & density & porosity &
-  thickness & scale & etching rate\\
+  thickness & scale & rate\\
   $I$ (mA) &$x'_n$ (cm)&  $j$ ($\text{mA}/\text{cm}^2$) & $p$
@@
 \hline
-$G_1$/ 5 &0.2 & 3.609 & 0.4943 & 0.3402 & 0.8493&  1.3608 \\
-         &0.4 & 3.361 & 0.5713 & 0.3895 & 0.9789&  1.558  \\
-         &0.6  & 2.884 & 0.5657 & 0.3312 & 0.9569&  1.3248 \\
-         &0.8 & 2.322 & 0.5555 & 0.2732 & 0.9536&  1.0928 \\
-         &1.0 & 1.799 & 0.5592 & 0.2236 & 0.9951&  0.8944 \\
-         &1.2 & 1.374 & 0.5557 & 0.1886 & 0.9729&  0.7544 \\
-         &1.4 & 1.056 & 0.5491 & 0.1512 & 0.9606&  0.6048 \\
-         &1.6 & 0.833 & 0.5519 & 0.1238 & 0.9897&  0.4952 \\
-$G_2$/10&0.2 & 7.219 & 0.5910 & 0.6347 & 0.8559&  2.5388 \\
-         &0.4 & 6.723 & 0.6437 & 0.6934 & 0.9914&  2.7736 \\
-         &0.6 & 5.769 & 0.6383 & 0.5907 & 0.9523&  2.3628 \\
-         &0.8 & 4.645 & 0.6265 & 0.5327 & 0.9798&  2.1308 \\
-         &1.0 & 3.599 & 0.5991 & 0.4587 & 0.9389&  1.8348 \\
-         &1.2 & 2.749 & 0.5902 & 0.4044 & 0.9449&  1.6176 \\
-         &1.4 & 2.112 & 0.5753 & 0.3378 & 0.9361&  1.3512 \\
-         &1.6 & 1.666 & 0.5711 & 0.2958 & 0.9481&  1.1832 \\
-$G_3$/20 &0.2 & 14.438& 0.6860 & 1.2044 & 1.1491&  4.8176 \\
-          &0.4 & 13.44 & 0.7129 & 1.1931 & 1.0767&  4.7724 \\
-          &0.6 &11.538 & 0.7031 & 1.0443 & 1.0588&  4.1772 \\
-          &0.8 & 9.29  & 0.6258 & 0.7516 & 1.0063&  3.0064 \\
-          &1.0 & 7.198 & 0.6247 & 0.5380 & 1.0104&  2.152  \\
-          &1.2 & 5.498 & 0.5927 & 0.4387 & 0.9625&  1.7548 \\
-          &1.4 & 4.224 & 0.5844 & 0.3633 & 0.9625&  1.4532 \\
-          &1.6 & 3.332 & 0.5909 & 0.3392 & 1.0112&  1.3568 \\
+$G_1$/ 5 &0.2 & 3.61 & 0.494 & 0.340 & 0.849&  1.361 \\
+         &0.4 & 3.36 & 0.571 & 0.390 & 0.979&  1.558  \\
+         &0.6  & 2.88& 0.566 & 0.331 & 0.957&  1.325 \\
+         &0.8 & 2.32 & 0.556 & 0.273 & 0.954&  1.093 \\
+         &1.0 & 1.80 & 0.559 & 0.227 & 0.995&  0.894 \\
+         &1.2 & 1.37 & 0.556 & 0.189 & 0.973&  0.754 \\
+         &1.4 & 1.06 & 0.549 & 0.151 & 0.961&  0.605 \\
+         &1.6 & 0.83 & 0.552 & 0.124 & 0.990&  0.495 \\
+$G_2$/10 &0.2 & 7.22 & 0.591 & 0.635 & 0.856&  2.539 \\
+         &0.4 & 6.72 & 0.644 & 0.693 & 0.991&  2.774 \\
+         &0.6 & 5.77 & 0.638 & 0.591 & 0.952&  2.363 \\
+         &0.8 & 4.64 & 0.626 & 0.533 & 0.980&  2.131 \\
+         &1.0 & 3.60 & 0.599 & 0.459 & 0.939&  1.835 \\
+         &1.2 & 2.75 & 0.590 & 0.404 & 0.945&  1.618 \\
+         &1.4 & 2.11 & 0.575 & 0.338 & 0.936&  1.351 \\
+         &1.6 & 1.67 & 0.571 & 0.296 & 0.948&  1.183 \\
+$G_3$/20 &0.2 &14.45 & 0.686 & 1.204 & 1.149&  4.818 \\
+         &0.4 & 13.44 & 0.713 & 1.193 & 1.078&  4.772 \\
+         &0.6 & 11.54 & 0.703 & 1.044 & 1.059&  4.177 \\
+         &0.8 &  9.29 & 0.626 & 0.752 & 1.006&  3.006 \\
+         &1.0 &  7.20 & 0.625 & 0.538 & 1.010&  2.152  \\
+         &1.2 &  5.50 & 0.593 & 0.439 & 0.962&  1.755 \\
+         &1.4 &  4.22 & 0.584 & 0.363 & 0.962&  1.453 \\
+         &1.6 &  3.33 & 0.591 & 0.339 & 1.011&  1.357 \\
 \end{tabular}
@@
     thick lines. The arrows point to data that correspond to
-    position $x'_1=0.2\,\text{cm}$, joined to the other data by a thin
-    line (see text). We include linear fits to the data from
+    position $x'_1=0.2\,\text{cm}$, joined to the other data by thin
+    lines (see text). We include linear fits to the data from
     sample $G_3$ (thick straight line) and to that from all the
@@
 
-Using Eqs. \eqref{eq:p}, \eqref{eq:v}, \eqref{Eq:ECMR}, and
-\eqref{Eq:Brugg}, we can calculate the reflectance spectra for any
+Using Eqs.  \eqref{Eq:ECMR}-\eqref{eq:v} we can calculate the
+reflectance spectra for any
 desired current density $j_\perp$ and etching time. This is
@@
 The theoretical reflectance coudl as well be calculated using
-Eqs. \eqref{eq:p}, \eqref{eq:v}, \eqref{Eq:ECMR}, and
-\eqref{Eq:Brugg}, for more complicated structures, in which the
+\eqref{Eq:ECMR}-\eqref{eq:v} for more complicated structures, in which the
 current $I$ is modulated in time, allowing the design and analysis of

### 2020-09-18 paper.tex
Puse la cita al 1d rough de Guille

@@
 interface roughness might also reduce the contrast through scattering
-and its corresponding apparent dissipation \notaL{citar a Guille}.
+and its corresponding apparent dissipation \notaL{citar a:
+  Missoni, Leandro L., Guillermo P. Ortiz, María Luz Martínez Ricci,
+  Victor J. Toranzos, and W. Luis Mochán. 2020. “Rough 1D Photonic
+  Crystals: A Transfer Matrix Approach.” Optical Materials 109
+  (November): 110012. https://doi.org/10.1016/j.optmat.2020.110012.
+}.
 The loss of contrast is most notable for the thicker regions

### 2020-10-13 paper.tex

@@
 \notaL{Cambié el abstract, pero habrá que revisarlo después.}
-\notaL{Si quieres ponerme algún comentario en el manuscrito usa el
-  comando notaC, similar al comando notaL que uso yo}
+
+\notaV{Surfaces with gradient in refractive index has attracted attention due
+ ti its ability to unpair the relation between the shape of the optical 
+lens with its optical response. In spite of its possible usage in 
+different kinds of devices and applications, it still remains
+desirable to predesign GRIN structures with spacial predictability 
+of electrochemical gradients.  In this work we report}
+
 \section{Introduction}
 \label{sec:introduction}
-\notaL{Debiste poner etiquetas en todas las subsecciones y secciones, y
-  ecuaciones y figuras.}
-\notaL{No entiendo nada de la introducción}
-The structural properties of nanostructured materials  has  received a
-considerable attention,  and a large research effort has been devoted
-to them \cite{I1}. We found a great way to go for future
-technological  explorations,  countless  challenges and  that  open a
-range of possibilities to develop further  study  on these
-issues\cite{I2}. Porous silicon (PS) is a versatile nanostructured
-material and an excellent candidate as a technological platform for
-different sensing applications \cite{I3, I4}, due to its easy
-manufacturing,  large surface area, high surface reactivity,  and
-moreover, its optical transduction capacity.  Photonic crystals are
-multilayer dielectric structures that have periodicity in the
-dielectric function along one direction \cite{I5}. It has numerous
-studies for high reflectivity and the ability to adjust  the photonic
-prohibited  band (PBG)\cite{I6} , which leads to possible applications
-such as filters\cite{I7}, optical switches\cite{I8}, omnidirectional
-mirrors\cite{I9}, waveguides for PC \cite{I10} etc. In the
-conventional manufacturing of PS the desired result  is to obtain
-homogeneous samples (same structural characteristics) from the
-periphery  to the center  of the electrochemically  attacked area.
-However, with an asymmetric anodizing configuration,  samples with a
-lateral gradient in terms of pore size and thickness of the porous
-layer are obtained \cite{I101}. In this configuration,  the face of
-the platinum  electrode (cathode)  is relatively maintained
-perpendicular  to the surface of the Si substrate (anode) at one end
-of the cell, so that the distribution of the current within the
-electrolyte  solution varies depending on the distance  of the
-electrode due to the resistance of the electrolyte,  resulting  in a
-decrease in current density as the distance from the electrode
-increases \cite{I102, I103}. The result is a porous surface with
-different pore sizes ranging from a few nanometers  to pores on the
-order of a few micrometers  \cite{I104}. The dimensions of the pores
-obtained on the same chip can be controlled by adjusting the anodizing
-current and electrolyte concentration \cite{I11}. Currently, these
-types of samples have found their application relevant as optical band
-filters \cite{I12}, devices with a multidirectional photonic band
-(photonic bar codes) \cite{I13} and mainly as biosensors. In this way,
-the effect of different topographies (porosities in the same sample)
-on the culture / adhesion of certain cells \cite{I14} is studied,
-considerably reducing the number of samples and cost of the study. In
-addition, they are also very useful when a biomolecule size-exclusion
-technique is required allowing the identification and separation of
-these biological compounds \cite{I15}. Recent studies  have shown that
-the  combination  of thermal  oxidation  and infiltration of TiO2   by
-ALD offers the  opportunity to manufacture  a high index of refraction
-of contrast, visibly transparent GRIN \notaL{Define acrónimos antes de
-  usarlos}. optical elements from PS
-absorbent structures \cite{I16}. A Despite previous research on the
-formation of porous silicon with GRIN, type p in manufacturing and
-characterization, there was no control of current densities, much less
-a model that  explained said lateral  gradient. In this work, we
-reported a gradient refractive index (GRIN) structure by varying the
-current density on the fabrication of porous silicon photonic
-structure. This current density values, depth, and porosity of the
-photonic structure were calculated from an electrostatic model for
-photonic crystals with a gradient refractive index
-(EMPCGRIN). Moreover, the theoretical and experimental studies were
-exhibited similar results.
-
-The paper is organized as follows. In Section 2  we report the effect
-of how the current density can be calculated from an electrostatic
-model for photonic crystals with gradient refractive index (EMPCGRIN),
-demonstrating that there is a direct relation of the gradient
-generated by the electrode when it attacks the Silicon sample, we can
-see the depth of the structure and its porosity, in each of the
-measuring points. In Subsection 2.2 we present a formalism based on
-the methods used for the analysis of photonic crystal structures is
-the transfer matrix method. We use it to investigate the reflectance
-of light in a one-dimensional photonic crystal. In Section 3 we
-provide experimental  details about the manufacture of PS dielectric
-multilayers and Section 4 we shows the comparison of numerical and
-experimental results followed. Finally,  the conclusions given in
-Section. 5 \notaL{Checar que esto corresponda a lo que sigue del
-  artículo}
+\notaV{$
+Introduction
+
+Surfaces with gradient in the refractive index (GRIN) are of 
+importance not only due to the possibility of being able to 
+engineer/tune the propagation of light within the structure’s 
+surface for applications such as flat lenses, but also for several 
+interesting biological applications where the continual topographical 
+variation is being exploited [X]. As an example, roughness dependent 
+response of the cells has been tested on such materials for applications 
+in medical implants [Y].   Gradients have also been employed for several 
+technological applications such as high-yield screening of catalysts, 
+sensing materials and biomolecules [W. F. Maier, K. Stçwe, S. Sieg, Angew. 
+Chem. 2007, 119, 6122; Angew. Chem. Int. Ed. 2007, 46, 6016. ;  S. Jayaraman, 
+A. C. Hillier, J. Comb. Chem. 2004, 6, 27; S. Jayaraman, A. C. Hillier, Meas. 
+Sci. Technol. 2005, 16, 5. ; R. A. Potyrailo, V. M. Mirsky, Chem. Rev. 2008, 108, 770.]
+
+Apart from some methods developed by S.E. Fosdick et al [JACS  2010, 132, 9226-9227], 
+synthesis of  Ag-Au alloy gradients on steel and chemical composition gradients of CdS 
+on gold electrode have been made by Shannon’s group[].  Among the electrochemical methods, 
+compositional and doping density changes in the conducting polymer have been used to 
+produce the gradients using Indium tin oxide electrode [S. Inagi, Y. Ishiguro et al 
+Angew Chem Int. Ed. 2010, 49, 10136-10139; Angew Chem 2010 122, 10334-10337].   
+Electrochemically induced potential gradients have been shown to catalyze the 
+reactions and gradient doping of the polymers [Gradient Doping of Conducting Polymer 
+Films by Means of Bipolar Electrochemistry Y. Ishiguro, S. Inagi, and T.Fuchigami 
+Langmuir 2011 27 (11), 7158-7162].   (PENDING : few MORE EXAMPLES from last couple of years)
+As compared to the above mentioned techniques, a relatively economical, 
+fast and easy approach with an additional advantage of being compatible 
+with VLSI devices & integrable with microelectronics, for the fabrication 
+of refractive index (pore size) gradient has been the development of asymmetric 
+electrode configuration in the electrochemical synthesis of porous silicon [].  
+Although porous silicon initially stimulated the interest of the scientific 
+community due to visible PL at room temperature, presently it has 
+been accepted as a multifaceted optical material due to its large surface 
+area, biocompatibility, ease of fabrication and tunable refractive index. 
+Porous silicon emanating applications now cover various fields such as 
+chemical and biosensor [Porous Silicon Fabry–Pérot Interferometer for
+N-Acetyl-β-d-Glucosaminidase Biomarker Monitoring  D. Nanda Kumar, 
+Nofar Pinker, and Giorgi Shtenberg  ACS Sensors 2020 5 (7), 1969-1976; DOI: 
+10.1021/acssensors.0c00348], microelectronics and MEMS[xx], as well as a 
+range of optical[XXX] and optoelectronic applications[XXX].  Specifically, 
+the temporal variation of current density results in the variation of 
+porosity along the depth for the easy fabrication of different kinds 
+[xxX] of 1D photonics crystals. 
+Although the conventional fabrication of PS requires laterally 
+homogeneous samples (with same structural characteristics on the 
+porous surface), asymmetric configuration to produce porous silicon 
+with a lateral gradient (in terms of optical thickness/ pore size and t
+hickness of the porous layer) has also been exploited for different applications 
+[REF… ]. In this configuration, a small platinum electrode (cathode)  
+is positioned perpendicular  to the surface of the Si substrate (anode) 
+at one end or the center  of the cell, resulting  in a decrease in current 
+density  with an increase in the distance from the electrode \cite{I102, I103}. 
+The resulting porous surface can have pore sizes ranging from a few nanometers  
+to  few micrometers  \cite{I104}. The range of the dimensions of the pores and 
+the corresponding  thickness obtained on the same chip can be controlled by 
+adjusting the location of the pin/circular electrode,  anodizing current density
+and etching time period for a given silicon wafer.   Sailor Group 
+in 2002 \cite{I101} applied it for the determination of protein size. 
+Additionally, due to the biocompatible nature of PS, possible gating of 
+the optical response by variation in pH of the solution was shown to 
+trap/release the biomolecule for possible drug delivery applications. 
+ Similar asymmetric electrode configuration was used to fabricate 
+ optical filters (multilayered structures) with lateral gradient 
+ [Li, Yang Yang, Peter Kim, and Michael J. Sailor. 
+ "Painting a rainbow on silicon–a simple method to 
+ generate a porous silicon band filter gradient.
+ " physica status solidi (a) 202.8 (2005): 1616-1618.] for 
+ developing ethanol sensor (Sailor 2012...). Additionally it 
+ has been shown that the combination of thermal  oxidation  and 
+ infiltration of TiO2  by ALD offers the  opportunity to manufacture 
+a high refractive indices contrast in visibly transparent GRIN 
+optical elements from PS \cite{I16}.    Kruger et al showed 
+the ...  [ Krueger, Neil A., et al. "Porous silicon gradient 
+refractive index micro-optics." Nano letters 16.12 (2016): 7402-7407.] 
+In addition the same group ...[Krueger, Neil A., et al. 
+ "Electrochemical Fabrication of Flat, Polymer‐Embedded 
+Porous Silicon 1D Gradient Refractive Index Microlens 
+Arrays." physica status solidi (a) 215.13 (2018): 1800088].  
+Recently, J Wang et al. has shown the fabrication of 
+miniature spectrometer with PS based rugate filter using 
+radial interfacial potential distribution (Wang, Joanna, 
+Michael J. Sailor, and Byoung‐Yong Chang. "Fabrication of a lateral 
+gradient rugate in porous silicon for a miniature spectrometer
+application." ChemElectroChem 6.24 (2019): 5967-5972. On the other 
+hand, the effect of different topographical features present on the 
+same chip, has also been used to culture / adhesion of certain cells \cite{I14}
+In the investigation of such practically applicable systems, 
+the spacial predictability of electrochemical gradients can 
+be useful for predesigning the devices for different applications.  
+In this work, we report a simple analytical model to quantitatively 
+analyze the gradient (calculate the porosity /current density and 
+thickness) at any point of the GRIN structure.  The paper is organized 
+as follows. In Section 2  we report a simple analytical model to calculate 
+the current density/porosity and thickness  at any point of the GRIN structure. 
+The model contemplates (Dr. Mochan) the formation of electrochemically generated 
+porous surface  (applicable/extendible to photonic crystals with lateral gradient) 
+with lateral gradient in refractive index  ...with predictable  depth and porosity 
+at any point on surface.   In Section 3 we provide experimental details for the 
+synthesis of porous silicon samples with lateral refractive index gradient.  
+Section 4 includes experimental results and its comparison with numerically 
+evaluated parameters . Finally,  the conclusions are given in Section X
+
+$}
+
+\notaV{$ Painting a rainbow on silicon - A simple method to 
+\notaV{generate a porous silicon 
+band filter gradient. / Li, Yang Yang; Kim, Peter; Sailor, Michael J.
+In: Physica Status Solidi (A) Applications and Materials Science, 
+Vol. 202, No. 8, 06.2005, p. 1616-1618.  (https://doi.org/10.1002/pssa.200461200)
+
+Electrochemical Preparation of Pore Wall Modification Gradients 
+across Thin Porous Silicon Layers
+Corrina M. Thompson, Michel Nieuwoudt, Anne M. Ruminski, 
+Michael J. Sailor, and Gordon M. Miskelly
+Langmuir 2010 26 (10), 7598-7603
+DOI: 10.1021/la904408h
+
+ Richardson, Kathleen A., et al. "Advances in infrared gradient 
+ refractive index (GRIN) materials: a review." Optical Engineering 59.11 (2020): 112602.
+
+Lavanant, Enora, et al. "Radial gradient refractive index 
+(GRIN) infrared lens based on spatially resolved crystallization 
+of chalcogenide glass." Optical Materials Express 10.4 (2020): 860-867.
+While widely used in the visible, radial gradient refractive 
+index (GRIN) lenses are still elusive in the IR waveband. 
+In this paper we introduce a new method based on spatially
+resolved crystallization of chalcogenide glass to produce such lenses. 
+Optical and structural
+
+Yoon, Sun Mi, et al. "Subwavelength Hollow-Nanopillared Glass 
+with Gradient Refractive Index for Ultralow Diffuse Reflectance 
+and Antifogging." ACS applied materials & interfaces 12.5 (2020): 6234-6242.
+Nanostructured glass with subwavelength hollow nanopillars 
+of diameters of sub-65 nm was fabricated, showing high optical 
+transmittance and ultralow diffuse reflectance. A simple
+process involving single-step plasma etching was used on a 
+glass slide coated with a SiO2...
+
+Perez, Julius C., Tahmid H. Talukdar, and Judson D. Ryckman. 
+"Patterning Refractive Index on the Surface of a Chip by Direct 
+Nanoimprinting." CLEO: QELS_Fundamental Science. Optical Society of America, 2020.
+
+Szymanowski, Hieronim, et al. "Thin SiNC/SiOC Coatings with a 
+Gradient of Refractive Index Deposited from Organosilicon Precursor." Coatings 10.8 (2020): 794.
+
+Perez, Julius C., Tahmid H. Talukdar, and Judson D. Ryckman.
+ "Patterning Refractive Index on the Surface of a Chip by Direct 
+ Nanoimprinting." CLEO: QELS_Fundamental Science. Optical Society of America, 2020.
+
+$
+}
 

### 2020-10-22 paper.tex
Coloque las bibliografias en un bib y coloque las modificaciones de la Dra

@@
 %\usepackage{showkeys}
+%\usepackage{ieeetr}
 \usepackage{bm}
@@
 built.
-
+\notaV{ABSTRACT :  Surfaces with the gradient in the refractive index 
+have attracted attention due to their ability to unpair the relation
+ between the shape of the optical lens with its optical response. 
+  For enhancing the versatility  of electrochemical gradients and its possible usage in
+different kinds of devices and applications, it is
+desirable to predesign GRIN structures with spatial 
+predictability of porosity and the corresponding etching rate.  
+In this work, we propose a simple model for the calculation of the current
+density as a function of position within an electrochemical cell used
+to produce porous silicon structures with a controlled gradient in their
+index of refraction. The characterization of some typical PS samples with 
+lateral porosity and thickness gradient (produced using pin Pt electrode) 
+with scanning electron microscopy and
+ultraviolet-visible-near infrared reflectance spectroscopy was 
+found to be in conformity with the properties predicted through 
+the proposed model. In addition,
+as the results allow us to obtain the complete dependence of
+porosity, dielectric function and the corresponding etching rate for each 
+current density from some measurements performed on a single or 
+a couple of samples, the proposed model can facilitate the designing 
+of novel sensing devices based on surfaces with lateral gradient in refractive indices.}
 Keywords: Porous Silicon; GRIN; Reflectance Spectra.
@@
 
-\notaV{Surfaces with gradient in refractive index has attracted attention due
- ti its ability to unpair the relation between the shape of the optical 
-lens with its optical response. In spite of its possible usage in 
-different kinds of devices and applications, it still remains
-desirable to predesign GRIN structures with spacial predictability 
-of electrochemical gradients.  In this work we report}
-
 \section{Introduction}
 \label{sec:introduction}
-\notaV{$
+\notaV{
 Introduction
@@
 interesting biological applications where the continual topographical 
-variation is being exploited [X]. As an example, roughness dependent 
-response of the cells has been tested on such materials for applications 
-in medical implants [Y].   Gradients have also been employed for several 
+variation is being exploited \cite{pierscionek2012gradient}. As an example, 
+roughness dependent  response of the cells has been tested on such 
+materials for applications in medical implants \cite{bai2020bioinspired}.  
+ Gradients have also been employed for several 
 technological applications such as high-yield screening of catalysts, 
-sensing materials and biomolecules [W. F. Maier, K. Stçwe, S. Sieg, Angew. 
-Chem. 2007, 119, 6122; Angew. Chem. Int. Ed. 2007, 46, 6016. ;  S. Jayaraman, 
-A. C. Hillier, J. Comb. Chem. 2004, 6, 27; S. Jayaraman, A. C. Hillier, Meas. 
-Sci. Technol. 2005, 16, 5. ; R. A. Potyrailo, V. M. Mirsky, Chem. Rev. 2008, 108, 770.]
-
-Apart from some methods developed by S.E. Fosdick et al [JACS  2010, 132, 9226-9227], 
+sensing materials and biomolecules \cite{maier2007combinatorial, jayaraman2004construction, 
+potyrailo2008combinatorial}
+%[W. F. Maier, K. Stçwe, S. Sieg, Angew. 
+%Chem. 2007, 119, 6122; Angew. Chem. Int. Ed. 2007, 46, 6016. ;  S. Jayaraman, 
+%A. C. Hillier, J. Comb. Chem. 2004, 6, 27; S. Jayaraman, A. C. Hillier, Meas. 
+%Sci. Technol. 2005, 16, 5. ; R. A. Potyrailo, V. M. Mirsky, Chem. Rev. 2008, 108, 770.]
+%%
+Apart from some methods developed by S.E. Fosdick et al \cite{fosdick2010two},
+%[JACS  2010, 132, 9226-9227], 
 synthesis of  Ag-Au alloy gradients on steel and chemical composition gradients of CdS 
-on gold electrode have been made by Shannon’s group[].  Among the electrochemical methods, 
-compositional and doping density changes in the conducting polymer have been used to 
-produce the gradients using Indium tin oxide electrode [S. Inagi, Y. Ishiguro et al 
-Angew Chem Int. Ed. 2010, 49, 10136-10139; Angew Chem 2010 122, 10334-10337].   
+on gold electrode have been made by Shannon’s group\cite{wang2019fabrication}.  
+Among the electrochemical methods, compositional and doping density changes 
+in the conducting polymer have been used to produce the gradients using Indium tin 
+oxide electrode \cite{inagi2010bipolar}
+%[S. Inagi, Y. Ishiguro et al Angew Chem Int. Ed. 2010, 49, 10136-10139;
+%Angew Chem 2010 122, 10334-10337].   
 Electrochemically induced potential gradients have been shown to catalyze the 
-reactions and gradient doping of the polymers [Gradient Doping of Conducting Polymer 
-Films by Means of Bipolar Electrochemistry Y. Ishiguro, S. Inagi, and T.Fuchigami 
-Langmuir 2011 27 (11), 7158-7162].   (PENDING : few MORE EXAMPLES from last couple of years)
+reactions and gradient doping of the polymers \cite{qin2020bipolar, ishiguro2011gradient}
+%[Gradient Doping of Conducting Polymer 
+%Films by Means of Bipolar Electrochemistry Y. Ishiguro, S. Inagi, and T.Fuchigami 
+%Langmuir 2011 27 (11), 7158-7162].   (PENDING : few MORE EXAMPLES from last couple of years)
 As compared to the above mentioned techniques, a relatively economical, 
 fast and easy approach with an additional advantage of being compatible 
-with VLSI devices & integrable with microelectronics, for the fabrication 
+with VLSI devices and integrable with microelectronics, for the fabrication 
 of refractive index (pore size) gradient has been the development of asymmetric 
-electrode configuration in the electrochemical synthesis of porous silicon [].  
+electrode configuration in the electrochemical synthesis of porous silicon \cite{sailor2012porous}.  
 Although porous silicon initially stimulated the interest of the scientific 
@@
 Porous silicon emanating applications now cover various fields such as 
-chemical and biosensor [Porous Silicon Fabry–Pérot Interferometer for
-N-Acetyl-β-d-Glucosaminidase Biomarker Monitoring  D. Nanda Kumar, 
-Nofar Pinker, and Giorgi Shtenberg  ACS Sensors 2020 5 (7), 1969-1976; DOI: 
-10.1021/acssensors.0c00348], microelectronics and MEMS[xx], as well as a 
-range of optical[XXX] and optoelectronic applications[XXX].  Specifically, 
+chemical and biosensor \cite{kumar2020porous},
+%[Porous Silicon Fabry–Pérot Interferometer for
+%N-Acetyl-β-d-Glucosaminidase Biomarker Monitoring  D. Nanda Kumar, 
+%Nofar Pinker, and Giorgi Shtenberg  ACS Sensors 2020 5 (7), 1969-1976; DOI: 
+%10.1021/acssensors.0c00348], 
+microelectronics and MEMS \cite{martinez2016dual},as well as a 
+range of optical \cite{estevez2014porous} and optoelectronic applications
+\cite{ramadan2020fabrication}. Specifically, 
 the temporal variation of current density results in the variation of 
 porosity along the depth for the easy fabrication of different kinds 
-[xxX] of 1D photonics crystals. 
+\cite{perez2018reflectivity} of 1D photonics crystals. 
 Although the conventional fabrication of PS requires laterally 
@@
 porous surface), asymmetric configuration to produce porous silicon 
-with a lateral gradient (in terms of optical thickness/ pore size and t
-hickness of the porous layer) has also been exploited for different applications 
-[REF… ]. In this configuration, a small platinum electrode (cathode)  
+with a lateral gradient (in terms of optical thickness/ pore size and thickness 
+of the porous layer) has also been exploited for different applications 
+\cite{collins2002determining}. In this configuration, a small platinum electrode (cathode)  
 is positioned perpendicular  to the surface of the Si substrate (anode) 
 at one end or the center  of the cell, resulting  in a decrease in current 
-density  with an increase in the distance from the electrode \cite{I102, I103}. 
+density  with an increase in the distance from the electrode
+ \cite{khung2008using, clements2011mesenchymal}. 
 The resulting porous surface can have pore sizes ranging from a few nanometers  
-to  few micrometers  \cite{I104}. The range of the dimensions of the pores and 
+to  few micrometers  \cite{wang2015screening}. The range of the dimensions of the pores and 
 the corresponding  thickness obtained on the same chip can be controlled by 
@@
 and etching time period for a given silicon wafer.   Sailor Group 
-in 2002 \cite{I101} applied it for the determination of protein size. 
+in 2002 \cite{collins2002determining, sailor2012porous} applied it 
+for the determination of protein size. 
 Additionally, due to the biocompatible nature of PS, possible gating of 
@@
  Similar asymmetric electrode configuration was used to fabricate 
- optical filters (multilayered structures) with lateral gradient 
- [Li, Yang Yang, Peter Kim, and Michael J. Sailor. 
- "Painting a rainbow on silicon–a simple method to 
- generate a porous silicon band filter gradient.
- " physica status solidi (a) 202.8 (2005): 1616-1618.] for 
- developing ethanol sensor (Sailor 2012...). Additionally it 
- has been shown that the combination of thermal  oxidation  and 
+ optical filters (multilayered structures) with lateral gradient \cite{li2005painting}
+% [Li, Yang Yang, Peter Kim, and Michael J. Sailor. 
+% "Painting a rainbow on silicon–a simple method to 
+% generate a porous silicon band filter gradient.
+% " physica status solidi (a) 202.8 (2005): 1616-1618.] 
+for developing ethanol sensor (Sailor 2012)\cite{sailor2012porous}. 
+ Additionally it has been shown that the combination of thermal  oxidation  and 
  infiltration of TiO2  by ALD offers the  opportunity to manufacture 
 a high refractive indices contrast in visibly transparent GRIN 
-optical elements from PS \cite{I16}.    Kruger et al showed 
-the ...  [ Krueger, Neil A., et al. "Porous silicon gradient 
-refractive index micro-optics." Nano letters 16.12 (2016): 7402-7407.] 
-In addition the same group ...[Krueger, Neil A., et al. 
- "Electrochemical Fabrication of Flat, Polymer‐Embedded 
-Porous Silicon 1D Gradient Refractive Index Microlens 
-Arrays." physica status solidi (a) 215.13 (2018): 1800088].  
+optical elements from PS \cite{ocier2017tunable}.    
+Kruger et al showed the \cite{krueger2016porous}
+%the ...  [ Krueger, Neil A., et al. "Porous silicon gradient 
+%refractive index micro-optics." Nano letters 16.12 (2016): 7402-7407.] 
+In addition the same group \cite{krueger2018electrochemical}
+%[Krueger, Neil A., et al. 
+% "Electrochemical Fabrication of Flat, Polymer‐Embedded 
+%Porous Silicon 1D Gradient Refractive Index Microlens 
+%Arrays." physica status solidi (a) 215.13 (2018): 1800088].  
 Recently, J Wang et al. has shown the fabrication of 
 miniature spectrometer with PS based rugate filter using 
-radial interfacial potential distribution (Wang, Joanna, 
-Michael J. Sailor, and Byoung‐Yong Chang. "Fabrication of a lateral 
-gradient rugate in porous silicon for a miniature spectrometer
-application." ChemElectroChem 6.24 (2019): 5967-5972. On the other 
-hand, the effect of different topographical features present on the 
-same chip, has also been used to culture / adhesion of certain cells \cite{I14}
+radial interfacial potential distribution \cite{wang2019fabrication}
+%(Wang, Joanna, 
+%Michael J. Sailor, and Byoung‐Yong Chang. "Fabrication of a lateral 
+%gradient rugate in porous silicon for a miniature spectrometer
+%application." ChemElectroChem 6.24 (2019): 5967-5972.
+On the other hand, the effect of different topographical
+features present on the same chip, has also been 
+used to culture / adhesion of certain cells \cite{khung2008using}
 In the investigation of such practically applicable systems, 
@@
 Section 4 includes experimental results and its comparison with numerically 
-evaluated parameters . Finally,  the conclusions are given in Section X
-
-$}
-
-\notaV{$ Painting a rainbow on silicon - A simple method to 
-\notaV{generate a porous silicon 
-band filter gradient. / Li, Yang Yang; Kim, Peter; Sailor, Michael J.
-In: Physica Status Solidi (A) Applications and Materials Science, 
-Vol. 202, No. 8, 06.2005, p. 1616-1618.  (https://doi.org/10.1002/pssa.200461200)
-
-Electrochemical Preparation of Pore Wall Modification Gradients 
-across Thin Porous Silicon Layers
-Corrina M. Thompson, Michel Nieuwoudt, Anne M. Ruminski, 
-Michael J. Sailor, and Gordon M. Miskelly
-Langmuir 2010 26 (10), 7598-7603
-DOI: 10.1021/la904408h
-
- Richardson, Kathleen A., et al. "Advances in infrared gradient 
- refractive index (GRIN) materials: a review." Optical Engineering 59.11 (2020): 112602.
-
-Lavanant, Enora, et al. "Radial gradient refractive index 
-(GRIN) infrared lens based on spatially resolved crystallization 
-of chalcogenide glass." Optical Materials Express 10.4 (2020): 860-867.
-While widely used in the visible, radial gradient refractive 
-index (GRIN) lenses are still elusive in the IR waveband. 
-In this paper we introduce a new method based on spatially
-resolved crystallization of chalcogenide glass to produce such lenses. 
-Optical and structural
-
-Yoon, Sun Mi, et al. "Subwavelength Hollow-Nanopillared Glass 
-with Gradient Refractive Index for Ultralow Diffuse Reflectance 
-and Antifogging." ACS applied materials & interfaces 12.5 (2020): 6234-6242.
-Nanostructured glass with subwavelength hollow nanopillars 
-of diameters of sub-65 nm was fabricated, showing high optical 
-transmittance and ultralow diffuse reflectance. A simple
-process involving single-step plasma etching was used on a 
-glass slide coated with a SiO2...
-
-Perez, Julius C., Tahmid H. Talukdar, and Judson D. Ryckman. 
-"Patterning Refractive Index on the Surface of a Chip by Direct 
-Nanoimprinting." CLEO: QELS_Fundamental Science. Optical Society of America, 2020.
-
-Szymanowski, Hieronim, et al. "Thin SiNC/SiOC Coatings with a 
-Gradient of Refractive Index Deposited from Organosilicon Precursor." Coatings 10.8 (2020): 794.
-
-Perez, Julius C., Tahmid H. Talukdar, and Judson D. Ryckman.
- "Patterning Refractive Index on the Surface of a Chip by Direct 
- Nanoimprinting." CLEO: QELS_Fundamental Science. Optical Society of America, 2020.
-
-$
+evaluated parameters. Finally,  the conclusions are given in Section 5
+%$ 
+%
 }
+
+%\notaV{ $Painting a rainbow on silicon - A simple method to  generate a porous silicon 
+%band filter gradient. / Li, Yang Yang; Kim, Peter; Sailor, Michael J.
+%In: Physica Status Solidi (A) Applications and Materials Science, 
+%Vol. 202, No. 8, 06.2005, p. 1616-1618.  (https://doi.org/10.1002/pssa.200461200)
+%
+%Electrochemical Preparation of Pore Wall Modification Gradients 
+%across Thin Porous Silicon Layers
+%Corrina M. Thompson, Michel Nieuwoudt, Anne M. Ruminski, 
+%Michael J. Sailor, and Gordon M. Miskelly
+%Langmuir 2010 26 (10), 7598-7603
+%DOI: 10.1021/la904408h
+%
+% Richardson, Kathleen A., et al. "Advances in infrared gradient 
+% refractive index (GRIN) materials: a review." Optical Engineering 59.11 (2020): 112602.
+% 
+%
+%Lavanant, Enora, et al. "Radial gradient refractive index 
+%(GRIN) infrared lens based on spatially resolved crystallization 
+%of chalcogenide glass." Optical Materials Express 10.4 (2020): 860-867.
+%While widely used in the visible, radial gradient refractive 
+%index (GRIN) lenses are still elusive in the IR waveband. 
+%In this paper we introduce a new method based on spatially
+%resolved crystallization of chalcogenide glass to produce such lenses. 
+%Optical and structural
+%
+%Yoon, Sun Mi, et al. "Subwavelength Hollow-Nanopillared Glass 
+%with Gradient Refractive Index for Ultralow Diffuse Reflectance 
+%and Antifogging." ACS applied materials & interfaces 12.5 (2020): 6234-6242.
+%Nanostructured glass with subwavelength hollow nanopillars 
+%of diameters of sub-65 nm was fabricated, showing high optical 
+%transmittance and ultralow diffuse reflectance. A simple
+%process involving single-step plasma etching was used on a 
+%glass slide coated with a SiO2...
+%
+%Perez, Julius C., Tahmid H. Talukdar, and Judson D. Ryckman. 
+%"Patterning Refractive Index on the Surface of a Chip by Direct 
+%Nanoimprinting." CLEO: QELS_Fundamental Science. Optical Society of America, 2020.
+%
+%Szymanowski, Hieronim, et al. "Thin SiNC/SiOC Coatings with a 
+%Gradient of Refractive Index Deposited from Organosilicon Precursor." Coatings 10.8 (2020): 794.
+%  
+%Perez, Julius C., Tahmid H. Talukdar, and Judson D. Ryckman.
+% "Patterning Refractive Index on the Surface of a Chip by Direct 
+% Nanoimprinting." CLEO: QELS_Fundamental Science. Optical Society of America, 2020.
+% $
+%}
 
@@
   \centering
-  \includegraphics[width=\textwidth]{celdan1}
+  \includegraphics[width=\textwidth]{celdan1.png}
   \caption{Prism shaped electrolytic cell with a rectangular base of
@@
 Here, $\delta^{(D)}$ is Dirac's delta function in $D$ dimensions.
-This problem may be solved readily using image charge theory \cite{T1,T2}.
+This problem may be solved readily using image charge theory \cite{jackson1999classical}.
 The potential within the electrolytic cell coincides
@@
 convergence properties. The potential can be obtained
-using the Ewald summation technique \cite{T3,T4,T5}, which yields
+using the Ewald summation technique \cite{brodka2004ewald}, which yields
 two rapidly converging series, one in real space and another one in reciprocal space.
@@
 simple periodic lattice of charges using a fast convergent sum over the 2D
-reciprocal vectors, then sum over the charges that form the basis
+reciprocal vectors \cite{kratzer2019basics}, then sum over the charges that form the basis
 of the 2D {\em crystal} plane, and finally sum over all the
- planes \cite{T6,T7}.\notaL{¿Estas referencias son relevantes? ¿En verdad
+ planes \notaC{cite{T6,T7}, esta citas las quite porque no puedo contestar esa pregunta de 
+ abajo}.\notaL{¿Estas referencias son relevantes? ¿En verdad
  se define en ellas la suma de Ewald por planos? Dime dónde p.f., en qué
@@
 rectangular prism on the bottom of which we place a Si wafer which makes
-electrical contact to a gold plate \notaL{Lo inventé; de qué material es
+electrical contact to a brass \notaC{ laton. gold plate} 
+\notaL{Lo inventé; de qué material es
   el contacto bajo la muestra?} which together make the anode. The
@@
 conditions. The process was performed at
-room temperature,\notaL{OJO. No controlaste la temperatura} with an
+\notaC{room temperature, no controle latempertaura}
+,\notaL{OJO. No controlaste la temperatura} with an
 electrolytic mixture of aqueous hydrofluoric
@@
 ethanol (purity 99.9\% wt) in a 3:7:1 volume ratio. \notaL{Checa que
-  todo esto sí corresponda a tus últimas muestras} After the
-anodizing process, the samples were rinsed with
+  todo esto sí corresponda a tus últimas muestras} \notaC{SI corresponde}
+   After the anodizing process, the samples were rinsed with
 ethanol (purity: 99.9 $ \% $  wt). The electrolytic cell had the shape
@@
   usó? Si sí, ¿hay algo internesante que decir sobre el? Cosas como el
-tamaño de mancha, resolución espectral, etc.} For interpretation of the
-data layer we used
-the standard formula \cite{T8,T9} for the reflectance of three media:
+tamaño de mancha, resolución espectral, etc.} \notaC{Data collection absoluto
+reflectance mode. Spot size, physical setting, width (0.7mm) and length (2.0mm).
+Instrument setting, slit width (0.6mm). Method settings 
+wavelength from(1400nm) to(300nm)}
+
+ For interpretation of the data layer we used
+the standard formula \cite{stenzel2015physics} for the reflectance of three media:
 air (0) environment, the PS film (1) and the c-Si substrate (2),
@@
 where $r_{01}$ and $r_{12}$ are the Fresnel reflectance
-coefficients of the air/PS and PS/c-Si interfaces \cite{T10,T11}
+coefficients of the air/PS and PS/c-Si interfaces \cite{sattler2017silicon}
 and $\psi=k_1^\perp d$, where $k_1^\perp$ is
@@
 layer, which we relate to the porosity through Bruggeman's
-effective medium theory \cite{I20},
+effective medium theory \cite{theiss1997optical},
 \begin{equation}\label{Eq:Brugg}
@@
 than in our fitted curves. We believe this is due to the finite width
-\notaL{beams width=?} of the illuminating beam of our
+\notaL{beams width=?} \notaC{beams width width (0.7mm) and length (2.0mm)}
+of the illuminating beam of our
 spectrometer. Thus, as our GRIN sample is not macroscopically homogeneous and its
@@
 interface roughness might also reduce the contrast through scattering
-and its corresponding apparent dissipation \notaL{citar a:
+and its corresponding apparent dissipation \cite{missoni2020rough}
+\notaL{citar a:
   Missoni, Leandro L., Guillermo P. Ortiz, María Luz Martínez Ricci,
@@
 
+\notaV{By choosing a simple geometry for our electrochemical cell, namely, a
+rectangular prism, and employing a point-like electrode, we were able
+to derive a simple expression for the calculation of the electric current
+density along the surface of a Si sample. The expression was obtained
+by using image charge theory and a plane-wise summation of Coulomb
+potentials in reciprocal space, and it is made up of
+a rapidly converging sum of analytical terms. This allowed us to
+characterize the porosity of a PS layer and the etching
+rate for different values of the etching current density by making
+optical experiments on just a
+few samples. We illustrated the procedure with two samples each of which we
+measured at three different positions. These calibration curves are
+very useful as the etching rate for the formation of porous silicon
+and the resulting porosity is very sensitive to the growth conditions
+and to the properties of the substrate, such as its doping. Thus,
+there are no universal calibration curves. Having obtained these calibration curves
+and being able to compute the current density at different positions
+allows the prediction of the properties of GRIN structures. We
+illustrated this by desigining a PS GRIN microcavity tuned at one
+position to a given wavelength. (Q. for Dr. Mochan : Do we intend 
+to illustrate the design?) We found a good agreement between its
+measured reflectance spectra at different points with the spectra
+calculated from the values of the expected local current
+density using the calibration curves. We also found good agreement
+between the measured and the expected geometry of the system. These
+results show that the use of a simple electrolytic cell and our
+computational procedure does allow the accurate prediction of the
+optical properties of GRIN structures, and thus we believe it will
+prove helpful for the design fabrication and characterization of novel}
+
 \section*{Acknowledgments}
@@
   agradecimientos de Vivechna (quizás incluyendo al icf)}
-% \backmatter
-%\nocite{*}
-%\bibliographystyle{plain}
-%\bibliography{bibliografía.bib} %Aquí ponen el nombre del archivo .bib
+\nocite{*}
 \notaL{Manda toda la bibliografía a un archivo .bib}
@@
   cada uno de los artículos citados}
+% \bibliography{bibligrin} %Bibliographie
+%\printbibliography
+%\bibliographystyle{plain}
+%\bibliography{bibligrin.bib}
+%\medskip
+%
+
 \bibliographystyle{unsrt}
-\begin{thebibliography}{XX}
-  % forma de biblio es MLA
-\bibitem{I1} P. Yeh,\textquotedblleft \emph{Optical Waves in Layered
-    Media} \textquotedblright, 2nd edn. (Wiley-Interscience
-  Publication,
-  USA, 2005).
-\bibitem{I2}Canham, L. 1997.\textquotedblleft \emph{Properties of
-    Porous Silicon} \textquotedblright. Edited by Canham L. DERA,
-  Malvern, UK.
-\bibitem{I3}{Beale, M.I.J, J.D Benjamin, M.J Uren, N.G Chew, and A.G
-    Cullis. 1985. \emph{ \textquotedblleft An Experimental and
-      Theoretical Study of the Formation and Microstructure of
-      Porous Silicon.\textquotedblright} J. Crystal Growth 73:
-    622?36. doi:10.1021/jp0706984. }
-\bibitem{I4}Canham, L. T. 1990. \emph{\textquotedblleft Silicon
-    Quantum Wire Array Fabrication by Electrochemical and Chemical
-    Dissolution of Wafers.\textquotedblright} Applied Physics
-  Letters 57 (10): 1046. doi:10.1063/1.103561.
-\bibitem{I5} J. D. Joannopoulos et al.,\textquotedblleft
-  \emph{Photonic Crystals: Molding the Flow of
-    Light}\textquotedblright, 2nd edn.
-  (Princeton University Press, UK, 2008).
-\bibitem{I6} E. Yablonovitch, \textquotedblleft \emph{Photonic
-    band-gap structures,}\textquotedblright J. Opt. Soc. Am. B 10,
-  283-295 (1993)
-\bibitem{I7} Ilyas, S., and M. Gal.  \textquotedblleft \emph{
-    Optical devices from porous silicon having continuously varying
-    refractive index.}\textquotedblright Journal of Materials
-  Science: Materials in Electronics 18.1 (2007): 61-64.
-\bibitem{I8} Tran, P. \textquotedblleft \emph{Optical switching with
-    a nonlinear photonic crystal: a numerical
-    study.}\textquotedblright Optics letters 21.15 (1996):
-  1138-1140.
-\bibitem{I9} Ariza-Flores, A. David, L. M. Gaggero-Sager, and
-  V. Agarwal. \textquotedblleft \emph{White metal-like
-    omnidirectional mirror from porous silicon dielectric
-    multilayers.}\textquotedblright Applied Physics Letters 101.3
-  (2012): 031119.
-\bibitem{I10} Johnson, Steven G., et al.  \textquotedblleft
-  \emph{Linear waveguides in photonic-crystal
-    slabs.}\textquotedblright Physical Review B 62.12 (2000): 8212.
-
-  % asimetrica
-\bibitem{I101}Collins, Boyce E., et al. \textquotedblleft \emph{
-    Determining protein size using an electrochemically machined
-    pore gradient in silicon.}\textquotedblright Advanced Functional
-  Materials 12.3 (2002): 187-191.
-
-\bibitem{I102} Khung, Y. L., G. Barritt, and
-  N. H. Voelcker. \textquotedblleft \emph{Using continuous porous
-    silicon gradients to study the influence of surface topography
-    on the behaviour of neuroblastoma cells.}\textquotedblright
-  Experimental cell research 314.4 (2008): 789-800.
-
-\bibitem{I103} Clements, Lauren R., et al. \textquotedblleft
-  \emph{Mesenchymal stem cell attachment to peptide density
-    gradients on porous silicon generated by
-    electrografting.}\textquotedblright physica status solidi (a)
-  208.6 (2011): 1440-1445.
-
-\bibitem{I104} Wang, Peng-Yuan, et al. \textquotedblleft
-  \emph{Screening the attachment and spreading of bone
-    marrow-derived and adipose-derived mesenchymal stem cells on
-    porous silicon gradients.}\textquotedblright Rsc Advances 2.33
-  (2012): 12857-12865.
-\bibitem{I11} Canham, L. \textquotedblleft \emph{Properties of
-    Porous Silicon.}\textquotedblright Edited by Canham L. DERA,
-  Malvern, UK. (1997).
-\bibitem{I12} Li, Yang Yang, Peter Kim, and Michael J
-  Sailor.\textquotedblleft \emph{Painting a Rainbow on Silicon A
-    Simple Method to Generate a Porous Silicon Band Filter
-    Gradient}\textquotedblright Physica Status Solidi (a) 1618 (8):
-  161618. doi:10.1002/pssa.200461200.(2005)
-\bibitem{I13} Khung, Y L, and N H
-  Voelcker. 2009.\textquotedblleft\emph{ Multidirectional Lateral
-    Gradient Films with Position-Dependent Photonic Signatures Made
-    from Porous Silicon.}\textquotedblright Optical Materials 32
-  (1): 23442. doi:10.1016/j.optmat.2009.07.015.
-\bibitem{I14}  Khung, Y L, G Barritt, and N H Voelcker.
-  \textquotedblleft \emph{Using Continuous Porous Silicon Gradients
-    to Study the Influence of Surface Topography on the Behaviour of
-    Neuroblastoma Cells.}\textquotedblright Experimental Cell
-  Research 314 (4): 78900. doi:10.1016/j.yexcr.2007.10.015.(2008.)
-\bibitem{I15} Collins, B.E., K.-P.S. Dancil, G. Abbi, and
-  M.J. Sailor. 2002.\textquotedblleft \emph{Determining Protein Size
-    Using an Electrochemically Machined Pore Gradient in
-    Silicon.}\textquotedblright Advanced Functional Materials 12 (3):
-  187. doi:10.1002/1616-3028(200203)12:3,187::AID-ADFM187,3.0.CO;2-E.(
-  2002.)
-
-\bibitem{I16} Ocier, C. R., Krueger, N. A., Zhou, W. and  Braun,
-  P. V. (2017).\textquotedblleft \emph{Tunable visibly transparent
-    optics derived from porous silicon.}\textquotedblright ACS
-  Photonics, 4(4), 909-914.
-
-  \bibitem{T1}Jackson, John David. \textquotedblleft
-  \emph{Classical electrodynamics.}\textquotedblright (1999): 841-842.
-
-\bibitem{T2}Griffiths, David J. \textquotedblleft
-\emph{Introduction to electrodynamics.}\textquotedblright
- New Jersey: Prentice Hall, 1962.
-
- \bibitem{T3} Mahfoud Belhadj, Howard E. Alper, and Ronald M. Levy. \textquotedblleft
- \emph{ Molecular dynamics simulations of water with Ewald summation
- 	for the long range electrostatic interactions.}\textquotedblright Chemical
-  Physics Letters, 179(1-2):13–20, 1991.
-   \bibitem{T4}A. Bródka.\textquotedblleft
-   \emph{ Ewald summation method with electrostatic layer correction for
-  interactions of point dipoles in slab geometry.}\textquotedblright Chemical
-Physics Letters, 400(1):62–67, December 2004.
- \bibitem{T5} A. Grzybowski, E. Gwóźdź, and A. Bródka.\textquotedblleft
- \emph{ Ewald summation of electrostatic interactions in molecular dynamics
- 	 of a three-dimensional system with periodicity in two directions.}\textquotedblright
-  Physical Review B, 61(10):6706–6712, March 2000.
-
- \bibitem{T6} Kratzer, Peter, and Jörg Neugebauer. \textquotedblleft \emph{The basics of
- 	electronic structure theory for periodic systems.}\textquotedblright
-  Frontiers in chemistry 7 (2019).
- \bibitem{T7} Charles Kittel. \textquotedblleft \emph{Introduction to Solid State
- 	 Physics.}\textquotedblright Wiley, Hoboken, NJ, 8 edition, 2005.
-
- \bibitem{T8}Born, Max, and Emil Wolf. \textquotedblleft \emph{Basic properties of
-   	the electromagnetic field.}\textquotedblright Principles of optics 44 (1980).
-  \bibitem{T9} Stenzel, Olaf. \textquotedblleft \emph{ The physics of thin film
-  	optical spectra.}\textquotedblright Springer, 2015.
-
-  \bibitem{T10}Born, Max, and Emil Wolf.\textquotedblleft \emph{ Principles of optics:
-  	electromagnetic theory of propagation, interference
-  	 and diffraction of light.}\textquotedblright Elsevier, 2013.
-  \bibitem{T11} Sattler, Klaus D., ed. \textquotedblleft \emph{ Silicon Nanomaterials
-  	Sourcebook: Low-Dimensional Structures, Quantum Dots, and Nanowires }\textquotedblright,
-   Volume One. CRC Press, 2017.
-
-\bibitem{I17} Dariani RS, Ebrahimnasab S (2014). \textquotedblleft
-  \emph{Root Mean Square Roughness of Nano Porous Silicon by
-    Scattering Spectra.}\textquotedblright The
-  European Physical Journal Plus 129: 129.
-\bibitem{I18} Lerondel G, Romestain R (1997).\textquotedblleft
-  \emph{Roughness of the Porous Silicon Dissolution
-    Interface.}\textquotedblright Journal of Applied Physics 81:
-  61716178.
-\bibitem{I19} Lérondel G, Romestain R, Barret S
-  (1997).\textquotedblleft \emph{Quantitative Analysis of the Light
-    Scattering Effect on Porous Silicon
-    Optical Measurements.}\textquotedblright Thin Solid Films 297:
-  114?117.
-
-\bibitem{I20} Thei, W. \textquotedblleft \emph{Optical Properties of porous silicon.}
-\textquotedblright Surf. Sci. Rep. 1997, 29, 91?93.
-\bibitem{I21} Van Groesen, E.; Sopaheluwakan, A.; Andonowati,
-  A. \textquotedblleft  \emph{Direct characterization of states and
-    modes in defect grating structures.}\textquotedblright
-  J. Nonlinear Opt. Phys. Mater. 2004, 13, 155173.
-
-\bibitem{In} Mazzoleni, C., and L. Pavesi. \textquotedblleft
-  \emph{Application to optical components of dielectric porous silicon
-    multilayers.}\textquotedblright Applied Physics Letters 67.20
-  (1995): 2983-2985
-
-\end{thebibliography}
+%
+\bibliography{bibligrin} %Aquí ponen el nombre del archivo .bib
 

### 2020-10-26 Programas/GrinJI.pl
ya

@@ -91,8 +91,12 @@ $gw->plot({
     xrange=>[0,$a], yrange=>[0,$b],
     #view=>['equal','xy'], #parece no funcionar
     #size=>['ratio',-1],
-    size=>'1,.5',
-    origin=>[0,.5],
+    #mochan
+    #size=>'1,.5',
+    #origin=>[0,.5],
+    #cris
+    #size=>'1,.5',
+    #origin=>[0,.5],
     justify=>1,
     label=>[1, "(a)", at=>"screen .8,.95", textcolor=>'"white"'],
     xlabel=>["x(cm)"] ,ylabel=>["y (cm)"], cblabel=>["j_⟂/I(1/cm²)"]
@@ -177,4 +181,4 @@ BEGIN {
     };
 }
 
-#perl GrinJIN.pl --a=2.03 --b=0.62 --C=1 --X0=0.1 --Y0=0.31 --Z0=0.9 --Z=0 --I=5 --N=100
+#perl GrinJI.pl --a=2.03 --b=1.48 --C=1 --X0=0.2 --Y0=0.74 --Z0=0.9 --Z=0 --I=5 --N=100

### 2020-10-26 paper.tex

@@
 \title{\textbf{Optimization of Porous Silicon Gradient Refractive
-    Index Structures.} }
+    Index Structures. \notaV{Index Structures (NOTE: WE NEED TO CHANGE THE NAME;  
+    Probably "Analytical model for  porous silicon structures with 1D gradient refractive index"}} }
 \author[1]{C. A. Ospina de la Cruz}
@@
 built.
-\notaV{ABSTRACT :  Surfaces with the gradient in the refractive index 
-have attracted attention due to their ability to unpair the relation
- between the shape of the optical lens with its optical response. 
-  For enhancing the versatility  of electrochemical gradients and its possible usage in
+\notaV{Surfaces with  the gradient in the refractive index have 
+attracted attention due to their capacity to unpair the relation 
+between the shape of the optical 
+lens with its optical response.  For enhancing the versatility  of 
+electrochemical gradients and its possible usage in 
 different kinds of devices and applications, it is
-desirable to predesign GRIN structures with spatial 
-predictability of porosity and the corresponding etching rate.  
-In this work, we propose a simple model for the calculation of the current
+desirable to predesign GRIN structures with spatial predictability of 
+porosity and the corresponding etching rate.  In this work, we propose a 
+simple model for the calculation of the current
 density as a function of position within an electrochemical cell used
@@
 lateral porosity and thickness gradient (produced using pin Pt electrode) 
-with scanning electron microscopy and
-ultraviolet-visible-near infrared reflectance spectroscopy was 
-found to be in conformity with the properties predicted through 
-the proposed model. In addition,
-as the results allow us to obtain the complete dependence of
-porosity, dielectric function and the corresponding etching rate for each 
-current density from some measurements performed on a single or 
-a couple of samples, the proposed model can facilitate the designing 
-of novel sensing devices based on surfaces with lateral gradient in refractive indices.}
+with scanning electron microscopy andultraviolet-visible-near infrared 
+reflectance spectroscopy was found to be in conformity with the properties 
+predicted through the proposed model. In addition, 
+as the results allow us to obtain the complete dependence of porosity,
+dielectric function and the corresponding etching rate for each current
+density from some measurements performed on a single or a couple of samples,
+the proposed model can facilitate the designing of novel sensing devices 
+based on surfaces with lateral gradient in refractive indices.}
 Keywords: Porous Silicon; GRIN; Reflectance Spectra.
@@
 
-Surfaces with gradient in the refractive index (GRIN) are of 
+Gradient in the refractive index (GRIN) of a material is of 
 importance not only due to the possibility of being able to 
-engineer/tune the propagation of light within the structure’s 
-surface for applications such as flat lenses, but also for several 
+engineer/tune the propagation of light within the structure for 
+applications such as flat lenses, but also for several 
 interesting biological applications where the continual topographical 
@@
 optical elements from PS \cite{ocier2017tunable}.    
-Kruger et al showed the \cite{krueger2016porous}
+Krueger et al. \cite{krueger2018electrochemical} in 2018 used porous 
+silicon 1D GRIN structure 
+infiltrated with polymer to synthesize flat microns arrays. 
 %the ...  [ Krueger, Neil A., et al. "Porous silicon gradient 
 %refractive index micro-optics." Nano letters 16.12 (2016): 7402-7407.]
-In addition the same group \cite{krueger2018electrochemical}
+
 %[Krueger, Neil A., et al. 

### 2020-10-28 paper.tex
Remove extra space
Start correcting manuscript. Title.

--- 2020-10-22 paper.tex
@@
 
-\title{\textbf{Optimization of Porous Silicon Gradient Refractive
-    Index Structures.} }
+\title{Model for Porous Silicon Structures with a Lateral Gradient}
 \author[1]{C. A. Ospina de la Cruz}
-\author[2]{W. L. Mochán }
-\author[3]{V. Agarwal }
+\author[2]{V. Agarwal}
+\author[3]{W. L. Mochán}
 
@@
   62209, México}
-\affil[2]{Instituto de Ciencias F\'isica ,Universidad Nacional
+\affil[2]{Centro de Investigaci\'on en Ingenier\'ia y Ciencias
+  Aplicadas,Universidad del Estado de Morelos, Av. Universidad 1001
+  Col. Chamilpa, Cuernavaca, Morelos 62209, Mexico  }
+\affil[3]{Instituto de Ciencias F\'isica ,Universidad Nacional
   Autonoma de Mexico, Av. Universidad S/N, Col. Chamilpa, 62210
   Cuernavaca, Morelos, Mexico}
-\affil[3]{Centro de Investigaci\'on en Ingenier\'ia y Ciencias
-  Aplicadas,Universidad del Estado de Morelos, Av. Universidad 1001
-  Col. Chamilpa, Cuernavaca, Morelos 62209, Mexico  }
 \begin{document}
@@
 \maketitle
-
+\notaV{Index Structures (NOTE: WE NEED TO CHANGE THE NAME;
+  Probably "Analytical model for  porous silicon structures with 1D
+  gradient refractive index)}
+\notaL{The calculation is 2D, seems 1D due to the narrow geometry chosen.}
 \begin{abstract}

### 2020-10-29 paper.tex
Check Vivechna suggegstions

--- 2020-10-26 paper.tex
@@
 
-\title{\textbf{Optimization of Porous Silicon Gradient Refractive
-    Index Structures. \notaV{Index Structures (NOTE: WE NEED TO CHANGE THE NAME;  
-    Probably "Analytical model for  porous silicon structures with 1D gradient refractive index"}} }
+\title{Model for Porous Silicon Structures with a Lateral Gradient}
 \author[1]{C. A. Ospina de la Cruz}
-\author[2]{W. L. Mochán }
-\author[3]{V. Agarwal }
+\author[2]{V. Agarwal}
+\author[3]{W. L. Mochán}
 
@@
 \maketitle
-
+\notaV{Index Structures (NOTE: WE NEED TO CHANGE THE NAME;
+  Probably "Analytical model for  porous silicon structures with 1D
+  gradient refractive index)}
+\notaL{The calculation is 2D, seems 1D due to the narrow geometry chosen.}
 \begin{abstract}
-We propose a simple setup which that the calculation of the current
+  We propose a simple setup with which that the calculation of the current
 density as a function of position within an electrochemical cell used
@@
 built.
-\notaV{Surfaces with  the gradient in the refractive index have 
-attracted attention due to their capacity to unpair the relation 
-between the shape of the optical 
-lens with its optical response.  For enhancing the versatility  of 
-electrochemical gradients and its possible usage in 
+\notaV{ABSTRACT :  Surfaces with the gradient in the refractive index
+have attracted attention due to their ability to unpair the relation
+ between the shape of the optical lens with its optical response.
+  For enhancing the versatility  of electrochemical gradients and its possible usage in
 different kinds of devices and applications, it is
-desirable to predesign GRIN structures with spatial predictability of 
-porosity and the corresponding etching rate.  In this work, we propose a 
-simple model for the calculation of the current
+desirable to predesign GRIN structures with spatial
+predictability of porosity and the corresponding etching rate.
+In this work, we propose a simple model for the calculation of the current
 density as a function of position within an electrochemical cell used
@@
 lateral porosity and thickness gradient (produced using pin Pt electrode)
-with scanning electron microscopy andultraviolet-visible-near infrared 
-reflectance spectroscopy was found to be in conformity with the properties 
-predicted through the proposed model. In addition, 
-as the results allow us to obtain the complete dependence of porosity,
-dielectric function and the corresponding etching rate for each current
-density from some measurements performed on a single or a couple of samples,
-the proposed model can facilitate the designing of novel sensing devices 
-based on surfaces with lateral gradient in refractive indices.}
+with scanning electron microscopy and
+ultraviolet-visible-near infrared reflectance spectroscopy was
+found to be in conformity with the properties predicted through
+the proposed model. In addition,
+as the results allow us to obtain the complete dependence of
+porosity, dielectric function and the corresponding etching rate for each
+current density from some measurements performed on a single or
+a couple of samples, the proposed model can facilitate the designing
+of novel sensing devices based on surfaces with lateral gradient in refractive indices.}
 Keywords: Porous Silicon; GRIN; Reflectance Spectra.
@@
 
-Gradient in the refractive index (GRIN) of a material is of 
+Surfaces with gradient in the refractive index (GRIN) are of
 importance not only due to the possibility of being able to
-engineer/tune the propagation of light within the structure for 
-applications such as flat lenses, but also for several 
+engineer/tune the propagation of light within the structure’s
+surface for applications such as flat lenses, but also for several
 interesting biological applications where the continual topographical
@@
 electrode configuration in the electrochemical synthesis of porous silicon \cite{sailor2012porous}.
+
 Although porous silicon initially stimulated the interest of the scientific
@@
 optical elements from PS \cite{ocier2017tunable}.
-Krueger et al. \cite{krueger2018electrochemical} in 2018 used porous 
-silicon 1D GRIN structure 
-infiltrated with polymer to synthesize flat microns arrays. 
+Kruger et al showed the \cite{krueger2016porous}
 %the ...  [ Krueger, Neil A., et al. "Porous silicon gradient
 %refractive index micro-optics." Nano letters 16.12 (2016): 7402-7407.]
+In addition the same group \cite{krueger2018electrochemical} used porous silicon 1D GRIN structure infiltrated with polymer to synthesize flat microns arrays.
 
@@
 the current density, as well as the etching rate and the thickness of the
-porous layer. Nevertheless, it is not a simple task to measure the
+porous layer. Nevertheless, it is challeging to measure the
 {\em local} value of $\bm j(\bm r)$ along the surface. This hampers the
@@
 unit cell. Putting everything together, the problem is that of solving
-Poisson's equation within an orthothombic lattice of size
+Poisson's equation within an orthorhombic lattice of size
 $2a\times2b\times4c$ with a basis of 16 point charges of charge $\pm
@@
 rectangular prism on the bottom of which we place a Si wafer which makes
-electrical contact to a brass \notaC{ laton. gold plate} 
+electrical contact to a brass \notaC{ laton. gold plate}\notaL{Porqué
+  vivechna dice silver/copper?}
 \notaL{Lo inventé; de qué material es
@@
 
-\subsection{Fabrication of GRIN  PS Single Layers}
+\subsection{Fabrication of PS  GRIN Single Layers}
 \label{sec:fabrication-ps-grin}
-We manufactured single layer PS structures through electrochemical
-anodization of a (100) $p$-type crystalline Si wafer
+Single layer PS structures were fabricated through electrochemical
+anodization of (100) oriented $p$-type crystalline Si wafer
 (resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
@@
 $c=1\,\text{cm}$. The cathode was a
-platinum wire that with a diameter of $0.41\,\text{mm}$ insulated by a
-teflon cylinder of external diameter $\,2\text{mm}$, with an uncovered
+platinum wire that with a diameter of $0.41\,\text{mm}$ insulated with
+teflon tape \notaL{Según Vivechna esto es falso: by a
+teflon cylinder of external diameter $\,2\text{mm}$}, with an uncovered
 tip located at $\bm r_0=(x_0,

### 2020-10-29 paper.tex
Revise abstract

@@
 \begin{abstract}
-  We propose a simple setup with which that the calculation of the current
-density as a function of position within an electrochemical cell used
-to produce porous Silicon structures with a controlled gradient in their
-index of refraction. We produced samples under several conditions and
-characterized them with scanning electron microscopy, and
-ultraviolet-visible-near infrared reflectance spectroscopy. Our
-results allow us to obtain from experiments on a single or just a few
-samples a full characterization of the dependence of porosity,
-dielectric function and speed of attack on the current density and on
-position, so that novel nonhomogeneous devices may be designed and
-built.
-\notaV{ABSTRACT :  Surfaces with the gradient in the refractive index
-have attracted attention due to their ability to unpair the relation
- between the shape of the optical lens with its optical response.
-  For enhancing the versatility  of electrochemical gradients and its possible usage in
-different kinds of devices and applications, it is
-desirable to predesign GRIN structures with spatial
-predictability of porosity and the corresponding etching rate.
-In this work, we propose a simple model for the calculation of the current
-density as a function of position within an electrochemical cell used
-to produce porous silicon structures with a controlled gradient in their
-index of refraction. The characterization of some typical PS samples with
-lateral porosity and thickness gradient (produced using pin Pt electrode)
-with scanning electron microscopy and
-ultraviolet-visible-near infrared reflectance spectroscopy was
-found to be in conformity with the properties predicted through
-the proposed model. In addition,
-as the results allow us to obtain the complete dependence of
-porosity, dielectric function and the corresponding etching rate for each
-current density from some measurements performed on a single or
-a couple of samples, the proposed model can facilitate the designing
-of novel sensing devices based on surfaces with lateral gradient in refractive indices.}
+
+Layered systems with a lateral gradient in their refractive indices
+and thicknesses may be employed for the development of a variety of
+optical devices and
+applications. They may be fabricated of porous silicon (PS) through a
+position dependent electrochemical process. Thus, the possibility of
+predicting the local current density $j$ and the co rresponding
+porosity $p$
+and etching rate $v$ would be desirable for a systematic design of these
+structures. In this work, we propose a
+simple model for the calculation of $j$
+as a function of position within an electrochemical cell. We prepared
+some graded single layer PS samples, measured their optical properties with
+ultraviolet-visible-near infrared reflectance
+spectroscopy, \notaL{Should we mention microscopy?}, and related them
+to their local porosity and thickness which, together with our model, were then used to obtain
+the $p$ vs. $j$ and $v$ vs. $j$ calibration curves. We corroborated
+our model by comparing the calibration curves for different samples. Thus, from
+measurements on only one, or a few simple systems, we may obtain full
+calibration curves which may be used to predict, design, and fabricate
+more complex novel nonhomogenous devices with lateral gradients which can be used
+for manifold applications.
+
 Keywords: Porous Silicon; GRIN; Reflectance Spectra.
 \end{abstract}
-\notaL{Cambié el abstract, pero habrá que revisarlo después.}
 
@@
 \label{sec:introduction}
-\notaV{
-Introduction
-
 Surfaces with gradient in the refractive index (GRIN) are of
@@
 %
-}
 

### 2020-10-30 paper.tex
Revise abstract

@@
 
-Layered systems with a lateral gradient in their refractive indices
-and thicknesses may be employed for the development of a variety of
-optical devices and
-applications. They may be fabricated of porous silicon (PS) through a
-position dependent electrochemical process. Thus, the possibility of
-predicting the local current density $j$ and the co rresponding
-porosity $p$
-and etching rate $v$ would be desirable for a systematic design of these
+A variety of optical devices and applications may be based on layered
+systems which have a lateral gradient in both their refractive indices
+and their thicknesses. They may be fabricated of porous silicon (PS) through an
+electrochemical process in which the etching current depends on position. Thus, the possibility of
+predicting the local current density $j$ and the corresponding
+porosity $p$ and etching rate $v$ would be desirable for a systematic design of these
 structures. In this work, we propose a
@@
 as a function of position within an electrochemical cell. We prepared
-some graded single layer PS samples, measured their optical properties with
+some graded single layer PS samples, measured their optical properties through
 ultraviolet-visible-near infrared reflectance

### 2020-10-30 paper.tex
revise start of introduction

@@
 \label{sec:introduction}
-Surfaces with gradient in the refractive index (GRIN) are of
-importance not only due to the possibility of being able to
-engineer/tune the propagation of light within the structure’s
-surface for applications such as flat lenses, but also for several
-interesting biological applications where the continual topographical
-variation is being exploited \cite{pierscionek2012gradient}. As an example,
-roughness dependent  response of the cells has been tested on such
-materials for applications in medical implants \cite{bai2020bioinspired}.
+Surfaces with a gradient in the refractive index (GRIN) are of
+importance as they allow the engineering and tuning of the optical
+phase along their surface, yielding applications such as flat
+lenses. Furtheremore, there are important biological applications
+which combine topographical features with index of refraction
+gradients \cite{pierscionek2012gradient}. Preparation of structures
+with gradients in other properties have also shown their
+usefulness. \notaL{I believe the examples below are unrelated to GRIN,
+  thats why I added this remark.} As an example, the
+roughness dependent  response of cells has been tested on
+materials used applications in medical implants
+\cite{bai2020bioinspired}.
 Gradients have also been employed for several
@@
 potyrailo2008combinatorial}
-%[W. F. Maier, K. Stçwe, S. Sieg, Angew.
-%Chem. 2007, 119, 6122; Angew. Chem. Int. Ed. 2007, 46, 6016. ;  S. Jayaraman,
-%A. C. Hillier, J. Comb. Chem. 2004, 6, 27; S. Jayaraman, A. C. Hillier, Meas.
-%Sci. Technol. 2005, 16, 5. ; R. A. Potyrailo, V. M. Mirsky, Chem. Rev. 2008, 108, 770.]
-%%
 Apart from some methods developed by S.E. Fosdick et al \cite{fosdick2010two},
 %[JACS  2010, 132, 9226-9227],
-synthesis of  Ag-Au alloy gradients on steel and chemical composition gradients of CdS
-on gold electrode have been made by Shannon’s group\cite{wang2019fabrication}.
-Among the electrochemical methods, compositional and doping density changes
-in the conducting polymer have been used to produce the gradients using Indium tin
-oxide electrode \cite{inagi2010bipolar}
-%[S. Inagi, Y. Ishiguro et al Angew Chem Int. Ed. 2010, 49, 10136-10139;
-%Angew Chem 2010 122, 10334-10337].
+synthesis of  Ag-Au alloy gradients on steel and chemical composition
+gradients of CdS layers
+on gold electrodes have been obtained made by Shannon’s
+group\cite{wang2019fabrication}. \notaL{Is this Shannon a big shot, or
+  why should we name him?}
+Among electrochemical methods, compositional and doping density changes
+in  conducting polymers have been used to produce gradients using Indium Tin
+Oxide electrodes \cite{inagi2010bipolar}
 Electrochemically induced potential gradients have been shown to catalyze the
-reactions and gradient doping of the polymers \cite{qin2020bipolar, ishiguro2011gradient}
-%[Gradient Doping of Conducting Polymer
-%Films by Means of Bipolar Electrochemistry Y. Ishiguro, S. Inagi, and T.Fuchigami
-%Langmuir 2011 27 (11), 7158-7162].   (PENDING : few MORE EXAMPLES from last couple of years)
+reactions and gradient doping of polymers \cite{qin2020bipolar, ishiguro2011gradient}.
 As compared to the above mentioned techniques, a relatively economical,
-fast and easy approach with an additional advantage of being compatible
-with VLSI devices and integrable with microelectronics, for the fabrication
-of refractive index (pore size) gradient has been the development of asymmetric
-electrode configuration in the electrochemical synthesis of porous silicon \cite{sailor2012porous}.
+fast and easy approach for the fabrication
+of gradient materials has been the use  of asymmetrical
+electrode configurations in the electrochemical synthesis of porous silicon \cite{sailor2012porous}.
+This technique has the additional advantage of being compatible
+with VLSI devices and integrable with microelectronics.
 

### 2020-10-30 paper.tex
Review introduction to the end

@@
 usefulness. \notaL{I believe the examples below are unrelated to GRIN,
-  thats why I added this remark.} As an example, the
+  thats why I added the previous remark.} As an example, the
 roughness dependent  response of cells has been tested on
@@
 
-Although porous silicon initially stimulated the interest of the scientific
-community due to visible PL at room temperature, presently it has
-been accepted as a multifaceted optical material due to its large surface
+Although porous silicon (PS) initially stimulated the interest of the scientific
+community due to its photoluminiscence in the visible range at room
+temperature, it has presently
+been recognized as a multifaceted optical material due to its large surface
 area, biocompatibility, ease of fabrication and tunable refractive index.
-Porous silicon emanating applications now cover various fields such as
-chemical and biosensor \cite{kumar2020porous},
-%[Porous Silicon Fabry–Pérot Interferometer for
-%N-Acetyl-β-d-Glucosaminidase Biomarker Monitoring  D. Nanda Kumar,
-%Nofar Pinker, and Giorgi Shtenberg  ACS Sensors 2020 5 (7), 1969-1976; DOI:
-%10.1021/acssensors.0c00348],
+Applications based on porous silicon now cover various fields such as
+chemical sensors and biosensors \cite{kumar2020porous},
 microelectronics and MEMS \cite{martinez2016dual},as well as a
@@
 \cite{ramadan2020fabrication}. Specifically,
-the temporal variation of current density results in the variation of
-porosity along the depth for the easy fabrication of different kinds
-\cite{perez2018reflectivity} of 1D photonics crystals.
-Although the conventional fabrication of PS requires laterally
-homogeneous samples (with same structural characteristics on the
-porous surface), asymmetric configuration to produce porous silicon
-with a lateral gradient (in terms of optical thickness/ pore size and thickness
-of the porous layer) has also been exploited for different applications
-\cite{collins2002determining}. In this configuration, a small platinum electrode (cathode)
-is positioned perpendicular  to the surface of the Si substrate (anode)
-at one end or the center  of the cell, resulting  in a decrease in current
-density  with an increase in the distance from the electrode
+the temporal variation of the current density results in a variation of
+porosity along the depth, allowing the easy fabrication of different kinds
+\cite{perez2018reflectivity} of 1D photonics crystals and other
+structures. \notaL{Photonic crystals only in the periodic case.}
+Although the conventional fabrication of PS yields laterally
+homogeneous samples, with invariant structural and optical properties
+along the surface, an asymmetric configuration \notaL{Is it clear what
+  is asymmetric?} may produce porous
+Silicon structures with a lateral gradient in properties such as
+thickness, pore size and density, and thus, refractive index and
+optical thickness. In this configuration, a small platinum electrode (cathode)
+is positioned perpendicular  to the surface of a Si substrate (anode)
+near one end \notaL{ At the center wouldn't be asymmetric: or the
+  center} of the cell, resulting  in a current
+density  which decreases as the distance to the electrode increases
  \cite{khung2008using, clements2011mesenchymal}.
@@
 to  few micrometers  \cite{wang2015screening}. The range of the dimensions of the pores and
-the corresponding  thickness obtained on the same chip can be controlled by
-adjusting the location of the pin/circular electrode,  anodizing current density
-and etching time period for a given silicon wafer.   Sailor Group
-in 2002 \cite{collins2002determining, sailor2012porous} applied it
+the corresponding  thickness range on the same chip can be controlled by
+adjusting the location of the electrode, the  anodizing current
+and the etching time. Different
+applications have been found for the resulting structures
+\cite{collins2002determining}. For example, Sailor's group
+\cite{collins2002determining, sailor2012porous} applied it
 for the determination of protein size.
-Additionally, due to the biocompatible nature of PS, possible gating of
-the optical response by variation in pH of the solution was shown to
-trap/release the biomolecule for possible drug delivery applications.
- Similar asymmetric electrode configuration was used to fabricate
- optical filters (multilayered structures) with lateral gradient \cite{li2005painting}
-% [Li, Yang Yang, Peter Kim, and Michael J. Sailor.
-% "Painting a rainbow on silicon–a simple method to
-% generate a porous silicon band filter gradient.
-% " physica status solidi (a) 202.8 (2005): 1616-1618.]
-for developing ethanol sensor (Sailor 2012)\cite{sailor2012porous}.
+Additionally, gating of
+the optical response through a variation in pH of the solution was shown to
+trap/release biomolecules for possible drug delivery
+applications, given the biocompatible nature of PS, . \notaL{How is this related to the gradient?}
+A similar asymmetric electrode configuration was used to fabricate
+multilayered optical filters with lateral a gradient
+\cite{li2005painting} and
+for developing ethanol sensors \cite{sailor2012porous}.
 Additionally it has been shown that the combination of thermal  oxidation  and
- infiltration of TiO2  by ALD offers the  opportunity to manufacture
-a high refractive indices contrast in visibly transparent GRIN
-optical elements from PS \cite{ocier2017tunable}.
-Kruger et al showed the \cite{krueger2016porous}
-%the ...  [ Krueger, Neil A., et al. "Porous silicon gradient
-%refractive index micro-optics." Nano letters 16.12 (2016): 7402-7407.]
-In addition the same group \cite{krueger2018electrochemical} used porous silicon 1D GRIN structure infiltrated with polymer to synthesize flat microns arrays.
-
-%[Krueger, Neil A., et al.
-% "Electrochemical Fabrication of Flat, Polymer‐Embedded
-%Porous Silicon 1D Gradient Refractive Index Microlens
-%Arrays." physica status solidi (a) 215.13 (2018): 1800088].
+infiltration of TiO2  by ALD \notaL{What is this acronym?} allows the manufacture
+of transparent GRIN
+optical elements with a high refractive index contrast \cite{ocier2017tunable}.
+Kruger et al. showed the \cite{krueger2016porous} \notaL{What did
+  Kruger show?}
+Furthermore, the same group \cite{krueger2018electrochemical} used
+a porous silicon 1D GRIN structure infiltrated with polymer to
+synthesize flat microlens arrays.
 Recently, J Wang et al. has shown the fabrication of
-miniature spectrometer with PS based rugate filter using
+a miniature spectrometer with PS based rugate filter using a
 radial interfacial potential distribution \cite{wang2019fabrication}
-%(Wang, Joanna,
-%Michael J. Sailor, and Byoung‐Yong Chang. "Fabrication of a lateral
-%gradient rugate in porous silicon for a miniature spectrometer
-%application." ChemElectroChem 6.24 (2019): 5967-5972.
 On the other hand, the effect of different topographical
 features present on the same chip, has also been
-used to culture / adhesion of certain cells \cite{khung2008using}
-In the investigation of such practically applicable systems,
-the spacial predictability of electrochemical gradients can
-be useful for predesigning the devices for different applications.
+used to study the dependence of the adhesion of certain cells on the
+surface topography \cite{khung2008using}.
+
+For applications such as those mentioned above,
+it would be very useful to be able to predict beforehand the spatially dependent
+properties of the resulting structures. This would allow the design
+and optimization of the desired devices.
 In this work, we report a simple analytical model to quantitatively
-analyze the gradient (calculate the porosity /current density and
-thickness) at any point of the GRIN structure.  The paper is organized
-as follows. In Section 2  we report a simple analytical model to calculate
-the current density/porosity and thickness  at any point of the GRIN structure.
-The model contemplates (Dr. Mochan) the formation of electrochemically generated
-porous surface  (applicable/extendible to photonic crystals with lateral gradient)
-with lateral gradient in refractive index  ...with predictable  depth and porosity
-at any point on surface.   In Section 3 we provide experimental details for the
+analyze the spatial dependence of the current density during the
+electrochemical on Si to produce PS structures. A calibration
+procedure may then relate the current density to the porosity and the
+etching rate. Thus, for a given etching current acting over a given
+time, we may predict the position dependence of the index of
+refraction and optical thickness of the resulting inhomogeneous
+layer, thus allowing the prediction of the optical properties of
+multilayered GRIN structure. The structure of the paper is the
+following.
+\notaL{Check when finished}. In Section \ref{sec:theory} we develop a
+simple analytical model to calculate
+the current density at any point over the GRIN structure under preparaton.
+In Section \ref{sec:procedures} we provide experimental details for the
 synthesis of porous silicon samples with lateral refractive index gradient.
-Section 4 includes experimental results and its comparison with numerically
-evaluated parameters. Finally,  the conclusions are given in Section 5
-%$
-%
-
-%\notaV{ $Painting a rainbow on silicon - A simple method to  generate a porous silicon
-%band filter gradient. / Li, Yang Yang; Kim, Peter; Sailor, Michael J.
-%In: Physica Status Solidi (A) Applications and Materials Science,
-%Vol. 202, No. 8, 06.2005, p. 1616-1618.  (https://doi.org/10.1002/pssa.200461200)
-%
-%Electrochemical Preparation of Pore Wall Modification Gradients
-%across Thin Porous Silicon Layers
-%Corrina M. Thompson, Michel Nieuwoudt, Anne M. Ruminski,
-%Michael J. Sailor, and Gordon M. Miskelly
-%Langmuir 2010 26 (10), 7598-7603
-%DOI: 10.1021/la904408h
-%
-% Richardson, Kathleen A., et al. "Advances in infrared gradient
-% refractive index (GRIN) materials: a review." Optical Engineering 59.11 (2020): 112602.
-%
-%
-%Lavanant, Enora, et al. "Radial gradient refractive index
-%(GRIN) infrared lens based on spatially resolved crystallization
-%of chalcogenide glass." Optical Materials Express 10.4 (2020): 860-867.
-%While widely used in the visible, radial gradient refractive
-%index (GRIN) lenses are still elusive in the IR waveband.
-%In this paper we introduce a new method based on spatially
-%resolved crystallization of chalcogenide glass to produce such lenses.
-%Optical and structural
-%
-%Yoon, Sun Mi, et al. "Subwavelength Hollow-Nanopillared Glass
-%with Gradient Refractive Index for Ultralow Diffuse Reflectance
-%and Antifogging." ACS applied materials & interfaces 12.5 (2020): 6234-6242.
-%Nanostructured glass with subwavelength hollow nanopillars
-%of diameters of sub-65 nm was fabricated, showing high optical
-%transmittance and ultralow diffuse reflectance. A simple
-%process involving single-step plasma etching was used on a
-%glass slide coated with a SiO2...
-%
-%Perez, Julius C., Tahmid H. Talukdar, and Judson D. Ryckman.
-%"Patterning Refractive Index on the Surface of a Chip by Direct
-%Nanoimprinting." CLEO: QELS_Fundamental Science. Optical Society of America, 2020.
-%
-%Szymanowski, Hieronim, et al. "Thin SiNC/SiOC Coatings with a
-%Gradient of Refractive Index Deposited from Organosilicon Precursor." Coatings 10.8 (2020): 794.
-%
-%Perez, Julius C., Tahmid H. Talukdar, and Judson D. Ryckman.
-% "Patterning Refractive Index on the Surface of a Chip by Direct
-% Nanoimprinting." CLEO: QELS_Fundamental Science. Optical Society of America, 2020.
-% $
-%}
+Section \ref{sec:discussion-results} includes experimental results and
+its comparison with numerically evaluated parameters. Finally, we
+devote Section \ref{sec:conclusions} to our concusions.
 
@@
 Here, $\delta^{(D)}$ is Dirac's delta function in $D$ dimensions.
-This problem may be solved readily using image charge theory \cite{jackson1999classical}.
+This problem may be solved readily using image charge theory \cite{jackson1975classical}.
 The potential within the electrolytic cell coincides
@@
 \section{Conclusions}
-\label{sec:conclusion}
+\label{sec:conclusions}
 By choosing a simple geometry for our electrochemical cell, namely, a

### 2020-10-30 paper.tex
Correct small mistake with extra citation.

@@
 optical elements with a high refractive index contrast \cite{ocier2017tunable}.
-Kruger et al. showed the \cite{krueger2016porous} \notaL{What did
-  Kruger show?}
-Furthermore, the same group \cite{krueger2018electrochemical} used
+Kruger et al. \cite{krueger2018electrochemical} used
 a porous silicon 1D GRIN structure infiltrated with polymer to
@@
 
-\section{Theory: current density}
+\section{Theory}
 \label{sec:theory}

### 2020-10-30 paper.tex
Revise paper up to procedures

@@
 Each plane of charges upon reflection on the surface of the sample at
-the bottom of the cell yields an
+the bottom of the cell yields a
 plane of image charges of the opposite sign, while each reflection
@@
 convergence properties. The potential can be obtained
-using the Ewald summation technique \cite{brodka2004ewald}, which yields
+using the Ewald summation technique
+\cite{ewald1921calculation, belhadj1991molecular-dynamics,
+  schmidt1997multipole, grzybowski2000ewald, toukmaji2000efficient,
+  brodka2004ewald, campione2012ewald}, which yields
 two rapidly converging series, one in real space and another one in reciprocal space.
@@
 simple periodic lattice of charges using a fast convergent sum over the 2D
-reciprocal vectors \cite{kratzer2019basics}, then sum over the charges that form the basis
+reciprocal vectors \cite{nijboer1957calculation, nijboer1958internal,
+  de_wette1965internal, watson1981madelung, grindlay1981k}
+\notaL{¿De qué se trata esta referencia que pusiste
+  aquí: \cite{kratzer2019basics}?}, then sum over the charges that form the basis
 of the 2D {\em crystal} plane, and finally sum over all the
- planes \notaC{cite{T6,T7}, esta citas las quite porque no puedo contestar esa pregunta de
- abajo}.\notaL{¿Estas referencias son relevantes? ¿En verdad
- se define en ellas la suma de Ewald por planos? Dime dónde p.f., en qué
- página. Y checa que todas las referencias tengan que ver con lo que decimos}
+ planes.
 
@@
 $2a$ and $2b$, and lying, for the time being, at the $z=0$ plane.
-The potential it produces obeys
+The potential $\phi$ it produces obeys
 \begin{equation}
@@
 capacitor $E_{0z}=-4\pi q_0/ab=-16\pi q_0/A$, which corresponds to the
-potential $\phi_0=16\pi q_0 z/A$. Other pairs of contiguous planes of with opposite charges
+potential $\phi_0=16\pi q_0 z/A$. Other pairs of contiguous planes with opposite charges
 contribute to the field elsewhere. The contributions to the potential
@@
 properties.
-
-\notaL{Quizás ni merece ser mencionado aquí: For the calculation of the optical properties we use the
-well known transfer matrix method \notaL{refs}.}
 
@@
 rectangular prism on the bottom of which we place a Si wafer which makes
-electrical contact to a brass \notaC{ laton. gold plate}\notaL{Porqué
+electrical contact to a brass \notaC{ laton.}\notaL{Porqué
   vivechna dice silver/copper?}

### 2020-10-30 paper.tex
Revise up to results

@@
 
-  \caption{Experimental set-up for
+  \caption{Schematic experimental set-up for
     the fabrication of GRIN PS structures. We show a side view of the
@@
     (middle and lower panels),
-    illustrating eght regions $1\ldots8$ of decreasing porosity,
+    illustrating eight regions $1\ldots8$ of decreasing porosity,
     illustrating the changes in pore radii,
@@
 rectangular prism on the bottom of which we place a Si wafer which makes
-electrical contact to a brass \notaC{ laton.}\notaL{Porqué
-  vivechna dice silver/copper?}
-\notaL{Lo inventé; de qué material es
-  el contacto bajo la muestra?} which together make the anode. The
+electrical contact to a brass plate\notaC{ laton.}\notaL{Porqué
+  vivechna dice silver/copper? De qué era: latón, plata, cobre, una
+  aleación de cobre y plata? Era un alambre o una placa?}
+which together make the anode. The
 cathode consists of a platinum wire insulated except for a small region
@@
 (resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
-conditions. The process was performed at
-\notaC{room temperature, no controle latempertaura}
-,\notaL{OJO. No controlaste la temperatura} with an
+conditions. The process was performed at room temperatured with an
 electrolytic mixture of aqueous hydrofluoric
 acid (HF) (concentration 48\% wt), glycerol (purity 99.8 \% wt) and
-ethanol (purity 99.9\% wt) in a 3:7:1 volume ratio. \notaL{Checa que
-  todo esto sí corresponda a tus últimas muestras} \notaC{SI corresponde}
+ethanol (purity 99.9\% wt) in a 3:7:1 volume ratio.
 After the anodizing process, the samples were rinsed with
@@
 of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
-sides $a=2.01\,\text{cm}$ \notaL{Cambié el número, de acuerdo a unas
-  mediciones de Cristian} and $b=1.48\,\text{cm}$, with an uncovered sample area
+sides $a=2.01\,\text{cm}$ and $b=1.48\,\text{cm}$, with an uncovered sample area
 of about $3\,\text{cm}^2$. The height of the liquid was set at
 $c=1\,\text{cm}$. The cathode was a
-platinum wire that with a diameter of $0.41\,\text{mm}$ insulated with
-teflon tape \notaL{Según Vivechna esto es falso: by a
-teflon cylinder of external diameter $\,2\text{mm}$}, with an uncovered
+platinum wire with a diameter of $0.41\,\text{mm}$ insulated with
+teflon tape, with an uncovered
 tip located at $\bm r_0=(x_0,
@@
 samples using a {\em Perkin Elmer Lambda 950}
-UV-Vis-NIR spectrophotometer.\notaL{Finalmente, ¿fue éste el que se
-  usó? Si sí, ¿hay algo internesante que decir sobre el? Cosas como el
-tamaño de mancha, resolución espectral, etc.} \notaC{Data collection absoluto
-reflectance mode. Spot size, physical setting, width (0.7mm) and length (2.0mm).
-Instrument setting, slit width (0.6mm). Method settings
-wavelength from(1400nm) to(300nm)}
-
- For interpretation of the data layer we used
-the standard formula \cite{stenzel2015physics} for the reflectance of three media:
-air (0) environment, the PS film (1) and the c-Si substrate (2),
+UV-Vis-NIR spectrophotometer in its data collection absolute
+reflectance mode, using a rectangular spot size of
+$0.7\text{mm}\times2.0\text{mm}$, a slit width of $0.6\text{mm}$ and
+a wavelength range from $1400\text{nm}$ to
+$300\text{nm}$.\notaL{Vivechna: puedes checar si así se reportan estos parámetros?}
+
+For interpretation of the data we used
+the standard formula \cite{stenzel2015physics} for the reflectance of
+a three media system:
+an air environment  (0), the PS film (1) and the c-Si substrate (2),
 \begin{equation}\label{Eq:ECMR}

### 2020-10-30 paper.tex
Revise to the end

@@
 (Sec. \ref{sec:fabrication-ps-grin}) but applying different currents
-$I_1=5\,\text{mA}$, $I_2=10\,\text{mA}$, and $I_3=20\,\text{mA}$, . The results are shown in
+$I_1=5\,\text{mA}$, $I_2=10\,\text{mA}$, and $I_3=20\,\text{mA}$. The results are shown in
 Figs. \ref{fig:R5}, \ref{fig:R10}, and \ref{fig:R20}.
@@
 than in our fitted curves. We believe this is due to the finite width
-\notaL{beams width=?} \notaC{beams width width (0.7mm) and length (2.0mm)}
-of the illuminating beam of our
+$0.7\text{mm}\times2.0\text{mm}$ of the illuminating beam of our
 spectrometer. Thus, as our GRIN sample is not macroscopically homogeneous and its
@@
 interface roughness might also reduce the contrast through scattering
-and its corresponding apparent dissipation \cite{missoni2020rough}
-\notaL{citar a:
-  Missoni, Leandro L., Guillermo P. Ortiz, María Luz Martínez Ricci,
-  Victor J. Toranzos, and W. Luis Mochán. 2020. “Rough 1D Photonic
-  Crystals: A Transfer Matrix Approach.” Optical Materials 109
-  (November): 110012. https://doi.org/10.1016/j.optmat.2020.110012.
-}.
+and its corresponding apparent dissipation \cite{missoni2020rough}.
 The loss of contrast is most notable for the thicker regions
@@
 \end{equation}
+The discrepancies may be due to the ill definition of the edge of the
+sample (the position of the sealing o-ring) with respect to which we
+measured the position of the illuminating spot. A rigid displacement along
+$x$ yields mostly a horizontal shift of the results shown in
+Fig. \ref{fig:p} and that can bring them into closer agreement.
 
@@
 \end{equation}
+The discrepancies, as in Fig. \ref{fig:p} might be due to our poor
+definition of our reference position and may be eliminated by
+introducing a rigid displacement along $x$ between the samples. For
+multilayered samples, produced by modulating the current $I$ in time,
+without changing wafers, these error source would be absent.
 
@@
 
-The theoretical reflectance coudl as well be calculated using
+The theoretical reflectance could as well be calculated using
 \eqref{Eq:ECMR}-\eqref{eq:v} for more complicated structures, in which the
@@
 curves that allow the approximate prediction of the properties of the other
-samples. The calibration curves can be used to design and calculate the optical
+samples. We believe that the discrepancies we found between samples
+are due to difficulties in defining a common reference position and
+may be eliminated through a rigid shift along the $x$ direction.
+The calibration curves can be used to design and calculate the optical
 properties of other systems prepared under similar conditions, such as
@@
 
-\notaV{By choosing a simple geometry for our electrochemical cell, namely, a
-rectangular prism, and employing a point-like electrode, we were able
-to derive a simple expression for the calculation of the electric current
-density along the surface of a Si sample. The expression was obtained
-by using image charge theory and a plane-wise summation of Coulomb
-potentials in reciprocal space, and it is made up of
-a rapidly converging sum of analytical terms. This allowed us to
-characterize the porosity of a PS layer and the etching
-rate for different values of the etching current density by making
-optical experiments on just a
-few samples. We illustrated the procedure with two samples each of which we
-measured at three different positions. These calibration curves are
-very useful as the etching rate for the formation of porous silicon
-and the resulting porosity is very sensitive to the growth conditions
-and to the properties of the substrate, such as its doping. Thus,
-there are no universal calibration curves. Having obtained these calibration curves
-and being able to compute the current density at different positions
-allows the prediction of the properties of GRIN structures. We
-illustrated this by desigining a PS GRIN microcavity tuned at one
-position to a given wavelength. (Q. for Dr. Mochan : Do we intend
-to illustrate the design?) We found a good agreement between its
-measured reflectance spectra at different points with the spectra
-calculated from the values of the expected local current
-density using the calibration curves. We also found good agreement
-between the measured and the expected geometry of the system. These
-results show that the use of a simple electrolytic cell and our
-computational procedure does allow the accurate prediction of the
-optical properties of GRIN structures, and thus we believe it will
-prove helpful for the design fabrication and characterization of novel}
-
 \section*{Acknowledgments}
@@
   agradecimientos de Vivechna (quizás incluyendo al icf)}
-\nocite{*}
-\notaL{Manda toda la bibliografía a un archivo .bib}
-\notaL{Cuando esté listo, quiero que me expliques por qué incluiste
-  cada uno de los artículos citados}
-% \bibliography{bibligrin} %Bibliographie
-%\printbibliography
-%\bibliographystyle{plain}
-%\bibliography{bibligrin.bib}
-%\medskip
-%
-
 \bibliographystyle{unsrt}
-%
 \bibliography{bibligrin} %Aquí ponen el nombre del archivo .bib
-
 \end{document}

### 2020-11-07 paper.tex
coloque las observaciones de la Dra Vivechana y cambios bib

@@
 to their local porosity and thickness which, together with our model, were then used to obtain
-the $p$ vs. $j$ and $v$ vs. $j$ calibration curves. We corroborated
+the $p$ vs. $j$ and $v$ vs. $j$ calibration curves. 
+\notaV{Thickness was additionally viewed through scanning electron microscopy}. We corroborated
 our model by comparing the calibration curves for different samples. Thus, from
@@
 usefulness. \notaL{I believe the examples below are unrelated to GRIN,
-  thats why I added the previous remark.} As an example, the
+  thats why I added the previous remark.} \notaV{Response : 
+ALL the examples are related to GRIN} As an example, the
 roughness dependent  response of cells has been tested on
@@
 group\cite{wang2019fabrication}. \notaL{Is this Shannon a big shot, or
-  why should we name him?}
+  why should we name him?} \notaV{R : Eliminated the name}
 Among electrochemical methods, compositional and doping density changes
@@
 applications, given the biocompatible nature of PS, . \notaL{How is this related to the gradient?}
+\notaV{ The idea
+here was to mention the usefulness of GRIN in portion 
+size determination followed by its delivery through the variation of pH ; 
+If you find this comment too way off, further applicability of protein 
+size determination in drug delivery application can
+ be removed "ADDITIONALLY.....applications" }
 A similar asymmetric electrode configuration was used to fabricate
@@
 Additionally it has been shown that the combination of thermal  oxidation  and
-infiltration of TiO2  by ALD \notaL{What is this acronym?} allows the manufacture
+infiltration of TiO2  by \notaV{Atomic Layer Deposition} (ALD) \notaL{What is this acronym?} 
+allows the manufacture
 of transparent GRIN
@@
 simple analytical model to calculate
-the current density at any point over the GRIN structure under preparaton.
+the current density at any point over the GRIN structure under preparation.
 In Section \ref{sec:procedures} we provide experimental details for the
@@
 Section \ref{sec:discussion-results} includes experimental results and
-its comparison with numerically evaluated parameters. Finally, we
-devote Section \ref{sec:conclusions} to our concusions.
+it's comparison with numerically evaluated parameters. Finally, we
+devote Section \ref{sec:conclusions} to our conclusions.
 
@@
 design and optimization of well characterized reproducible GRIN PS
-structures.\notaL{Tenemos referencias para afirmar esto?} Thus, we
-believe a
+structures.\notaL{Tenemos referencias para afirmar esto?}
+\notaV{NOT THAT I KNOW, so I changed the expression has been changed}
+ Thus, we believe a
 system for which the current density field may be
@@
 \notaL{¿De qué se trata esta referencia que pusiste
-  aquí: \cite{kratzer2019basics}?}, then sum over the charges that form the basis
+  aquí: \cite{kratzer2019basics}?}, \notaC{Lo que quiero con este paper 
+es resaltar los Conceptos básicos de la cristalografía, 
+grupo de puntos cristalográficos, la red recíproca y algunos relaciones de la 
+zona de Brillouin.}
+then sum over the charges that form the basis
 of the 2D {\em crystal} plane, and finally sum over all the
@@
 rectangular prism on the bottom of which we place a Si wafer which makes
-electrical contact to a brass plate\notaC{ laton.}\notaL{Porqué
+electrical contact to a silver plate\notaC{ plata.}\notaL{Porqué
 vivechna dice silver/copper? De qué era: latón, plata, cobre, una
 aleación de cobre y plata? Era un alambre o una placa?}
+\notaV{CRISTIAN :  POR FAVOR COLOCAS lo que usaste.}
 which together make the anode. The
@@
 $300\text{nm}$.\notaL{Vivechna: puedes checar si así se reportan estos parámetros?}
-
+\notaV{CHANGED}
 For interpretation of the data we used
@@
   agradecimientos de Vivechna (quizás incluyendo al icf)}
+\notaV{ acknowledges support from CONACyT Basic Sciences project A-S1 30393, 
+PRODEP and ICF.}
 \bibliographystyle{unsrt}

### 2020-11-07 paper.tex
Remove trailing spaces
Incorporate more Vivechna's suggestions

@@
 ultraviolet-visible-near infrared reflectance
-spectroscopy, \notaL{Should we mention microscopy?}, and related them
+spectroscopy \notaL{Should we mention microscopy?}, and related them
 to their local porosity and thickness which, together with our model, were then used to obtain
-the $p$ vs. $j$ and $v$ vs. $j$ calibration curves. 
-\notaV{Thickness was additionally viewed through scanning electron microscopy}. We corroborated
+the $p$ vs. $j$ and $v$ vs. $j$ calibration curves.  Thickness was additionally viewed through scanning electron microscopy. We corroborated
 our model by comparing the calibration curves for different samples. Thus, from
@@
 gradients of CdS layers
-on gold electrodes have been obtained made by Shannon’s
-group\cite{wang2019fabrication}. \notaL{Is this Shannon a big shot, or
-  why should we name him?} \notaV{R : Eliminated the name}
+on gold electrodes have also been obtained\cite{wang2019fabrication}. \notaL{Is this Shannon a big shot, or
+  why should we name him?; R : Eliminated the name}
 Among electrochemical methods, compositional and doping density changes
@@
 porosity along the depth, allowing the easy fabrication of different kinds
-\cite{perez2018reflectivity} of 1D photonics crystals and other
+\cite{perez2018reflectivity} of 1D dielectric multilayered
 structures. \notaL{Photonic crystals only in the periodic case.}
@@
 homogeneous samples, with invariant structural and optical properties
-along the surface, an asymmetric configuration \notaL{Is it clear what
-  is asymmetric?} may produce porous
-Silicon structures with a lateral gradient in properties such as
+along the surface, another configuration where a Pt pin electrode is placed
+perpendicular to the silicon wafer (anode)\notaL{Is it clear what
+  is asymmetric?}, produces porous
+silicon structures with a lateral gradient in properties such as
 thickness, pore size and density, and thus, refractive index and
-optical thickness. In this configuration, a small platinum electrode (cathode)
-is positioned perpendicular  to the surface of a Si substrate (anode)
-near one end \notaL{ At the center wouldn't be asymmetric: or the
-  center} of the cell, resulting  in a current
-density  which decreases as the distance to the electrode increases
- \cite{khung2008using, clements2011mesenchymal}.
+optical thickness \cite{khung2008using, clements2011mesenchymal}.
 The resulting porous surface can have pore sizes ranging from a few nanometers
@@
 Additionally it has been shown that the combination of thermal  oxidation  and
-infiltration of TiO2  by \notaV{Atomic Layer Deposition} (ALD) \notaL{What is this acronym?} 
-allows the manufacture
+infiltration of TiO2  by Atomic Layer Deposition \notaL{What is this acronym?} allows the manufacture
 of transparent GRIN
@@
 the current density, as well as the etching rate and the thickness of the
-porous layer. Nevertheless, it is challeging to measure the
-{\em local} value of $\bm j(\bm r)$ along the surface. This hampers the
-design and optimization of well characterized reproducible GRIN PS
-structures.\notaL{Tenemos referencias para afirmar esto?}
-\notaV{NOT THAT I KNOW, so I changed the expression has been changed}
- Thus, we believe a
-system for which the current density field may be
-easily computed would be useful.
+porous layer. Nevertheless, it is challenging to measure the
+{\em local} value of $\bm j(\bm r)$ along the surface. As
+designing a GRIN structure with predefined parameters such as porosity
+and thickness at each point of a GRIN based optical device is desirable
+for reproducible device performance, we
+propose a simple method to compute the current density field at each point
+of the device.
 Though $\bm j(\bm r)$ may be numerically calculated for any
@@
 reciprocal vectors \cite{nijboer1957calculation, nijboer1958internal,
-  de_wette1965internal, watson1981madelung, grindlay1981k}
-\notaL{¿De qué se trata esta referencia que pusiste
-  aquí: \cite{kratzer2019basics}?}, \notaC{Lo que quiero con este paper 
-es resaltar los Conceptos básicos de la cristalografía, 
-grupo de puntos cristalográficos, la red recíproca y algunos relaciones de la 
-zona de Brillouin.}
+  de_wette1965internal, watson1981madelung, grindlay1981k},
 then sum over the charges that form the basis
@@
 rectangular prism on the bottom of which we place a Si wafer which makes
-electrical contact to a silver plate\notaC{ plata.}\notaL{Porqué
+electrical contact to a brass plate\notaC{ laton.}\notaL{Porqué
   vivechna dice silver/copper? De qué era: latón, plata, cobre, una
-aleación de cobre y plata? Era un alambre o una placa?}
-\notaV{CRISTIAN :  POR FAVOR COLOCAS lo que usaste.}
+  aleación de cobre y plata? Era un alambre o una placa?  CRISTIAN :  POR FAVOR COLOCAS lo que usaste.  }
 which together make the anode. The
@@
 \label{sec:refl-meas}
-We measured the reflectivity spectra at different positions over our
-samples using a {\em Perkin Elmer Lambda 950}
-UV-Vis-NIR spectrophotometer in its data collection absolute
-reflectance mode, using a rectangular spot size of
-$0.7\text{mm}\times2.0\text{mm}$, a slit width of $0.6\text{mm}$ and
-a wavelength range from $1400\text{nm}$ to
-$300\text{nm}$.\notaL{Vivechna: puedes checar si así se reportan estos parámetros?}
-\notaV{CHANGED}
+We measured absolute reflectance at different positions over our
+samples using Universal reflectance accessory  equipped {\em Perkin Elmer Lambda 950}
+UV-Vis-NIR spectrophotometer, with a rectangular spot size of
+$0.7\text{mm}\times2.0\text{mm}$, a slit width of $0.6\text{mm}$ in
+a wavelength range from $300\text{nm}$ to
+$1400\text{nm}$.\notaL{Vivechna: puedes checar si así se reportan estos parámetros? CHANGED}
+
 For interpretation of the data we used
@@
 WLM acknowledges the support of DGAPA-UNAM under grant
-IN111119. \notaL{Cristian debe agradecer a conacyt y faltan
+IN111119. VA acknowledges support from CONACyT Basic Sciences project A-S1 30393, PRODEP and ICF. \notaL{Cristian debe agradecer a conacyt y faltan
   agradecimientos de Vivechna (quizás incluyendo al icf)}

### 2020-11-08 paper.tex
Revise paper.

@@
 \author[1]{C. A. Ospina de la Cruz}
-\author[2]{V. Agarwal}
+\author[2,3]{V. Agarwal}
 \author[3]{W. L. Mochán}
@@
 \maketitle
-\notaV{Index Structures (NOTE: WE NEED TO CHANGE THE NAME;
-  Probably "Analytical model for  porous silicon structures with 1D
-  gradient refractive index)}
-\notaL{The calculation is 2D, seems 1D due to the narrow geometry chosen.}
+
 \begin{abstract}
@@
 ultraviolet-visible-near infrared reflectance
-spectroscopy \notaL{Should we mention microscopy?}, and related them
+spectroscopy, and related them
 to their local porosity and thickness which, together with our model, were then used to obtain
-the $p$ vs. $j$ and $v$ vs. $j$ calibration curves.  Thickness was additionally viewed through scanning electron microscopy. We corroborated
-our model by comparing the calibration curves for different samples. Thus, from
+the $p$ vs. $j$ and $v$ vs. $j$ calibration curves.  The dependence of
+porosity and thickness with position was corroborated through scanning electron microscopy. We
+compared the calibration curves for different samples. Thus, from
 measurements on only one, or a few simple systems, we may obtain full
@@
 with gradients in other properties have also shown their
-usefulness. \notaL{I believe the examples below are unrelated to GRIN,
-  thats why I added the previous remark.} \notaV{Response :
-ALL the examples are related to GRIN} As an example, the
+usefulness. As an example, the
 roughness dependent  response of cells has been tested on
-materials used applications in medical implants
+materials used for applications in medical implants
 \cite{bai2020bioinspired}.
@@
 gradients of CdS layers
-on gold electrodes have also been obtained\cite{wang2019fabrication}. \notaL{Is this Shannon a big shot, or
-  why should we name him?; R : Eliminated the name}
+on gold electrodes have also been obtained \cite{wang2019fabrication}.
 Among electrochemical methods, compositional and doping density changes
 in  conducting polymers have been used to produce gradients using Indium Tin
-Oxide electrodes \cite{inagi2010bipolar}
+Oxide electrodes \cite{inagi2010bipolar}.
 Electrochemically induced potential gradients have been shown to catalyze the
@@
 This technique has the additional advantage of being compatible
-with VLSI devices and integrable with microelectronics.
+with very large scale integration (VLSI) devices and integrable with microelectronics.
 
@@
 chemical sensors and biosensors \cite{kumar2020porous},
-microelectronics and MEMS \cite{martinez2016dual},as well as a
+microelectronics and micromechanical systems (MEMS) \cite{martinez2016dual},as well as a
 range of optical \cite{estevez2014porous} and optoelectronic applications
@@
 \cite{perez2018reflectivity} of 1D dielectric multilayered
-structures. \notaL{Photonic crystals only in the periodic case.}
+structures.
 Although the conventional fabrication of PS yields laterally
@@
 along the surface, another configuration where a Pt pin electrode is placed
-perpendicular to the silicon wafer (anode)\notaL{Is it clear what
-  is asymmetric?}, produces porous
+perpendicular to the silicon wafer, produces porous
 silicon structures with a lateral gradient in properties such as
@@
 \cite{collins2002determining}. For example, Sailor's group
-\cite{collins2002determining, sailor2012porous} applied it
+\cite{sailor2012porous, collins2002determining} applied it
 for the determination of protein size.
-Additionally, gating of
-the optical response through a variation in pH of the solution was shown to
-trap/release biomolecules for possible drug delivery
-applications, given the biocompatible nature of PS, . \notaL{How is this related to the gradient?}
-\notaV{ The idea
-here was to mention the usefulness of GRIN in portion
-size determination followed by its delivery through the variation of pH ;
-If you find this comment too way off, further applicability of protein
-size determination in drug delivery application can
- be removed "ADDITIONALLY.....applications" }
+Additionally, a variation in pH of the solution could gate the
+trapping/release of biomolecules at regions with different porosity, a
+result potentially useful for drug delivery
+applications given the biocompatible nature of PS.
 A similar asymmetric electrode configuration was used to fabricate
@@
 for developing ethanol sensors \cite{sailor2012porous}.
-Additionally it has been shown that the combination of thermal  oxidation  and
-infiltration of TiO2  by Atomic Layer Deposition \notaL{What is this acronym?} allows the manufacture
+Additionally, it has been shown that the combination of thermal  oxidation  and
+infiltration of TiO2  by atomic layer deposition allows the manufacture
 of transparent GRIN
@@
 Recently, J Wang et al. has shown the fabrication of
-a miniature spectrometer with PS based rugate filter using a
+a miniature spectrometer with a PS based rugate filter using a
 radial interfacial potential distribution \cite{wang2019fabrication}
@@
 layer, thus allowing the prediction of the optical properties of
-multilayered GRIN structure. The structure of the paper is the
+multilayered GRIN structures. The structure of the paper is the
 following.
-\notaL{Check when finished}. In Section \ref{sec:theory} we develop a
+In Section \ref{sec:theory} we develop a
 simple analytical model to calculate
-the current density at any point over the GRIN structure under preparation.
+the current density at any point over the GRIN structure under
+preparation for the case of an electrolytic cell with a simple shape.
 In Section \ref{sec:procedures} we provide experimental details for the
@@
 Section \ref{sec:discussion-results} includes experimental results and
-it's comparison with numerically evaluated parameters. Finally, we
+their comparison with numerically evaluated parameters. Finally, we
 devote Section \ref{sec:conclusions} to our conclusions.
@@
 \label{sec:calc-curr-dens}
-\notaL{check where acronyms are first defined}
-A gradient in the optical properties of porous Silicon (PS) systems may be
+A gradient in the optical properties of PS systems may be
 obtained by electrochemically attacking a Si surface with a position dependent current
 density ${\bm j(\bm r)}$, as the porosity and refractive index depend on
-the current density, as well as the etching rate and the thickness of the
+the current density, as does the etching rate and the thickness of the
 porous layer. Nevertheless, it is challenging to measure the
@@
 and thickness at each point of a GRIN based optical device is desirable
-for reproducible device performance, we
+for reproducible device fabrication, we
 propose a simple method to compute the current density field at each point
@@
   \label{eq:poisson}
-  \nabla^2\phi=-4\pi q_0\delta^{(3)}(\bm r-\bm r_0),
+  \nabla^2\phi(\bm r)=-4\pi q_0\delta^{(3)}(\bm r-\bm r_0),
 \end{equation}
@@
 within the region $0\le x\le a$, $0\le y \le b$, $0\le z\le c$
-with that an infinite fictitious empty space but for the point charge
+with that within an infinite fictitious empty space but for the point charge
 $q_0$ at the tip of the electrode at $\bm r_0$, and an array of its fictitious image
@@
 summation, where we first obtain the potential and field produced by a
-simple periodic lattice of charges using a fast convergent sum over the 2D
+simple periodic lattice of charges using a fast convergent sum over
+the two dimensional (2D)
 reciprocal vectors \cite{nijboer1957calculation, nijboer1958internal,
@@
 where $\bm r_\|$ is the projection of the observation position $\bm
-r=(x,y,z)$ onto the $xy$ plane, $\{\bm G\}$ is the
+r=(x,y,z)$ onto the $xy$ plane, $\{\bm G\}$ is the 2D
 reciprocal lattice defined through $e^{i\bm G\cdot\bm R}=1$ for all
@@
 solved. After applying boundary conditions at $z=0$ and regularity
-conditions at infinity, we obtain
+conditions at infinity (for $G\ne 0$), we obtain
 \begin{equation}
@@
     parameters of the arrangement $x_0$, $z_0$, $a$ and $c$
-    and the current source and a few schematic current flux
+    and a few schematic current flux
     lines. Top and side schematic views of the resulting sample
     (middle and lower panels),
-    illustrating eight regions $1\ldots8$ of decreasing porosity,
+    illustrating eight regions $1\ldots8$ of decreasing porosity and thickness,
     illustrating the changes in pore radii,
@@
 experimental setup to manufacture GRIN PS structures.
-As dicussed above, we fabricated an electrolytic cell with the shape of a
+As discussed above, we fabricated an electrolytic cell with the shape of a
 rectangular prism on the bottom of which we place a Si wafer which makes
-electrical contact to a brass plate\notaC{ laton.}\notaL{Porqué
-  vivechna dice silver/copper? De qué era: latón, plata, cobre, una
-  aleación de cobre y plata? Era un alambre o una placa?  CRISTIAN :  POR FAVOR COLOCAS lo que usaste.  }
+electrical contact to a brass plate
 which together make the anode. The
@@
 tip located at $\bm r_0=(x_0,
-y_0,z_0)=(0.2\,\text{cm},0.74\,\text{cm},0.9\,\text{cm})$. \notaL{Checa todos estos datos}
+y_0,z_0)=(0.2\,\text{cm},0.74\,\text{cm},0.9\,\text{cm})$.
 We manufactured three samples $G_1$, $G_2$ and $G_3$ by applying a
@@
 \label{sec:refl-meas}
-We measured absolute reflectance at different positions over our
+We measured the absolute reflectance at different positions over our
 samples using Universal reflectance accessory  equipped {\em Perkin Elmer Lambda 950}
-UV-Vis-NIR spectrophotometer, with a rectangular spot size of
+ultraviolet-visible-near infrared (UV-Vis-NIR) spectrophotometer, with a rectangular spot size of
 $0.7\text{mm}\times2.0\text{mm}$, a slit width of $0.6\text{mm}$ in
 a wavelength range from $300\text{nm}$ to
-$1400\text{nm}$.\notaL{Vivechna: puedes checar si así se reportan estos parámetros? CHANGED}
+$1400\text{nm}$.
 
@@
 a three media system:
-an air environment  (0), the PS film (1) and the c-Si substrate (2),
+an air environment  (0), the PS film (1) and the crystalline Si (c-Si) substrate (2),
 \begin{equation}\label{Eq:ECMR}
@@
 
+\subsection{Scanning Electron Microscopy}
+\notaL{Insert a paragraph explaining something about how the
+  micrographs were obtained. Choose an appropriate title for the
+  subsection. Include the definition of the acronym SEM}
+
 \section{Discussion and Results}
@@
 that vary mostly along the $x$ direction. Of course, this would differ
-for cells with different aspect ratios.
+for cells with different aspect ratios and for different positions of
+the electrode.
 
@@
     in Fig. \ref{fig:DR1} with a current $ I_3=20 \text{mA}$,
-    during a time $t=250\text{s}$. We indicate eight regions $x_i$
+    during a time $t=250\text{s}$. We indicate the centerline with a
+    dashed line and eight regions $x_i$
     $(i=1, 2,...8)$ centered at positions,
@@
 
-\subsection{Reflectance}
+In Fig. \ref{fig:sem} we show some SEM images of the sample $G_3$,
+including top views and lateral views taken after
+the optical characterization was completed and the sample was cut
+along its centerline (see Sec. \ref{sec:R}) from
+three regions around to the left side, the center, and the right side
+of the sample shown in Fig. \ref{fig:SI3}.
+\begin{figure}
+  \centering
+  \includegraphics[width=.3\textwidth]{sema}
+  \includegraphics[width=.3\textwidth]{semb}
+  \includegraphics[width=.3\textwidth]{semc}
+  \includegraphics[width=.3\textwidth]{semd}
+  \includegraphics[width=.3\textwidth]{seme}
+  \includegraphics[width=.3\textwidth]{semf}
+  \caption{Top ((a), (b), and (c)) and lateral ((d), (e), and (f)) SEM
+    micrographs of the sample $G_3$ taken from a region corresponding to the left
+    side ((a) and (d)), center ((b) and (e)), and right side ((c) and
+    (f)) along the centerline shown in Fig. \ref{fig:SI3}.}
+  \label{fig:sem}
+\end{figure}
+We confirm that as we move away from the electrode, the pore
+size and pore density diminish (panels (a) to (c) of
+Fig. \ref{fig:sem}) and the sample becomes much thinner (panels (d) to (f)).
+
+\subsection{Reflectance}\label{sec:R}
 
@@
 experimental results have contributions from regions with slightly
-different porosities and thicknesses, averaging out the interference
+different porosities and thicknesses, partially averaging out the interference
 maxima and minima. We expect microscopic inhomogeneities such as
@@
 \ref{t:jpdv}. Notice that the scaling parameters are close to 1,
-showing that the calibration was adequate. \notaL{Is this meaningful?}.
+showing that the calibration was adequate.
 
@@
 WLM acknowledges the support of DGAPA-UNAM under grant
-IN111119. VA acknowledges support from CONACyT Basic Sciences project A-S1 30393, PRODEP and ICF. \notaL{Cristian debe agradecer a conacyt y faltan
-  agradecimientos de Vivechna (quizás incluyendo al icf)}
-\notaV{ acknowledges support from CONACyT Basic Sciences project A-S1 30393,
-PRODEP and ICF.}
+IN111119. VA acknowledges support from CONACyT Basic Sciences project
+A-S1 30393 and from PRODEP, and is grateful to ICF where she spent a
+sabatical. CODLC is grateful for a scholarship from CONACyT.
 \bibliographystyle{unsrt}
-\bibliography{bibligrin} %Aquí ponen el nombre del archivo .bib
+\bibliography{bibligrin}
 \end{document}

### 2020-11-10 paper.tex
Modify Cristian's name
colocambo la subsecion del sem

@@
 \title{Model for Porous Silicon Structures with a Lateral Gradient}
-\author[1]{C. A. Ospina de la Cruz}
+\author[1]{C. A. Ospina-Delacruz}
 \author[2,3]{V. Agarwal}
@@
 
-\subsection{Scanning Electron Microscopy}
+\notaC{\subsection{Morphological studies}}
+\notaC{The morphologies of the etched porous layers (plan-view and cross-sectional) was observed using 
+(SEM) scanning electron microscopy (Hitachi SU1510  High Technologies Canada, 
+Inc., Toronto, Canada), the thickness  and porosity  of each fabricated  film was measured.}
 \notaL{Insert a paragraph explaining something about how the
@@
 A-S1 30393 and from PRODEP, and is grateful to ICF where she spent a
-sabatical. CODLC is grateful for a scholarship from CONACyT.
+sabatical. CAOD is grateful for a scholarship from CONACyT.
 \bibliographystyle{unsrt}

### 2020-11-11 paper.tex
Incorporated Cristian's description of SEM

--- 2020-11-08 paper.tex
@@
 
-\subsection{Scanning Electron Microscopy}
-\notaL{Insert a paragraph explaining something about how the
-  micrographs were obtained. Choose an appropriate title for the
-  subsection. Include the definition of the acronym SEM}
+\subsection{Morphological studies}
+
+The morphology of the etched porous layers (plan-view and
+cross-sectional) was observed using (SEM) scanning electron microscopy
+(Hitachi SU1510  High Technologies Canada,  Inc., Toronto, Canada).
+
+% the thickness  and porosity  of each fabricated  film was measured.
 

### 2020-11-12 paper.tex
Apply Vivechnas suggestions.

@@
 \author[1]{C. A. Ospina-Delacruz}
-\author[2,3]{V. Agarwal}
-\author[3]{W. L. Mochán}
+\author[1,2]{V. Agarwal}
+\author[2]{W. L. Mochán}
 
-\affil[1]{Posgrado en Ingenier\'ia y Ciencias Aplicadas del Centro de
-  Investigación en Ingenier\'ia y Ciencias Aplicadas (CIICAp-IICBA),
+\affil[1]{Centro de
+  Investigación en Ingeniería y Ciencias Aplicadas (CIICAp-IICBA),
   Universidad Autónoma del Estado de Morelos (UAEM), Cuernavaca CP
   62209, México}
-\affil[2]{Centro de Investigaci\'on en Ingenier\'ia y Ciencias
-  Aplicadas,Universidad del Estado de Morelos, Av. Universidad 1001
-  Col. Chamilpa, Cuernavaca, Morelos 62209, Mexico  }
-\affil[3]{Instituto de Ciencias F\'isica ,Universidad Nacional
-  Autonoma de Mexico, Av. Universidad S/N, Col. Chamilpa, 62210
-  Cuernavaca, Morelos, Mexico}
+\affil[2]{Instituto de Ciencias F\'isicas, Universidad Nacional
+  Autonóma de México, Av. Universidad S/N, Col. Chamilpa, 62210
+  Cuernavaca, Morelos, México}
 \begin{document}
@@
 calibration curves which may be used to predict, design, and fabricate
-more complex novel nonhomogenous devices with lateral gradients which can be used
+more complex novel non-homogenous devices with lateral gradients which can be used
 for manifold applications.
@@
 phase along their surface, yielding applications such as flat
-lenses. Furtheremore, there are important biological applications
+lenses. Furthermore, there are important biological applications
 which combine topographical features with index of refraction
@@
 Although porous silicon (PS) initially stimulated the interest of the scientific
-community due to its photoluminiscence in the visible range at room
+community due to its photoluminescence in the visible range at room
 temperature, it has presently
@@
 properties of the resulting structures. This would allow the design
-and optimization of the desired devices.
+and possible optimization of the desired devices.
 In this work, we report a simple analytical model to quantitatively
 analyze the spatial dependence of the current density during the
-electrochemical on Si to produce PS structures. A calibration
+electrochemical etching of Si to produce PS nanostructures with a
+lateral gradient. A calibration
 procedure may then relate the current density to the porosity and the
-etching rate. Thus, for a given etching current acting over a given
+etching rate. Thus, for a given etching current acting over for a given
 time, we may predict the position dependence of the index of

### 2020-11-13 paper.tex
Adapt to Elsevier. Make small corrections.

@@
-\documentclass{article}
+\documentclass[review,sort&compress]{cas-sc}
+%\documentclass{article}
 \usepackage{amsmath}
 \usepackage{graphicx} % gráficos
-\usepackage[noblocks]{authblk}
+\usepackage[numbers]{natbib}
+%\usepackage[noblocks]{authblk}
 %\usepackage{authblk}
@@
 \usepackage{hyperref}
-\usepackage[normalem]{ulem} %opcional para la correcciones
+%\usepackage[normalem]{ulem} %opcional para la correcciones
 \newcommand{\abs}[1]{\lvert#1\rvert}
@@
 
-\title{Model for Porous Silicon Structures with a Lateral Gradient}
-\author[1]{C. A. Ospina-Delacruz}
-\author[1,2]{V. Agarwal}
-\author[2]{W. L. Mochán}
-
-\affil[1]{Centro de
+\begin{document}
+\shorttitle{Model for PS Structures with a Lateral Gradient}
+\shortauthors{Ospina-Delacruz et al.}
+\title[mode=title]{Model for Porous Silicon Structures with a Lateral Gradient}
+\author[1]{C. A. Ospina-Delacruz}[orcid=0000-0000-0000-0000]
+\ead{crisalod@gmail.com}
+\credit{Investigation; Software; Writing - original draft}
+\author[1,2]{V. Agarwal}[orcid=0000-0003-2168-853X]
+\fnmark[1]
+\ead{vagarwal@uaem.mx}
+\credit{Funding acquisition; Investigation; Supervision; Software; Writing - review \& editing}
+\author[2]{W. L. Mochán}[type=editor,orcid=0000-0003-0418-5375]
+%\cormark[1]
+\ead{mochan@fis.unam.mx}
+\credit{Conceptualization; Funding acquisition; Investigation;
+  Methodology; Supervision; Writing - review \& editing}
+\address[1]{Centro de
   Investigación en Ingeniería y Ciencias Aplicadas (CIICAp-IICBA),
@@
   62209, México}
-\affil[2]{Instituto de Ciencias F\'isicas, Universidad Nacional
+\address[2]{Instituto de Ciencias F\'isicas, Universidad Nacional
   Autonóma de México, Av. Universidad S/N, Col. Chamilpa, 62210
   Cuernavaca, Morelos, México}
-\begin{document}
+\fntext[fn1]{On sabatical leave at ICF-UNAM from CIICAP-UAEM.}
+%\cortext[cor1]{Corresponding author}
+
+\begin{keywords}
+  Porous Silicon\sep GRIN \sep Reflectance Spectra.
+\end{keywords}
 
@@
 \begin{abstract}
-
 A variety of optical devices and applications may be based on layered
@@
 for manifold applications.
-
-Keywords: Porous Silicon; GRIN; Reflectance Spectra.
 \end{abstract}
@@
 \end{equation}
-where $\phi_{\bm G}(z)$ is the Fourier coefficient of the potential at
+where $\phi_{\bm G}(z)$ is the 2D Fourier coefficient of the potential at
 the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
@@
 The morphology of the etched porous layers (plan-view and
-cross-sectional) was observed using (SEM) scanning electron microscopy
-(Hitachi SU1510  High Technologies Canada,  Inc., Toronto, Canada).
+cross-sectional) was observed with a {\em Hitachi SU1510} scanning electron microscope
+(SEM).
+%High Technologies Canada,  Inc., Toronto, Canada).
 
@@
   \centering
-  \includegraphics[width=1.2\textwidth]{j_Ivsxy.png}
-  \includegraphics[width=\textwidth]{j_Ivsx.png}
+  \includegraphics[width=.8\textwidth]{j_Ivsxy.png}
+  \includegraphics[width=.6\textwidth]{j_Ivsx.png}
   \caption{Normalized current density $j_\perp(x,y,0)/I$ calculated a
@@
     on which we measured reflectance spectra. Here,
-    $x'_n=x_n+0.14\,\text{cm}$ is the position from the sealing o-ring.}
+    $x'_n=x_n+0.14\,\text{cm}$ is the position from the left side sealing o-ring.}
   \label{fig:SI3}
@@
 $w=0.14\,\text{cm}$. Thus, we may expect our formula \eqref{Eq:J}
-to fail within that region and close to the border, at distances of the order of the radius
-of the cross-section of the o-ring, of the order of a milimeter. The
+to {\em fail} within that region and close to the border, at distances of the order of the radius
+of the cross-section of the o-ring, about a milimeter. The
 figure shows eight positions
@@
 measured the near normal incidence reflection spectra of the
-sample. Here, we defined $x'_n=x_n+w$ as the distance to the sealing o-ring,
-where $x_n$ is the corresponding distance to the wall of the
+sample. Here, we defined $x'_n=x_n+w$ as the distance to the edge of
+the etched sample, determined by the position of the sealing o-ring,
+whereas $x_n$ is the corresponding distance to the wall of the
 cell.
@@
     panel, see text). We indicate with the numbers 1, 2, 3 the
-    data corresponding to the corresponding samples $G_1$, $G_2$ and
-    $G_3$.}
+    data corresponding to the corresponding samples $G_1$, $G_2$
+    (shifted, see text) and  $G_3$.}
   \label{fig:Rvsjl}
@@
 
-The theoretical reflectance could as well be calculated using
-\eqref{Eq:ECMR}-\eqref{eq:v} for more complicated structures, in which the
+The theoretical reflectance could as well be calculated using Eqs.
+\eqref{Eq:Brugg}-\eqref{eq:v} and a transfer matrix approach for more
+complicated structures, in which the
 current $I$ is modulated in time, allowing the design and analysis of
@@
 \label{sec:acknowledgments}
+CAOD is grateful for a scholarship from CONACyT and to
+V. Castillo-Gallardo for useful discussions. VA acknowledges support
+from CONACyT Basic Sciences project A-S1 30393 and from PRODEP, and is
+grateful to ICF where she spent a sabatical.
 WLM acknowledges the support of DGAPA-UNAM under grant
-IN111119. VA acknowledges support from CONACyT Basic Sciences project
-A-S1 30393 and from PRODEP, and is grateful to ICF where she spent a
-sabatical. CAOD is grateful for a scholarship from CONACyT.
+IN111119.
+
+\printcredits
+
 \bibliographystyle{unsrt}

### 2020-11-16 paper.tex
Finish formatting for Elsevier. Submit to SLMS.
Change title and journal in paper and cover letter

@@
 \begin{document}
-\shorttitle{Model for PS Structures with a Lateral Gradient}
+\shorttitle{Model for the ECh Sythesis of PS Structures with a Lateral Gradient}
 \shortauthors{Ospina-Delacruz et al.}
-\title[mode=title]{Model for Porous Silicon Structures with a Lateral Gradient}
-\author[1]{C. A. Ospina-Delacruz}[orcid=0000-0000-0000-0000]
+\title[mode=title]{Model for the Electrochemical Synthesis of Porous
+  Silicon Structures with a Lateral Gradient}
+\author[1]{C. A. Ospina-Delacruz}[orcid=0000-0002-9609-3031]
 \ead{crisalod@gmail.com}
@@
 \author[2]{W. L. Mochán}[type=editor,orcid=0000-0003-0418-5375]
-%\cormark[1]
+\cormark[cor1]
 \ead{mochan@fis.unam.mx}
@@
 \fntext[fn1]{On sabatical leave at ICF-UNAM from CIICAP-UAEM.}
-%\cortext[cor1]{Corresponding author}
+\cortext[cor1]{Corresponding author}
 
@@
 CAOD is grateful for a scholarship from CONACyT and to
-V. Castillo-Gallardo for useful discussions. VA acknowledges support
+V. Castillo-Gallardo and L.E. Puente Díaz for useful discussions. VA acknowledges support
 from CONACyT Basic Sciences project A-S1 30393 and from PRODEP, and is

### 2020-11-17 paper.tex
Change abstract

@@
 \begin{document}
-\shorttitle{Model for the ECh Sythesis of PS Structures with a Lateral Gradient}
+\shorttitle{Model of the Current Density in the Electrochemical
+  Synthesis of PS Structures with a Lateral Gradient}
 \shortauthors{Ospina-Delacruz et al.}
-\title[mode=title]{Model for the Electrochemical Synthesis of Porous
-  Silicon Structures with a Lateral Gradient}
+\title[mode=title]{Analytical Model for the Current Density in
+the Electrochemical Synthesis of Porous Silicon Structures with a
+Lateral Gradient}
 \author[1]{C. A. Ospina-Delacruz}[orcid=0000-0002-9609-3031]
@@
 \author[2]{W. L. Mochán}[type=editor,orcid=0000-0003-0418-5375]
-\cormark[cor1]
+\cormark[1]
 \ead{mochan@fis.unam.mx}
@@
 \cortext[cor1]{Corresponding author}
-
 \begin{keywords}
-  Porous Silicon\sep GRIN \sep Reflectance Spectra.
+  Porous Silicon\sep GRIN \sep Reflectance Spectra.\sep
 \end{keywords}
-
 \maketitle
-
 \begin{abstract}
-A variety of optical devices and applications may be based on layered
-systems which have a lateral gradient in both their refractive indices
-and their thicknesses. They may be fabricated of porous silicon (PS) through an
-electrochemical process in which the etching current depends on position. Thus, the possibility of
-predicting the local current density $j$ and the corresponding
-porosity $p$ and etching rate $v$ would be desirable for a systematic design of these
-structures. In this work, we propose a
-simple model for the calculation of $j$
-as a function of position within an electrochemical cell. We prepared
-some graded single layer PS samples, measured their optical properties through
-ultraviolet-visible-near infrared reflectance
-spectroscopy, and related them
-to their local porosity and thickness which, together with our model, were then used to obtain
-the $p$ vs. $j$ and $v$ vs. $j$ calibration curves.  The dependence of
-porosity and thickness with position was corroborated through scanning electron microscopy. We
-compared the calibration curves for different samples. Thus, from
-measurements on only one, or a few simple systems, we may obtain full
-calibration curves which may be used to predict, design, and fabricate
-more complex novel non-homogenous devices with lateral gradients which can be used
-for manifold applications.
+  A variety of optical devices and applications are based on
+  layered systems which have a lateral gradient in both their
+  refractive indices and their thicknesses. Simple fabrication of such
+  systems can be carried out through the electrochemical synthesis of
+  porous silicon (PS) using an etching current with a density $\bm
+  j(\bm r_\|)$ that has a spatial variation along the surface of the
+  sample. Thus, the possibility of predicting the local
+  value of $\bm j(\bm r_\|)$ and the corresponding values of the porosity
+  $p(\bm r_\|)$ and the etching rate $v(\bm r_\|)$ is desirable for a
+  systematic design of these structures.
+  In this work, we propose a simple analytical model based on a simple
+  fast converging planewise summation of Coulomb potentials in two
+  dimensional reciprocal space for the
+  calculation of $\bm j(\bm r_\|)$ as a function of position
+  within a prism shaped electrochemical cell. Some graded single layer PS samples
+  were synthesized and their optical reflectance were used to
+  estimate their local porosity $p(\bm r_\|)$ and thickness $d(\bm r_\|)$
+  which, together with our model, were then used to obtain the basic
+  calibration curves $p$ vs $\bm j$ and $v$ vs $\bm j$.
+  The dependence of porosity and thickness with position was
+  corroborated through scanning electron microscopy.
+  Agreement was found between the calibration curves from
+  different samples. Thus, from measurements on only one system, full
+  calibration curves may be obtained and used to predict, design, and
+  fabricate more complex novel non-homogenous multilayered devices with lateral
+  gradients which can be used for manifold applications.
+
 \end{abstract}

### 2020-11-17 paper.tex
Insert and correct new abstract by Vivechna

@@
   systematic design of these structures.
-  In this work, we propose a simple analytical model based on a simple
+  In this work, we propose a simple analytical model based on a
   fast converging planewise summation of Coulomb potentials in two
@@
   Agreement was found between the calibration curves from
-  different samples. Thus, from measurements on only one system, full
-  calibration curves may be obtained and used to predict, design, and
-  fabricate more complex novel non-homogenous multilayered devices with lateral
-  gradients which can be used for manifold applications.
-
+  different samples. Thus, from measurements on only one sample, our
+  model allows us to obtain full calibration curves which may be
+  used to predict, design, and fabricate more complex novel
+  non-homogenous multilayered devices with lateral gradients for
+  manifold applications.
 \end{abstract}

### 2020-11-17 paper.tex
Don't pluralize thickness

@@
   layered systems which have a lateral gradient in both their
-  refractive indices and their thicknesses. Simple fabrication of such
+  refractive indices and their thickness. Simple fabrication of such
   systems can be carried out through the electrochemical synthesis of

### 2020-11-17 paper.tex
Shorten abstract to 150 words

@@
 \begin{abstract}
-  A variety of optical devices and applications are based on
-  layered systems which have a lateral gradient in both their
-  refractive indices and their thickness. Simple fabrication of such
-  systems can be carried out through the electrochemical synthesis of
-  porous silicon (PS) using an etching current with a density $\bm
-  j(\bm r_\|)$ that has a spatial variation along the surface of the
-  sample. Thus, the possibility of predicting the local
-  value of $\bm j(\bm r_\|)$ and the corresponding values of the porosity
-  $p(\bm r_\|)$ and the etching rate $v(\bm r_\|)$ is desirable for a
-  systematic design of these structures.
-  In this work, we propose a simple analytical model based on a
-  fast converging planewise summation of Coulomb potentials in two
-  dimensional reciprocal space for the
-  calculation of $\bm j(\bm r_\|)$ as a function of position
-  within a prism shaped electrochemical cell. Some graded single layer PS samples
-  were synthesized and their optical reflectance were used to
-  estimate their local porosity $p(\bm r_\|)$ and thickness $d(\bm r_\|)$
-  which, together with our model, were then used to obtain the basic
-  calibration curves $p$ vs $\bm j$ and $v$ vs $\bm j$.
-  The dependence of porosity and thickness with position was
-  corroborated through scanning electron microscopy.
-  Agreement was found between the calibration curves from
-  different samples. Thus, from measurements on only one sample, our
-  model allows us to obtain full calibration curves which may be
-  used to predict, design, and fabricate more complex novel
+  Layered optical devices with a lateral gradient
+  can be fabricated through electrochemical synthesis of
+  porous silicon (PS) using a position dependent etching current
+  density  $\bm j(\bm r_\|)$. Predicting the local
+  value of $\bm j(\bm r_\|)$ and the corresponding porosity
+  $p(\bm r_\|)$ and etching rate $v(\bm r_\|)$ is desirable for their
+  systematic design.
+  We develop a simple analytical model for the
+  calculation of $\bm j(\bm r_\|)$ within a prism shaped
+  cell. Graded single layer PS samples
+  were synthesized and their local calibration curves $p$ vs $\bm j$ and $v$
+  vs $\bm j$ were obtained from our model and their reflectance spectra.
+  The agreement found between the calibration curves from
+  different samples shows that from one sample we
+  could obtain full calibration curves which may be
+  used to predict, design, and fabricate more complex
   non-homogenous multilayered devices with lateral gradients for
@@
 \end{abstract}
+%  A variety of optical devices and applications are based on
+%  layered systems which have a lateral gradient in both their
+%  refractive indices and their thickness. Simple fabrication of such
+%  systems can be carried out through the electrochemical synthesis of
+%  porous silicon (PS) using an etching current with a density $\bm
+%  j(\bm r_\|)$ that has a spatial variation along the surface of the
+%  sample. Thus, the possibility of predicting the local
+%  value of $\bm j(\bm r_\|)$ and the corresponding values of the porosity
+%  $p(\bm r_\|)$ and the etching rate $v(\bm r_\|)$ is desirable for a
+%  systematic design of these structures.
+%  In this work, we propose a simple analytical model based on a
+%  fast converging planewise summation of Coulomb potentials in two
+%  dimensional reciprocal space for the
+%  calculation of $\bm j(\bm r_\|)$ as a function of position
+%  within a prism shaped electrochemical cell. Some graded single layer PS samples
+%  were synthesized and their optical reflectance were used to
+%  estimate their local porosity $p(\bm r_\|)$ and thickness $d(\bm r_\|)$
+%  which, together with our model, were then used to obtain the basic
+%  calibration curves $p$ vs $\bm j$ and $v$ vs $\bm j$.
+%  The dependence of porosity and thickness with position was
+%  corroborated through scanning electron microscopy.
+%  Agreement was found between the calibration curves from
+%  different samples. Thus, from measurements on only one sample, our
+%  model allows us to obtain full calibration curves which may be
+%  used to predict, design, and fabricate more complex novel
+%  non-homogenous multilayered devices with lateral gradients for
+%  manifold applications.
 

### 2020-11-23 paper.tex
Change caption of fig 5

@@
   \centering
-  \includegraphics[width=.8\textwidth]{j_Ivsxy.png}
-  \includegraphics[width=.6\textwidth]{j_Ivsx.png}
-  \caption{Normalized current density $j_\perp(x,y,0)/I$ calculated a
-    the surface of the sample through
-    Eq. (\ref{Eq:J}) for a
-    system as in Figs. \ref{f:celda} and \ref{fig:DE1} for a cell of
+  \begin{picture}(400,300)
+    \put(0,0){\includegraphics[width=.8\textwidth]{j_Ivsx.png}}
+    \put(160,140){\includegraphics[trim=50 50 70 80,clip,width=.4\textwidth]{j_Ivsxy.png}}
+  \end{picture}
+  \caption{Normalized current density $j_\perp(x,y,0)/I$ for a system
+    as in Figs. \ref{f:celda} and \ref{fig:DE1} for a cell of
     length $a = 2.01\,\text{cm}$ and width $b=1.48\,\text{cm}$, with
@@
     point-like electrode at $\bm r_0=(0.2\,\text{cm},
-    0.74\,\text{cm},0.9\,\text{cm})$ (top panel). Normalized current
-    along the center line $y=0.74\,\text{cm}$ (bottom
-    panel).}
+    0.74\,\text{cm},0.9\,\text{cm})$,  calculated through
+    Eq. (\ref{Eq:J}) along the center line
+    $y=0.74\,\text{cm}$. Inset: current over the whole surface.}
   \label{fig:DR1}

### 2020-12-22 paper.tex
Add panel letters to fig. 4

@@
 
-  \caption{Schematic experimental set-up for
+  \caption{(a): Schematic experimental set-up for
     the fabrication of GRIN PS structures. We show a side view of the
     electrochemical cell with the shape of a
-    rectangular prism (top panel). We indicate the Si wafer (dark
+    rectangular prism. We indicate the Si wafer (dark
     gray), the teflon cell (light gray), the sealing o-ring (black
@@
     and a few schematic current flux
-    lines. Top and side schematic views of the resulting sample
-    (middle and lower panels),
+    lines. (b) and (c): Top and side schematic views of expected resulting sample
     illustrating eight regions $1\ldots8$ of decreasing porosity and thickness,

### 2020-12-22 paper.tex
Add remark to avoid confusion about micrographs

@@
 %\usepackage[usenames]{color}
-%\usepackage{showkeys}
+\usepackage{showkeys}
 %\usepackage{ieeetr}
@@
 along its centerline (see Sec. \ref{sec:R}) from
-three regions around to the left side, the center, and the right side
+three regions around the left side, the center, and the right side
 of the sample shown in Fig. \ref{fig:SI3}.
@@
 size and pore density diminish (panels (a) to (c) of
-Fig. \ref{fig:sem}) and the sample becomes much thinner (panels (d) to (f)).
+Fig. \ref{fig:sem}) and the sample becomes much thinner (panels (d) to
+(f)). We remark that these micrographs were taken at three positions
+that do not correspond to the eight locations at which we measured the
+optical spectra. Thus, we didn't use them to obtain quantitatively the
+thickness nor the porosity of the PS layer, but to verify
+qualitative our expected results (Fig. \ref{fig:DE1}) and our
+actual results (Table \ref{t:jpdv}) obtained from our calculation and
+the optical spectra, as explained below.
 

### 2020-12-22 paper.tex
Mention that in fig. 5 the current is normalized.
Change G_n->S_n in text and figures

@@
 y_0,z_0)=(0.2\,\text{cm},0.74\,\text{cm},0.9\,\text{cm})$.
-We manufactured three samples $G_1$, $G_2$ and $G_3$ by applying a
+We manufactured three samples $S_1$, $S_2$ and $S_3$ by applying a
 current $I_1=5\,\text{mA}$, $I_2=10\,\text{mA}$ and
@@
 \end{figure}
-In Fig. \ref{fig:DR1} we show the current density $j_\perp(x,y,0)$ calculated through
+In Fig. \ref{fig:DR1} we show the normalized current density $j_\perp(x,y,0)/I$ calculated through
 Eq. \eqref{Eq:J} at the surface of the sample for our cell, as shown
@@
  \includegraphics[width=\textwidth]{G3I20proc}
-  \caption{ Photograph of sample $G_3$ prepared as described in
+  \caption{ Photograph of sample $S_3$ prepared as described in
     Sec. \ref{sec:fabrication-ps-grin} using the same parameters as
@@
 In Fig. \ref{fig:SI3} we show a photograph of one of our samples,
-$G_3$
+$S_3$
 prepared as described in Sec. \ref{sec:fabrication-ps-grin}, with the
@@
 
-In Fig. \ref{fig:sem} we show some SEM images of the sample $G_3$,
+In Fig. \ref{fig:sem} we show some SEM images of the sample $S_3$,
 including top views and lateral views taken after
@@
   \caption{Top ((a), (b), and (c)) and lateral ((d), (e), and (f)) SEM
-    micrographs of the sample $G_3$ taken from a region corresponding to the left
+    micrographs of the sample $S_3$ taken from a region corresponding to the left
     side ((a) and (d)), center ((b) and (e)), and right side ((c) and
@@
     ($x'_n=0.2-1.6\,\text{cm}$, $y=0.74\,\text{cm}$)
-    on sample $G_1$ ($I_1=5\,\text{mA}$). We show
+    on sample $S_1$ ($I_1=5\,\text{mA}$). We show
   experimental results and results fitted through
@@
     ($x'_n=0.2-1.6\,\text{cm}$, $y=0.74\,\text{cm}$)
-    on sample $G_2$ ($I_1=10\,\text{mA}$). We show
+    on sample $S_2$ ($I_1=10\,\text{mA}$). We show
   experimental results and results fitted through
@@
     ($x'_n=0.2-1.6\,\text{cm}$, $y=0.74\,\text{cm}$)
-    on sample $G_3$ ($I_3=20\,\text{mA}$) (Fig. \ref{fig:SI3}),
+    on sample $S_3$ ($I_3=20\,\text{mA}$) (Fig. \ref{fig:SI3}),
     We show
@@
 We measured the reflectance spectra  at the positions indicated in
-Fig. \ref{fig:SI3} on our three samples $G_1$, $G_2$,
-and $G_3$, prepared using the same procedure
+Fig. \ref{fig:SI3} on our three samples $S_1$, $S_2$,
+and $S_3$, prepared using the same procedure
 (Sec. \ref{sec:fabrication-ps-grin}) but applying different currents
@@
 \hline
-$G_1$/ 5 &0.2 & 3.61 & 0.494 & 0.340 & 0.849&  1.361 \\
+$S_1$/ 5 &0.2 & 3.61 & 0.494 & 0.340 & 0.849&  1.361 \\
          &0.4 & 3.36 & 0.571 & 0.390 & 0.979&  1.558  \\
@@
          &1.6 & 0.83 & 0.552 & 0.124 & 0.990&  0.495 \\
-$G_2$/10 &0.2 & 7.22 & 0.591 & 0.635 & 0.856&  2.539 \\
+$S_2$/10 &0.2 & 7.22 & 0.591 & 0.635 & 0.856&  2.539 \\
          &0.4 & 6.72 & 0.644 & 0.693 & 0.991&  2.774 \\
@@
          &1.6 & 1.67 & 0.571 & 0.296 & 0.948&  1.183 \\
-$G_3$/20 &0.2 &14.45 & 0.686 & 1.204 & 1.149&  4.818 \\
+$S_3$/20 &0.2 &14.45 & 0.686 & 1.204 & 1.149&  4.818 \\
          &0.4 & 13.44 & 0.713 & 1.193 & 1.078&  4.772 \\
@@
   \caption{Porosity as a function of current density for three samples
-    $G_1$, $G_2$, $G_3$. The data points for each sample are joined by
+    $S_1$, $S_2$, $S_3$. The data points for each sample are joined by
     thick lines. The arrows point to data that correspond to
@@
     lines (see text). We include linear fits to the data from
-    sample $G_3$ (thick straight line) and to that from all the
+    sample $S_3$ (thick straight line) and to that from all the
     samples (thin straight line). }
@@
 For this reason, we exclude those points from the following
-analysis. We made a linear fit to the data from sample $G_3$ and to
+analysis. We made a linear fit to the data from sample $S_3$ and to
 the data from the three samples. A comparison shows that a fit to the
-data of just one sample, $G_3$, turns out to be a reasonable predictor for the
+data of just one sample, $S_3$, turns out to be a reasonable predictor for the
 porosity of all the samples.  From that fit we obtain that for our
@@
   \caption{Etching rate as a function of current density for three samples
-    $G_1$, $G_2$, $G_3$. The data points for each sample are joined by
+    $S_1$, $S_2$, $S_3$. The data points for each sample are joined by
     thick lines. The arrows point to data that correspond to
@@
 may all be approximated by a linear fit to the data of just one
-sample, $G_3$, from which we get
+sample, $S_3$, from which we get
 \begin{equation}\label{eq:v}
@@
     panel, see text). We indicate with the numbers 1, 2, 3 the
-    data corresponding to the corresponding samples $G_1$, $G_2$
-    (shifted, see text) and  $G_3$.}
+    data corresponding to the corresponding samples $S_1$, $S_2$
+    (shifted, see text) and  $S_3$.}
   \label{fig:Rvsjl}
@@
 eliminated the data corresponding to position $x'_1$ on all
-samples. Furthermore, as the results corresponding to sample $G_2$ in
+samples. Furthermore, as the results corresponding to sample $S_2$ in
 Figs. \ref{fig:p} and  \ref{fig:v} seem shifted with respect to those

### 2020-12-22 paper.tex
Add corrections about linear fit.

@@
 
-From the data in Table \ref{t:jpdv} we can plot the fitted porosity as
-a function of the calculated density current, as shown for our three
+From the data in Table \ref{t:jpdv} we can plot the fitted porosity vs.
+the calculated density current, as shown for our three
 samples in Fig. \ref{fig:p}.
@@
   \includegraphics[width=\textwidth]{pvsj}
-  \caption{Porosity as a function of current density for three samples
+  \caption{Porosity vs. current density for the three samples
     $S_1$, $S_2$, $S_3$. The data points for each sample are joined by
@@
     position $x'_1=0.2\,\text{cm}$, joined to the other data by thin
-    lines (see text). We include linear fits to the data from
-    sample $S_3$ (thick straight line) and to that from all the
-    samples (thin straight line). }
+    lines (see text). We include linear fits of the form
+    $p=mj_\perp+b$ to the data from
+    sample $S_3$ (thick straight line, with parameters $m=0.0134$ and
+    $b=0.5288$) and to that from all the samples (thin straight line). }
   \label{fig:p}
@@
 For this reason, we exclude those points from the following
-analysis. We made a linear fit to the data from sample $S_3$ and to
+analysis. We made a linear fit of the form $p=mj_\perp+b$ to the data from sample $S_3$ and to
 the data from the three samples. A comparison shows that a fit to the

### 2020-12-28 paper.tex
Advance in the reply

@@
   \centering
-  \includegraphics[width=\textwidth]{pvsj}
+  \includegraphics[width=\textwidth]{pvsjerr}
   \caption{Porosity vs. current density for the three samples
@@
 
-Similarly, we can plot the fitted etching rate as
-a function of the calculated density current, as shown for our three
+Similarly, we can plot the fitted etching rate vs.
+the calculated density current, as shown for our three
 samples in Fig. \ref{fig:v}.
@@
   \centering
-  \includegraphics[width=\textwidth]{vvsj}
-  \caption{Etching rate as a function of current density for three samples
+  \includegraphics[width=\textwidth]{vvsjerr}
+  \caption{Etching rate vs. current density for three samples
     $S_1$, $S_2$, $S_3$. The data points for each sample are joined by
@@
     position $x'_1=0.2\,\text{cm}$, joined to the other data by thin
-    lines (see text). We include linear fits to the data from
-    sample $S_3$ (thick straight line) and to that from all the
-    samples (thin straight line). }
+    lines (see text). We include linear fits of the form
+    $v=mj_\perp+b$ to the data from
+    sample $S_3$ (thick straight line, with parameters $m=0.3543$,
+    $b=0.0924$) and to that from all the samples (thin straight line). }
   \label{fig:v}

### 2020-12-29 paper.tex
Change reflectance plots by migrad fits
Include position uncertainty
Advance in the reply to the referee

@@
   used to predict, design, and fabricate more complex
-  non-homogenous multilayered devices with lateral gradients for
+  non-homogeneous multilayered devices with lateral gradients for
   manifold applications.
@@
 technological applications such as high-yield screening of catalysts,
-sensing materials and biomolecules \cite{maier2007combinatorial, jayaraman2004construction,
+sensing materials and bio-molecules \cite{maier2007combinatorial, jayaraman2004construction,
 potyrailo2008combinatorial}
-Apart from some methods developed by S.E. Fosdick et al \cite{fosdick2010two},
+Apart from some methods developed by S.E. Fosdick et al. \cite{fosdick2010two},
 %[JACS  2010, 132, 9226-9227],
@@
 on gold electrodes have also been obtained \cite{wang2019fabrication}.
-Among electrochemical methods, compositional and doping density changes
-in  conducting polymers have been used to produce gradients using Indium Tin
+Among electrochemical methods, changes in the composition and doping density
+of  conducting polymers have been used to produce gradients using Indium Tin
 Oxide electrodes \cite{inagi2010bipolar}.
@@
 This technique has the additional advantage of being compatible
-with very large scale integration (VLSI) devices and integrable with microelectronics.
+with very-large-scale-integration (VLSI) devices that may be
+integrated in  microelectronic circuits.
 
 Although porous silicon (PS) initially stimulated the interest of the scientific
-community due to its photoluminescence in the visible range at room
+community due to its photo-luminescence in the visible range at room
 temperature, it has presently
 been recognized as a multifaceted optical material due to its large surface
-area, biocompatibility, ease of fabrication and tunable refractive index.
+area, bio-compatibility, ease of fabrication and tunable refractive index.
 Applications based on porous silicon now cover various fields such as
 chemical sensors and biosensors \cite{kumar2020porous},
-microelectronics and micromechanical systems (MEMS) \cite{martinez2016dual},as well as a
-range of optical \cite{estevez2014porous} and optoelectronic applications
+microelectronics and micro-mechanical systems (MEMS)
+\cite{martinez2016dual}, as well as a
+range of optical \cite{estevez2014porous} and opto-electronic applications
 \cite{ramadan2020fabrication}. Specifically,
@@
 Additionally, a variation in pH of the solution could gate the
-trapping/release of biomolecules at regions with different porosity, a
+trapping/release of bio-molecules at regions with different porosity, a
 result potentially useful for drug delivery
-applications given the biocompatible nature of PS.
+applications given the bio-compatible nature of PS.
 A similar asymmetric electrode configuration was used to fabricate
@@
 Additionally, it has been shown that the combination of thermal  oxidation  and
-infiltration of TiO2  by atomic layer deposition allows the manufacture
+infiltration of TiO$_2$  by atomic layer deposition allows the manufacture
 of transparent GRIN
@@
 a porous silicon 1D GRIN structure infiltrated with polymer to
-synthesize flat microlens arrays.
+synthesize flat micro-lens arrays.
 Recently, J Wang et al. has shown the fabrication of
@@
 within the region $0\le x\le a$, $0\le y \le b$, $0\le z\le c$
-with that within an infinite fictitious empty space but for the point charge
+with that within an infinite fictitious space  empty but for the point charge
 $q_0$ at the tip of the electrode at $\bm r_0$, and an array of its fictitious image
@@
 current density on the surface of the sample on which  no
-real nor image charges lie, we may perform a somewhat simpler planewise
+real nor image charges lie, we may perform a somewhat simpler plane-wise
 summation, where we first obtain the potential and field produced by a
@@
 We consider first a system made of identical {\em unit} charges
-ocuppying the positions $\bm R$ of a 2D Bravais lattice $\{\bm R\}$,
+occupying the positions $\bm R$ of a 2D Bravais lattice $\{\bm R\}$,
 which we will take as a rectangular lattice with lattice parameters
@@
  \end{eqnarray}
-where the prime indicates that the term $G=0$ should be ommited from
+where the prime indicates that the term $G=0$ should be omitted from
 the sum.
@@
 four positions $(\pm x_0, \pm y_0,0)$. Each of the corresponding four
-sublattices produces a potential as that in Eq. \eqref{eq:phiG1} but
+sub-lattices produces a potential as that in Eq. \eqref{eq:phiG1} but
 shifted by the corresponding basis vector, yielding
@@
     rectangular prism. We indicate the Si wafer (dark
-    gray), the teflon cell (light gray), the sealing o-ring (black
+    gray), the Teflon cell (light gray), the sealing o-ring (black
     circles), the insulated feeding cable (white lines within black
@@
 (resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
-conditions. The process was performed at room temperatured with an
+conditions. The process was performed at room temperature with an
 electrolytic mixture of aqueous hydrofluoric
@@
 platinum wire with a diameter of $0.41\,\text{mm}$ insulated with
-teflon tape, with an uncovered
+Teflon tape, with an uncovered
 tip located at $\bm r_0=(x_0,
@@
 samples using Universal reflectance accessory  equipped {\em Perkin Elmer Lambda 950}
-ultraviolet-visible-near infrared (UV-Vis-NIR) spectrophotometer, with a rectangular spot size of
+ultraviolet-visible-near infrared (UV-Vis-NIR) spectro-photometer, with a rectangular spot size of
 $0.7\text{mm}\times2.0\text{mm}$, a slit width of $0.6\text{mm}$ in
@@
 and $\psi=k_1^\perp d$, where $k_1^\perp$ is
-the component of the wavevector perpendicular to the surface within
+the component of the wave-vector perpendicular to the surface within
 the porous layer of thickness $d$. The reflectance depends on the
@@
 where $\epsilon_2=\epsilon_{\text{Si}}$ is the dielectric function of
-the c-Si substrate, and
+the c-Si substrate and
 $\epsilon_1=n_{\text{PS}}^2$ is the dielectric function of the PS layer.
@@
 
-\section{Discussion and Results}
+\section{Results and Discussion}
 \label{sec:discussion-results}
@@
     length $a = 2.01\,\text{cm}$ and width $b=1.48\,\text{cm}$, with
-    the surface of the electrolyte at a heigth $c=1.0\,\text{cm}$, with a
+    the surface of the electrolyte at a height $c=1.0\,\text{cm}$, with a
     point-like electrode at $\bm r_0=(0.2\,\text{cm},
@@
     in Fig. \ref{fig:DR1} with a current $ I_3=20 \text{mA}$,
-    during a time $t=250\text{s}$. We indicate the centerline with a
+    during a time $t=250\text{s}$. We indicate the center-line with a
     dashed line and eight regions $x_i$
@@
 to {\em fail} within that region and close to the border, at distances of the order of the radius
-of the cross-section of the o-ring, about a milimeter. The
+of the cross-section of the o-ring, about a millimeter. The
 figure shows eight positions
@@
 sample. Here, we defined $x'_n=x_n+w$ as the distance to the edge of
-the etched sample, determined by the position of the sealing o-ring,
+the etched sample, which corresponds to the position of the sealing o-ring,
 whereas $x_n$ is the corresponding distance to the wall of the
@@
 normalized current density $j_\perp/I$ expected at the positions $n$ indicated in
-Fig. \ref{fig:SI3}.
+Fig. \ref{fig:SI3}. We included an estimated uncertainty in the
+distance to the wall of the cell, and the corresponding (asymmetrical)
+uncertainty in the computed current density. This
+uncertainty arises from the uncontrolled deformation of the o-ring as
+it is pressed against the wafer to seal in the electrolyte, so that
+its distance to the wall of the cell is ill defined, and we estimate
+it as the radius of the o-ring. \notaL{Would it be a good idea to use a
+  larger uncertainty? 1mm? The beam spot is 2mm wide.}
 (Table \ref{t:xj}).
@@
   \centering
+  \renewcommand{\arraystretch}{1.1}
    \begin{tabular}{rrr}
@@
      \hline
-    0.2 & 0.06 & 0.722\\
-    0.4 & 0.26 & 0.672\\
-    0.6 & 0.46 & 0.577\\
-    0.8 & 0.66 & 0.464\\
-    1.0 & 0.86 & 0.360\\
-    1.2 & 1.06 & 0.275\\
-    1.4 & 1.26 & 0.211\\
-    1.6 & 1.46 & 0.167\\
+     0.2 &$ 0.06\pm0.05$ & $0.722^{+0.003}_{-0.007}$\\
+     0.4 &$ 0.26\pm0.05$ & $0.672^{+0.018}_{-0.021}$\\
+     0.6 &$ 0.46\pm0.05$ & $0.577^{+0.027}_{-0.028}$\\
+     0.8 &$ 0.66\pm0.05$ & $0.464^{+0.028}_{-0.028}$\\
+     1.0 &$ 0.86\pm0.05$ & $0.360^{+0.025}_{-0.023}$\\
+     1.2 &$ 1.06\pm0.05$ & $0.275^{+0.019}_{-0.018}$\\
+     1.4 &$ 1.26\pm0.05$ & $0.211^{+0.014}_{-0.013}$\\
+     1.6 &$ 1.46\pm0.05$ & $0.167^{+0.010}_{-0.009}$\\
   \end{tabular}
@@
 the optical characterization was completed and the sample was cut
-along its centerline (see Sec. \ref{sec:R}) from
+along its center-line (see Sec. \ref{sec:R}) from
 three regions around the left side, the center, and the right side
@@
     side ((a) and (d)), center ((b) and (e)), and right side ((c) and
-    (f)) along the centerline shown in Fig. \ref{fig:SI3}.}
+    (f)) along the center-line shown in Fig. \ref{fig:SI3}.}
   \label{fig:sem}
@@
   \centering
-  \includegraphics[width=\textwidth]{R5vslambda}
+  \includegraphics[width=\textwidth]{R5migradvslambda}
   \caption{Reflectance spectra at different positions
@@
   \centering
-  \includegraphics[width=\textwidth]{R10vslambda}
+  \includegraphics[width=\textwidth]{R10migradvslambda}
   \caption{Reflectance spectra at different positions
@@
   \centering
-  \includegraphics[width=\textwidth]{R20vslambda}
+  \includegraphics[width=\textwidth]{R20migradvslambda}
   \caption{Reflectance spectra at different positions
@@
 film  $d$ as
-adjustable parameters. We also fitted a scaling parameter $s$ to allow
-for calibration variations among spectra. From the thickness we
+adjustable parameters. To that end we used the {\tt migrad} routine of
+the {\tt Minuit} minimization software. From the thickness we
 obtained the etching rate $v=d/t$ at each position. Notice that the fits are reasonably
@@
 The results obtained from the reflectance fits are summarized in table
-\ref{t:jpdv}. Notice that the scaling parameters are close to 1,
-showing that the calibration was adequate.
-
+\ref{t:jpdv}.
 \begin{table}
 \centering
-\begin{tabular}{lrrrrrr}
-  Sample/ & position & density & porosity &
-  thickness & scale & rate\\
-  $I$ (mA) &$x'_n$ (cm)&  $j$ ($\text{mA}/\text{cm}^2$) & $p$
-       & $d$ ($\mu\text{m}$) & $s$ & $v$ (nm/s)\\
+\renewcommand{\arraystretch}{1.1}
+\begin{tabular}{lrrrrr}
+  Sample & position & density & porosity &
+  thickness & rate\\
+  ($I$ (mA)) &$x'_n$ (cm)&  $j$ ($\text{mA}/\text{cm}^2$) & $p$
+       & $d$ ($\mu\text{m}$) & $v$ (nm/s)\\
 \hline
-$S_1$/ 5 &0.2 & 3.61 & 0.494 & 0.340 & 0.849&  1.361 \\
-         &0.4 & 3.36 & 0.571 & 0.390 & 0.979&  1.558  \\
-         &0.6  & 2.88& 0.566 & 0.331 & 0.957&  1.325 \\
-         &0.8 & 2.32 & 0.556 & 0.273 & 0.954&  1.093 \\
-         &1.0 & 1.80 & 0.559 & 0.227 & 0.995&  0.894 \\
-         &1.2 & 1.37 & 0.556 & 0.189 & 0.973&  0.754 \\
-         &1.4 & 1.06 & 0.549 & 0.151 & 0.961&  0.605 \\
-         &1.6 & 0.83 & 0.552 & 0.124 & 0.990&  0.495 \\
-$S_2$/10 &0.2 & 7.22 & 0.591 & 0.635 & 0.856&  2.539 \\
-         &0.4 & 6.72 & 0.644 & 0.693 & 0.991&  2.774 \\
-         &0.6 & 5.77 & 0.638 & 0.591 & 0.952&  2.363 \\
-         &0.8 & 4.64 & 0.626 & 0.533 & 0.980&  2.131 \\
-         &1.0 & 3.60 & 0.599 & 0.459 & 0.939&  1.835 \\
-         &1.2 & 2.75 & 0.590 & 0.404 & 0.945&  1.618 \\
-         &1.4 & 2.11 & 0.575 & 0.338 & 0.936&  1.351 \\
-         &1.6 & 1.67 & 0.571 & 0.296 & 0.948&  1.183 \\
-$S_3$/20 &0.2 &14.45 & 0.686 & 1.204 & 1.149&  4.818 \\
-         &0.4 & 13.44 & 0.713 & 1.193 & 1.078&  4.772 \\
-         &0.6 & 11.54 & 0.703 & 1.044 & 1.059&  4.177 \\
-         &0.8 &  9.29 & 0.626 & 0.752 & 1.006&  3.006 \\
-         &1.0 &  7.20 & 0.625 & 0.538 & 1.010&  2.152  \\
-         &1.2 &  5.50 & 0.593 & 0.439 & 0.962&  1.755 \\
-         &1.4 &  4.22 & 0.584 & 0.363 & 0.962&  1.453 \\
-         &1.6 &  3.33 & 0.591 & 0.339 & 1.011&  1.357 \\
+$S_1$(5) &0.2 &$ 3.61^{+0.014}_{-0.03}  $&$0.562\pm0.031$ &$0.381\pm0.021$ &$   1.524\pm0.084$ \\
+         &0.4 &$ 3.36^{+0.09}_{-0.11}   $&$0.588\pm0.019$ &$0.403\pm0.014$ &$  1.611\pm0.057$  \\
+         &$0.6$  &$ 2.88^{+0.13}_{-0.14}$&$0.582\pm0.024$ &$0.342\pm0.015$ &$   1.366\pm0.060$ \\
+         &$0.8$ &$ 2.32^{+0.14}_{-0.14} $&$0.566\pm0.022$ &$0.278\pm0.011$ &$  1.113\pm0.044$ \\
+         &$1.0$ &$ 1.80^{+0.13}_{-0.12} $&$0.561\pm0.021$ &$0.224\pm0.009$ &$  0.897\pm0.034$ \\
+         &$1.2$ &$ 1.37^{+0.10}_{-0.09} $&$0.561\pm0.019$ &$0.190\pm0.007$ &$  0.761\pm0.027$ \\
+         &$1.4$ &$ 1.06^{+0.07}_{-0.06} $&$0.556\pm0.018$ &$0.153\pm0.005$ &$  0.611\pm0.021$ \\
+         &$1.6$ &$ 0.83^{+0.05}_{-0.04} $&$0.556\pm0.016$ &$0.124\pm0.004$ &$  0.497\pm0.016$ \\
+$S_2$(10) &$0.2$ &$ 7.22^{+0.03}_{-0.07} $&$0.635\pm0.040$ &$0.686\pm0.054$ &$  2.744\pm0.216$ \\
+         &$0.4$ &$ 6.72^{+0.02}_{-0,21} $&$0.644\pm0.018$ &$0.694\pm0.025$ &$  2.777\pm0.101$ \\
+         &$0.6$ &$ 5.77^{+0.27}_{-0.28} $&$0.640\pm0.033$ &$0.592\pm0.037$ &$  2.368\pm0.149$ \\
+         &$0.8$ &$ 4.64^{+0.28}_{-0.28} $&$0.624\pm0.034$ &$0.530\pm0.034$ &$  2.118\pm0.138$ \\
+         &$1.0$ &$ 3.60^{+0.25}_{-0.23} $&$0.612\pm0.030$ &$0.470\pm0.027$ &$  1.879\pm0.107$ \\
+         &$1.2$ &$ 2.75^{+0.19}_{-0.18} $&$0.603\pm0.034$ &$0.414\pm0.026$ &$  1.658\pm0.104$ \\
+         &$1.4$ &$ 2.11^{+0.14}_{-0.13} $&$0.594\pm0.028$ &$0.350\pm0.018$ &$  1.401\pm0.073$ \\
+         &$1.6$ &$ 1.67^{+0.10}_{-0.09} $&$0.583\pm0.024$ &$0.302\pm0.014$ &$  1.207\pm0.054$ \\
+$S_3$(20) &$0.2$ &$14.45^{+0.06}_{-0.14} $&$0.688\pm0.019$ &$1.208\pm0.047$ &$  4.834\pm0.188$ \\
+         &$0.4$ &$ 13.44^{+0.35}_{-0.41}$&$0.718\pm0.024$ &$1.205\pm0.057$ &$  4.820\pm0.228$ \\
+         &$0.6$ &$ 11.54^{+0.53}_{-0.55}$&$0.706\pm0.027$ &$1.050\pm0.058$ &$  4.199\pm0.232$ \\
+         &$0.8$ &$  9.29^{+0.57}_{-0.55}$&$0.636\pm0.063$ &$0.766\pm0.088$ &$  3.063\pm0.354$ \\
+         &$1.0$ &$  7.20^{+0.49}_{-0.47}$&$0.626\pm0.035$ &$0.540\pm0.037$ &$  2.158\pm0.147$  \\
+         &$1.2$ &$  5.50^{+0.38}_{-0.36}$&$0.606\pm0.043$ &$0.449\pm0.035$ &$  1.797\pm0.140$ \\
+         &$1.4$ &$  4.22^{+0.28}_{-0.26}$&$0.593\pm0.026$ &$0.369\pm0.018$ &$  1.478\pm0.071$ \\
+         &$1.6$ &$  3.33^{+0.19}_{-0.17}$&$0.590\pm0.022$ &$0.338\pm0.014$ &$  1.352\pm0.057$ \\
 \end{tabular}
 \caption{\label{t:jpdv}
-  Current density and fitted parameters for saveral positions on
-  three samples:  porosity, thickness, scale factor and etching rate.}
+  Current density and fitted parameters for several positions on
+  three samples:  porosity, thickness, and etching rate.}
 \end{table}
+The uncertainties in the fitted parameters $p$, $d$, and $v$ were
+chosen as those that increase the sum of squared errors by 10\% with
+respect to its minimum value.
 
 From the data in Table \ref{t:jpdv} we can plot the fitted porosity vs.
-the calculated density current, as shown for our three
+the calculated density current $\j_\perp$, as shown for our three
 samples in Fig. \ref{fig:p}.
@@
   \caption{Porosity vs. current density for the three samples
-    $S_1$, $S_2$, $S_3$. The data points for each sample are joined by
-    thick lines. The arrows point to data that correspond to
-    position $x'_1=0.2\,\text{cm}$, joined to the other data by thin
-    lines (see text). We include linear fits of the form
-    $p=mj_\perp+b$ to the data from
-    sample $S_3$ (thick straight line, with parameters $m=0.0134$ and
-    $b=0.5288$) and to that from all the samples (thin straight line). }
+    $S_1$, $S_2$, $S_3$. The arrows point to data that correspond to
+    position $x'_1=0.2\,\text{cm}$ (see text). We include a linear fit of the form
+    $p=mj_\perp+b$ with parameters
+    $m=(0.0122\pm0.001)\frac{\text{cm}^2}{\text{mA}}$ and
+    $b=0.551\pm.005$.
+    }
   \label{fig:p}
@@
 For this reason, we exclude those points from the following
-analysis. We made a linear fit of the form $p=mj_\perp+b$ to the data from sample $S_3$ and to
-the data from the three samples. A comparison shows that a fit to the
-data of just one sample, $S_3$, turns out to be a reasonable predictor for the
-porosity of all the samples.  From that fit we obtain that for our
-preparation conditions
+analysis. We made a linear fit of the form $p=mj_\perp+b$ obtaining
 \begin{equation}\label{eq:p}
-  p\approx 0.013\frac{\text{cm}^2}{\text{mA}} j_\perp+0.53.
-\end{equation}
-The discrepancies may be due to the ill definition of the edge of the
-sample (the position of the sealing o-ring) with respect to which we
-measured the position of the illuminating spot. A rigid displacement along
-$x$ yields mostly a horizontal shift of the results shown in
-Fig. \ref{fig:p} and that can bring them into closer agreement.
+  p\approx (0.0122\pm0.001)\frac{\text{cm}^2}{\text{mA}} j_\perp+(0.551\pm.005).
+\end{equation}
+Thought the fit is reasonably good, it is noticeable that most of the data from
+sample $S_2$ lie to the left of the fitted line while most of the data
+from the other samples lie to the right. This discrepancies may be due
+to the uncertainty in the positions $x_n$ (see Table \ref{t:xj}) due
+to the ill defined distance from the edge of the sample (which roughly
+corresponds to the position of the o-ring) to the edge of the cell. A
+deformation of the o-ring when the cell is pressed against the wafer
+would be equivalent to a rigid shift of the sample, i.e., to adding a
+constant to all the positions $x_n$. Thus it is likely that the sign
+and magnitude of that uncontrolled constant displacement changes among
+samples.
 
@@
   \caption{Etching rate vs. current density for three samples
-    $S_1$, $S_2$, $S_3$. The data points for each sample are joined by
-    thick lines. The arrows point to data that correspond to
-    position $x'_1=0.2\,\text{cm}$, joined to the other data by thin
-    lines (see text). We include linear fits of the form
-    $v=mj_\perp+b$ to the data from
-    sample $S_3$ (thick straight line, with parameters $m=0.3543$,
-    $b=0.0924$) and to that from all the samples (thin straight line). }
+    $S_1$, $S_2$, $S_3$. The arrows point to data that correspond to
+    position $x'_1=0.2\,\text{cm}$ (see text). We include a linear fit of the form
+    $v=mj_\perp+b$ to the data with parameters $m=(0.312\pm
+    0.017)(\text{cm}^2/\text{mA})(\text{nm/s})$ and
+    $b=(0.44\pm0.09)\text{nm/s}$. }
   \label{fig:v}
 \end{figure}
-As for the porosity, there are outlier points corresponding to the
-immediate proximity of the wall of the cell, but the remaining points
-lie on straight lines for each sample, and they
-may all be approximated by a linear fit to the data of just one
-sample, $S_3$, from which we get
+As for the porosity, excluding the points in the
+immediate proximity of the wall of the cell, the remaining points
+lie roughly on straight lines for each sample, and they
+may all be approximated by a linear fit to all the data, from which we get
 \begin{equation}\label{eq:v}
-  v\approx 0.35\frac{\text{cm}^2}{\text{mA}}
-  \frac{\text{nm}}{\text{s}}j_\perp + 0.092\frac{\text{nm}}{{s}}.
-\end{equation}
-The discrepancies, as in Fig. \ref{fig:p} might be due to our poor
-definition of our reference position and may be eliminated by
-introducing a rigid displacement along $x$ between the samples. For
-multilayered samples, produced by modulating the current $I$ in time,
-without changing wafers, these error source would be absent.
+  v\approx (0.312\pm0.017)\frac{\text{cm}^2}{\text{mA}}
+  \frac{\text{nm}}{\text{s}}j_\perp + (0.44\pm0.09)\frac{\text{nm}}{{s}}.
+\end{equation}
+Similarly to
+Fig. \ref{fig:p}, most data from sample $S_2$ lies to the left of the
+fitted line and most of the data from $S_1$ and $S_3$  lie to the
+right, which could be similarly explained and corrected.
+These corrections are different for layers grown on different samples,
+but for a multilayered system, produced by modulating the current $I$ in
+time, a single correction ought to be enough for all the layers.
 
@@
   \centering
-  \includegraphics[width=\textwidth]{jlr}
+  \includegraphics[width=\textwidth]{jlrb}
   \caption{Reflection $R$ of a PS film as a function of the current density
@@
 eliminated the data corresponding to position $x'_1$ on all
-samples. Furthermore, as the results corresponding to sample $S_2$ in
-Figs. \ref{fig:p} and  \ref{fig:v} seem shifted with respect to those
-of the other samples, in order to facilitate the visualization of the
-results, we artificially shifted horizontally towards the
-right their contributions to Fig. \ref{fig:Rvsjl} by
-$1\,\text{mA}/\text{cm}^2$. Notice that the experimental results may
-be grouped along bright and dark bands and that they correspond closely to
+samples. Furthermore, as discussed above and for visualization
+purposes we applied small rigid translations to the samples along the
+$x$ direction, thereby modifying $j_\perp$, before patching together
+the reflectance spectra.
+Notice that the experimental results may
+be grouped along bright and dark bands that correspond closely to
 those expected theoretically, though the experimental bands are somewhat shifted,
-especially for low current densities, and the minima are not as low.
+especially for low current densities, and their minima are not as low.
 
@@
 density along the surface of a Si sample. The expression was obtained
-by using image charge theory and a planewise summation of Coulomb
+by using image charge theory and a plane-wise summation of Coulomb
 potentials in 2D reciprocal space, and it is made up of
 a rapidly converging sum of analytical terms, just a few of which
-should be kept. This allows the characterization
+need be kept. This allows the characterization
 of the porosity of a PS layer and the etching
@@
 measured reflectance spectra at eight different positions.
-Through a optimization procedure we fitted the porosity and etching
-rate corresponding to each current density.
-We showed that an analysis of the data of just one of the samples, which we chose
-as that with the largest current density range, yielded calibration
-curves that allow the approximate prediction of the properties of the other
-samples. We believe that the discrepancies we found between samples
-are due to difficulties in defining a common reference position and
-may be eliminated through a rigid shift along the $x$ direction.
-The calibration curves can be used to design and calculate the optical
+Through an optimization procedure, we fitted the porosity and etching
+rates corresponding to each current density. We used these data to
+obtain calibration curves that allow the approximate prediction of the
+properties of porous Si samples prepared with a current density that
+spans a range of more than one order of magnitude. The
+small discrepancies we found between our samples and the fit
+are probably due to our unfortunate choice of reference point for
+measuring positions, as we used as reference the ill defined edge of
+the sample, while the important reference for our calculation is the
+edge of the wall of the electrolytic cell. Nevertheless, these
+discrepancies are reduced through a rigid shift of the coordinates
+$x_n$ used in the analysis. Our calibration curves can be used to
+design and calculate the optical
 properties of other systems prepared under similar conditions, such as
-multilayered GRIN systems from which photonic crystals, microcavities
-and sensors with position dependent properties. This is the subject of
+multilayered GRIN systems from which photonic crystals, micro-cavities
+and sensors with position-dependent properties. This is the subject of
 ongoing work. As the etching rate for the formation of porous silicon
@@
 there are no universal calibration curves. Thus, it is useful to have
-a procedure that from just one sample can produce calibration curves
-that may be employed for other samples grown in the same conditions.
+a procedure that from just one or a few samples can produce calibration curves
+that may be employed for other samples grown under similar conditions.
 
@@
 from CONACyT Basic Sciences project A-S1 30393 and from PRODEP, and is
-grateful to ICF where she spent a sabatical.
+grateful to ICF where she spent a sabbatical.
 WLM acknowledges the support of DGAPA-UNAM under grant

### 2021-01-06 paper.tex
Add references suggested by Vivechna

@@
 gradients of CdS layers
-on gold electrodes have also been obtained \cite{wang2019fabrication}.
+on gold electrodes have also been obtained
+\cite{ramaswamy_screening_2011,ramakrishnan_display_2010}.
 Among electrochemical methods, changes in the composition and doping density
@@
 Applications based on porous silicon now cover various fields such as
-chemical sensors and biosensors \cite{kumar2020porous},
+chemical sensors and biosensors \cite{kumar2020porous,lin_porous_1997,dancil_porous_1999},
 microelectronics and micro-mechanical systems (MEMS)
@@
 range of optical \cite{estevez2014porous} and opto-electronic applications
-\cite{ramadan2020fabrication}. Specifically,
+\cite{ramadan2020fabrication,namavar_optoelectronic_1993,galkin_mechanisms_2017,gelloz_electroluminescence_2018}. Specifically,
 the temporal variation of the current density results in a variation of
 porosity along the depth, allowing the easy fabrication of different kinds
-\cite{perez2018reflectivity} of 1D dielectric multilayered
-structures.
+\cite{perez2018reflectivity,ariza-flores_white_2012,ghulinyan_porous_2003,girault_porous_2017}
+of 1D dielectric multilayered structures.
 Although the conventional fabrication of PS yields laterally
@@
 The resulting porous surface can have pore sizes ranging from a few nanometers
-to  few micrometers  \cite{wang2015screening}. The range of the dimensions of the pores and
+to  few micrometers  \cite{canham_routes_2018}. The range of the dimensions of the pores and
 the corresponding  thickness range on the same chip can be controlled by
@@
 in particular, to calculate the current $j_\perp(x,y,0)$ that attacks
-the substrate to produce the PS sample.
+the substrate to produce the PS sample. As expected, the current
+at the surface $z=0$ of the sample becomes more homogeneous as the
+distance $z_0$ to the tip of the electrode and the height of the
+electrolite $c>z_0$ increase, as each term in the sum decays
+approximately exponentially with increasing $z_0$.
 Integrating over the surface of the sample we verify
@@
 From the data in Table \ref{t:jpdv} we can plot the fitted porosity vs.
-the calculated density current $\j_\perp$, as shown for our three
+the calculated density current $j_\perp$, as shown for our three
 samples in Fig. \ref{fig:p}.

### 2021-01-08 paper.tex
Eliminate digits in table 2
Highlight changes since previous submission

@@
 %\usepackage[usenames]{color}
-\usepackage{showkeys}
+%\usepackage{showkeys}
 %\usepackage{ieeetr}
@@
 \usepackage{xcolor}
-\newif{\ifinclude}
-\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
-\newcommand{\notaC}[1]{{\color{green}+C:#1+}}
-\newcommand{\notaV}[1]{{\color{red}+V:#1+}}
+% \newif{\ifinclude}
+%\usepackage{soul}
+%\sethlcolor{yellow}
+\newcommand{\hl}[1]{{\color{orange}#1}}
+%\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
+%\newcommand{\notaC}[1]{{\color{green}+C:#1+}}
+%\newcommand{\notaV}[1]{{\color{red}+V:#1+}}
 
@@
 This technique has the additional advantage of being compatible
-with very-large-scale-integration (VLSI) devices that may be
-integrated in  microelectronic circuits.
+with very-large-scale-integration (VLSI) devices \hl{that may be
+integrated in  microelectronic circuits.}
 
@@
 in particular, to calculate the current $j_\perp(x,y,0)$ that attacks
-the substrate to produce the PS sample. As expected, the current
+the substrate to produce the PS sample. \hl{As expected, the current
 at the surface $z=0$ of the sample becomes more homogeneous as the
@@
 electrolite $c>z_0$ increase, as each term in the sum decays
-approximately exponentially with increasing $z_0$.
+approximately exponentially with increasing $z_0$.}
 Integrating over the surface of the sample we verify
@@
 
-  \caption{(a): Schematic experimental set-up for
+  \caption{\hl{(a):} Schematic experimental set-up for
     the fabrication of GRIN PS structures. We show a side view of the
@@
     and a few schematic current flux
-    lines. (b) and (c): Top and side schematic views of expected resulting sample
+    lines. \hl{(b) and (c):} Top and side schematic views of expected resulting sample
     illustrating eight regions $1\ldots8$ of decreasing porosity and thickness,
@@
 y_0,z_0)=(0.2\,\text{cm},0.74\,\text{cm},0.9\,\text{cm})$.
-We manufactured three samples $S_1$, $S_2$ and $S_3$ by applying a
+We manufactured three samples \hl{$S_1$, $S_2$ and $S_3$} by applying a
 current $I_1=5\,\text{mA}$, $I_2=10\,\text{mA}$ and
@@
 
-\section{Results and Discussion}
+\section{\hl{Results and Discussion}}
 \label{sec:discussion-results}
@@
 \end{figure}
-In Fig. \ref{fig:DR1} we show the normalized current density $j_\perp(x,y,0)/I$ calculated through
+In Fig. \ref{fig:DR1} we show the \hl{normalized} current density $j_\perp(x,y,0)/I$ calculated through
 Eq. \eqref{Eq:J} at the surface of the sample for our cell, as shown
@@
  \includegraphics[width=\textwidth]{G3I20proc}
-  \caption{ Photograph of sample $S_3$ prepared as described in
+  \caption{ Photograph of sample \hl{$S_3$} prepared as described in
     Sec. \ref{sec:fabrication-ps-grin} using the same parameters as
@@
 In Fig. \ref{fig:SI3} we show a photograph of one of our samples,
-$S_3$
+\hl{$S_3$},
 prepared as described in Sec. \ref{sec:fabrication-ps-grin}, with the
@@
 sample. Here, we defined $x'_n=x_n+w$ as the distance to the edge of
-the etched sample, which corresponds to the position of the sealing o-ring,
+the etched sample, \hl{which corresponds to} the position of the sealing o-ring,
 whereas $x_n$ is the corresponding distance to the wall of the
@@
 normalized current density $j_\perp/I$ expected at the positions $n$ indicated in
-Fig. \ref{fig:SI3}. We included an estimated uncertainty in the
-distance to the wall of the cell, and the corresponding (asymmetrical)
+Fig. \ref{fig:SI3}. \hl{We included an estimated uncertainty $\Delta
+  x_n=\Delta x$ in the
+distances $x_n$ to the wall of the cell, and the corresponding (asymmetrical)
 uncertainty in the computed current density. This
@@
 it is pressed against the wafer to seal in the electrolyte, so that
-its distance to the wall of the cell is ill defined, and we estimate
-it as the radius of the o-ring. \notaL{Would it be a good idea to use a
-  larger uncertainty? 1mm? The beam spot is 2mm wide.}
-(Table \ref{t:xj}).
+its distance $x'_n-x_n\approx 0.14\text{cm}\pm\Delta x$ to the wall of
+the cell is not well determined. We estimate $\Delta x$
+as the radius of the o-ring (Table \ref{t:xj}). }
 \begin{table}
@@
   \renewcommand{\arraystretch}{1.1}
+  \hl{
     \begin{tabular}{rrr}
-     \(x'_n\)(cm) & \(x\)(cm)& \(j_\perp/I\) (\(\text{cm}^{-2})\)\\
+     $x'_n$(cm) &$x_n$(cm)&$j_\perp/I$ ($\text{cm}^{-2})$\\
      from edge& from wall&\\
@@
     \end{tabular}
+    }
   \caption{Normalized current density $j_\perp/I$ expected at different positions $x'_n$.}
@@
 
-In Fig. \ref{fig:sem} we show some SEM images of the sample $S_3$,
+In Fig. \ref{fig:sem} we show some SEM images of the sample \hl{$S_3$,}
 including top views and lateral views taken after
@@
   \caption{Top ((a), (b), and (c)) and lateral ((d), (e), and (f)) SEM
-    micrographs of the sample $S_3$ taken from a region corresponding to the left
+    micrographs of the sample \hl{$S_3$} taken from a region corresponding to the left
     side ((a) and (d)), center ((b) and (e)), and right side ((c) and
@@
 Fig. \ref{fig:sem}) and the sample becomes much thinner (panels (d) to
-(f)). We remark that these micrographs were taken at three positions
-that do not correspond to the eight locations at which we measured the
-optical spectra. Thus, we didn't use them to obtain quantitatively the
-thickness nor the porosity of the PS layer, but to verify
-qualitative our expected results (Fig. \ref{fig:DE1}) and our
-actual results (Table \ref{t:jpdv}) obtained from our calculation and
-the optical spectra, as explained below.
+(f)). \hl{We remark that these micrographs were taken at three positions
+that were not chosen to correspond to the eight locations at which we measured the
+optical spectra. Thus, we didn't use SEM measurements for the quantitative
+determination of neither the thickess nor the porosity; they were used
+for the qualitative verification of the expected (Fig. \ref{fig:DE1})
+and obtained (Table \ref{t:jpdv}) results. Actually, one of our
+goals is to show that relatively inexpensive reflectance
+measurements might be enough to characterize both the porosity and
+etching rate variations along the sample.
+}
 
@@
 film  $d$ as
-adjustable parameters. To that end we used the {\tt migrad} routine of
-the {\tt Minuit} minimization software. From the thickness we
+adjustable parameters. \hl{To that end we used the {\tt migrad} routine of
+the {\tt Minuit} minimization software.} From the thickness we
 obtained the etching rate $v=d/t$ at each position. Notice that the fits are reasonably
@@
 \renewcommand{\arraystretch}{1.1}
+\hl{
 \begin{tabular}{lrrrrr}
@@
 \hline
-$S_1$(5) &0.2 &$ 3.61^{+0.014}_{-0.03}  $&$0.562\pm0.031$ &$0.381\pm0.021$ &$   1.524\pm0.084$ \\
-         &0.4 &$ 3.36^{+0.09}_{-0.11}   $&$0.588\pm0.019$ &$0.403\pm0.014$ &$  1.611\pm0.057$  \\
-         &$0.6$  &$ 2.88^{+0.13}_{-0.14}$&$0.582\pm0.024$ &$0.342\pm0.015$ &$   1.366\pm0.060$ \\
-         &$0.8$ &$ 2.32^{+0.14}_{-0.14} $&$0.566\pm0.022$ &$0.278\pm0.011$ &$  1.113\pm0.044$ \\
-         &$1.0$ &$ 1.80^{+0.13}_{-0.12} $&$0.561\pm0.021$ &$0.224\pm0.009$ &$  0.897\pm0.034$ \\
-         &$1.2$ &$ 1.37^{+0.10}_{-0.09} $&$0.561\pm0.019$ &$0.190\pm0.007$ &$  0.761\pm0.027$ \\
-         &$1.4$ &$ 1.06^{+0.07}_{-0.06} $&$0.556\pm0.018$ &$0.153\pm0.005$ &$  0.611\pm0.021$ \\
-         &$1.6$ &$ 0.83^{+0.05}_{-0.04} $&$0.556\pm0.016$ &$0.124\pm0.004$ &$  0.497\pm0.016$ \\
-$S_2$(10) &$0.2$ &$ 7.22^{+0.03}_{-0.07} $&$0.635\pm0.040$ &$0.686\pm0.054$ &$  2.744\pm0.216$ \\
-         &$0.4$ &$ 6.72^{+0.02}_{-0,21} $&$0.644\pm0.018$ &$0.694\pm0.025$ &$  2.777\pm0.101$ \\
-         &$0.6$ &$ 5.77^{+0.27}_{-0.28} $&$0.640\pm0.033$ &$0.592\pm0.037$ &$  2.368\pm0.149$ \\
-         &$0.8$ &$ 4.64^{+0.28}_{-0.28} $&$0.624\pm0.034$ &$0.530\pm0.034$ &$  2.118\pm0.138$ \\
-         &$1.0$ &$ 3.60^{+0.25}_{-0.23} $&$0.612\pm0.030$ &$0.470\pm0.027$ &$  1.879\pm0.107$ \\
-         &$1.2$ &$ 2.75^{+0.19}_{-0.18} $&$0.603\pm0.034$ &$0.414\pm0.026$ &$  1.658\pm0.104$ \\
-         &$1.4$ &$ 2.11^{+0.14}_{-0.13} $&$0.594\pm0.028$ &$0.350\pm0.018$ &$  1.401\pm0.073$ \\
-         &$1.6$ &$ 1.67^{+0.10}_{-0.09} $&$0.583\pm0.024$ &$0.302\pm0.014$ &$  1.207\pm0.054$ \\
-$S_3$(20) &$0.2$ &$14.45^{+0.06}_{-0.14} $&$0.688\pm0.019$ &$1.208\pm0.047$ &$  4.834\pm0.188$ \\
-         &$0.4$ &$ 13.44^{+0.35}_{-0.41}$&$0.718\pm0.024$ &$1.205\pm0.057$ &$  4.820\pm0.228$ \\
-         &$0.6$ &$ 11.54^{+0.53}_{-0.55}$&$0.706\pm0.027$ &$1.050\pm0.058$ &$  4.199\pm0.232$ \\
-         &$0.8$ &$  9.29^{+0.57}_{-0.55}$&$0.636\pm0.063$ &$0.766\pm0.088$ &$  3.063\pm0.354$ \\
-         &$1.0$ &$  7.20^{+0.49}_{-0.47}$&$0.626\pm0.035$ &$0.540\pm0.037$ &$  2.158\pm0.147$  \\
-         &$1.2$ &$  5.50^{+0.38}_{-0.36}$&$0.606\pm0.043$ &$0.449\pm0.035$ &$  1.797\pm0.140$ \\
-         &$1.4$ &$  4.22^{+0.28}_{-0.26}$&$0.593\pm0.026$ &$0.369\pm0.018$ &$  1.478\pm0.071$ \\
-         &$1.6$ &$  3.33^{+0.19}_{-0.17}$&$0.590\pm0.022$ &$0.338\pm0.014$ &$  1.352\pm0.057$ \\
+$S_1$(5) &0.2 &$ 3.61^{+0.01}_{-0.03}   $&$0.56\pm0.03$ &$0.381\pm0.021$ &$  1.52\pm0.08$ \\
+         &0.4 &$ 3.36^{+0.09}_{-0.11}   $&$0.59\pm0.02$ &$0.403\pm0.014$ &$  1.61\pm0.06$  \\
+         &$0.6$  &$ 2.88^{+0.13}_{-0.14}$&$0.58\pm0.02$ &$0.342\pm0.015$ &$  1.37\pm0.06$ \\
+         &$0.8$ &$ 2.32^{+0.14}_{-0.14} $&$0.57\pm0.02$ &$0.278\pm0.011$ &$  1.11\pm0.04$ \\
+         &$1.0$ &$ 1.80^{+0.13}_{-0.12} $&$0.56\pm0.02$ &$0.224\pm0.009$ &$  0.90\pm0.03$ \\
+         &$1.2$ &$ 1.37^{+0.10}_{-0.09} $&$0.56\pm0.02$ &$0.190\pm0.007$ &$  0.76\pm0.03$ \\
+         &$1.4$ &$ 1.06^{+0.07}_{-0.06} $&$0.56\pm0.02$ &$0.153\pm0.005$ &$  0.61\pm0.02$ \\
+         &$1.6$ &$ 0.83^{+0.05}_{-0.04} $&$0.56\pm0.02$ &$0.124\pm0.004$ &$  0.50\pm0.02$ \\
+$S_2$(10) &$0.2$ &$ 7.22^{+0.03}_{-0.07}$&$0.64\pm0.04$ &$0.686\pm0.054$ &$  2.74\pm0.22$ \\
+         &$0.4$ &$ 6.72^{+0.02}_{-0,21} $&$0.64\pm0.02$ &$0.694\pm0.025$ &$  2.78\pm0.10$ \\
+         &$0.6$ &$ 5.77^{+0.27}_{-0.28} $&$0.64\pm0.03$ &$0.592\pm0.037$ &$  2.37\pm0.15$ \\
+         &$0.8$ &$ 4.64^{+0.28}_{-0.28} $&$0.62\pm0.03$ &$0.530\pm0.034$ &$  2.12\pm0.14$ \\
+         &$1.0$ &$ 3.60^{+0.25}_{-0.23} $&$0.61\pm0.03$ &$0.470\pm0.027$ &$  1.88\pm0.11$ \\
+         &$1.2$ &$ 2.75^{+0.19}_{-0.18} $&$0.60\pm0.03$ &$0.414\pm0.026$ &$  1.66\pm0.10$ \\
+         &$1.4$ &$ 2.11^{+0.14}_{-0.13} $&$0.59\pm0.03$ &$0.350\pm0.018$ &$  1.40\pm0.07$ \\
+         &$1.6$ &$ 1.67^{+0.10}_{-0.09} $&$0.58\pm0.02$ &$0.302\pm0.014$ &$  1.21\pm0.05$ \\
+$S_3$(20) &$0.2$ &$14.45^{+0.06}_{-0.14}$&$0.69\pm0.03$ &$1.208\pm0.047$ &$  4.83\pm0.19$ \\
+         &$0.4$ &$ 13.44^{+0.35}_{-0.41}$&$0.72\pm0.02$ &$1.205\pm0.057$ &$  4.82\pm0.23$ \\
+         &$0.6$ &$ 11.54^{+0.53}_{-0.55}$&$0.71\pm0.03$ &$1.050\pm0.058$ &$  4.20\pm0.23$ \\
+         &$0.8$ &$  9.29^{+0.57}_{-0.55}$&$0.64\pm0.06$ &$0.766\pm0.088$ &$  3.06\pm0.35$ \\
+         &$1.0$ &$  7.20^{+0.49}_{-0.47}$&$0.63\pm0.04$ &$0.540\pm0.037$ &$  2.16\pm0.15$  \\
+         &$1.2$ &$  5.50^{+0.38}_{-0.36}$&$0.61\pm0.04$ &$0.449\pm0.035$ &$  1.80\pm0.14$ \\
+         &$1.4$ &$  4.22^{+0.28}_{-0.26}$&$0.59\pm0.03$ &$0.369\pm0.018$ &$  1.48\pm0.07$ \\
+         &$1.6$ &$  3.33^{+0.19}_{-0.17}$&$0.59\pm0.02$ &$0.338\pm0.014$ &$  1.35\pm0.06$ \\
 \end{tabular}
+}
 \caption{\label{t:jpdv}
-  Current density and fitted parameters for several positions on
-  three samples:  porosity, thickness, and etching rate.}
+  \hl{Current density and fitted parameters for several positions on
+  three samples:  porosity, thickness, and etching rate.}}
 \end{table}
-The uncertainties in the fitted parameters $p$, $d$, and $v$ were
+\hl{The uncertainties in the fitted parameters $p$, $d$, and $v$ were
 chosen as those that increase the sum of squared errors by 10\% with
-respect to its minimum value.
-
-From the data in Table \ref{t:jpdv} we can plot the fitted porosity vs.
-the calculated density current $j_\perp$, as shown for our three
+respect to its minimum value.}
+
+From the data in Table \ref{t:jpdv} \hl{we can plot the fitted porosity vs.
+the calculated density current $j_\perp$,} as shown for our three
 samples in Fig. \ref{fig:p}.
@@
   \includegraphics[width=\textwidth]{pvsjerr}
-  \caption{Porosity vs. current density for the three samples
+  \caption{\hl{Porosity vs. current density for the three samples
     $S_1$, $S_2$, $S_3$. The arrows point to data that correspond to
@@
     $b=0.551\pm.005$.
-    }
+    }}
   \label{fig:p}
@@
 For this reason, we exclude those points from the following
-analysis. We made a linear fit of the form $p=mj_\perp+b$ obtaining
+analysis. \hl{We made a linear fit of the form $p=mj_\perp+b$ obtaining
 \begin{equation}\label{eq:p}
@@
 \end{equation}
-Thought the fit is reasonably good, it is noticeable that most of the data from
+Though the fit is reasonably good, it is noticeable that most of the data from
 sample $S_2$ lie to the left of the fitted line while most of the data
@@
 and magnitude of that uncontrolled constant displacement changes among
-samples.
-
-Similarly, we can plot the fitted etching rate vs.
-the calculated density current, as shown for our three
+samples.}
+
+\hl{Similarly, we can plot the fitted etching rate vs.
+the calculated density current,} as shown for our three
 samples in Fig. \ref{fig:v}.
@@
   \includegraphics[width=\textwidth]{vvsjerr}
-  \caption{Etching rate vs. current density for three samples
+  \caption{\hl{Etching rate vs. current density for three samples
     $S_1$, $S_2$, $S_3$. The arrows point to data that correspond to
@@
     0.017)(\text{cm}^2/\text{mA})(\text{nm/s})$ and
-    $b=(0.44\pm0.09)\text{nm/s}$. }
+    $b=(0.44\pm0.09)\text{nm/s}$. }}
   \label{fig:v}
 \end{figure}
-As for the porosity, excluding the points in the
+\hl{As for the porosity, excluding the points in the
 immediate proximity of the wall of the cell, the remaining points
 lie roughly on straight lines for each sample, and they
-may all be approximated by a linear fit to all the data, from which we get
+may all be approximated by a linear fit to all the data, from which we get}
 \begin{equation}\label{eq:v}
-  v\approx (0.312\pm0.017)\frac{\text{cm}^2}{\text{mA}}
-  \frac{\text{nm}}{\text{s}}j_\perp + (0.44\pm0.09)\frac{\text{nm}}{{s}}.
-\end{equation}
-Similarly to
+  \hl{v\approx (0.312\pm0.017)\frac{\text{cm}^2}{\text{mA}}
+  \frac{\text{nm}}{\text{s}}j_\perp +
+  (0.44\pm0.09)\frac{\text{nm}}{{s}}.
+  }
+\end{equation}
+\hl{Similarly to
 Fig. \ref{fig:p}, most data from sample $S_2$ lies to the left of the
@@
 but for a multilayered system, produced by modulating the current $I$ in
-time, a single correction ought to be enough for all the layers.
+time, a single correction ought to be enough for all the layers.}
 
@@
     panel, see text). We indicate with the numbers 1, 2, 3 the
-    data corresponding to the corresponding samples $S_1$, $S_2$
-    (shifted, see text) and  $S_3$.}
+    data corresponding to the corresponding samples \hl{$S_1$, $S_2$
+    (shifted, see text) and  $S_3$.}}
   \label{fig:Rvsjl}
@@
 eliminated the data corresponding to position $x'_1$ on all
-samples. Furthermore, as discussed above and for visualization
+samples. \hl{Furthermore, as discussed above and for visualization
 purposes we applied small rigid translations to the samples along the
 $x$ direction, thereby modifying $j_\perp$, before patching together
-the reflectance spectra.
+the reflectance spectra.}
 Notice that the experimental results may
@@
 Through an optimization procedure, we fitted the porosity and etching
-rates corresponding to each current density. We used these data to
+rates corresponding to each current density. \hl{We used these data to
 obtain calibration curves that allow the approximate prediction of the
@@
 discrepancies are reduced through a rigid shift of the coordinates
-$x_n$ used in the analysis. Our calibration curves can be used to
+$x_n$ used in the analysis. Our calibration curves can be used to}
 design and calculate the optical
@@
 there are no universal calibration curves. Thus, it is useful to have
-a procedure that from just one or a few samples can produce calibration curves
-that may be employed for other samples grown under similar conditions.
+\hl{a procedure that from just one or a few samples can produce calibration curves
+that may be employed for other samples grown under similar conditions.}
 

### 2021-01-09 paper.tex
Remove highlighted text

--- 2021-01-06 paper.tex
@@
 \usepackage{xcolor}
-\newif{\ifinclude}
-\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
-\newcommand{\notaC}[1]{{\color{green}+C:#1+}}
-\newcommand{\notaV}[1]{{\color{red}+V:#1+}}
+% \newif{\ifinclude}
+%\usepackage{soul}
+%\sethlcolor{yellow}
+%\newcommand{\hl}[1]{{\color{orange}#1}}
+%\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
+%\newcommand{\notaC}[1]{{\color{green}+C:#1+}}
+%\newcommand{\notaV}[1]{{\color{red}+V:#1+}}
 
@@
 In Fig. \ref{fig:SI3} we show a photograph of one of our samples,
-$S_3$
+$S_3$,
 prepared as described in Sec. \ref{sec:fabrication-ps-grin}, with the
@@
 normalized current density $j_\perp/I$ expected at the positions $n$ indicated in
-Fig. \ref{fig:SI3}. We included an estimated uncertainty in the
-distance to the wall of the cell, and the corresponding (asymmetrical)
+Fig. \ref{fig:SI3}. We included an estimated uncertainty $\Delta
+  x_n=\Delta x$ in the
+distances $x_n$ to the wall of the cell, and the corresponding (asymmetrical)
 uncertainty in the computed current density. This
@@
 it is pressed against the wafer to seal in the electrolyte, so that
-its distance to the wall of the cell is ill defined, and we estimate
-it as the radius of the o-ring. \notaL{Would it be a good idea to use a
-  larger uncertainty? 1mm? The beam spot is 2mm wide.}
-(Table \ref{t:xj}).
+its distance $x'_n-x_n\approx 0.14\text{cm}\pm\Delta x$ to the wall of
+the cell is not well determined. We estimate $\Delta x$
+as the radius of the o-ring (Table \ref{t:xj}).
 \begin{table}
@@
     \begin{tabular}{rrr}
-     \(x'_n\)(cm) & \(x\)(cm)& \(j_\perp/I\) (\(\text{cm}^{-2})\)\\
+     $x'_n$(cm) &$x_n$(cm)&$j_\perp/I$ ($\text{cm}^{-2})$\\
      from edge& from wall&\\
@@
 (f)). We remark that these micrographs were taken at three positions
-that do not correspond to the eight locations at which we measured the
-optical spectra. Thus, we didn't use them to obtain quantitatively the
-thickness nor the porosity of the PS layer, but to verify
-qualitative our expected results (Fig. \ref{fig:DE1}) and our
-actual results (Table \ref{t:jpdv}) obtained from our calculation and
-the optical spectra, as explained below.
+that were not chosen to correspond to the eight locations at which we measured the
+optical spectra. Thus, we didn't use SEM measurements for the quantitative
+determination of neither the thickess nor the porosity; they were used
+for the qualitative verification of the expected (Fig. \ref{fig:DE1})
+and obtained (Table \ref{t:jpdv}) results. Actually, one of our
+goals is to show that relatively inexpensive reflectance
+measurements might be enough to characterize both the porosity and
+etching rate variations along the sample.
 
@@
 \hline
-$S_1$(5) &0.2 &$ 3.61^{+0.014}_{-0.03}  $&$0.562\pm0.031$ &$0.381\pm0.021$ &$   1.524\pm0.084$ \\
-         &0.4 &$ 3.36^{+0.09}_{-0.11}   $&$0.588\pm0.019$ &$0.403\pm0.014$ &$  1.611\pm0.057$  \\
-         &$0.6$  &$ 2.88^{+0.13}_{-0.14}$&$0.582\pm0.024$ &$0.342\pm0.015$ &$   1.366\pm0.060$ \\
-         &$0.8$ &$ 2.32^{+0.14}_{-0.14} $&$0.566\pm0.022$ &$0.278\pm0.011$ &$  1.113\pm0.044$ \\
-         &$1.0$ &$ 1.80^{+0.13}_{-0.12} $&$0.561\pm0.021$ &$0.224\pm0.009$ &$  0.897\pm0.034$ \\
-         &$1.2$ &$ 1.37^{+0.10}_{-0.09} $&$0.561\pm0.019$ &$0.190\pm0.007$ &$  0.761\pm0.027$ \\
-         &$1.4$ &$ 1.06^{+0.07}_{-0.06} $&$0.556\pm0.018$ &$0.153\pm0.005$ &$  0.611\pm0.021$ \\
-         &$1.6$ &$ 0.83^{+0.05}_{-0.04} $&$0.556\pm0.016$ &$0.124\pm0.004$ &$  0.497\pm0.016$ \\
-$S_2$(10) &$0.2$ &$ 7.22^{+0.03}_{-0.07} $&$0.635\pm0.040$ &$0.686\pm0.054$ &$  2.744\pm0.216$ \\
-         &$0.4$ &$ 6.72^{+0.02}_{-0,21} $&$0.644\pm0.018$ &$0.694\pm0.025$ &$  2.777\pm0.101$ \\
-         &$0.6$ &$ 5.77^{+0.27}_{-0.28} $&$0.640\pm0.033$ &$0.592\pm0.037$ &$  2.368\pm0.149$ \\
-         &$0.8$ &$ 4.64^{+0.28}_{-0.28} $&$0.624\pm0.034$ &$0.530\pm0.034$ &$  2.118\pm0.138$ \\
-         &$1.0$ &$ 3.60^{+0.25}_{-0.23} $&$0.612\pm0.030$ &$0.470\pm0.027$ &$  1.879\pm0.107$ \\
-         &$1.2$ &$ 2.75^{+0.19}_{-0.18} $&$0.603\pm0.034$ &$0.414\pm0.026$ &$  1.658\pm0.104$ \\
-         &$1.4$ &$ 2.11^{+0.14}_{-0.13} $&$0.594\pm0.028$ &$0.350\pm0.018$ &$  1.401\pm0.073$ \\
-         &$1.6$ &$ 1.67^{+0.10}_{-0.09} $&$0.583\pm0.024$ &$0.302\pm0.014$ &$  1.207\pm0.054$ \\
-$S_3$(20) &$0.2$ &$14.45^{+0.06}_{-0.14} $&$0.688\pm0.019$ &$1.208\pm0.047$ &$  4.834\pm0.188$ \\
-         &$0.4$ &$ 13.44^{+0.35}_{-0.41}$&$0.718\pm0.024$ &$1.205\pm0.057$ &$  4.820\pm0.228$ \\
-         &$0.6$ &$ 11.54^{+0.53}_{-0.55}$&$0.706\pm0.027$ &$1.050\pm0.058$ &$  4.199\pm0.232$ \\
-         &$0.8$ &$  9.29^{+0.57}_{-0.55}$&$0.636\pm0.063$ &$0.766\pm0.088$ &$  3.063\pm0.354$ \\
-         &$1.0$ &$  7.20^{+0.49}_{-0.47}$&$0.626\pm0.035$ &$0.540\pm0.037$ &$  2.158\pm0.147$  \\
-         &$1.2$ &$  5.50^{+0.38}_{-0.36}$&$0.606\pm0.043$ &$0.449\pm0.035$ &$  1.797\pm0.140$ \\
-         &$1.4$ &$  4.22^{+0.28}_{-0.26}$&$0.593\pm0.026$ &$0.369\pm0.018$ &$  1.478\pm0.071$ \\
-         &$1.6$ &$  3.33^{+0.19}_{-0.17}$&$0.590\pm0.022$ &$0.338\pm0.014$ &$  1.352\pm0.057$ \\
+$S_1$(5) &0.2 &$ 3.61^{+0.01}_{-0.03}   $&$0.56\pm0.03$ &$0.381\pm0.021$ &$  1.52\pm0.08$ \\
+         &0.4 &$ 3.36^{+0.09}_{-0.11}   $&$0.59\pm0.02$ &$0.403\pm0.014$ &$  1.61\pm0.06$  \\
+         &$0.6$  &$ 2.88^{+0.13}_{-0.14}$&$0.58\pm0.02$ &$0.342\pm0.015$ &$  1.37\pm0.06$ \\
+         &$0.8$ &$ 2.32^{+0.14}_{-0.14} $&$0.57\pm0.02$ &$0.278\pm0.011$ &$  1.11\pm0.04$ \\
+         &$1.0$ &$ 1.80^{+0.13}_{-0.12} $&$0.56\pm0.02$ &$0.224\pm0.009$ &$  0.90\pm0.03$ \\
+         &$1.2$ &$ 1.37^{+0.10}_{-0.09} $&$0.56\pm0.02$ &$0.190\pm0.007$ &$  0.76\pm0.03$ \\
+         &$1.4$ &$ 1.06^{+0.07}_{-0.06} $&$0.56\pm0.02$ &$0.153\pm0.005$ &$  0.61\pm0.02$ \\
+         &$1.6$ &$ 0.83^{+0.05}_{-0.04} $&$0.56\pm0.02$ &$0.124\pm0.004$ &$  0.50\pm0.02$ \\
+$S_2$(10) &$0.2$ &$ 7.22^{+0.03}_{-0.07}$&$0.64\pm0.04$ &$0.686\pm0.054$ &$  2.74\pm0.22$ \\
+         &$0.4$ &$ 6.72^{+0.02}_{-0,21} $&$0.64\pm0.02$ &$0.694\pm0.025$ &$  2.78\pm0.10$ \\
+         &$0.6$ &$ 5.77^{+0.27}_{-0.28} $&$0.64\pm0.03$ &$0.592\pm0.037$ &$  2.37\pm0.15$ \\
+         &$0.8$ &$ 4.64^{+0.28}_{-0.28} $&$0.62\pm0.03$ &$0.530\pm0.034$ &$  2.12\pm0.14$ \\
+         &$1.0$ &$ 3.60^{+0.25}_{-0.23} $&$0.61\pm0.03$ &$0.470\pm0.027$ &$  1.88\pm0.11$ \\
+         &$1.2$ &$ 2.75^{+0.19}_{-0.18} $&$0.60\pm0.03$ &$0.414\pm0.026$ &$  1.66\pm0.10$ \\
+         &$1.4$ &$ 2.11^{+0.14}_{-0.13} $&$0.59\pm0.03$ &$0.350\pm0.018$ &$  1.40\pm0.07$ \\
+         &$1.6$ &$ 1.67^{+0.10}_{-0.09} $&$0.58\pm0.02$ &$0.302\pm0.014$ &$  1.21\pm0.05$ \\
+$S_3$(20) &$0.2$ &$14.45^{+0.06}_{-0.14}$&$0.69\pm0.03$ &$1.208\pm0.047$ &$  4.83\pm0.19$ \\
+         &$0.4$ &$ 13.44^{+0.35}_{-0.41}$&$0.72\pm0.02$ &$1.205\pm0.057$ &$  4.82\pm0.23$ \\
+         &$0.6$ &$ 11.54^{+0.53}_{-0.55}$&$0.71\pm0.03$ &$1.050\pm0.058$ &$  4.20\pm0.23$ \\
+         &$0.8$ &$  9.29^{+0.57}_{-0.55}$&$0.64\pm0.06$ &$0.766\pm0.088$ &$  3.06\pm0.35$ \\
+         &$1.0$ &$  7.20^{+0.49}_{-0.47}$&$0.63\pm0.04$ &$0.540\pm0.037$ &$  2.16\pm0.15$  \\
+         &$1.2$ &$  5.50^{+0.38}_{-0.36}$&$0.61\pm0.04$ &$0.449\pm0.035$ &$  1.80\pm0.14$ \\
+         &$1.4$ &$  4.22^{+0.28}_{-0.26}$&$0.59\pm0.03$ &$0.369\pm0.018$ &$  1.48\pm0.07$ \\
+         &$1.6$ &$  3.33^{+0.19}_{-0.17}$&$0.59\pm0.02$ &$0.338\pm0.014$ &$  1.35\pm0.06$ \\
 \end{tabular}
@@
   v\approx (0.312\pm0.017)\frac{\text{cm}^2}{\text{mA}}
-  \frac{\text{nm}}{\text{s}}j_\perp + (0.44\pm0.09)\frac{\text{nm}}{{s}}.
+  \frac{\text{nm}}{\text{s}}j_\perp +
+  (0.44\pm0.09)\frac{\text{nm}}{{s}}.
 \end{equation}

### 2021-01-22 paper.tex
Rename figures to fig1, fig2, etc.
Rename bibliography file
Correct couple of spelling mistakes

@@
   \centering
-  \includegraphics[width=\textwidth]{celdan1.png}
+  \includegraphics[width=\textwidth]{fig1.png}
   \caption{Prism shaped electrolytic cell with a rectangular base of
@@
   \centering
-  \includegraphics[width=\textwidth]{paper-1}
+  \includegraphics[width=\textwidth]{fig2}
   \caption{Top view of the $z=z_0$ plane of the fictitious system formed by reflections of
@@
   \centering
-  \includegraphics[width=\textwidth]{paper-2}
+  \includegraphics[width=\textwidth]{fig3}
   \caption{Side view of the $y=y_0$ plane of the fictitious system formed by reflections of
@@
 distance $z_0$ to the tip of the electrode and the height of the
-electrolite $c>z_0$ increase, as each term in the sum decays
+electrolyte $c>z_0$ increase, as each term in the sum decays
 approximately exponentially with increasing $z_0$.
@@
   \centering
-  \includegraphics[width=.8\textwidth]{paper-3}\\[12pt]
-  \includegraphics[width=.8\textwidth]{paper-4}\\[12pt]
-  \includegraphics[width=.8\textwidth]{paper-5}
+  \includegraphics[width=.8\textwidth]{fig4a}\\[12pt]
+  \includegraphics[width=.8\textwidth]{fig4b}\\[12pt]
+  \includegraphics[width=.8\textwidth]{fig4c}
 
@@
   \begin{picture}(400,300)
-    \put(0,0){\includegraphics[width=.8\textwidth]{j_Ivsx.png}}
-    \put(160,140){\includegraphics[trim=50 50 70 80,clip,width=.4\textwidth]{j_Ivsxy.png}}
+    \put(0,0){\includegraphics[width=.8\textwidth]{fig5a.png}}
+    \put(160,140){\includegraphics[trim=50 50 70 80,clip,width=.4\textwidth]{fig5b.png}}
   \end{picture}
@@
  \centering
- \includegraphics[width=\textwidth]{G3I20proc}
+ \includegraphics[width=\textwidth]{fig6}
   \caption{ Photograph of sample $S_3$ prepared as described in
@@
   \centering
-  \includegraphics[width=.3\textwidth]{sema}
-  \includegraphics[width=.3\textwidth]{semb}
-  \includegraphics[width=.3\textwidth]{semc}
-  \includegraphics[width=.3\textwidth]{semd}
-  \includegraphics[width=.3\textwidth]{seme}
-  \includegraphics[width=.3\textwidth]{semf}
+  \includegraphics[width=.3\textwidth]{fig7a}
+  \includegraphics[width=.3\textwidth]{fig7b}
+  \includegraphics[width=.3\textwidth]{fig7c}
+  \includegraphics[width=.3\textwidth]{fig7d}
+  \includegraphics[width=.3\textwidth]{fig7e}
+  \includegraphics[width=.3\textwidth]{fig7f}
   \caption{Top ((a), (b), and (c)) and lateral ((d), (e), and (f)) SEM
@@
 optical spectra. Thus, we didn't use SEM measurements for the quantitative
-determination of neither the thickess nor the porosity; they were used
+determination of neither the thickness nor the porosity; they were used
 for the qualitative verification of the expected (Fig. \ref{fig:DE1})
@@
   \centering
-  \includegraphics[width=\textwidth]{R5migradvslambda}
+  \includegraphics[width=\textwidth]{fig8}
   \caption{Reflectance spectra at different positions
@@
   \centering
-  \includegraphics[width=\textwidth]{R10migradvslambda}
+  \includegraphics[width=\textwidth]{fig9}
   \caption{Reflectance spectra at different positions
@@
   \centering
-  \includegraphics[width=\textwidth]{R20migradvslambda}
+  \includegraphics[width=\textwidth]{fig10}
   \caption{Reflectance spectra at different positions
@@
   \centering
-  \includegraphics[width=\textwidth]{pvsjerr}
+  \includegraphics[width=\textwidth]{fig11}
   \caption{Porosity vs. current density for the three samples
@@
   \centering
-  \includegraphics[width=\textwidth]{vvsjerr}
+  \includegraphics[width=\textwidth]{fig12}
   \caption{Etching rate vs. current density for three samples
@@
   \centering
-  \includegraphics[width=\textwidth]{jlrb}
+  \includegraphics[width=\textwidth]{fig13}
   \caption{Reflection $R$ of a PS film as a function of the current density
@@
 \bibliographystyle{unsrt}
-\bibliography{bibligrin}
+\bibliography{bibliography}
 \end{document}
